### 2024-09-04 index.Rmd
treees

---
title: "Lab journal"
author: "by: Vero"
bibliography: references.bib

---

```{r, install remotely, globalsettings, echo=FALSE, warning=FALSE, results='hide'}
# install.packages("remotes")
# remotes::install_github("rlesur/klippy") # is what makes it possible to hover over top right of code on website to COPY AND PASTE it 
```

```{r, globalsettings, echo=FALSE, warning=FALSE, results='hide'}
library(knitr)

knitr::opts_chunk$set(echo = TRUE)
opts_chunk$set(tidy.opts=list(width.cutoff=100),tidy=TRUE, warning = FALSE, message = FALSE,comment = "#>", cache=TRUE, class.source=c("test"), class.output=c("test2"))
options(width = 100)
rgl::setupKnitr()

colorize <- function(x, color) {sprintf("<span style='color: %s;'>%s</span>", color, x) }

```

```{r klippy, echo=FALSE, include=TRUE}
klippy::klippy(position = c('top', 'right'))
#klippy::klippy(color = 'darkred')
#klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done')
```

----

<!--- The ---- is a visual line (page break looking mf) on the 
website 
Always ADD A SPACE BETWEEN A PAE BREAK AND the next comment, otherwise it will appear on page --->

<!--- This is the best way to write a comment. 
It also demonstrates, you can add html directly in your rmarkdown file. See: https://www.w3schools.com/html/html_comments.asp --->

<!--- to use a multi column page we use Pandoc's fenced Div. 
see here: https://bookdown.org/yihui/rmarkdown-cookbook/multi-column.html 
But please note, we are not here to make a beautiful website, our intention is just to have a quick lab journal up and running --->

:::: {.columns}
::: {.column width="50%"}

# My Lab Journal
Last compiled on `r format(Sys.time(), '%B, %Y')`

*Describe lab journal here.*

<br>

----

## Open Science

Everyone can fork this repository. Use this example to journal your lab work and assignments.

We, Jochem Tolsma and Bas Hofstra, use this repository for our Social Network Analysis For Social Scientists course [@SNASS]. <!--- this is a reference, stored in references.bib. It will be automatically added at the bottom of the page --->

treeeeees

:::

::: {.column width="50%"}

![](images/cover.jpg)

:::
::::

## How to use

1. Fork the repository for this website and follow instructions on `README` to get started [here](https://github.com/JochemTolsma/labjournal).

2. Journal your work, by editing the .Rmd-files

3. ...

4. Change everything to make it your own!

<br>

Use the top menu to navigate through the journal.

----

# References

### 2024-09-11 RQdraft1.Rmd
week1push

---
title: "RQdraft1"
author: "Vero"
date: "2024-09-10"
output: html_document
---

```{r, globalsettings, echo=FALSE, warning=FALSE, results='hide'}
library(knitr)

knitr::opts_chunk$set(echo = TRUE)
opts_chunk$set(tidy.opts=list(width.cutoff=100),tidy=TRUE, warning = FALSE, message = FALSE,comment = "#>", cache=TRUE, class.source=c("test"), class.output=c("test2"))
options(width = 100)
rgl::setupKnitr()

colorize <- function(x, color) {sprintf("<span style='color: %s;'>%s</span>", color, x) }

```

```{r klippy, echo=FALSE, include=TRUE}
klippy::klippy(position = c('top', 'right'))
#klippy::klippy(color = 'darkred')
#klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done')
```
# Brainstorm
- Journal prestige 
- Gender homphily 
- Age 
- repeated publications 
- nr of publications
- Dutch or English text publications
- gender segregation and field of publication (journal field)

---

# Research Questions
RQ1a: 
  To what extent does gender homophily occur across all co-publications of the staff of the Sociology Department and Computing Sciences at Radboud University?

RQ1b:
  To what extent do the two departments differ in their gender homophily?

RQ2:
  To what extent does gender homophily in co-publishing influence the prestige of the publication journal?

RQ3:
  To what extent do structural network effects influence the gender homophily of each department?

- (1a+b needed? Would like more concise, not ask uneccessary questions)
- (2&3 seem random and disconnected; Journal prestige of interest tho, how to best include?)
- (necessity to have RQ3 that asks about structural networks effects?)

## Horta et al. (2022)
- male researchers preferred to co-publish with other male researchers, 
- and female researchers preferred to collaborate with other females.
- researchers of approximately similar ages tended to collaborate more with each other.
- geographical, cultural, & institutional proximity were strongest predictors of collaboration.
- analysis shows that in the social sciences, ACQUIRED attributes (particularly preferences regarding research agendas) take precedence over ASCRIBED attributes (e.g. gender or age)

- Horta et al. (2022) - RQs:
  - (1) What homophily preferences determine research collaborations among higher education researchers? 
  - (2) What are the most powerful homophily indicators in research collaborations in higher education research?

## Kwiek & Roszka (2021)
- Most male scientists collaborate solely with males.
- Most female scientists, in contrast, do not collaborate with females at all.
- All-female authorship marginal, all-male authorship pervasive, in all age groups.
- Articles written in mixed-sex collaboration published in more prestigious journals.

---

# References:

Horta, H., Feng, S., & Santos, J. M. (2022). Homophily in higher education research: a perspective based on co-authorships. Scientometrics, 127(1), 523–543. https://doi.org/10.1007/s11192-021-04227-z

Kwiek, M., & Roszka, W. (2021). Gender-based homophily in research: A large-scale study of man-woman collaboration. Journal of Informetrics, 15(3), 101171. https://doi.org/10.1016/j.joi.2021.101171

-

### 2024-09-11 _week1.Rmd
week1push

---
title: "_SNASS tutorial"
author: "TreesDude"
date: "2024-09-04"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

```{r token}
#install.packages("gitcreds")
# gitcreds::gitcreds_set()
```

```{r}
# TO MAKENEW CHUNKS: ctrl + Alt + i

```

```{r}
########################### Title: Introducation to R for SNA Author: J Tolsma version: 30-10-2019

# start with clean workspace
rm(list = ls())

# install.packages I will need later here
install.packages("installr")  # you  first install packages
install.packages("foreign")
require(foreign)  # used to read in spss data files
require(tidyverse)

# define workdirectory, note the double backslashes
setwd("C:\Users\Vero\OneDrive - Radboud Universiteit\Documents\GitHub\labjournal")  # change to your own workdirectory
```

```{r}
# ignore the warnings ?read.spss note that I have saved the data files in a folder called
# 'addfiles'.

cv08 <- foreign::read.spss("addfiles\\Cultural_Changes_2008.sav", use.value.labels = T, to.data.frame = T)
cv10 <- foreign::read.spss("addfiles\\Cultural_Changes_2010.sav", use.value.labels = T, to.data.frame = T)

# normally I think setting use.value.labels=F is more convenient. Thus lets load the data again but
# now without labels
cv08_nolab <- foreign::read.spss("addfiles\\Cultural_Changes_2008.sav", use.value.labels = F, to.data.frame = T)
cv10_nolab <- foreign::read.spss("addfiles\\Cultural_Changes_2010.sav", use.value.labels = F, to.data.frame = T)

# finally, import the data using haven
cv08_haven <- haven::read_spss("addfiles\\Cultural_Changes_2008.sav")
cv10_haven <- haven::read_spss("addfiles\\Cultural_Changes_2010.sav")
```

### 2024-09-11 index.Rmd
week1push

@@
 
+```{r token}
+#install.packages("gitcreds")
+# gitcreds::gitcreds_set()
+```
+
+```{r}
+# ctrl + Alt + i  to MAKE CHUNKS
+
+```
+
 ----
@@
 website 
-Always ADD A SPACE BETWEEN A PAE BREAK AND the next comment, otherwise it will appear on page --->
+Always ADD A SPACE BETWEEN A PAGE BREAK AND the next comment, otherwise it will appear on page --->
 

### 2024-09-11 testjt.Rmd
week1push

---
title: "t62al"
author: "by: Vero"
bibliography: references.bib

---

```{r, globalsettings, echo=FALSE, warning=FALSE, results='hide'}
library(knitr)

knitr::opts_chunk$set(echo = TRUE)
opts_chunk$set(tidy.opts=list(width.cutoff=100),tidy=TRUE, warning = FALSE, message = FALSE,comment = "#>", cache=TRUE, class.source=c("test"), class.output=c("test2"))
options(width = 100)
rgl::setupKnitr()

colorize <- function(x, color) {sprintf("<span style='color: %s;'>%s</span>", color, x) }

```

```{r klippy, echo=FALSE, include=TRUE}
klippy::klippy(position = c('top', 'right'))
#klippy::klippy(color = 'darkred')
#klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done')
```

<!--- 
HOW TO MAKE TOKENS:
install.packages("gitcreds") 
gitcreds::gitcreds_set() --->

<!--- TO MAKE NEW CHUNKS: ctrl + Alt + i --->

```{r, eval=FALSE}
########################### Title: Introduction to R for SNA Author: J Tolsma version: 30-10-2019

# start with clean workspace
rm(list = ls())

# install.packages I will need later here
install.packages("installr")  # you  first install packages
install.packages("foreign")
install.packages("tidyverse")
```

```{r}
require(foreign)  # used to read in spss data files
require(tidyverse)

# define workdirectory, note the double backslashes
# setwd("C:\Users\Vero\OneDrive - Radboud Universiteit\Documents\GitHub\labjournal")  # change to your own workdirectory
```
```{r Cheat sheet}
###########Cheat Sheet##########

# variable labels 
# c("primary", "secondary", "tertiary")

# Operator symbols: 
# $
# == logical operator. What are the other logical operators in R?
# [] is used to subset elements from an object (e.g. dataframe/vector/matrix)
#  NA is used in R to define missing values. It means Not Applicable.

# Functions:
# summary(), attributes(), attr(), table(), names(), head(), fix(), View()

# as.character() 
# as.numeric()

# in tidy: 
  #the piping operator 
  # %>%, 
  # the left is transported to the (first argument of the) function on the right. Thus, in the example below, you see that in the second and third call to mutate I don’t have to tell the function which dataset I am using.

# mean(), 
# rowMeans(), 
# rowSums, 
# cbind(), 
# is.na(), 
# ifelse().

# logicals FALSE and TRUE can be summed? (FALSE equals 0 and TRUE equals 1).
```

```{r}
# ignore the warnings ?read.spss note that I have saved the data files in a folder called
# 'addfiles'.

cv08 <- foreign::read.spss("tutorial_data\\Cultural_Changes_2008.sav", use.value.labels = T, to.data.frame = T)
cv10 <- foreign::read.spss("tutorial_data\\Cultural_Changes_2010.sav", use.value.labels = T, to.data.frame = T)

# normally I think setting use.value.labels=F is more convenient. Thus lets load the data again but
# now WITHOUT LABELS 
cv08_nolab <- foreign::read.spss("tutorial_data\\Cultural_Changes_2008.sav", use.value.labels = F, to.data.frame = T)
cv10_nolab <- foreign::read.spss("tutorial_data\\Cultural_Changes_2010.sav", use.value.labels = F, to.data.frame = T)

# finally, import the data using haven
cv08_haven <- haven::read_spss("tutorial_data\\Cultural_Changes_2008.sav")
cv10_haven <- haven::read_spss("tutorial_data\\Cultural_Changes_2010.sav")

str(cv08) # str = asks for structure of an object 
str(cv08_nolab)
str(cv08_haven)

# acsessing variable:
# datasetname$variablename

str(cv08$lftop)  # a factor
str(cv08_nolab$lftop)  # a numeric variable
str(cv08_haven$lftop)  # a 'dbl+lbl' this stands for doubles, or real numbers, which are labeled  
# next to the data itself, attributes are stored
attributes(cv08$lftop)
attributes(cv08_nolab$lftop)
attributes(cv08_haven$lftop)

# to access specific attributes
attr(cv08_haven$lftop, "labels")

summary(cv08$lftop)
summary(cv08_nolab$lftop)
summary(cv08_haven$lftop)
table(cv08_haven$lftop, useNA = "always")

#LOOKING AT DATA 
names(cv08_haven)
summary(cv08_haven)
head(cv08_haven)

# fix(cv08_haven) #will produce an error
# fix(cv08)
# View(cv08_haven)

```

----
```{r A.7.1 Define Missings}

str(cv08_haven$lftop)
summary(cv08_haven$lftop)
attr(cv08_haven$lftop, "labels")
table(cv08_haven$lftop, useNA = "always")

# copy the original variable in a new one, and attach it to the dataset. 
cv08$lftop_new <- cv08$lftop

# replace those values of our new variable
cv08$lftop_new[cv08$lftop_new == "Onbekend"] <- NA

#Check if recode works 
table(cv08$lftop_new, useNA = "always")

levels(cv08$lftop_new)

# as numeric variable not as a factor (categorical).
str(cv08$lftop_new)

cv08$agen <- as.numeric(as.character(cv08$lftop_new))  
# how clumsy. we first convert the factor to a string and then to a numeric variable.
table(cv08$agen, useNA = "always")

str(cv08$agen)

```

```{r A.7.2 Tidy }

# install.packages("tidyverse")
library(tidyverse)

# ‘mutate’ the original dataset by adding a variable.
cv08_haven <- mutate(cv08_haven, lftop_new = lftop)

#Replace missings.Note: 99 is the “onbekend” category.
cv08_haven$lftop_new <- na_if(cv08_haven$lftop_new, 99)

#Normally: combine these two steps into one
cv08_haven <- mutate(cv08_haven, lftop_new = na_if(lftop, 99))

#check
table(cv08_haven$lftop_new, useNA = "always")

```
----
```{r A.8 Recode variables}

# var006n = second variable lets us recode the variable education (in CV08)
#create a new variable educ3 with three levels:
#1. primary
#2. secondary
#3. tertiary

#levels
levels(cv08$var006n)

# table 
table(cv08$var006n, useNA = "always")

# lets make it a numeric variable first
cv08$educn <- as.numeric(cv08$var006n)
# check
table(cv08$educn, useNA = "always")

# start with an empty variable
cv08$educ3 <- NA
# fill category by category
cv08$educ3[cv08$educn == 2 | cv08$educn == 3] <- 1
cv08$educ3[cv08$educn > 3 & cv08$educn < 8] <- 2
cv08$educ3[cv08$educn > 7 & cv08$educn < 11] <- 3

# check
table(cv08$educ3, useNA = "always")

prop.table(table(cv08$educ3, useNA = "always"))

# now educ3 is a numeric variable, we want it as factor
cv08$educ3 <- as.factor(cv08$educ3)
table(cv08$educ3, useNA = "always")

levels(cv08$educ3) <- c("primary", "secondary", "tertiary")
table(cv08$educ3, useNA = "always")
```

```{r A.8.2 Tidy}

# dplyr::recode   #doesnt work on labelled variables that were imported via haven package

# install.packages('labelled')
require(labelled)  # to be able to use the recode function on haven labelled variables

# inspect variable
str(cv08_haven$var006n)

attr(cv08_haven$var006n, "labels")

table(cv08_haven$var006n, useNA = "always")

# recode values, all missings as one value
cv08_haven <- mutate(cv08_haven, educ3 = recode(var006n, `-3` = -9, `-1` = 1, `1` = 1, `2` = 2, `3` = 2,
    `4` = 2, `5` = 2, `6` = 3, `7` = 3, `8` = 3, `10` = -9), .keep_value_labels = FALSE)

# replace missing values with NA.
cv08_haven <- mutate(cv08_haven, educ3 = na_if(educ3, -9))

# make educ3 a factor
cv08_haven <- mutate(cv08_haven, educ3 = factor(educ3, levels = c(1, 2, 3), labels = c("primary", "secondary",
    "tertiary")))

# check
table(cv08_haven$educ3, useNA = "always")

#the piping operator 
  # %>%, 
  # the left is transported to the (first argument of the) function on the right. Thus, in the example below, you see that in the second and third call to mutate I don’t have to tell the function which dataset I am using.
# in Base R (since 4.1.0) operator: |>

cv08_haven <- mutate(cv08_haven, educ3 = recode(var006n, `-3` = -9, `-1` = 1, `1` = 1, `2` = 2, `3` = 2,
    `4` = 2, `5` = 2, `6` = 3, `7` = 3, `8` = 3, `10` = -9), .keep_value_labels = FALSE) %>%
    mutate(educ3 = na_if(educ3, -9)) %>%
    mutate(educ3 = factor(educ3, levels = c(1, 2, 3), labels = c("primary", "secondary", "tertiary")))

# even more tidy:
cv08_haven <- cv08_haven %>%
    mutate(educ3 = recode(var006n, `-3` = -9, `-1` = 1, `1` = 1, `2` = 2, `3` = 2, `4` = 2, `5` = 2,
        `6` = 3, `7` = 3, `8` = 3, `10` = -9), .keep_value_labels = FALSE) %>%
    mutate(educ3 = na_if(educ3, -9)) %>%
    mutate(educ3 = factor(educ3, levels = c(1, 2, 3), labels = c("primary", "secondary", "tertiary")))

# the MOST tidy:
cv08_haven <- cv08_haven %>%
    mutate(educ3 = recode(var006n, `-3` = -9, `-1` = 1, `1` = 1, `2` = 2, `3` = 2, `4` = 2, `5` = 2,
        `6` = 3, `7` = 3, `8` = 3, `10` = -9, .keep_value_labels = FALSE), educ3 = na_if(educ3, -9),
        educ3 = factor(educ3, levels = c(1, 2, 3), labels = c("primary", "secondary", "tertiary")))
```
----
```{r A.9 Means and counting specific values}
# A.9.1. R Base

# Step 1: Look at the various 
summary(cv08$int055)
summary(cv08$int056)
summary(cv08$int057)

# Step 2: Make numeric 
cv08$int055n <- as.numeric(cv08$int055)
table(cv08$int055n, useNA = "always")

cv08$int056n <- as.numeric(cv08$int056)
table(cv08$int056n, useNA = "always")

cv08$int057n <- as.numeric(cv08$int057)
table(cv08$int057n, useNA = "always")

# Step 3: Define missings and recode
cv08$int055n[cv08$int055n < 5] <- NA
cv08$int055n <- cv08$int055n - 4

cv08$int056n[cv08$int056n < 5] <- NA
cv08$int056n <- cv08$int056n - 4

cv08$int057n[cv08$int057n < 5] <- NA
cv08$int057n <- cv08$int057n - 4

# Step 4: Calculate means
# How does the function mean work in R?
mean(cv08$int055n)  # whoops
mean(cv08$int055n, na.rm = TRUE)  # works.  but not what we want. 
# na.rm -> tells function whether or not to remove NA values from the calculation

mean(c(cv08$int055n, cv08$int056n, cv08$int057n), na.rm = T)  # works but not what we want.

# calculate a mean for each row/respondent. 
testmeans <- rowMeans(cbind(cv08$int055n, cv08$int056n, cv08$int057n), na.rm = T)
head(testmeans)  # yes!
# head() function : Return the First or Last Part of an Object

# What we really want is a mean but only if there is a maximum of 1 NA in the three variables.
# lets first count how many missings we have for each respondent
nmis <- rowSums(is.na(cbind(cv08$int055n, cv08$int056n, cv08$int057n)))

# ?is.na ?rowSums
testmeans <- ifelse(nmis < 2, testmeans, NA)

# add the calculated means to our dataset
cv08$int_mean <- testmeans

```

----

----

# References

### 2024-09-11 week2.Rmd
week1push

--- 2024-09-11 testjt.Rmd
@@
 ---
-title: "t62al"
-author: "by: Vero"
-bibliography: references.bib
-
+title: "week2"
+author: "Vero"
+date: "2024-09-10"
+output: html_document
 ---
@@
 ```
-
-<!--- 
-HOW TO MAKE TOKENS:
-install.packages("gitcreds") 
-gitcreds::gitcreds_set() --->
-
-<!--- TO MAKE NEW CHUNKS: ctrl + Alt + i --->
-
-```{r, eval=FALSE}
-########################### Title: Introduction to R for SNA Author: J Tolsma version: 30-10-2019
-
-# start with clean workspace
-rm(list = ls())
-
-# install.packages I will need later here
-install.packages("installr")  # you  first install packages
-install.packages("foreign")
-install.packages("tidyverse")
-```
-
-```{r}
-require(foreign)  # used to read in spss data files
-require(tidyverse)
-
-# define workdirectory, note the double backslashes
-# setwd("C:\Users\Vero\OneDrive - Radboud Universiteit\Documents\GitHub\labjournal")  # change to your own workdirectory
-```
-```{r Cheat sheet}
-###########Cheat Sheet##########
-
-# variable labels 
-# c("primary", "secondary", "tertiary")
-
-# Operator symbols: 
-# $
-# == logical operator. What are the other logical operators in R?
-# [] is used to subset elements from an object (e.g. dataframe/vector/matrix)
-#  NA is used in R to define missing values. It means Not Applicable.
-
-# Functions:
-# summary(), attributes(), attr(), table(), names(), head(), fix(), View()
-
-# as.character() 
-# as.numeric()
-
-# in tidy: 
-  #the piping operator 
-  # %>%, 
-  # the left is transported to the (first argument of the) function on the right.
-Thus, in the example below, you see that in the second and third call to mutate I don’t have to tell the function which dataset I am using.
-
-# mean(), 
-# rowMeans(), 
-# rowSums, 
-# cbind(), 
-# is.na(), 
-# ifelse().
-
-# logicals FALSE and TRUE can be summed? (FALSE equals 0 and TRUE equals 1).
-```
-
-```{r}
-# ignore the warnings ?read.spss note that I have saved the data files in a folder called
-# 'addfiles'.
-
-cv08 <- foreign::read.spss("tutorial_data\\Cultural_Changes_2008.sav", use.value.labels = T, to.data.frame = T)
-cv10 <- foreign::read.spss("tutorial_data\\Cultural_Changes_2010.sav", use.value.labels = T, to.data.frame = T)
-
-# normally I think setting use.value.labels=F is more convenient. Thus lets load the data again but
-# now WITHOUT LABELS 
-cv08_nolab <- foreign::read.spss("tutorial_data\\Cultural_Changes_2008.sav", use.value.labels = F, to.data.frame = T)
-cv10_nolab <- foreign::read.spss("tutorial_data\\Cultural_Changes_2010.sav", use.value.labels = F, to.data.frame = T)
-
-# finally, import the data using haven
-cv08_haven <- haven::read_spss("tutorial_data\\Cultural_Changes_2008.sav")
-cv10_haven <- haven::read_spss("tutorial_data\\Cultural_Changes_2010.sav")
-
-str(cv08) # str = asks for structure of an object 
-str(cv08_nolab)
-str(cv08_haven)
-
-# acsessing variable:
-# datasetname$variablename
-
-str(cv08$lftop)  # a factor
-str(cv08_nolab$lftop)  # a numeric variable
-str(cv08_haven$lftop)  # a 'dbl+lbl' this stands for doubles, or real numbers, which are labeled  
-# next to the data itself, attributes are stored
-attributes(cv08$lftop)
-attributes(cv08_nolab$lftop)
-attributes(cv08_haven$lftop)
-
-# to access specific attributes
-attr(cv08_haven$lftop, "labels")
-
-summary(cv08$lftop)
-summary(cv08_nolab$lftop)
-summary(cv08_haven$lftop)
-table(cv08_haven$lftop, useNA = "always")
-
-#LOOKING AT DATA 
-names(cv08_haven)
-summary(cv08_haven)
-head(cv08_haven)
-
-# fix(cv08_haven) #will produce an error
-# fix(cv08)
-# View(cv08_haven)
-
-```
-
-----
-```{r A.7.1 Define Missings}
-
-str(cv08_haven$lftop)
-summary(cv08_haven$lftop)
-attr(cv08_haven$lftop, "labels")
-table(cv08_haven$lftop, useNA = "always")
-
-# copy the original variable in a new one, and attach it to the dataset. 
-cv08$lftop_new <- cv08$lftop
-
-# replace those values of our new variable
-cv08$lftop_new[cv08$lftop_new == "Onbekend"] <- NA
-
-#Check if recode works 
-table(cv08$lftop_new, useNA = "always")
-
-levels(cv08$lftop_new)
-
-# as numeric variable not as a factor (categorical).
-str(cv08$lftop_new)
-
-cv08$agen <- as.numeric(as.character(cv08$lftop_new))  
-# how clumsy. we first convert the factor to a string and then to a numeric variable.
-table(cv08$agen, useNA = "always")
-
-str(cv08$agen)
-
-```
-
-```{r A.7.2 Tidy }
-
-# install.packages("tidyverse")
-library(tidyverse)
-
-# ‘mutate’ the original dataset by adding a variable.
-cv08_haven <- mutate(cv08_haven, lftop_new = lftop)
-
-#Replace missings.Note: 99 is the “onbekend” category.
-cv08_haven$lftop_new <- na_if(cv08_haven$lftop_new, 99)
-
-#Normally: combine these two steps into one
-cv08_haven <- mutate(cv08_haven, lftop_new = na_if(lftop, 99))
-
-#check
-table(cv08_haven$lftop_new, useNA = "always")
-
-```
-----
-```{r A.8 Recode variables}
-
-# var006n = second variable lets us recode the variable education (in CV08)
-#create a new variable educ3 with three levels:
-#1. primary
-#2. secondary
-#3. tertiary
-
-#levels
-levels(cv08$var006n)
-
-# table 
-table(cv08$var006n, useNA = "always")
-
-# lets make it a numeric variable first
-cv08$educn <- as.numeric(cv08$var006n)
-# check
-table(cv08$educn, useNA = "always")
-
-# start with an empty variable
-cv08$educ3 <- NA
-# fill category by category
-cv08$educ3[cv08$educn == 2 | cv08$educn == 3] <- 1
-cv08$educ3[cv08$educn > 3 & cv08$educn < 8] <- 2
-cv08$educ3[cv08$educn > 7 & cv08$educn < 11] <- 3
-
-# check
-table(cv08$educ3, useNA = "always")
-
-prop.table(table(cv08$educ3, useNA = "always"))
-
-# now educ3 is a numeric variable, we want it as factor
-cv08$educ3 <- as.factor(cv08$educ3)
-table(cv08$educ3, useNA = "always")
-
-levels(cv08$educ3) <- c("primary", "secondary", "tertiary")
-table(cv08$educ3, useNA = "always")
-```
-
-```{r A.8.2 Tidy}
-
-# dplyr::recode   #doesnt work on labelled variables that were imported via haven package
-
-# install.packages('labelled')
-require(labelled)  # to be able to use the recode function on haven labelled variables
-
-# inspect variable
-str(cv08_haven$var006n)
-
-attr(cv08_haven$var006n, "labels")
-
-table(cv08_haven$var006n, useNA = "always")
-
-# recode values, all missings as one value
-cv08_haven <- mutate(cv08_haven, educ3 = recode(var006n, `-3` = -9, `-1` = 1, `1` = 1, `2` = 2, `3` = 2,
-    `4` = 2, `5` = 2, `6` = 3, `7` = 3, `8` = 3, `10` = -9), .keep_value_labels = FALSE)
-
-# replace missing values with NA.
-cv08_haven <- mutate(cv08_haven, educ3 = na_if(educ3, -9))
-
-# make educ3 a factor
-cv08_haven <- mutate(cv08_haven, educ3 = factor(educ3, levels = c(1, 2, 3), labels = c("primary", "secondary",
-    "tertiary")))
-
-# check
-table(cv08_haven$educ3, useNA = "always")
-
-#the piping operator 
-  # %>%, 
-  # the left is transported to the (first argument of the) function on the right.
-Thus, in the example below, you see that in the second and third call to mutate I don’t have to tell the function which dataset I am using.
-# in Base R (since 4.1.0) operator: |>
-
-cv08_haven <- mutate(cv08_haven, educ3 = recode(var006n, `-3` = -9, `-1` = 1, `1` = 1, `2` = 2, `3` = 2,
-    `4` = 2, `5` = 2, `6` = 3, `7` = 3, `8` = 3, `10` = -9), .keep_value_labels = FALSE) %>%
-    mutate(educ3 = na_if(educ3, -9)) %>%
-    mutate(educ3 = factor(educ3, levels = c(1, 2, 3), labels = c("primary", "secondary", "tertiary")))
-
-# even more tidy:
-cv08_haven <- cv08_haven %>%
-    mutate(educ3 = recode(var006n, `-3` = -9, `-1` = 1, `1` = 1, `2` = 2, `3` = 2, `4` = 2, `5` = 2,
-        `6` = 3, `7` = 3, `8` = 3, `10` = -9), .keep_value_labels = FALSE) %>%
-    mutate(educ3 = na_if(educ3, -9)) %>%
-    mutate(educ3 = factor(educ3, levels = c(1, 2, 3), labels = c("primary", "secondary", "tertiary")))
-
-# the MOST tidy:
-cv08_haven <- cv08_haven %>%
-    mutate(educ3 = recode(var006n, `-3` = -9, `-1` = 1, `1` = 1, `2` = 2, `3` = 2, `4` = 2, `5` = 2,
-        `6` = 3, `7` = 3, `8` = 3, `10` = -9, .keep_value_labels = FALSE), educ3 = na_if(educ3, -9),
-        educ3 = factor(educ3, levels = c(1, 2, 3), labels = c("primary", "secondary", "tertiary")))
-```
-----
-```{r A.9 Means and counting specific values}
-# A.9.1. R Base
-
-# Step 1: Look at the various 
-summary(cv08$int055)
-summary(cv08$int056)
-summary(cv08$int057)
-
-# Step 2: Make numeric 
-cv08$int055n <- as.numeric(cv08$int055)
-table(cv08$int055n, useNA = "always")
-
-cv08$int056n <- as.numeric(cv08$int056)
-table(cv08$int056n, useNA = "always")
-
-cv08$int057n <- as.numeric(cv08$int057)
-table(cv08$int057n, useNA = "always")
-
-# Step 3: Define missings and recode
-cv08$int055n[cv08$int055n < 5] <- NA
-cv08$int055n <- cv08$int055n - 4
-
-cv08$int056n[cv08$int056n < 5] <- NA
-cv08$int056n <- cv08$int056n - 4
-
-cv08$int057n[cv08$int057n < 5] <- NA
-cv08$int057n <- cv08$int057n - 4
-
-# Step 4: Calculate means
-# How does the function mean work in R?
-mean(cv08$int055n)  # whoops
-mean(cv08$int055n, na.rm = TRUE)  # works.  but not what we want. 
-# na.rm -> tells function whether or not to remove NA values from the calculation
-
-mean(c(cv08$int055n, cv08$int056n, cv08$int057n), na.rm = T)  # works but not what we want.
-
-# calculate a mean for each row/respondent. 
-testmeans <- rowMeans(cbind(cv08$int055n, cv08$int056n, cv08$int057n), na.rm = T)
-head(testmeans)  # yes!
-# head() function : Return the First or Last Part of an Object
-
-# What we really want is a mean but only if there is a maximum of 1 NA in the three variables.
-# lets first count how many missings we have for each respondent
-nmis <- rowSums(is.na(cbind(cv08$int055n, cv08$int056n, cv08$int057n)))
-
-# ?is.na ?rowSums
-testmeans <- ifelse(nmis < 2, testmeans, NA)
-
-# add the calculated means to our dataset
-cv08$int_mean <- testmeans
-
-```
-
-----
-
-----
-
-# References

### 2024-09-11 RQdraft1.Rmd
week1push-dptm

@@
 RQ1a: 
-  To what extent does gender homophily occur across all co-publications of the staff of the Sociology Department and Computing Sciences at Radboud University?
+  To what extent does gender homophily occur across all co-publications of the staff of the Sociology Department and Political Science Department at Radboud University?
 

### 2024-09-11 week2.Rmd
updatedmenusweek2

@@
 ---
-title: "week2"
-author: "Vero"
+title: "Week2 - Descriptives"
+author: "Veroooo"
 date: "2024-09-10"
@@
 ```
+
+```{r}
+# install.packages("igraph")
+library(igraph)
+#install.packages("sna")
+library(sna)
+
+# Create a 4x4 matrix filled with 0's
+matrix_zeros <- matrix(0, nrow = 4, ncol = 4)
+
+# Add a tie between node 1 and node 3 by placing a 1
+matrix_zeros[1, 3] <- 1  # From node 1 to node 3
+
+# Print the matrix
+print(matrix_zeros)
+
+matrix_graph <- graph.adjacency(matrix_zeros)
+sna::triad.census(matrix_zeros)
+
+# output shows the count of each of the 16 possible configurations of triads  
+    # so if below 003 it says e.g. 2, that means that the configuration 003 (A,B,C, the empty graph) is possible 2 times
+
+```
+
+```{r}
+# 003
+# A,B,C, the empty graph.
+
+# 012
+# A->B, C, the graph with a single directed edge.
+
+# 102
+# A<->B, C, the graph with a mutual connection between two vertices.
+
+# 021D
+# A<-B->C, the out-star.
+
+# 021U
+# A->B<-C, the in-star.
+
+# 021C
+# A->B->C, directed line.
+
+# 111D
+# A<->B<-C.
+
+# 111U
+# A<->B->C.
+
+# 030T
+# A->B<-C, A->C.
+
+# 030C
+# A<-B<-C, A->C.
+
+# 201
+# A<->B<->C.
+
+# 120D
+# A<-B->C, A<->C.
+
+# 120U
+# A->B<-C, A<->C.
+
+# 120C
+# A->B->C, A<->C.
+
+# 210
+# A->B<->C, A<->C.
+
+# 300
+# A<->B<->C, A<->C, the complete graph.
+
+```
+
+```{r}
+# install.packages("RSiena")
+library(RSiena)
+#install.packages("igraph")
+# library(igraph)
+#install.packages("sna")
+library(sna)
+
+?s501 # Network 1 data: excerpt from "Teenage Friends and Lifestyle Study" data.
+dim(s501) # get dimensions of data
+
+tenxten <- s501[1:10,1:10] # select a 10 x 10 matrix [rows and columns are divided by comma])
+
+tenxten_graph <- graph.adjacency(tenxten) # make matrixa graph object 
+plot(tenxten_graph) # make plot of network
+
+# assignment: give (on ego level) descriptive statistics on all kind of centrality measures
+
+```

### 2024-09-11 RQdraft1.Rmd
updatedmenusweek2
usingrefsandnotes

--- 2024-09-11 RQdraft1.Rmd
@@
 title: "RQdraft1"
-author: "Vero"
+author: "Verooo"
 date: "2024-09-10"
@@
 ```
+
 # Brainstorm
+
 -   Journal prestige
@@
 
----
+------------------------------------------------------------------------
 
 # Research Questions
-RQ1a: 
-  To what extent does gender homophily occur across all co-publications of the staff of the Sociology Department and Computing Sciences at Radboud University?
 
-RQ1b:
-  To what extent do the two departments differ in their gender homophily?
+**RQ1a:**
 
-RQ2:
-  To what extent does gender homophily in co-publishing influence the prestige of the publication journal?
+To what extent does gender homophily occur across all co-publications of the staff of the Sociology Department and Political Science Department at Radboud University?
 
-RQ3:
-  To what extent do structural network effects influence the gender homophily of each department?
+RQ1b: To what extent do the two departments differ in their gender homophily?
+
+RQ2: To what extent does gender homophily in co-publishing influence the prestige of the publication journal?
+
+RQ3: To what extent do structural network effects influence the gender homophily of each department?
 
@@
 ## Horta et al. (2022)
+
 -   male researchers preferred to co-publish with other male researchers,
+
 -   and female researchers preferred to collaborate with other females.
+
 -   researchers of approximately similar ages tended to collaborate more with each other.
+
 -   geographical, cultural, & institutional proximity were strongest predictors of collaboration.
+
 -   analysis shows that in the social sciences, ACQUIRED attributes (particularly preferences regarding research agendas) take precedence over ASCRIBED attributes (e.g. gender or age)
@@
 -   Horta et al. (2022) - RQs:
-  - (1) What homophily preferences determine research collaborations among higher education researchers? 
-  - (2) What are the most powerful homophily indicators in research collaborations in higher education research?
+
+    1.  What homophily preferences determine research collaborations among higher education researchers?
+
+    ```{=html}
+    <!-- -->
+    ```
+    2.  What are the most powerful homophily indicators in research collaborations in higher education research?
 
 ## Kwiek & Roszka (2021)
+
 -   Most male scientists collaborate solely with males.
@@
 
----
+------------------------------------------------------------------------
 
@@
 
-Horta, H., Feng, S., & Santos, J. M. (2022). Homophily in higher education research: a perspective based on co-authorships. Scientometrics, 127(1), 523–543. https://doi.org/10.1007/s11192-021-04227-z
+Horta, H., Feng, S., & Santos, J.
+M.
+(2022).
+Homophily in higher education research: a perspective based on co-authorships.
+Scientometrics, 127(1), 523–543.
+<https://doi.org/10.1007/s11192-021-04227-z>
 
-Kwiek, M., & Roszka, W. (2021). Gender-based homophily in research: A large-scale study of man-woman collaboration. Journal of Informetrics, 15(3), 101171. https://doi.org/10.1016/j.joi.2021.101171
-
--
+Kwiek, M., & Roszka, W. (2021). Gender-based homophily in research: A large-scale study of man-woman collaboration. Journal of Informetrics, 15(3), 101171. <https://doi.org/10.1016/j.joi.2021.101171>

### 2024-09-11 RQdraft2.Rmd
usingrefsandnotes

--- 2024-09-11 RQdraft1.Rmd
@@
 ---
-title: "RQdraft1"
-author: "Vero"
-date: "2024-09-10"
+title: "RQdraft2"
+author: "Verooo"
+date: "2024-09-11"
 output: html_document
@@
 # Brainstorm
-- Journal prestige 
-- Gender homphily 
-- Age 
-- repeated publications 
-- nr of publications
-- Dutch or English text publications
-- gender segregation and field of publication (journal field)
 
@@
 
-# Research Questions
+# Research Questions (old, replace with new ones!)
 RQ1a: 
-  To what extent does gender homophily occur across all co-publications of the staff of the Sociology Department and Computing Sciences at Radboud University?
+  To what extent does gender homophily occur across all co-publications of the staff of the Sociology Department and Political Science Department at Radboud University?
 
@@
   To what extent do structural network effects influence the gender homophily of each department?
-
-- (1a+b needed? Would like more concise, not ask uneccessary questions)
-- (2&3 seem random and disconnected; Journal prestige of interest tho, how to best include?)
-- (necessity to have RQ3 that asks about structural networks effects?)
 
@@
 Kwiek, M., & Roszka, W. (2021). Gender-based homophily in research: A large-scale study of man-woman collaboration. Journal of Informetrics, 15(3), 101171. https://doi.org/10.1016/j.joi.2021.101171
-
--

### 2024-09-11 week2.Rmd
usingrefsandnotes

@@
 
+# Triads - 4x4 matrix
+
 ```{r}
@@
 
+## Triad census output
+
 ```{r}
+
 # 003
@@
 
+# heading (learning to take notes with R)
+
+note:
+
+1.  kjhg\
+2.  lkjh
+    -   kjh
+    -   kjhgf
+
+text here \$ N = ß \Sigma lss \sqrt {sd } \$ text again
+
+# Centrality measures (practice with a network)
+
 ```{r}
@@
 
-# assignment: give (on ego level) descriptive statistics on all kind of centrality measures
+sna::triad.census(tenxten)
 
+# Nr. of possible Triad compositions:
+  # 10*9*8 / 6 =
+
+# Play around with Centrality Measures 
 ```
+
+# START WRITING INTRO (UPDATE RESEARCH QUESTIONS)
+
+Try to be specific show that you UNDERSTAND INTER-DEPENDENCIES
+
+MAKE A LISTOFTHE TYPE OF DATA YOU WILL NEED Relational attributes, etc.
+
+Update Lab journal
+
+[USING THE REFERENCES]{.underline}
+
+Open: references.bib take "bibTex Citation" if you want to use it, use \@ - symbol and use the word behind the { \
+In this example, it would be \@ "rmarkdown2018" (without the quotation marks
+
+@Book{rmarkdown2018, title = {R Markdown: The Definitive Guide}, author = {Yihui Xie and J.J.
+Allaire and Garrett Grolemund}, publisher = {Chapman and Hall/CRC}, address = {Boca Raton, Florida}, year = {2018}, note = {ISBN 9781138359338}, url = {<https://bookdown.org/yihui/rmarkdown>}, }

### 2024-09-14 week2.Rmd
week2 edits

@@
 
-# heading (learning to take notes with R)
-
-note:
-
-1.  kjhg\
-2.  lkjh
-    -   kjh
-    -   kjhgf
-
-text here \$ N = ß \Sigma lss \sqrt {sd } \$ text again
-
 # Centrality measures (practice with a network)
@@
 
-# START WRITING INTRO (UPDATE RESEARCH QUESTIONS)
+# HW: START WRITING INTRO (UPDATE RESEARCH QUESTIONS)
 
@@
 
-MAKE A LISTOFTHE TYPE OF DATA YOU WILL NEED Relational attributes, etc.
+MAKE A LIST OF THE TYPE OF DATA YOU WILL NEED Relational attributes, etc.
 
@@
 
-[USING THE REFERENCES]{.underline}
+Also still redo what i missed in class: make centrality measures of the 10x10 matrix
 
-Open: references.bib take "bibTex Citation" if you want to use it, use \@ - symbol and use the word behind the { \
-In this example, it would be \@ "rmarkdown2018" (without the quotation marks
+# heading (learning to take notes with R)
+
+note:
+
+1.  kjhg\
+2.  lkjh
+    -   kjh
+    -   kjhgf
+
+text here
+$$
+N = ß \Sigma lss \sqrt {sd }
+$$
+text again
+
+text here
+$$
+N = 1 
+$$
+text again
+
+# USING THE REFERENCES
+
+Open: references.bib
+
+take "bibTex Citation" from online and put it in there
+
+if you want to use it, use \@ - symbol and use the word behind the " { "\
+In this example, it would be \@ "rmarkdown2018" (without the quotation marks)
 

### 2024-09-16 RQdraft2.Rmd
ch8menuinsert

--- 2024-09-11 RQdraft1.Rmd
@@
 ---
-title: "RQdraft1"
+title: "RQdraft2"
 author: "Verooo"
-date: "2024-09-10"
+date: "2024-09-11"
 output: html_document
@@
 
--   Journal prestige
--   Gender homphily
--   Age
--   repeated publications
--   nr of publications
--   Dutch or English text publications
--   gender segregation and field of publication (journal field)
-
 ------------------------------------------------------------------------
 
-# Research Questions
+# Research Questions (old, replace with new ones!)
 
-**RQ1a:**
-
-To what extent does gender homophily occur across all co-publications of the staff of the Sociology Department and Political Science Department at Radboud University?
+RQ1a: To what extent does gender homophily occur across all co-publications of the staff of the Sociology Department and Political Science Department at Radboud University?
 
@@
 RQ3: To what extent do structural network effects influence the gender homophily of each department?
-
--   (1a+b needed? Would like more concise, not ask uneccessary questions)
--   (2&3 seem random and disconnected; Journal prestige of interest tho, how to best include?)
--   (necessity to have RQ3 that asks about structural networks effects?)
 
@@
 
-    1.  What homophily preferences determine research collaborations among higher education researchers?
+    -
 
-    ```{=html}
-    <!-- -->
-    ```
-    2.  What are the most powerful homophily indicators in research collaborations in higher education research?
+        (1) What homophily preferences determine research collaborations among higher education researchers?
+
+    -
+
+        (2) What are the most powerful homophily indicators in research collaborations in higher education research?
 
@@
 Kwiek, M., & Roszka, W. (2021). Gender-based homophily in research: A large-scale study of man-woman collaboration. Journal of Informetrics, 15(3), 101171. <https://doi.org/10.1016/j.joi.2021.101171>
+
+# Data types needed for research
+
++------------------------------------+---------------------------------------------------------+--------------------------------------------------------------------------------------------------------+
+| Variable                           | Potential measurement                                   | Notes                                                                                                  |
++====================================+=========================================================+========================================================================================================+
+| **Actor attributes**               |                                                         |                                                                                                        |
++------------------------------------+---------------------------------------------------------+--------------------------------------------------------------------------------------------------------+
+| Gender                             | Google Scholar: \                                       | What about gender neutral names?
+If we go by this principle, then gender neutral names = non-binary ??
+|
+|                                    | Name ➙ Look up in gendered list whether Woman or Man    |                                                                                                        |
++------------------------------------+---------------------------------------------------------+--------------------------------------------------------------------------------------------------------+
+|                                    | Linked-in: \                                            | Not everyone puts their pronouns on linkedin\                                                          |
+|                                    | Pronouns                                                | And: not everyone who uses e.g.
+She/her pronouns is a Woman                                            |
++------------------------------------+---------------------------------------------------------+--------------------------------------------------------------------------------------------------------+
+| High prestige publication (prior)  | If the author had a publication in a journal that ....\ |                                                                                                        |
+|                                    | before the publication of the paper in question         |                                                                                                        |
++------------------------------------+---------------------------------------------------------+--------------------------------------------------------------------------------------------------------+
+| **Relational Attributes**          |                                                         |                                                                                                        |
++------------------------------------+---------------------------------------------------------+--------------------------------------------------------------------------------------------------------+
+| Initiation of the co-authorship    | First author of paper = initiator                       |                                                                                                        |
++------------------------------------+---------------------------------------------------------+--------------------------------------------------------------------------------------------------------+
+| Paper                              | A paper people have co-authorship on                    | How prevent from counting double?
+\                                                                    |
+|                                    |                                                         | Overall: systematic approach to webscrape?
+|
+|                                    | Signifier: DOI?
+|                                                                                                        |
++------------------------------------+---------------------------------------------------------+--------------------------------------------------------------------------------------------------------+
+|                                    |                                                         |                                                                                                        |
++------------------------------------+---------------------------------------------------------+--------------------------------------------------------------------------------------------------------+
+
+: Data types

### 2024-09-16 Webscraping-Chapter8-tutorial.Rmd
ch8menuinsert

---
title: "Chapter 8 - SNASS"
author: "Verooo"
date: "2024-09-16"
output: html_document
---
#########################################Title: Webscraping in R Author: Bas Hofstra Version:
######################################### 29-07-2

# start with clean workspace
rm(list = ls())

# install.packages('data.table')
library(data.table)  # mainly for faster data handling
library(tidyverse)  # I assume you already installed this one!
#install.packages('httr') # we don't need this for now require(httr)
install.packages("xml2")
require(xml2)
install.packages("rvest")
require(rvest)
install.packages("devtools")
require(devtools)
#Note we're doing something different here. We're installing a *latest* version directly from
#GitHub This is because the released version of this packages contains some errors!
devtools::install_github("jkeirstead/scholar")

require(scholar)

#define workdirectory, note the double *backslashes* if you're on windows setwd('/yourpathhere)'

### 2024-09-17 RQdraft2.Rmd
ch8contd

@@
 
-+------------------------------------+---------------------------------------------------------+--------------------------------------------------------------------------------------------------------+
++-----------------------------------+---------------------------------------------------------+--------------------------------------------------------------------------------------------------------+
 | Variable                          | Potential measurement                                   | Notes                                                                                                  |
-+====================================+=========================================================+========================================================================================================+
++===================================+=========================================================+========================================================================================================+
 | **Actor attributes**              |                                                         |                                                                                                        |
-+------------------------------------+---------------------------------------------------------+--------------------------------------------------------------------------------------------------------+
-| Gender                             | Google Scholar: \                                       | What about gender neutral names?
-If we go by this principle, then gender neutral names = non-binary ??
-|
++-----------------------------------+---------------------------------------------------------+--------------------------------------------------------------------------------------------------------+
+| Name                              | Name from university department website                 | using "read_html()" function                                                                           |
++-----------------------------------+---------------------------------------------------------+--------------------------------------------------------------------------------------------------------+
+| Gender                            | Google Scholar:\                                        | What about gender neutral names? If we go by this principle, then gender neutral names = non-binary ?? |
 |                                   | Name ➙ Look up in gendered list whether Woman or Man    |                                                                                                        |
-+------------------------------------+---------------------------------------------------------+--------------------------------------------------------------------------------------------------------+
-|                                    | Linked-in: \                                            | Not everyone puts their pronouns on linkedin\                                                          |
-|                                    | Pronouns                                                | And: not everyone who uses e.g.
-She/her pronouns is a Woman                                            |
-+------------------------------------+---------------------------------------------------------+--------------------------------------------------------------------------------------------------------+
++-----------------------------------+---------------------------------------------------------+--------------------------------------------------------------------------------------------------------+
+|                                   | Linked-in:\                                             | Not everyone puts their pronouns on linkedin\                                                          |
+|                                   | Pronouns                                                | And: not everyone who uses e.g. She/her pronouns is a Woman                                            |
++-----------------------------------+---------------------------------------------------------+--------------------------------------------------------------------------------------------------------+
 | High prestige publication (prior) | If the author had a publication in a journal that ....\ |                                                                                                        |
 |                                   | before the publication of the paper in question         |                                                                                                        |
-+------------------------------------+---------------------------------------------------------+--------------------------------------------------------------------------------------------------------+
++-----------------------------------+---------------------------------------------------------+--------------------------------------------------------------------------------------------------------+
+| Affiliation                       | Name of university they work at (radboud university)    | Taken from university website about department                                                         |
++-----------------------------------+---------------------------------------------------------+--------------------------------------------------------------------------------------------------------+
 | **Relational Attributes**         |                                                         |                                                                                                        |
-+------------------------------------+---------------------------------------------------------+--------------------------------------------------------------------------------------------------------+
++-----------------------------------+---------------------------------------------------------+--------------------------------------------------------------------------------------------------------+
 | Initiation of the co-authorship   | First author of paper = initiator                       |                                                                                                        |
-+------------------------------------+---------------------------------------------------------+--------------------------------------------------------------------------------------------------------+
-| Paper                              | A paper people have co-authorship on                    | How prevent from counting double?
-\                                                                    |
-|                                    |                                                         | Overall: systematic approach to webscrape?
-|
-|                                    | Signifier: DOI?
-|                                                                                                        |
-+------------------------------------+---------------------------------------------------------+--------------------------------------------------------------------------------------------------------+
++-----------------------------------+---------------------------------------------------------+--------------------------------------------------------------------------------------------------------+
+| Paper                             | A paper people have co-authorship on                    | How prevent from counting double?\                                                                     |
+|                                   |                                                         | Overall: systematic approach to webscrape?                                                             |
+|                                   | Signifier: DOI?                                         |                                                                                                        |
++-----------------------------------+---------------------------------------------------------+--------------------------------------------------------------------------------------------------------+
 |                                   |                                                         |                                                                                                        |
-+------------------------------------+---------------------------------------------------------+--------------------------------------------------------------------------------------------------------+
++-----------------------------------+---------------------------------------------------------+--------------------------------------------------------------------------------------------------------+
 

### 2024-09-17 Webscraping-Chapter8-tutorial.Rmd
ch8contd

@@
 ---
-#########################################Title: Webscraping in R Author: Bas Hofstra Version:
-######################################### 29-07-2
+
+###Title: Webscraping in R Author: Bas Hofstra Version: \### 29-07-2
+
+# Set-up
+
+```{r}
 
@@
 #install.packages('httr') # we don't need this for now require(httr)
-install.packages("xml2")
+#install.packages("devtools")
+require(devtools)
+
+#install.packages("rvest")
+require(rvest)
+# rvest:This is the explanation the writers of the package give: “rvest is new package that makes it easy to scrape (or harvest) data from html web pages.” Seems like something we need, a package that stores information from webpages into relatively structured data that we can then query/manipulate.
+
+#install.packages("xml2")
 require(xml2)
-install.packages("rvest")
-require(rvest)
-install.packages("devtools")
-require(devtools)
+#xml2:This is what the writers of the package say about it: “Work with XML files using a simple, consistent interface.” So we can manipulate the data scraped with rvest, using the xml2 package functions
+
 #Note we're doing something different here. We're installing a *latest* version directly from
@@
 
+library(dplyr)
 #define workdirectory, note the double *backslashes* if you're on windows setwd('/yourpathhere)'
+
+```
+
+# Get anchor data
+
+goal: get to know \
+(i) who the Radboud University Department of Sociology staff is, \
+(ii) what they publish with respect to scientific work, and \
+(iii) who they collaborate with.
+
+```{r, Anchor data}
+soc_staff <- read_html("https://web.archive.org/web/20230528153336/https://www.ru.nl/sociology/research/staff/") #extracts the source html of a webpage
+
+head(soc_staff)
+
+#which object? 
+class(soc_staff)
+
+#so we need to find WHERE the table is located in the html 'inspect element' in mozilla firefox or
+# view page source' and you see that everything AFTER /td in the 'body' of the page seems to be
+# the table we do need
+soc_staff <- soc_staff %>%
+    rvest::html_nodes("body") %>%
+    xml2::xml_find_all("//td") %>%
+    rvest::html_text()
+
+soc_staff
+
+#Assigning even and odd rows to 'fodd' and 'feven' (bc the output just lists the left and right side of the table interchangably)
+fodd <- function(x) x%%2 != 0
+feven <- function(x) x%%2 == 0
+
+# How long are the data? nstaf beinhalted wie viele staff members es gibt ABER ist z.Z. noch falsch weil jede zweite Zeile information und kein Name ist) 
+nstaff <- length(soc_staff)
+nstaff
+
+#make variable that holds all the names (aka. all the information in uneven rows)
+soc_names <- soc_staff[fodd(1:nstaff)] 
+# needs to be 0:nstaff instead of 1:nstaff 
+  #(because the list positions start with 0 NOT with 1)
+#OR insert the fODD function here 
+  # because the names are actually in the uneven rows, as opposed to the SNASS example where they are in even-numbered rows 
+head(soc_names)
+
+#
+soc_expertise <- soc_staff[feven(1:nstaff)]  #in the 1 until 94st number, get the even elements
+head(soc_expertise)
+
+#put the two vectors [variables in Vero's mind] (names and exptertise) together in a data frame (list) 
+soc_df <- data.frame(cbind(soc_names, soc_expertise))  #columnbind those and we have a DF for soc staff!
+
+# inspect in environment -> Data
+
+#inspect again, and remove the rows we don't need (check for yourself to be certain!)
+delrows <- which(soc_df$soc_names == "Staff:" | soc_df$soc_names == "PhD:" | soc_df$soc_names == "External PhD:" |
+    soc_df$soc_names == "Guest researchers:" | soc_df$soc_names == "Other researchers:")
+
+soc_df <- soc_df[-delrows, ]
+
+# inspect in environment -> Data
+
+```
+
+# Extract names and last names 
+```{r, name extraction}
+# gsub   is a function that remove something and replaces it with something else
+
+# select only last names aka. DELETE everything BEHIND a comma 
+# [because the staff is listed with the last name in first place like e.g.: Müller, K. (Katrin) MSc]
+
+  #Last name seems to be everything before the comma
+soc_df$last_name <- gsub(",.*$", "", soc_df$soc_names)
+
+# first name is everything between brackets
+
+# stringr PACKAGE NEEDED
+# install.packages("stringr")
+# STILL DOESNT WORK BC NEWEST stringr PACKAGE FUCKS SHIT UP 
+# INSTALL AN OLDER VERSION OF THE PACKAGE:
+
+  # install.packages("devtools")
+  # devtools::install_version("stringr", version = "1.4.1")
+# soc_df$first_name <- str_extract_all(soc_df$soc_names, "(?<=\\().+?(?=\\))", simplify = TRUE)
+
+# still does not work 
+#My own attempt at fixing above mistake:
+ # soc_df$first_name_TRY <-substr(soc_df$soc_names, start = "(", stop = ")")
+
+require(tidyverse)
+soc_df$first_name <- str_extract_all(soc_df$soc_names, "(?<=\\().+?(?=\\))", simplify = TRUE)
+
+ view(soc_df)
+
+```
+
+## clean up names 
+```{r, clean up names }
+
+soc_df$last_name <- gsub(" J. \\(Jansje\\) van MSc", "", soc_df$last_name)
+soc_df$first_name <- tolower(soc_df$first_name)  # everything to lower!
+soc_df$last_name <- tolower(soc_df$last_name)
+# trimws() looses all spacing before and after (if you specify 'both') a character string
+soc_df$last_name <- trimws(soc_df$last_name, which = c("both"), whitespace = "[ \t\r\n]")
+soc_df$first_name <- trimws(soc_df$first_name, which = c("both"), whitespace = "[ \t\r\n]")
+soc_df$soc_expertise <- trimws(soc_df$soc_expertise, which = c("both"), whitespace = "[ \t\r\n]")
+soc_df$soc_names <- trimws(soc_df$soc_names, which = c("both"), whitespace = "[ \t\r\n]")
+```
+
+## make new variable (staff being from Radboud)
+
+```{r, new variable}
+# create a variable that contains a character string “radboud university” for all.
+soc_df$affiliation <- "radboud university"
+view(soc_df)
+
+```
+
+# Google Scholar Profiles and Publication
+## reminder: for loops 
+```{r, for loop}
+# The 'for loop': for every i in a vector (can be numbers, strings, etc.), say 1 to 10, you can do
+# 'something'
+for (i in 1:10) {
+    print(i)  # So for every i from 1 to 10, we print i, see what happens!
+}
+
+# # or do something more complicated p <- rnorm(10, 0, 1) # draw 10 normally distributed numbers
+# with mean 0 and SD 1 (so z-scores, essentially) plot(density(p)) # relatively, normal, right?  u
+# <- 0 # make an element we can fill up in the loop below for (i in 1:10) { u[i] <- p[i]*p[i] # get
+# p-squared for every i-th element in vector p print(u[i]) # and print that squared element }
+```
+## linking a SINGLE staff member to their google scholar link 
+```{r}
+
+soc_df$gs_id <- ""  # we set an empty identifier
+
+# using get_scholar_id()
+# The function get_scholar_id needs a last name, first name, and affiliation.
+
+require(scholar)
+#downloaded function:
+get_scholar_id_fix <- function (last_name = "", first_name = "", affiliation = NA)
+{
+  if (!any(nzchar(c(first_name, last_name))))
+    stop("At least one of first and last name must be specified!")
+  site <- getOption("scholar_site")
+  url <- paste0(site, "/citations?view_op=search_authors&mauthors=",
+                first_name, "+", last_name, "&hl=en&oi=ao")
+  page <- get_scholar_resp(url)
+  if (is.null(page))
+    return(NA)
+  aa <- httr::content(page, as = "text")
+  # added by Bas Hofstra: bugfix for IDs that have a dash ("-")
+  ids <- substring(aa, regexpr(";user=", aa))
+  ids <- substr(ids, 1, 19) # error prone, but unsure how to solve otherwise
+  # if (nchar(stringr::str_extract_all(string = aa, pattern = ";user=[[:alnum:]]+[[:punct:]]")[[1]][1]) < 18) {
+  #   ids <- stringr::str_extract_all(string = aa, pattern = ";user=[[:alnum:]]+[[:punct:]]+[[:alnum:]]+[[:punct:]]")
+  # } else {
+  #   ids <- stringr::str_extract_all(string = aa, pattern = ";user=[[:alnum:]]+[[:punct:]]")
+  # }
+  if (length(unlist(ids)) == 0) {
+    message("No Scholar ID found.")
+    return(NA)
+  }
+  ids <- ids %>% unlist %>% gsub(";user=|[[:punct:]]$", "",
+                                 .) %>% unique
+  if (length(ids) > 1) {
+    profiles <- lapply(ids, scholar::get_profile)
+    if (is.na(affiliation)) {
+      x_profile <- profiles[[1]]
+      warning("Selecting first out of ", length(profiles),
+              " candidate matches.")
+    }
+    else {
+      which_profile <- sapply(profiles, function(x) {
+        stringr::str_count(string = x$affiliation, pattern = stringr::coll(affiliation,
+                                                                           ignore_case = TRUE))
+      })
+      if (all(which_profile == 0)) {
+        warning("No researcher found at the indicated affiliation.")
+        return(NA)
+      }
+      else {
+        x_profile <- profiles[[which(which_profile !=
+                                       0)]]
+      }
+    }
+  }
+  else {
+    x_profile <- scholar::get_profile(id = ids)
+  }
+  return(x_profile$id)
+}
+
+#TRYING get_scholar_id from ONE staff member first
+
+# SETTING SOURCE:
+#source("C:/Users/Vero/OneDrive - Radboud Universiteit/Documents/GitHub/labjournal")  
+# DOES NOT WORK BUT WORKS IF YOU DEFINE FUNCTION IN THE SAME SCRIPT YOU ARE WORKINGIN 
+# Put the function_fix.R in your working directory, we need this first line.
+# Vero: I put the function in an R-Script and saved it in the same folder as the script I have open rn.
+
+get_scholar_id_fix(last_name = "tolsma", first_name = "jochem", affiliation = "radboud university")
+
+get_profile("Iu23-90AAAAJ")  # Jochem's profile
+
+```
+### get scholar publications, citations
+```{r, pubs and citations}
+get_publications("Iu23-90AAAAJ")  # Jochem's pubs
+
+get_citation_history("Iu23-90AAAAJ")  # Jochem's citation history
+```
+### get collaborators 
+```{r, collaborators}
+jochem_coauthors <- get_coauthors("Iu23-90AAAAJ", n_coauthors = 50, n_deep = 1)  
+# Jochem's collaborators and their co-authors!
+
+```
+
+## plot network of single staff member 
+```{r, plot}
+plot_coauthors(get_coauthors("Iu23-90AAAAJ", n_coauthors = 20, n_deep = 1), size_labels = 2)  
+# Doesn't look like much yet, but we'll make it prettier later.
+
+```
+# link scholar profiles of ALL STAFF 
+```{r, staff total scholar link, eval=FALSE, include=FALSE}
+# Look throught get_scholar_id_fix(last_name, first_name, affiliation) 
+# if we can find google scholar profiles of sociology staff!
+for (i in 1:nrow(soc_df)) {
+
+  time <- runif(1, 0, 8) # randomized request times bc scholar has a "trip switch" against spam 
+  Sys.sleep(time)
+# for every number from 1 to 10 we draw one number from 0 to 8 from a uniform distribution we put
+# the wrapper sys.sleep around it that we put R to sleep for the drawn number
+
+  tryCatch({
+     soc_df[i,c("gs_id")] <- get_scholar_id_fix(last_name = soc_df[i, c("last_name")], # so search on last_name of staff (third column)
+                                             first_name = soc_df[i, c("first_name")],  # search on first_name of staff (fourth column)
+                                             affiliation = soc_df[i,c("affiliation")]) # search on affiliation of each staff (fifth column)
+
+    }, error=function(e){cat("ERROR :", conditionMessage(e), "\n")}) # continue on error, but print the error
+  }
+
+# remove those without pubs from the df
+# seems we're left with about 34 sociology staff members!
+soc_df <- soc_df[!soc_df$gs_id == "", ]
+soc_df
+```
+## get publications (all staff)
+```{r eval=FALSE, include=FALSE}
+#CURRENTLY: CODE IN THIS CHUNK IS NOT RUN (change in little setting weel at the top rightof this chunk)
+
+# gather the profiles and publications and store them in a LIST
+
+soc_list_profiles <- list()  # first we create an empty list that we then fill up with the for loop
+soc_list_publications <- list()
+
+for (i in 1:nrow(soc_df)) {
+
+    time <- runif(1, 0, 10) # randomized requests? 
+    Sys.sleep(time)
+
+    # note how you call different elements in a list '[[]]', fill in the i-th element
+    soc_list_profiles[[i]] <- get_profile(soc_df[i, c("gs_id")])  # Note how we call row i (remember how to call rows in a DF/Matrix) and then the associated scholar id
+    soc_list_publications[[i]] <- get_publications(soc_df[i, c("gs_id")])
+    soc_list_publications[[i]][, c("gs_id")] <- soc_df[i, c("gs_id")]  # note that we again attach an id
+    # so both functions here call the entire profile and pubs for an author, based on google scholar ids
+
+}
+# Notice how fast the data blow up! The 34 RU sociology scholars publish ~3000 papers
+soc_df_publications <- bind_rows(soc_list_publications)
+
+```
+## google scholar says NO :(  (too many requests despite random requests)
+-> cannot make lists with publications and profiles as of now (evening of 17th September) :/
+
+# continue shortly before "getting collaborators" at Chapter 8.6.4
+search and find: note how soc_list_profiles

### 2024-09-17 function_fix.R

@@ -1,0 +1,59 @@
+# function get_scholar_id_fix
+# functions for chapter 8 tutorial 
+
+require(scholar)
+#downloaded function:
+get_scholar_id_fix <- function (last_name = "", first_name = "", affiliation = NA)
+{
+  if (!any(nzchar(c(first_name, last_name))))
+    stop("At least one of first and last name must be specified!")
+  site <- getOption("scholar_site")
+  url <- paste0(site, "/citations?view_op=search_authors&mauthors=",
+                first_name, "+", last_name, "&hl=en&oi=ao")
+  page <- get_scholar_resp(url)
+  if (is.null(page))
+    return(NA)
+  aa <- httr::content(page, as = "text")
+  # added by Bas Hofstra: bugfix for IDs that have a dash ("-")
+  ids <- substring(aa, regexpr(";user=", aa))
+  ids <- substr(ids, 1, 19) # error prone, but unsure how to solve otherwise
+  # if (nchar(stringr::str_extract_all(string = aa, pattern = ";user=[[:alnum:]]+[[:punct:]]")[[1]][1]) < 18) {
+  #   ids <- stringr::str_extract_all(string = aa, pattern = ";user=[[:alnum:]]+[[:punct:]]+[[:alnum:]]+[[:punct:]]")
+  # } else {
+  #   ids <- stringr::str_extract_all(string = aa, pattern = ";user=[[:alnum:]]+[[:punct:]]")
+  # }
+  if (length(unlist(ids)) == 0) {
+    message("No Scholar ID found.")
+    return(NA)
+  }
+  ids <- ids %>% unlist %>% gsub(";user=|[[:punct:]]$", "",
+                                 .) %>% unique
+  if (length(ids) > 1) {
+    profiles <- lapply(ids, scholar::get_profile)
+    if (is.na(affiliation)) {
+      x_profile <- profiles[[1]]
+      warning("Selecting first out of ", length(profiles),
+              " candidate matches.")
+    }
+    else {
+      which_profile <- sapply(profiles, function(x) {
+        stringr::str_count(string = x$affiliation, pattern = stringr::coll(affiliation,
+                                                                           ignore_case = TRUE))
+      })
+      if (all(which_profile == 0)) {
+        warning("No researcher found at the indicated affiliation.")
+        return(NA)
+      }
+      else {
+        x_profile <- profiles[[which(which_profile !=
+                                       0)]]
+      }
+    }
+  }
[…]

### 2024-09-18 RQdraft2.Rmd
hwForWeek3

@@
 
-# Brainstorm
-
 ------------------------------------------------------------------------
 
-# Research Questions (old, replace with new ones!)
+# Research Questions
 
@@
 
-RQ2: To what extent does gender homophily in co-publishing influence the prestige of the publication journal?
+RQ2: How to does gender homophily affect collaboration differently for collaborations between staff who have published in low vs. high prestige journals?
 
@@
 +-----------------------------------+---------------------------------------------------------+--------------------------------------------------------------------------------------------------------+
+| Age                               | length of career                                        | time since first publication                                                                           |
++-----------------------------------+---------------------------------------------------------+--------------------------------------------------------------------------------------------------------+
 | Gender                            | Google Scholar:\                                        | What about gender neutral names? If we go by this principle, then gender neutral names = non-binary ?? |

### 2024-09-18 Webscraping-Chapter8-tutorial.Rmd
hwForWeek3

@@
 
-  time <- runif(1, 0, 8) # randomized request times bc scholar has a "trip switch" against spam 
+  time <- runif(1, 0, 8) # randomized request times bc scholar has a "trip switch" against spam (rate limit)
   Sys.sleep(time)

### 2024-09-18 RQdraft2.Rmd
hw3
introfirstdraftpush

@@
 author: "Verooo"
-date: "2024-09-11"
+date: "2024-09-18"
 output: html_document
@@
 ```
+
+# Introduction draft
+
+Collaboration has become an essential part of modern academia, with scholars increasingly engaging in joint research efforts.
+Co-authorship allows researchers to combine expertise, share resources, and enhance their scholarly output (Cheong & Corbitt, 2009).
+However, the dynamics of academic collaboration are not free from social patterns, and gender homophily—where individuals prefer to collaborate with others of the same gender—may play a significant role.
+Understanding how gender affects co-authorship networks, particularly in terms of homophily, can reveal important insights into how academic opportunities and achievements are distributed across genders.
+
+Previous studies have found that male researchers often prefer collaborating with other men, while female researchers tend to collaborate with other women, albeit to a lesser extent (Horta et al., 2022).
+This raises critical questions about the structure and inclusiveness of academic networks.
+In fields such as Sociology and Political Science, where collaboration is crucial for scholarly success, gender-based patterns could shape the career trajectories of researchers.
+Furthermore, as Kwiek and Roszka (2021) point out, all-male authorship is far more prevalent than all-female authorship, indicating that male-dominated collaboration networks may reinforce existing gender imbalances in academia.
+
+In this study, I explore the extent to which gender homophily influences co-authorship networks among faculty in the Sociology and Political Science Departments at Radboud University.
+Specifically, I aim to examine whether there are differences in gender homophily between the two departments, and how homophily patterns vary depending on the prestige of the journals in which researchers publish.
+Additionally, I investigate whether structural network factors—such as the size and composition of collaboration networks—affect gender homophily in each department.
+
+The research will contribute to a growing body of literature that seeks to understand the social dynamics underlying academic collaboration.
+By analyzing gender homophily and network structures in two different academic disciplines, this study will shed light on how gender shapes collaboration opportunities and how these dynamics may differ across scholarly fields.
+Moreover, exploring the role of journal prestige in shaping homophily will offer insights into whether gender-based preferences shift in response to career-enhancing factors like publishing in high-prestige venues.
 

### 2024-09-18 Webscraping-Chapter8-tutorial.Rmd
week3class

@@
 
-# Get anchor data
+# Get anchor data -RU sociology
 
@@
 # the table we do need
+
+# soc_staff_0 <- soc_staff %>%
+#     rvest::html_nodes("body") %>%
+#     xml2::xml_find_all("//td") %>% # xml2 here looks across multiple layers/ child-elements (hence the // !!! )
+#     rvest::html_text()
+# 
+# 
+# # BETTER?
+# # using html_elements to ONLY USE ONE PACKAGE (RVEST)
 soc_staff <- soc_staff %>%
-    rvest::html_nodes("body") %>%
-    xml2::xml_find_all("//td") %>%
+    rvest::html_elements("body") %>%
+    rvest::html_elements ("td") %>%
+    rvest::html_text()
+#   
+#     
+# view(soc_staff)
+# 
+# # Get whole table at once? 
+# soc_staff_1 <- soc_staff %>%
+#     rvest::html_elements("body") %>%
+#     rvest::html_table()
+
+#view(soc_staff_1)
+#class(soc_staff_1) # list (you can turn into a data frame to use it for further data manipulatino fromhere on)
+
+# (fshowdf) to make output look pretty (but i probably misunderstood what exactly Jochem said)
+
+```
+
+# get anchor data - Leiden University - PolSci 
+```{r}
+
+#do it for Leiden University 
+leiden_polsci_staff <- read_html("https://www.universiteitleiden.nl/en/academic-staff/overview?pageNumber=1&faculty=social-and-behavioural-sciences&facultyinstitute=institute-of-political-science") #extracts the source html of a webpage
+
+# div id content 
+# section 
+# ul class table list
+
+leiden_polsci_staff_2 <- leiden_polsci_staff %>%
+    rvest::html_elements("body") %>%
+    rvest::html_elements("li")  %>%
+    rvest::html_elements("strong") %>%
     rvest::html_text()
 
-soc_staff
+view(leiden_polsci_staff_2)
 
+```
+
+# sort rows into names and expertise 
+```{r}
 #Assigning even and odd rows to 'fodd' and 'feven' (bc the output just lists the left and right side of the table interchangably)
@@
 search and find: note how soc_list_profiles
+
+# gender from names 
+```{r}
+# voornamenbank Maartens insitute 
+# e.g. Vero:
+# https://nvb.meertens.knaw.nl/naam/is/Vero
+
+# use the concatenate function cat 
+# and make a loop that just fills in the name in question in the link
+
+# INSERT CODE HERE
+
+# Last names: https://cbgfamilienamen.nl/nfb/
+```
+
+# custom functions chunk for functions to run later on 
+```{r}
+fpackage.check <- function(packages) {
+    lapply(packages, FUN = function(x) {
+        if (!require(x, character.only = TRUE)) {
+            install.packages(x, dependencies = TRUE)
+            library(x, character.only = TRUE)
+        }
+    })
+}
+
+fsave <- function(x, file = NULL, location = "./data/processed/") {
+    ifelse(!dir.exists("data"), dir.create("data"), FALSE)
+    ifelse(!dir.exists("data/processed"), dir.create("data/processed"), FALSE)
+    if (is.null(file))
+        file = deparse(substitute(x))
+    datename <- substr(gsub("[:-]", "", Sys.time()), 1, 8)
+    totalname <- paste(location, datename, file, ".rda", sep = "")
+    save(x, file = totalname)  #need to fix if file is reloaded as input name, not as x. 
+}
+
+fload <- function(filename) {
+    load(filename)
+    get(ls()[ls() != "filename"])
+}
+
+#install.packages("kableExtra")
+library(kableExtra)
+
+fshowdf <- function(x, ...) {
+    knitr::kable(x, digits = 2, "html", ...) %>%
+        kableExtra::kable_styling(bootstrap_options = c("striped", "hover")) %>%
+        kableExtra::scroll_box(width = "100%", height = "300px")
+}
+```
+# Open alex 
+```{r}
+# SEE SUNBELT WEBSITE: Attributes tab 
+# if you put html from open alex api into the read html function then you need to replace any spaces with a + symbol
+
+# get JSON package so it can read the JSON object
+
+```
+# R Package openalexR (using r wrapper )
+```{r}
+# make JSON object easier to use
+
+#install.packages("openalexR")
+library(openalexR)
+
+options(openalexR.mailto = "palmtreesdude@gmail.com")
+
+df <- oa_fetch(entity= "author", search = "Jochem Tolsma")
+
+fshowdf(df)
+
+#second affiliation ofJochem is lost when using this wrapper 
+# SOMETIMES INFORMATION CAN GET LOST 
+df_papers <- oa_fetch(entity = "works", author.id = df$id)
+df_papers$author[1] # selecting first item in column "author" which in this case is a full data base 
+# OUtput gives us id from author AND CO-author
+
+# To prevent doubles for authors that have common names we can use MULTIPLE FILTERS: eg. institution Radboud University and country NL and so on...
+
+# find institution ids first to then filterforinstitutions:
+oa_fetch(entity = "institutions", search = "Radboud University")
+#output will show id: https://openalex.org/I145872427	 for Radboud University Nijmegen
+
+# in code on Jochems in line 162 file title 45 publicationsOpenAlex.rmd
+
+oa_fetch(entity= "author", search = "Jochem Tolsma", affiliations.institution.id = "https://openalex.org/I145872427")
+#putput already has a lot of information on Jochem
+
+# NEXT: find all papers Jochem wrote
+
+oa_fetch (entity = "works", author.id = 'https://openalex.org/A5087380803')
+ # id is the author id  from somewhere prior in Jochems script
+
+```
+## Adjacency matrix for 4 authors 
+```{r}
+packages <- c("tidyverse", "scholar", "openalexR", "rvest", "jsonlite")
+fpackage.check(packages)
+# make adjacency matrix for these four people
+
+#Jochem tolsma
+# Tom van de Meer
+# Maurice Gesthuizen 
+# Michael Savelkoul
+
+# What data do we need? 
+  # Authors, University, works, and co-authors 
+  # All in one data frame
+
+# Jochem Tolsma 
+df_jochem <- oa_fetch(entity= "author", search = "Jochem Tolsma", affiliations.institution.id = "https://openalex.org/I145872427")
+
+fshowdf(df_jochem)
+
+# Maurice Gesthuizen
+df_maurice <- oa_fetch(entity= "author", search = "Maurice Gesthuizen", affiliations.institution.id = "https://openalex.org/I145872427")
+
+fshowdf(df_maurice)
+
+# Michael Savelkoul
+df_michael <- oa_fetch(entity= "author", search = "Michael Savelkoul", affiliations.institution.id = "https://openalex.org/I145872427")
+
+fshowdf(df_michael)
+
+# Tom van der Meer
+df_tom <- oa_fetch(entity= "author", search = "Tom van der Meer", affiliations.institution.id = "https://openalex.org/I145872427")[1,]
+
+fshowdf(df_tom)
+#if output two id's: make decision rule
+# here savest bet isto collect all 5 tom's there are bc we make a matrix
+# if we want to look at citation scores, we have to probably only take the first id
+
+#one vector with all authors 
+all_authors <- rbind(df_jochem, df_maurice, df_michael, df_tom)
+
+```
+### works
+
+```{r}
+# Jochem's work 
+df_works_jochem <- oa_fetch (entity = "works", author.id = "https://openalex.org/A5087380803")
+
+# Maurice Gesthuizen
+df_works_maurice <- oa_fetch (entity = "works", author.id = "https://openalex.org/A5007673492")
+
+# Michael Savelkoul
+df_works_michael <- oa_fetch (entity = "works", author.id = "https://openalex.org/A5048988743")
+
+# Tom van der Meer
+df_works_tom <- oa_fetch (entity = "works", author.id = "https://openalex.org/A5010780363")
+
+# vector with all works
+all_works <- rbind(df_works_tom, df_works_michael, df_works_maurice, df_works_jochem)
+
+```
+## make matrix 
+```{r}
+# ALT + MINUS make the ARROWS <- 
+# STR + SHIFT + M makes the %>% 
+# STR + SHIFT + C can make a comment of multiple lines you highlighted
+
+# use column 'author' from works overview 
+# 4x4 matrix
+# decide for which time period 
+  # 2 waves of 4 years: 2019-2023, 2014-2018 
+  # select papers with publication date in this date frame 
+    # publication year variable
+
+# make selection of dates
+#wave 1
+works_wave1 <- all_works %>% filter(publication_year >= 2014 & publication_year <= 2018)
+#wave 2
+works_wave2 <- all_works %>% filter(publication_year >= 2019 & publication_year <= 2023)
+
+# make empty 4x4 matrix
+  # name each row and column with the identifiers of scholars
+
+matrix_wave1 <- matrix(0, nrow = 4, ncol = 4)
+
+rownames(matrix_wave1) <- c("https://openalex.org/A5087380803", "https://openalex.org/A5007673492", "https://openalex.org/A5048988743", "https://openalex.org/A5010780363")
+
+colnames(matrix_wave1)<- c("https://openalex.org/A5087380803", "https://openalex.org/A5007673492", "https://openalex.org/A5048988743", "https://openalex.org/A5010780363")
+
+print(matrix_wave1)
+
+# loop through works
+
+  # row 1: 
+    # works[1,] # in the loop it would be 'i'
+
+  # output shows we want information from column"au_id"
+    works_wave1[1,]$author[[1]]$au_id
+
+    # output: first listed is the SENDER
+    ego <- works_wave1[1,]$author[[1]]$au_id[1]
+
+    # the RECEIVERS are everyone BUT the ego aka. the first one
+    alters <- works_wave1[1,]$author[[1]]$au_id[-1]
+
+  # CHECK if ego is part of authors 
+  # Filter only the author who are part of the other authors 
+    # Check if author is in list 
+      # t[t %in% authors]
+
+  matrix_wave1[ego,alters] <- 1
+  #works_wave1[ego,alters] <- works_wave1[ego,alters] + 1
+
+# Create a 4x4 matrix filled with 0's
+matrix_wave2 <- matrix(0, nrow = 4, ncol = 4)
+
+rownames(matrix_wave2) <- c("https://openalex.org/A5087380803", "https://openalex.org/A5007673492", "https://openalex.org/A5048988743", "https://openalex.org/A5010780363")
+
+colnames(matrix_wave2)<- c("https://openalex.org/A5087380803", "https://openalex.org/A5007673492", "https://openalex.org/A5048988743", "https://openalex.org/A5010780363")
+
+print(matrix_wave2)
+
+# old code from week 2 
+# matrix_graph <- graph.adjacency(matrix_wave1)
+
+# print(matrix_graph)
+```

### 2024-09-18 week3RSelenium.Rmd
week3class

--- 2024-09-11 testjt.Rmd
@@
 ---
-title: "t62al"
-author: "by: Vero"
-bibliography: references.bib
+title: "week3 - class RSelenium"
+author: "Verooo"
+date: "2024-09-18"
+output: html_document
+---
+
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = TRUE)
+```
 
@@
 
-<!--- 
-HOW TO MAKE TOKENS:
-install.packages("gitcreds") 
-gitcreds::gitcreds_set() --->
-
-<!--- TO MAKE NEW CHUNKS: ctrl + Alt + i --->
-
-```{r, eval=FALSE}
-########################### Title: Introduction to R for SNA Author: J Tolsma version: 30-10-2019
-
+# see: https://jochemtolsma.github.io/webscraping/12scholars.html#13_necessary_packages
+```{r}
 # start with clean workspace
@@
 
-# install.packages I will need later here
-install.packages("installr")  # you  first install packages
-install.packages("foreign")
-install.packages("tidyverse")
-```
+# install.packages("RSelenium")
+library(RSelenium)
 
-```{r}
-require(foreign)  # used to read in spss data files
-require(tidyverse)
-
-# define workdirectory, note the double backslashes
-# setwd("C:\Users\Vero\OneDrive - Radboud Universiteit\Documents\GitHub\labjournal")  # change to your own workdirectory
-```
-```{r Cheat sheet}
-###########Cheat Sheet##########
-
-# variable labels 
-# c("primary", "secondary", "tertiary")
-
-# Operator symbols: 
-# $
-# == logical operator. What are the other logical operators in R?
-# [] is used to subset elements from an object (e.g. dataframe/vector/matrix)
-#  NA is used in R to define missing values. It means Not Applicable.
-
-# Functions:
-# summary(), attributes(), attr(), table(), names(), head(), fix(), View()
-
-# as.character() 
-# as.numeric()
-
-# in tidy: 
-  #the piping operator 
-  # %>%, 
-  # the left is transported to the (first argument of the) function on the right.
-Thus, in the example below, you see that in the second and third call to mutate I don’t have to tell the function which dataset I am using.
-
-# mean(), 
-# rowMeans(), 
-# rowSums, 
-# cbind(), 
-# is.na(), 
-# ifelse().
-
-# logicals FALSE and TRUE can be summed? (FALSE equals 0 and TRUE equals 1).
-```
-
-```{r}
-# ignore the warnings ?read.spss note that I have saved the data files in a folder called
-# 'addfiles'.
-
-cv08 <- foreign::read.spss("tutorial_data\\Cultural_Changes_2008.sav", use.value.labels = T, to.data.frame = T)
-cv10 <- foreign::read.spss("tutorial_data\\Cultural_Changes_2010.sav", use.value.labels = T, to.data.frame = T)
-
-# normally I think setting use.value.labels=F is more convenient. Thus lets load the data again but
-# now WITHOUT LABELS 
-cv08_nolab <- foreign::read.spss("tutorial_data\\Cultural_Changes_2008.sav", use.value.labels = F, to.data.frame = T)
-cv10_nolab <- foreign::read.spss("tutorial_data\\Cultural_Changes_2010.sav", use.value.labels = F, to.data.frame = T)
-
-# finally, import the data using haven
-cv08_haven <- haven::read_spss("tutorial_data\\Cultural_Changes_2008.sav")
-cv10_haven <- haven::read_spss("tutorial_data\\Cultural_Changes_2010.sav")
-
-str(cv08) # str = asks for structure of an object 
-str(cv08_nolab)
-str(cv08_haven)
-
-# acsessing variable:
-# datasetname$variablename
-
-str(cv08$lftop)  # a factor
-str(cv08_nolab$lftop)  # a numeric variable
-str(cv08_haven$lftop)  # a 'dbl+lbl' this stands for doubles, or real numbers, which are labeled  
-# next to the data itself, attributes are stored
-attributes(cv08$lftop)
-attributes(cv08_nolab$lftop)
-attributes(cv08_haven$lftop)
-
-# to access specific attributes
-attr(cv08_haven$lftop, "labels")
-
-summary(cv08$lftop)
-summary(cv08_nolab$lftop)
-summary(cv08_haven$lftop)
-table(cv08_haven$lftop, useNA = "always")
-
-#LOOKING AT DATA 
-names(cv08_haven)
-summary(cv08_haven)
-head(cv08_haven)
-
-# fix(cv08_haven) #will produce an error
-# fix(cv08)
-# View(cv08_haven)
+# Web Driving with R Silenium
 
 ```
-
-----
-```{r A.7.1 Define Missings}
-
-str(cv08_haven$lftop)
-summary(cv08_haven$lftop)
-attr(cv08_haven$lftop, "labels")
-table(cv08_haven$lftop, useNA = "always")
-
-# copy the original variable in a new one, and attach it to the dataset. 
-cv08$lftop_new <- cv08$lftop
-
-# replace those values of our new variable
-cv08$lftop_new[cv08$lftop_new == "Onbekend"] <- NA
-
-#Check if recode works 
-table(cv08$lftop_new, useNA = "always")
-
-levels(cv08$lftop_new)
-
-# as numeric variable not as a factor (categorical).
-str(cv08$lftop_new)
-
-cv08$agen <- as.numeric(as.character(cv08$lftop_new))  
-# how clumsy. we first convert the factor to a string and then to a numeric variable.
-table(cv08$agen, useNA = "always")
-
-str(cv08$agen)
-
-```
-
-```{r A.7.2 Tidy }
-
-# install.packages("tidyverse")
-library(tidyverse)
-
-# ‘mutate’ the original dataset by adding a variable.
-cv08_haven <- mutate(cv08_haven, lftop_new = lftop)
-
-#Replace missings.Note: 99 is the “onbekend” category.
-cv08_haven$lftop_new <- na_if(cv08_haven$lftop_new, 99)
-
-#Normally: combine these two steps into one
-cv08_haven <- mutate(cv08_haven, lftop_new = na_if(lftop, 99))
-
-#check
-table(cv08_haven$lftop_new, useNA = "always")
-
-```
-----
-```{r A.8 Recode variables}
-
-# var006n = second variable lets us recode the variable education (in CV08)
-#create a new variable educ3 with three levels:
-#1. primary
-#2. secondary
-#3. tertiary
-
-#levels
-levels(cv08$var006n)
-
-# table 
-table(cv08$var006n, useNA = "always")
-
-# lets make it a numeric variable first
-cv08$educn <- as.numeric(cv08$var006n)
-# check
-table(cv08$educn, useNA = "always")
-
-# start with an empty variable
-cv08$educ3 <- NA
-# fill category by category
-cv08$educ3[cv08$educn == 2 | cv08$educn == 3] <- 1
-cv08$educ3[cv08$educn > 3 & cv08$educn < 8] <- 2
-cv08$educ3[cv08$educn > 7 & cv08$educn < 11] <- 3
-
-# check
-table(cv08$educ3, useNA = "always")
-
-prop.table(table(cv08$educ3, useNA = "always"))
-
-# now educ3 is a numeric variable, we want it as factor
-cv08$educ3 <- as.factor(cv08$educ3)
-table(cv08$educ3, useNA = "always")
-
-levels(cv08$educ3) <- c("primary", "secondary", "tertiary")
-table(cv08$educ3, useNA = "always")
-```
-
-```{r A.8.2 Tidy}
-
-# dplyr::recode   #doesnt work on labelled variables that were imported via haven package
-
-# install.packages('labelled')
-require(labelled)  # to be able to use the recode function on haven labelled variables
-
-# inspect variable
-str(cv08_haven$var006n)
-
-attr(cv08_haven$var006n, "labels")
-
-table(cv08_haven$var006n, useNA = "always")
-
-# recode values, all missings as one value
-cv08_haven <- mutate(cv08_haven, educ3 = recode(var006n, `-3` = -9, `-1` = 1, `1` = 1, `2` = 2, `3` = 2,
-    `4` = 2, `5` = 2, `6` = 3, `7` = 3, `8` = 3, `10` = -9), .keep_value_labels = FALSE)
-
-# replace missing values with NA.
-cv08_haven <- mutate(cv08_haven, educ3 = na_if(educ3, -9))
-
-# make educ3 a factor
-cv08_haven <- mutate(cv08_haven, educ3 = factor(educ3, levels = c(1, 2, 3), labels = c("primary", "secondary",
-    "tertiary")))
-
-# check
-table(cv08_haven$educ3, useNA = "always")
-
-#the piping operator 
-  # %>%, 
-  # the left is transported to the (first argument of the) function on the right.
-Thus, in the example below, you see that in the second and third call to mutate I don’t have to tell the function which dataset I am using.
-# in Base R (since 4.1.0) operator: |>
-
-cv08_haven <- mutate(cv08_haven, educ3 = recode(var006n, `-3` = -9, `-1` = 1, `1` = 1, `2` = 2, `3` = 2,
-    `4` = 2, `5` = 2, `6` = 3, `7` = 3, `8` = 3, `10` = -9), .keep_value_labels = FALSE) %>%
-    mutate(educ3 = na_if(educ3, -9)) %>%
-    mutate(educ3 = factor(educ3, levels = c(1, 2, 3), labels = c("primary", "secondary", "tertiary")))
-
-# even more tidy:
-cv08_haven <- cv08_haven %>%
-    mutate(educ3 = recode(var006n, `-3` = -9, `-1` = 1, `1` = 1, `2` = 2, `3` = 2, `4` = 2, `5` = 2,
-        `6` = 3, `7` = 3, `8` = 3, `10` = -9), .keep_value_labels = FALSE) %>%
-    mutate(educ3 = na_if(educ3, -9)) %>%
-    mutate(educ3 = factor(educ3, levels = c(1, 2, 3), labels = c("primary", "secondary", "tertiary")))
-
-# the MOST tidy:
-cv08_haven <- cv08_haven %>%
-    mutate(educ3 = recode(var006n, `-3` = -9, `-1` = 1, `1` = 1, `2` = 2, `3` = 2, `4` = 2, `5` = 2,
-        `6` = 3, `7` = 3, `8` = 3, `10` = -9, .keep_value_labels = FALSE), educ3 = na_if(educ3, -9),
-        educ3 = factor(educ3, levels = c(1, 2, 3), labels = c("primary", "secondary", "tertiary")))
-```
-----
-```{r A.9 Means and counting specific values}
-# A.9.1. R Base
-
-# Step 1: Look at the various 
-summary(cv08$int055)
-summary(cv08$int056)
-summary(cv08$int057)
-
-# Step 2: Make numeric 
-cv08$int055n <- as.numeric(cv08$int055)
-table(cv08$int055n, useNA = "always")
-
-cv08$int056n <- as.numeric(cv08$int056)
-table(cv08$int056n, useNA = "always")
-
-cv08$int057n <- as.numeric(cv08$int057)
-table(cv08$int057n, useNA = "always")
-
-# Step 3: Define missings and recode
-cv08$int055n[cv08$int055n < 5] <- NA
-cv08$int055n <- cv08$int055n - 4
-
-cv08$int056n[cv08$int056n < 5] <- NA
-cv08$int056n <- cv08$int056n - 4
-
-cv08$int057n[cv08$int057n < 5] <- NA
-cv08$int057n <- cv08$int057n - 4
-
-# Step 4: Calculate means
-# How does the function mean work in R?
-mean(cv08$int055n)  # whoops
-mean(cv08$int055n, na.rm = TRUE)  # works.  but not what we want. 
-# na.rm -> tells function whether or not to remove NA values from the calculation
-
-mean(c(cv08$int055n, cv08$int056n, cv08$int057n), na.rm = T)  # works but not what we want.
-
-# calculate a mean for each row/respondent. 
-testmeans <- rowMeans(cbind(cv08$int055n, cv08$int056n, cv08$int057n), na.rm = T)
-head(testmeans)  # yes!
-# head() function : Return the First or Last Part of an Object
-
-# What we really want is a mean but only if there is a maximum of 1 NA in the three variables.
-# lets first count how many missings we have for each respondent
-nmis <- rowSums(is.na(cbind(cv08$int055n, cv08$int056n, cv08$int057n)))
-
-# ?is.na ?rowSums
-testmeans <- ifelse(nmis < 2, testmeans, NA)
-
-# add the calculated means to our dataset
-cv08$int_mean <- testmeans
-
-```
-
-----
-
-----
-
-# References
+# citing openalexR in paper!
+If you use openalexR in research, please cite: (Priem, Piwowar, and Orr 2022)

### 2024-09-20 RQdraft3.Rmd
makingfilesw3

--- 2024-09-18 week3RSelenium.Rmd
@@
 ---
-title: "week3 - class RSelenium"
+title: "RQ draft 3"
 author: "Verooo"
-date: "2024-09-18"
+date: "2024-09-20"
 output: html_document
----
-
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
-```
-
 ---
@@
 ```
-
-# see: https://jochemtolsma.github.io/webscraping/12scholars.html#13_necessary_packages
-```{r}
-# start with clean workspace
-rm(list = ls())
-
-# install.packages("RSelenium")
-library(RSelenium)
-
-# Web Driving with R Silenium
-
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = TRUE)
 ```
-# citing openalexR in paper!
-If you use openalexR in research, please cite: (Priem, Piwowar, and Orr 2022)

### 2024-09-20 webscraping1.Rmd
makingfilesw3

--- 2024-09-11 _week1.Rmd
@@
 ---
-title: "_SNASS tutorial"
-author: "TreesDude"
-date: "2024-09-04"
+title: "Webscraping my data 1"
+author: "Verooo"
+date: "2024-09-20"
 output: html_document
@@
 Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
-
-```{r token}
-#install.packages("gitcreds")
-# gitcreds::gitcreds_set()
-```
-
-```{r}
-# TO MAKENEW CHUNKS: ctrl + Alt + i
-
-```
-
-```{r}
-########################### Title: Introducation to R for SNA Author: J Tolsma version: 30-10-2019
-
-# start with clean workspace
-rm(list = ls())
-
-# install.packages I will need later here
-install.packages("installr")  # you  first install packages
-install.packages("foreign")
-require(foreign)  # used to read in spss data files
-require(tidyverse)
-
-# define workdirectory, note the double backslashes
-setwd("C:\Users\Vero\OneDrive - Radboud Universiteit\Documents\GitHub\labjournal")  # change to your own workdirectory
-```
-
-```{r}
-# ignore the warnings ?read.spss note that I have saved the data files in a folder called
-# 'addfiles'.
-
-cv08 <- foreign::read.spss("addfiles\\Cultural_Changes_2008.sav", use.value.labels = T, to.data.frame = T)
-cv10 <- foreign::read.spss("addfiles\\Cultural_Changes_2010.sav", use.value.labels = T, to.data.frame = T)
-
-# normally I think setting use.value.labels=F is more convenient. Thus lets load the data again but
-# now without labels
-cv08_nolab <- foreign::read.spss("addfiles\\Cultural_Changes_2008.sav", use.value.labels = F, to.data.frame = T)
-cv10_nolab <- foreign::read.spss("addfiles\\Cultural_Changes_2010.sav", use.value.labels = F, to.data.frame = T)
-
-# finally, import the data using haven
-cv08_haven <- haven::read_spss("addfiles\\Cultural_Changes_2008.sav")
-cv10_haven <- haven::read_spss("addfiles\\Cultural_Changes_2010.sav")
-```

### 2024-09-20 RQdraft3.Rmd
editsheadingw3

--- 2024-09-18 week3RSelenium.Rmd
@@
 
-# see: https://jochemtolsma.github.io/webscraping/12scholars.html#13_necessary_packages
-```{r}
-# start with clean workspace
-rm(list = ls())
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = TRUE)
+```
 
-# install.packages("RSelenium")
-library(RSelenium)
+# Research Questions
 
-# Web Driving with R Silenium
+**RQ1a:**
 
-```
-# citing openalexR in paper!
-If you use openalexR in research, please cite: (Priem, Piwowar, and Orr 2022)
+-   To what extent does gender homophily occur across all co-publications of the staff of the Sociology Department and Political Science Department at Radboud University?
+
+**RQ1b:**
+
+-   To what extent do the two departments differ in their gender homophily?
+
+**RQ2:**
+
+-   How to does gender homophily affect collaboration differently for collaborations between staff who have published in low vs. high prestige journals?
+
+# Overview:
+
+-   Sample:
+
+    -   Radboud Sociology Dptm.
+
+    -   Radboud Pol Sci Dptm.
+
+-   Time frame: 2019 - 2023 ( Why? Well... because. )
+
+-   Data:
+
+    -   names
+
+    -   publications
+
+        -   connected to authors (for collaborations)
+
+    -   initiator: position in list ofcollaborators
+
+    -   sex/gender (f,m/w,m)
+
+        -   using name data bank
+
+    -   journals of the publications
+
+        -   prestige: their ?-Index
+
+        -   --\> categorize ? scale?
+
+-   age
+
+    -   time since first publication
+
+        -   **until last publication? until present?**
+
+# Questions
+
+-   How scrape position of name in list of collaborators?
+
+-
+
+# To-Do
+
+-   Read up on G-index, H-index, prestige indicators of journals
+
+    -   decide which one as indicator
+
+-

### 2024-09-20 webscraping1.Rmd
editsheadingw3

@@
 
+---
+title: "RQ draft 3"
+author: "Verooo"
+date: "2024-09-20"
+output: html_document
+---
+
+```{r, globalsettings, echo=FALSE, warning=FALSE, results='hide'}
+library(knitr)
+
+knitr::opts_chunk$set(echo = TRUE)
+opts_chunk$set(tidy.opts=list(width.cutoff=100),tidy=TRUE, warning = FALSE, message = FALSE,comment = "#>", cache=TRUE, class.source=c("test"), class.output=c("test2"))
+options(width = 100)
+rgl::setupKnitr()
+
+colorize <- function(x, color) {sprintf("<span style='color: %s;'>%s</span>", color, x) }
+
+```
+
+```{r klippy, echo=FALSE, include=TRUE}
+klippy::klippy(position = c('top', 'right'))
+#klippy::klippy(color = 'darkred')
+#klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done')
+```
 ```{r setup, include=FALSE}
@@
 ```
-
-## R Markdown
-
-This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.
-
-When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
-You can embed an R code chunk like this:
-
-```{r cars}
-summary(cars)
-```
-
-## Including Plots
-
-You can also embed plots, for example:
-
-```{r pressure, echo=FALSE}
-plot(pressure)
-```
-
-Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2024-10-02 Webscraping-Chapter8-tutorial.Rmd
indexrenewal

@@
 
-goal: get to know \
-(i) who the Radboud University Department of Sociology staff is, \
-(ii) what they publish with respect to scientific work, and \
+goal: get to know\
+(i) who the Radboud University Department of Sociology staff is,\
+(ii) what they publish with respect to scientific work, and\
 (iii) who they collaborate with.
@@
 # get anchor data - Leiden University - PolSci
+
 ```{r}
@@
 # sort rows into names and expertise
+
 ```{r}
@@
 # Extract names and last names
+
 ```{r, name extraction}
@@
 ## clean up names
+
 ```{r, clean up names }
@@
 # Google Scholar Profiles and Publication
+
 ## reminder: for loops
+
 ```{r, for loop}
@@
 ```
+
 ## linking a SINGLE staff member to their google scholar link
+
 ```{r}
@@
 ```
+
 ### get scholar publications, citations
+
 ```{r, pubs and citations}
@@
 ```
+
 ### get collaborators
+
 ```{r, collaborators}
@@
 ## plot network of single staff member
+
 ```{r, plot}
@@
 ```
+
 # link scholar profiles of ALL STAFF
+
 ```{r, staff total scholar link, eval=FALSE, include=FALSE}
@@
 ```
+
 ## get publications (all staff)
+
 ```{r eval=FALSE, include=FALSE}
@@
 ```
+
 ## google scholar says NO :( (too many requests despite random requests)
--> cannot make lists with publications and profiles as of now (evening of 17th September) :/
+
+-\> cannot make lists with publications and profiles as of now (evening of 17th September) :/
 
 # continue shortly before "getting collaborators" at Chapter 8.6.4
+
 search and find: note how soc_list_profiles
@@
 # gender from names
+
 ```{r}
@@
 # custom functions chunk for functions to run later on
+
 ```{r}
@@
 ```
+
 # Open alex
+
 ```{r}
@@
 ```
+
 # R Package openalexR (using r wrapper )
+
 ```{r}
@@
 ```
+
 ## Adjacency matrix for 4 authors
+
 ```{r}
@@
 ```
+
 ### works
@@
 ```
+
 ## make matrix
+
 ```{r}

### 2024-10-02 index.Rmd
updatedmenusweek2
indexrenewal

--- 2024-09-04 index.Rmd
@@
 title: "Lab journal"
-author: "by: Vero"
+author: "by: Verooo"
 bibliography: references.bib
-
 ---
@@
 
-----
+```{r token, include=FALSE}
+#install.packages("gitcreds")
+# gitcreds::gitcreds_set()
+```
 
+# First page of something totally awesome yes.
+
+[CTRL + ALT + I to make new chunks]{.smallcaps}
+
+[ALT + MINUS makes \<-]{.smallcaps}
+
+[STR + SHIFT + M makes the %\>%]{.smallcaps}
+
+[STR + SHIFT + C can make a comment of multiple lines you highlighted]{.smallcaps}
+
+------------------------------------------------------------------------
+
+```{=html}
 <!--- The ---- is a visual line (page break looking mf) on the 
 website 
-Always ADD A SPACE BETWEEN A PAE BREAK AND the next comment, otherwise it will appear on page --->
-
+Always ADD A SPACE BETWEEN A PAGE BREAK AND the next comment, otherwise it will appear on page --->
+```
+```{=html}
 <!--- This is the best way to write a comment. 
 It also demonstrates, you can add html directly in your rmarkdown file. See: https://www.w3schools.com/html/html_comments.asp --->
-
+```
+```{=html}
 <!--- to use a multi column page we use Pandoc's fenced Div. 
@@
 But please note, we are not here to make a beautiful website, our intention is just to have a quick lab journal up and running --->
+```
+::: columns
+::: {.column width="50%"}
+# Lab Journal
 
-:::: {.columns}
-::: {.column width="50%"}
-
-# My Lab Journal
 Last compiled on `r format(Sys.time(), '%B, %Y')`
 
-*Describe lab journal here.*
+*Description: Very cool lab journal. Yes, yes.*
 
@@
 
-----
+------------------------------------------------------------------------
 
@@
 treeeeees
-
 :::
@@
 ::: {.column width="50%"}
-
-![](images/cover.jpg)
-
+![](images/krill-issue.jpg)
 :::
-::::
-
-## How to use
-
-1. Fork the repository for this website and follow instructions on `README` to get started [here](https://github.com/JochemTolsma/labjournal).
-
-2. Journal your work, by editing the .Rmd-files
-
-3. ...
-
-4. Change everything to make it your own!
-
-<br>
-
-Use the top menu to navigate through the journal.
-
-----
-
-# References
+:::

### 2024-10-02 networkvis.Rmd
w4heading
indexrenewal

--- 2024-09-20 webscraping1.Rmd
@@
 ---
-title: "Webscraping my data 1"
+title: "Chapter 9 - Network Visualisation Practice"
 author: "Verooo"
-date: "2024-09-20"
-output: html_document
----
-
----
-title: "RQ draft 3"
-author: "Verooo"
-date: "2024-09-20"
+date: "2024-09-25"
 output: html_document
@@
 ```
+
 ```{r setup, include=FALSE}
@@
 ```
+
+# 9.1 Zachary’s karate club
+
+```{r }
+require(igraph)
+g <- make_graph("Zachary")
+plot(g)
+
+# adjacentcy matrix 
+gmat <- as_adjacency_matrix(g, type = "both", sparse = FALSE)
+gmat
+```
+
+## 9.1.1. Descriptive statistics
+
+### Size
+
+```{r}
+# number of nodes
+vcount(g)
+# number of edges
+ecount(g)
+```
+
+#### degree
+
+In-degree = how many ties come “towards you”
+
+```{r}
+igraph::degree(g)
+
+hist(table(degree(g)), xlab='indegree', main= 'Histogram of indegree')
+```
+
+#### transitivity
+
+For undirected networks, the clustering coefficient is the same as the **transitivity index:\
+**the number of transitive triads divided by all possible transitive triads.\
+For directed graphs not so.
+
+```{r}
+# be aware that directed graphs are considered as undirected. but g is undirected.
+igraph::transitivity(g, type = c("localundirected"), isolates = c("NaN", "zero"))
+
+```
+
+see also: 9.1.3 triad-census
+
+#### betweenness
+
+For all dyads: testing shortest path.
+
+Number of shortest path between two nodes\
+divided by\
+How many of those shortest paths is "i" part of ?
+
+```{r}
+igraph::betweenness(g, directed = FALSE)
+```
+
+## 9.1.2 dyad-census
+
+```{r}
+igraph::dyad_census(g)
+```
+
+##9.1.3 triad-census
+
+```{r}
+igraph::triad_census(g)
+# I will use sna because it shows the names of the triads as well.
+sna::triad.census(gmat)
+
+unloadNamespace("sna")  #I will detach this package again, otherwise it will interfere with all kind of functions from igraph, and my students will hate me for that.
+
+# calculate transitivity 
+igraph::transitivity(g, type = "global")
+sna::gtrans(gmat)
+
+triad_g <- data.frame(sna::triad.census(gmat))
+
+transitivity_g <- (3 * triad_g$X300)/(triad_g$X201 + 3 * triad_g$X300)
+transitivity_g
+# 0.2556818
+
+```
+
+## 9.1.4 Network visualisation
+
+### proportional betweenness score
+
+```{r}
+# changing V
+V(g)$size = betweenness(g, normalized = T, directed = FALSE) * 60 + 10  #after some trial and error
+plot(g, mode = "undirected")
+```
+
+placing node 33 and 34 further apart:
+
+```{r}
+set.seed(2345)
+l <- layout_with_mds(g)  #https://igraph.org/r/doc/layout_with_mds.html
+plot(g, layout = l)
+```
+
+place 33 and 34 even further apart:
+
+```{r}
+l  #let us take a look at the coordinates
+l[1, 1] <- 4
+l[34, 1] <- -3.5
+plot(g, layout = l)
+```
+
+***CAUTION!!***
+
+"In the last step we manipulated our data.
+The coordinates of two nodes have been altered manually and are no longer determined by some ‘objective’ algorithm.
+Is this not the same as slightly changing an inconvenient correlation in a correlation matrix or as removing some outliers from our dataset?
+At the very minimum, make sure to tell your readers what you have done!
+Add a note/legend to your graph."
+
+```{r}
+plot(g, layout = l, margin = c(0, 0, 0, 0))
+legend(x = -2.5, y = -1.5, c("Note: the position of nodes 1 and 34 have been set by Jochem Tolsma \n for visualisation purposes only and do not reflect network properties"), bty = "n", cex = 0.8, xpd=TRUE)
+
+```
+
+PROBLEM: Note is not visible in my output
+
+SOLUTION: added the "xpd = TRUE" to legend
+
+## 9.2 Twittersphere in the Dutch HoP
+
+```{r}
+load("twitter_20190919.RData")  #change to your working directory
+str(twitter_20190919, 1)
+keyf <- twitter_20190919[[1]]
+mydata <- twitter_20190919[[2]]
+seats <- twitter_20190919[[3]]
+```
+
+So, what do we have?
+
+-   `keyf`: a data.frame on 147 Dutch MPs.
+
+-   `mydata`: This an object which is ready to analyze in RSiena. It is actually a quite complicated object. For now three things are important:
+
+    1.  The nodes in `mydata` are the same as in `keyf` and in `seats`.
+
+    2.  It contains the twitter data at three timepoints (in `mydata$depvars`). We have three layers:
+
+        -   fnet: who follows whom
+
+        -   atmnet: who atmentions whom
+
+        -   rtnet: who retweats whom
+
+    3.  It also contains time invariant information on the nodes (in `mydata$cCovars`)
+
+-   `seats`: a dataset which contains the coordinates of the seats in the House of Parliament in the Netherlands.

### 2024-10-02 week5.Rmd
indexrenewal

--- 2024-09-20 webscraping1.Rmd
@@
 ---
-title: "Webscraping my data 1"
+title: "Week 5"
 author: "Verooo"
-date: "2024-09-20"
-output: html_document
----
-
----
-title: "RQ draft 3"
-author: "Verooo"
-date: "2024-09-20"
+date: "2024-10-02"
 output: html_document
@@
 
-```{r klippy, echo=FALSE, include=TRUE}
+```{r klippy, echo=FALSE, include=FALSE}
 klippy::klippy(position = c('top', 'right'))
@@
 ```
+
+# Notes while discussing other peeps plots
+Using RSiena for evolutin of network 
+Wave, Ego alters 
+RSciena: Ego, alter, wave 
+Reorganize into an array for RSciena
+
+Set size of isolates to SMALL 
+put all isolates in one place 
+then you have enough room left to have a more "zoomed in" frame for the actual collaborator networks
+
+Or just remove all isolates lol 
+```{r}
+
+```

### 2024-10-02 index.Rmd
indexupdate

@@
 
+::: columns
+::: {.column width="50%"}
 # First page of something totally awesome yes.
@@
 
-------------------------------------------------------------------------
+Last compiled on `r format(Sys.time(), '%B, %Y')`
+
+*Description: Very cool lab journal. Yes, yes.*
 
@@
 ```
-::: columns
-::: {.column width="50%"}
-# Lab Journal
-
-Last compiled on `r format(Sys.time(), '%B, %Y')`
-
-*Description: Very cool lab journal. Yes, yes.*
-
-<br>
-
-------------------------------------------------------------------------
-
 ## Open Science

### 2024-10-02 week5-2.Rmd
week5firstpush

---
title: "Week 5  - Chapter 7 pt. 2 - Analysis"
author: "Verooo"
date: "2024-10-02"
output: html_document
---

```{r, globalsettings, echo=FALSE, warning=FALSE, results='hide'}
library(knitr)

knitr::opts_chunk$set(echo = TRUE)
opts_chunk$set(tidy.opts=list(width.cutoff=100),tidy=TRUE, warning = FALSE, message = FALSE,comment = "#>", cache=TRUE, class.source=c("test"), class.output=c("test2"))
options(width = 100)
rgl::setupKnitr()

colorize <- function(x, color) {sprintf("<span style='color: %s;'>%s</span>", color, x) }

```

```{r klippy, echo=FALSE, include=FALSE}
klippy::klippy(position = c('top', 'right'))
#klippy::klippy(color = 'darkred')
#klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done')
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# start with clean workspace
rm(list = ls())
```

# Packages
```{r}
#install.packages("tidyverse")
require (tidyverse)
require (RSiena)

```

# Functions 
```{r}

fpackage.check <- function(packages) {
    lapply(packages, FUN = function(x) {
        if (!require(x, character.only = TRUE)) {
            install.packages(x, dependencies = TRUE)
            library(x, character.only = TRUE)
        }
    })
}

fsave <- function(x, file = NULL, location = "./data/processed/") {
    ifelse(!dir.exists("data"), dir.create("data"), FALSE)
    ifelse(!dir.exists("data/processed"), dir.create("data/processed"), FALSE)
    if (is.null(file))
        file = deparse(substitute(x))
    datename <- substr(gsub("[:-]", "", Sys.time()), 1, 8)
    totalname <- paste(location, file, "_", datename, ".rda", sep = "")
    save(x, file = totalname)  #need to fix if file is reloaded as input name, not as x. 
}

fload <- function(filename) {
    load(filename)
    get(ls()[ls() != "filename"])
}

fshowdf <- function(x, ...) {
    knitr::kable(x, digits = 2, "html", ...) %>%
        kableExtra::kable_styling(bootstrap_options = c("striped", "hover")) %>%
        kableExtra::scroll_box(width = "100%", height = "300px")
}

# this is the most important one. We created it in the previous script

f_pubnets <- function(df_scholars = df, list_publications = publications, discip = "sociology", affiliation = "RU",
    waves = list(wave1 = c(2018, 2019, 2020), wave2 = c(2021, 2022, 2023))) {

    publications <- list_publications %>%
        bind_rows() %>%
        distinct(title, .keep_all = TRUE)

    df_scholars %>%
        filter(affil1 == affiliation | affil2 == affiliation) %>%
        filter(discipline == discip) -> df_sel

    networklist <- list()
    for (wave in 1:length(waves)) {
        networklist[[wave]] <- matrix(0, nrow = nrow(df_sel), ncol = nrow(df_sel))
    }

    publicationlist <- list()
    for (wave in 1:length(waves)) {
        publicationlist[[wave]] <- publications %>%
            filter(gs_id %in% df_sel$gs_id) %>%
            filter(year %in% waves[[wave]]) %>%
            select(author) %>%
            lapply(str_split, pattern = ",")
    }

    publicationlist2 <- list()
    for (wave in 1:length(waves)) {
        publicationlist2[[wave]] <- publicationlist[[wave]]$author %>%
            # lowercase
        lapply(tolower) %>%
            # Removing diacritics
        lapply(stri_trans_general, id = "latin-ascii") %>%
            # only last name
        lapply(word, start = -1, sep = " ") %>%
            # only last last name
        lapply(word, start = -1, sep = "-")
    }

    for (wave in 1:length(waves)) {
        # let us remove all publications with only one author
        remove <- which(sapply(publicationlist2[[wave]], FUN = function(x) length(x) == 1) == TRUE)
        publicationlist2[[wave]] <- publicationlist2[[wave]][-remove]
    }

    for (wave in 1:length(waves)) {
        pubs <- publicationlist2[[wave]]
        for (ego in 1:nrow(df_sel)) {
            # which ego?
            lastname_ego <- df_sel$lastname[ego]
            # for all publications
            for (pub in 1:length(pubs)) {
                # only continue if ego is author of pub
                if (lastname_ego %in% pubs[[pub]]) {
                  aut_pot <- which.max(pubs[[pub]] %in% lastname_ego)
                  # only continue if ego is first author of pub
                  if (aut_pot == 1) {
                    # check all alters/co-authors
                    for (alter in 1:nrow(df_sel)) {
                      # which alter
                      lastname_alter <- df_sel$lastname[alter]
                      if (lastname_alter %in% pubs[[pub]]) {
                        networklist[[wave]][ego, alter] <- networklist[[wave]][ego, alter] + 1
                      }
                    }
                  }
                }
            }
        }
    }
    return(list(df = df_sel, network = networklist))
}
```

# KEEP THIS ON TOP OF YOUR RSIENA CODE ALWAYS!

```{r}
fcolnet <- function(data = scholars, university = "RU", discipline = "sociology", waves = list(c(2015,
    2018), c(2019, 2023)), type = c("first")) {

    # step 1
    demographics <- do.call(rbind.data.frame, data$demographics)
    demographics <- demographics %>%
        mutate(Universiteit1.22 = replace(Universiteit1.22, is.na(Universiteit1.22), ""), Universiteit2.22 = replace(Universiteit2.22,
            is.na(Universiteit2.22), ""), Universiteit1.24 = replace(Universiteit1.24, is.na(Universiteit1.24),
            ""), Universiteit2.24 = replace(Universiteit2.24, is.na(Universiteit2.24), ""), discipline.22 = replace(discipline.22,
            is.na(discipline.22), ""), discipline.24 = replace(discipline.24, is.na(discipline.24), ""))

    sample <- which((demographics$Universiteit1.22 %in% university | demographics$Universiteit2.22 %in%
        university | demographics$Universiteit1.24 %in% university | demographics$Universiteit2.24 %in%
        university) & (demographics$discipline.22 %in% discipline | demographics$discipline.24 %in% discipline))

    demographics_soc <- demographics[sample, ]
    scholars_sel <- lapply(scholars, "[", sample)

    # step 2
    ids <- demographics_soc$au_id
    nwaves <- length(waves)
    nets <- array(0, dim = c(nwaves, length(ids), length(ids)), dimnames = list(wave = 1:nwaves, ids,
        ids))
    dimnames(nets)

    # step 3
    df_works <- tibble(works_id = unlist(lapply(scholars_sel$work, function(l) l$id)), works_author = unlist(lapply(scholars_sel$work,
        function(l) l$author), recursive = FALSE), works_year = unlist(lapply(scholars_sel$work, function(l) l$publication_year),
        recursive = FALSE))

    df_works <- df_works[!duplicated(df_works), ]

    # step 4
    if (type == "first") {
        for (j in 1:nwaves) {
            df_works_w <- df_works[df_works$works_year >= waves[[j]][1] & df_works$works_year <= waves[[j]][2],
                ]
            for (i in 1:nrow(df_works_w)) {
                ego <- df_works_w$works_author[i][[1]]$au_id[1]
                alters <- df_works_w$works_author[i][[1]]$au_id[-1]
                if (sum(ids %in% ego) > 0 & sum(ids %in% alters) > 0) {
                  nets[j, which(ids %in% ego), which(ids %in% alters)] <- 1
                }
            }
        }
    }

    if (type == "last") {
        for (j in 1:nwaves) {
            df_works_w <- df_works[df_works$works_year >= waves[[j]][1] & df_works$works_year <= waves[[j]][2],
                ]
            for (i in 1:nrow(df_works_w)) {
                ego <- rev(df_works_w$works_author[i][[1]]$au_id)[1]
                alters <- rev(df_works_w$works_author[i][[1]]$au_id)[-1]
                if (sum(ids %in% ego) > 0 & sum(ids %in% alters) > 0) {
                  nets[j, which(ids %in% ego), which(ids %in% alters)] <- 1
                }
            }
        }
    }

    if (type == "all") {
        for (j in 1:nwaves) {
            df_works_w <- df_works[df_works$works_year >= waves[[j]][1] & df_works$works_year <= waves[[j]][2],
                ]
            for (i in 1:nrow(df_works_w)) {
                egos <- df_works_w$works_author[i][[1]]$au_id
                if (sum(ids %in% egos) > 0) {
                  nets[j, which(ids %in% egos), which(ids %in% egos)] <- 1
                }
            }
        }
    }
    output <- list()
    output$data <- scholars_sel
    output$nets <- nets
    return(output)
}

```
## Load data 
```{r}
scholars <- fload("./data/processed/scholars_20240924.rda")
```

```{r}

#save the output of your function
test <- fcolnet(data = scholars, 
                university = "RU", 
                discipline = "sociology", 
                waves = list(c(2015, 2018), c(2019, 2023)), 
                type = c("first"))

```

# 7.10 Step 1: Define Data
```{r}

str(test$nets)
length(test$nets)
dim(test$nets)

```

```{r}
wave1 <- test$nets[1,,]
wave2 <- test$nets[2,,]

# let us put the diagonal to zero
diag(wave1) <- 0
diag(wave2) <- 0
# we want a binary tie (not a weighted tie)
wave1[wave1 > 1] <- 1
wave2[wave2 > 1] <- 1
# put the nets in an array
net_soc_array <- array(data = c(wave1, wave2), dim = c(dim(wave1), 2))
str(net_soc_array) #now we basically restructured this 
# dependent
net <- sienaDependent(net_soc_array)
```

# 7.11 Step 2: Create effects structure

```{r}

# didnt' make the IV gender butif i Had: mydata <- sienaDataCreate(net, gender)

#for now we will do it without
mydata <- sienaDataCreate(net)     #effects based on your data (here reciprocity and degree only)

myeff <- getEffects(mydata)
# effectsDocumentation(myeff)    #if you run this part you are told whihc ones are POSSIBLE

```
THIS IS ALL THE EFFECTS YOU COULD LOOK AT IN YOUR NETWORK 
e.g. outdegree (density), called density, three things: evaluation, endowment, and creation
  you can only include two of the three (tie creation, breaking and maintaining)
  Assumption meachnisms to make and breka a tie are the same so we only use the EVALUATION part

  All these effects are describedin the manual of RSiena Chapter 12 (9?)

# 7.12 Step 3: Get initial description

```{r}
ifelse(!dir.exists("results"), dir.create("results"), FALSE)
#if there is not a folder called "results" in your repository: make one
```

```{r}
print01Report(mydata, modelname = "./results/soc_init") # create file with report in results folder 
```
 Has a lot of information in there 
 Also: how tie CHANGED 
    Also: Jaccard index (measure of stability)
 Also rate parameter and outdegree

# 7.13 STEP 4: Specify model 
Sometimes similartostep 2 (but here you include specifically the effects you want to look at)
```{r}
# if you want to select only specific effects in your model:

myeff <- includeEffects(myeff, isolateNet, inPop, outAct)  #we know that quite a lot of staff has not published with someone else

```
inpope ppl with lots of indegrees will havelotof indegrees later (in population)
 outAct ppl with lots of outdegrees will have lot of indegrees later

 hint for my own project: interaction effect of these statistics and the effect of gender

```{r}

# myeff <- includeEffects(myeff, sameX, egoX, altX, interaction1 = "gender")

```
altX 
egos send more ties who have more on gender (aka. gender =1)

egoX
[definition?]

 "interaction1" HAS NOTHING TO DO WITH AN INTERACTION EFFECT

# 7.14 STEP 5: Estimate model 
```{r}
myAlgorithm <- sienaAlgorithmCreate(projname = "soc_init")
ansM1 <- siena07(myAlgorithm, data = mydata, effects = myeff, returnDeps = TRUE)

# if necessary estimate again!  ansM1 <- siena07(myAlgorithm, data = mydata, effects = myeff,
# prevAns = ansM1, returnDeps=TRUE)

ansM1  # shortfor answers model 1
```
convergence ratio should be <.25

# 7.15 Step 6: GOF (goodness of fit) - next week

---

# Sidenote: H- index via openAlex

Hirsch-Index is NOT scraped in open-alex already but you have the nr. of citations and you can google how someone else did it

# STUDY CHAPTER 12 of RSiena Manual!

### 2024-10-02 week5.Rmd
indexupdate
week5firstpush

@@
 ---
-title: "Week 5"
+title: "Week 5 - Chapter 7 pt.1 - Analysis"
 author: "Verooo"
@@
 output: html_document
+editor_options: 
+  markdown: 
+    wrap: 72
 ---
@@
 # Notes while discussing other peeps plots
-Using RSiena for evolutin of network 
-Wave, Ego alters 
-RSciena: Ego, alter, wave 
-Reorganize into an array for RSciena
 
-Set size of isolates to SMALL 
-put all isolates in one place 
-then you have enough room left to have a more "zoomed in" frame for the actual collaborator networks
+Using RSiena for evolutin of network Wave, Ego alters RSciena: Ego,
+alter, wave Reorganize into an array for RSciena
+
+Set size of isolates to SMALL put all isolates in one place then you
+have enough room left to have a more "zoomed in" frame for the actual
+collaborator networks
 
 Or just remove all isolates lol
+
+## decision tree . order!
+
+Something I really need a grasp of (bc very poor prioritization)!
+
+## data were scraped at author level bceasier if you want to look at author "characteristics"
+
+# Analysing data - Chapter 7 (SNASS)
+
+## custom functions
+
+```{r}
+fpackage.check <- function(packages) {
+    lapply(packages, FUN = function(x) {
+        if (!require(x, character.only = TRUE)) {
+            install.packages(x, dependencies = TRUE)
+            library(x, character.only = TRUE)
+        }
+    })
+}
+
+fsave <- function(x, file = NULL, location = "./data/processed/") {
+    ifelse(!dir.exists("data"), dir.create("data"), FALSE)
+    ifelse(!dir.exists("data/processed"), dir.create("data/processed"), FALSE)
+    if (is.null(file))
+        file = deparse(substitute(x))
+    datename <- substr(gsub("[:-]", "", Sys.time()), 1, 8)
+    totalname <- paste(location, datename, file, ".rda", sep = "")
+    save(x, file = totalname)  #need to fix if file is reloaded as input name, not as x. 
+}
+
+fload <- function(filename) {
+    load(filename)
+    get(ls()[ls() != "filename"])
+}
+
+fshowdf <- function(x, ...) {
+    knitr::kable(x, digits = 2, "html", ...) %>%
+        kableExtra::kable_styling(bootstrap_options = c("striped", "hover")) %>%
+        kableExtra::scroll_box(width = "100%", height = "300px")
+}
+```
+
+## packages
+
+RSiena RsienaTwoStep: this packages assesses the ministep assumption of
+RSiena but is useful for this tutorial devtools: to load from github
+igraph: plotting tools. For a tutorial on plotting networks, see 8
+
+```{r}
+packages = c("RSiena", "devtools", "igraph")
+fpackage.check(packages)
+devtools::install_github('JochemTolsma/RsienaTwoStep', build_vignettes=TRUE)
+packages = c("RsienaTwoStep")
+fpackage.check(packages)
+
+```
+
+## RSiena as ABM
+
+### Stochastic Actor-Oriented Models,aka. SAOM (see SNASS book)
+
+### 7.5.1 Sample an ego
+
+```{r}
+ts_net1
+
+# plot the network 
+net1g <- graph_from_adjacency_matrix(ts_net1, mode = "directed")
+coords <- layout_(net1g, nicely())  #let us keep the layout
+par(mar = c(0.1, 0.1, 0.1, 0.1))
+{
+    plot.igraph(net1g, layout = coords)
+    graphics::box()
+}
+```
+
+randomly select/sample an agent.
+
 ```{r}
 
+set.seed(24553253)
+ego <- ts_select(net = ts_net1, steps = 1)  #in rsienatwostep two actors may make a change together but here not
+ego
 ```
+
+### possible networks after ministep
+
+```{r}
+options <- ts_alternatives_ministep(net = ts_net1, ego = ego)
+# options
+plots <- lapply(options, graph_from_adjacency_matrix, mode = "directed")
+par(mar = c(0, 0, 0, 0) + 0.1)
+par(mfrow = c(1, 2))
+
+fplot <- function(x) {
+    plot.igraph(x, layout = coords, margin = 0)
+    graphics::box()
+}
+
+lapply(plots, fplot)
+```
+
+###7.5.3 Network statistics (see chapter 9 for more)
+
+```{r}
+# count the number of ties ego sends to alters
+ts_degree(net = options[[1]], ego = ego)
+# or for all options
+lapply(options, ts_degree, ego = ego)
+
+# count the number of reciprocated ties
+lapply(options, ts_recip, ego = ego)
+```
+
+In the package RsienaTwoStep there are functions for the following
+network statistics *s* :
+
+**degree:** ts_degree()\
+**reciprocity**: ts_recip()\
+**outdegree activity**: ts_outAct()\
+**indegree activity**: ts_inAct(**)**\
+**outdegree popularity:** ts_outPop()\
+**indegree popularity:** ts_inPop()\
+**transitivity:** ts_transTrip()\
+**mediated transitivity**: ts_transMedTrip()\
+**transitive reciprocated triplets**: ts_transRecTrip()\
+**number of three-cycles**: ts_cycle3()
+
+### 7.5.4 Evaluation function
+
+fi(x)=Σkβksik(x),
+
+x= network
+
+f = evaluation function (how we evaluate the nework)
+
+i = the ego "i"
+
+summing over k (k are diff. statistics (in our case degree and
+reciprocity))
+
+beta = value of the statistic
+
+s = the specific statistic for ego i for network statistics k for our
+network x
+
+we are basically counting for each stats how many we have and
+multipyling it by...
+
+```{r}
+option <- 4 # example of prior 4th option of the network of ego 4 
+ts_degree(options[[option]], ego = ego) * -1 + ts_recip(options[[option]], ego = ego) * 1.5
+```
+
+Value for the network OF ego FOUR is 0.5 (coming from (-1\*1) + (1\*1.5)
+= 0.5)
+
+Or you could use the `ts_eval()`.
+
+```{r}
+eval <- sapply(options, FUN = ts_eval, ego = ego, statistics = list(ts_degree, ts_recip), parameters = c(-1,
+    1.5))
+eval
+print("network with maximum evaluation score:")
+which.max(eval)
+```
+
+calculate the evaluation of all possible networks (10) of ego 4 :
+
+```{r}
+eval <- sapply(options, FUN = ts_eval, ego = ego, statistics = list(ts_degree, ts_recip), parameters = c(-1,
+    1.5))
+eval
+print("network with maximum evaluation score:")
+which.max(eval)
+```
+
+higher evaluation score means ego 4 is more likely to have this kind of
+network (option 4)
+
+Translating the evaluation scores we just got into probabilities.
+
+we know all probabilities will be between 0 and 1
+
+and we know all the statistics (in our case the 10) will sum up to 1
+
+1/e\^-0.5 "e to the power of -0.5" = 0.6065306 (idk how to write this in
+R so I do not get an error that object e was not found :(
+
+### 7.5.5 Choice function
+
+We sum all the evaluation scores e to power of (0.6 etc.)
+
+```{r}
+# forcing ego to make a choice 
+choice <- sample(1:length(eval), size = 1, prob = exp(eval)/sum(exp(eval)))
+print("choice:")
+choice
+# print('network:') options[[choice]]
+```
+
+When you run it multiple times, it is different one every time. (this is
+related to the see we set in the beginning. usually you would want to
+set the seed in a way that multiple people all get the same number)
+**This example should ideally be 10**.
+
+--\> This is how to perform ONE MINI STEP
+
+If we want to do it for next ego (e.g. ego ) in the network, that ego's
+network depends on our prior ego's network (here it was ego/person 4)
+
+Network changes of ego 2 depend on changes of ego 1. WHo is ego 1 and
+who is ego 2 is random.
+
+--\> Monte Carlo simulation
+
+This is Agent-based modeling (if you do not use this for estimation).
+Aka. setting rules and seeing if the output is like what we expected and
+then trial and error to simulate the output as close as possible.
+
+## 7.6 Simulation example
+
+Let us now simulate how the network **could** evolve
+given:^[18](https://snass.netlify.app/socionetsm#fn18)^
+
+-   starting point at T1T1 is `ts_net1`
+
+-   rate is set to 2
+
+-   we as scientists think only network statistics degree and
+    reciprocity are important
+
+-   `RSiena::siena07` has determined the parameters for these statistics
+    are -1 and 1.5 respectively
+
+-   We adhere to the ministep assumption and hence set `p2step` to
+    `c(1,0,0)`
+
+```{r}
+rate <- 2
+degree <- -1
+recip <- 1.5
+ts_sims(nsims = 1, net = ts_net1, startvalues = c(rate, degree, recip), statistics = list(ts_degree,
+    ts_recip), p2step = c(1, 0, 0), chain = FALSE)  #not that rate parameter is automatically included. 
+```
+
+This is one of the possible outputs from all the choices the egos made
+in the networks in this simulation.
+
+If we repeat this thousands of times, we can approximate a likely
+network constellation.
+
+## 7.7 Estimation logic
+
+*How does the estimation work?*
+
+Well, that is quite complicated. But it goes something like
+this:^[19](https://snass.netlify.app/socionetsm#fn19)^
+
+1.  Define model: researcher includes effects
+
+2.  initial parameter values of effects (commonly ‘0’)
+
+3.  simulate an outcome network based on these parameter values
+
+4.  [compare]{.underline} the network statistics of the
+    [simulated]{.underline} outcome network with the
+    [observed]{.underline} outcome network at (i.e. the *target values*)
+
+    -   based on the included effects. Thus the simulated network may
+        contain 10 ties, but the observed network may contain 20 ties.
+        Apparently, with the current parameter values we underestimate
+        the density of the outcome network.
+
+5.  tweak/update parameter values in *some smart way*
+
+    (there is plenty of maths on this but in our case manually: our
+    network density was too low, we looked at degree and reciprocity. We
+    can increase the value of degree and try to approximate a value
+    where changes in degree don't really make a change anymore. \
+    Then we would change reciprocity parameter, in our case: increase
+    it. We will have more reciprocity but also automatically increasing
+    ties because reciprocity DEPENDS on ties\
+    Thus, we need to find a way to do this automatically that can adjust
+    both numbers at the same time.\
+    We do not go about this ourselves though bc [as one may see] this is
+    not very efficient)\
+    \
+
+6.  GOTO 3 (BREAK RULE: until parameter values cannot be improved
+    anymore / or reached good fit)
+
+7.  simulate a bunch of outcome networks with the obtained parameter
+    values and compare the *expected values* of statistics of the
+    simulated outcome networks with the *target values* of the actual
+    observed outcome network.
+
+    -   [Estimate a TARGET VALUE (outcome network). In an example we did
+        it class: degree= 4, reciprocity 1]
+
+    -   we can assess the fit
+
+    -   estimate SE of the parameters
+
+Let us suppose network `s501` developed into `s502`. For more
+information on these networks see `?s501`.
+
+To estimate this network with
+`ts_estim`^[20](https://snass.netlify.app/socionetsm#fn20)^, we can do
+the following:
+
+```{r}
+# we do not calculate SE for now.
+# ans <- ts_estim(net1 = s501, net2 = s502, statistics = list(ts_degree, ts_recip), p2step = c(1, 0, 0), # used two different networks 
+#    conv = 0.01, phase3 = TRUE, itef3 = 50, verbose = TRUE)
+
+# looking at final result 
+# ans
+```
+
+#output:
+
+```         
+#>            estim        SE 
+#> rate    5.122247 1.1833275 
+#> degree -2.258332 0.1371387 
+#> recip   2.428552 0.2102846
+```
+
+## 7.8 Interpretation of parameters
+
+### Network statistics
+
+positive parameter = " i like"
+
+positive degrees? people like degrees (higher degrees)
+
+Sometimes it's easier to look at **Ratios**
+
+Dividing two probabilities
+
+when probability [statistics of one network]{.underline} is [*one more
+than* another network,]{.underline} the answer is the exponential of the
+parameter value in your model (the value we got for the network)
+
+(given that alllllll other things are same between two things = ceterus
+paribus condition)
+
+ceterus paribusis not fulfilledif we look at degrees and reciprocity
+htough, since reciprocity increasing also automatically makes the
+degrees increase
+
+if stat, for reciprocity is 2 and degree is 1, then they are of the same
+unit (as opposed to other units like age, or years etc. )
+
+#### in paper report:
+
+descriptives, statistics
+
+simple: higher scores = more positive
+
+and recalculate in probability ratio: take exponent of parameter value \
+"if netw. increases in this stats by one the probability ration is
+this."
+
+(you could have HUGE parameters but they might not be relevant at all
+for the macro level change in networks)
+
+Model of RSiena is modeling on EGO LEVEL only
+
+-   statements like gender homphiliy is more important in my network
+    than educational homophily
+
+do smth similar
+
+test with Rsiena:
+
+-   for egos: Given a choice, gender homphily is more important than
+    education...
+
+-   more nuanced: GIVEN the network at T1, ...
+
+MATCH YOUR HYPOTHESIS TO YOUR METHODS

### 2024-10-02 week5.Rmd
correcitonweek5

@@
 output: html_document
-editor_options: 
-  markdown: 
-    wrap: 72
 ---
@@
 
-## data were scraped at author level bceasier if you want to look at author "characteristics"
+***data were scraped at author level bc easier if you want to look at
+author "characteristics"***
+
+---
 
@@
 
-## packages
+## Packages
 
@@
     can increase the value of degree and try to approximate a value
-    where changes in degree don't really make a change anymore. \
+    where changes in degree don't really make a change anymore.\
     Then we would change reciprocity parameter, in our case: increase
@@
 
-#### in paper report:
+# in paper report:
 
@@
 
-and recalculate in probability ratio: take exponent of parameter value \
+and recalculate in probability ratio: take exponent of parameter value\
 "if netw. increases in this stats by one the probability ration is

### 2024-10-02 datapractice1.Rmd
datapracticew5

--- 2024-10-02 week5-2.Rmd
@@
 ---
-title: "Week 5  - Chapter 7 pt. 2 - Analysis"
+title: "Practice handling data 1 - 02.10.24"
 author: "Verooo"
@@
 
-# 7.10 Step 1: Define Data
 ```{r}
+nets <- test$nets
 
-str(test$nets)
-length(test$nets)
-dim(test$nets)
+df_ego_demo <- test$data$demographics
+df_ego_oa <- test$data$scholars_oa
+df_ego_works <- test$data$works
+
+# str(df_ego_demo, 1)
+# df_ego_demo[[1]]
+
+df_ego_demo <- do.call(rbind.data.frame, df_ego_demo)
+
+str(df_ego_oa, 1)
+df_ego_oa[[1]]
+
+df_ego_oa <- do.call(rbind.data.frame, df_ego_oa)
+
+?join.data.frame
+df_ego <- left_join(df_ego_demo, df_ego_oa, by = join_by(au_id == id))
+
+#yes, the correct ones!!!
+rownames(nets[1,,]) == df_ego$au_id
+
+df_ego_works[[1]]$author
+df_ego$Naam
+# df_ego$gender <- c(1,0,1,1) # manually fill in gender
 
 ```
-
-```{r}
-wave1 <- test$nets[1,,]
-wave2 <- test$nets[2,,]
-
-# let us put the diagonal to zero
-diag(wave1) <- 0
-diag(wave2) <- 0
-# we want a binary tie (not a weighted tie)
-wave1[wave1 > 1] <- 1
-wave2[wave2 > 1] <- 1
-# put the nets in an array
-net_soc_array <- array(data = c(wave1, wave2), dim = c(dim(wave1), 2))
-str(net_soc_array) #now we basically restructured this 
-# dependent
-net <- sienaDependent(net_soc_array)
-```
-
-# 7.11 Step 2: Create effects structure
-
-```{r}
-
-# didnt' make the IV gender butif i Had: mydata <- sienaDataCreate(net, gender)
-
-#for now we will do it without
-mydata <- sienaDataCreate(net)     #effects based on your data (here reciprocity and degree only)
-
-myeff <- getEffects(mydata)
-# effectsDocumentation(myeff)    #if you run this part you are told whihc ones are POSSIBLE
-
-```
-THIS IS ALL THE EFFECTS YOU COULD LOOK AT IN YOUR NETWORK 
-e.g. outdegree (density), called density, three things: evaluation, endowment, and creation
-  you can only include two of the three (tie creation, breaking and maintaining)
-  Assumption meachnisms to make and breka a tie are the same so we only use the EVALUATION part
-
-  All these effects are describedin the manual of RSiena Chapter 12 (9?)
-
-# 7.12 Step 3: Get initial description
-
-```{r}
-ifelse(!dir.exists("results"), dir.create("results"), FALSE)
-#if there is not a folder called "results" in your repository: make one
-```
-
-```{r}
-print01Report(mydata, modelname = "./results/soc_init") # create file with report in results folder 
-```
- Has a lot of information in there 
- Also: how tie CHANGED 
-    Also: Jaccard index (measure of stability)
- Also rate parameter and outdegree
-
-# 7.13 STEP 4: Specify model 
-Sometimes similartostep 2 (but here you include specifically the effects you want to look at)
-```{r}
-# if you want to select only specific effects in your model:
-
-myeff <- includeEffects(myeff, isolateNet, inPop, outAct)  #we know that quite a lot of staff has not published with someone else
-
-```
-inpope ppl with lots of indegrees will havelotof indegrees later (in population)
- outAct ppl with lots of outdegrees will have lot of indegrees later
-
- hint for my own project: interaction effect of these statistics and the effect of gender
-
-```{r}
-
-# myeff <- includeEffects(myeff, sameX, egoX, altX, interaction1 = "gender")
-
-```
-altX 
-egos send more ties who have more on gender (aka. gender =1)
-
-egoX
-[definition?]
-
- "interaction1" HAS NOTHING TO DO WITH AN INTERACTION EFFECT
-
-# 7.14 STEP 5: Estimate model 
-```{r}
-myAlgorithm <- sienaAlgorithmCreate(projname = "soc_init")
-ansM1 <- siena07(myAlgorithm, data = mydata, effects = myeff, returnDeps = TRUE)
-
-# if necessary estimate again!  ansM1 <- siena07(myAlgorithm, data = mydata, effects = myeff,
-# prevAns = ansM1, returnDeps=TRUE)
-
-ansM1  # shortfor answers model 1
-```
-convergence ratio should be <.25
-
-# 7.15 Step 6: GOF (goodness of fit) - next week
-
----
-
-# Sidenote: H- index via openAlex
-
-Hirsch-Index is NOT scraped in open-alex already but you have the nr. of citations and you can google how someone else did it
-
-# STUDY CHAPTER 12 of RSiena Manual!

### 2024-10-09 week6.Rmd
week6page

--- 2024-10-02 datapractice1.Rmd
@@
 ---
-title: "Practice handling data 1 - 02.10.24"
+title: "Week 6"
 author: "Verooo"
-date: "2024-10-02"
+date: "2024-10-09"
 output: html_document
@@
 
-```{r}
-# start with clean workspace
-rm(list = ls())
-```
+::: {.column width="50%"} ![](images/krill-yourself.jpg)
 
-# Packages
-```{r}
-#install.packages("tidyverse")
-require (tidyverse)
-require (RSiena)
+# "Kudos make you run!" - paper discussion
 
-```
+Franken, R., Bekhuis, H., & Tolsma, J.
+(2022).
+Kudos make you run!
+How runners influence each other on the online social network Strava.
+Social Networks, 72, 151–164.
+<https://doi.org/10.1016/j.socnet.2022.10.001>
 
-# Functions 
-```{r}
+## Event vs. relation
 
-fpackage.check <- function(packages) {
-    lapply(packages, FUN = function(x) {
-        if (!require(x, character.only = TRUE)) {
-            install.packages(x, dependencies = TRUE)
-            library(x, character.only = TRUE)
-        }
-    })
-}
-
-fsave <- function(x, file = NULL, location = "./data/processed/") {
-    ifelse(!dir.exists("data"), dir.create("data"), FALSE)
-    ifelse(!dir.exists("data/processed"), dir.create("data/processed"), FALSE)
-    if (is.null(file))
-        file = deparse(substitute(x))
-    datename <- substr(gsub("[:-]", "", Sys.time()), 1, 8)
-    totalname <- paste(location, file, "_", datename, ".rda", sep = "")
-    save(x, file = totalname)  #need to fix if file is reloaded as input name, not as x. 
-}
-
-fload <- function(filename) {
-    load(filename)
-    get(ls()[ls() != "filename"])
-}
-
-fshowdf <- function(x, ...) {
-    knitr::kable(x, digits = 2, "html", ...) %>%
-        kableExtra::kable_styling(bootstrap_options = c("striped", "hover")) %>%
-        kableExtra::scroll_box(width = "100%", height = "300px")
-}
-
-# this is the most important one. We created it in the previous script
-
-f_pubnets <- function(df_scholars = df, list_publications = publications, discip = "sociology", affiliation = "RU",
-    waves = list(wave1 = c(2018, 2019, 2020), wave2 = c(2021, 2022, 2023))) {
-
-    publications <- list_publications %>%
-        bind_rows() %>%
-        distinct(title, .keep_all = TRUE)
-
-    df_scholars %>%
-        filter(affil1 == affiliation | affil2 == affiliation) %>%
-        filter(discipline == discip) -> df_sel
-
-    networklist <- list()
-    for (wave in 1:length(waves)) {
-        networklist[[wave]] <- matrix(0, nrow = nrow(df_sel), ncol = nrow(df_sel))
-    }
-
-    publicationlist <- list()
-    for (wave in 1:length(waves)) {
-        publicationlist[[wave]] <- publications %>%
-            filter(gs_id %in% df_sel$gs_id) %>%
-            filter(year %in% waves[[wave]]) %>%
-            select(author) %>%
-            lapply(str_split, pattern = ",")
-    }
-
-    publicationlist2 <- list()
-    for (wave in 1:length(waves)) {
-        publicationlist2[[wave]] <- publicationlist[[wave]]$author %>%
-            # lowercase
-        lapply(tolower) %>%
-            # Removing diacritics
-        lapply(stri_trans_general, id = "latin-ascii") %>%
-            # only last name
-        lapply(word, start = -1, sep = " ") %>%
-            # only last last name
-        lapply(word, start = -1, sep = "-")
-    }
-
-    for (wave in 1:length(waves)) {
-        # let us remove all publications with only one author
-        remove <- which(sapply(publicationlist2[[wave]], FUN = function(x) length(x) == 1) == TRUE)
-        publicationlist2[[wave]] <- publicationlist2[[wave]][-remove]
-    }
-
-    for (wave in 1:length(waves)) {
-        pubs <- publicationlist2[[wave]]
-        for (ego in 1:nrow(df_sel)) {
-            # which ego?
-            lastname_ego <- df_sel$lastname[ego]
-            # for all publications
-            for (pub in 1:length(pubs)) {
-                # only continue if ego is author of pub
-                if (lastname_ego %in% pubs[[pub]]) {
-                  aut_pot <- which.max(pubs[[pub]] %in% lastname_ego)
-                  # only continue if ego is first author of pub
-                  if (aut_pot == 1) {
-                    # check all alters/co-authors
-                    for (alter in 1:nrow(df_sel)) {
-                      # which alter
-                      lastname_alter <- df_sel$lastname[alter]
-                      if (lastname_alter %in% pubs[[pub]]) {
-                        networklist[[wave]][ego, alter] <- networklist[[wave]][ego, alter] + 1
-                      }
-                    }
-                  }
-                }
-            }
-        }
-    }
-    return(list(df = df_sel, network = networklist))
-}
-```
-
-# KEEP THIS ON TOP OF YOUR RSIENA CODE ALWAYS!
-
-```{r}
-fcolnet <- function(data = scholars, university = "RU", discipline = "sociology", waves = list(c(2015,
-    2018), c(2019, 2023)), type = c("first")) {
-
-    # step 1
-    demographics <- do.call(rbind.data.frame, data$demographics)
-    demographics <- demographics %>%
-        mutate(Universiteit1.22 = replace(Universiteit1.22, is.na(Universiteit1.22), ""), Universiteit2.22 = replace(Universiteit2.22,
-            is.na(Universiteit2.22), ""), Universiteit1.24 = replace(Universiteit1.24, is.na(Universiteit1.24),
-            ""), Universiteit2.24 = replace(Universiteit2.24, is.na(Universiteit2.24), ""), discipline.22 = replace(discipline.22,
-            is.na(discipline.22), ""), discipline.24 = replace(discipline.24, is.na(discipline.24), ""))
-
-    sample <- which((demographics$Universiteit1.22 %in% university | demographics$Universiteit2.22 %in%
-        university | demographics$Universiteit1.24 %in% university | demographics$Universiteit2.24 %in%
-        university) & (demographics$discipline.22 %in% discipline | demographics$discipline.24 %in% discipline))
-
-    demographics_soc <- demographics[sample, ]
-    scholars_sel <- lapply(scholars, "[", sample)
-
-    # step 2
-    ids <- demographics_soc$au_id
-    nwaves <- length(waves)
-    nets <- array(0, dim = c(nwaves, length(ids), length(ids)), dimnames = list(wave = 1:nwaves, ids,
-        ids))
-    dimnames(nets)
-
-    # step 3
-    df_works <- tibble(works_id = unlist(lapply(scholars_sel$work, function(l) l$id)), works_author = unlist(lapply(scholars_sel$work,
-        function(l) l$author), recursive = FALSE), works_year = unlist(lapply(scholars_sel$work, function(l) l$publication_year),
-        recursive = FALSE))
-
-    df_works <- df_works[!duplicated(df_works), ]
-
-    # step 4
-    if (type == "first") {
-        for (j in 1:nwaves) {
-            df_works_w <- df_works[df_works$works_year >= waves[[j]][1] & df_works$works_year <= waves[[j]][2],
-                ]
-            for (i in 1:nrow(df_works_w)) {
-                ego <- df_works_w$works_author[i][[1]]$au_id[1]
-                alters <- df_works_w$works_author[i][[1]]$au_id[-1]
-                if (sum(ids %in% ego) > 0 & sum(ids %in% alters) > 0) {
-                  nets[j, which(ids %in% ego), which(ids %in% alters)] <- 1
-                }
-            }
-        }
-    }
-
-    if (type == "last") {
-        for (j in 1:nwaves) {
-            df_works_w <- df_works[df_works$works_year >= waves[[j]][1] & df_works$works_year <= waves[[j]][2],
-                ]
-            for (i in 1:nrow(df_works_w)) {
-                ego <- rev(df_works_w$works_author[i][[1]]$au_id)[1]
-                alters <- rev(df_works_w$works_author[i][[1]]$au_id)[-1]
-                if (sum(ids %in% ego) > 0 & sum(ids %in% alters) > 0) {
-                  nets[j, which(ids %in% ego), which(ids %in% alters)] <- 1
-                }
-            }
-        }
-    }
-
-    if (type == "all") {
-        for (j in 1:nwaves) {
-            df_works_w <- df_works[df_works$works_year >= waves[[j]][1] & df_works$works_year <= waves[[j]][2],
-                ]
-            for (i in 1:nrow(df_works_w)) {
-                egos <- df_works_w$works_author[i][[1]]$au_id
-                if (sum(ids %in% egos) > 0) {
-                  nets[j, which(ids %in% egos), which(ids %in% egos)] <- 1
-                }
-            }
-        }
-    }
-    output <- list()
-    output$data <- scholars_sel
-    output$nets <- nets
-    return(output)
-}
-
-```
-## Load data 
-```{r}
-scholars <- fload("./data/processed/scholars_20240924.rda")
-```
+-   Giving a like (aka. a "kudos" on the Strava platform) is an *event* but RSiena looks at *relationships,* which are more constant.
 
@@
 
-#save the output of your function
-test <- fcolnet(data = scholars, 
-                university = "RU", 
-                discipline = "sociology", 
-                waves = list(c(2015, 2018), c(2019, 2023)), 
-                type = c("first"))
-
 ```
-
-```{r}
-nets <- test$nets
-
-df_ego_demo <- test$data$demographics
-df_ego_oa <- test$data$scholars_oa
-df_ego_works <- test$data$works
-
-# str(df_ego_demo, 1)
-# df_ego_demo[[1]]
-
-df_ego_demo <- do.call(rbind.data.frame, df_ego_demo)
-
-str(df_ego_oa, 1)
-df_ego_oa[[1]]
-
-df_ego_oa <- do.call(rbind.data.frame, df_ego_oa)
-
-?join.data.frame
-df_ego <- left_join(df_ego_demo, df_ego_oa, by = join_by(au_id == id))
-
-#yes, the correct ones!!!
-rownames(nets[1,,]) == df_ego$au_id
-
-df_ego_works[[1]]$author
-df_ego$Naam
-# df_ego$gender <- c(1,0,1,1) # manually fill in gender
-
-```

### 2024-10-27 Webscraping-Chapter8-tutorial.Rmd
journalupdatew6bug

@@
 #install.packages("xml2")
+
 require(xml2)
+
 #xml2:This is what the writers of the package say about it: “Work with XML files using a simple, consistent interface.” So we can manipulate the data scraped with rvest, using the xml2 package functions

### 2024-10-27 week6.Rmd
journalupdatew6bug

--- 2024-10-02 datapractice1.Rmd
@@
 
+::: {.column width="50%"} 
+![](images/krill-yourself.jpg)
+
+# "Kudos make you run!" - paper discussion
+
+Franken, R., Bekhuis, H., & Tolsma, J.
+(2022).
+Kudos make you run!
+How runners influence each other on the online social network Strava.
+Social Networks, 72, 151–164.
+<https://doi.org/10.1016/j.socnet.2022.10.001>
+
+## Tie meaning
+
+### Event vs. relation
+
+-   Giving a like (aka. a "kudos" on the Strava platform) is an *event* but RSiena looks at *relationships,* which are more constant.
+
+## Demarkation of sample
+
+important to define
+
+## what we wanna know
+
+behavior of egos as consequence of their network *ties*
+
+## Reason for why RSiena
+
+in paper: closest to causality
+
+not for this paper but mabe fits to in our projects in this course: to control for higher macro level influences
+
+## Main network statistic
+
+### Frequency, volume, (and intensity) of doing sport
+
+-   Frequency (how often you do sports, aka. nr. of activities)
+
+-   Volume (how long),
+
+-   (and intensity) of doing sport
+
+    -   intensity is unethical to scrape so it was not scraped (heart rate, pace etc.)
+
+## theory of influence
+
+if validated by peers (you have more kudos) more likely to run again
+
+If you have higher in-degree, leads to behavioral increase
+
+ACTUALITY: the more **different** people you received kudos by in a month: the more likely they were to do activity again
+
+The more out degrees the more people tended to act in similar way
+
+people giving kudos to people with lower activity more likely to decrease activity than someone giving the same amount of kudos to people with higher activity
+
+## Evaluation of *behavior*
+
+-   behavior = *Z*
+
+-   network = *X*
+
+-   X ij is outdegrees
+
+-   1 if there is relation
+
+-   0 if there is no relation
+
+-   we want alter mean effect which is the alter TOTAL effect DIVIDED by MEAN effect
+
+-   RSiena models the scores before doing the formulas so the RSiena manual likely differs from what we talked about
+
+# Netw. Statistics: Reciprocity
+
+## RSiena statistics
+
+SBeh = behavior
+
+SNet = network
+
+## Reciprocity formula form RSiena manual
+
+<https://www.stats.ox.ac.uk/~snijders/siena/RSiena_Manual.pdf>
+
+Xij = value for tie from i to j [1 or 0]
+
+Xji = value tie from j to i [1 or 0]
+
+# Final project information
+
+-   statistics: include degrees, reciprocity
+
+-   control for skewness (indegree, outdegree, popularity)
+
+often: friends of friends become friends. Most often bc of *opportunity structures*.
+
+-   including transitivity effect
+
+    -   only include one transtrip effect transtrip1 not the other ones for now
+
+# GOF
+
+- tests if our model is able to replicate the data
+
+# Playing arond with my data
+
+##clean workspace
+
 ```{r}
@@
 
-# Packages
+## packages
+
 ```{r}
@@
 require (RSiena)
-
 ```
 
-# Functions 
+## Functions
+
 ```{r}
@@
 
-# KEEP THIS ON TOP OF YOUR RSIENA CODE ALWAYS!
+## KEEP THIS ON TOP OF YOUR RSIENA CODE ALWAYS!
 
@@
     nwaves <- length(waves)
-    nets <- array(0, dim = c(nwaves, length(ids), length(ids)), dimnames = list(wave = 1:nwaves, ids,
-        ids))
+    nets <- array(0, dim = c(nwaves, length(ids), length(ids)), dimnames = list(wave = 1:nwaves, ids, ids))
     dimnames(nets)
@@
 ```
+
 ## Load data
+
 ```{r}
@@
 ```{r}
-
 #save the output of your function
@@
 
+### demographics    
+```{r}
+
+df_ego_demo <- test$data$demographics
+df_ego_demo <- do.call(rbind.data.frame, df_ego_demo)
+
+df_ego_oa <- test$data$scholars_oa 
+df_ego_oa <- do.call(rbind.data.frame, df_ego_oa)
+# 
+# df_ego_works <- test$data$works  #did not do anything with this one yet
+# 
+df_ego <- left_join(df_ego_demo, df_ego_oa, by = join_by(au_id == id))
+
+```
+
+```{r}
+df_ego_demo <- do.call(rbind.data.frame, df_ego_demo)
+df_ego_demo[[1]]
+
+str(df_ego_oa, 1)
+# df_ego_oa <- do.call(rbind.data.frame, df_ego_oa)
+# df_ego_oa[[1]]
+
+# ?join.data.frame
+
+# rownames(nets[1,,]) == df_ego$au_id # checking if the author id's are the same as in df_ego in nets dataframe 
+# Yes, the correct ones!!
+```
+
+```{r}
+df_ego$Naam
+df_ego$gender <- c(0,1,0,1,0,0,1,1,0,0,
+                   0,1,1,0,1,0,1,1,1,1,
+                   0,1,1,0,1,1,0,1,0,1,
+                   0,1,0,0,0,0,0,0,1,0,
+                   0,1,1,1,0,1,0,1,0,0) 
+# manually filled in gender 0 = woman, 1 = man, based on majority NL voornamen bank
+
+# view(df_ego[c('Naam', 'gender', 'au_id')])
+
+```
+
+# RSiena
+
+1.  Define data
+2.  Create effects structure
+3.  Get initial description
+4.  Specify model
+5.  Estimate model
+6.  GOF measures [week7]
+
+## Step 1: Define data
+
+### dep var
+
 ```{r}
 nets <- test$nets
+wave1 <- test$nets[1, , ]
+wave2 <- test$nets[2, , ]
 
-df_ego_demo <- test$data$demographics
-df_ego_oa <- test$data$scholars_oa
-df_ego_works <- test$data$works
+# let us put the diagonal to zero
+diag(wave1) <- 0
+diag(wave2) <- 0
+# we want a binary tie (not a weighted tie)
+wave1[wave1 > 1] <- 1
+wave2[wave2 > 1] <- 1
+# put the nets in an array
+net_soc_array <- array(data = c(wave1, wave2), dim = c(dim(wave1), 2))
 
-# str(df_ego_demo, 1)
-# df_ego_demo[[1]]
-
-df_ego_demo <- do.call(rbind.data.frame, df_ego_demo)
-
-str(df_ego_oa, 1)
-df_ego_oa[[1]]
-
-df_ego_oa <- do.call(rbind.data.frame, df_ego_oa)
-
-?join.data.frame
-df_ego <- left_join(df_ego_demo, df_ego_oa, by = join_by(au_id == id))
-
-#yes, the correct ones!!!
-rownames(nets[1,,]) == df_ego$au_id
-
-df_ego_works[[1]]$author
-df_ego$Naam
-# df_ego$gender <- c(1,0,1,1) # manually fill in gender
+# dependent
+net <- sienaDependent(net_soc_array)
 
 ```
+
+### gender
+
+```{r}
+
+gender <- coCovar(df_ego$gender)
+
+```
+
+### combine data
+
+```{r}
+mydata <- sienaDataCreate(net, gender)
+```
+
+## Step 2: Create effects structure
+
+```{r}
+myeff <- getEffects(mydata)
+```
+
+## Step 3: Get initial description
+
+## Step 4: Specify model
+
+```{r}
+myeff <- getEffects(mydata)
+myeff <- includeEffects(myeff, sameX, interaction1 = 'gender')
+```
+
+## Step 5: Estimate model
+
+```{r}
+myAlgorithm <- sienaAlgorithmCreate(projname = "soc_init")
+ansM1 <- siena07(myAlgorithm, data = mydata, effects = myeff, returnDeps = TRUE)
+
+#0 and 1 is about whether tie is the same now, notabout male and female anymore
+
+```
+
+## (Step 6: GOF measures [week7]

### 2024-10-27 weekbacktrack.Rmd
journalupdatew6bug

--- 2024-10-09 week6.Rmd
@@
 ---
-title: "Week 6"
+title: "week getbackontrack"
 author: "Verooo"
-date: "2024-10-09"
+date: "2024-10-27"
 output: html_document
@@
 
-::: {.column width="50%"} ![](images/krill-yourself.jpg)
+# Brainstorm
 
-# "Kudos make you run!" - paper discussion
+## Parts fo project
 
-Franken, R., Bekhuis, H., & Tolsma, J.
-(2022).
-Kudos make you run!
-How runners influence each other on the online social network Strava.
-Social Networks, 72, 151–164.
-<https://doi.org/10.1016/j.socnet.2022.10.001>
+### Research Design
 
-## Event vs. relation
+-   Clarify Research Questions
 
--   Giving a like (aka. a "kudos" on the Strava platform) is an *event* but RSiena looks at *relationships,* which are more constant.
+-   Clarify design to answer this question
 
-```{r}
+-   Clarify which data is needed in the design
 
-```
+### Steps to analysis
+
+-   Step 1: Define data
+
+-   Step 2: Create effects structure
+
+-   Step 3: Get initial description
+
+-   Step 4: Specify model
+
+-   Step 5: Estimate model
+
+-   Step 6: Goodness of Fit
+
+### Report writing
+
+-   Introduction
+
+-   Theory
+
+-   Data & Methods
+
+-   Results
+
+-   Discussion & Conclusion
+
+### Simultaneously possible
+
+-   Clarify RQs and Design \<-\> Writing introduction and theory
+
+-   Defining Data & effects structure, initial description and model specification \<-\> Data & Methods part
+
+-   Estimate Model & Goodness of fit \<-\> Results section
+
+-   Afterwards: Discussion and Conclusion
+
+## Timeline
+
+tentative deadline: Saturday, 16.11.24

### 2024-10-27 week5-2.Rmd
getbackontrack

@@
 
+# Week 5-2
 ```{r, globalsettings, echo=FALSE, warning=FALSE, results='hide'}
@@
 ```
+
+![](images/you-krilled-him.jpg)
 
@@
 # STUDY CHAPTER 12 of RSiena Manual! 
+# COLLECTIVELY SEND PAPER TO JOCHEM BEFORE WEEKEND!
+# PrACTICE WITH RSIENA 
+# LOOK AT MANUAL
+
+# DONT GO OVERBOARD!!! 
+# REMAIN FOCUSED!!!

### 2024-10-27 week5.Rmd
datapracticew5
getbackontrack

@@
 ---
-
+# Week 5-1
 ```{r, globalsettings, echo=FALSE, warning=FALSE, results='hide'}
@@
 ```
+::: {.column width="50%"}
+![](images/krill-yourself.jpg)
+:::
 
-# Notes while discussing other peeps plots
+# Notes while discussing other peeps' plots
 

### 2024-10-27 week6.Rmd
getbackontrack

@@
 ---
-
+# Week 6
 ```{r, globalsettings, echo=FALSE, warning=FALSE, results='hide'}

### 2024-10-27 weekbacktrack.Rmd
getbackontrack

@@
 
-## Parts fo project
+## Project parts
 
@@
 
-tentative deadline: Saturday, 16.11.24
+tentative deadline: Saturday, 23.11.24
+
++--------------------------------------------------------------------+------------------------------------------------+---------------------------------------------------------------+-----------------------------------------------------------------------+--------------------------------------------------------------------------+-----------------------------------------------------------------------------------------+------------------------------------------+
+| Mon                                                                | Tue                                            | Wed                                                           | Thu                                                                   | Fri                                                                      | Sat                                                                                     | Sun                                      |
++:===================================================================+:===============================================+:==============================================================+:======================================================================+:=========================================================================+:========================================================================================+:=========================================+
+| 28\.
+| 29\.
+| 30\.
+| 31\.
+| 01.11.
+| 02\.
+| 03\.
+|
+|                                                                    |                                                |                                                               |                                                                       |                                                                          |                                                                                         |                                          |
+| ![](images/used_arson%20frog.jpg)                                  | ![](images/used_arson%20frog.jpg){width="952"} | ![](images/socialnetworking.jpg){width="800"}Clarify RQs [D]\ | ![](images/socialnetworking_meh.jpg){width="800"}Intro and theory [W] | ![](images/socialnetworking.jpg){width="800"}Intro and theory [W]\       | ![](images/socialnetworking_meh.jpg){width="800"}Define data [S1]                       | ![](images/Trixie-joke.jpg){width="800"} |
+|                                                                    |                                                | & Clarify design [D]                                          |                                                                       | Clarify [D] & define data [S1]                                           |                                                                                         |                                          |
++--------------------------------------------------------------------+------------------------------------------------+---------------------------------------------------------------+-----------------------------------------------------------------------+--------------------------------------------------------------------------+-----------------------------------------------------------------------------------------+------------------------------------------+
+| 04\.
+| 05\.
+| 06\.
+| 07\.
+| 08\.
+| 09\.
+| 10\.
+|
+|                                                                    |                                                |                                                               |                                                                       |                                                                          |                                                                                         |                                          |
+| ![](images/socialnetworking_meh.jpg){width="800"}Define data [S1]\ | ![](images/used_arson%20frog.jpg){width="952"} | ![](images/used_arson%20frog.jpg)                             | ![](images/socialnetworking_meh.jpg){width="800"}\                    | ![](images/socialnetworking.jpg){width="800"}Initial description [S3]\   | ![](images/socialnetworking.jpg){width="800"}Plotting                                   | ![](images/Trixie-joke.jpg){width="800"} |
+| & create effects structure [S2]                                    |                                                |                                                               | Create effects structure [S2]\                                        | & plotting                                                               |                                                                                         |                                          |
++--------------------------------------------------------------------+------------------------------------------------+---------------------------------------------------------------+-----------------------------------------------------------------------+--------------------------------------------------------------------------+-----------------------------------------------------------------------------------------+------------------------------------------+
+| 11\.
+| 12\.
+| 13\.
+| 14\.
+| 15\.
+| 16\.
+| 17\.
+|
+|                                                                    |                                                |                                                               |                                                                       |                                                                          |                                                                                         |                                          |
+| ![](images/socialnetworking_meh.jpg){width="800"}Plotting          | ![](images/used_arson%20frog.jpg){width="952"} | ![](images/used_arson%20frog.jpg)                             | ![](images/socialnetworking.jpg){width="800"}Specify model [S4]\      | ![](images/socialnetworking.jpg){width="800"}Data & methods [W]          | ![](images/socialnetworking.jpg){width="800"}Estimate model [S5] & goodness of fit [S6] | ![](images/Trixie-joke.jpg){width="800"} |
+|                                                                    |                                                |                                                               | Data & methods part [W]                                               |                                                                          |                                                                                         |                                          |
++--------------------------------------------------------------------+------------------------------------------------+---------------------------------------------------------------+-----------------------------------------------------------------------+--------------------------------------------------------------------------+-----------------------------------------------------------------------------------------+------------------------------------------+
+| 18\.
+| 19\.
+| 20\.
+| 21\.
+| 22\.
+| **23.**                                                                                 | 24\.
+|
+|                                                                    |                                                |                                                               |                                                                       |                                                                          |                                                                                         |                                          |
+| ![](images/socialnetworking_meh.jpg){width="800"}Results [W]       | ![](images/used_arson%20frog.jpg){width="952"} | ![](images/used_arson%20frog.jpg)                             | ![](images/socialnetworking_meh.jpg){width="800"}Finish results [W]   | ![](images/socialnetworking.jpg){width="800"}Discussion & conclusion [W] | ![](images/socialnetworking.jpg){width="800"}Read over project & hand in!
+| ![](images/Trixie-joke.jpg){width="800"} |
++--------------------------------------------------------------------+------------------------------------------------+---------------------------------------------------------------+-----------------------------------------------------------------------+--------------------------------------------------------------------------+-----------------------------------------------------------------------------------------+------------------------------------------+
+
+: Days overview
+
+**Legend**
+
+::: columns
+::: {.column width="50%"}
+![social network plot (color) = time for SNA (obvious... or not?)](images/socialnetworking.jpg){width="80"}
+
+![social network plot (muted) = not a lot of time for SNA, but SOME](images/socialnetworking_meh.jpg){width="80"}
+:::
+
+::: {.column width="50%"}
+![arson = otherwise busy/NO time for SNA](images/used_arson%20frog.jpg){width="80"}
+
+![you think this is a joke? = chores, admin work, and mental breakdowns/ NO time for SNA](images/Trixie-joke.jpg){width="80"}
+:::
+:::
+
+[D] = task refers to research design
+
+[S#] = task refers to step of analysis
+
+[W] = task refers to writing the report
+
+### Timeline Question
+
+When is plotting done in this progression? At the initial description part or earlier?
+
+## Project Planning
+
+I have decided to drop another course I was taking and focus on the deadline of this course.
+
+I think the workload of both courses' deadlines exceeds my capacities, especially since the courses of PER 3 already start on 04.11. and I also have duties relating to my board year simultaneously.
+
+### Suggestions for Jochem:
+
+I will update you once a week to inform you of my progress.
+This can act as an "accountability-measure" and pushes me to face some struggles head-on, that I would otherwise try to avoid.
+It also creates a predesignated time to discuss the project, which can help me ask questions I would otherwise deem "not important enough to reach out to you".
+\
+I propose that I write you an email about the **current state of affairs on Mondays**, since I cannot work on the project on Tuesday and Wednesday anyways and that gives you some time to reply.
+Please let me know if this is okay for you.
+\
+In your reply I would appreciate input on how to move on in case I am facing a hurdle that "stalls" the project's progress, and I also welcome redirection if I seem to get "lost in the sauce".
+Any hints on how to take "shortcuts" that I was not aware of are also very much invited (e.g.
+"I know of this online resource that is about *exactly* this issue.").

### 2024-10-30 clarifyRQsandDesign.Rmd
restructurecommit

---
title: "Clarify RQ and Design"
author: "Verooo"
date: "2024-10-30"
output: html_document
---

```{r, globalsettings, echo=FALSE, warning=FALSE, results='hide'}
library(knitr)

knitr::opts_chunk$set(echo = TRUE)
opts_chunk$set(tidy.opts=list(width.cutoff=100),tidy=TRUE, warning = FALSE, message = FALSE,comment = "#>", cache=TRUE, class.source=c("test"), class.output=c("test2"))
options(width = 100)
rgl::setupKnitr()

colorize <- function(x, color) {sprintf("<span style='color: %s;'>%s</span>", color, x) }

```

```{r klippy, echo=FALSE, include=FALSE}
klippy::klippy(position = c('top', 'right'))
#klippy::klippy(color = 'darkred')
#klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done')
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Clarify Research Questions

**RQ1a:**

To what extent does gender homophily occur across all co-publications of the staff of the Sociology Department and Political Science Department at Radboud University?

aka. looking at whole sample: do we see homophiliy? how much ?

**RQ1b:**

To what extent do the two departments differ in their gender homophily?

aka. looking at Sociology Department and extent of homphily in there \
and comparing it with Political Science Department and extent of homophily in there.

**RQ2:**

Jochem's input: insert here another RQ before last RQ

Do we observe gender homophily (preferences) in collaboration networks...

Questions:

-   Does this question need to ask whether we observe gender homophily in collaboration networks to begin with?

    -   Isn't that the same question as RQ1a then?

-   Does the question need to ask whether we observe gender homophily in collaborations over time?

    -   Did not intent to look at changes over time. this would change things up.

-   Or should it be about the prestige variable in some way? \
    e.g. whether we observe gender homophily within collaboration networks of high prestige scholars and within collaboration networks of lower prestige scholars

    -   but that presupposes that we have pre-established that there are collaboration networks of high-prestige scholars and low prestige scholars

    -   also doesn't this question take away from RQ3?

-   Concern: Overall, I want to keep things simple. Adding a RQ might be needed to help set up the last RQ here but I wonder if there is a way to simplify the project design then?

**RQ3:**

How to does gender homophily affect collaboration differently for collaborations between staff who have published in low vs. high prestige journals?

aka. looking at whole sample: does the gender homophily in collaboration networks look different depending on the scholars' publishing prestige?

# Design

# Project parts

## Research Design

-   Clarify Research Questions

-   Clarify design to answer this question

-   Clarify which data is needed in the design

## Steps to analysis

-   Step 1: Define data

-   Step 2: Create effects structure

-   Step 3: Get initial description

-   Step 4: Specify model

-   Step 5: Estimate model

-   Step 6: Goodness of Fit

## Report writing

-   Introduction

-   Theory

-   Data & Methods

-   Results

-   Discussion & Conclusion

### 2024-10-30 weekbacktrack.Rmd
weekbackontrack2
restructurecommit

@@
 
-# Brainstorm
+# Brainstorm - Getting back on track
 
@@
 This can act as an "accountability-measure" and pushes me to face some struggles head-on, that I would otherwise try to avoid.
-It also creates a predesignated time to discuss the project, which can help me ask questions I would otherwise deem "not important enough to reach out to you".
-\
+It also creates a predesignated time to discuss the project, which can help me ask questions I would otherwise deem "not important enough to reach out to you".\
 I propose that I write you an email about the **current state of affairs on Mondays**, since I cannot work on the project on Tuesday and Wednesday anyways and that gives you some time to reply.
-Please let me know if this is okay for you.
-\
+Please let me know if this is okay for you.\
 In your reply I would appreciate input on how to move on in case I am facing a hurdle that "stalls" the project's progress, and I also welcome redirection if I seem to get "lost in the sauce".
@@
 "I know of this online resource that is about *exactly* this issue.").
+
+Thank you in advance.

### 2024-10-31 clarifyRQsandDesign.Rmd
restructurecommit2
jochemfeedbackrqs

@@
 
+*yes perfect. just a descriptive question at the macro-level. keep it as it is.*
+
 **RQ1b:**
@@
 
-aka. looking at Sociology Department and extent of homphily in there \
+aka. looking at Sociology Department and extent of homphily in there\
 and comparing it with Political Science Department and extent of homophily in there.
+
+*also okay. still a descriptive question at the macro-level. keep it as it is.*
 
@@
     -   Isn't that the same question as RQ1a then?
+    -   *yes and no.
+;-)  this is your hypothesis for your RSiena models.
+whether within a dyad men tend to (or 'prefer') work with men and women with women, (controlled for structural network effects).
+\
+        I hope that you understand that this **dyadic preferences does not necessarily translates to your macro-outcome** (because of all structural effects possibly at play and other covariate-effects).*
 
@@
     -   Did not intent to look at changes over time. this would change things up.
+    -   *okay, simply do not do this then.*
 
--   Or should it be about the prestige variable in some way? \
+-   Or should it be about the prestige variable in some way?\
     e.g. whether we observe gender homophily within collaboration networks of high prestige scholars and within collaboration networks of lower prestige scholars
@@
 
+-   *keep it simple! completely agree.*
+
+    *so far we simply have a descriptive question on gender homophily at the network-level (RQ1) and one at the dyad-level (after controlling for structural network effects and covariate-effects) (RQ2).*
+
 **RQ3:**
@@
 
-# Design
+*Try to reformulate this to your RSiena model and not at your macro-level. I let you struggle a little bit on this last one okay. \
+But the idea is fine; whether prestige (of ego/alter/dyad) impacts gender homophily in some way.*
 
-# Project parts
+*Thus **start with your descriptives and modelling \
+**and rephrase RQ3 later.*
 
-## Research Design
-
--   Clarify Research Questions
-
--   Clarify design to answer this question
-
--   Clarify which data is needed in the design
-
-## Steps to analysis
-
--   Step 1: Define data
-
--   Step 2: Create effects structure
-
--   Step 3: Get initial description
-
--   Step 4: Specify model
-
--   Step 5: Estimate model
-
--   Step 6: Goodness of Fit
-
-## Report writing
-
--   Introduction
-
--   Theory
-
--   Data & Methods
-
--   Results
-
--   Discussion & Conclusion
+*try to **plot asap in the process**. \
+and update plots after descriptives and multivariate analyses along the way. it is an iterative process.*

### 2024-10-31 weekbacktrack.Rmd
panicadded

@@
 Thank you in advance.
+
+## ACTUAL Timeline
+
+deadline: Saturday, 23.11.24
+
++---------------------------------------------------------------------------------------------+------------------------------------------------------------+---------------------------------------------------------------+--------------------------------------------------------------------------------------------+-----------------------------------------------------------------+---------------------------------------------------------------------------+----------------------------------------------------------+
+| Mon                                                                                         | Tue                                                        | Wed                                                           | Thu                                                                                        | Fri                                                             | Sat                                                                       | Sun                                                      |
++:============================================================================================+:===========================================================+:==============================================================+:===========================================================================================+:================================================================+:==========================================================================+:=========================================================+
+| 28\.
+| 29\.
+| 30\.
+| 31\.
+| 01.11.
+| 02\.
+| 03\.
+|
+|                                                                                             |                                                            |                                                               |                                                                                            |                                                                 |                                                                           |                                                          |
+| ![](images/used_arson%20frog.jpg)                                                           | ![](images/used_arson%20frog.jpg){width="952"}             | ![](images/socialnetworking.jpg){width="800"}Clarify RQs [D]\ | ![](images/socialnetworking_meh.jpg){width="800"}Rework schedule [according Jochems input] | ![](images/socialnetworking.jpg){width="800"}\                  | ![](images/socialnetworking_meh.jpg){width="800"}Plotting                 | ![](images/timetopanic.gif){width="800"}[chores at home] |
+|                                                                                             |                                                            | [Asked Jochem for input]                                      |                                                                                            | Clarify [D] & define data [S1]\                                 |                                                                           |                                                          |
+|                                                                                             |                                                            |                                                               | Outline Intro and theory [W]                                                               | & create effects structure [S2]                                 | Revisit RQs [D]                                                           |                                                          |
+|                                                                                             |                                                            |                                                               |                                                                                            |                                                                 |                                                                           |                                                          |
+|                                                                                             |                                                            |                                                               | Clarify [D] & define data [S1]                                                             |                                                                 |                                                                           |                                                          |
++---------------------------------------------------------------------------------------------+------------------------------------------------------------+---------------------------------------------------------------+--------------------------------------------------------------------------------------------+-----------------------------------------------------------------+---------------------------------------------------------------------------+----------------------------------------------------------+
+| 04\.
+| 05\.
+| 06\.
+| 07\.
+| 08\.
+| 09\.
+| 10\.
+|
+|                                                                                             |                                                            |                                                               |                                                                                            |                                                                 |                                                                           |                                                          |
+| ![](images/socialnetworking_meh.jpg){width="800"}\                                          | ![](images/used_arson%20frog.jpg){width="952"}[university] | ![](images/used_arson%20frog.jpg)[university]                 | ![](images/socialnetworking_meh.jpg){width="800"}\                                         | ![](images/socialnetworking.jpg){width="800"}\                  | ![](images/socialnetworking.jpg){width="800"}Specify model [S4]           | ![](images/timetopanic.gif){width="800"}[Grandmas bday]  |
+| Plotting                                                                                    |                                                            |                                                               | Initial description [S3]                                                                   | rewrite intro and Theory [W]                                    |                                                                           |                                                          |
+|                                                                                             |                                                            |                                                               |                                                                                            |                                                                 | Plotting                                                                  |                                                          |
+|                                                                                             |                                                            |                                                               | Revisit RQs                                                                                |                                                                 |                                                                           |                                                          |
++---------------------------------------------------------------------------------------------+------------------------------------------------------------+---------------------------------------------------------------+--------------------------------------------------------------------------------------------+-----------------------------------------------------------------+---------------------------------------------------------------------------+----------------------------------------------------------+
+| 11\.
+| 12\.
+| 13\.
+| 14\.
+| 15\.
+| 16\.
+| 17\.
+|
+|                                                                                             |                                                            |                                                               |                                                                                            |                                                                 |                                                                           |                                                          |
+| ![](images/socialnetworking_meh.jpg){width="800"}                                           | ![](images/used_arson%20frog.jpg){width="952"}[university] | ![](images/used_arson%20frog.jpg)[university]                 | ![](images/socialnetworking.jpg){width="800"}Data & methods part [W]\                      | ![](images/socialnetworking.jpg){width="800"}estimate model     | ![](images/socialnetworking.jpg){width="800"}goodness of fit [S6]         | ![](images/kermit-panic.gif)                             |
+|                                                                                             |                                                            |                                                               |                                                                                            |                                                                 |                                                                           |                                                          |
+| Data & methods part [W]                                                                     |                                                            |                                                               |                                                                                            | Plotting                                                        | Start Results [W]                                                         | [chores at home and university]                          |
++---------------------------------------------------------------------------------------------+------------------------------------------------------------+---------------------------------------------------------------+--------------------------------------------------------------------------------------------+-----------------------------------------------------------------+---------------------------------------------------------------------------+----------------------------------------------------------+
+| 18\.
+| 19\.
+| 20\.
+| 21\.
+| 22\.
+| **23.**                                                                   | 24\.
+|
+|                                                                                             |                                                            |                                                               |                                                                                            |                                                                 |                                                                           |                                                          |
+| ![](images/used_arson frog.jpg)[Research project course starts: little time to work on SNA] | ![](images/used_arson%20frog.jpg){width="952"}[university] | ![](images/used_arson%20frog.jpg)[university]                 | ![](images/socialnetworking_meh.jpg){width="800"}Results [W]                               | ![](images/socialnetworking.jpg){width="800"}Finish Results [W] | ![](images/socialnetworking.jpg){width="800"}Discussion & conclusion [W]  |                                                          |
+|                                                                                             |                                                            |                                                               |                                                                                            |                                                                 |                                                                           |                                                          |
+|                                                                                             |                                                            |                                                               |                                                                                            | Discussion & conclusion [W]                                     | ![](images/kermit-panic.gif){width="500"}Format project website& hand in!
+|                                                          |
++---------------------------------------------------------------------------------------------+------------------------------------------------------------+---------------------------------------------------------------+--------------------------------------------------------------------------------------------+-----------------------------------------------------------------+---------------------------------------------------------------------------+----------------------------------------------------------+
+
+: Days overview
+
+**Legend**
+
+::: columns
+::: {.column width="50%"}
+![social network plot (color) = time for SNA (obvious... or not?)](images/socialnetworking.jpg){alt="social network plot (color) = time for SNA (obvious... or not?)" width="80"}
+
+![social network plot (muted) = not a lot of time for SNA, but SOME](images/socialnetworking_meh.jpg){alt="social network plot (muted) = not a lot of time for SNA, but SOME" width="80"}
+
+![arson = otherwise busy/NO time for SNA](images/used_arson%20frog.jpg){alt="arson = otherwise busy/NO time for SNA" width="80"}
+:::
+
+::: {.column width="50%"}
+![time to panic = chores, admin work, and mental breakdowns/ NO time for SNA](images/timetopanic.gif){width="80"}
+
+![kermit panicking = self-explanatory](images/kermit-panic.gif){width="80"}
+:::
+:::
+
+[D] = task refers to research design
+
+[S#] = task refers to step of analysis
+
+[W] = task refers to writing the report

### 2024-10-31 draftintro.Rmd
theorydraftfirst

--- 2024-09-17 RQdraft2.Rmd
@@
 ---
-title: "RQdraft2"
+title: "Daft-Introduction"
 author: "Verooo"
-date: "2024-09-11"
+date: "2024-10-31"
 output: html_document
+bibliography: references.bib
 ---
@@
 
-# Brainstorm
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = TRUE)
+```
 
-------------------------------------------------------------------------
+# Introduction draft
 
-# Research Questions (old, replace with new ones!)
+Collaboration has become an essential part of modern academia, with scholars increasingly engaging in joint research efforts.
+Co-authorship allows researchers to combine expertise, share resources, and enhance their scholarly output (@Cheong2009).
+However, the dynamics of academic collaboration are not free from social patterns, and gender homophily—where individuals prefer to collaborate with others of the same gender—may play a significant role.
+Understanding how gender affects co-authorship networks, particularly in terms of homophily, can reveal important insights into how academic opportunities and achievements are distributed across genders.
 
-RQ1a: To what extent does gender homophily occur across all co-publications of the staff of the Sociology Department and Political Science Department at Radboud University?
+Previous studies have found that male researchers often prefer collaborating with other men, while female researchers tend to collaborate with other women, albeit to a lesser extent (@Horta2022).
+This raises critical questions about the structure and inclusiveness of academic networks.
+In fields such as Sociology and Political Science, where collaboration is crucial for scholarly success, gender-based patterns could shape the career trajectories of researchers (@Cheong2009).
+Furthermore, as Kwiek and Roszka (@Kwiek2021) point out, all-male authorship is far more prevalent than all-female authorship, indicating that male-dominated collaboration networks may reinforce existing gender imbalances in academia.
 
-RQ1b: To what extent do the two departments differ in their gender homophily?
+Another influential factor in collaboration between scholars seems to be the scholars' 'prestige', namely whether they have published in renowned journals.
+**SOURCE** found that .....PART ABOUT JOURNAL PRESTIGE
 
-RQ2: To what extent does gender homophily in co-publishing influence the prestige of the publication journal?
+In this study, I explore the extent to which gender homophily influences co-authorship networks among faculty in the Sociology and Political Science Departments at Radboud University.
+Specifically, I aim to examine whether there are differences in gender homophily between the two departments, and how homophily patterns vary depending on the prestige of the journals in which researchers publish.
 
-RQ3: To what extent do structural network effects influence the gender homophily of each department?
+This research will contribute to a growing body of literature that seeks to understand the social dynamics underlying academic collaboration.
+By analyzing gender homophily and network structures in two different academic disciplines, this study will shed light on how gender shapes collaboration opportunities and how these dynamics may differ across scholarly fields.
+Moreover, exploring the role of journal prestige in shaping homophily will offer insights into whether gender-based preferences shift in response to career-enhancing factors like publishing in high-prestige journals.
 
-## Horta et al. (2022)
-
--   male researchers preferred to co-publish with other male researchers,
-
--   and female researchers preferred to collaborate with other females.
-
--   researchers of approximately similar ages tended to collaborate more with each other.
-
--   geographical, cultural, & institutional proximity were strongest predictors of collaboration.
-
--   analysis shows that in the social sciences, ACQUIRED attributes (particularly preferences regarding research agendas) take precedence over ASCRIBED attributes (e.g. gender or age)
-
--   Horta et al. (2022) - RQs:
-
-    -
-
-        (1) What homophily preferences determine research collaborations among higher education researchers?
-
-    -
-
-        (2) What are the most powerful homophily indicators in research collaborations in higher education research?
-
-## Kwiek & Roszka (2021)
-
--   Most male scientists collaborate solely with males.
--   Most female scientists, in contrast, do not collaborate with females at all.
--   All-female authorship marginal, all-male authorship pervasive, in all age groups.
--   Articles written in mixed-sex collaboration published in more prestigious journals.
-
-------------------------------------------------------------------------
-
-# References:
-
-Horta, H., Feng, S., & Santos, J.
-M.
-(2022).
-Homophily in higher education research: a perspective based on co-authorships.
-Scientometrics, 127(1), 523–543.
-<https://doi.org/10.1007/s11192-021-04227-z>
-
-Kwiek, M., & Roszka, W. (2021). Gender-based homophily in research: A large-scale study of man-woman collaboration. Journal of Informetrics, 15(3), 101171. <https://doi.org/10.1016/j.joi.2021.101171>
-
-# Data types needed for research
-
-+-----------------------------------+---------------------------------------------------------+--------------------------------------------------------------------------------------------------------+
-| Variable                          | Potential measurement                                   | Notes                                                                                                  |
-+===================================+=========================================================+========================================================================================================+
-| **Actor attributes**              |                                                         |                                                                                                        |
-+-----------------------------------+---------------------------------------------------------+--------------------------------------------------------------------------------------------------------+
-| Name                              | Name from university department website                 | using "read_html()" function                                                                           |
-+-----------------------------------+---------------------------------------------------------+--------------------------------------------------------------------------------------------------------+
-| Gender                            | Google Scholar:\                                        | What about gender neutral names? If we go by this principle, then gender neutral names = non-binary ?? |
-|                                   | Name ➙ Look up in gendered list whether Woman or Man    |                                                                                                        |
-+-----------------------------------+---------------------------------------------------------+--------------------------------------------------------------------------------------------------------+
-|                                   | Linked-in:\                                             | Not everyone puts their pronouns on linkedin\                                                          |
-|                                   | Pronouns                                                | And: not everyone who uses e.g. She/her pronouns is a Woman                                            |
-+-----------------------------------+---------------------------------------------------------+--------------------------------------------------------------------------------------------------------+
-| High prestige publication (prior) | If the author had a publication in a journal that ....\ |                                                                                                        |
-|                                   | before the publication of the paper in question         |                                                                                                        |
-+-----------------------------------+---------------------------------------------------------+--------------------------------------------------------------------------------------------------------+
-| Affiliation                       | Name of university they work at (radboud university)    | Taken from university website about department                                                         |
-+-----------------------------------+---------------------------------------------------------+--------------------------------------------------------------------------------------------------------+
-| **Relational Attributes**         |                                                         |                                                                                                        |
-+-----------------------------------+---------------------------------------------------------+--------------------------------------------------------------------------------------------------------+
-| Initiation of the co-authorship   | First author of paper = initiator                       |                                                                                                        |
-+-----------------------------------+---------------------------------------------------------+--------------------------------------------------------------------------------------------------------+
-| Paper                             | A paper people have co-authorship on                    | How prevent from counting double?\                                                                     |
-|                                   |                                                         | Overall: systematic approach to webscrape?                                                             |
-|                                   | Signifier: DOI?                                         |                                                                                                        |
-+-----------------------------------+---------------------------------------------------------+--------------------------------------------------------------------------------------------------------+
-|                                   |                                                         |                                                                                                        |
-+-----------------------------------+---------------------------------------------------------+--------------------------------------------------------------------------------------------------------+
-
-: Data types
+# References

### 2024-10-31 drafttheory.Rmd
theorydraftfirst

---
title: "Draft-Theory"
author: "Verooo"
date: "2024-10-31"
output: html_document
bibliography: references.bib
---

```{r, globalsettings, echo=FALSE, warning=FALSE, results='hide'}
library(knitr)

knitr::opts_chunk$set(echo = TRUE)
opts_chunk$set(tidy.opts=list(width.cutoff=100),tidy=TRUE, warning = FALSE, message = FALSE,comment = "#>", cache=TRUE, class.source=c("test"), class.output=c("test2"))
options(width = 100)
rgl::setupKnitr()

colorize <- function(x, color) {sprintf("<span style='color: %s;'>%s</span>", color, x) }

```

```{r klippy, echo=FALSE, include=FALSE}
klippy::klippy(position = c('top', 'right'))
#klippy::klippy(color = 'darkred')
#klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done')
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Theory

-   Explanation of gender homophily in scholarship

-   often: Males publishing with males, females publishing with females

-   **Hypothesis 1**: across the collaboration networks of both departments (pol. sci & soc.) scholars prefer to collaborate with same-sex scholars over different-sex scholars (gender homophily is present).

    -   [RQ1: To what extent does gender homophily occur across all co-publications of the staff of the Sociology Department and Political Science Department at Radboud University? descriptive, at network level]\

[**look at descriptives: how many men how many women in each department]**

-   Due to bias that social jobs are more feminine and politics are related to rationality, which is often stereotyped to be masculine: Expect less gender homophily in sociology than in pol.sci. department.

```{=html}
<!-- -->
```
-   Hypothesis 2: between the collaboration networks of both departments (pol. sci & soc.) scholars in the sociology department prefer to collaborate with same-sex scholars less strongly than scholars from the pol. sci. department

    -   [RQ2: To what extent do the two departments differ in their gender homophily?*descriptive, at the dyad-level (after controlling for structural network effects and covariate-effects].*

RQ2 b? Do we observe gender homophily (preferences) in collaboration networks...

Questions:

-   Does this question need to ask whether we observe gender homophily in collaboration networks to begin with?

    -   Isn't that the same question as RQ1a then?

    -   *yes and no. ;-) this is your hypothesis for your RSiena models. whether within a dyad men tend to (or 'prefer') work with men and women with women, (controlled for structural network effects).\
        I hope that you understand that this **dyadic preferences does not necessarily translates to your macro-outcome** (because of all structural effects possibly at play and other covariate-effects).*

Hypothesis 3:

RQ3: How to does gender homophily affect collaboration differently for collaborations between staff who have published in low vs. high prestige journals?

aka. looking at whole sample: does the gender homophily in collaboration networks look different depending on the scholars' publishing prestige?

*Try to **reformulate this to your RSiena model** and not at your macro-level. I let you struggle a little bit on this last one okay.\
But the idea is fine; whether prestige (of ego/alter/dyad) impacts gender homophily in some way.*

# References

### 2024-10-31 drafttheory.Rmd
theoryfirstdraftpush

@@
 
+-   (logical error: yeah but that only makes sense if men are the only ones initiating and breaking ties, right?)
+
 ```{=html}
@@
 ```
--   Hypothesis 2: between the collaboration networks of both departments (pol.
+-   **Hypothesis 2**: between the collaboration networks of both departments (pol.
 sci & soc.) scholars in the sociology department prefer to collaborate with same-sex scholars less strongly than scholars from the pol.
@@
 
-RQ2 b? Do we observe gender homophily (preferences) in collaboration networks...
+```{=html}
+<!-- -->
+```
+-   *hypothesis for your RSiena models: whether within a dyad men tend to (or 'prefer') work with men and women with women, (controlled for structural network effects).*
 
-Questions:
+    -   **confusion: where would the comparison between depatments be here? this wold fit rq one more, but that one is supposed to be on the network level but this is about dyads...**
 
--   Does this question need to ask whether we observe gender homophily in collaboration networks to begin with?
+-
 
-    -   Isn't that the same question as RQ1a then?
+```{=html}
+<!-- -->
+```
+-   **Hypothesis 3:** On the ego level, the preference of *men to work with men and women with women, (controlled for structural network effects), is less influential in the choice to collaborate if the alter is someone who published in a high-prestige journal.*
 
-    -   *yes and no.
-;-) this is your hypothesis for your RSiena models.
-whether within a dyad men tend to (or 'prefer') work with men and women with women, (controlled for structural network effects).\
-        I hope that you understand that this **dyadic preferences does not necessarily translates to your macro-outcome** (because of all structural effects possibly at play and other covariate-effects).*
-
-Hypothesis 3:
-
-RQ3: How to does gender homophily affect collaboration differently for collaborations between staff who have published in low vs. high prestige journals?
-
-aka. looking at whole sample: does the gender homophily in collaboration networks look different depending on the scholars' publishing prestige?
-
-*Try to **reformulate this to your RSiena model** and not at your macro-level. I let you struggle a little bit on this last one okay.\
-But the idea is fine; whether prestige (of ego/alter/dyad) impacts gender homophily in some way.*
+    -   [RQ3: How to does gender homophily affect collaboration differently for collaborations between staff who have published in low vs.
+high prestige journals?
+ego-level] *idea: whether prestige (of ego/alter/dyad) impacts gender homophily in some way.*
 

### 2024-11-01 1definedata.Rmd
definedatafirstpush

---
title: "1-Define Data"
author: "Verooo"
date: "2024-11-01"
output: html_document
---

```{r, globalsettings, echo=FALSE, warning=FALSE, results='hide'}
library(knitr)

knitr::opts_chunk$set(echo = TRUE)
opts_chunk$set(tidy.opts=list(width.cutoff=100),tidy=TRUE, warning = FALSE, message = FALSE,comment = "#>", cache=TRUE, class.source=c("test"), class.output=c("test2"))
options(width = 100)
rgl::setupKnitr()

colorize <- function(x, color) {sprintf("<span style='color: %s;'>%s</span>", color, x) }

```

```{r klippy, echo=FALSE, include=FALSE}
klippy::klippy(position = c('top', 'right'))
klippy::klippy(color = 'darkred')
klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done')
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

[**Defining Data**]{.underline}

# Before the start

## Clean workspace

```{r}
# start with clean workspace
rm(list = ls())

```

## Packages

```{r}
# install.packages('tidyverse')
require(tidyverse)

# install an old version of RSiena including sienaRI
# remove.packages("RSiena") #use this to remove the current version of RSiena
#devtools::install_version("RSiena", version = "1.3.14", repos = "http://cran.us.r-project.org") # This installs an older version

# Run R as administrator when you install the older version!!

# You should end up with version 1.3.14 loaded in instead of 1.4.7, 
# but then make sure there isn't a install.packages("RSiena") function running somewhere, because then it will reinstall the newest version

```

## Functions

### Question

**HOW do I get the discipline of political science in there too?**

**How can I find out what the name for the discipline of political science in the original data frame (e.g. whether it is called polsci, political science, or politicalscience)?**

**I don't know how to view the data set BEFORE we include only those scholars that have discipline = sociology. I cannot view the data**

I tried removing the discipline = "sociology" part in the fcolnet and all following functions that select data BUT SINCE 'discipline' is also relevant in the rest of the functions' code, it does not end up doing what I hoped (having a dataset with scholars of no specific discipline because then I could hopefully check how the department is named in the data and then find out how to add that to the data set initially).

```{r}

fpackage.check <- function(packages) {
    lapply(packages, FUN = function(x) {
        if (!require(x, character.only = TRUE)) {
            install.packages(x, dependencies = TRUE)
            library(x, character.only = TRUE)
        }
    })
}

fsave <- function(x, file = NULL, location = "./data/processed/") {
    ifelse(!dir.exists("data"), dir.create("data"), FALSE)
    ifelse(!dir.exists("data/processed"), dir.create("data/processed"), FALSE)
    if (is.null(file))
        file = deparse(substitute(x))
    datename <- substr(gsub("[:-]", "", Sys.time()), 1, 8)
    totalname <- paste(location, file, "_", datename, ".rda", sep = "")
    save(x, file = totalname)  #need to fix if file is reloaded as input name, not as x. 
}

fload <- function(filename) {
    load(filename)
    get(ls()[ls() != "filename"])
}

fshowdf <- function(x, ...) {
    knitr::kable(x, digits = 2, "html", ...) %>%
        kableExtra::kable_styling(bootstrap_options = c("striped", "hover")) %>%
        kableExtra::scroll_box(width = "100%", height = "300px")
}

# before my edits:
# f_pubnets <- function(df_scholars = df, list_publications = publications, discip = "sociology", affiliation = "RU",
#     wave = list(wave1 = c(2018, 2019, 2020), wave2 = c(2021, 2022, 2023)))

#after taking out discipline= "sociology" in this first part    
f_pubnets <- function(df_scholars = df, list_publications = publications, affiliation = "RU",
    wave = list(wave1 = c(2018, 2019, 2020), wave2 = c(2021, 2022, 2023))) {

    publications <- list_publications %>%
        bind_rows() %>%
        distinct(title, .keep_all = TRUE)

    df_scholars %>%
        filter(affil1 == affiliation | affil2 == affiliation) %>%
        filter(discipline == discip) -> df_sel

    networklist <- list()
    for (wave in 1:length(wave)) {
        networklist[[wave]] <- matrix(0, nrow = nrow(df_sel), ncol = nrow(df_sel))
    }

    publicationlist <- list()
    for (wave in 1:length(wave)) {
        publicationlist[[wave]] <- publications %>%
            filter(gs_id %in% df_sel$gs_id) %>%
            filter(year %in% wave[[wave]]) %>%
            select(author) %>%
            lapply(str_split, pattern = ",")
    }

    publicationlist2 <- list()
    for (wave in 1:length(wave)) {
        publicationlist2[[wave]] <- publicationlist[[wave]]$author %>%
            # lowercase
        lapply(tolower) %>%
            # Removing diacritics
        lapply(stri_trans_general, id = "latin-ascii") %>%
            # only last name
        lapply(word, start = -1, sep = " ") %>%
            # only last last name
        lapply(word, start = -1, sep = "-")
    }

    for (wave in 1:length(wave)) {
        # let us remove all publications with only one author
        remove <- which(sapply(publicationlist2[[wave]], FUN = function(x) length(x) == 1) == TRUE)
        publicationlist2[[wave]] <- publicationlist2[[wave]][-remove]
    }

    for (wave in 1:length(wave)) {
        pubs <- publicationlist2[[wave]]
        for (ego in 1:nrow(df_sel)) {
            # which ego?
            lastname_ego <- df_sel$lastname[ego]
            # for all publications
            for (pub in 1:length(pubs)) {
                # only continue if ego is author of pub
                if (lastname_ego %in% pubs[[pub]]) {
                  aut_pot <- which.max(pubs[[pub]] %in% lastname_ego)
                  # only continue if ego is first author of pub
                  if (aut_pot == 1) {
                    # check all alters/co-authors
                    for (alter in 1:nrow(df_sel)) {
                      # which alter
                      lastname_alter <- df_sel$lastname[alter]
                      if (lastname_alter %in% pubs[[pub]]) {
                        networklist[[wave]][ego, alter] <- networklist[[wave]][ego, alter] + 1
                      }
                    }
                  }
                }
            }
        }
    }
    return(list(df = df_sel, network = networklist))
}
```

```{r}
view(f_pubnets)
```

## more functions

```{r}

#prior to my edits:
# fcolnet <- function(data = scholars, university = "RU", discipline = "sociology", wave = list(c(2019, 2023)), type = c("first"))

#after taking out discipline= "sociology" in the first part 
fcolnet <- function(data = scholars, university = "RU", wave = list(c(2019, 2023)), type = c("first")) {

    # step 1
    demographics <- do.call(rbind.data.frame, data$demographics)
    demographics <- demographics %>%
        mutate(Universiteit1.22 = replace(Universiteit1.22, is.na(Universiteit1.22), ""), Universiteit2.22 = replace(Universiteit2.22,
            is.na(Universiteit2.22), ""), Universiteit1.24 = replace(Universiteit1.24, is.na(Universiteit1.24),
            ""), Universiteit2.24 = replace(Universiteit2.24, is.na(Universiteit2.24), ""), discipline.22 = replace(discipline.22,
            is.na(discipline.22), ""), discipline.24 = replace(discipline.24, is.na(discipline.24), ""))

    sample <- which((demographics$Universiteit1.22 %in% university | demographics$Universiteit2.22 %in%
        university | demographics$Universiteit1.24 %in% university | demographics$Universiteit2.24 %in%
        university) & (demographics$discipline.22 %in% discipline | demographics$discipline.24 %in% discipline))

    demographics_soc <- demographics[sample, ]
    scholars_sel <- lapply(scholars, "[", sample)

    # step 2
    ids <- demographics_soc$au_id
    nwave <- length(wave)
    nets <- array(0, dim = c(nwave, length(ids), length(ids)), dimnames = list(wave = 1:nwave, ids,
        ids))
    dimnames(nets)

    # step 3
    df_works <- tibble(works_id = unlist(lapply(scholars_sel$work, function(l) l$id)), works_author = unlist(lapply(scholars_sel$work,
        function(l) l$author), recursive = FALSE), works_year = unlist(lapply(scholars_sel$work, function(l) l$publication_year),
        recursive = FALSE))

    df_works <- df_works[!duplicated(df_works), ]

    # step 4
    if (type == "first") {
        for (j in 1:nwave) {
            df_works_w <- df_works[df_works$works_year >= wave[[j]][1] & df_works$works_year <= wave[[j]][2],
                ]
            for (i in 1:nrow(df_works_w)) {
                ego <- df_works_w$works_author[i][[1]]$au_id[1]
                alters <- df_works_w$works_author[i][[1]]$au_id[-1]
                if (sum(ids %in% ego) > 0 & sum(ids %in% alters) > 0) {
                  nets[j, which(ids %in% ego), which(ids %in% alters)] <- 1
                }
            }
        }
    }

    if (type == "last") {
        for (j in 1:nwave) {
            df_works_w <- df_works[df_works$works_year >= wave[[j]][1] & df_works$works_year <= wave[[j]][2],
                ]
            for (i in 1:nrow(df_works_w)) {
                ego <- rev(df_works_w$works_author[i][[1]]$au_id)[1]
                alters <- rev(df_works_w$works_author[i][[1]]$au_id)[-1]
                if (sum(ids %in% ego) > 0 & sum(ids %in% alters) > 0) {
                  nets[j, which(ids %in% ego), which(ids %in% alters)] <- 1
                }
            }
        }
    }

    if (type == "all") {
        for (j in 1:nwave) {
            df_works_w <- df_works[df_works$works_year >= wave[[j]][1] & df_works$works_year <= wave[[j]][2],
                ]
            for (i in 1:nrow(df_works_w)) {
                egos <- df_works_w$works_author[i][[1]]$au_id
                if (sum(ids %in% egos) > 0) {
                  nets[j, which(ids %in% egos), which(ids %in% egos)] <- 1
                }
            }
        }
    }
    output <- list()
    output$data <- scholars_sel
    output$nets <- nets
    return(output)

}

```

## load data

```{r}
scholars <- fload("./data/processed/scholars_20240924.rda")

# save the output of your function

# before my edits:
# test <- fcolnet(data = scholars, university = "RU", discipline = "sociology", wave = list(c(2019, 2023)), type = c("first"))

# after taking discipline= "sociology" out
# test <- fcolnet(data = scholars, university = "RU", wave = list(c(2019, 2023)), type = c("first"))

# here is where the error occurs due to taking out the discipline = "sociology" in multiple prior parts of the code 
```

------------------------------------------------------------------------

# Define Data

```{r}
wave <- test$nets[1, , ]

# let us put the diagonal to zero
diag(wave) <- 0
# we want a binary tie (not a weighted tie)
wave[wave > 1] <- 1

# put the nets in an array
net_soc_array <- array(data = c(wave), dim = c(dim(wave), 2)) 
str(net_soc_array)  #now we basically restructured this 
# output: num [1:50, 1:50, 1:2] 0 0 0 0 0 0 0 0 0 0

# since I only take one wave should I replace the 2 with a 1 here? 
net_soc_array1 <- array(data = c(wave), dim = c(dim(wave), 1)) 
str(net_soc_array1)  #now we basically restructured this 
# output: num [1:50, 1:50, 1] 0 0 0 0 0 0 0 0 0 0
```

### **QUESTION:**

**What's the difference between putting the 2 and the 1 at the dimensions. I feel like one is appropriate since I am only looking at one wave, not two, but since the output is among the 'values' not 'data', I cannot view the variable net_soc_array(1) nor "visualize" what that means in terms of its structure. I don't really know what the difference would be between the 1:2 and the 1 in the outputs, structurally.**

## Examine structure

```{r}
dim(test$nets)
```

not using net_soc_array for now since I am unsure about its use due to question above

```{r}
# dependent
    # not using net_soc_array for now since I am unsure about its use due to question above
# net <- sienaDependent(net_soc_array)

# dependent 
 nets <- test$nets

df_ego_demo <- test$data$demographics
df_ego_oa <- test$data$scholars_oa
df_ego_works <- test$data$works

# DEMO
  str(df_ego_demo, 1)

  df_ego_demo <- do.call(rbind.data.frame, df_ego_demo)
  df_ego_demo[[1]]

# OA
  #str(df_ego_oa, 1)
  df_ego_oa[[1]]
  df_ego_oa <- do.call(rbind.data.frame, df_ego_oa)

# --> EGO DATAFRAME with demo and oa 
  ?join.data.frame
  df_ego <- left_join(df_ego_demo, df_ego_oa, by = join_by(au_id == id))

  rownames(nets[1,,]) == df_ego$au_id # checking if the author id's are the same as in df_ego in nets dataframe 
  # --> yes, the correct ones!!!

df_ego_works[[1]]$author 
#authors of all the works that first scholar (here: Ana Macanovic) is part of

```

## Gender

```{r}
df_ego$Naam # list of all names

df_ego$gender <- c(0,1,0,1,0,0,1,1,0,0,
                   0,1,1,0,1,0,1,1,1,1,
                   0,1,1,0,1,1,0,1,0,1,
                   0,1,0,0,0,0,0,0,1,0,
                   0,1,1,1,0,1,0,1,0,0) 
# manually filled in gender 0 = woman, 1 = man, based on majority given in NL voornamen bank

# check if it went smoothly 
view(df_ego[c('Naam', 'gender', 'au_id')])

#covariate 
# gender <- coCovar(df_ego$gender)
```

## H-index

Inspired by Lucan's code:

```{r, include=FALSE}
# Add h-index and i10-index columns to df_ego
df_ego <- df_ego %>%
  mutate(h_index = NA_real_, i10_index = NA_real_)

# Get H-index and i10-index 
get_openalex_metrics <- function(openalex_id) {
  url <- paste0("https://api.openalex.org/authors/", openalex_id)
  author_data <- tryCatch({
    jsonlite::fromJSON(url)
  }, error = function(e) {
    message(paste("Error fetching data for OpenAlex ID:", openalex_id))
    return(NULL)
  })

  if (!is.null(author_data)) {
    h_index <- author_data$summary_stats$h_index
    i10_index <- author_data$summary_stats$i10_index
    works_count <- author_data$works_count
    cited_by_count <- author_data$cited_by_count
    return(list(h_index = h_index, i10_index = i10_index, works_count = works_count, cited_by_count = cited_by_count))
  } else {
    return(list(h_index = NA, i10_index = NA, works_count = NA, cited_by_count = NA))
  }
}

# Loop for each scholar 
for (i in 1:nrow(df_ego)) {
  openalex_id <- df_ego$au_id[i]  # assuming au_id is the OpenAlex ID in df_ego
  metrics <- get_openalex_metrics(openalex_id)
  df_ego$h_index[i] <- metrics$h_index
  df_ego$i10_index[i] <- metrics$i10_index
  df_ego$works_count[i] <- metrics$works_count
  df_ego$cited_by_count[i] <- metrics$cited_by_count
}

# View updated df_ego with h-index and i10-index
view(df_ego[c('au_id','Naam','gender','h_index','i10_index')])

#covariate 
# h_index <- coCovar(df_ego$h_index)
```

```{r}

view(data('discipline'))
```

### 2024-11-01 clarifyRQsandDesign.Rmd
definedatafirstpush

@@
 ;-)  this is your hypothesis for your RSiena models.
-whether within a dyad men tend to (or 'prefer') work with men and women with women, (controlled for structural network effects).
-\
+whether within a dyad men tend to (or 'prefer') work with men and women with women, (controlled for structural network effects).\
         I hope that you understand that this **dyadic preferences does not necessarily translates to your macro-outcome** (because of all structural effects possibly at play and other covariate-effects).*
@@
 
-*Try to reformulate this to your RSiena model and not at your macro-level. I let you struggle a little bit on this last one okay. \
+*Try to reformulate this to your RSiena model and not at your macro-level. I let you struggle a little bit on this last one okay.\
 But the idea is fine; whether prestige (of ego/alter/dyad) impacts gender homophily in some way.*
 
-*Thus **start with your descriptives and modelling \
+*Thus **start with your descriptives and modelling\
 **and rephrase RQ3 later.*
 
-*try to **plot asap in the process**. \
+*try to **plot asap in the process**.\
 and update plots after descriptives and multivariate analyses along the way. it is an iterative process.*

### 2024-11-01 draftdata.Rmd
definedatafirstpush

--- 2024-10-31 drafttheory.Rmd
@@
 ---
-title: "Draft-Theory"
+title: "draft-data"
 author: "Verooo"
-date: "2024-10-31"
+date: "2024-11-01"
 output: html_document
-bibliography: references.bib
 ---
@@
 knitr::opts_chunk$set(echo = TRUE)
+
 ```
 
-# Theory
-
--   Explanation of gender homophily in scholarship
-
--   often: Males publishing with males, females publishing with females
-
--   **Hypothesis 1**: across the collaboration networks of both departments (pol.
-sci & soc.) scholars prefer to collaborate with same-sex scholars over different-sex scholars (gender homophily is present).
-
-    -   [RQ1: To what extent does gender homophily occur across all co-publications of the staff of the Sociology Department and Political Science Department at Radboud University?
-descriptive, at network level]\
-
-[**look at descriptives: how many men how many women in each department]**
-
--   Due to bias that social jobs are more feminine and politics are related to rationality, which is often stereotyped to be masculine: Expect less gender homophily in sociology than in pol.sci.
-department.
-
--   (logical error: yeah but that only makes sense if men are the only ones initiating and breaking ties, right?)
-
-```{=html}
-<!-- -->
-```
--   **Hypothesis 2**: between the collaboration networks of both departments (pol.
-sci & soc.) scholars in the sociology department prefer to collaborate with same-sex scholars less strongly than scholars from the pol.
-sci.
-department
-
-    -   [RQ2: To what extent do the two departments differ in their gender homophily?*descriptive, at the dyad-level (after controlling for structural network effects and covariate-effects].*
-
-```{=html}
-<!-- -->
-```
--   *hypothesis for your RSiena models: whether within a dyad men tend to (or 'prefer') work with men and women with women, (controlled for structural network effects).*
-
-    -   **confusion: where would the comparison between depatments be here? this wold fit rq one more, but that one is supposed to be on the network level but this is about dyads...**
-
--
-
-```{=html}
-<!-- -->
-```
--   **Hypothesis 3:** On the ego level, the preference of *men to work with men and women with women, (controlled for structural network effects), is less influential in the choice to collaborate if the alter is someone who published in a high-prestige journal.*
-
-    -   [RQ3: How to does gender homophily affect collaboration differently for collaborations between staff who have published in low vs.
-high prestige journals?
-ego-level] *idea: whether prestige (of ego/alter/dyad) impacts gender homophily in some way.*
-
-# References
+# Data Draft

### 2024-11-01 draftintro.Rmd
definedatafirstpush

@@
 output: html_document
+
+citation_package: apacite
 bibliography: references.bib
+biblio-style: apacite
+natbiboptions: round
 ---
@@
 klippy::klippy(position = c('top', 'right'))
-#klippy::klippy(color = 'darkred')
-#klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done')
+klippy::klippy(color = 'darkred')
+klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done')
 ```

### 2024-11-01 drafttheory.Rmd
definedatafirstpush

@@
 knitr::opts_chunk$set(echo = TRUE)
+
 ```
 
-# Theory
+# Theory Draft
 
@@
 
--   often: Males publishing with males, females publishing with females
+-   often: Males publishing with males, females publishing with females (@Horta2022)
 
@@
 
-[**look at descriptives: how many men how many women in each department]**
+[\*\*look at descriptives: how many men how many women in each department]\*\*
 
@@
 
-```{=html}
 <!-- -->
-```
+
 -   **Hypothesis 2**: between the collaboration networks of both departments (pol.
@@
 
-    -   [RQ2: To what extent do the two departments differ in their gender homophily?*descriptive, at the dyad-level (after controlling for structural network effects and covariate-effects].*
+    -   [RQ2: To what extent do the two departments differ in their gender homophily?\*descriptive, at the dyad-level (after controlling for structural network effects and covariate-effects].\*
 
-```{=html}
 <!-- -->
-```
+
 -   *hypothesis for your RSiena models: whether within a dyad men tend to (or 'prefer') work with men and women with women, (controlled for structural network effects).*
@@
 
--
+<!-- -->
 
-```{=html}
-<!-- -->
-```
 -   **Hypothesis 3:** On the ego level, the preference of *men to work with men and women with women, (controlled for structural network effects), is less influential in the choice to collaborate if the alter is someone who published in a high-prestige journal.*
 
-    -   [RQ3: How to does gender homophily affect collaboration differently for collaborations between staff who have published in low vs.
+    -   [RQ3: How does gender homophily in collaborations between staff differ depending on scholars having published in low vs.
 high prestige journals?

### 2024-11-01 weekbacktrack.Rmd
theorydraftfirst
definedatafirstpush

--- 2024-10-30 weekbacktrack.Rmd
@@
 
-+--------------------------------------------------------------------+------------------------------------------------+---------------------------------------------------------------+-----------------------------------------------------------------------+--------------------------------------------------------------------------+-----------------------------------------------------------------------------------------+------------------------------------------+
++--------------------------------------------------------------------+------------------------------------------------+---------------------------------------------------------------+------------------------------------------------------------------------+--------------------------------------------------------------------------+-----------------------------------------------------------------------------------------+------------------------------------------+
 | Mon                                                                | Tue                                            | Wed                                                           | Thu                                                                    | Fri                                                                      | Sat                                                                                     | Sun                                      |
-+:===================================================================+:===============================================+:==============================================================+:======================================================================+:=========================================================================+:========================================================================================+:=========================================+
++:===================================================================+:===============================================+:==============================================================+:=======================================================================+:=========================================================================+:========================================================================================+:=========================================+
 | 28\.
@@
 |                                                                    |                                                |                                                               |                                                                        |                                                                          |                                                                                         |                                          |
-| ![](images/used_arson%20frog.jpg)                                  | ![](images/used_arson%20frog.jpg){width="952"} | ![](images/socialnetworking.jpg){width="800"}Clarify RQs [D]\ | ![](images/socialnetworking_meh.jpg){width="800"}Intro and theory [W] | ![](images/socialnetworking.jpg){width="800"}Intro and theory [W]\       | ![](images/socialnetworking_meh.jpg){width="800"}Define data [S1]                       | ![](images/Trixie-joke.jpg){width="800"} |
+| ![](images/used_arson%20frog.jpg)                                  | ![](images/used_arson%20frog.jpg){width="952"} | ![](images/socialnetworking.jpg){width="800"}Clarify RQs [D]\ | ![](images/socialnetworking_meh.jpg){width="800"}Intro and theory [W]\ | ![](images/socialnetworking.jpg){width="800"}Intro and theory [W]\       | ![](images/socialnetworking_meh.jpg){width="800"}Define data [S1]                       | ![](images/Trixie-joke.jpg){width="800"} |
 |                                                                    |                                                | & Clarify design [D]                                          |                                                                        | Clarify [D] & define data [S1]                                           |                                                                                         |                                          |
-+--------------------------------------------------------------------+------------------------------------------------+---------------------------------------------------------------+-----------------------------------------------------------------------+--------------------------------------------------------------------------+-----------------------------------------------------------------------------------------+------------------------------------------+
++--------------------------------------------------------------------+------------------------------------------------+---------------------------------------------------------------+------------------------------------------------------------------------+--------------------------------------------------------------------------+-----------------------------------------------------------------------------------------+------------------------------------------+
 | 04\.
@@
 | & create effects structure [S2]                                    |                                                |                                                               | Create effects structure [S2]\                                         | & plotting                                                               |                                                                                         |                                          |
-+--------------------------------------------------------------------+------------------------------------------------+---------------------------------------------------------------+-----------------------------------------------------------------------+--------------------------------------------------------------------------+-----------------------------------------------------------------------------------------+------------------------------------------+
++--------------------------------------------------------------------+------------------------------------------------+---------------------------------------------------------------+------------------------------------------------------------------------+--------------------------------------------------------------------------+-----------------------------------------------------------------------------------------+------------------------------------------+
 | 11\.
@@
 |                                                                    |                                                |                                                               | Data & methods part [W]                                                |                                                                          |                                                                                         |                                          |
-+--------------------------------------------------------------------+------------------------------------------------+---------------------------------------------------------------+-----------------------------------------------------------------------+--------------------------------------------------------------------------+-----------------------------------------------------------------------------------------+------------------------------------------+
++--------------------------------------------------------------------+------------------------------------------------+---------------------------------------------------------------+------------------------------------------------------------------------+--------------------------------------------------------------------------+-----------------------------------------------------------------------------------------+------------------------------------------+
 | 18\.
@@
 | ![](images/Trixie-joke.jpg){width="800"} |
-+--------------------------------------------------------------------+------------------------------------------------+---------------------------------------------------------------+-----------------------------------------------------------------------+--------------------------------------------------------------------------+-----------------------------------------------------------------------------------------+------------------------------------------+
++--------------------------------------------------------------------+------------------------------------------------+---------------------------------------------------------------+------------------------------------------------------------------------+--------------------------------------------------------------------------+-----------------------------------------------------------------------------------------+------------------------------------------+
 
@@
 Thank you in advance.
+
+## ACTUAL Timeline
+
+deadline: Saturday, 23.11.24
+
++-----------------------------------------------------------------------------------------------+------------------------------------------------------------+---------------------------------------------------------------+--------------------------------------------------------------------------------------------+-----------------------------------------------------------------+---------------------------------------------------------------------------+----------------------------------------------------------+
+| Mon                                                                                           | Tue                                                        | Wed                                                           | Thu                                                                                        | Fri                                                             | Sat                                                                       | Sun                                                      |
++:==============================================================================================+:===========================================================+:==============================================================+:===========================================================================================+:================================================================+:==========================================================================+:=========================================================+
+| 28\.
+| 29\.
+| 30\.
+| 31\.
+| 01.11.
+| 02\.
+| 03\.
+|
+|                                                                                               |                                                            |                                                               |                                                                                            |                                                                 |                                                                           |                                                          |
+| ![](images/used_arson%20frog.jpg)                                                             | ![](images/used_arson%20frog.jpg){width="952"}             | ![](images/socialnetworking.jpg){width="800"}Clarify RQs [D]\ | ![](images/socialnetworking_meh.jpg){width="800"}Rework schedule [according Jochems input] | ![](images/socialnetworking.jpg){width="800"}\                  | ![](images/socialnetworking_meh.jpg){width="800"}Plotting                 | ![](images/timetopanic.gif){width="800"}[chores at home] |
+|                                                                                               |                                                            | [Asked Jochem for input]                                      |                                                                                            | hyp.
+3                                                          |                                                                           |                                                          |
+|                                                                                               |                                                            |                                                               | Outline Intro and theory [W]\                                                              |                                                                 | Revisit RQs [D]                                                           |                                                          |
+|                                                                                               |                                                            |                                                               | (missing H3 still)                                                                         | Clarify [D]\                                                    |                                                                           |                                                          |
+|                                                                                               |                                                            |                                                               |                                                                                            | & define data [S1]\                                             |                                                                           |                                                          |
+|                                                                                               |                                                            |                                                               |                                                                                            | & create effects structure [S2]                                 |                                                                           |                                                          |
++-----------------------------------------------------------------------------------------------+------------------------------------------------------------+---------------------------------------------------------------+--------------------------------------------------------------------------------------------+-----------------------------------------------------------------+---------------------------------------------------------------------------+----------------------------------------------------------+
+| 04\.
+| 05\.
+| 06\.
+| 07\.
+| 08\.
+| 09\.
+| 10\.
+|
+|                                                                                               |                                                            |                                                               |                                                                                            |                                                                 |                                                                           |                                                          |
+| ![](images/socialnetworking_meh.jpg){width="800"}\                                            | ![](images/used_arson%20frog.jpg){width="952"}[university] | ![](images/used_arson%20frog.jpg)[university]                 | ![](images/socialnetworking_meh.jpg){width="800"}\                                         | ![](images/socialnetworking.jpg){width="800"}\                  | ![](images/socialnetworking.jpg){width="800"}Specify model [S4]           | ![](images/timetopanic.gif){width="800"}[Grandmas bday]  |
+| Plotting                                                                                      |                                                            |                                                               | Initial description [S3]                                                                   | rewrite intro and Theory [W]                                    |                                                                           |                                                          |
+|                                                                                               |                                                            |                                                               |                                                                                            |                                                                 | Plotting                                                                  |                                                          |
+|                                                                                               |                                                            |                                                               | Revisit RQs                                                                                |                                                                 |                                                                           |                                                          |
++-----------------------------------------------------------------------------------------------+------------------------------------------------------------+---------------------------------------------------------------+--------------------------------------------------------------------------------------------+-----------------------------------------------------------------+---------------------------------------------------------------------------+----------------------------------------------------------+
+| 11\.
+| 12\.
+| 13\.
+| 14\.
+| 15\.
+| 16\.
+| 17\.
+|
+|                                                                                               |                                                            |                                                               |                                                                                            |                                                                 |                                                                           |                                                          |
+| ![](images/socialnetworking_meh.jpg){width="800"}                                             | ![](images/used_arson%20frog.jpg){width="952"}[university] | ![](images/used_arson%20frog.jpg)[university]                 | ![](images/socialnetworking.jpg){width="800"}Data & methods part [W]\                      | ![](images/socialnetworking.jpg){width="800"}estimate model     | ![](images/socialnetworking.jpg){width="800"}goodness of fit [S6]         | ![](images/kermit-panic.gif)                             |
+|                                                                                               |                                                            |                                                               |                                                                                            |                                                                 |                                                                           |                                                          |
+| Data & methods part [W]                                                                       |                                                            |                                                               |                                                                                            | Plotting                                                        | Start Results [W]                                                         | [chores at home and university]                          |
++-----------------------------------------------------------------------------------------------+------------------------------------------------------------+---------------------------------------------------------------+--------------------------------------------------------------------------------------------+-----------------------------------------------------------------+---------------------------------------------------------------------------+----------------------------------------------------------+
+| 18\.
+| 19\.
+| 20\.
+| 21\.
+| 22\.
+| **23.**                                                                   | 24\.
+|
+|                                                                                               |                                                            |                                                               |                                                                                            |                                                                 |                                                                           |                                                          |
+| ![](images/used_arson%20frog.jpg)[Research project course starts: little time to work on SNA] | ![](images/used_arson%20frog.jpg){width="952"}[university] | ![](images/used_arson%20frog.jpg)[university]                 | ![](images/socialnetworking_meh.jpg){width="800"}Results [W]                               | ![](images/socialnetworking.jpg){width="800"}Finish Results [W] | ![](images/socialnetworking.jpg){width="800"}Discussion & conclusion [W]  |                                                          |
+|                                                                                               |                                                            |                                                               |                                                                                            |                                                                 |                                                                           |                                                          |
+|                                                                                               |                                                            |                                                               |                                                                                            | Discussion & conclusion [W]                                     | ![](images/kermit-panic.gif){width="500"}Format project website& hand in!
+|                                                          |
++-----------------------------------------------------------------------------------------------+------------------------------------------------------------+---------------------------------------------------------------+--------------------------------------------------------------------------------------------+-----------------------------------------------------------------+---------------------------------------------------------------------------+----------------------------------------------------------+
+
+: Days overview
+
+**Legend**
+
+::: columns
+::: {.column width="50%"}
+![social network plot (color) = time for SNA (obvious... or not?)](images/socialnetworking.jpg){width="80"}
+
+![social network plot (muted) = not a lot of time for SNA, but SOME](images/socialnetworking_meh.jpg){width="80"}
+
+![arson = otherwise busy/NO time for SNA](images/used_arson%20frog.jpg){width="80"}
+:::
+
+::: {.column width="50%"}
+![time to panic = chores, admin work, and mental breakdowns/ NO time for SNA](images/timetopanic.gif){width="80"}
+
+![kermit panicking = self-explanatory](images/kermit-panic.gif){width="80"}
+:::
+:::
+
+[D] = task refers to research design
+
+[S#] = task refers to step of analysis
+
+[W] = task refers to writing the report

### 2024-11-01 1definedata.Rmd
definedatapush2

@@
 
-I tried removing the discipline = "sociology" part in the fcolnet and all following functions that select data BUT SINCE 'discipline' is also relevant in the rest of the functions' code, it does not end up doing what I hoped (having a dataset with scholars of no specific discipline because then I could hopefully check how the department is named in the data and then find out how to add that to the data set initially).
+I tried removing the discipline = "sociology" part in the f_pubnets, fcolnet and all following functions that select data BUT SINCE 'discipline' is also relevant in the rest of the functions' code, it does not end up doing what I hoped (having a dataset with scholars of no specific discipline because then I could hopefully check how the department is named in the data and then find out how to add that to the data set initially).
 
@@
 
-#after taking out discipline= "sociology" in this first part    
+#after taking out discip = "sociology" in this first part    
 f_pubnets <- function(df_scholars = df, list_publications = publications, affiliation = "RU",
@@
 
+## My data
+
 not using net_soc_array for now since I am unsure about its use due to question above
@@
 # dependent
-    # not using net_soc_array for now since I am unsure about its use due to question above
 # net <- sienaDependent(net_soc_array)
@@
 
-```{r, include=FALSE}
+```{r}
 # Add h-index and i10-index columns to df_ego
@@
 ```
-
-```{r}
-
-view(data('discipline'))
-```

### 2024-11-03 1definedata.Rmd
defindedatapolsci

@@
 # install an old version of RSiena including sienaRI
-# remove.packages("RSiena") #use this to remove the current version of RSiena
-#devtools::install_version("RSiena", version = "1.3.14", repos = "http://cran.us.r-project.org") # This installs an older version
+#remove.packages("RSiena") #use this to remove the current version of RSiena
+#devtools::install_version("RSiena", version = "1.3.14", repos = "C:/Users/Vero/OneDrive - Radboud Universiteit/Documents/GitHub/labjournal") # This installs an older version
 
@@
 
+# require(RSiena)
+# require(RsienaTwoStep)
+
 ```
+
+I do not seem to be able to call on the package RSiena, nor can I reinstall it.... I know programming never works on the first try but... goddamnit, why not even after 15?
 
@@
 ```{r}
-
 fpackage.check <- function(packages) {
@@
 
-# before my edits:
-# f_pubnets <- function(df_scholars = df, list_publications = publications, discip = "sociology", affiliation = "RU",
-#     wave = list(wave1 = c(2018, 2019, 2020), wave2 = c(2021, 2022, 2023)))
+# this is the most important one. We created it in the previous script
 
-#after taking out discip = "sociology" in this first part    
-f_pubnets <- function(df_scholars = df, list_publications = publications, affiliation = "RU",
-    wave = list(wave1 = c(2018, 2019, 2020), wave2 = c(2021, 2022, 2023))) {
+f_pubnets <- function(df_scholars = df, list_publications = publications, discip = "sociology"+"political science", affiliation = "RU",
+    waves = list(wave1 = c(2018, 2019, 2020), wave2 = c(2021, 2022, 2023))) {
 
@@
     networklist <- list()
-    for (wave in 1:length(wave)) {
+    for (wave in 1:length(waves)) {
         networklist[[wave]] <- matrix(0, nrow = nrow(df_sel), ncol = nrow(df_sel))
@@
     publicationlist <- list()
-    for (wave in 1:length(wave)) {
+    for (wave in 1:length(waves)) {
         publicationlist[[wave]] <- publications %>%
             filter(gs_id %in% df_sel$gs_id) %>%
-            filter(year %in% wave[[wave]]) %>%
+            filter(year %in% waves[[wave]]) %>%
             select(author) %>%
@@
     publicationlist2 <- list()
-    for (wave in 1:length(wave)) {
+    for (wave in 1:length(waves)) {
         publicationlist2[[wave]] <- publicationlist[[wave]]$author %>%
@@
 
-    for (wave in 1:length(wave)) {
+    for (wave in 1:length(waves)) {
         # let us remove all publications with only one author
@@
 
-    for (wave in 1:length(wave)) {
+    for (wave in 1:length(waves)) {
         pubs <- publicationlist2[[wave]]
@@
 }
-```
 
-```{r}
-view(f_pubnets)
 ```
@@
 ```{r}
-
-#prior to my edits:
-# fcolnet <- function(data = scholars, university = "RU", discipline = "sociology", wave = list(c(2019, 2023)), type = c("first"))
-
-#after taking out discipline= "sociology" in the first part 
-fcolnet <- function(data = scholars, university = "RU", wave = list(c(2019, 2023)), type = c("first")) {
+fcolnet <- function(data = scholars, university = "RU", discipline = "sociology"+"political science", waves = list(c(2015,
+    2018), c(2019, 2023)), type = c("first")) {
 
@@
     ids <- demographics_soc$au_id
-    nwave <- length(wave)
-    nets <- array(0, dim = c(nwave, length(ids), length(ids)), dimnames = list(wave = 1:nwave, ids,
+    nwaves <- length(waves)
+    nets <- array(0, dim = c(nwaves, length(ids), length(ids)), dimnames = list(wave = 1:nwaves, ids,
         ids))
@@
     if (type == "first") {
-        for (j in 1:nwave) {
-            df_works_w <- df_works[df_works$works_year >= wave[[j]][1] & df_works$works_year <= wave[[j]][2],
+        for (j in 1:nwaves) {
+            df_works_w <- df_works[df_works$works_year >= waves[[j]][1] & df_works$works_year <= waves[[j]][2],
                 ]
@@
     if (type == "last") {
-        for (j in 1:nwave) {
-            df_works_w <- df_works[df_works$works_year >= wave[[j]][1] & df_works$works_year <= wave[[j]][2],
+        for (j in 1:nwaves) {
+            df_works_w <- df_works[df_works$works_year >= waves[[j]][1] & df_works$works_year <= waves[[j]][2],
                 ]
@@
     if (type == "all") {
-        for (j in 1:nwave) {
-            df_works_w <- df_works[df_works$works_year >= wave[[j]][1] & df_works$works_year <= wave[[j]][2],
+        for (j in 1:nwaves) {
+            df_works_w <- df_works[df_works$works_year >= waves[[j]][1] & df_works$works_year <= waves[[j]][2],
                 ]
@@
     return(output)
-
 }
@@
 
-## load data
+## load and inspect data
 
 ```{r}
-scholars <- fload("./data/processed/scholars_20240924.rda")
+scholars <- fload("./data/processed/scholars_20240924.rda") #make sure to lead fload first ofcourse
+
+#inspecting scholars_20240924.rda object
+#df_ego <- do.call(rbind.data.frame, scholars$demographics)
+#unique(df_ego$discipline.22)
 
 # save the output of your function
+testsoc  <- fcolnet(data = scholars, 
+                university = "RU", 
+                discipline = "sociology", 
+                waves = list(c(2015, 2018), c(2019, 2023)),
 
-# before my edits:
-# test <- fcolnet(data = scholars, university = "RU", discipline = "sociology", wave = list(c(2019, 2023)), type = c("first"))
+                            type = c("first"))
 
-# after taking discipline= "sociology" out
-# test <- fcolnet(data = scholars, university = "RU", wave = list(c(2019, 2023)), type = c("first"))
+# I DONT KNOW HOW TO MAKE ALL SCHOLARS BE PART OF SAME FUNCTION ("sociology"+ "political science" does not work...)
 
-# here is where the error occurs due to taking out the discipline = "sociology" in multiple prior parts of the code 
+testpolsci <- fcolnet(data = scholars, 
+                university = "RU", 
+                discipline = "political science", 
+                waves = list(c(2015, 2018), c(2019, 2023)), 
+                type = c("first"))
 ```
@@
 
+## waves - sociology department
+
 ```{r}
-wave <- test$nets[1, , ]
 
+# Jochem messed up and did: waves, rows, columns [1, , ]
+socwave1 <- testsoc$nets[ , ,1]  #rows, columns, waves
+socwave2 <- testsoc$nets[ , ,2]  #rows, columns, waves
 # let us put the diagonal to zero
-diag(wave) <- 0
+diag(socwave1) <- 0
+diag(socwave2) <- 0
 # we want a binary tie (not a weighted tie)
-wave[wave > 1] <- 1
+socwave1[socwave1 > 1] <- 1
+socwave2[socwave2 > 1] <- 1
+# put the nets in an array
+net_soc_array <- array(data = c(socwave1, socwave2), dim = c(dim(socwave1), 2))
 
-# put the nets in an array
-net_soc_array <- array(data = c(wave), dim = c(dim(wave), 2)) 
 str(net_soc_array)  #now we basically restructured this 
 # output: num [1:50, 1:50, 1:2] 0 0 0 0 0 0 0 0 0 0
+```
 
-# since I only take one wave should I replace the 2 with a 1 here? 
-net_soc_array1 <- array(data = c(wave), dim = c(dim(wave), 1)) 
-str(net_soc_array1)  #now we basically restructured this 
-# output: num [1:50, 1:50, 1] 0 0 0 0 0 0 0 0 0 0
+## waves - polsci department
+
+```{r}
+# Jochem messed up and did: waves, rows, columns [1, , ]
+polwave1 <- testpolsci$nets[ , ,1]  #rows, columns, waves
+polwave2 <- testpolsci$nets[ , ,2]  #rows, columns, waves
+# let us put the diagonal to zero
+diag(polwave1) <- 0
+diag(polwave2) <- 0
+# we want a binary tie (not a weighted tie)
+polwave1[polwave1 > 1] <- 1
+polwave2[polwave2 > 1] <- 1
+# put the nets in an array
+net_pol_array <- array(data = c(polwave1, polwave2), dim = c(dim(polwave1), 2))
+
+str(net_pol_array)  #now we basically restructured this
+
 ```
@@
 
+### ANSWER:
+
+RSiena needs at least two waves, because it models the evolution of the networks.
+We have to store the networks in an array before we can convert it to an dependent variable objects.
+Moreover, for RSiena the dimensions should be in the following order: rows, columns, waves.
+
+I 'messed up' my function (for didactic reasons ;-) )and stored the nets in the following order: waves, rows, columns.
+Thus, either correct my function or retrieve the separate waves and store them in the order RSiena requires.
+
+### QUESTION TO THE ANSWER:
+
+We had agreed on me only investigating one time point for the sake of simplicity.
+It seems I basically have no choice but to investigate two waves, revisit my RQs and make an additional RQ about tie changes over time, right?
+
+Then I would end up with 4 RQs and that seems like more than it needs to be for this project (great for a research incentive, but for this class I need to keep it simple, as I am currently very overworked).
+
+Any advice on how I can keep it simple, nonetheless?
+
 ## Examine structure
@@
 ```{r}
-dim(test$nets)
+dim(testsoc$nets)
+```
+
+```{r}
+dim(testpolsci$nets)
 ```
@@
 ## My data
+
+### sociology dep.
 
@@
 # dependent 
- nets <- test$nets
+nets <- testsoc$nets
 
-df_ego_demo <- test$data$demographics
-df_ego_oa <- test$data$scholars_oa
-df_ego_works <- test$data$works
+df_ego_demo <- testsoc$data$demographics
+df_ego_oa <- testsoc$data$scholars_oa
+df_ego_works <- testsoc$data$works
 
@@
 
-# --> EGO DATAFRAME with demo and oa 
+  # --> EGO DATAFRAME with demo and oa (sociology)
   ?join.data.frame
-  df_ego <- left_join(df_ego_demo, df_ego_oa, by = join_by(au_id == id))
+  df_soc_ego <- left_join(df_ego_demo, df_ego_oa, by = join_by(au_id == id))
 
-  rownames(nets[1,,]) == df_ego$au_id # checking if the author id's are the same as in df_ego in nets dataframe 
+  rownames(nets[1,,]) == df_soc_ego$au_id # checking if the author id's are the same as in df_ego in nets dataframe 
   # --> yes, the correct ones!!!
@@
 
+### polsci department
+
+```{r}
+# dependent
+# pol_net <- sienaDependent(net_pol_array)
+
+# dependent 
+pol_nets <- testpolsci$nets
+
+df_pol_ego_demo <- testpolsci$data$demographics
+df_pol_ego_oa <- testpolsci$data$scholars_oa
+df_pol_ego_works <- testpolsci$data$works
+
+# DEMO
+  str(df_pol_ego_demo, 1)
+
+  df_pol_ego_demo <- do.call(rbind.data.frame, df_pol_ego_demo)
+  df_pol_ego_demo[[1]]
+
+# OA
+  #str(df_pol_ego_oa, 1)
+  df_pol_ego_oa[[1]]
+  df_pol_ego_oa <- do.call(rbind.data.frame, df_pol_ego_oa)
+
+# --> EGO DATAFRAME with demo and oa (political science)
+  df_pol_ego <- left_join(df_pol_ego_demo, df_pol_ego_oa, by = join_by(au_id == id))
+
+  rownames(pol_nets[1,,]) == df_pol_ego$au_id # checking if the author id's are the same as in df_ego in nets dataframe 
+  # --> yes, the correct ones!!!
+```
+
 ## Gender
 
+### gender-soc
+
 ```{r}
-df_ego$Naam # list of all names
+df_soc_ego$Naam # list of all names in sociology department
 
-df_ego$gender <- c(0,1,0,1,0,0,1,1,0,0,
+df_soc_ego$gender <- c(0,1,0,1,0,0,1,1,0,0,
                        0,1,1,0,1,0,1,1,1,1,
@@
 # check if it went smoothly 
-view(df_ego[c('Naam', 'gender', 'au_id')])
+view(df_soc_ego[c('Naam', 'gender', 'au_id')])
+
+```
+
+### gender - polsci
+
+```{r}
+df_pol_ego$Naam # list of all names
+
+df_pol_ego$gender <- c(1,0,1,0,0,0,1,0,1,0,
+                       1,1,0,0,1,1,1,0,0,1,
+                       0,1,1,0,0,1,1,1,0,0,
+                       0,0,0,1,1,0,0,1,1,0,
+                       0,0,0,1,0,1,1,1,0,0,0) 
+    # manually filled in gender 0 = woman, 1 = man, based on majority given in NL voornamen bank, Guangyu was not in name bank but based on the employee-picture of RU, this person presents feminine, thus I assumed 0.
+
+# check if it went smoothly 
+view(df_pol_ego[c('Naam', 'gender', 'au_id')])
 
@@
 
-## H-index
+### joining polsci and soc data
 
-Inspired by Lucan's code:
+```{r}
+df_both_ego <- full_join(df_soc_ego, df_pol_ego, by = join_by
+                    (au_id == au_id, 
+                     Naam==Naam, 
+                     gender == gender, 
+                     discipline.22 == discipline.22,
+                     discipline.24 == discipline.24,
+                     counts_by_year== counts_by_year, 
+                     works_count == works_count, 
+                     cited_by_count == cited_by_count, 
+                     Universiteit1.22 == Universiteit1.22,
+                     Universiteit2.22 == Universiteit2.22,
+                     Universiteit1.24 == Universiteit1.24,
+                     Universiteit2.24 == Universiteit2.24,
+                     Universiteit.22 == Universiteit.22, 
+                     Universiteit.24 == Universiteit.24,
+                     no_oa_id == no_oa_id,
+                     display_name == display_name,
+                     display_name_alternatives == display_name_alternatives,
+                     ids== ids,
+                     orcid == orcid,
+                     year.22 == year.22,
+                     year.24 == year.24,
+                     Functie.24== Functie.24,
+                     relevance_score == relevance_score,
+                     affiliation_display_name == affiliation_display_name,
+                     affiliation_ror == affiliation_ror,
+                     affiliation_id == affiliation_id,
+                     affiliation_country_code == affiliation_country_code,
+                     affiliation_type == affiliation_type,
+                     affiliations_other == affiliations_other,
+                     affiliation_lineage == affiliation_lineage,
+                     Specialisatie.22 == Specialisatie.22,
+                     Specialisatie.24 == Specialisatie.24,
+                     x_concepts == x_concepts,
+                     works_api_url == works_api_url))
+# 101 scholars (50 sociology + 51 polsci) and 43 variables (as opposed to 21 bc i could not join them all.)
+
+# GODDAMMIT WHY DO I ONLY FIND THIS NOW?!?!?!?!
+# mydata <- sienaDataCreate(net, gender)
+```
+
+## QUESTION:
+
+With 101 scholars, instead of the nr.
+of scholars of looking at just one department, I wonder if this is where we could simplify.
+Looking at a change over time, but not looking through a lens that wants to compare the two departments.
+Instead, I could just look at one department.
+
+What do you think?
+
+## H-index webscraping
+
+Credits to Lucan for the code.
 
@@
 # Add h-index and i10-index columns to df_ego
-df_ego <- df_ego %>%
+df_ego <- df_both_ego %>%
   mutate(h_index = NA_real_, i10_index = NA_real_)
@@
 ```
+
+## Actually define data:
+
+```{r}
+# dependent:
+# net <- sienaDependent(net_soc_array)
+
+#covariate 1
+# gender <- coCovar(df_ego$gender)
+# covariate 2
+# h_index <- coCovar(df_ego$h_index)
+
+#combining data: wish I knew of this shit earlier...
+# mydata <- sienaDataCreate(net, gender)
+```
+
+# Create effects structure
+
+```{r}
+#myeff <- getEffects(mydata)
+```

### 2024-11-03 weekbacktrack.Rmd
defindedatapolsci

@@
 
-+-----------------------------------------------------------------------------------------------+------------------------------------------------------------+---------------------------------------------------------------+--------------------------------------------------------------------------------------------+-----------------------------------------------------------------+---------------------------------------------------------------------------+----------------------------------------------------------+
++-----------------------------------------------------------------------------------------------+------------------------------------------------------------+---------------------------------------------------------------+--------------------------------------------------------------------------------------------+-----------------------------------------------------------------+---------------------------------------------------------------------------+---------------------------------------------------------+
 | Mon                                                                                           | Tue                                                        | Wed                                                           | Thu                                                                                        | Fri                                                             | Sat                                                                       | Sun                                                     |
-+:==============================================================================================+:===========================================================+:==============================================================+:===========================================================================================+:================================================================+:==========================================================================+:=========================================================+
++:==============================================================================================+:===========================================================+:==============================================================+:===========================================================================================+:================================================================+:==========================================================================+:========================================================+
 | 28\.
@@
 |                                                                                               |                                                            |                                                               |                                                                                            |                                                                 |                                                                           |                                                         |
-| ![](images/used_arson%20frog.jpg)                                                             | ![](images/used_arson%20frog.jpg){width="952"}             | ![](images/socialnetworking.jpg){width="800"}Clarify RQs [D]\ | ![](images/socialnetworking_meh.jpg){width="800"}Rework schedule [according Jochems input] | ![](images/socialnetworking.jpg){width="800"}\                  | ![](images/socialnetworking_meh.jpg){width="800"}Plotting                 | ![](images/timetopanic.gif){width="800"}[chores at home] |
-|                                                                                               |                                                            | [Asked Jochem for input]                                      |                                                                                            | hyp.
-3                                                          |                                                                           |                                                          |
-|                                                                                               |                                                            |                                                               | Outline Intro and theory [W]\                                                              |                                                                 | Revisit RQs [D]                                                           |                                                          |
-|                                                                                               |                                                            |                                                               | (missing H3 still)                                                                         | Clarify [D]\                                                    |                                                                           |                                                          |
-|                                                                                               |                                                            |                                                               |                                                                                            | & define data [S1]\                                             |                                                                           |                                                          |
-|                                                                                               |                                                            |                                                               |                                                                                            | & create effects structure [S2]                                 |                                                                           |                                                          |
-+-----------------------------------------------------------------------------------------------+------------------------------------------------------------+---------------------------------------------------------------+--------------------------------------------------------------------------------------------+-----------------------------------------------------------------+---------------------------------------------------------------------------+----------------------------------------------------------+
+| ![](images/used_arson%20frog.jpg)                                                             | ![](images/used_arson%20frog.jpg){width="952"}             | ![](images/socialnetworking.jpg){width="800"}Clarify RQs [D]\ | ![](images/socialnetworking_meh.jpg){width="800"}Rework schedule [according Jochems input] | ![](images/socialnetworking.jpg){width="800"}\                  | ![](images/timetopanic.gif){width="800"}[chores at home, depression day]  | ![](images/socialnetworking_meh.jpg)Get polSci data,    |
+|                                                                                               |                                                            | [Asked Jochem for input]                                      |                                                                                            | Clarify [D]\                                                    |                                                                           |                                                         |
+|                                                                                               |                                                            |                                                               | OUTLINE Intro and theory [W]\                                                              | & define data [S1]\                                             |                                                                           | define data                                             |
+|                                                                                               |                                                            |                                                               | (missing H3 still)                                                                         |                                                                 |                                                                           |                                                         |
+|                                                                                               |                                                            |                                                               |                                                                                            | \* struggle with polsci data \*                                 |                                                                           |                                                         |
++-----------------------------------------------------------------------------------------------+------------------------------------------------------------+---------------------------------------------------------------+--------------------------------------------------------------------------------------------+-----------------------------------------------------------------+---------------------------------------------------------------------------+---------------------------------------------------------+
 | 04\.
@@
 | ![](images/socialnetworking_meh.jpg){width="800"}\                                            | ![](images/used_arson%20frog.jpg){width="952"}[university] | ![](images/used_arson%20frog.jpg)[university]                 | ![](images/socialnetworking_meh.jpg){width="800"}\                                         | ![](images/socialnetworking.jpg){width="800"}\                  | ![](images/socialnetworking.jpg){width="800"}Specify model [S4]           | ![](images/timetopanic.gif){width="800"}[Grandmas bday] |
+| & create effects structure [S2]                                                               |                                                            |                                                               | Plotting & revisit RQs                                                                     | Revisit RQs                                                     |                                                                           |                                                         |
+|                                                                                               |                                                            |                                                               |                                                                                            |                                                                 | Plotting                                                                  |                                                         |
 | Plotting                                                                                      |                                                            |                                                               | Initial description [S3]                                                                   | rewrite intro and Theory [W]                                    |                                                                           |                                                         |
-|                                                                                               |                                                            |                                                               |                                                                                            |                                                                 | Plotting                                                                  |                                                          |
-|                                                                                               |                                                            |                                                               | Revisit RQs                                                                                |                                                                 |                                                                           |                                                          |
-+-----------------------------------------------------------------------------------------------+------------------------------------------------------------+---------------------------------------------------------------+--------------------------------------------------------------------------------------------+-----------------------------------------------------------------+---------------------------------------------------------------------------+----------------------------------------------------------+
+|                                                                                               |                                                            |                                                               |                                                                                            |                                                                 |                                                                           |                                                         |
+| revisit RQs                                                                                   |                                                            |                                                               |                                                                                            |                                                                 |                                                                           |                                                         |
++-----------------------------------------------------------------------------------------------+------------------------------------------------------------+---------------------------------------------------------------+--------------------------------------------------------------------------------------------+-----------------------------------------------------------------+---------------------------------------------------------------------------+---------------------------------------------------------+
 | 11\.
@@
 | Data & methods part [W]                                                                       |                                                            |                                                               |                                                                                            | Plotting                                                        | Start Results [W]                                                         | [chores at home and university]                         |
-+-----------------------------------------------------------------------------------------------+------------------------------------------------------------+---------------------------------------------------------------+--------------------------------------------------------------------------------------------+-----------------------------------------------------------------+---------------------------------------------------------------------------+----------------------------------------------------------+
++-----------------------------------------------------------------------------------------------+------------------------------------------------------------+---------------------------------------------------------------+--------------------------------------------------------------------------------------------+-----------------------------------------------------------------+---------------------------------------------------------------------------+---------------------------------------------------------+
 | 18\.
@@
 |                                                         |
-+-----------------------------------------------------------------------------------------------+------------------------------------------------------------+---------------------------------------------------------------+--------------------------------------------------------------------------------------------+-----------------------------------------------------------------+---------------------------------------------------------------------------+----------------------------------------------------------+
++-----------------------------------------------------------------------------------------------+------------------------------------------------------------+---------------------------------------------------------------+--------------------------------------------------------------------------------------------+-----------------------------------------------------------------+---------------------------------------------------------------------------+---------------------------------------------------------+
 

### 2024-11-04 1definedata.Rmd
definedataprogressiguess

@@
 
-# require(RSiena)
-# require(RsienaTwoStep)
+require(RSiena)
+require(RsienaTwoStep)
 
@@
 # Jochem messed up and did: waves, rows, columns [1, , ]
-socwave1 <- testsoc$nets[ , ,1]  #rows, columns, waves
-socwave2 <- testsoc$nets[ , ,2]  #rows, columns, waves
+socwave1 <- testsoc$nets[1, , ]  #rows, columns, waves
+socwave2 <- testsoc$nets[2, , ]  #rows, columns, waves
 # let us put the diagonal to zero
@@
 # output: num [1:50, 1:50, 1:2] 0 0 0 0 0 0 0 0 0 0
+
+# dependent
+net <- sienaDependent(net_soc_array)
 ```
+
+## QUESTION:
+
+HOW COME: when I "correct" Jochem and put [rows,columns,waves] instead of [waves, rows, columns], the sienaDependent function does not work, but it DOES work if I leave the "incorrect" version unchanged?!
 
@@
 # Jochem messed up and did: waves, rows, columns [1, , ]
-polwave1 <- testpolsci$nets[ , ,1]  #rows, columns, waves
-polwave2 <- testpolsci$nets[ , ,2]  #rows, columns, waves
+polwave1 <- testpolsci$nets[1, , ]  #rows, columns, waves
+polwave2 <- testpolsci$nets[2, , ]  #rows, columns, waves
 # let us put the diagonal to zero
@@
 
-### **QUESTION:**
+### **(old) QUESTION:**
 
@@
 
-### QUESTION TO THE ANSWER:
+## (new) QUESTION:
 
@@
 ```{r}
-# dependent
+# # dependent
 # net <- sienaDependent(net_soc_array)
 
-# dependent 
-nets <- testsoc$nets
+# dependent ?
+# nets <- testsoc$nets
 
@@
 
+?full_join
+
 # GODDAMMIT WHY DO I ONLY FIND THIS NOW?!?!?!?!
@@
 
+### RSiena troubleshooting
+
+(Cannot install RSiena for some reason.)
+
+```{r}
+#require(RSiena)
+#require(RsienaTwoStep)
+```
+
+Changed administration rights in properties to get around the "file not found"-error.
+
 ```{r}
 # dependent:
-# net <- sienaDependent(net_soc_array)
+# net <- sienaDependent(net_soc_array) # Does not work "need 2 node sets for a bipartite network"
+
+#also this is only the array for sociology, I need to have a combined DV for both departments for RQ1 ...
+
+# str(net_soc_array)
+# my output here: 1:2, 1:50, 1:2
+# but in week 5-2: 1:50, 1:50, 1:2
+
+# net <- sienaDependent(net_soc_array) # Which array to take
 

### 2024-11-04 week5-2.Rmd
definedataprogressiguess

@@
 require (RSiena)
+#require(RsienaTwoStep
 
@@
 
-# didnt' make the IV gender butif i Had: mydata <- sienaDataCreate(net, gender)
+# didnt' make the IV gender butif i Had: 
+# mydata <- sienaDataCreate(net, gender)
 

### 2024-11-04 weekbacktrack.Rmd
definedataprogressiguess

@@
 |                                                                                               |                                                            |                                                               |                                                                                            |                                                                 |                                                                           |                                                         |
-| ![](images/socialnetworking_meh.jpg){width="800"}\                                            | ![](images/used_arson%20frog.jpg){width="952"}[university] | ![](images/used_arson%20frog.jpg)[university]                 | ![](images/socialnetworking_meh.jpg){width="800"}\                                         | ![](images/socialnetworking.jpg){width="800"}\                  | ![](images/socialnetworking.jpg){width="800"}Specify model [S4]           | ![](images/timetopanic.gif){width="800"}[Grandmas bday] |
-| & create effects structure [S2]                                                               |                                                            |                                                               | Plotting & revisit RQs                                                                     | Revisit RQs                                                     |                                                                           |                                                         |
-|                                                                                               |                                                            |                                                               |                                                                                            |                                                                 | Plotting                                                                  |                                                         |
-| Plotting                                                                                      |                                                            |                                                               | Initial description [S3]                                                                   | rewrite intro and Theory [W]                                    |                                                                           |                                                         |
+| ![](images/socialnetworking_meh.jpg){width="800"}\                                            | ![](images/used_arson%20frog.jpg){width="952"}[university] | ![](images/used_arson%20frog.jpg)[university]                 | ![](images/socialnetworking_meh.jpg){width="800"}\                                         | ![](images/socialnetworking.jpg){width="800"}\                  | ![](images/socialnetworking.jpg){width="800"}rewrite intro and Theory [W] | ![](images/timetopanic.gif){width="800"}[Grandmas bday] |
+| fix package error,                                                                            |                                                            |                                                               | Read Jochems answer & revisit RQs                                                          | Initial description [S3]                                        |                                                                           |                                                         |
+|                                                                                               |                                                            |                                                               |                                                                                            |                                                                 | Specify model [S4]                                                        |                                                         |
+| Define variables (get stuck with sienaDependent)                                              |                                                            |                                                               | & create effects structure [S2]                                                            | Plotting& Revisit RQs                                           |                                                                           |                                                         |
 |                                                                                               |                                                            |                                                               |                                                                                            |                                                                 |                                                                           |                                                         |
-| revisit RQs                                                                                   |                                                            |                                                               |                                                                                            |                                                                 |                                                                           |                                                         |
+| check in with Jochem                                                                          |                                                            |                                                               | Plotting & revisit RQs                                                                     |                                                                 |                                                                           |                                                         |
+|                                                                                               |                                                            |                                                               |                                                                                            |                                                                 |                                                                           |                                                         |
+| Plotting                                                                                      |                                                            |                                                               |                                                                                            |                                                                 |                                                                           |                                                         |
 +-----------------------------------------------------------------------------------------------+------------------------------------------------------------+---------------------------------------------------------------+--------------------------------------------------------------------------------------------+-----------------------------------------------------------------+---------------------------------------------------------------------------+---------------------------------------------------------+
@@
 |                                                                                               |                                                            |                                                               |                                                                                            |                                                                 |                                                                           |                                                         |
-| ![](images/socialnetworking_meh.jpg){width="800"}                                             | ![](images/used_arson%20frog.jpg){width="952"}[university] | ![](images/used_arson%20frog.jpg)[university]                 | ![](images/socialnetworking.jpg){width="800"}Data & methods part [W]\                      | ![](images/socialnetworking.jpg){width="800"}estimate model     | ![](images/socialnetworking.jpg){width="800"}goodness of fit [S6]         | ![](images/kermit-panic.gif)                            |
+| ![](images/socialnetworking_meh.jpg){width="800"}Data & methods part [W]                      | ![](images/used_arson%20frog.jpg){width="952"}[university] | ![](images/used_arson%20frog.jpg)[university]                 | ![](images/socialnetworking.jpg){width="800"}Data & methods part [W]\                      | ![](images/socialnetworking.jpg){width="800"}estimate model     | ![](images/socialnetworking.jpg){width="800"}goodness of fit [S6]         | ![](images/kermit-panic.gif)                            |
 |                                                                                               |                                                            |                                                               |                                                                                            |                                                                 |                                                                           |                                                         |
-| Data & methods part [W]                                                                       |                                                            |                                                               |                                                                                            | Plotting                                                        | Start Results [W]                                                         | [chores at home and university]                         |
+| Check in with Jochem                                                                          |                                                            |                                                               |                                                                                            | Plotting                                                        | Start Results [W]                                                         | [chores at home and university]                         |
 +-----------------------------------------------------------------------------------------------+------------------------------------------------------------+---------------------------------------------------------------+--------------------------------------------------------------------------------------------+-----------------------------------------------------------------+---------------------------------------------------------------------------+---------------------------------------------------------+
@@
 |                                                                                               |                                                            |                                                               |                                                                                            |                                                                 |                                                                           |                                                         |
-|                                                                                               |                                                            |                                                               |                                                                                            | Discussion & conclusion [W]                                     | ![](images/kermit-panic.gif){width="500"}Format project website& hand in!
+| Check in with Jochem?
+|                                                            |                                                               |                                                                                            | Discussion & conclusion [W]                                     | ![](images/kermit-panic.gif){width="500"}Format project website& hand in!
 |                                                         |

### 2024-11-04 plotting1.Rmd
plotting1start

--- 2024-11-04 1definedata.Rmd
@@
 ---
-title: "1-Define Data"
+title: "Plotting plots and Hotzenplotz"
 author: "Verooo"
-date: "2024-11-01"
+date: "2024-11-04"
 output: html_document
@@
 klippy::klippy(position = c('top', 'right'))
-klippy::klippy(color = 'darkred')
-klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done')
+#klippy::klippy(color = 'darkred')
+#klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done')
 ```
@@
 ```
-
-[**Defining Data**]{.underline}
-
-# Before the start
-
+# Set-up
 ## Clean workspace
-
 ```{r}
-# start with clean workspace
 rm(list = ls())
-
 ```
@@
 ```{r}
-# install.packages('tidyverse')
 require(tidyverse)
-
-# install an old version of RSiena including sienaRI
-#remove.packages("RSiena") #use this to remove the current version of RSiena
-#devtools::install_version("RSiena", version = "1.3.14", repos = "C:/Users/Vero/OneDrive - Radboud Universiteit/Documents/GitHub/labjournal") # This installs an older version
-
-# Run R as administrator when you install the older version!!
-
-# You should end up with version 1.3.14 loaded in instead of 1.4.7, 
-# but then make sure there isn't a install.packages("RSiena") function running somewhere, because then it will reinstall the newest version
-
 require(RSiena)
@@
 
+#install.packages("data.table")
+require(data.table)  # mainly for faster data handling
+# install.packages('xml2')
+require(xml2)
+# install.packages('rvest')
+require(rvest)
+require(igraph)
+
+require(ggraph)
+#install.packages('visNetwork')
+require(visNetwork)
+#install.packages('threejs')
+require(threejs)
+#install.packages('networkD3')
+require(networkD3)
+
 ```
 
-I do not seem to be able to call on the package RSiena, nor can I reinstall it.... I know programming never works on the first try but... goddamnit, why not even after 15?
-
 ## Functions 
-
-### Question
-
-**HOW do I get the discipline of political science in there too?**
-
-**How can I find out what the name for the discipline of political science in the original data frame (e.g. whether it is called polsci, political science, or politicalscience)?**
-
-**I don't know how to view the data set BEFORE we include only those scholars that have discipline = sociology. I cannot view the data**
-
-I tried removing the discipline = "sociology" part in the f_pubnets, fcolnet and all following functions that select data BUT SINCE 'discipline' is also relevant in the rest of the functions' code, it does not end up doing what I hoped (having a dataset with scholars of no specific discipline because then I could hopefully check how the department is named in the data and then find out how to add that to the data set initially).
-
 ```{r}
@@
 
-## more functions
-
+## More functions 
 ```{r}
@@
 }
-
 ```
 
-## load and inspect data
+## Load data
 
@@
 
-#inspecting scholars_20240924.rda object
-#df_ego <- do.call(rbind.data.frame, scholars$demographics)
-#unique(df_ego$discipline.22)
+```
 
+```{r}
 # save the output of your function
@@
 
-------------------------------------------------------------------------
-
-# Define Data
-
-## waves - sociology department
+### waves - sociology department
 
@@
 
-## QUESTION:
-
-HOW COME: when I "correct" Jochem and put [rows,columns,waves] instead of [waves, rows, columns], the sienaDependent function does not work, but it DOES work if I leave the "incorrect" version unchanged?!
-
-## waves - polsci department
+### waves - polsci department
 
@@
 
-### **(old) QUESTION:**
+### My data
 
-**What's the difference between putting the 2 and the 1 at the dimensions.
-I feel like one is appropriate since I am only looking at one wave, not two, but since the output is among the 'values' not 'data', I cannot view the variable net_soc_array(1) nor "visualize" what that means in terms of its structure.
-I don't really know what the difference would be between the 1:2 and the 1 in the outputs, structurally.**
-
-### ANSWER:
-
-RSiena needs at least two waves, because it models the evolution of the networks.
-We have to store the networks in an array before we can convert it to an dependent variable objects.
-Moreover, for RSiena the dimensions should be in the following order: rows, columns, waves.
-
-I 'messed up' my function (for didactic reasons ;-) )and stored the nets in the following order: waves, rows, columns.
-Thus, either correct my function or retrieve the separate waves and store them in the order RSiena requires.
-
-## (new) QUESTION:
-
-We had agreed on me only investigating one time point for the sake of simplicity.
-It seems I basically have no choice but to investigate two waves, revisit my RQs and make an additional RQ about tie changes over time, right?
-
-Then I would end up with 4 RQs and that seems like more than it needs to be for this project (great for a research incentive, but for this class I need to keep it simple, as I am currently very overworked).
-
-Any advice on how I can keep it simple, nonetheless?
-
-## Examine structure
-
-```{r}
-dim(testsoc$nets)
-```
-
-```{r}
-dim(testpolsci$nets)
-```
-
-## My data
-
-### sociology dep.
+#### sociology dep.
 
@@
   # --> EGO DATAFRAME with demo and oa (sociology)
-  ?join.data.frame
+  # ?join.data.frame
   df_soc_ego <- left_join(df_ego_demo, df_ego_oa, by = join_by(au_id == id))
@@
 
-### polsci department
+#### polsci department
 
@@
 
-## Gender
+### Gender
 
-### gender-soc
+#### gender-soc
 
@@
 
-### gender - polsci
+#### gender - polsci
 
@@
 
-### joining polsci and soc data
-
+### joining soc and polsci data
 ```{r}
@@
 
-## QUESTION:
-
-With 101 scholars, instead of the nr.
-of scholars of looking at just one department, I wonder if this is where we could simplify.
-Looking at a change over time, but not looking through a lens that wants to compare the two departments.
-Instead, I could just look at one department.
-
-What do you think?
-
-## H-index webscraping
+### H-index webscraping
 
@@
 
-## Actually define data:
+# Plots and such 
+## wave 1 - soc
+```{r}
+testsoc_w1 <- igraph::graph_from_adjacency_matrix(
+  testsoc$nets[1,,], # first wave of data. 
+  # (thus I select the array of networks and take the first matrix)
+  mode = c("directed"),
+  weighted = NULL,
+  diag = FALSE,
+  add.colnames = NULL,
+  add.rownames = NULL
+)
 
-### RSiena troubleshooting
+plot(testsoc_w1,
+     vertex.label = NA,
+     edge.width = 0.2,
+     edge.arrow.size =0.2)
 
-(Cannot install RSiena for some reason.)
+```
+## wave 2 - soc
+```{r}
+testsoc_w2 <- igraph::graph_from_adjacency_matrix(
+  testsoc$nets[2,,], #take the second wave 
+  mode = c("directed"),
+  weighted = NULL,
+  diag = FALSE,
+  add.colnames = NULL
+  )
 
-```{r}
-#require(RSiena)
-#require(RsienaTwoStep)
+plot(testsoc_w2,
+     vertex.label = NA,
+     edge.width = 0.2,
+     edge.arrow.size =0.2)
 ```
 
-Changed administration rights in properties to get around the "file not found"-error.
+## wave 1 - pol
+```{r}
+testpol_w1 <- igraph::graph_from_adjacency_matrix(
+  testpolsci$nets[1,,], #for this example I take the first wave of data. (thus I select the array of networks and take the first matrix)
+  mode = c("directed"),
+  weighted = NULL,
+  diag = FALSE,
+  add.colnames = NULL,
+  add.rownames = NULL
+  )
 
-```{r}
-# dependent:
-# net <- sienaDependent(net_soc_array) # Does not work "need 2 node sets for a bipartite network"
+plot(testpol_w1,
+     vertex.label = NA,
+     edge.width = 0.2,
+     edge.arrow.size =0.2)
 
-#also this is only the array for sociology, I need to have a combined DV for both departments for RQ1 ...
-
-# str(net_soc_array)
-# my output here: 1:2, 1:50, 1:2
-# but in week 5-2: 1:50, 1:50, 1:2
-
-# net <- sienaDependent(net_soc_array) # Which array to take
-
-#covariate 1
-# gender <- coCovar(df_ego$gender)
-# covariate 2
-# h_index <- coCovar(df_ego$h_index)
-
-#combining data: wish I knew of this shit earlier...
-# mydata <- sienaDataCreate(net, gender)
 ```
 
-# Create effects structure
+## wave 2 - pol
+```{r}
+testpol_w2 <- igraph::graph_from_adjacency_matrix(
+  testpolsci$nets[2,,], #take the second wave 
+  mode = c("directed"),
+  weighted = NULL,
+  diag = FALSE,
+  add.colnames = NULL
+  )
 
+plot(testpol_w2,
+     vertex.label = NA,
+     edge.width = 0.2,
+     edge.arrow.size =0.2)
+```
+
+##  Ego characteristics 
+### soc ego
+```{r, include=FALSE}
+#Let us find ego characteristics. 
+#first fish out the data
+# df <- df_ego$data
+
+#same complicated structure as 'scholars' thus first make a dataframe from the list in which all info was saved. 
+# df_ego <- do.call(rbind.data.frame, df$demographics)
+#DO NOT MESS UP THE ORDER! THUS IF YOU JOIN THIS DATA WITH YOUR OWN DATA CHECK THAT ORDER REMAINED THE SAME!!
+
+# plot(test_w2,
+     # vertex.color = ifelse(df_ego$Universiteit.24 == "RU", "red", "blue"), #now, I can use actor attributes for plotting. 
+     # vertex.label = NA,
+     # edge.width = 0.2,
+     # edge.arrow.size =0.2)
+```
+
+### pol ego
+```{r, include=FALSE}
+#Let us find ego characteristics. 
+#first fish out the data
+# df <- testpolsci$data
+
+#same complicated structure as 'scholars' thus first make a dataframe from the list in which all info was saved. 
+# df_ego <- do.call(rbind.data.frame, df$demographics)
+#DO NOT MESS UP THE ORDER! THUS IF YOU JOIN THIS DATA WITH YOUR OWN DATA CHECK THAT ORDER REMAINED THE SAME!!
+
+# plot(test_w2,
+#      vertex.color = ifelse(df_ego$Universiteit.24 == "RU", "red", "blue"), #now, I can use actor attributes for plotting. 
+     # vertex.label = NA,
+     # edge.width = 0.2,
+     # edge.arrow.size =0.2)
+```
+
+# Descriptives 
 ```{r}
-#myeff <- getEffects(mydata)
+
 ```

### 2024-11-04 plotting1.Rmd
weekbacktrackchange

@@
 ```
+
 ## wave 2 - soc

### 2024-11-04 weekbacktrack.Rmd
weekbacktrackchange

@@
 |                                                                                               |                                                            |                                                               |                                                                                            |                                                                 |                                                                           |                                                         |
-| ![](images/socialnetworking_meh.jpg){width="800"}\                                            | ![](images/used_arson%20frog.jpg){width="952"}[university] | ![](images/used_arson%20frog.jpg)[university]                 | ![](images/socialnetworking_meh.jpg){width="800"}\                                         | ![](images/socialnetworking.jpg){width="800"}\                  | ![](images/socialnetworking.jpg){width="800"}rewrite intro and Theory [W] | ![](images/timetopanic.gif){width="800"}[Grandmas bday] |
+| ![](images/socialnetworking_meh.jpg){width="800"}\                                            | ![](images/used_arson%20frog.jpg){width="952"}[work]       | ![](images/used_arson%20frog.jpg)[university]                 | ![](images/socialnetworking_meh.jpg){width="800"}\                                         | ![](images/socialnetworking.jpg){width="800"}\                  | ![](images/socialnetworking.jpg){width="800"}rewrite intro and Theory [W] | ![](images/timetopanic.gif){width="800"}[Grandmas bday] |
 | fix package error,                                                                            |                                                            |                                                               | Read Jochems answer & revisit RQs                                                          | Initial description [S3]                                        |                                                                           |                                                         |
-|                                                                                               |                                                            |                                                               |                                                                                            |                                                                 | Specify model [S4]                                                        |                                                         |
+|                                                                                               | Talk to Jochem                                             |                                                               |                                                                                            |                                                                 | Specify model [S4]                                                        |                                                         |
 | Define variables (get stuck with sienaDependent)                                              |                                                            |                                                               | & create effects structure [S2]                                                            | Plotting& Revisit RQs                                           |                                                                           |                                                         |
-|                                                                                               |                                                            |                                                               |                                                                                            |                                                                 |                                                                           |                                                         |
+|                                                                                               | [university]                                               |                                                               |                                                                                            |                                                                 |                                                                           |                                                         |
 | check in with Jochem                                                                          |                                                            |                                                               | Plotting & revisit RQs                                                                     |                                                                 |                                                                           |                                                         |

### 2024-11-07 revisitwithJochem.Rmd
checkinwithjochempush

--- 2024-11-04 plotting1.Rmd
@@
 author: "Verooo"
-date: "2024-11-04"
+date: "2024-11-05"
 output: html_document
@@
 ```
-# Set-up
-## Clean workspace
-```{r}
+
+Meeting with Jochem
+
+look at publications website (sunbelt workshop)
+
+# Getting started
+
+```{r clean}
 rm(list = ls())
@@
 
-```{r}
+```{r package}
 require(tidyverse)
@@
 ## Functions
-```{r}
+
+```{r functions 1}
 fpackage.check <- function(packages) {
@@
 ## More functions
-```{r}
+
+```{r functions 2}
 fcolnet <- function(data = scholars, university = "RU", discipline = "sociology"+"political science", waves = list(c(2015,
@@
 
-```{r}
+```{r data}
 scholars <- fload("./data/processed/scholars_20240924.rda") #make sure to lead fload first ofcourse
+```
+
+```{r saving output}
+# save the output of your function
+
+test  <- fcolnet(data = scholars, 
+                university = "RU", 
+                discipline = c("sociology", "political science"),
+                waves = list(c(2015, 2018), c(2019, 2023)), 
+                type = c("all")) # all, first, last # which ties in there
+
+# USE not all but first or last so the ties are directed from "perspective" of first author of the publications 
+# usually first most prestige
 
@@
 
+# Gender
+
+## saving data for each deapartment
+
 ```{r}
+#inspecting scholars_20240924.rda object
+#df_ego <- do.call(rbind.data.frame, scholars$demographics)
+#unique(df_ego$discipline.22)
+
 # save the output of your function
@@
 
-### waves - sociology department
-
-```{r}
-
-# Jochem messed up and did: waves, rows, columns [1, , ]
-socwave1 <- testsoc$nets[1, , ]  #rows, columns, waves
-socwave2 <- testsoc$nets[2, , ]  #rows, columns, waves
-# let us put the diagonal to zero
-diag(socwave1) <- 0
-diag(socwave2) <- 0
-# we want a binary tie (not a weighted tie)
-socwave1[socwave1 > 1] <- 1
-socwave2[socwave2 > 1] <- 1
-# put the nets in an array
-net_soc_array <- array(data = c(socwave1, socwave2), dim = c(dim(socwave1), 2))
-
-str(net_soc_array)  #now we basically restructured this 
-# output: num [1:50, 1:50, 1:2] 0 0 0 0 0 0 0 0 0 0
-
-# dependent
-net <- sienaDependent(net_soc_array)
-```
-
-### waves - polsci department
-
-```{r}
-# Jochem messed up and did: waves, rows, columns [1, , ]
-polwave1 <- testpolsci$nets[1, , ]  #rows, columns, waves
-polwave2 <- testpolsci$nets[2, , ]  #rows, columns, waves
-# let us put the diagonal to zero
-diag(polwave1) <- 0
-diag(polwave2) <- 0
-# we want a binary tie (not a weighted tie)
-polwave1[polwave1 > 1] <- 1
-polwave2[polwave2 > 1] <- 1
-# put the nets in an array
-net_pol_array <- array(data = c(polwave1, polwave2), dim = c(dim(polwave1), 2))
-
-str(net_pol_array)  #now we basically restructured this
-
-```
-
-### My data
-
-#### sociology dep.
-
-not using net_soc_array for now since I am unsure about its use due to question above
+#### soc department
 
@@
   # --> EGO DATAFRAME with demo and oa (sociology)
-  # ?join.data.frame
+  ?join.data.frame
   df_soc_ego <- left_join(df_ego_demo, df_ego_oa, by = join_by(au_id == id))
@@
 
-### Gender
+### gender-soc
 
-#### gender-soc
-
-```{r}
+```{r gender s}
 df_soc_ego$Naam # list of all names in sociology department
@@
 
+# fsave(df_soc_ego)
+
 ```
 
-#### gender - polsci
+### gender - polsci
 
-```{r}
+```{r gender p}
 df_pol_ego$Naam # list of all names
@@
 # gender <- coCovar(df_ego$gender)
+
+# fsave(df_pol_ego)
 ```
 
-### joining soc and polsci data
-```{r}
-df_both_ego <- full_join(df_soc_ego, df_pol_ego, by = join_by
-                    (au_id == au_id, 
-                     Naam==Naam, 
-                     gender == gender, 
-                     discipline.22 == discipline.22,
-                     discipline.24 == discipline.24,
-                     counts_by_year== counts_by_year, 
-                     works_count == works_count, 
-                     cited_by_count == cited_by_count, 
-                     Universiteit1.22 == Universiteit1.22,
-                     Universiteit2.22 == Universiteit2.22,
-                     Universiteit1.24 == Universiteit1.24,
-                     Universiteit2.24 == Universiteit2.24,
-                     Universiteit.22 == Universiteit.22, 
-                     Universiteit.24 == Universiteit.24,
-                     no_oa_id == no_oa_id,
-                     display_name == display_name,
-                     display_name_alternatives == display_name_alternatives,
-                     ids== ids,
-                     orcid == orcid,
-                     year.22 == year.22,
-                     year.24 == year.24,
-                     Functie.24== Functie.24,
-                     relevance_score == relevance_score,
-                     affiliation_display_name == affiliation_display_name,
-                     affiliation_ror == affiliation_ror,
-                     affiliation_id == affiliation_id,
-                     affiliation_country_code == affiliation_country_code,
-                     affiliation_type == affiliation_type,
-                     affiliations_other == affiliations_other,
-                     affiliation_lineage == affiliation_lineage,
-                     Specialisatie.22 == Specialisatie.22,
-                     Specialisatie.24 == Specialisatie.24,
-                     x_concepts == x_concepts,
-                     works_api_url == works_api_url))
-# 101 scholars (50 sociology + 51 polsci) and 43 variables (as opposed to 21 bc i could not join them all.)
+### save gender data sets
 
-?full_join
-
-# GODDAMMIT WHY DO I ONLY FIND THIS NOW?!?!?!?!
-# mydata <- sienaDataCreate(net, gender)
+```{r gender data}
+soc_gender <- fload("./data/processed/df_soc_ego_20241105.rda")
+pol_gender <- fload("./data/processed/df_pol_ego_20241105.rda")
 ```
 
-### H-index webscraping
+### Combine data (gender)
+
+```{r combine gender set}
+df <- test$data
+df_ego <- do.call(rbind.data.frame, df$demographics)
+
+soc_gender <- soc_gender[,c("Naam", "gender")]
+pol_gender <- pol_gender[,c("Naam", "gender")]
+
+gender <- rbind(soc_gender, pol_gender) # combining data sets
+
+df_ego <- df_ego %>% 
+            left_join(gender) #dataset 
+```
+
+# Quick RSiena
+
+```{r RSiena}
+#step1 data
+wave1 <- test$nets[1,,]
+wave2 <- test$nets[2,,]
+
+#put diagonals to zero 
+diag(wave1) <- 0
+diag(wave2) <- 0
+# we want a binary tie (not a weighted tie)
+wave1[wave1 > 1] <- 1
+wave2[wave2 > 1] <- 1
+# put the nets in an array
+net_array <- array(data = c(wave1, wave2), dim = c(dim(wave1), 2))
+
+gender <- df_ego$gender
+
+#dependent
+nets <- sienaDependent(net_array)
+#covariate
+genderrs <- coCovar(gender)
+#define data 
+mydata <- sienaDataCreate(nets, genderrs)
+
+#define effects structure 
+myeff <- getEffects(mydata)
+
+#skipped description
+
+myeff <- includeEffects(myeff, isolateNet, inPop, outAct)
+
+myeff <- includeEffects(myeff, egoX, altX, sameX, interaction1 = "genderrs")
+
+#look up which effects to iclude
+
+myAlgorithm <- sienaAlgorithmCreate(modelType = c(nets=6), projname = "proProject")
+# undirected: model 6 "additive model", #check manual for this
+
+# estimate
+model1 <- siena07(myAlgorithm, data = mydata, effects = myeff, returnDeps = TRUE)
+#latter needed for GOF
+
+model1
+
+# output:  convergence ration NA probably bc we chose all ties to be included (type = "all") earlier
+# we can go back and change that or change it here in the myAlgorithm function
+
+# Make it a directed network 
+# focus: writing, h index, 
+# model interpretation
+
+```
+
+# H-index webscraping
 
@@
 
-```{r}
+```{r h-index, include=FALSE, eval= FALSE}
 # Add h-index and i10-index columns to df_ego
@@
 
-# Plots and such 
-## wave 1 - soc
+# Plotting
+
 ```{r}
-testsoc_w1 <- igraph::graph_from_adjacency_matrix(
-  testsoc$nets[1,,], # first wave of data. 
+test_w1 <- igraph::graph_from_adjacency_matrix(
+  test$nets[1,,], # first wave of data. 
   # (thus I select the array of networks and take the first matrix)
@@
   add.colnames = NULL,
-  add.rownames = NULL
-)
+  add.rownames = NULL)
 
-plot(testsoc_w1,
-     vertex.label = NA,
-     edge.width = 0.2,
-     edge.arrow.size =0.2)
-
-```
-
-## wave 2 - soc
-```{r}
-testsoc_w2 <- igraph::graph_from_adjacency_matrix(
-  testsoc$nets[2,,], #take the second wave 
-  mode = c("directed"),
-  weighted = NULL,
-  diag = FALSE,
-  add.colnames = NULL
-  )
-
-plot(testsoc_w2,
+plot(test_w1,
      vertex.label = NA,
@@
 
-## wave 1 - pol
 ```{r}
-testpol_w1 <- igraph::graph_from_adjacency_matrix(
-  testpolsci$nets[1,,], #for this example I take the first wave of data. (thus I select the array of networks and take the first matrix)
-  mode = c("directed"),
-  weighted = NULL,
-  diag = FALSE,
-  add.colnames = NULL,
-  add.rownames = NULL
-  )
+names(df_ego) #see labels of variables
 
-plot(testpol_w1,
+plot(test_w1,
+vertex.color = ifelse(df_ego$gender == 1, "red", "blue"), #now, I can use actor attributes for plotting.
 vertex.label = NA,
@@
 
+# if you dont want plot to turn, save the layout (look at SNASS)
 ```
-
-## wave 2 - pol
-```{r}
-testpol_w2 <- igraph::graph_from_adjacency_matrix(
-  testpolsci$nets[2,,], #take the second wave 
-  mode = c("directed"),
-  weighted = NULL,
-  diag = FALSE,
-  add.colnames = NULL
-  )
-
-plot(testpol_w2,
-     vertex.label = NA,
-     edge.width = 0.2,
-     edge.arrow.size =0.2)
-```
-
-##  Ego characteristics 
-### soc ego
-```{r, include=FALSE}
-#Let us find ego characteristics. 
-#first fish out the data
-# df <- df_ego$data
-
-#same complicated structure as 'scholars' thus first make a dataframe from the list in which all info was saved. 
-# df_ego <- do.call(rbind.data.frame, df$demographics)
-#DO NOT MESS UP THE ORDER! THUS IF YOU JOIN THIS DATA WITH YOUR OWN DATA CHECK THAT ORDER REMAINED THE SAME!!
-
-# plot(test_w2,
-     # vertex.color = ifelse(df_ego$Universiteit.24 == "RU", "red", "blue"), #now, I can use actor attributes for plotting. 
-     # vertex.label = NA,
-     # edge.width = 0.2,
-     # edge.arrow.size =0.2)
-```
-
-### pol ego
-```{r, include=FALSE}
-#Let us find ego characteristics. 
-#first fish out the data
-# df <- testpolsci$data
-
-#same complicated structure as 'scholars' thus first make a dataframe from the list in which all info was saved. 
-# df_ego <- do.call(rbind.data.frame, df$demographics)
-#DO NOT MESS UP THE ORDER! THUS IF YOU JOIN THIS DATA WITH YOUR OWN DATA CHECK THAT ORDER REMAINED THE SAME!!
-
-# plot(test_w2,
-#      vertex.color = ifelse(df_ego$Universiteit.24 == "RU", "red", "blue"), #now, I can use actor attributes for plotting. 
-     # vertex.label = NA,
-     # edge.width = 0.2,
-     # edge.arrow.size =0.2)
-```
-
-# Descriptives 
-```{r}
-
-```

### 2024-11-07 week5-2.Rmd
checkinwithjochempush

@@
   you can only include two of the three (tie creation, breaking and maintaining)
-  Assumption meachnisms to make and breka a tie are the same so we only use the EVALUATION part
+  Assumption mechanisms to make and breaka a tie are the same so we only use the EVALUATION part
 
-  All these effects are describedin the manual of RSiena Chapter 12 (9?)
+  All these effects are described in the manual of RSiena Chapter 12 (9?)
 
@@
 # STUDY CHAPTER 12 of RSiena Manual! 
-# COLLECTIVELY SEND PAPER TO JOCHEM BEFORE WEEKEND!
 # PrACTICE WITH RSIENA
-# LOOK AT MANUAL
 

### 2024-11-07 draftdata.Rmd
checkinwithjochempush
unnecessarypushbutheyherewego

@@
 # Data Draft
+
+Information about data set:
+
+-   Data set provided by Jochem
+
+-   collaborations of scholars in NL
+
+-   time frame: ?
+
+    -   timeframe of focus
+
+## DV: Collaboration between scholars
+
+## Covariate 1: Gender
+
+-   assumed binary for simplicity and ethical considerations of assuming gender based on other characterstics
+
+-   Names of scholars manually checked in Dutch Voornamenbank website **(NAME WEBSITE)**
+
+-   with 0 = female and 1 = male.
+
+-
+
+## Covariate 2: Prestige
+
+-   indicated by H-Index: and i10 index
+
+-   definitions indeces:
+
+-
+
+-   number of citations and publications webscraped through OpenAlex **[source]**
+
+-   h index and i10 index calculated based on these counts
+
+```{=html}
+<!-- -->
+```
+-

### 2024-11-07 revisitwithJochem.Rmd
unnecessarypushbutheyherewego

@@
 ```{r combine gender set}
-df <- test$data
-df_ego <- do.call(rbind.data.frame, df$demographics)
+df <- test$data # make dataset with all data 
+df_ego <- do.call(rbind.data.frame, df$demographics) # dataset with demographic information
 
-soc_gender <- soc_gender[,c("Naam", "gender")]
-pol_gender <- pol_gender[,c("Naam", "gender")]
+soc_gender <- soc_gender[,c("Naam", "gender")] # selecting only the content we need
+pol_gender <- pol_gender[,c("Naam", "gender")] # selecting only the content we need
 
-gender <- rbind(soc_gender, pol_gender) # combining data sets
+gender <- rbind(soc_gender, pol_gender) # combining the gender data sets
 
 df_ego <- df_ego %>% 
-            left_join(gender) #dataset 
+            left_join(gender) #dcombininf dataset of gender with the one with demographic information 
 ```
@@
 vertex.color = ifelse(df_ego$gender == 1, "red", "blue"), #now, I can use actor attributes for plotting.
+# here: if gender = 1 (aka man) then red dot, if not then blue 
 vertex.label = NA,

### 2024-11-07 week5-2.Rmd
unnecessarypushbutheyherewego

@@
   you can only include two of the three (tie creation, breaking and maintaining)
-  Assumption mechanisms to make and breaka a tie are the same so we only use the EVALUATION part
 
-  All these effects are described in the manual of RSiena Chapter 12 (9?)
+The assumption is: mechanisms to make and break a a tie are the same so WE ONLY USE THE EVALUATION part
+
+  All these effects are described in the manual of RSiena Chapter 12!
 
@@
 ```
-inpope ppl with lots of indegrees will havelotof indegrees later (in population)
+over time:
+inpope ppl with lots of indegrees will havelot of indegrees later (in population)
  outAct ppl with lots of outdegrees will have lot of indegrees later
 
- hint for my own project: interaction effect of these statistics and the effect of gender
+ hint FOR MY OWN PROJECT: interaction effect of these statistics and the effect of gender
 

### 2024-11-08 draftdata.Rmd
pushitpushitrestructure

@@
 output: html_document
+bibliography: references.bib
 ---
@@
 
-# Data Draft
+# Data
 
@@
 
-## DV: Collaboration between scholars
+## DV: formation of ties between scholars
+
+-   formation of ties between scholars
+
+-   adjacency-matrix
+
+-
 
@@
 
--   Names of scholars manually checked in Dutch Voornamenbank website **(NAME WEBSITE)**
+-   Names of scholars manually checked in Dutch Voornamenbank website of the Meertens Institute (@MeertensInstituut)
 
@@
 
+-   control variable in this research design
+
 -   indicated by H-Index: and i10 index
@@
 
--
+        -    H-index: Hirsch-Index
+
+            -   From Lucan: "The h-index namely measures an author’s prestige by calculating the number of publications that have been cited at least as many times as the total number of their publications.
+As explained by the creator of the h-index, ” A scientist has index h if h of his or her Np papers have at least h citations each and the other (Np - h) papers have ≤h citations each” (@Hirsch2005) "
+
+        -   i10-index:
 
@@
 ```
--
+-   Code for this was provided by a fellow course mate, namely Lucan Bovens
+
+# Data preparation /Methods
+
+### RSiena
+
+-   definition
+
+    -   "SIENA, shorthand for **Simulation Investigation for Empirical Network Analysis**, is a computer program that carries out the statistical estimation of models for repeated measures of social networks according to the dynamic actor-oriented model of Snijders and van Duijn (1997), Snijders (2001), and Snijders, Steglich, and Schweinberger (2007); also see Steglich, Snijders, and Pearson (2009).
+A tutorial for these models is in Snijders, van de Bunt, and Steglich (2009).
+Some examples are presented, e.g., in van de Bunt (1999); van de Bunt, van Duijn, and Snijders (1999); and van Duijn, Zeggelink, Stokman, and Wasseur (2003); and Steglich, Snijders, and West (2006).
+A website for SIENA is maintained at http://www.stats.ox.ac.uk/\~snijders/siena/ .
+At this website (‘publications’ tab) you shall also find references to introductions in various other languages.
+        This is a provisional manual for SIENA version 4.0, which is also called RSiena.
+This is a contributed package for the R statistical system which can be downloaded from http://cran.r-project.org.
+For the operation of R, the reader is referred to the corresponding manual.
+If desired, SIENA can be operated apparently independently of R, as is explained in Section 2.1.
+        RSiena was programmed by Ruth Ripley and Krists Boitmanis, in collaboration with Tom Snijders."
+
+Ripley, Ruth, and Snijders, Tom A.B.
+2009.
+Manual for SIENA version 4.0 (provisional version, July 6, 2009).
+Oxford: University of Oxford, Department of Statistics; Nuffield College.
+<http://www.stats.ox.ac.uk/siena/>
+
+Manual reference: @RSiena_manual
+
+Siena package refrence: @RSiena_package
+
+Methods, aka use of RSiena for SNA
+
+-   Jochem Tolsma and Bas Hofstra: [**Methods**](https://jochemtolsma.github.io/SNA-4-Social-Scientists/socionetsm.html) (focusing on RSiena), Chapter 7 of [**Social Network Analysis for Social Scientists**](https://jochemtolsma.github.io/SNA-4-Social-Scientists/) ("SNASS").
+
+    -   reference: \@SNASS
+
+# Data description

### 2024-11-08 revisitwithJochem.Rmd
pushitpushitrestructure

@@
 
-#### soc department
+#### soc department save
 
 ```{r}
-# # dependent
-# net <- sienaDependent(net_soc_array)
-
-# dependent ?
-# nets <- testsoc$nets
+soc_nets <- testsoc$nets
 
@@
 
-  rownames(nets[1,,]) == df_soc_ego$au_id # checking if the author id's are the same as in df_ego in nets dataframe 
+  rownames(soc_nets[1,,]) == df_soc_ego$au_id # checking if the author id's are the same as in df_ego in nets dataframe 
   # --> yes, the correct ones!!!
@@
 
-#### polsci department
+#### polsci department save
 
@@
 # DEMO
-  str(df_pol_ego_demo, 1)
+  #str(df_pol_ego_demo, 1)
 
@@
 
-### gender-soc
+### gender - sociology department
 
@@
 # check if it went smoothly 
-view(df_soc_ego[c('Naam', 'gender', 'au_id')])
+# view(df_soc_ego[c('Naam', 'gender', 'au_id')])
 
@@
 # check if it went smoothly 
-view(df_pol_ego[c('Naam', 'gender', 'au_id')])
+# view(df_pol_ego[c('Naam', 'gender', 'au_id')])
 
@@
 df <- test$data # make dataset with all data 
-df_ego <- do.call(rbind.data.frame, df$demographics) # dataset with demographic information
+df_ego <- do.call(rbind.data.frame, df$demographics) # data set with demographic information
 
@@
 df_ego <- df_ego %>% 
-            left_join(gender) #dcombininf dataset of gender with the one with demographic information 
+            left_join(gender) #dcombining data set of gender with the one with demographic information 
 ```
 
-# Quick RSiena
+# H-index 
+Credits to Lucan Bovens for the code.
 
-```{r RSiena}
-#step1 data
-wave1 <- test$nets[1,,]
-wave2 <- test$nets[2,,]
-
-#put diagonals to zero 
-diag(wave1) <- 0
-diag(wave2) <- 0
-# we want a binary tie (not a weighted tie)
-wave1[wave1 > 1] <- 1
-wave2[wave2 > 1] <- 1
-# put the nets in an array
-net_array <- array(data = c(wave1, wave2), dim = c(dim(wave1), 2))
-
-gender <- df_ego$gender
-
-#dependent
-nets <- sienaDependent(net_array)
-#covariate
-genderrs <- coCovar(gender)
-#define data 
-mydata <- sienaDataCreate(nets, genderrs)
-
-#define effects structure 
-myeff <- getEffects(mydata)
-
-#skipped description
-
-myeff <- includeEffects(myeff, isolateNet, inPop, outAct)
-
-myeff <- includeEffects(myeff, egoX, altX, sameX, interaction1 = "genderrs")
-
-#look up which effects to iclude
-
-myAlgorithm <- sienaAlgorithmCreate(modelType = c(nets=6), projname = "proProject")
-# undirected: model 6 "additive model", #check manual for this
-
-# estimate
-model1 <- siena07(myAlgorithm, data = mydata, effects = myeff, returnDeps = TRUE)
-#latter needed for GOF
-
-model1
-
-# output:  convergence ration NA probably bc we chose all ties to be included (type = "all") earlier
-# we can go back and change that or change it here in the myAlgorithm function
-
-# Make it a directed network 
-# focus: writing, h index, 
-# model interpretation
-
-```
-
-# H-index webscraping
-
-Credits to Lucan for the code.
-
-```{r h-index, include=FALSE, eval= FALSE}
+```{r h-index}
 # Add h-index and i10-index columns to df_ego
-df_ego <- df_both_ego %>%
+df_ego <- df_ego %>%
   mutate(h_index = NA_real_, i10_index = NA_real_)
@@
 
+```
+
+# Quick RSiena
+
+```{r RSiena}
+#step1 data
+wave1 <- test$nets[1,,]
+wave2 <- test$nets[2,,]
+
+#put diagonals to zero 
+diag(wave1) <- 0
+diag(wave2) <- 0
+# we want a binary tie (not a weighted tie)
+wave1[wave1 > 1] <- 1
+wave2[wave2 > 1] <- 1
+```
+
+```{r RSiena2}
+# put the nets in an array
+net_array <- array(data = c(wave1, wave2), dim = c(dim(wave1), 2))
+#dependent
+nets <- sienaDependent(net_array)
+
+#put gender in object 
+gender <- df_ego$gender
 #covariate
-# h_index <- coCovar(df_ego$h_index)
+gender_RS <- coCovar(gender) # gender as covariate in Rsiena
+
+#put h-index in object 
+h_index <- df_ego$h_index
+df_ego$h_index
+#covarite 2
+h_index_RS <- coCovar(h_index) # h_index as covariate in RSiena
+
+#define data 
+mydata <- sienaDataCreate(nets, gender_RS, h_index_RS)
+
+#define effects structure 
+myeff <- getEffects(mydata)
+
+# skipped initial description part
+
+myeff <- includeEffects(myeff, isolateNet, inPop, outAct)
+
+myeff <- includeEffects(myeff, egoX, altX, sameX, interaction1 = "gender_RS")
+#include effect of h index later too etc
+#look up which effects to iclude
+
+myAlgorithm <- sienaAlgorithmCreate(modelType = c(nets=6), projname = "proProject")
+# undirected: model 6 "additive model", #check manual for this
+```
+
+```{r RSiena-model estimate}
+# estimate the model 
+model1 <- siena07(myAlgorithm, data = mydata, effects = myeff, returnDeps = TRUE)
+#latter needed for GOF
+
+model1
+
+# output:  convergence ration NA probably bc we chose all ties to be included (type = "all") earlier
+# we can go back and change that or change it here in the myAlgorithm function
+
+# Make it a directed network 
+# focus: writing, h index, 
+# model interpretation
+
 ```
@@
 # Plotting
-
 ```{r}
@@
 plot(test_w1,
-vertex.color = ifelse(df_ego$gender == 1, "red", "blue"), #now, I can use actor attributes for plotting.
+vertex.color = ifelse(df_ego$gender == 1, "red", "blue"), # now, I can use actor attributes for plotting.
 # here: if gender = 1 (aka man) then red dot, if not then blue 

### 2024-11-09 RSienatry.Rmd
restructuredprepdescriptivesandrsiena

--- 2024-11-08 revisitwithJochem.Rmd
@@
 ---
-title: "Plotting plots and Hotzenplotz"
+title: "RSienatry"
 author: "Verooo"
-date: "2024-11-05"
+date: "2024-11-08"
 output: html_document
 ---
-
 ```{r, globalsettings, echo=FALSE, warning=FALSE, results='hide'}
@@
 
-Meeting with Jochem
-
-look at publications website (sunbelt workshop)
-
 # Getting started
@@
 require(igraph)
+require(ggraph)
 
-require(ggraph)
 #install.packages('visNetwork')
@@
 
-# Gender
-
-## saving data for each deapartment
-
-```{r}
-#inspecting scholars_20240924.rda object
-#df_ego <- do.call(rbind.data.frame, scholars$demographics)
-#unique(df_ego$discipline.22)
-
-# save the output of your function
-testsoc  <- fcolnet(data = scholars, 
-                university = "RU", 
-                discipline = "sociology", 
-                waves = list(c(2015, 2018), c(2019, 2023)),
-
-                            type = c("first"))
-
-# I DONT KNOW HOW TO MAKE ALL SCHOLARS BE PART OF SAME FUNCTION ("sociology"+ "political science" does not work...)
-
-testpolsci <- fcolnet(data = scholars, 
-                university = "RU", 
-                discipline = "political science", 
-                waves = list(c(2015, 2018), c(2019, 2023)), 
-                type = c("first"))
-```
-
-#### soc department save
-
-```{r}
-soc_nets <- testsoc$nets
-
-df_ego_demo <- testsoc$data$demographics
-df_ego_oa <- testsoc$data$scholars_oa
-df_ego_works <- testsoc$data$works
-
-# DEMO
-  str(df_ego_demo, 1)
-
-  df_ego_demo <- do.call(rbind.data.frame, df_ego_demo)
-  df_ego_demo[[1]]
-
-# OA
-  #str(df_ego_oa, 1)
-  df_ego_oa[[1]]
-  df_ego_oa <- do.call(rbind.data.frame, df_ego_oa)
-
-  # --> EGO DATAFRAME with demo and oa (sociology)
-  ?join.data.frame
-  df_soc_ego <- left_join(df_ego_demo, df_ego_oa, by = join_by(au_id == id))
-
-  rownames(soc_nets[1,,]) == df_soc_ego$au_id # checking if the author id's are the same as in df_ego in nets dataframe 
-  # --> yes, the correct ones!!!
-
-  df_ego_works[[1]]$author 
-#authors of all the works that first scholar (here: Ana Macanovic) is part of
-
-```
-
-#### polsci department save
-
-```{r}
-# dependent
-# pol_net <- sienaDependent(net_pol_array)
-
-# dependent 
-pol_nets <- testpolsci$nets
-
-df_pol_ego_demo <- testpolsci$data$demographics
-df_pol_ego_oa <- testpolsci$data$scholars_oa
-df_pol_ego_works <- testpolsci$data$works
-
-# DEMO
-  #str(df_pol_ego_demo, 1)
-
-  df_pol_ego_demo <- do.call(rbind.data.frame, df_pol_ego_demo)
-  df_pol_ego_demo[[1]]
-
-# OA
-  #str(df_pol_ego_oa, 1)
-  df_pol_ego_oa[[1]]
-  df_pol_ego_oa <- do.call(rbind.data.frame, df_pol_ego_oa)
-
-# --> EGO DATAFRAME with demo and oa (political science)
-  df_pol_ego <- left_join(df_pol_ego_demo, df_pol_ego_oa, by = join_by(au_id == id))
-
-  rownames(pol_nets[1,,]) == df_pol_ego$au_id # checking if the author id's are the same as in df_ego in nets dataframe 
-  # --> yes, the correct ones!!!
-```
-
-### gender - sociology department
-
-```{r gender s}
-df_soc_ego$Naam # list of all names in sociology department
-
-df_soc_ego$gender <- c(0,1,0,1,0,0,1,1,0,0,
-                       0,1,1,0,1,0,1,1,1,1,
-                       0,1,1,0,1,1,0,1,0,1,
-                       0,1,0,0,0,0,0,0,1,0,
-                       0,1,1,1,0,1,0,1,0,0) 
-# manually filled in gender 0 = woman, 1 = man, based on majority given in NL voornamen bank
-
-# check if it went smoothly 
-# view(df_soc_ego[c('Naam', 'gender', 'au_id')])
-
-# fsave(df_soc_ego)
-
-```
-
-### gender - polsci
-
-```{r gender p}
-df_pol_ego$Naam # list of all names
-
-df_pol_ego$gender <- c(1,0,1,0,0,0,1,0,1,0,
-                       1,1,0,0,1,1,1,0,0,1,
-                       0,1,1,0,0,1,1,1,0,0,
-                       0,0,0,1,1,0,0,1,1,0,
-                       0,0,0,1,0,1,1,1,0,0,0) 
-    # manually filled in gender 0 = woman, 1 = man, based on majority given in NL voornamen bank, Guangyu was not in name bank but based on the employee-picture of RU, this person presents feminine, thus I assumed 0.
-
-# check if it went smoothly 
-# view(df_pol_ego[c('Naam', 'gender', 'au_id')])
-
-#covariate 
-# gender <- coCovar(df_ego$gender)
-
-# fsave(df_pol_ego)
-```
-
-### save gender data sets
-
-```{r gender data}
-soc_gender <- fload("./data/processed/df_soc_ego_20241105.rda")
-pol_gender <- fload("./data/processed/df_pol_ego_20241105.rda")
-```
-
-### Combine data (gender)
-
-```{r combine gender set}
-df <- test$data # make dataset with all data 
-df_ego <- do.call(rbind.data.frame, df$demographics) # data set with demographic information
-
-soc_gender <- soc_gender[,c("Naam", "gender")] # selecting only the content we need
-pol_gender <- pol_gender[,c("Naam", "gender")] # selecting only the content we need
-
-gender <- rbind(soc_gender, pol_gender) # combining the gender data sets
-
-df_ego <- df_ego %>% 
-            left_join(gender) #dcombining data set of gender with the one with demographic information 
-```
-
-# H-index 
-Credits to Lucan Bovens for the code.
-
-```{r h-index}
-# Add h-index and i10-index columns to df_ego
-df_ego <- df_ego %>%
-  mutate(h_index = NA_real_, i10_index = NA_real_)
-
-# Get H-index and i10-index 
-get_openalex_metrics <- function(openalex_id) {
-  url <- paste0("https://api.openalex.org/authors/", openalex_id)
-  author_data <- tryCatch({
-    jsonlite::fromJSON(url)
-  }, error = function(e) {
-    message(paste("Error fetching data for OpenAlex ID:", openalex_id))
-    return(NULL)
-  })
-
-  if (!is.null(author_data)) {
-    h_index <- author_data$summary_stats$h_index
-    i10_index <- author_data$summary_stats$i10_index
-    works_count <- author_data$works_count
-    cited_by_count <- author_data$cited_by_count
-    return(list(h_index = h_index, i10_index = i10_index, works_count = works_count, cited_by_count = cited_by_count))
-  } else {
-    return(list(h_index = NA, i10_index = NA, works_count = NA, cited_by_count = NA))
-  }
-}
-
-# Loop for each scholar 
-for (i in 1:nrow(df_ego)) {
-  openalex_id <- df_ego$au_id[i]  # assuming au_id is the OpenAlex ID in df_ego
-  metrics <- get_openalex_metrics(openalex_id)
-  df_ego$h_index[i] <- metrics$h_index
-  df_ego$i10_index[i] <- metrics$i10_index
-  df_ego$works_count[i] <- metrics$works_count
-  df_ego$cited_by_count[i] <- metrics$cited_by_count
-}
-
-# View updated df_ego with h-index and i10-index
-view(df_ego[c('au_id','Naam','gender','h_index','i10_index')])
-
-```
-
-# Quick RSiena
-
+## Step 1: Define data
 ```{r RSiena}
@@
 
-```{r RSiena2}
+```{r RSiena define 1}
 # put the nets in an array
@@
 nets <- sienaDependent(net_array)
+```
+
+```{r RSiena define 2}
+
+df_ego <- fload("./data/processed/df_ego_20241108.rda") #make sure to lead fload first ofcourse
 
@@
 
+```
+
+## Step 2: Make effects structure 
+```{r RSiena myeff}
 #define effects structure 
@@
 
-# skipped initial description part
+```
+
+## Step 3: initial description (skipped)
+Nothing for now. :)
+
+## Step 4: Specify model 
+```{r RSiena spec mod}
 
@@
 
-```{r RSiena-model estimate}
+## Step 5: Estimate model 
+```{r RSiena-model estimate, eval = FALSE}
 # estimate the model 
@@
 # Make it a directed network 
-# focus: writing, h index, 
+# focus: writing, 
 # model interpretation
@@
 ```
-
-# Plotting
-```{r}
-test_w1 <- igraph::graph_from_adjacency_matrix(
-  test$nets[1,,], # first wave of data. 
-  # (thus I select the array of networks and take the first matrix)
-  mode = c("directed"),
-  weighted = NULL,
-  diag = FALSE,
-  add.colnames = NULL,
-  add.rownames = NULL)
-
-plot(test_w1,
-     vertex.label = NA,
-     edge.width = 0.2,
-     edge.arrow.size =0.2)
-```
-
-```{r}
-names(df_ego) #see labels of variables
-
-plot(test_w1,
-vertex.color = ifelse(df_ego$gender == 1, "red", "blue"), # now, I can use actor attributes for plotting.
-# here: if gender = 1 (aka man) then red dot, if not then blue 
-vertex.label = NA,
-edge.width = 0.2,
-edge.arrow.size =0.2)
-
-# if you dont want plot to turn, save the layout (look at SNASS)
-```

### 2024-11-09 datapreptrynew.Rmd
restructuredprepdescriptivesandrsiena

--- 2024-11-08 revisitwithJochem.Rmd
@@
 ---
-title: "Plotting plots and Hotzenplotz"
+title: "datapreptrynew"
 author: "Verooo"
-date: "2024-11-05"
+date: "2024-11-08"
 output: html_document
@@
 ```
-
-Meeting with Jochem
-
-look at publications website (sunbelt workshop)
 
@@
 
+ note to self:look at publications website (sunbelt workshop)
+
 # Gender
 
-## saving data for each deapartment
+## saving data for each department 
+This part, despite being lengthy and principally unnecessary, needed to stay in my code for the sake of transparency.
+AFterall, this code is what accumulated in the gender-data of each department in my data set.
 
@@
                             type = c("first"))
-
-# I DONT KNOW HOW TO MAKE ALL SCHOLARS BE PART OF SAME FUNCTION ("sociology"+ "political science" does not work...)
 
@@
   # --> EGO DATAFRAME with demo and oa (sociology)
-  ?join.data.frame
+
   df_soc_ego <- left_join(df_ego_demo, df_ego_oa, by = join_by(au_id == id))
@@
 # H-index
+
 Credits to Lucan Bovens for the code.
@@
 
-```
-
-# Quick RSiena
-
-```{r RSiena}
-#step1 data
-wave1 <- test$nets[1,,]
-wave2 <- test$nets[2,,]
-
-#put diagonals to zero 
-diag(wave1) <- 0
-diag(wave2) <- 0
-# we want a binary tie (not a weighted tie)
-wave1[wave1 > 1] <- 1
-wave2[wave2 > 1] <- 1
-```
-
-```{r RSiena2}
-# put the nets in an array
-net_array <- array(data = c(wave1, wave2), dim = c(dim(wave1), 2))
-#dependent
-nets <- sienaDependent(net_array)
-
-#put gender in object 
-gender <- df_ego$gender
-#covariate
-gender_RS <- coCovar(gender) # gender as covariate in Rsiena
-
-#put h-index in object 
-h_index <- df_ego$h_index
-df_ego$h_index
-#covarite 2
-h_index_RS <- coCovar(h_index) # h_index as covariate in RSiena
-
-#define data 
-mydata <- sienaDataCreate(nets, gender_RS, h_index_RS)
-
-#define effects structure 
-myeff <- getEffects(mydata)
-
-# skipped initial description part
-
-myeff <- includeEffects(myeff, isolateNet, inPop, outAct)
-
-myeff <- includeEffects(myeff, egoX, altX, sameX, interaction1 = "gender_RS")
-#include effect of h index later too etc
-#look up which effects to iclude
-
-myAlgorithm <- sienaAlgorithmCreate(modelType = c(nets=6), projname = "proProject")
-# undirected: model 6 "additive model", #check manual for this
-```
-
-```{r RSiena-model estimate}
-# estimate the model 
-model1 <- siena07(myAlgorithm, data = mydata, effects = myeff, returnDeps = TRUE)
-#latter needed for GOF
-
-model1
-
-# output:  convergence ration NA probably bc we chose all ties to be included (type = "all") earlier
-# we can go back and change that or change it here in the myAlgorithm function
-
-# Make it a directed network 
-# focus: writing, h index, 
-# model interpretation
+# fsave(df_ego)
 
 ```
-
-# Plotting
-```{r}
-test_w1 <- igraph::graph_from_adjacency_matrix(
-  test$nets[1,,], # first wave of data. 
-  # (thus I select the array of networks and take the first matrix)
-  mode = c("directed"),
-  weighted = NULL,
-  diag = FALSE,
-  add.colnames = NULL,
-  add.rownames = NULL)
-
-plot(test_w1,
-     vertex.label = NA,
-     edge.width = 0.2,
-     edge.arrow.size =0.2)
-```
-
-```{r}
-names(df_ego) #see labels of variables
-
-plot(test_w1,
-vertex.color = ifelse(df_ego$gender == 1, "red", "blue"), # now, I can use actor attributes for plotting.
-# here: if gender = 1 (aka man) then red dot, if not then blue 
-vertex.label = NA,
-edge.width = 0.2,
-edge.arrow.size =0.2)
-
-# if you dont want plot to turn, save the layout (look at SNASS)
-```

### 2024-11-09 datapreptryold.Rmd
restructuredprepdescriptivesandrsiena

--- 2024-11-04 1definedata.Rmd
@@
 
-I do not seem to be able to call on the package RSiena, nor can I reinstall it.... I know programming never works on the first try but... goddamnit, why not even after 15?
-
 ## Functions
 
-### Question
+### (old) Question
 
@@
 
-#combining data: wish I knew of this shit earlier...
+#combining data: GODDAMNIT, I wish I knew of this shit earlier...
 # mydata <- sienaDataCreate(net, gender)

### 2024-11-09 descriptivestry.Rmd
restructuredprepdescriptivesandrsiena

--- 2024-11-07 revisitwithJochem.Rmd
@@
 ---
-title: "Plotting plots and Hotzenplotz"
+title: "Descriptive adventures"
 author: "Verooo"
-date: "2024-11-05"
+date: "2024-11-08"
 output: html_document
@@
 
-```{r data}
-scholars <- fload("./data/processed/scholars_20240924.rda") #make sure to lead fload first ofcourse
+Scholar
+
+```{r scholar data}
+scholars <- fload("./data/processed/scholars_20240924.rda") 
+#make sure to lead fload first of course
 ```
 
-```{r saving output}
+```{r saving schoalr output}
 # save the output of your function
@@
 # USE not all but first or last so the ties are directed from "perspective" of first author of the publications 
-# usually first most prestige
-
+# usually first author has most prestige
 ```
 
-# Gender
+Ego
 
-## saving data for each deapartment
-
-```{r}
-#inspecting scholars_20240924.rda object
-#df_ego <- do.call(rbind.data.frame, scholars$demographics)
-#unique(df_ego$discipline.22)
-
-# save the output of your function
-testsoc  <- fcolnet(data = scholars, 
-                university = "RU", 
-                discipline = "sociology", 
-                waves = list(c(2015, 2018), c(2019, 2023)),
-
-                            type = c("first"))
-
-# I DONT KNOW HOW TO MAKE ALL SCHOLARS BE PART OF SAME FUNCTION ("sociology"+ "political science" does not work...)
-
-testpolsci <- fcolnet(data = scholars, 
-                university = "RU", 
-                discipline = "political science", 
-                waves = list(c(2015, 2018), c(2019, 2023)), 
-                type = c("first"))
+```{r df_ego data}
+df_ego <- fload("./data/processed/df_ego_20241108.rda")
 ```
 
-#### soc department
+```{r matrix data ego}
 
-```{r}
-# # dependent
-# net <- sienaDependent(net_soc_array)
-
-# dependent ?
-# nets <- testsoc$nets
-
-df_ego_demo <- testsoc$data$demographics
-df_ego_oa <- testsoc$data$scholars_oa
-df_ego_works <- testsoc$data$works
-
-# DEMO
-  str(df_ego_demo, 1)
-
-  df_ego_demo <- do.call(rbind.data.frame, df_ego_demo)
-  df_ego_demo[[1]]
-
-# OA
-  #str(df_ego_oa, 1)
-  df_ego_oa[[1]]
-  df_ego_oa <- do.call(rbind.data.frame, df_ego_oa)
-
-  # --> EGO DATAFRAME with demo and oa (sociology)
-  ?join.data.frame
-  df_soc_ego <- left_join(df_ego_demo, df_ego_oa, by = join_by(au_id == id))
-
-  rownames(nets[1,,]) == df_soc_ego$au_id # checking if the author id's are the same as in df_ego in nets dataframe 
-  # --> yes, the correct ones!!!
-
-  df_ego_works[[1]]$author 
-#authors of all the works that first scholar (here: Ana Macanovic) is part of
-
-```
-
-#### polsci department
-
-```{r}
-# dependent
-# pol_net <- sienaDependent(net_pol_array)
-
-# dependent 
-pol_nets <- testpolsci$nets
-
-df_pol_ego_demo <- testpolsci$data$demographics
-df_pol_ego_oa <- testpolsci$data$scholars_oa
-df_pol_ego_works <- testpolsci$data$works
-
-# DEMO
-  str(df_pol_ego_demo, 1)
-
-  df_pol_ego_demo <- do.call(rbind.data.frame, df_pol_ego_demo)
-  df_pol_ego_demo[[1]]
-
-# OA
-  #str(df_pol_ego_oa, 1)
-  df_pol_ego_oa[[1]]
-  df_pol_ego_oa <- do.call(rbind.data.frame, df_pol_ego_oa)
-
-# --> EGO DATAFRAME with demo and oa (political science)
-  df_pol_ego <- left_join(df_pol_ego_demo, df_pol_ego_oa, by = join_by(au_id == id))
-
-  rownames(pol_nets[1,,]) == df_pol_ego$au_id # checking if the author id's are the same as in df_ego in nets dataframe 
-  # --> yes, the correct ones!!!
-```
-
-### gender-soc
-
-```{r gender s}
-df_soc_ego$Naam # list of all names in sociology department
-
-df_soc_ego$gender <- c(0,1,0,1,0,0,1,1,0,0,
-                       0,1,1,0,1,0,1,1,1,1,
-                       0,1,1,0,1,1,0,1,0,1,
-                       0,1,0,0,0,0,0,0,1,0,
-                       0,1,1,1,0,1,0,1,0,0) 
-# manually filled in gender 0 = woman, 1 = man, based on majority given in NL voornamen bank
-
-# check if it went smoothly 
-view(df_soc_ego[c('Naam', 'gender', 'au_id')])
-
-# fsave(df_soc_ego)
-
-```
-
-### gender - polsci
-
-```{r gender p}
-df_pol_ego$Naam # list of all names
-
-df_pol_ego$gender <- c(1,0,1,0,0,0,1,0,1,0,
-                       1,1,0,0,1,1,1,0,0,1,
-                       0,1,1,0,0,1,1,1,0,0,
-                       0,0,0,1,1,0,0,1,1,0,
-                       0,0,0,1,0,1,1,1,0,0,0) 
-    # manually filled in gender 0 = woman, 1 = man, based on majority given in NL voornamen bank, Guangyu was not in name bank but based on the employee-picture of RU, this person presents feminine, thus I assumed 0.
-
-# check if it went smoothly 
-view(df_pol_ego[c('Naam', 'gender', 'au_id')])
-
-#covariate 
-# gender <- coCovar(df_ego$gender)
-
-# fsave(df_pol_ego)
-```
-
-### save gender data sets
-
-```{r gender data}
-soc_gender <- fload("./data/processed/df_soc_ego_20241105.rda")
-pol_gender <- fload("./data/processed/df_pol_ego_20241105.rda")
-```
-
-### Combine data (gender)
-
-```{r combine gender set}
-df <- test$data
-df_ego <- do.call(rbind.data.frame, df$demographics)
-
-soc_gender <- soc_gender[,c("Naam", "gender")]
-pol_gender <- pol_gender[,c("Naam", "gender")]
-
-gender <- rbind(soc_gender, pol_gender) # combining data sets
-
-df_ego <- df_ego %>% 
-            left_join(gender) #dataset 
-```
-
-# Quick RSiena
-
-```{r RSiena}
-#step1 data
-wave1 <- test$nets[1,,]
-wave2 <- test$nets[2,,]
-
-#put diagonals to zero 
-diag(wave1) <- 0
-diag(wave2) <- 0
-# we want a binary tie (not a weighted tie)
-wave1[wave1 > 1] <- 1
-wave2[wave2 > 1] <- 1
-# put the nets in an array
-net_array <- array(data = c(wave1, wave2), dim = c(dim(wave1), 2))
-
-gender <- df_ego$gender
-
-#dependent
-nets <- sienaDependent(net_array)
-#covariate
-genderrs <- coCovar(gender)
-#define data 
-mydata <- sienaDataCreate(nets, genderrs)
-
-#define effects structure 
-myeff <- getEffects(mydata)
-
-#skipped description
-
-myeff <- includeEffects(myeff, isolateNet, inPop, outAct)
-
-myeff <- includeEffects(myeff, egoX, altX, sameX, interaction1 = "genderrs")
-
-#look up which effects to iclude
-
-myAlgorithm <- sienaAlgorithmCreate(modelType = c(nets=6), projname = "proProject")
-# undirected: model 6 "additive model", #check manual for this
-
-# estimate
-model1 <- siena07(myAlgorithm, data = mydata, effects = myeff, returnDeps = TRUE)
-#latter needed for GOF
-
-model1
-
-# output:  convergence ration NA probably bc we chose all ties to be included (type = "all") earlier
-# we can go back and change that or change it here in the myAlgorithm function
-
-# Make it a directed network 
-# focus: writing, h index, 
-# model interpretation
-
-```
-
-# H-index webscraping
-
-Credits to Lucan for the code.
-
-```{r h-index, include=FALSE, eval= FALSE}
-# Add h-index and i10-index columns to df_ego
-df_ego <- df_both_ego %>%
-  mutate(h_index = NA_real_, i10_index = NA_real_)
-
-# Get H-index and i10-index 
-get_openalex_metrics <- function(openalex_id) {
-  url <- paste0("https://api.openalex.org/authors/", openalex_id)
-  author_data <- tryCatch({
-    jsonlite::fromJSON(url)
-  }, error = function(e) {
-    message(paste("Error fetching data for OpenAlex ID:", openalex_id))
-    return(NULL)
-  })
-
-  if (!is.null(author_data)) {
-    h_index <- author_data$summary_stats$h_index
-    i10_index <- author_data$summary_stats$i10_index
-    works_count <- author_data$works_count
-    cited_by_count <- author_data$cited_by_count
-    return(list(h_index = h_index, i10_index = i10_index, works_count = works_count, cited_by_count = cited_by_count))
-  } else {
-    return(list(h_index = NA, i10_index = NA, works_count = NA, cited_by_count = NA))
-  }
-}
-
-# Loop for each scholar 
-for (i in 1:nrow(df_ego)) {
-  openalex_id <- df_ego$au_id[i]  # assuming au_id is the OpenAlex ID in df_ego
-  metrics <- get_openalex_metrics(openalex_id)
-  df_ego$h_index[i] <- metrics$h_index
-  df_ego$i10_index[i] <- metrics$i10_index
-  df_ego$works_count[i] <- metrics$works_count
-  df_ego$cited_by_count[i] <- metrics$cited_by_count
-}
-
-# View updated df_ego with h-index and i10-index
-view(df_ego[c('au_id','Naam','gender','h_index','i10_index')])
-
-#covariate 
-# h_index <- coCovar(df_ego$h_index)
-```
-
-# Plotting
-
-```{r}
 test_w1 <- igraph::graph_from_adjacency_matrix(
@@
 
+```
+
+# Descriptives
+
+## Ego level
+
+### Gender
+
+-   Gender
+
+    -   descriptives (mean etc.)
+
+```{r sum gender}
+summary(df_ego$gender)
+
+```
+
+    -   overall
+
+```{r hist gender}
+# Histogram of prestige scores for Wave 1  
+hist(df_ego$gender, breaks = , main = "Distribution of gender",     xlab = "Gender", ylab = "Frequency", col = "#B3DE69") # INSERT YEARS OF WAVE/TIME FRAME STILL
+```
+
+```         
+-   Gender per department
+```
+
+```{r gender per dep.}
+# STILL DO 
+```
+
+### h index
+
+```         
+-   descriptives (mean etc.)
+```
+
+```{r sum h index}
+summary(df_ego$h_index) 
+```
+
+```         
+- Overall  (INSERT YEARS STILL)
+```
+
+```{r hist h index}
+
+# Histogram of prestige scores for Wave 1 
+hist(df_ego$h_index, breaks = 30, main = "Distribution of H-Index from yearX to yearX",     xlab = "H Index", ylab = "Frequency", col = "#B3DE69") # INSERT YEARS OF WAVE/TIME FRAME STILL
+```
+
+```         
+-   H index per department
+```
+
+```{r h index per dep.}
+# STILL DO 
+```
+
+## Ego network
+
+### basic descriptives
+
+-   Nr. of nodes
+
+```{r nodes}
+vcount(test_w1)
+```
+
+-   Nr. of edges
+
+```{r edges}
+ecount(test_w1)
+```
+
+-   Dyad census
+
+    ```{r dyad cen}
+    # still do 
+    ```
+
+-   Triad-census
+
+    ```{r triad cen}
+    # still do 
+    ```
+
+-   edge-density
+
+    ```{r edge dens}
+    #still do 
+    ```
+
+### more indepth:
+
+-   reciprocity
+
+    ```{r recip}
+    #still do 
+    ```
+
+-   degree centrality / degreee?
+
+    ```{r degree}
+    # still do 
+    ```
+
+-   Betweenness centrality /betweenness?
+
+    ```{r betweenness}
+    #still do 
+    ```
+
+-   Clustering
+
+    ```{r clustering}
+    #still do 
+    ```
+
+## Network-level descriptives
+
+-   Density
+
+    ```{r density}
+    #still do 
+    ```
+
+-   Average path length
+
+    ```{r path length}
+    # still do 
+    ```
+
+-   Segregation
+
+    -   Mortons I
+    -   igraphs
+    -   ggraphs
+
+```{r plot}
+
 plot(test_w1,
@@
 
-```{r}
+```{r plot gender}
 names(df_ego) #see labels of variables
@@
 plot(test_w1,
-vertex.color = ifelse(df_ego$gender == 1, "red", "blue"), #now, I can use actor attributes for plotting.
+vertex.color = ifelse(df_ego$gender == 1, "#FB8072", "#80B1D3"), # now, I can use actor attributes for plotting.
+# here: if gender = 1 (aka man) then red dot, if not then blue 
 vertex.label = NA,
@@
 # if you dont want plot to turn, save the layout (look at SNASS)
+
 ```
+
+# Detour: Colors
+
+```{r mypalette, include = FALSE, eval = FALSE}
+# palette i like:
+palette("Set 3");  sinplot("Set 3")
+palette.swatch("Set 3")
+palette.colors(palette = "Set 3")
+ "#8DD3C7" "#FFFFB3" "#BEBADA" "#FB8072" "#80B1D3" "#FDB462"
+ "#B3DE69" "#FCCDE5" "#D9D9D9" "#BC80BD" "#CCEBC5" "#FFED6F"
+```
+
+```{r colors in R, include = FALSE, eval = FALSE}
+colors (distinct = TRUE) # prints all colors R knows
+palette.pals()
+#  [1] "R3"              "R4"              "ggplot2"        
+#  [4] "Okabe-Ito"       "Accent"          "Dark 2"         
+#  [7] "Paired"          "Pastel 1"        "Pastel 2"       
+# [10] "Set 1"           "Set 2"           "Set 3"          
+# [13] "Tableau 10"      "Classic Tableau" "Polychrome 36"  
+# [16] "Alphabet"
+
+palette.colors(palette = "-palette name here-")
+# [1] "#000000" "#E69F00" "#56B4E9" "#009E73" "#F0E442" "#0072B2"
+# [7] "#D55E00" "#CC79A7" "#999999"
+```
+
+```{r look at colors PLOT, include = FALSE, eval = FALSE}
+## Demonstrate the colors 1:8 in different palettes using a custom matplot()
+sinplot <- function(main=NULL, n = 8) {
+    x <- outer(
+	seq(-pi, pi, length.out = 50),
+	seq(  0, pi, length.out = n),
+	function(x, y) sin(x - y)
+    )
+    matplot(x, type = "l", lwd = 4, lty = 1, col = 1:n, ylab = "", main=main)
+}
+sinplot("default palette")
+
+palette("R3");        sinplot("R3")
+palette("Okabe-Ito"); sinplot("Okabe-Ito")
+palette("Tableau")  ; sinplot("Tableau", n = 10) # i like 
+palROB <- colorRampPalette(c("red", "darkorange2", "blue"), space = "Lab")
+palette(palROB(16)); sinplot("palROB(16)", n = 16) # the orange purple blue rainbow retro vibe yay 
+palette("default") # reset
+```
+
+```{r look at colors SWATCH, include = FALSE, eval = FALSE}
+palette.swatch <- function(palette = palette.pals(), n = 8, nrow = 8,
+                           border = "black", cex = 1, ...)
+{
+     cols <- sapply(palette, palette.colors, n = n, recycle = TRUE)
+     ncol <- ncol(cols)
+     nswatch <- min(ncol, nrow)
+     op <- par(mar = rep(0.1, 4),
+               mfrow = c(1, min(5, ceiling(ncol/nrow))),
+     	       cex = cex, ...)
+     on.exit(par(op))
+     while (length(palette)) {
+ 	subset <- seq_len(min(nrow, ncol(cols)))
+ 	plot.new()
+ 	plot.window(c(0, n), c(0.25, nrow + 0.25))
+ 	y <- rev(subset)
+ 	text(0, y + 0.1, palette[subset], adj = c(0, 0))
+ 	y <- rep(y, each = n)
+ 	rect(rep(0:(n-1), n), y, rep(1:n, n), y - 0.5,
+ 	     col = cols[, subset], border = border)
+ 	palette <- palette[-subset]
+ 	cols    <- cols [, -subset, drop = FALSE]
+     }
+}
+
+palette.swatch()
+
+palette.swatch(n = 26) # show full "Alphabet"; recycle most others
+
+```

### 2024-11-09 weekbacktrack.Rmd
restructuredprepdescriptivesandrsiena

@@
 
-+-----------------------------------------------------------------------------------------------+------------------------------------------------------------+---------------------------------------------------------------+--------------------------------------------------------------------------------------------+-----------------------------------------------------------------+---------------------------------------------------------------------------+---------------------------------------------------------+
++-----------------------------------------------------------------------------------------------+------------------------------------------------------------+---------------------------------------------------------------+--------------------------------------------------------------------------------------------+-----------------------------------------------------------------+---------------------------------------------------------------------------+---------------------------------------------------------------------+
 | Mon                                                                                           | Tue                                                        | Wed                                                           | Thu                                                                                        | Fri                                                             | Sat                                                                       | Sun                                                                 |
-+:==============================================================================================+:===========================================================+:==============================================================+:===========================================================================================+:================================================================+:==========================================================================+:========================================================+
++:==============================================================================================+:===========================================================+:==============================================================+:===========================================================================================+:================================================================+:==========================================================================+:====================================================================+
 | 28\.
@@
 |                                                                                               |                                                            |                                                               |                                                                                            | \* struggle with polsci data \*                                 |                                                                           |                                                                     |
-+-----------------------------------------------------------------------------------------------+------------------------------------------------------------+---------------------------------------------------------------+--------------------------------------------------------------------------------------------+-----------------------------------------------------------------+---------------------------------------------------------------------------+---------------------------------------------------------+
++-----------------------------------------------------------------------------------------------+------------------------------------------------------------+---------------------------------------------------------------+--------------------------------------------------------------------------------------------+-----------------------------------------------------------------+---------------------------------------------------------------------------+---------------------------------------------------------------------+
 | 04\.
@@
 |                                                                                               |                                                            |                                                               |                                                                                            |                                                                 |                                                                           |                                                                     |
-| ![](images/socialnetworking_meh.jpg){width="800"}\                                            | ![](images/used_arson%20frog.jpg){width="952"}[work]       | ![](images/used_arson%20frog.jpg)[university]                 | ![](images/socialnetworking_meh.jpg){width="800"}\                                         | ![](images/socialnetworking.jpg){width="800"}\                  | ![](images/socialnetworking.jpg){width="800"}rewrite intro and Theory [W] | ![](images/timetopanic.gif){width="800"}[Grandmas bday] |
-| fix package error,                                                                            |                                                            |                                                               | Read Jochems answer & revisit RQs                                                          | Initial description [S3]                                        |                                                                           |                                                         |
-|                                                                                               | Talk to Jochem                                             |                                                               |                                                                                            |                                                                 | Specify model [S4]                                                        |                                                         |
-| Define variables (get stuck with sienaDependent)                                              |                                                            |                                                               | & create effects structure [S2]                                                            | Plotting& Revisit RQs                                           |                                                                           |                                                         |
+| ![](images/socialnetworking_meh.jpg){width="800"}\                                            | ![](images/used_arson%20frog.jpg){width="952"}[work]       | ![](images/used_arson%20frog.jpg)[university]                 | ![](images/socialnetworking_meh.jpg){width="800"}\                                         | ![](images/socialnetworking.jpg){width="800"}\                  | ![](images/socialnetworking.jpg){width="800"}rewrite intro and Theory [W] | ![](images/timetopanic.gif){width="800"}[Grandmas bday celebration] |
+| fix package error,                                                                            |                                                            |                                                               | Read Jochems answer & revisit code                                                         | fix bugging webjournal                                          |                                                                           |                                                                     |
+|                                                                                               | Talk to Jochem                                             |                                                               |                                                                                            |                                                                 | read into specifying model [S4]                                           |                                                                     |
+| Define variables (get stuck with sienaDependent)                                              |                                                            |                                                               | & create effects structure [S2]                                                            | journal, make submenus                                          |                                                                           |                                                                     |
 |                                                                                               | [university]                                               |                                                               |                                                                                            |                                                                 |                                                                           |                                                                     |
-| check in with Jochem                                                                          |                                                            |                                                               | Plotting & revisit RQs                                                                     |                                                                 |                                                                           |                                                         |
+| check in with Jochem                                                                          |                                                            |                                                               | make h index                                                                               | Reorganize code                                                 |                                                                           |                                                                     |
 |                                                                                               |                                                            |                                                               |                                                                                            |                                                                 |                                                                           |                                                                     |
-| Plotting                                                                                      |                                                            |                                                               |                                                                                            |                                                                 |                                                                           |                                                         |
-+-----------------------------------------------------------------------------------------------+------------------------------------------------------------+---------------------------------------------------------------+--------------------------------------------------------------------------------------------+-----------------------------------------------------------------+---------------------------------------------------------------------------+---------------------------------------------------------+
+| Plotting                                                                                      |                                                            |                                                               |                                                                                            | Starting with initial description [S3]                          |                                                                           |                                                                     |
+|                                                                                               |                                                            |                                                               |                                                                                            |                                                                 |                                                                           |                                                                     |
+|                                                                                               |                                                            |                                                               |                                                                                            | Plotting                                                        |                                                                           |                                                                     |
++-----------------------------------------------------------------------------------------------+------------------------------------------------------------+---------------------------------------------------------------+--------------------------------------------------------------------------------------------+-----------------------------------------------------------------+---------------------------------------------------------------------------+---------------------------------------------------------------------+
 | 11\.
@@
 |                                                                                               |                                                            |                                                               |                                                                                            |                                                                 |                                                                           |                                                                     |
-| ![](images/socialnetworking_meh.jpg){width="800"}Data & methods part [W]                      | ![](images/used_arson%20frog.jpg){width="952"}[university] | ![](images/used_arson%20frog.jpg)[university]                 | ![](images/socialnetworking.jpg){width="800"}Data & methods part [W]\                      | ![](images/socialnetworking.jpg){width="800"}estimate model     | ![](images/socialnetworking.jpg){width="800"}goodness of fit [S6]         | ![](images/kermit-panic.gif)                            |
+| ![](images/socialnetworking_meh.jpg){width="800"}Write Data & methods part [W]                | ![](images/used_arson%20frog.jpg){width="952"}[university] | ![](images/used_arson%20frog.jpg)[university]                 | ![](images/socialnetworking.jpg){width="800"}Data & methods part [W]\                      | ![](images/socialnetworking.jpg){width="800"}estimate model     | ![](images/socialnetworking.jpg){width="800"}goodness of fit [S6]         | ![](images/kermit-panic.gif)                                        |
 |                                                                                               |                                                            |                                                               |                                                                                            |                                                                 |                                                                           |                                                                     |
-| Check in with Jochem                                                                          |                                                            |                                                               |                                                                                            | Plotting                                                        | Start Results [W]                                                         | [chores at home and university]                         |
-+-----------------------------------------------------------------------------------------------+------------------------------------------------------------+---------------------------------------------------------------+--------------------------------------------------------------------------------------------+-----------------------------------------------------------------+---------------------------------------------------------------------------+---------------------------------------------------------+
+| Check in with Jochem                                                                          |                                                            |                                                               |                                                                                            | goodness of fit                                                 | Start Results [W]                                                         | [chores at home and university]                                     |
++-----------------------------------------------------------------------------------------------+------------------------------------------------------------+---------------------------------------------------------------+--------------------------------------------------------------------------------------------+-----------------------------------------------------------------+---------------------------------------------------------------------------+---------------------------------------------------------------------+
 | 18\.
@@
 |                                                                     |
-+-----------------------------------------------------------------------------------------------+------------------------------------------------------------+---------------------------------------------------------------+--------------------------------------------------------------------------------------------+-----------------------------------------------------------------+---------------------------------------------------------------------------+---------------------------------------------------------+
++-----------------------------------------------------------------------------------------------+------------------------------------------------------------+---------------------------------------------------------------+--------------------------------------------------------------------------------------------+-----------------------------------------------------------------+---------------------------------------------------------------------------+---------------------------------------------------------------------+
 

### 2024-11-11 draftdata.Rmd
pushrestructuresubmenudata

@@
 
+        ```         
         -   From Lucan: "The h-index namely measures an author’s prestige by calculating the number of publications that have been cited at least as many times as the total number of their publications.
 As explained by the creator of the h-index, ” A scientist has index h if h of his or her Np papers have at least h citations each and the other (Np - h) papers have ≤h citations each” (@Hirsch2005) "
+        ```
 
@@
 
-```{=html}
 <!-- -->
-```
+
 -   Code for this was provided by a fellow course mate, namely Lucan Bovens
@@
 Some examples are presented, e.g., in van de Bunt (1999); van de Bunt, van Duijn, and Snijders (1999); and van Duijn, Zeggelink, Stokman, and Wasseur (2003); and Steglich, Snijders, and West (2006).
-A website for SIENA is maintained at http://www.stats.ox.ac.uk/\~snijders/siena/ .
+A website for SIENA is maintained at [http://www.stats.ox.ac.uk/\\\~snijders/siena/](http://www.stats.ox.ac.uk/\~snijders/siena/){.uri} .
 At this website (‘publications’ tab) you shall also find references to introductions in various other languages.
 This is a provisional manual for SIENA version 4.0, which is also called RSiena.
-This is a contributed package for the R statistical system which can be downloaded from http://cran.r-project.org.
+This is a contributed package for the R statistical system which can be downloaded from <http://cran.r-project.org>.
 For the operation of R, the reader is referred to the corresponding manual.

### 2024-11-11 revisitwithJochem.Rmd
pushrestructuresubmenudata

@@
 
-## saving data for each deapartment
+## saving data for each department 
+This part, despite being lengthy and principally unnecessary, needed to stay in my code for the sake of transparency.
+AFterall, this code is what accumulated in the gender-data of each department in my data set.
 
@@
 
+# fsave(df_ego)
+
 ```
@@
 
+## Step 1: Define data
 ```{r RSiena}
@@
 
-```{r RSiena2}
+```{r RSiena define}
 # put the nets in an array
@@
 
+## Step 5: Estimate model 
 ```{r RSiena-model estimate}
@@
 
-model1
+# model1   #remove the comment to run model!!!!!
 

### 2024-11-11 weekbacktrack.Rmd
weekbacktrackupdate111124

@@
 
-+-----------------------------------------------------------------------------------------------+------------------------------------------------------------+---------------------------------------------------------------+--------------------------------------------------------------------------------------------+-----------------------------------------------------------------+---------------------------------------------------------------------------+---------------------------------------------------------------------+
++---------------------------------------------------------------------------------------------------+--------------------------------------------------------------+-----------------------------------------------------------------+--------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------+----------------------------------------------------------------------------+--------------------------------------------------------------------------+
 | Mon                                                                                               | Tue                                                          | Wed                                                             | Thu                                                                                        | Fri                                                                           | Sat                                                                        | Sun                                                                      |
-+:==============================================================================================+:===========================================================+:==============================================================+:===========================================================================================+:================================================================+:==========================================================================+:====================================================================+
++:==================================================================================================+:=============================================================+:================================================================+:===========================================================================================+:==============================================================================+:===========================================================================+:=========================================================================+
 | 28\.
@@
 | 31\.
-| 01.11.
-| 02\.
+| **01.11.**                                                                    | 02\.
 | 03\.
@@
 |                                                                                                   |                                                              |                                                                 |                                                                                            |                                                                               |                                                                            |                                                                          |
-| ![](images/used_arson%20frog.jpg)                                                             | ![](images/used_arson%20frog.jpg){width="952"}             | ![](images/socialnetworking.jpg){width="800"}Clarify RQs [D]\ | ![](images/socialnetworking_meh.jpg){width="800"}Rework schedule [according Jochems input] | ![](images/socialnetworking.jpg){width="800"}\                  | ![](images/timetopanic.gif){width="800"}[chores at home, depression day]  | ![](images/socialnetworking_meh.jpg)Get polSci data,                |
+| ![](images/used_arson%20frog.jpg)                                                                 | ![](images/used_arson%20frog.jpg){width="952"}               | ![](images/socialnetworking.jpg){width="800"}Clarify RQs [D]\   | ![](images/socialnetworking_meh.jpg){width="800"}Rework schedule [according Jochems input] | ![](images/socialnetworking.jpg){width="800"}\                                | ![](images/timetopanic.gif){width="800"}*[chores at home, depression day]* | ![](images/socialnetworking_meh.jpg)Get polSci data,                     |
 |                                                                                                   |                                                              | [Asked Jochem for input]                                        |                                                                                            | Clarify [D]\                                                                  |                                                                            |                                                                          |
@@
 |                                                                                                   |                                                              |                                                                 |                                                                                            | \* struggle with polsci data \*                                               |                                                                            |                                                                          |
-+-----------------------------------------------------------------------------------------------+------------------------------------------------------------+---------------------------------------------------------------+--------------------------------------------------------------------------------------------+-----------------------------------------------------------------+---------------------------------------------------------------------------+---------------------------------------------------------------------+
++---------------------------------------------------------------------------------------------------+--------------------------------------------------------------+-----------------------------------------------------------------+--------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------+----------------------------------------------------------------------------+--------------------------------------------------------------------------+
 | 04\.
@@
 |                                                                                                   |                                                              |                                                                 |                                                                                            |                                                                               |                                                                            |                                                                          |
-| ![](images/socialnetworking_meh.jpg){width="800"}\                                            | ![](images/used_arson%20frog.jpg){width="952"}[work]       | ![](images/used_arson%20frog.jpg)[university]                 | ![](images/socialnetworking_meh.jpg){width="800"}\                                         | ![](images/socialnetworking.jpg){width="800"}\                  | ![](images/socialnetworking.jpg){width="800"}rewrite intro and Theory [W] | ![](images/timetopanic.gif){width="800"}[Grandmas bday celebration] |
+| ![](images/socialnetworking_meh.jpg){width="800"}\                                                | ![](images/used_arson%20frog.jpg){width="952"}*[work]*       | ![](images/used_arson%20frog.jpg)*[university]*                 | ![](images/socialnetworking_meh.jpg){width="800"}\                                         | ![](images/socialnetworking.jpg){width="800"}\                                | ![](images/kermit-panic.gif){width="800"}*[personal circumstances]*        | ![](images/timetopanic.gif){width="800"}*[Grandmas bday celebration]*    |
 | fix package error,                                                                                |                                                              |                                                                 | Read Jochems answer & revisit code                                                         | fix bugging webjournal                                                        |                                                                            |                                                                          |
-|                                                                                               | Talk to Jochem                                             |                                                               |                                                                                            |                                                                 | read into specifying model [S4]                                           |                                                                     |
-| Define variables (get stuck with sienaDependent)                                              |                                                            |                                                               | & create effects structure [S2]                                                            | journal, make submenus                                          |                                                                           |                                                                     |
+|                                                                                                   | Talk to Jochem                                               |                                                                 |                                                                                            |                                                                               |                                                                            |                                                                          |
+| Define variables (get stuck with sienaDependent)                                                  |                                                              |                                                                 | make h index                                                                               | journal, make submenus                                                        |                                                                            |                                                                          |
 |                                                                                                   | [university]                                                 |                                                                 |                                                                                            |                                                                               |                                                                            |                                                                          |
-| check in with Jochem                                                                          |                                                            |                                                               | make h index                                                                               | Reorganize code                                                 |                                                                           |                                                                     |
+| check in with Jochem                                                                              |                                                              |                                                                 |                                                                                            | Restructure code                                                              |                                                                            |                                                                          |
 |                                                                                                   |                                                              |                                                                 |                                                                                            |                                                                               |                                                                            |                                                                          |
@@
 |                                                                                                   |                                                              |                                                                 |                                                                                            | Plotting                                                                      |                                                                            |                                                                          |
-+-----------------------------------------------------------------------------------------------+------------------------------------------------------------+---------------------------------------------------------------+--------------------------------------------------------------------------------------------+-----------------------------------------------------------------+---------------------------------------------------------------------------+---------------------------------------------------------------------+
++---------------------------------------------------------------------------------------------------+--------------------------------------------------------------+-----------------------------------------------------------------+--------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------+----------------------------------------------------------------------------+--------------------------------------------------------------------------+
 | 11\.
@@
 |                                                                                                   |                                                              |                                                                 |                                                                                            |                                                                               |                                                                            |                                                                          |
-| ![](images/socialnetworking_meh.jpg){width="800"}Write Data & methods part [W]                | ![](images/used_arson%20frog.jpg){width="952"}[university] | ![](images/used_arson%20frog.jpg)[university]                 | ![](images/socialnetworking.jpg){width="800"}Data & methods part [W]\                      | ![](images/socialnetworking.jpg){width="800"}estimate model     | ![](images/socialnetworking.jpg){width="800"}goodness of fit [S6]         | ![](images/kermit-panic.gif)                                        |
+| ![](images/socialnetworking_meh.jpg){width="800"}Check in with Jochem                             | ![](images/used_arson%20frog.jpg){width="952"}*[university]* | ![](images/used_arson%20frog.jpg)*[university]*                 | ![](images/socialnetworking.jpg){width="800"}Continue description & plotting [S3]          | ![](images/socialnetworking.jpg){width="800"}Write theory [W]                 | ![](images/socialnetworking.jpg){width="800"}goodness of fit [S6]          | ![](images/timetopanic.gif)*[chores at home and university]*             |
 |                                                                                                   |                                                              |                                                                 |                                                                                            |                                                                               |                                                                            |                                                                          |
-| Check in with Jochem                                                                          |                                                            |                                                               |                                                                                            | goodness of fit                                                 | Start Results [W]                                                         | [chores at home and university]                                     |
-+-----------------------------------------------------------------------------------------------+------------------------------------------------------------+---------------------------------------------------------------+--------------------------------------------------------------------------------------------+-----------------------------------------------------------------+---------------------------------------------------------------------------+---------------------------------------------------------------------+
+| Continue description & plotting [S3]                                                              |                                                              |                                                                 | Data & methods part [W]                                                                    | estimate model [S5]                                                           | Start Results [W]                                                          |                                                                          |
+|                                                                                                   |                                                              |                                                                 |                                                                                            |                                                                               |                                                                            |                                                                          |
+|                                                                                                   |                                                              |                                                                 | Write introduction and theory [W]                                                          | goodness of fit [S6]                                                          |                                                                            |                                                                          |
++---------------------------------------------------------------------------------------------------+--------------------------------------------------------------+-----------------------------------------------------------------+--------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------+----------------------------------------------------------------------------+--------------------------------------------------------------------------+
 | 18\.
@@
 |                                                                                                   |                                                              |                                                                 |                                                                                            |                                                                               |                                                                            |                                                                          |
-| ![](images/used_arson%20frog.jpg)[Research project course starts: little time to work on SNA] | ![](images/used_arson%20frog.jpg){width="952"}[university] | ![](images/used_arson%20frog.jpg)[university]                 | ![](images/socialnetworking_meh.jpg){width="800"}Results [W]                               | ![](images/socialnetworking.jpg){width="800"}Finish Results [W] | ![](images/socialnetworking.jpg){width="800"}Discussion & conclusion [W]  |                                                                     |
+| ![](images/socialnetworking_meh.jpg){width="800"}*[RP course starts: little time to work on SNA]* | ![](images/used_arson%20frog.jpg){width="952"}*[university]* | ![](images/used_arson%20frog.jpg)*[university]*                 | ![](images/socialnetworking_meh.jpg){width="800"}*[LOW capacities]*                        | ![](images/socialnetworking_meh.jpg)*[LOW capacities]*                        | ![](images/socialnetworking.jpg){width="800"}Discussion & conclusion [W]   | ![](images/socialnetworking_meh.jpg)*[chores at home, mental breakdown]* |
 |                                                                                                   |                                                              |                                                                 |                                                                                            |                                                                               |                                                                            |                                                                          |
-| Check in with Jochem?
-|                                                            |                                                               |                                                                                            | Discussion & conclusion [W]                                     | ![](images/kermit-panic.gif){width="500"}Format project website& hand in!
-|                                                                     |
-+-----------------------------------------------------------------------------------------------+------------------------------------------------------------+---------------------------------------------------------------+--------------------------------------------------------------------------------------------+-----------------------------------------------------------------+---------------------------------------------------------------------------+---------------------------------------------------------------------+
+| Check in with Jochem                                                                              |                                                              |                                                                 | Results [W]                                                                                | Finish Results [W]                                                            |                                                                            | Rework intro [W]                                                         |
++---------------------------------------------------------------------------------------------------+--------------------------------------------------------------+-----------------------------------------------------------------+--------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------+----------------------------------------------------------------------------+--------------------------------------------------------------------------+
+| 25\.
+| 26\.
+| 27\.
+| 28\.
+| 29\.
+| 30\.
+| **1.12.**                                                                |
+|                                                                                                   |                                                              |                                                                 |                                                                                            |                                                                               |                                                                            |                                                                          |
+| ![](images/socialnetworking.jpg){width="800"}Discussion & conclusion [W]                          | ![](images/used_arson frog.jpg)*[university]*                | ![](images/socialnetworking_meh.jpg){width="800"}*[university]* | ![](images/socialnetworking_meh.jpg){width="800"}[*work, bc I don't want to get fired]*    | ![](images/socialnetworking_meh.jpg)*[university]*                            | *[Catch up on uni]*                                                        | *[Catch up on uni]*                                                      |
+|                                                                                                   |                                                              |                                                                 |                                                                                            |                                                                               |                                                                            |                                                                          |
+|                                                                                                   |                                                              | Discussion & conclusion [W]                                     | Finish discussion & conclusion [W]                                                         | ![](images/kermit-panic.gif){width="800"}**Format project website& hand in!** |                                                                            |                                                                          |
++---------------------------------------------------------------------------------------------------+--------------------------------------------------------------+-----------------------------------------------------------------+--------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------+----------------------------------------------------------------------------+--------------------------------------------------------------------------+
 

### 2024-11-12 descriptivestry.Rmd
prettyplotsindescriptives

@@
 df_ego <- fload("./data/processed/df_ego_20241108.rda")
+
 ```
@@
 
-    -   descriptives (mean etc.)
+    -   descriptives (mean etc.) in whole sample
 
@@
 summary(df_ego$gender)
-
 ```
 
-    -   overall
+    - gender counts across whole sample (0 = female, 1 = male)
+
+```{r counts gender-all}
+table(df_ego$gender)
+```
+
+    -   overall gender distribution in sample
 
@@
 # Histogram of prestige scores for Wave 1  
-hist(df_ego$gender, breaks = , main = "Distribution of gender",     xlab = "Gender", ylab = "Frequency", col = "#B3DE69") # INSERT YEARS OF WAVE/TIME FRAME STILL
+hist(df_ego$gender, breaks = 2, main = "Distribution of gender",     xlab = "Gender", ylab = "Frequency", col = "#B3DE69") # INSERT YEARS OF WAVE/TIME FRAME STILL
 ```
 
-```         
--   Gender per department
-```
+    -   Genders per department (0 = female, 1 = male)
 
 ```{r gender per dep.}
-# STILL DO 
+
+# Wave 1: Gender count per department 
+table(df_ego$discipline.24, df_ego$gender)
 ```
@@
 
-```         
     -   descriptives (mean etc.)
-```
-
-```{r sum h index}
+```{r summary h index}
 summary(df_ego$h_index)
 ```
-
-```         
     - Overall  (INSERT YEARS STILL)
-```
 
 ```{r hist h index}
-
 # Histogram of prestige scores for Wave 1 
@@
 
-```         
     -   H index per department
-```
 
-```{r h index per dep.}
-# STILL DO 
+```{r table per dep h index}
+# Wave 1: Prestige distribution by dep. and total
+df_ego %>%
+    group_by(discipline.24) %>%
+    summarise(mean_h_index = mean(h_index, na.rm = TRUE), min_h_index = min(h_index,
+        na.rm = TRUE), max_h_index = max(h_index, na.rm = TRUE), sd_h_index = sd(h_index,
+        na.rm = TRUE)) %>%
+    bind_rows(df_ego %>%
+        summarise(discipline.24 = "total", mean_h_index = mean(h_index, na.rm = TRUE), min_h_index = min(h_index,
+            na.rm = TRUE), max_h_index = max(h_index, na.rm = TRUE), sd_h_index = sd(h_index,
+            na.rm = TRUE)))
 ```
@@
     ```{r dyad cen}
-    # still do 
+
+igraph::dyad_census(test_w1)
     ```
@@
     ```{r triad cen}
-    # still do 
+igraph::triad_census(test_w1)
     ```
@@
     ```{r edge dens}
-    #still do 
+# edge density
+igraph::edge_density(test_w1)
     ```
@@
     ```{r recip}
-    #still do 
+reciprocity(test_w1, ignore.loops = TRUE, mode = c("default", "ratio"))
     ```
+reciprocity = 1 makes sense since the ties are undirected rn
 
@@
     ```{r degree}
-    # still do 
+
+degree_testw1 <- degree(test_w1)
+degree_testw1 <- as.data.frame(degree_testw1)
+ggplot(degree_testw1, aes(as.numeric(degree_testw1), colour = as.numeric(degree_testw1) )) +
+  geom_histogram(binwidth = .9) +
+  labs(
+    title = "Distribution Degrees Wave 1",
+    x = "Distribution of Degrees",
+    y = "Count"  ) +
+  ylim(0, 65)
+
     ```
@@
     ```{r betweenness}
-    #still do 
+betweenness_w1 <- igraph::betweenness(test_w1, directed = T)
+betweenness_w1 <- as.data.frame(betweenness_w1)
+ggplot(betweenness_w1, aes(as.numeric(betweenness_w1), colour = as.numeric(betweenness_w1))) +
+  geom_histogram(binwidth = 1.2) +
+  labs(
+    title = "Distribution Betweenness Wave 1",
+    x = "Distribution of Betweenness",
+    y = "Count")
+
     ```
@@
     ```{r clustering}
-    #still do 
+#clustering w1
+clustering_w1 <- igraph::transitivity(test_w1, type = "local")
+clustering_w1 <- as.data.frame(clustering_w1)
+ggplot(clustering_w1, aes(as.numeric(clustering_w1), colour = as.numeric(clustering_w1) )) +
+  geom_histogram(binwidth = .05) +
+  labs(
+    title = "Distribution Clustering Wave 1",
+    x = "Distribution of Clustering",
+    y = "Count" )
     ```
@@
     ```{r density}
-    #still do 
+density_w1 <- igraph::edge_density(test_w1)
+density_w1
     ```
@@
     ```{r path length}
-    # still do 
+mean((ego_size(test_w1, order = 2, mode = "out") - 1)/vcount(test_w1))
     ```
@@
 
+### Plotting: Gender 
+#### with isolates
 ```{r plot gender}
-names(df_ego) #see labels of variables
+# names(df_ego) #see labels of variables
 
 plot(test_w1,
-vertex.color = ifelse(df_ego$gender == 1, "#FB8072", "#80B1D3"), # now, I can use actor attributes for plotting.
+     vertex.color = ifelse(df_ego$gender == 1, "#FFED6F", "#80B1D3"), # now, I can use actor attributes for plotting.
 # here: if gender = 1 (aka man) then red dot, if not then blue 
   vertex.label = NA,
-edge.width = 0.2,
-edge.arrow.size =0.2)
+  vertex.size = 7.5,
+  edge.width = 0.5,
+  edge.arrow.size = 0.1,
+  main = "Network with isolates [yellow = female, blue = male]")
 
 # if you dont want plot to turn, save the layout (look at SNASS)
+```
+
+#### without isolates
+```{r removing isolates}
+indegr_w1 <- igraph::degree(test_w1, mode = "in")
+
+isolates_w1 <- V(test_w1)[degree(test_w1, mode = "all") == 0]
+
+noisolates_w1 <- delete_vertices(test_w1, isolates_w1)
+
+gsize(noisolates_w1) # edges
+
+gorder(noisolates_w1) # vertices
+```
+
+```{r plot wo isolates}
+plot(noisolates_w1,
+  vertex.color = ifelse(df_ego$gender == 1, "#80B1D3", "#FFED6F"), # now, I can use actor attributes for plotting.
+  # here: if gender = 1 (aka man) then red dot, if not then blue 
+  vertex.label = NA,
+  vertex.size = 9,
+  vertex.frame.color = "black",
+  edge.curved = 0.2,
+  edge.arrow.size = 0.3,
+  edge.color = "gray",
+  edge.width = 0.2,
+  main = "Network without isolates [yellow = female, blue = male]")
+```
+
+### Plotting: h-index -ggraph
+Credits to Hannah Groennou for the basis of the code of these graphs. 
+#### with isolates ?
+```{r}
+
+indegr_w1 <- degree(test_w1, mode = "in")
+
+# assign h-index to scholar
+V(test_w1)$h_index <- df_ego$h_index
+V(test_w1)$indegree <- indegr_w1
+
+#set size of plot
+options(repr.plot.width = 15, repr.plot.height = 18)
+
+#plot wave 1 with isolates
+p_iso <- ggraph(test_w1,
+       layout = "fr") +
+  geom_edge_link(color = "#BEBADA", width = 0.5) +
+  geom_node_point(aes(size = indegree, color = h_index)) + 
+  scale_size(range = c(3, 10)) + 
+  scale_color_gradient(low = "red", high = "blue") + 
+  theme_void()
+
+p_iso + labs(title = "Network with isolates",
+        subtitle = "Plot of indegree and H-index",
+        caption = "Data refer to: Scholars RU sociology and political science departments") + theme(plot.title = element_text(hjust = 0.5, face = "bold"), plot.subtitle = element_text(hjust=0.5), plot.caption = element_text(hjust = 1))
+```
+
+#### without isolates
+```{r}
+
+indegr_w1 <- degree(test_w1, mode = "in")
+
+# assign h-index to scholar
+V(test_w1)$h_index <- df_ego$h_index
+V(test_w1)$indegree <- indegr_w1
+
+#remove isolates
+noisolates_w1 <- delete_vertices(test_w1, V(test_w1)[degree(test_w1) == 0])
+
+#set size of plot
+options(repr.plot.width = 15, repr.plot.height = 15)
+
+#plot wave 1 without isolates 
+p_noiso <- ggraph(noisolates_w1,
+       layout = "fr") +
+  geom_edge_link(color = "#BEBADA", width = 0.7) +
+  geom_node_point(aes(size = indegree, color = h_index)) + 
+  scale_size(range = c(3, 10)) + 
+  scale_color_gradient(low = "red", high = "blue") + 
+  theme_void()
+
+p_noiso + labs(title = "Network without isolates",
+        subtitle = "Plot of indegree and H-index",
+        caption = "Data refer to: Scholars RU sociology and political science departments") + theme(plot.title = element_text(hjust = 0.5, face = "bold"), plot.subtitle = element_text(hjust=0.5))
+
+# allowed values for the font face include: “plain”, “italic”, “bold” and “bold.italic”.
+
+```
+
+##### H-index per department
+```{r}
+indegr_w1 <- degree(test_w1, mode = "in")
+
+# assign h-index to scholar
+V(test_w1)$h_index <- df_ego$h_index
+# assign discipline to scholar
+V(test_w1)$discipline <- df_ego$discipline.24
+
+V(test_w1)$indegree <- indegr_w1
+
+#remove isolates
+noisolates_w1 <- delete_vertices(test_w1, V(test_w1)[degree(test_w1) == 0])
+
+#set size of plot
+options(repr.plot.width = 15, repr.plot.height = 15)
+
+#plot wave 1 without isolates 
+p_noiso <- ggraph(noisolates_w1,
+       layout = "fr") +
+  geom_edge_link(color = "#BEBADA", width = 0.7) +
+  geom_node_point(aes(size = indegree, color = h_index, shape = as.factor(discipline))) + 
+  scale_size(range = c(3, 10)) + 
+  scale_color_gradient(low = "red", high = "blue") + 
+  theme_void()
+
+p_noiso + labs(title = "Departments without isolates",
+        subtitle = "Plot of indegree and H-index",
+        caption = "Data refer to scholars from Radboud University.") + theme(plot.title = element_text(hjust = 0.5, face = "bold"), plot.subtitle = element_text(hjust=0.5))
+
+# allowed values for the font face include: “plain”, “italic”, “bold” and “bold.italic”.
+
+```
+
+### Plotting gender - ggraph 
+#### with isolates per department 
+```{r}
+#assign gender to scholar 
+V(test_w1)$gender <- df_ego$gender
+
+# assign discipline to scholar
+V(test_w1)$discipline <- df_ego$discipline.24
+
+V(test_w1)$indegree <- indegr_w1
+
+p_gender <- ggraph(test_w1,
+  layout = "fr") +
+  geom_edge_link(color = "#BEBADA", width = 0.5) +
+  geom_node_point(aes(size = indegree, color = as.factor(discipline), shape = as.factor(gender))) +   
+  scale_size(range = c(3, 10)) + 
+  theme_void()
+
+p_gender + labs(title = "Departments with isolates",
+        subtitle = "Plot of indegree and gender",
+        caption = "Gender: 0 = female, 1 = male.\n Data refer to scholars from Radboud University.") + theme(plot.title = element_text(hjust = 0.5, face = "bold"), plot.subtitle = element_text(hjust=0.5), plot.caption = element_text(hjust = 1))
+
+```
+
+#### without isolates per department 
+```{r}
+#assign gender to scholar 
+V(test_w1)$gender <- df_ego$gender
+
+# assign disciplines to scholars
+V(test_w1)$discipline <- df_ego$discipline.24
+V(test_w1)$indegree <- indegr_w1
+
+#remove isolates
+noisolates_w1 <- delete_vertices(test_w1, V(test_w1)[degree(test_w1) == 0])
+
+p_noisgender <- ggraph(noisolates_w1,
+  layout = "fr") +
+  geom_edge_link(color = "#BEBADA", width = 0.5) +
+  geom_node_point(aes(size = indegree, color = as.factor(discipline), shape = as.factor(gender))) +   
+  scale_size(range = c(3, 10)) + 
+  theme_void()
+
+p_noisgender + labs(title = "Departments with isolates",
+        subtitle = "Plot of indegree and gender",
+        caption = "Gender: 0 = female, 1 = male.\n Data refer to scholars from Radboud University.") + theme(plot.title = element_text(hjust = 0.5, face = "bold"), plot.subtitle = element_text(hjust=0.5), plot.caption = element_text(hjust = 1))
+
+```
+
+### Plotting h index and gender -ggraph
+#### with isolates 
+```{r}
+#assign gender to scholar 
+V(test_w1)$gender <- df_ego$gender
+# V(test_w1)$gender <- ifelse(df_ego$gender >= 0.5,1,0)
+
+# assign h-index to scholar
+V(test_w1)$h_index <- df_ego$h_index
+V(test_w1)$indegree <- indegr_w1
+
+p_gender <- ggraph(test_w1,
+  layout = "fr") +
+  geom_edge_link(color = "#BEBADA", width = 0.5) +
+  geom_node_point(aes(size = indegree, color = h_index, shape = as.factor(gender))) +   
+  scale_size(range = c(3, 10)) + 
+  scale_color_gradient(low = "red", high = "blue") + 
+  theme_void()
+
+p_gender + labs(title = "Network with isolates",
+        subtitle = "Plot of indegree, H-index and gender",
+        caption = "Gender: 0 = female, 1 = male.\n Data refer to: Scholars RU sociology and political science departments.") + theme(plot.title = element_text(hjust = 0.5, face = "bold"), plot.subtitle = element_text(hjust=0.5), plot.caption = element_text(hjust = 1))
+
+```
+#### without isolates 
+```{r gen without iso}
+#assign gender to scholar 
+V(test_w1)$gender <- df_ego$gender
+
+# assign h-index to scholar
+V(test_w1)$h_index <- df_ego$h_index
+V(test_w1)$indegree <- indegr_w1
+
+#remove isolates
+noisolates_w1 <- delete_vertices(test_w1, V(test_w1)[degree(test_w1) == 0])
+
+p_noisogender <- ggraph(noisolates_w1,
+  layout = "fr") +
+  geom_edge_link(color = "#BEBADA", width = 0.5) +
+  geom_node_point(aes(size = indegree, color = h_index, shape = as.factor(gender))) +   
+  scale_size(range = c(3, 10)) + 
+  scale_color_gradient(low = "red", high = "blue") + 
+  theme_void()
+
+p_noisogender + labs(title = "Network without isolates",
+        subtitle = "Plot of indegree, H-index and gender",
+        caption = "Gender: 0 = female, 1 = male.\n Data refer to: Scholars RU sociology and political science departments.") + theme(plot.title = element_text(hjust = 0.5, face = "bold"), plot.subtitle = element_text(hjust=0.5))
 

### 2024-11-12 weekbacktrack.Rmd
prettyplotsindescriptives

@@
 |                                                                                                   |                                                              |                                                                 |                                                                                            |                                                                               |                                                                            |                                                                          |
-| ![](images/socialnetworking.jpg){width="800"}Discussion & conclusion [W]                          | ![](images/used_arson frog.jpg)*[university]*                | ![](images/socialnetworking_meh.jpg){width="800"}*[university]* | ![](images/socialnetworking_meh.jpg){width="800"}[*work, bc I don't want to get fired]*    | ![](images/socialnetworking_meh.jpg)*[university]*                            | *[Catch up on uni]*                                                        | *[Catch up on uni]*                                                      |
+| ![](images/socialnetworking.jpg){width="800"}Discussion & conclusion [W]                          | ![](images/used_arson%20frog.jpg)*[university]*              | ![](images/socialnetworking_meh.jpg){width="800"}*[university]* | ![](images/socialnetworking_meh.jpg){width="800"}[\*work, bc I don't want to get fired]\*  | ![](images/socialnetworking_meh.jpg)*[university]*                            | *[Catch up on uni]*                                                        | *[Catch up on uni]*                                                      |
 |                                                                                                   |                                                              |                                                                 |                                                                                            |                                                                               |                                                                            |                                                                          |

### 2024-11-15 descriptivestry.Rmd
minorplotscorrections

@@
 
-```{r hist gender}
-# Histogram of prestige scores for Wave 1  
-hist(df_ego$gender, breaks = 2, main = "Distribution of gender",     xlab = "Gender", ylab = "Frequency", col = "#B3DE69") # INSERT YEARS OF WAVE/TIME FRAME STILL
+```{r}
+# Create the histogram
+ggplot(df_ego, aes(x = gender))+
+  geom_bar(color = "darkgrey", fill ="#B3DE69", width = 0.75)+
+  labs(title = "Histogram of Gender", x = "Gender\n (0 = female, 1 = male)", y = "Count") + theme(plot.title = element_text(hjust = 0.5, face = "bold"))
+
 ```
@@
 
-### Plotting: Gender 
+### Plotting: Gender - igraph
 #### with isolates
@@
 
-p_noisgender + labs(title = "Departments with isolates",
+p_noisgender + labs(title = "Departments without isolates",
         subtitle = "Plot of indegree and gender",
@@
 ```
+
 #### without isolates
+
 ```{r gen without iso}
@@
 
-```{r mypalette, include = FALSE, eval = FALSE}
+```{r mypalette, include = FALSE, eval = FALSE, hide = TRUE}
 # palette i like:
@@
 
-```{r colors in R, include = FALSE, eval = FALSE}
+```{r colors in R, include = TRUE, eval = FALSE, hide = TRUE}
 colors (distinct = TRUE) # prints all colors R knows
@@
 
-```{r look at colors PLOT, include = FALSE, eval = FALSE}
+```{r look at colors PLOT, include = TRUE, eval = FALSE, hide = TURE}
 ## Demonstrate the colors 1:8 in different palettes using a custom matplot()
@@
 
-```{r look at colors SWATCH, include = FALSE, eval = FALSE}
+```{r look at colors SWATCH, include = TRUE, eval = FALSE, hide = TRUE}
 palette.swatch <- function(palette = palette.pals(), n = 8, nrow = 8,

### 2024-11-15 descriptivestry.Rmd
datadraftcontd

@@
 
-```{r look at colors PLOT, include = TRUE, eval = FALSE, hide = TURE}
+```{r look at colors PLOT, include = TRUE, eval = FALSE, hide = TRUE}
 ## Demonstrate the colors 1:8 in different palettes using a custom matplot()

### 2024-11-15 draftdata.Rmd
prettyplotsindescriptives
datadraftcontd

@@
 
-Information about data set:
+## Sample data
 
--   Data set provided by Jochem
+-   The data for this study was obtained by collecting information from all Sociology and Political Science scholars at all Dutch institutions.
+During the initial phase of data collection, all important information regarding the author's position, university affiliation, names, IDs, departments, and more was gathered.
+The coordinator of this course, Jochem Tolsma, has provided a dataset with said information to be used in this project (**source sunbelt?** ).
+OpenAlex was used to scrape all published works, including important work-related information such as work id, concepts, citations, abstracts, and subjects, up until 2024 (@Priem2022).
+From this data, I created a final dataset (n=101) that included all authors from the Sociology and Political Science departments at Radboud University.
 
--   collaborations of scholars in NL
+-   source open alex: Priem et al. (2022)
 
--   time frame: ?
+    -   Priem, J., Piwowar, H., & Orr, R. (2022). *OpenAlex: A fully-open index of scholarly works, authors, venues, institutions, and concepts*. ArXiv. https://arxiv.org/abs/2205.01833
 
@@
 
-## DV: formation of ties between scholars
+## Dependent variable: Ties between scholars
+
+-   The dependent variable in this dataset, indicated by the ties between scholars, refers to academic collaborations between them, often also known as co-authorships.
+The data was scraped from OpenAlex API using the rvest and XML packages in R ( @Priem2022, @xml2**, @rvest**).
+The dependent variable, represented by an *adjacency matrix*, shows whether two actors or writers collaborated on one of their publications in the specified wave.
+\
+    Each dyad (author combination) is assessed based on whether they collaborated (1) or not (0) throughout the data period, which in this case is the first or second wave.
+
+-   ***In this study, ties are described as directional***, which implies that they are delivered by one actor and received by another.
+This means each actor has both outdegrees and indegrees.
+Outdegrees refer to 'sent' connections that refer to being the first author of a manuscript.
+Indegrees, or 'received' connections, imply collaboration on an article without being the 'initial' author.
+The generated adjacency matrix can take the form of a network, indicating the collaboration patterns of the academics who worked at the aforementioned university between **YEAR AND YEAR**.
 
@@
 
--   adjacency-matrix
+-   source rvest:
 
--
+    -   Wickham H (2024). rvest: Easily Harvest (Scrape) Web Pages. R package version 1.0.4, <https://github.com/tidyverse/rvest>, <https://rvest.tidyverse.org/>.
 
-## Covariate 1: Gender
+-   source xml2:
 
--   assumed binary for simplicity and ethical considerations of assuming gender based on other characterstics
+    -   Wickham H, Hester J, Ooms J (2023). *xml2: Parse XML*. R package version 1.3.6, <https://github.com/r-lib/xml2,> <https://xml2.r-lib.org/>.
 
--   Names of scholars manually checked in Dutch Voornamenbank website of the Meertens Institute (@MeertensInstituut)
+## Independent variables
 
--   with 0 = female and 1 = male.
+### Gender
 
--
+The first covariate of my study is the gender of the scholars in the sample.
+This information was not available through OpenAlex, and was instead manually generated by consulting the website of the Dutch 'Voornamenbank' of the Meertens Institute (@MeertensInstituut).
+If the website indicated that a name was used my more males than females, the scholar with that name was considered be male, and vice versa (female/male: 0/1).
 
-## Covariate 2: Prestige
+For simplicity's sake the concept of gender is not only inferred by the scholars name, but also assumed to be binary and indistinguishable from biological sex.
+I am aware that names do not equate to someone's gender identity and that gender identities encompass more than men and women.
+Further I am also aware that the terms men and women refer to gender identities and the terms male and female usually refer to biological sex.
+In this study these words have been conflated and it should be noted that this is not representative of the current scientific understanding of biological sex and gender, and that the way of obtaining this variable disregards scholars' self-identification of gender completely.
+This is done merely due to this project being part of a university assignment and is not something I would do, if I were to research outside of the context of my university curriculum.
 
--   control variable in this research design
+### Prestige
 
--   indicated by H-Index: and i10 index
-
-    -   definitions indeces:
-
-        -   H-index: Hirsch-Index
-
-        ```         
-        -   From Lucan: "The h-index namely measures an author’s prestige by calculating the number of publications that have been cited at least as many times as the total number of their publications.
-As explained by the creator of the h-index, ” A scientist has index h if h of his or her Np papers have at least h citations each and the other (Np - h) papers have ≤h citations each” (@Hirsch2005) "
-        ```
-
-        -   i10-index:
-
--   number of citations and publications webscraped through OpenAlex **[source]**
-
-    -   h index and i10 index calculated based on these counts
-
-<!-- -->
-
--   Code for this was provided by a fellow course mate, namely Lucan Bovens
+The scholars' h-indices will serve as a control variable in this research design (**find source : Bornmann et al.
+2020**).
+The h-index calculates the number of publications that have been cited at least as frequently as the author's total number of publications.
+This number can then be used as measure for the author's 'prestige' (@Hirsch2005).
+The number of citations and publications needed for this calculation were webscraped through OpenAlex API (@Priem2022**).** The code for this process was provided by a fellow course mate, namely Lucan Bovens.
 
@@
 Some examples are presented, e.g., in van de Bunt (1999); van de Bunt, van Duijn, and Snijders (1999); and van Duijn, Zeggelink, Stokman, and Wasseur (2003); and Steglich, Snijders, and West (2006).
-A website for SIENA is maintained at [http://www.stats.ox.ac.uk/\\\~snijders/siena/](http://www.stats.ox.ac.uk/\~snijders/siena/){.uri} .
+A website for SIENA is maintained at [http://www.stats.ox.ac.uk/\\\~snijders/siena/](http://www.stats.ox.ac.uk/~snijders/siena/){.uri} .
 At this website (‘publications’ tab) you shall also find references to introductions in various other languages.
@@
 
-Ripley, Ruth, and Snijders, Tom A.B.
+R Siena manual reference: @RSiena_manual
+
+-   Ripley, Ruth, and Snijders, Tom A.B.
 2009.
@@
 <http://www.stats.ox.ac.uk/siena/>
-
-Manual reference: @RSiena_manual
 
@@
 
-    -   reference: \@SNASS
-
-# Data description
+    -   reference: @SNASS

### 2024-11-15 weekbacktrack.Rmd
datadraftcontd

--- 2024-11-11 weekbacktrack.Rmd
@@
 
-+---------------------------------------------------------------------------------------------------+--------------------------------------------------------------+-----------------------------------------------------------------+--------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------+----------------------------------------------------------------------------+--------------------------------------------------------------------------+
++---------------------------------------------------------------------------------------------------+--------------------------------------------------------------+-----------------------------------------------------------------+---------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------+
 | Mon                                                                                               | Tue                                                          | Wed                                                             | Thu                                                                                         | Fri                                                                           | Sat                                                                                             | Sun                                                                      |
-+:==================================================================================================+:=============================================================+:================================================================+:===========================================================================================+:==============================================================================+:===========================================================================+:=========================================================================+
++:==================================================================================================+:=============================================================+:================================================================+:============================================================================================+:==============================================================================+:================================================================================================+:=========================================================================+
 | 28\.
@@
 |                                                                                                   |                                                              |                                                                 |                                                                                             | \* struggle with polsci data \*                                               |                                                                                                 |                                                                          |
-+---------------------------------------------------------------------------------------------------+--------------------------------------------------------------+-----------------------------------------------------------------+--------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------+----------------------------------------------------------------------------+--------------------------------------------------------------------------+
++---------------------------------------------------------------------------------------------------+--------------------------------------------------------------+-----------------------------------------------------------------+---------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------+
 | 04\.
@@
 |                                                                                                   |                                                              |                                                                 |                                                                                             | Plotting                                                                      |                                                                                                 |                                                                          |
-+---------------------------------------------------------------------------------------------------+--------------------------------------------------------------+-----------------------------------------------------------------+--------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------+----------------------------------------------------------------------------+--------------------------------------------------------------------------+
++---------------------------------------------------------------------------------------------------+--------------------------------------------------------------+-----------------------------------------------------------------+---------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------+
 | 11\.
@@
 |                                                                                                   |                                                              |                                                                 |                                                                                             |                                                                               |                                                                                                 |                                                                          |
-| ![](images/socialnetworking_meh.jpg){width="800"}Check in with Jochem                             | ![](images/used_arson%20frog.jpg){width="952"}*[university]* | ![](images/used_arson%20frog.jpg)*[university]*                 | ![](images/socialnetworking.jpg){width="800"}Continue description & plotting [S3]          | ![](images/socialnetworking.jpg){width="800"}Write theory [W]                 | ![](images/socialnetworking.jpg){width="800"}goodness of fit [S6]          | ![](images/timetopanic.gif)*[chores at home and university]*             |
+| ![](images/socialnetworking_meh.jpg){width="800"}Check in with Jochem                             | ![](images/used_arson%20frog.jpg){width="952"}*[university]* | ![](images/used_arson%20frog.jpg)*[university]*                 | ![](images/socialnetworking_meh.jpg)*[Depression]*                                          | ![](images/socialnetworking_meh.jpg)[*Depression]*                            | ![](images/socialnetworking.jpg){width="800"}Write data, methods, introduction, and theory [W]  | ![](images/socialnetworking_meh.jpg)[*university]*                       |
 |                                                                                                   |                                                              |                                                                 |                                                                                             |                                                                               |                                                                                                 |                                                                          |
-| Continue description & plotting [S3]                                                              |                                                              |                                                                 | Data & methods part [W]                                                                    | estimate model [S5]                                                           | Start Results [W]                                                          |                                                                          |
+| Continue description & plotting [S3]                                                              |                                                              |                                                                 | Continue description & plotting [S3]                                                        | Data & methods part [W]                                                       | estimate model [S5]                                                                             | goodness of fit [S6]                                                     |
 |                                                                                                   |                                                              |                                                                 |                                                                                             |                                                                               |                                                                                                 |                                                                          |
-|                                                                                                   |                                                              |                                                                 | Write introduction and theory [W]                                                          | goodness of fit [S6]                                                          |                                                                            |                                                                          |
-+---------------------------------------------------------------------------------------------------+--------------------------------------------------------------+-----------------------------------------------------------------+--------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------+----------------------------------------------------------------------------+--------------------------------------------------------------------------+
+|                                                                                                   |                                                              |                                                                 |                                                                                             |                                                                               |                                                                                                 | Start results                                                            |
++---------------------------------------------------------------------------------------------------+--------------------------------------------------------------+-----------------------------------------------------------------+---------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------+
 | 18\.
@@
 | Check in with Jochem                                                                              |                                                              |                                                                 | Results [W]                                                                                 | Finish Results [W]                                                            |                                                                                                 | Rework intro [W]                                                         |
-+---------------------------------------------------------------------------------------------------+--------------------------------------------------------------+-----------------------------------------------------------------+--------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------+----------------------------------------------------------------------------+--------------------------------------------------------------------------+
++---------------------------------------------------------------------------------------------------+--------------------------------------------------------------+-----------------------------------------------------------------+---------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------+
 | 25\.
@@
 |                                                                                                   |                                                              |                                                                 |                                                                                             |                                                                               |                                                                                                 |                                                                          |
-| ![](images/socialnetworking.jpg){width="800"}Discussion & conclusion [W]                          | ![](images/used_arson frog.jpg)*[university]*                | ![](images/socialnetworking_meh.jpg){width="800"}*[university]* | ![](images/socialnetworking_meh.jpg){width="800"}[*work, bc I don't want to get fired]*    | ![](images/socialnetworking_meh.jpg)*[university]*                            | *[Catch up on uni]*                                                        | *[Catch up on uni]*                                                      |
+| ![](images/socialnetworking.jpg){width="800"}Discussion & conclusion [W]                          | ![](images/used_arson%20frog.jpg)*[university]*              | ![](images/socialnetworking_meh.jpg){width="800"}*[university]* | ![](images/socialnetworking_meh.jpg){width="800"}*[\*work, bc I don't want to get fired]\** | ![](images/socialnetworking_meh.jpg)*[university]*                            | *[Catch up on uni]*                                                                             | *[Catch up on uni]*                                                      |
 |                                                                                                   |                                                              |                                                                 |                                                                                             |                                                                               |                                                                                                 |                                                                          |
 |                                                                                                   |                                                              | Discussion & conclusion [W]                                     | Finish discussion & conclusion [W]                                                          | ![](images/kermit-panic.gif){width="800"}**Format project website& hand in!** |                                                                                                 |                                                                          |
-+---------------------------------------------------------------------------------------------------+--------------------------------------------------------------+-----------------------------------------------------------------+--------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------+----------------------------------------------------------------------------+--------------------------------------------------------------------------+
++---------------------------------------------------------------------------------------------------+--------------------------------------------------------------+-----------------------------------------------------------------+---------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------+
 

### 2024-11-16 draftdata.Rmd
addingdatapreptodraft

@@
 
--   The data for this study was obtained by collecting information from all Sociology and Political Science scholars at all Dutch institutions.
+The data for this study was obtained by collecting information from all Sociology and Political Science scholars at all Dutch institutions.
 During the initial phase of data collection, all important information regarding the author's position, university affiliation, names, IDs, departments, and more was gathered.
@@
 OpenAlex was used to scrape all published works, including important work-related information such as work id, concepts, citations, abstracts, and subjects, up until 2024 (@Priem2022).
-From this data, I created a final dataset (n=101) that included all authors from the Sociology and Political Science departments at Radboud University.
-
--   source open alex: Priem et al. (2022)
-
-    -   Priem, J., Piwowar, H., & Orr, R. (2022). *OpenAlex: A fully-open index of scholarly works, authors, venues, institutions, and concepts*. ArXiv. https://arxiv.org/abs/2205.01833
+From this data, I created a final dataset (n=101) that included all authors from the Sociology and Political Science departments at Radboud University within the time frame of **[INSERT TIME FRAME]**.
 
@@
 
-## Dependent variable: Ties between scholars
+## Dependent variable
 
--   The dependent variable in this dataset, indicated by the ties between scholars, refers to academic collaborations between them, often also known as co-authorships.
+The dependent variable in this dataset, indicated by the ties between scholars, refers to academic collaborations between them, often also known as co-authorships.
 The data was scraped from OpenAlex API using the rvest and XML packages in R ( @Priem2022, @xml2**, @rvest**).
-The dependent variable, represented by an *adjacency matrix*, shows whether two actors or writers collaborated on one of their publications in the specified wave.
-\
-    Each dyad (author combination) is assessed based on whether they collaborated (1) or not (0) throughout the data period, which in this case is the first or second wave.
+The dependent variable, represented by an *adjacency matrix*, shows whether two actors or writers collaborated on one of their publications in the specified wave.\
+Each dyad (author combination) is assessed based on whether they collaborated (1) or not (0) throughout the data period.
 
@@
 Indegrees, or 'received' connections, imply collaboration on an article without being the 'initial' author.
-The generated adjacency matrix can take the form of a network, indicating the collaboration patterns of the academics who worked at the aforementioned university between **YEAR AND YEAR**.
+The generated adjacency matrix can take the form of a network, indicating the collaboration patterns of the academics at Radboud University between **YEAR AND YEAR**.
 
+```{=html}
+<!-- -->
+```
 -   formation of ties between scholars
-
--   source rvest:
-
-    -   Wickham H (2024). rvest: Easily Harvest (Scrape) Web Pages. R package version 1.0.4, <https://github.com/tidyverse/rvest>, <https://rvest.tidyverse.org/>.
-
--   source xml2:
-
-    -   Wickham H, Hester J, Ooms J (2023). *xml2: Parse XML*. R package version 1.3.6, <https://github.com/r-lib/xml2,> <https://xml2.r-lib.org/>.
 
@@
 This number can then be used as measure for the author's 'prestige' (@Hirsch2005).
-The number of citations and publications needed for this calculation were webscraped through OpenAlex API (@Priem2022**).** The code for this process was provided by a fellow course mate, namely Lucan Bovens.
+The number of citations and publications needed for this calculation were webscraped through OpenAlex API (@Priem2022**).** The code for this process was provided by Lucan Bovens.
 
@@
 
--   definition
+SIENA, which stands for *Simulation Investigation for Empirical Network Analysis*, is a software tool designed to perform statistical estimation of models for longitudinal social network data.
 
-    -   "SIENA, shorthand for **Simulation Investigation for Empirical Network Analysis**, is a computer program that carries out the statistical estimation of models for repeated measures of social networks according to the dynamic actor-oriented model of Snijders and van Duijn (1997), Snijders (2001), and Snijders, Steglich, and Schweinberger (2007); also see Steglich, Snijders, and Pearson (2009).
-A tutorial for these models is in Snijders, van de Bunt, and Steglich (2009).
-Some examples are presented, e.g., in van de Bunt (1999); van de Bunt, van Duijn, and Snijders (1999); and van Duijn, Zeggelink, Stokman, and Wasseur (2003); and Steglich, Snijders, and West (2006).
-A website for SIENA is maintained at [http://www.stats.ox.ac.uk/\\\~snijders/siena/](http://www.stats.ox.ac.uk/~snijders/siena/){.uri} .
-At this website (‘publications’ tab) you shall also find references to introductions in various other languages.
-This is a provisional manual for SIENA version 4.0, which is also called RSiena.
-This is a contributed package for the R statistical system which can be downloaded from <http://cran.r-project.org>.
-For the operation of R, the reader is referred to the corresponding manual.
-If desired, SIENA can be operated apparently independently of R, as is explained in Section 2.1.
-RSiena was programmed by Ruth Ripley and Krists Boitmanis, in collaboration with Tom Snijders."
+-   It operates based on the dynamic actor-oriented model, as developed in the works of
+
+    -   Snijders and van Duijn (1997),
+
+    -   Snijders (2001),
+
+    -   and Snijders, Steglich, and Schweinberger (2007).
+
+    -   Additional insights can be found in Steglich, Snijders, and Pearson (2009).
+
+SIENA version 4.0, also known as RSiena, is a package for the R statistical software and was developed by Ruth Ripley and Krists Boitmanis, in collaboration with Tom Snijders (@RSiena_package, @RSiena_manual).
+The use of RSiena for this project is highly based on the book "[**Social Network Analysis for Social Scientists**](https://jochemtolsma.github.io/SNA-4-Social-Scientists/)**"** by Jochem Tolsma and Bas Hofstra (@SNASS).
+
+# written references (remove in final paper)
 
@@
     -   reference: @SNASS
+
+source open alex: Priem et al. (2022)
+
+-   Priem, J., Piwowar, H., & Orr, R. (2022). *OpenAlex: A fully-open index of scholarly works, authors, venues, institutions, and concepts*. ArXiv. <https://arxiv.org/abs/2205.01833>
+
+source rvest:
+
+-   Wickham H (2024). rvest: Easily Harvest (Scrape) Web Pages. R package version 1.0.4, <https://github.com/tidyverse/rvest>, <https://rvest.tidyverse.org/>.
+
+source xml2:
+
+-   Wickham H, Hester J, Ooms J (2023). *xml2: Parse XML*. R package version 1.3.6, <https://github.com/r-lib/xml2,> <https://xml2.r-lib.org/>.
+
+# References

### 2024-11-16 weekbacktrack.Rmd
addingdatapreptodraft

@@
 
-+---------------------------------------------------------------------------------------------------+--------------------------------------------------------------+-----------------------------------------------------------------+---------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------+
++---------------------------------------------------------------------------------------------------+--------------------------------------------------------------+-----------------------------------------------------------------+--------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------+------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------+
 | Mon                                                                                               | Tue                                                          | Wed                                                             | Thu                                                                                        | Fri                                                                           | Sat                                                                                            | Sun                                                                      |
-+:==================================================================================================+:=============================================================+:================================================================+:============================================================================================+:==============================================================================+:================================================================================================+:=========================================================================+
++:==================================================================================================+:=============================================================+:================================================================+:===========================================================================================+:==============================================================================+:===============================================================================================+:=========================================================================+
 | 28\.
@@
 |                                                                                                   |                                                              |                                                                 |                                                                                            | \* struggle with polsci data \*                                               |                                                                                                |                                                                          |
-+---------------------------------------------------------------------------------------------------+--------------------------------------------------------------+-----------------------------------------------------------------+---------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------+
++---------------------------------------------------------------------------------------------------+--------------------------------------------------------------+-----------------------------------------------------------------+--------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------+------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------+
 | 04\.
@@
 |                                                                                                   |                                                              |                                                                 |                                                                                            | Plotting                                                                      |                                                                                                |                                                                          |
-+---------------------------------------------------------------------------------------------------+--------------------------------------------------------------+-----------------------------------------------------------------+---------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------+
++---------------------------------------------------------------------------------------------------+--------------------------------------------------------------+-----------------------------------------------------------------+--------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------+------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------+
 | 11\.
@@
 |                                                                                                   |                                                              |                                                                 |                                                                                            |                                                                               |                                                                                                |                                                                          |
-| ![](images/socialnetworking_meh.jpg){width="800"}Check in with Jochem                             | ![](images/used_arson%20frog.jpg){width="952"}*[university]* | ![](images/used_arson%20frog.jpg)*[university]*                 | ![](images/socialnetworking_meh.jpg)*[Depression]*                                          | ![](images/socialnetworking_meh.jpg)[*Depression]*                            | ![](images/socialnetworking.jpg){width="800"}Write data, methods, introduction, and theory [W]  | ![](images/socialnetworking_meh.jpg)[*university]*                       |
+| ![](images/socialnetworking_meh.jpg){width="800"}Check in with Jochem                             | ![](images/used_arson%20frog.jpg){width="952"}*[university]* | ![](images/used_arson%20frog.jpg)*[university]*                 | ![](images/socialnetworking_meh.jpg)*[Depression]*                                         | ![](images/socialnetworking_meh.jpg)*[Depression]*                            | ![](images/socialnetworking.jpg){width="800"}Write data, methods, introduction, and theory [W] | ![](images/socialnetworking_meh.jpg)*[university]*                       |
 |                                                                                                   |                                                              |                                                                 |                                                                                            |                                                                               |                                                                                                |                                                                          |
@@
 |                                                                                                   |                                                              |                                                                 |                                                                                            |                                                                               |                                                                                                | Start results                                                            |
-+---------------------------------------------------------------------------------------------------+--------------------------------------------------------------+-----------------------------------------------------------------+---------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------+
++---------------------------------------------------------------------------------------------------+--------------------------------------------------------------+-----------------------------------------------------------------+--------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------+------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------+
 | 18\.
@@
 | Check in with Jochem                                                                              |                                                              |                                                                 | Results [W]                                                                                | Finish Results [W]                                                            |                                                                                                | Rework intro [W]                                                         |
-+---------------------------------------------------------------------------------------------------+--------------------------------------------------------------+-----------------------------------------------------------------+---------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------+
++---------------------------------------------------------------------------------------------------+--------------------------------------------------------------+-----------------------------------------------------------------+--------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------+------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------+
 | 25\.
@@
 |                                                                                                   |                                                              |                                                                 |                                                                                            |                                                                               |                                                                                                |                                                                          |
-| ![](images/socialnetworking.jpg){width="800"}Discussion & conclusion [W]                          | ![](images/used_arson%20frog.jpg)*[university]*              | ![](images/socialnetworking_meh.jpg){width="800"}*[university]* | ![](images/socialnetworking_meh.jpg){width="800"}*[\*work, bc I don't want to get fired]\** | ![](images/socialnetworking_meh.jpg)*[university]*                            | *[Catch up on uni]*                                                                             | *[Catch up on uni]*                                                      |
+| ![](images/socialnetworking.jpg){width="800"}Discussion & conclusion [W]                          | ![](images/used_arson%20frog.jpg)*[university]*              | ![](images/socialnetworking_meh.jpg){width="800"}*[university]* | ![](images/socialnetworking_meh.jpg){width="800"}*[work, bc I don't want to get fired]*    | ![](images/socialnetworking_meh.jpg)*[university]*                            | *[Catch up on uni]*                                                                            | *[Catch up on uni]*                                                      |
 |                                                                                                   |                                                              |                                                                 |                                                                                            |                                                                               |                                                                                                |                                                                          |
 |                                                                                                   |                                                              | Discussion & conclusion [W]                                     | Finish discussion & conclusion [W]                                                         | ![](images/kermit-panic.gif){width="800"}**Format project website& hand in!** |                                                                                                |                                                                          |
-+---------------------------------------------------------------------------------------------------+--------------------------------------------------------------+-----------------------------------------------------------------+---------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------+
++---------------------------------------------------------------------------------------------------+--------------------------------------------------------------+-----------------------------------------------------------------+--------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------+------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------+
 

### 2024-11-16 descriptivestry.Rmd
draftdatadraftcontd

@@
 ## Functions
-
+Functions chunk 
 ```{r functions 1}
@@
 
-## More functions
-
+More functions
 ```{r functions 2}
@@
 
-Scholar
-
+Scholar data
 ```{r scholar data}
@@
 
-Ego
-
+Ego data
 ```{r df_ego data}
@@
 ### Gender
-
--   Gender
 
@@
 
-### more indepth:
+### more in depth:
 
@@
     -   Mortons I
-    -   igraphs
-    -   ggraphs
-
+    - also graphs below
 ```{r plot}

### 2024-11-16 draftdata.Rmd
draftdatadraftcontd

@@
 
--   timeframe of focus
+-   [**timeframe of focus**]{.underline}
 
@@
 
-The dependent variable in this dataset, indicated by the ties between scholars, refers to academic collaborations between them, often also known as co-authorships.
-The data was scraped from OpenAlex API using the rvest and XML packages in R ( @Priem2022, @xml2**, @rvest**).
+The dependent variable in this dataset, indicated by the ties between scholars, refers to academic collaborations between them and are often called co-authorships.
+The data was scraped from OpenAlex API using the rvest and xml2 packages in R ( @Priem2022, @xml2**,** @rvest).
 The dependent variable, represented by an *adjacency matrix*, shows whether two actors or writers collaborated on one of their publications in the specified wave.\
@@
 
--   ***In this study, ties are described as directional***, which implies that they are delivered by one actor and received by another.
+-   ***In this study, ties are described as directional*** **[ARE THEY??]** which implies that they are delivered by one actor and received by another.
 This means each actor has both outdegrees and indegrees.
@@
 The generated adjacency matrix can take the form of a network, indicating the collaboration patterns of the academics at Radboud University between **YEAR AND YEAR**.
-
-```{=html}
-<!-- -->
-```
--   formation of ties between scholars
 
@@
 
-The scholars' h-indices will serve as a control variable in this research design (**find source : Bornmann et al.
-2020**).
+The scholars' h-indices will serve as a control variable in this research design (@Bornmann2020, @Bornmann2021).
 The h-index calculates the number of publications that have been cited at least as frequently as the author's total number of publications.
@@
 
-# Data preparation /Methods
+# Methods
 
-### RSiena
+To evaluate the homophiliy in collaboration networks by gender and h-index, the analysis of the data will be as follows.
+The first step involves examining descriptives of the data to answer question of how homophily manifests in terms of degree and prestige within these networks.
+These descriptive findings will then serve as a foundation for the second phase of the analysis, which focuses on answering the explanatory research question of this study.
+This phase investigates the impact of homophily on collaboration and explores the interaction between gender and h-index.
+Descriptive analyses will utilize functions of the igraph and ggraph packages and t-tests, while the explanatory questions will be examined using Stochastic Actor-Based Models implemented via the RSiena package (@igraph, @ggraph, @RSiena_package, @RSiena_manual).
+
+## Descriptives
+
+**[Revisit and only talk about those that make sense to examine here]**
+
+First, ego-level descriptives such as the counts and distributions of gender and h-indices in both departments were generated to establish a clearer picture of the data at hand.
+
+I also examined descriptives of the ego network and of the whole network of scholars included in the data.
+Among others, these included the number of nodes, edges, reciprocity, degreee centrality, clustering, density, and path-length.
+With the help of these decriptives it was possible for me to......
+**[INSERT INSIGHT FROM DESCRIPTIVES HERE]**
+
+\
+**[UNSURE IF THIS IS NEEDED IF GENDER IS FIRST COVARIATE AND H INDEX ONLY CONTRL VARIABLE]**\
+Then, the networks were visualized using graphs to identify the presence of hubs and examine whether these hubs are concentrated among individuals with the highest h-index.
+Various centrality measures were also calculated and analyzed to determine their correlation with the scholars' h-index, providing further insight into whether network hubs tend to form around those with the highest h-index.
+
+## RSiena
 
 SIENA, which stands for *Simulation Investigation for Empirical Network Analysis*, is a software tool designed to perform statistical estimation of models for longitudinal social network data.
+SIENA version 4.0, also known as RSiena, is a package for the R statistical software and was developed by Ruth Ripley and Krists Boitmanis, in collaboration with Tom Snijders (@RSiena_package, @RSiena_manual).
+The use of RSiena for this project is highly based on the book "[Social Network Analysis for Social Scientists](https://jochemtolsma.github.io/SNA-4-Social-Scientists/)**"** by Jochem Tolsma and Bas Hofstra (@SNASS).
 
--   It operates based on the dynamic actor-oriented model, as developed in the works of
-
-    -   Snijders and van Duijn (1997),
-
-    -   Snijders (2001),
-
-    -   and Snijders, Steglich, and Schweinberger (2007).
-
-    -   Additional insights can be found in Steglich, Snijders, and Pearson (2009).
-
-SIENA version 4.0, also known as RSiena, is a package for the R statistical software and was developed by Ruth Ripley and Krists Boitmanis, in collaboration with Tom Snijders (@RSiena_package, @RSiena_manual).
-The use of RSiena for this project is highly based on the book "[**Social Network Analysis for Social Scientists**](https://jochemtolsma.github.io/SNA-4-Social-Scientists/)**"** by Jochem Tolsma and Bas Hofstra (@SNASS).
+[**CHECK AGAIN BEFORE SUBMITTING**]:\
+A total of four models, including a null model, were estimated.
+The null model excludes structural effects, focusing solely on reciprocity and density.
+The first model incorporates all structural network effects.
+Model 2 builds on this by adding the ego-level effect of gender.
+In Model 3, the ego-level control variable for h-index is included.
+\
+**[NEEDED?]** Finally, Model 4 is similar to Model 3 but replaces the quadratic effect of indegree popularity with a simple structural effect of indegree popularity.
 
@@
 
+**Bornmann et al. 2020?**
+
+-   Bornmann, L., Ganser, C., Tekles, A., & Leydesdorff, L.
+(2020).
+Does the h α-index reinforce the Matthew effect in science?
+the introduction of agent-based simulations into scientometrics. *Quantitative science studies*, *1*(1), 331-346.
+
+-   We follow up on the point about the Matthew effect in the current study by using a recently developed **Stata command (h_index)** and **R package (hindex)**, which can be **used to simulate *h*-index and *h*~α~-index applications in research evaluation**.
+
+    -   The user can investigate under which conditions *h*~α~ reinforces the Matthew effect.
+
+    -   The results of our study confirm what Leydesdorff et al. (2019) expected:
+
+        -   The h~α~-index reinforces the Matthew effect.
+
+        -   This effect can be intensified if strategic behavior of the publishing scientists and cumulative advantage effects are additionally considered in the simulation.
+
+-   @Bornmann2020
+
+**Bornmann et al. 2021**
+
+-   Bornmann, L., Ganser, C., & Tekles, A.
+(2021).
+Simulation of the h index use at university departments within the bibliometrics-based heuristics framework: Can the indicator be used to compare individual researchers?
+*Journal of Informetrics*, *16*(1), 101237.
+<https://doi.org/10.1016/j.joi.2021.101237>
+
+```{=html}
+<!-- -->
+```
+-   We developed the Stata command h_index and R package hindex.
+
+    -   •The command and package can be used to decide whether the h index can be used to compare all researchers in a university department.
+
+    -   •If the visualizations show great differences in the citation cultures between sub-groups in the department, the h index should not be used.
+
+-   @Bornmann2021
+
 R Siena manual reference: @RSiena_manual
 
--   Ripley, Ruth, and Snijders, Tom A.B.
-2009.
-Manual for SIENA version 4.0 (provisional version, July 6, 2009).
-Oxford: University of Oxford, Department of Statistics; Nuffield College.
-<http://www.stats.ox.ac.uk/siena/>
+-   Snijders TA, Ripley R, B'oda Z, V"or"os A, Preciado P (2024).
+Manual for RSiena.
+University of Groningen, Groningen, The Netherlands.
+R package version 1.4.7, <https://www.stats.ox.ac.uk/~snijders/siena/.>
 
-Siena package refrence: @RSiena_package
+Siena package reference: @RSiena_package
+
+-   Snijders TA, Ripley RM, Boitmanis K, Steglich C, Niezink NM, Amati V, Schoenenberger F (2024).
+“Siena - Simulation Investigation for Empirical Network Analysis.” R package version 1.4.7, <https://www.stats.ox.ac.uk/~snijders/siena/.>
 
@@
 
+source igraph:
+
+-   Csardi G, Nepusz T (2006). “The igraph software package for complex network research.” *InterJournal*, **Complex Systems**, 1695. [https://igraph.org](https://igraph.org/).
+
+-   Csárdi G, Nepusz T, Traag V, Horvát Sz, Zanini F, Noom D, Müller K (2024).
+\_igraph: Network Analysis and Visualization in R\_.
+doi:10.5281/zenodo.7682609 \<https://doi.org/10.5281/zenodo.7682609\>, R package version 2.1.1.9005, \<https://CRAN.R-project.org/package=igraph\>.
+
+source ggraph:
+
+-   Pedersen T (2024). *ggraph: An Implementation of Grammar of Graphics for Graphs and Networks*.
+R package version 2.2.1.9000, https://github.com/thomasp85/ggraph, [https://ggraph.data-imaginist.com](https://ggraph.data-imaginist.com/).
+
 # References

### 2024-11-16 descriptivestry.Rmd
darkmodeleggo

@@
 ---
+
+<!DOCTYPE html>
+<html lang="en">
+<head>
+    <meta charset="UTF-8">
+    <meta name="viewport" content="width=device-width, initial-scale=1.0">
+    <title>My Lab Journal</title>
+    <link rel="stylesheet" href="styles.css">  <!-- Link to the CSS file I created for dark mode code chunks -->
+
+</head>
+<body>
+    <header>
+        <h1>Welcome to My Lab Journal</h1>
+        <p>This is where I record my research and experiments.</p>
+    </header>
+
+    <main>
+        <section>
+            <h2>Experiment 1</h2>
+            <p>Details of the first experiment go here.</p>
+        </section>
+        <section>
+            <h2>Experiment 2</h2>
+            <p>Details of the second experiment go here.</p>
+        </section>
+    </main>
+
+    <footer>
+        <p>Created by Me, 2024</p>
+    </footer>
+</body>
+</html>
 

### 2024-11-16 draftdata.Rmd
darkmodeleggo

@@
 bibliography: references.bib
+csl: apa.csl
 ---
@@
 
-For simplicity's sake the concept of gender is not only inferred by the scholars name, but also assumed to be binary and indistinguishable from biological sex.
-I am aware that names do not equate to someone's gender identity and that gender identities encompass more than men and women.
-Further I am also aware that the terms men and women refer to gender identities and the terms male and female usually refer to biological sex.
-In this study these words have been conflated and it should be noted that this is not representative of the current scientific understanding of biological sex and gender, and that the way of obtaining this variable disregards scholars' self-identification of gender completely.
-This is done merely due to this project being part of a university assignment and is not something I would do, if I were to research outside of the context of my university curriculum.
+For the sake of simplicity, gender in this study was inferred from scholars’ names and treated as binary, conflating gender identity with biological sex.
+I acknowledge that names do not reliably indicate a person's gender identity and that gender encompasses more than the categories of men and women.
+Additionally, I recognize that while *men* and *women* typically refer to gender identities, *male* and *female* are often used to denote biological sex.
+These distinctions were not upheld in this study, which conflates the terms and disregards individuals' self-identified genders.
+This approach was taken solely due to the constraints of a university assignment and does not reflect my standard research practices, which would respect and account for the complexity of gender and self-identification outside the academic coursework context.
 
@@
 
-# written references (remove in final paper)
+# Ethical concerns
+
+## Webscraping
+
+This study relies on data obtained through web scraping publicly available sources, which raises several ethical concerns.
+One key issue is that the scholars included in the dataset did not provide informed consent for the use of their data in this research.
+To address this, several measures were implemented.
+First, efforts were made to anonymize the data presented in this study to the greatest extent possible.
+Second, only information directly relevant to the research objectives was collected, minimizing potential intrusions on privacy.
+Third, the scraped data did not include sensitive or harmful content, thereby reducing the risk of any negative consequences arising from its use.
+
+Despite these precautions, the fundamental issue of using non-consensual data persists.
+I do not adhere to the view that making data publicly available equates to granting unrestricted permission for its use in research.
+While the data in this study was already accessible online, the research generates new insights, such as patterns of tie formation between scholars, which were not previously explicit.
+Although names and other identifying details have been omitted to avoid recognizing individuals within network graphs or other outputs, informed consent for the use of personal data was not obtained.
+As such, this method of data collection remains ethically contentious at best.
+
+## Operationalization of gender
+
+An additional ethical concern relates to the treatment of gender in this study.
+The method used to infer gender, based on names and a binary framework, may raise issues regarding inclusivity and respect for individuals’ self-identified gender.
+This approach disregards the complexity of gender identity and risks misrepresentation.
+A more detailed explanation of how gender data was defined and its limitations is provided in the data definition section.
+
+# Written References (remove in final paper)
 

### 2024-11-16 draftintro.Rmd
darkmodeleggo

@@
 
-citation_package: apacite
 bibliography: references.bib
-biblio-style: apacite
-natbiboptions: round
+csl: apa.csl
 ---
+
+```{=html}
+<style>
+body {
+text-align: left;
+font-family: Times;
+}
+
+h1, .h1, h2, .h2, h3, .h3 {
+  margin-top: 24px;
+  font-family: Times;
+}
+
+</style>
+```
 
@@
 ```
+# intro second draft :
+# Introduction
+
+## Research Problem and Goal
+
+In this study, I examine the role of gender homophily in shaping co-authorship networks in the Sociology and Political Science Departments at Radboud University.
+Gender homophily refers to the tendency of individuals to collaborate with others of the same gender.
+This phenomenon can influence who gains access to collaboration opportunities, thereby shaping academic trajectories and reinforcing existing inequalities.
+Understanding these dynamics is essential to uncovering how collaboration networks may perpetuate or mitigate gender-based disparities in academia.
+
+### Gender and Collaboration
+
+Previous research has consistently shown that gender plays a significant role in academic collaboration.
+Studies by Horta (2022) and Kwiek and Roszka (2021) reveal that male researchers are more likely to collaborate with other men, while female researchers exhibit weaker but still present homophilous tendencies.
+This pattern contributes to the persistence of gender imbalances in co-authorship, where all-male teams remain more common than all-female teams.
+These trends are particularly concerning in fields such as Sociology and Political Science, where collaboration is vital for career advancement.
+
+The structure of these networks affects not only who collaborates but also how academic recognition and resources are distributed.
+For example, male-dominated networks may facilitate better access to high-impact collaborations and grant opportunities for men, further perpetuating the gender gap in academic success.
+
+### Prestige and Collaboration
+
+Another crucial factor influencing collaboration is academic prestige, often measured by publication in high-impact journals.
+Scholars with higher prestige, indicated by metrics such as the h-index or publication in top-tier journals, are generally more sought after as collaborators.
+Existing research suggests that prestige might interact with gender homophily in significant ways.
+Bellotti et al.
+(2022) found that prestigious male scholars often form networks that exclude women, while McDowell, Singell, and Stater (2006) observed that female scholars, despite demonstrating similar academic competence, face greater challenges in accessing high-prestige collaborative networks.
+
+In this context, it is crucial to explore whether the tendency for gender-based collaboration shifts when prestige factors come into play.
+Specifically, does publishing in prestigious journals mitigate or exacerbate gender homophily in academic networks?
+
+## Research Focus and Questions
+
+This study aims to analyze gender homophily within the co-authorship networks of the Sociology and Political Science Departments at Radboud University, focusing on the role of journal prestige.
+The research is guided by the following questions:
+
+- **RQ1a:** To what extent does gender homophily occur across all co-publications of the staff in the Sociology and Political Science Departments at Radboud University?
+
+- **RQ1b:** To what extent do the two departments differ in their levels of gender homophily?
+
+These questions focus on descriptive patterns, providing a macro-level view of gender clustering in academic networks.
+
+- **RQ2:** To what extent can gender homophily in collaboration networks be explained by preferences at the dyadic level, controlling for structural network and individual-level covariates?
+
+This question shifts the focus to the micro-level, examining whether individual choices and structural factors drive homophily in co-authorship.
+
+- **RQ3:** How does the prestige of scholars, measured by their publication in high- versus low-impact journals, influence gender homophily in co-authorship networks?
+
+This question explores whether prestige interacts with gender homophily, shedding light on how academic recognition impacts collaborative behaviors.
+Specifically, it investigates whether male and female scholars with similar prestige levels experience different patterns of collaboration and whether high-prestige contexts reduce or amplify gender clustering.
+
+## Relevance and Contribution
+
+This study contributes to the growing body of literature on gender inequalities in academia by focusing on the intersection of gender and academic prestige in shaping collaboration networks.
+By applying a social network perspective, it offers insights into how gender-based preferences influence co-authorship patterns and how these dynamics vary between disciplines.
+Moreover, by exploring the role of journal prestige, this research highlights how structural factors may intersect with social biases to shape academic opportunities, providing a nuanced understanding of the mechanisms underlying gender disparities in academia.
+
+---
 
@@
 
-Collaboration has become an essential part of modern academia, with scholars increasingly engaging in joint research efforts.
-Co-authorship allows researchers to combine expertise, share resources, and enhance their scholarly output (@Cheong2009).
-However, the dynamics of academic collaboration are not free from social patterns, and gender homophily—where individuals prefer to collaborate with others of the same gender—may play a significant role.
+## Contextualization
+Collaboration has become a cornerstone of modern academic practice, with scholars increasingly working together to leverage diverse expertise, share resources, and enhance their research output.
+Co-authorship, in particular, is a key indicator of collaboration, often reflecting the dynamics of professional relationships and the distribution of academic opportunities.
+As Cheong (@Cheong2009) highlights, collaboration enables researchers to combine intellectual and institutional resources, contributing significantly to their scholarly success.
+
+However, collaboration is not free from social patterns and biases.
+Academic networks often mirror broader societal inequalities, with persistent disparities in opportunities and recognition.
+One such disparity is gender inequality, which continues to shape interactions, opportunities, and outcomes within academia.
+
+## Research problem & goal
+
 Understanding how gender affects co-authorship networks, particularly in terms of homophily, can reveal important insights into how academic opportunities and achievements are distributed across genders.
+## N: Research Problem and Goal
+In this study, I examine the role of gender homophily in shaping co-authorship networks in the Sociology and Political Science Departments at Radboud University.
+Gender homophily refers to the tendency of individuals to collaborate with others of the same gender.
+This phenomenon can influence who gains access to collaboration opportunities, thereby shaping academic trajectories and reinforcing existing inequalities.
+Understanding these dynamics is essential to uncovering how collaboration networks may perpetuate or mitigate gender-based disparities in academia.
+
+## Short overview of prior findings:
+
+### gender & collaboration
 
@@
 Furthermore, as Kwiek and Roszka (@Kwiek2021) point out, all-male authorship is far more prevalent than all-female authorship, indicating that male-dominated collaboration networks may reinforce existing gender imbalances in academia.
+### N:Gender and Collaboration
+
+Previous research has consistently shown that gender plays a significant role in academic collaboration.
+Studies by Horta (2022) and Kwiek and Roszka (2021) reveal that male researchers are more likely to collaborate with other men, while female researchers exhibit weaker but still present homophilous tendencies.
+This pattern contributes to the persistence of gender imbalances in co-authorship, where all-male teams remain more common than all-female teams.
+These trends are particularly concerning in fields such as Sociology and Political Science, where collaboration is vital for career advancement.
+
+The structure of these networks affects not only who collaborates but also how academic recognition and resources are distributed.
+For example, male-dominated networks may facilitate better access to high-impact collaborations and grant opportunities for men, further perpetuating the gender gap in academic success.
+
+### h-index & collaboration
 
@@
 
+### Reiteration of (societal) relevance of study
+
 This research will contribute to a growing body of literature that seeks to understand the social dynamics underlying academic collaboration.
@@
 
+# Written references (remove in final paper)
+
+Bornmann, Lutz, Christian Ganser, and Alexander Tekles.
+2021.
+“Simulation of the h Index Use at University Departments Within the Bibliometrics-Based Heuristics Framework: Can the Indicator Be Used to Compare Individual Researchers?” *Journal of Informetrics* 16 (1): 101237.
+<https://doi.org/10.1016/j.joi.2021.101237>.
+
+@Bornmann2021
+
+Bornmann, Lutz, Christian Ganser, Alexander Tekles, and Loet Leydesdorff.
+2020.
+“Does the h αα-Index Reinforce the Matthew Effect in Science?
+The Introduction of Agent-Based Simulations into Scientometrics.” *Quantitative Science Studies* 1 (1): 331–46.
+
+@Bornmann2020
+
 # References

### 2024-11-16 drafttheory.Rmd
darkmodeleggo

@@
 
--   Explanation of gender homophily in scholarship
+## gender homophily in scholars' collaboration
 
@@
 
+## h-index and collaboration
+
 -   **Hypothesis 3:** On the ego level, the preference of *men to work with men and women with women, (controlled for structural network effects), is less influential in the choice to collaborate if the alter is someone who published in a high-prestige journal.*
@@
 
+# Written references (remove in final paper)
+
+Bornmann, Lutz, Christian Ganser, and Alexander Tekles.
+2021.
+“Simulation of the h Index Use at University Departments Within the Bibliometrics-Based Heuristics Framework: Can the Indicator Be Used to Compare Individual Researchers?” Journal of Informetrics 16 (1): 101237.
+<https://doi.org/10.1016/j.joi.2021.101237>.
+
+@Bornmann2021
+
+Bornmann, Lutz, Christian Ganser, Alexander Tekles, and Loet Leydesdorff.
+2020.
+“Does the h αα-Index Reinforce the Matthew Effect in Science?
+The Introduction of Agent-Based Simulations into Scientometrics.” Quantitative Science Studies 1 (1): 331–46.
+
+@Bornmann2020
+
 # References

### 2024-11-16 descriptivestry.Rmd
darkmodefixbug

@@
 
-<!DOCTYPE html>
 <html lang="en">
@@
 </head>
-<body>
-    <header>
-        <h1>Welcome to My Lab Journal</h1>
-        <p>This is where I record my research and experiments.</p>
-    </header>
-
-    <main>
-        <section>
-            <h2>Experiment 1</h2>
-            <p>Details of the first experiment go here.</p>
-        </section>
-        <section>
-            <h2>Experiment 2</h2>
-            <p>Details of the second experiment go here.</p>
-        </section>
-    </main>
-
-    <footer>
-        <p>Created by Me, 2024</p>
-    </footer>
-</body>
 </html>

### 2024-11-17 descriptivestry.Rmd
madepagesymlandstuff

@@
     <meta name="viewport" content="width=device-width, initial-scale=1.0">
-    <title>My Lab Journal</title>
+    <title>My Descriptives</title>
     <link rel="stylesheet" href="styles.css">  <!-- Link to the CSS file I created for dark mode code chunks -->
@@
 # Getting started
-
 ```{r clean}
@@
 ## Packages
-
 ```{r package}
@@
 ## Functions
+
 Functions chunk 
@@
 
-    -   descriptives (mean etc.) in whole sample
-
+descriptives (mean etc.) in whole sample
 ```{r sum gender}
@@
 
-    - gender counts across whole sample (0 = female, 1 = male)
-
+gender counts across whole sample (0 = female, 1 = male)
 ```{r counts gender-all}
@@
 
-    -   overall gender distribution in sample
-
+overall gender distribution in sample
 ```{r}
@@
 
-    -   Genders per department (0 = female, 1 = male)
-
+Genders per department (0 = female, 1 = male)
 ```{r gender per dep.}
@@
 
-    -   descriptives (mean etc.)
+descriptives (mean etc.)
 ```{r summary h index}
@@
 ```
-    - Overall  (INSERT YEARS STILL)
-
+Overall  (INSERT YEARS STILL)
 ```{r hist h index}
@@
 
-    -   H index per department
-
+H index per department
 ```{r table per dep h index}
@@
 
--   Nr. of nodes
-
+Nr. of nodes
 ```{r nodes}
@@
 
--   Nr. of edges
-
+Nr. of edges
 ```{r edges}
@@
 
--   Dyad census
-
+Dyad census
     ```{r dyad cen}
@@
 
--   Triad-census
-
+Triad-census
     ```{r triad cen}
@@
 
--   edge-density
-
+Edge-density
     ```{r edge dens}
@@
 
--   reciprocity
-
+reciprocity
     ```{r recip}
@@
 
--   degree centrality / degreee?
-
+degree centrality / degreee?
     ```{r degree}
@@
 
--   Betweenness centrality /betweenness?
-
+Betweenness centrality /betweenness?
     ```{r betweenness}
@@
 
--   Clustering
-
+Clustering
     ```{r clustering}
@@
 
--   Density
-
+Density
     ```{r density}
@@
 
--   Average path length
-
+Average path length
     ```{r path length}
@@
 
--   Segregation
-
+Segregation
     - Mortons I

### 2024-11-17 weekbacktrack.Rmd
madepagesymlandstuff

@@
 
-+---------------------------------------------------------------------------------------------------+--------------------------------------------------------------+-----------------------------------------------------------------+--------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------+------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------+
++---------------------------------------------------------------------------------------------------+--------------------------------------------------------------+-----------------------------------------------------------------+--------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------+----------------------------------------------------------------------------+--------------------------------------------------------------------------------------+
 | Mon                                                                                               | Tue                                                          | Wed                                                             | Thu                                                                                        | Fri                                                                           | Sat                                                                        | Sun                                                                                  |
-+:==================================================================================================+:=============================================================+:================================================================+:===========================================================================================+:==============================================================================+:===============================================================================================+:=========================================================================+
++:==================================================================================================+:=============================================================+:================================================================+:===========================================================================================+:==============================================================================+:===========================================================================+:=====================================================================================+
 | 28\.
@@
 |                                                                                                   |                                                              |                                                                 |                                                                                            | \* struggle with polsci data \*                                               |                                                                            |                                                                                      |
-+---------------------------------------------------------------------------------------------------+--------------------------------------------------------------+-----------------------------------------------------------------+--------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------+------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------+
++---------------------------------------------------------------------------------------------------+--------------------------------------------------------------+-----------------------------------------------------------------+--------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------+----------------------------------------------------------------------------+--------------------------------------------------------------------------------------+
 | 04\.
@@
 |                                                                                                   |                                                              |                                                                 |                                                                                            | Plotting                                                                      |                                                                            |                                                                                      |
-+---------------------------------------------------------------------------------------------------+--------------------------------------------------------------+-----------------------------------------------------------------+--------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------+------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------+
++---------------------------------------------------------------------------------------------------+--------------------------------------------------------------+-----------------------------------------------------------------+--------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------+----------------------------------------------------------------------------+--------------------------------------------------------------------------------------+
 | 11\.
@@
 |                                                                                                   |                                                              |                                                                 |                                                                                            |                                                                               |                                                                            |                                                                                      |
-| ![](images/socialnetworking_meh.jpg){width="800"}Check in with Jochem                             | ![](images/used_arson%20frog.jpg){width="952"}*[university]* | ![](images/used_arson%20frog.jpg)*[university]*                 | ![](images/socialnetworking_meh.jpg)*[Depression]*                                         | ![](images/socialnetworking_meh.jpg)*[Depression]*                            | ![](images/socialnetworking.jpg){width="800"}Write data, methods, introduction, and theory [W] | ![](images/socialnetworking_meh.jpg)*[university]*                       |
+| ![](images/socialnetworking_meh.jpg){width="800"}Check in with Jochem                             | ![](images/used_arson%20frog.jpg){width="952"}*[university]* | ![](images/used_arson%20frog.jpg)*[university]*                 | ![](images/socialnetworking_meh.jpg)*[Depression]*                                         | ![](images/socialnetworking_meh.jpg)*[Depression]*                            | ![](images/socialnetworking.jpg){width="800"}Write data, methods           | ![](images/socialnetworking_meh.jpg)*[university]*write introduction, and theory [W] |
 |                                                                                                   |                                                              |                                                                 |                                                                                            |                                                                               |                                                                            |                                                                                      |
-| Continue description & plotting [S3]                                                              |                                                              |                                                                 | Continue description & plotting [S3]                                                       | Data & methods part [W]                                                       | estimate model [S5]                                                                            | goodness of fit [S6]                                                     |
+| Continue description & plotting [S3]                                                              |                                                              |                                                                 | Continue description & plotting [S3]                                                       | Data & methods part [W]                                                       |                                                                            | estimate model [S5]                                                                  |
 |                                                                                                   |                                                              |                                                                 |                                                                                            |                                                                               |                                                                            |                                                                                      |
-|                                                                                                   |                                                              |                                                                 |                                                                                            |                                                                               |                                                                                                | Start results                                                            |
-+---------------------------------------------------------------------------------------------------+--------------------------------------------------------------+-----------------------------------------------------------------+--------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------+------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------+
+|                                                                                                   |                                                              |                                                                 |                                                                                            |                                                                               |                                                                            | goodness of fit [S6]                                                                 |
++---------------------------------------------------------------------------------------------------+--------------------------------------------------------------+-----------------------------------------------------------------+--------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------+----------------------------------------------------------------------------+--------------------------------------------------------------------------------------+
 | 18\.
@@
 |                                                                                                   |                                                              |                                                                 |                                                                                            |                                                                               |                                                                            |                                                                                      |
-| Check in with Jochem                                                                              |                                                              |                                                                 | Results [W]                                                                                | Finish Results [W]                                                            |                                                                                                | Rework intro [W]                                                         |
-+---------------------------------------------------------------------------------------------------+--------------------------------------------------------------+-----------------------------------------------------------------+--------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------+------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------+
+| Check in with Jochem                                                                              |                                                              |                                                                 | Results [W]                                                                                | Finish Results [W]                                                            | email Jochem if delay                                                      | Rework intro [W]                                                                     |
++---------------------------------------------------------------------------------------------------+--------------------------------------------------------------+-----------------------------------------------------------------+--------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------+----------------------------------------------------------------------------+--------------------------------------------------------------------------------------+
 | 25\.
@@
 |                                                                                                   |                                                              | Discussion & conclusion [W]                                     | Finish discussion & conclusion [W]                                                         | ![](images/kermit-panic.gif){width="800"}**Format project website& hand in!** |                                                                            |                                                                                      |
-+---------------------------------------------------------------------------------------------------+--------------------------------------------------------------+-----------------------------------------------------------------+--------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------+------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------+
++---------------------------------------------------------------------------------------------------+--------------------------------------------------------------+-----------------------------------------------------------------+--------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------+----------------------------------------------------------------------------+--------------------------------------------------------------------------------------+
 

### 2024-11-17 descriptivestry.Rmd
klippyfix

@@
 
-```{r klippy, echo=FALSE, include=FALSE}
+```{r klippy, echo=FALSE, include=TRUE}
 klippy::klippy(position = c('top', 'right'))
-klippy::klippy(color = 'darkred')
-klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done')
+#klippy::klippy(color = 'darkred')
+#klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done')
 ```

### 2024-11-17 draftintro.Rmd
klippyfix

@@
 ```
-
 ```{r, globalsettings, echo=FALSE, warning=FALSE, results='hide'}
@@
 ```
-# intro second draft :
-# Introduction
+
+------------------------------------------------------------------------
+
+# Introduction draft
+
+## Contextualization
+
+Collaboration has become a cornerstone of modern academic practice, with scholars increasingly working together to leverage diverse expertise, share resources, and enhance their research output.
+Co-authorship, in particular, is a key indicator of collaboration, often reflecting the dynamics of professional relationships and the distribution of academic opportunities.
+As Cheong (@Cheong2009) highlights, collaboration enables researchers to combine intellectual and institutional resources, contributing significantly to their scholarly success.
+
+However, collaboration is not free from social patterns and biases.
+Academic networks often mirror broader societal inequalities, with persistent disparities in opportunities and recognition.
+One such disparity is gender inequality, which continues to shape interactions, opportunities, and outcomes within academia.
 
@@
 
+## Prior findings
+
 ### Gender and Collaboration
@@
 Previous research has consistently shown that gender plays a significant role in academic collaboration.
-Studies by Horta (2022) and Kwiek and Roszka (2021) reveal that male researchers are more likely to collaborate with other men, while female researchers exhibit weaker but still present homophilous tendencies.
-This pattern contributes to the persistence of gender imbalances in co-authorship, where all-male teams remain more common than all-female teams.
-These trends are particularly concerning in fields such as Sociology and Political Science, where collaboration is vital for career advancement.
+Horta and colleagues (@Horta2022) reveal that male researchers are more likely to collaborate with other men, while female researchers exhibit a weaker but still present tendency towards homophily.
 
-The structure of these networks affects not only who collaborates but also how academic recognition and resources are distributed.
+Kwiek and Roszka (@Kwiek2021) found that such patterns contributes to the persistence of gender imbalances in co-authorship, where all-male teams remain more common than all-female teams.
+These trends are particularly concerning in fields such as Sociology and Political Science, where collaboration is vital for career advancement (@Cheong2009).
+
+The structure of these networks affects not only who collaborates but also how academic recognition and resources are distributed (@Cheong2009).
 For example, male-dominated networks may facilitate better access to high-impact collaborations and grant opportunities for men, further perpetuating the gender gap in academic success.
@@
 Bellotti et al.
-(2022) found that prestigious male scholars often form networks that exclude women, while McDowell, Singell, and Stater (2006) observed that female scholars, despite demonstrating similar academic competence, face greater challenges in accessing high-prestige collaborative networks.
+(@Bellotti2022) found that prestigious male scholars often form networks that exclude women, while McDowell, Singell, and Stater (@Mcdowell2007) observed that female scholars, despite demonstrating similar academic competence, face greater challenges in accessing high-prestige collaborative networks.
 
@@
 
-This study aims to analyze gender homophily within the co-authorship networks of the Sociology and Political Science Departments at Radboud University, focusing on the role of journal prestige.
+This study aims to analyze gender homophily within the co-authorship networks of the Sociology and Political Science Departments at Radboud University, focusing on the role of prestige.
 The research is guided by the following questions:
@@
 
-- **RQ3:** How does the prestige of scholars, measured by their publication in high- versus low-impact journals, influence gender homophily in co-authorship networks?
+-   **RQ3:** How does the prestige of scholars, measured by scholars' h-index, influence gender homophily in co-authorship networks?
 
 This question explores whether prestige interacts with gender homophily, shedding light on how academic recognition impacts collaborative behaviors.
-Specifically, it investigates whether male and female scholars with similar prestige levels experience different patterns of collaboration and whether high-prestige contexts reduce or amplify gender clustering.
+Specifically, it investigates whether male and female scholars with similar prestige levels experience different patterns of collaboration and whether prestige reduces or amplifies gender clustering.
 
@@
 Moreover, by exploring the role of journal prestige, this research highlights how structural factors may intersect with social biases to shape academic opportunities, providing a nuanced understanding of the mechanisms underlying gender disparities in academia.
-
----
-
-# Introduction draft
-
-## Contextualization
-Collaboration has become a cornerstone of modern academic practice, with scholars increasingly working together to leverage diverse expertise, share resources, and enhance their research output.
-Co-authorship, in particular, is a key indicator of collaboration, often reflecting the dynamics of professional relationships and the distribution of academic opportunities.
-As Cheong (@Cheong2009) highlights, collaboration enables researchers to combine intellectual and institutional resources, contributing significantly to their scholarly success.
-
-However, collaboration is not free from social patterns and biases.
-Academic networks often mirror broader societal inequalities, with persistent disparities in opportunities and recognition.
-One such disparity is gender inequality, which continues to shape interactions, opportunities, and outcomes within academia.
-
-## Research problem & goal
-
-Understanding how gender affects co-authorship networks, particularly in terms of homophily, can reveal important insights into how academic opportunities and achievements are distributed across genders.
-## N: Research Problem and Goal
-In this study, I examine the role of gender homophily in shaping co-authorship networks in the Sociology and Political Science Departments at Radboud University.
-Gender homophily refers to the tendency of individuals to collaborate with others of the same gender.
-This phenomenon can influence who gains access to collaboration opportunities, thereby shaping academic trajectories and reinforcing existing inequalities.
-Understanding these dynamics is essential to uncovering how collaboration networks may perpetuate or mitigate gender-based disparities in academia.
-
-## Short overview of prior findings:
-
-### gender & collaboration
-
-Previous studies have found that male researchers often prefer collaborating with other men, while female researchers tend to collaborate with other women, albeit to a lesser extent (@Horta2022).
-This raises critical questions about the structure and inclusiveness of academic networks.
-In fields such as Sociology and Political Science, where collaboration is crucial for scholarly success, gender-based patterns could shape the career trajectories of researchers (@Cheong2009).
-Furthermore, as Kwiek and Roszka (@Kwiek2021) point out, all-male authorship is far more prevalent than all-female authorship, indicating that male-dominated collaboration networks may reinforce existing gender imbalances in academia.
-### N:Gender and Collaboration
-
-Previous research has consistently shown that gender plays a significant role in academic collaboration.
-Studies by Horta (2022) and Kwiek and Roszka (2021) reveal that male researchers are more likely to collaborate with other men, while female researchers exhibit weaker but still present homophilous tendencies.
-This pattern contributes to the persistence of gender imbalances in co-authorship, where all-male teams remain more common than all-female teams.
-These trends are particularly concerning in fields such as Sociology and Political Science, where collaboration is vital for career advancement.
-
-The structure of these networks affects not only who collaborates but also how academic recognition and resources are distributed.
-For example, male-dominated networks may facilitate better access to high-impact collaborations and grant opportunities for men, further perpetuating the gender gap in academic success.
-
-### h-index & collaboration
-
-Another influential factor in collaboration between scholars seems to be the scholars' 'prestige', namely whether they have published in renowned journals.
-**SOURCE** found that .....PART ABOUT JOURNAL PRESTIGE
-
-In this study, I explore the extent to which gender homophily influences co-authorship networks among faculty in the Sociology and Political Science Departments at Radboud University.
-Specifically, I aim to examine whether there are differences in gender homophily between the two departments, and how homophily patterns vary depending on the prestige of the journals in which researchers publish.
-
-### Reiteration of (societal) relevance of study
-
-This research will contribute to a growing body of literature that seeks to understand the social dynamics underlying academic collaboration.
-By analyzing gender homophily and network structures in two different academic disciplines, this study will shed light on how gender shapes collaboration opportunities and how these dynamics may differ across scholarly fields.
-Moreover, exploring the role of journal prestige in shaping homophily will offer insights into whether gender-based preferences shift in response to career-enhancing factors like publishing in high-prestige journals.
 
@@
 
+Bellotti, E., Czerniawska, D., Everett, M.
+G., & Guadalupi, L.
+(2022).
+Gender inequalities in research funding: Unequal network configurations, or unequal network returns?
+*Social Networks*, *70*, 138–151.
+<https://doi.org/10.1016/j.socnet.2021.12.007>
+
+@Bellotti2022
+
+McDowell, John M., Larry D.
+Singell, and Mark Stater.
+2007. “Two to Tango?
+Gender Differences in the Decision to Publish and Coauthor.” *Economic Inquiry* 44 (1): 153–68. <https://doi.org/10.1093/ei/cbi065>.
+
+@Mcdowell2007
+
+------------------------------------------------------------------------
+
 # References

### 2024-11-18 clarifyRQsandDesign.Rmd
visualtextdarkmodecorrections

@@
 and update plots after descriptives and multivariate analyses along the way. it is an iterative process.*
+
+# 17.11.24:
+
+1.  **RQ1**: To what extent does gender homophily occur across all co-publications of the staff in the Sociology and Political Science Departments at Radboud University?\
+    *This question focuses on descriptive analysis at the network level, examining overall gender clustering patterns within and between departments.*
+
+2.  **RQ2**: To what extent do the two departments differ in their gender homophily?\
+    *This question compares the strength of gender homophily between the two departments, with a focus on dyadic-level interactions while controlling for structural network effects.*
+
+3.  **RQ3**: How does gender homophily in collaborations differ depending on scholars’ prestige (e.g., publication in high-impact journals)?\
+    *This question investigates the role of prestige in moderating gender homophily at the ego level.*

### 2024-11-18 descriptivestry.Rmd
visualtextdarkmodecorrections

@@
 Credits to Hannah Groennou for the basis of the code of these graphs.
+
+(test line)
+
 #### with isolates ?
@@
 
-palette.colors(palette = "-palette name here-")
-# [1] "#000000" "#E69F00" "#56B4E9" "#009E73" "#F0E442" "#0072B2"
-# [7] "#D55E00" "#CC79A7" "#999999"
+palette.colors(palette = "Alphabet")
+#R3
+"#000000" "#FF0000" "#00CD00" "#0000FF" "#00FFFF" "#FF00FF" "#FFFF00" "#BEBEBE"
+
+#R4
+"#000000" "#DF536B" "#61D04F" "#2297E6" "#28E2E5" "#CD0BBC" "#F5C710" "#9E9E9E"
+
+#ggplot2
+"#000000" "#F8766D" "#00BA38" "#619CFF" "#00BFC4" "#F564E3" "#B79F00" "#9E9E9E"
+
+#Okabe Ito 
+"#000000" "#E69F00" "#56B4E9" "#009E73" "#F0E442" "#0072B2" "#D55E00" "#CC79A7" "#999999"
+
+# Accent
+"#7FC97F" "#BEAED4" "#FDC086" "#FFFF99" "#386CB0" "#F0027F" "#BF5B17" "#666666"
+
+#Paired
+"#A6CEE3" "#1F78B4" "#B2DF8A" "#33A02C" "#FB9A99" "#E31A1C" "#FDBF6F" "#FF7F00"
+"#CAB2D6" "#6A3D9A" "#FFFF99" "#B15928"
+
+#Pastel 1
+"#FBB4AE" "#B3CDE3" "#CCEBC5" "#DECBE4" "#FED9A6" "#FFFFCC" "#E5D8BD" "#FDDAEC" "#F2F2F2"
+
+#Pastel 2
+"#B3E2CD" "#FDCDAC" "#CBD5E8" "#F4CAE4" "#E6F5C9" "#FFF2AE" "#F1E2CC" "#CCCCCC"
+
+#Set 1
+"#E41A1C" "#377EB8" "#4DAF4A" "#984EA3" "#FF7F00" "#FFFF33" "#A65628" "#F781BF""#999999"
+
+#Set 2
+"#66C2A5" "#FC8D62" "#8DA0CB" "#E78AC3" "#A6D854" "#FFD92F" "#E5C494" "#B3B3B3"
+
+#Set 3
+"#8DD3C7" "#FFFFB3" "#BEBADA" "#FB8072" "#80B1D3" "#FDB462" "#B3DE69" "#FCCDE5"
+"#D9D9D9" "#BC80BD" "#CCEBC5" "#FFED6F"
+
+# Tableau 10
+"#4E79A7" "#F28E2B" "#E15759" "#76B7B2" "#59A14F" "#EDC948" "#B07AA1" "#FF9DA7"
+"#9C755F" "#BAB0AC"
+
+#Classic Tableau
+"#1F77B4" "#FF7F0E" "#2CA02C" "#D62728" "#9467BD" "#8C564B" "#E377C2" "#7F7F7F"
+"#BCBD22" "#17BECF"
+
+# Polychrome 36:
+"#5A5156" "#E4E1E3" "#F6222E" "#FE00FA" "#16FF32" "#3283FE" "#FEAF16" "#B00068"
+"#1CFFCE" "#90AD1C" "#2ED9FF" "#DEA0FD" "#AA0DFE" "#F8A19F" "#325A9B" "#C4451C"
+"#1C8356" "#85660D" "#B10DA1" "#FBE426" "#1CBE4F" "#FA0087" "#FC1CBF" "#F7E1A0"
+"#C075A6" "#782AB6" "#AAF400" "#BDCDFF" "#822E1C" "#B5EFB5" "#7ED7D1" "#1C7F93"
+"#D85FF7" "#683B79" "#66B0FF" "#3B00FB"
+
+#Alphabet
+"#AA0DFE" "#3283FE" "#85660D" "#782AB6" "#565656" "#1C8356" "#16FF32" "#F7E1A0"
+"#E2E2E2" "#1CBE4F" "#C4451C" "#DEA0FD" "#FE00FA" "#325A9B" "#FEAF16" "#F8A19F"
+"#90AD1C" "#F6222E" "#1CFFCE" "#2ED9FF" "#B10DA1" "#C075A6" "#FC1CBF" "#B00068"
+"#FBE426" "#FA0087"
+
 ```

### 2024-11-18 draftdata.Rmd
visualtextdarkmodecorrections

@@
 
+```{=html}
+<style>
+body {
+text-align: left;
+line-height: 1.5;
+}
+
+h1, .h1, h2, .h2, h3, .h3 {
+  margin-top: 24px;
+  line-height: 1;
+}
+
+</style>
+```
 ```{r, globalsettings, echo=FALSE, warning=FALSE, results='hide'}
@@
 
-```{r klippy, echo=FALSE, include=FALSE}
+```{r klippy, echo=FALSE, include=TRUE}
 klippy::klippy(position = c('top', 'right'))
@@
 
-[**CHECK AGAIN BEFORE SUBMITTING**]:\
-A total of four models, including a null model, were estimated.
-The null model excludes structural effects, focusing solely on reciprocity and density.
-The first model incorporates all structural network effects.
-Model 2 builds on this by adding the ego-level effect of gender.
-In Model 3, the ego-level control variable for h-index is included.
-\
-**[NEEDED?]** Finally, Model 4 is similar to Model 3 but replaces the quadratic effect of indegree popularity with a simple structural effect of indegree popularity.
-
 # Ethical concerns
@@
 
-```{=html}
 <!-- -->
-```
+
 -   We developed the Stata command h_index and R package hindex.
@@
 \_igraph: Network Analysis and Visualization in R\_.
-doi:10.5281/zenodo.7682609 \<https://doi.org/10.5281/zenodo.7682609\>, R package version 2.1.1.9005, \<https://CRAN.R-project.org/package=igraph\>.
+<doi:10.5281/zenodo.7682609> \<[[https://doi.org/10.5281/zenodo.7682609\\\\](https://doi.org/10.5281/zenodo.7682609\\){.uri}]([https://doi.org/10.5281/zenodo.7682609\\](https://doi.org/10.5281/zenodo.7682609\){.uri}){.uri}\>, R package version 2.1.1.9005, \<[[https://CRAN.R-project.org/package=igraph\\\\](https://CRAN.R-project.org/package=igraph\\){.uri}]([https://CRAN.R-project.org/package=igraph\\](https://CRAN.R-project.org/package=igraph\){.uri}){.uri}\>.
 
@@
 -   Pedersen T (2024). *ggraph: An Implementation of Grammar of Graphics for Graphs and Networks*.
-R package version 2.2.1.9000, https://github.com/thomasp85/ggraph, [https://ggraph.data-imaginist.com](https://ggraph.data-imaginist.com/).
+R package version 2.2.1.9000, <https://github.com/thomasp85/ggraph>, [https://ggraph.data-imaginist.com](https://ggraph.data-imaginist.com/).
+
+------------------------------------------------------------------------
 

### 2024-11-18 draftintro.Rmd
visualtextdarkmodecorrections

@@
 text-align: left;
-font-family: Times;
+line-height: 1.5;
 }
@@
   margin-top: 24px;
-  font-family: Times;
+  line-height: 1;
 }
@@
 
--   **RQ1a:** To what extent does gender homophily occur across all co-publications of the staff in the Sociology and Political Science Departments at Radboud University?
+-   ***RQ1a:** To what extent does gender homophily occur across all co-publications of the staff in the Sociology and Political Science Departments at Radboud University?*
 
--   **RQ1b:** To what extent do the two departments differ in their levels of gender homophily?
+-   ***RQ1b:** To what extent do the two departments differ in their levels of gender homophily?*
 
@@
 
--   **RQ2:** To what extent can gender homophily in collaboration networks be explained by preferences at the dyadic level, controlling for structural network and individual-level covariates?
+-   ***RQ2:** To what extent can gender homophily in collaboration networks be explained by preferences at the dyadic level, controlling for structural network and individual-level covariates?*
 

### 2024-11-18 drafttheory.Rmd
visualtextdarkmodecorrections

@@
 # Theory Draft
+
+### Theory
+
+Understanding collaboration patterns in academia is crucial for unpacking the mechanisms behind the formation of scholarly networks.
+One key principle that shapes these networks is **homophily**, the tendency of individuals to associate with others who are similar to them (@McPherson2001).
+In the context of academic collaborations, **gender homophily**—the preference for scholars to collaborate with others of the same gender—has been widely observed.
+Research consistently shows that men tend to collaborate more frequently with other men, and women with other women ( @Horta2022; @Kwiek2021).
+However, the degree and dynamics of this homophily can vary across disciplines and contexts, making it a fertile ground for investigation.
+
+#### Hypothesis 1: Gender Homophily in Collaboration Networks
+
+The first hypothesis centers on the presence of gender homophily across two academic departments: Political Science and Sociology at Radboud University.
+Based on the homophily principle, I expect scholars to prefer same-gender collaborators, leading to gendered clustering in co-authorship networks.
+
+-   ***H1**: Across the collaboration networks of both departments, scholars are more likely to collaborate with same-gender peers than with different-gender peers, indicating the presence of gender homophily.*
+
+This hypothesis aligns with prior studies that highlight gender homophily as a key feature of collaboration networks in academia (@Kwiek2021).
+However, the extent to which this tendency manifests may depend on the structural characteristics of each department, as well as broader societal norms and stereotypes.
+
+#### Hypothesis 2: Variation in Gender Homophily Between Departments
+
+While gender homophily is a general phenomenon, its intensity may vary across disciplines due to their differing gender dynamics and societal perceptions.
+Sociology, often perceived as a more gender-balanced or even female-leaning field, may exhibit weaker gender homophily compared to Political Science, which is often associated with traditionally masculine traits such as rationality and assertiveness.
+These stereotypes may influence collaboration patterns, with scholars in more male-dominated fields showing stronger gender homophily (@Kwiek2021).
+
+-   ***H2**: Scholars in the Sociology Department exhibit weaker gender homophily in their collaborations than those in the Political Science Department.*
+
+This hypothesis builds on the idea that the gender composition and cultural norms of academic disciplines shape collaboration preferences.
+In sociology, where gender parity is more pronounced, collaboration across genders may be more normalized, reducing homophilic tendencies.
+
+#### Hypothesis 3: The Influence of Prestige on Gender Homophily
+
+While homophily can drive collaboration patterns, prestige also plays a critical role.
+Scholars are often drawn to collaborate with those who have high academic prestige, typically measured through metrics such as publication in high-impact journals or h-index scores (@Bornmann2020).
+This "prestige effect" may weaken the influence of gender homophily, as the opportunity to collaborate with a prestigious scholar may outweigh same-gender preferences.
+
+-   ***H3**: Gender homophily is less influential in collaboration decisions when the potential collaborator has a high level of academic prestige (e.g., a strong publication record in high-prestige journals).*
+
+This hypothesis posits that prestige serves as a countervailing force to homophily.
+Collaboration with high-prestige individuals is a strategic choice, driven by the potential for increased visibility and career advancement, which may diminish the salience of gender in collaboration decisions.
+
+### Theoretical Framework
+
+The theoretical framework draws on both **homophily theory** and the concept of **preferential attachment** in academic networks.
+The homophily principle explains the tendency for scholars to form ties with others who share their gender, while preferential attachment highlights the allure of prestigious collaborators ( @Merton1968; @Broido2019).
+Together, these mechanisms shape the structure and evolution of collaboration networks.
+
+Prior research suggests that men, particularly in male-dominated fields, are more likely to form same-gender ties, reinforcing gender inequalities in academia (@Kwiek2021).
+However, as women gain visibility and prestige, their collaboration opportunities expand, potentially mitigating homophily effects (@Knobloch2013).
+Understanding these dynamics requires a nuanced approach that accounts for both individual preferences and structural network constraints.
+
+By addressing these hypotheses, this study contributes to the broader literature on academic collaboration and gender dynamics, offering insights into how societal norms and institutional contexts influence the formation of scholarly networks.
+
+# prior notes:
 
@@
 
+Broido, A. D., & Clauset, A. (2019). Scale-free networks are rare. *Nature communications*, *10*(1), 1017. <https://doi.org/10.1038/s41467-019-08746-5>
+
+@Broido2019
+
+Merton, Robert K. 1968. “The Matthew Effect in Science: The Reward and Communication Systems of Science Are Considered.” *Science* 159 (3810): 56–63.
+
+@Merton1968
+
+Knobloch-Westerwick, Silvia, Carroll J Glynn, and Michael Huge.
+2013. “The Matilda Effect in Science Communication: An Experiment on Gender Bias in Publication Quality Perceptions and Collaboration Interest.” *Science Communication* 35 (5): 603–25.
+
+@Knobloch2013
+
+------------------------------------------------------------------------
+
 # References

### 2024-11-18 weekbacktrack.Rmd
visualtextdarkmodecorrections

@@
 |                                                                                                   |                                                              |                                                                 |                                                                                            |                                                                               |                                                                            |                                                                                      |
-| Continue description & plotting [S3]                                                              |                                                              |                                                                 | Continue description & plotting [S3]                                                       | Data & methods part [W]                                                       |                                                                            | estimate model [S5]                                                                  |
-|                                                                                                   |                                                              |                                                                 |                                                                                            |                                                                               |                                                                            |                                                                                      |
-|                                                                                                   |                                                              |                                                                 |                                                                                            |                                                                               |                                                                            | goodness of fit [S6]                                                                 |
+| Continue description & plotting [S3]                                                              |                                                              |                                                                 | Continue description & plotting [S3]                                                       | Data & methods part [W]                                                       |                                                                            |                                                                                      |
 +---------------------------------------------------------------------------------------------------+--------------------------------------------------------------+-----------------------------------------------------------------+--------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------+----------------------------------------------------------------------------+--------------------------------------------------------------------------------------+
@@
 |                                                                                                   |                                                              |                                                                 |                                                                                            |                                                                               |                                                                            |                                                                                      |
-| Check in with Jochem                                                                              |                                                              |                                                                 | Results [W]                                                                                | Finish Results [W]                                                            | email Jochem if delay                                                      | Rework intro [W]                                                                     |
+| Check in with Jochem!
+|                                                              |                                                                 | estimate model [S5]                                                                        | Results [W]                                                                   | email Jochem if delay                                                      | Rework intro [W]                                                                     |
+|                                                                                                   |                                                              |                                                                 |                                                                                            |                                                                               |                                                                            |                                                                                      |
+|                                                                                                   |                                                              |                                                                 | goodness of fit [S6]                                                                       |                                                                               |                                                                            |                                                                                      |
 +---------------------------------------------------------------------------------------------------+--------------------------------------------------------------+-----------------------------------------------------------------+--------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------+----------------------------------------------------------------------------+--------------------------------------------------------------------------------------+

### 2024-11-23 descriptivestry.Rmd
modelestimates-GOFs-desresults-darkgraph

--- 2024-11-17 descriptivestry.Rmd
@@
 <html lang="en">
+
 <head>
+
 <meta charset="UTF-8">
+
 <meta name="viewport" content="width=device-width, initial-scale=1.0">
+
 <title>My Descriptives</title>
+
 <link rel="stylesheet" href="styles.css"> <!-- Link to the CSS file I created for dark mode code chunks -->
@@
 </head>
+
 </html>
 
-```{r, globalsettings, echo=FALSE, warning=FALSE, results='hide'}
+```{r globalsettings, echo=FALSE, warning=FALSE, results='hide'}
 library(knitr)
@@
 # Getting started
+
 ```{r clean}
@@
 ## Packages
-```{r package}
+
+```{r package, hide=TRUE}
 require(tidyverse)
@@
 require(ggraph)
+require(ggplot2)
 
@@
 
+require(RColorBrewer)
+
 ```
@@
 Functions chunk
-```{r functions 1}
+
+```{r functions 1, hide =TRUE}
 fpackage.check <- function(packages) {
@@
 More functions
-```{r functions 2}
+
+```{r functions 2, hide=TRUE}
 fcolnet <- function(data = scholars, university = "RU", discipline = "sociology"+"political science", waves = list(c(2015,
@@
 Scholar data
+
 ```{r scholar data}
@@
 
-```{r saving schoalr output}
+```{r saving scholar output}
 # save the output of your function
@@
                 waves = list(c(2015, 2018), c(2019, 2023)), 
-                type = c("all")) # all, first, last # which ties in there
-
-# USE not all but first or last so the ties are directed from "perspective" of first author of the publications 
-# usually first author has most prestige
+                type = c("first"))
 ```
@@
 Ego data
+
 ```{r df_ego data}
@@
 
-# Descriptives
+# Descriptives - Demographics 
+The following graphs represent the segregation of the network based on gender and on H-index for the wave of interest (2015-2018).
 
@@
 descriptives (mean etc.) in whole sample
+
 ```{r sum gender}
@@
 gender counts across whole sample (0 = female, 1 = male)
+
 ```{r counts gender-all}
@@
 
-overall gender distribution in sample
-```{r}
-# Create the histogram
-ggplot(df_ego, aes(x = gender))+
-  geom_bar(color = "darkgrey", fill ="#B3DE69", width = 0.75)+
-  labs(title = "Histogram of Gender", x = "Gender\n (0 = female, 1 = male)", y = "Count") + theme(plot.title = element_text(hjust = 0.5, face = "bold"))
+Histogram: overall gender distribution in sample
+
+```{r histogram gender }
+# Convert gender to a factor to avoid errors
+df_ego$gender <- as.factor(df_ego$gender)
+# Create the histogram with a dark theme and two colors for bars
+ggplot(df_ego, aes(x = gender, fill = gender)) +
+  geom_bar(color = "darkgrey", width = 0.6) +  # Add borders for bars
+  scale_fill_manual(
+    values = c("0" = "#FFFFB3", "1" = "#80B1D3"),  # Custom colors: yellow for females, blue for males
+    labels = c("Female", "Male")  # Optional: customize legend labels
+  ) +
+  labs(
+    title = "Gender Distribution",
+    x = "Gender\n (0 = female, 1 = male)",
+    y = "Count",
+    fill = "Gender"  # Legend title
+  ) +
+  theme_minimal(base_family = "Arial") +  # Clean, minimal base theme
+  theme(
+    plot.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark background
+    panel.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark panel background
+    panel.grid.major = element_line(color = "#444444"),  # Subtle grid lines
+    panel.grid.minor = element_line(color = "#444444"),
+    axis.text = element_text(color = "#f0f0f0"),  # White axis text
+    axis.title = element_text(color = "#f0f0f0", face = "bold"),  # Bold white axis titles
+    plot.title = element_text(color = "#f0f0f0", face = "bold", hjust = 0.5),  # White centered title
+    legend.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark legend background
+    legend.text = element_text(color = "#f0f0f0"),  # White legend text
+    legend.title = element_text(color = "#f0f0f0")  # White legend title
+    )
 
@@
 Genders per department (0 = female, 1 = male)
+
 ```{r gender per dep.}
@@
 descriptives (mean etc.)
+
 ```{r summary h index}
@@
 ```
-Overall  (INSERT YEARS STILL)
+
+Overall(2015-2018)
+
 ```{r hist h index}
 # Histogram of prestige scores for Wave 1
-hist(df_ego$h_index, breaks = 30, main = "Distribution of H-Index from yearX to yearX",     xlab = "H Index", ylab = "Frequency", col = "#B3DE69") # INSERT YEARS OF WAVE/TIME FRAME STILL
+
+# Create a data frame for ggplot2 
+df_h_index <- data.frame(h_index = df_ego$h_index)
+
+# Generate the histogram with ggplot2
+ggplot(df_h_index, aes(x = h_index)) +
+  geom_histogram(
+    bins = 30,
+    fill = "#FFFFB3",  # Bar color
+    color = "black"    # Border color for bars
+  ) +
+  labs(
+    title = "Distribution of H-Index from 2015 to 2018",
+    x = "H Index",
+    y = "Frequency"
+  ) +
+  theme_minimal(base_family = "Arial") +  # Clean, minimal base theme
+  theme(
+    plot.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark background
+    panel.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark panel background
+    panel.grid.major = element_line(color = "#444444"),  # Subtle grid lines
+    panel.grid.minor = element_line(color = "#444444"),
+    axis.text = element_text(color = "#f0f0f0"),  # White axis text
+    axis.title = element_text(color = "#f0f0f0", face = "bold"),  # Bold white axis titles
+    plot.title = element_text(color = "#f0f0f0", face = "bold", hjust = 0.5)  # White centered title
+  )
+
 ```
@@
 H index per department
+
 ```{r table per dep h index}
@@
 ```
-
-## Ego network
-
-### basic descriptives
-
-Nr. of nodes
-```{r nodes}
-vcount(test_w1)
-```
-
-Nr. of edges
-```{r edges}
-ecount(test_w1)
-```
-
-Dyad census
-    ```{r dyad cen}
-
-igraph::dyad_census(test_w1)
-    ```
-
-Triad-census
-    ```{r triad cen}
-igraph::triad_census(test_w1)
-    ```
-
-Edge-density
-    ```{r edge dens}
-# edge density
-igraph::edge_density(test_w1)
-    ```
-
-### more in depth:
-
-reciprocity
-    ```{r recip}
-reciprocity(test_w1, ignore.loops = TRUE, mode = c("default", "ratio"))
-    ```
-reciprocity = 1 makes sense since the ties are undirected rn
-
-degree centrality / degreee?
-    ```{r degree}
-
-degree_testw1 <- degree(test_w1)
-degree_testw1 <- as.data.frame(degree_testw1)
-ggplot(degree_testw1, aes(as.numeric(degree_testw1), colour = as.numeric(degree_testw1) )) +
-  geom_histogram(binwidth = .9) +
-  labs(
-    title = "Distribution Degrees Wave 1",
-    x = "Distribution of Degrees",
-    y = "Count"  ) +
-  ylim(0, 65)
-
-    ```
-
-Betweenness centrality /betweenness?
-    ```{r betweenness}
-betweenness_w1 <- igraph::betweenness(test_w1, directed = T)
-betweenness_w1 <- as.data.frame(betweenness_w1)
-ggplot(betweenness_w1, aes(as.numeric(betweenness_w1), colour = as.numeric(betweenness_w1))) +
-  geom_histogram(binwidth = 1.2) +
-  labs(
-    title = "Distribution Betweenness Wave 1",
-    x = "Distribution of Betweenness",
-    y = "Count")
-
-    ```
-
-Clustering
-    ```{r clustering}
-#clustering w1
-clustering_w1 <- igraph::transitivity(test_w1, type = "local")
-clustering_w1 <- as.data.frame(clustering_w1)
-ggplot(clustering_w1, aes(as.numeric(clustering_w1), colour = as.numeric(clustering_w1) )) +
-  geom_histogram(binwidth = .05) +
-  labs(
-    title = "Distribution Clustering Wave 1",
-    x = "Distribution of Clustering",
-    y = "Count" )
-    ```
-
-## Network-level descriptives
-
-Density
-    ```{r density}
-density_w1 <- igraph::edge_density(test_w1)
-density_w1
-    ```
-
-Average path length
-    ```{r path length}
-mean((ego_size(test_w1, order = 2, mode = "out") - 1)/vcount(test_w1))
-    ```
-
-Segregation
-    - Mortons I
-    - also graphs below
-```{r plot}
-
-plot(test_w1,
-     vertex.label = NA,
-     edge.width = 0.2,
-     edge.arrow.size =0.2)
-```
-
-### Plotting: Gender - igraph
-#### with isolates
-```{r plot gender}
-# names(df_ego) #see labels of variables
-
-plot(test_w1,
-     vertex.color = ifelse(df_ego$gender == 1, "#FFED6F", "#80B1D3"), # now, I can use actor attributes for plotting.
-# here: if gender = 1 (aka man) then red dot, if not then blue 
-  vertex.label = NA,
-  vertex.size = 7.5,
-  edge.width = 0.5,
-  edge.arrow.size = 0.1,
-  main = "Network with isolates [yellow = female, blue = male]")
-
-# if you dont want plot to turn, save the layout (look at SNASS)
-```
-
-#### without isolates
-```{r removing isolates}
-indegr_w1 <- igraph::degree(test_w1, mode = "in")
-
-isolates_w1 <- V(test_w1)[degree(test_w1, mode = "all") == 0]
-
-noisolates_w1 <- delete_vertices(test_w1, isolates_w1)
-
-gsize(noisolates_w1) # edges
-
-gorder(noisolates_w1) # vertices
-```
-
-```{r plot wo isolates}
-plot(noisolates_w1,
-  vertex.color = ifelse(df_ego$gender == 1, "#80B1D3", "#FFED6F"), # now, I can use actor attributes for plotting.
-  # here: if gender = 1 (aka man) then red dot, if not then blue 
-  vertex.label = NA,
-  vertex.size = 9,
-  vertex.frame.color = "black",
-  edge.curved = 0.2,
-  edge.arrow.size = 0.3,
-  edge.color = "gray",
-  edge.width = 0.2,
-  main = "Network without isolates [yellow = female, blue = male]")
-```
-
-### Plotting: h-index -ggraph
-Credits to Hannah Groennou for the basis of the code of these graphs. 
-#### with isolates ?
-```{r}
-
-indegr_w1 <- degree(test_w1, mode = "in")
-
-# assign h-index to scholar
-V(test_w1)$h_index <- df_ego$h_index
-V(test_w1)$indegree <- indegr_w1
-
-#set size of plot
-options(repr.plot.width = 15, repr.plot.height = 18)
-
-#plot wave 1 with isolates
-p_iso <- ggraph(test_w1,
-       layout = "fr") +
-  geom_edge_link(color = "#BEBADA", width = 0.5) +
-  geom_node_point(aes(size = indegree, color = h_index)) + 
-  scale_size(range = c(3, 10)) + 
-  scale_color_gradient(low = "red", high = "blue") + 
-  theme_void()
-
-p_iso + labs(title = "Network with isolates",
-        subtitle = "Plot of indegree and H-index",
-        caption = "Data refer to: Scholars RU sociology and political science departments") + theme(plot.title = element_text(hjust = 0.5, face = "bold"), plot.subtitle = element_text(hjust=0.5), plot.caption = element_text(hjust = 1))
-```
-
-#### without isolates
-```{r}
-
-indegr_w1 <- degree(test_w1, mode = "in")
-
-# assign h-index to scholar
-V(test_w1)$h_index <- df_ego$h_index
-V(test_w1)$indegree <- indegr_w1
-
-#remove isolates
-noisolates_w1 <- delete_vertices(test_w1, V(test_w1)[degree(test_w1) == 0])
-
-#set size of plot
-options(repr.plot.width = 15, repr.plot.height = 15)
-
-#plot wave 1 without isolates 
-p_noiso <- ggraph(noisolates_w1,
-       layout = "fr") +
-  geom_edge_link(color = "#BEBADA", width = 0.7) +
-  geom_node_point(aes(size = indegree, color = h_index)) + 
-  scale_size(range = c(3, 10)) + 
-  scale_color_gradient(low = "red", high = "blue") + 
-  theme_void()
-
-p_noiso + labs(title = "Network without isolates",
-        subtitle = "Plot of indegree and H-index",
-        caption = "Data refer to: Scholars RU sociology and political science departments") + theme(plot.title = element_text(hjust = 0.5, face = "bold"), plot.subtitle = element_text(hjust=0.5))
-
-# allowed values for the font face include: “plain”, “italic”, “bold” and “bold.italic”.
-
-```
-
-##### H-index per department
-```{r}
-indegr_w1 <- degree(test_w1, mode = "in")
-
-# assign h-index to scholar
-V(test_w1)$h_index <- df_ego$h_index
-# assign discipline to scholar
-V(test_w1)$discipline <- df_ego$discipline.24
-
-V(test_w1)$indegree <- indegr_w1
-
-#remove isolates
-noisolates_w1 <- delete_vertices(test_w1, V(test_w1)[degree(test_w1) == 0])
-
-#set size of plot
-options(repr.plot.width = 15, repr.plot.height = 15)
-
-#plot wave 1 without isolates 
-p_noiso <- ggraph(noisolates_w1,
-       layout = "fr") +
-  geom_edge_link(color = "#BEBADA", width = 0.7) +
-  geom_node_point(aes(size = indegree, color = h_index, shape = as.factor(discipline))) + 
-  scale_size(range = c(3, 10)) + 
-  scale_color_gradient(low = "red", high = "blue") + 
-  theme_void()
-
-p_noiso + labs(title = "Departments without isolates",
-        subtitle = "Plot of indegree and H-index",
-        caption = "Data refer to scholars from Radboud University.") + theme(plot.title = element_text(hjust = 0.5, face = "bold"), plot.subtitle = element_text(hjust=0.5))
-
-# allowed values for the font face include: “plain”, “italic”, “bold” and “bold.italic”.
-
-```
-
-### Plotting gender - ggraph 
-#### with isolates per department 
-```{r}
-#assign gender to scholar 
-V(test_w1)$gender <- df_ego$gender
-
-# assign discipline to scholar
-V(test_w1)$discipline <- df_ego$discipline.24
-
-V(test_w1)$indegree <- indegr_w1
-
-p_gender <- ggraph(test_w1,
-  layout = "fr") +
-  geom_edge_link(color = "#BEBADA", width = 0.5) +
-  geom_node_point(aes(size = indegree, color = as.factor(discipline), shape = as.factor(gender))) +   
-  scale_size(range = c(3, 10)) + 
-  theme_void()
-
-p_gender + labs(title = "Departments with isolates",
-        subtitle = "Plot of indegree and gender",
-        caption = "Gender: 0 = female, 1 = male.\n Data refer to scholars from Radboud University.") + theme(plot.title = element_text(hjust = 0.5, face = "bold"), plot.subtitle = element_text(hjust=0.5), plot.caption = element_text(hjust = 1))
-
-```
-
-#### without isolates per department 
-```{r}
-#assign gender to scholar 
-V(test_w1)$gender <- df_ego$gender
-
-# assign disciplines to scholars
-V(test_w1)$discipline <- df_ego$discipline.24
-V(test_w1)$indegree <- indegr_w1
-
-#remove isolates
-noisolates_w1 <- delete_vertices(test_w1, V(test_w1)[degree(test_w1) == 0])
-
-p_noisgender <- ggraph(noisolates_w1,
-  layout = "fr") +
-  geom_edge_link(color = "#BEBADA", width = 0.5) +
-  geom_node_point(aes(size = indegree, color = as.factor(discipline), shape = as.factor(gender))) +   
-  scale_size(range = c(3, 10)) + 
-  theme_void()
-
-p_noisgender + labs(title = "Departments without isolates",
-        subtitle = "Plot of indegree and gender",
-        caption = "Gender: 0 = female, 1 = male.\n Data refer to scholars from Radboud University.") + theme(plot.title = element_text(hjust = 0.5, face = "bold"), plot.subtitle = element_text(hjust=0.5), plot.caption = element_text(hjust = 1))
-
-```
-
-### Plotting h index and gender -ggraph
-#### with isolates 
-```{r}
-#assign gender to scholar 
-V(test_w1)$gender <- df_ego$gender
-# V(test_w1)$gender <- ifelse(df_ego$gender >= 0.5,1,0)
-
-# assign h-index to scholar
-V(test_w1)$h_index <- df_ego$h_index
-V(test_w1)$indegree <- indegr_w1
-
-p_gender <- ggraph(test_w1,
-  layout = "fr") +
-  geom_edge_link(color = "#BEBADA", width = 0.5) +
-  geom_node_point(aes(size = indegree, color = h_index, shape = as.factor(gender))) +   
-  scale_size(range = c(3, 10)) + 
-  scale_color_gradient(low = "red", high = "blue") + 
-  theme_void()
-
-p_gender + labs(title = "Network with isolates",
-        subtitle = "Plot of indegree, H-index and gender",
-        caption = "Gender: 0 = female, 1 = male.\n Data refer to: Scholars RU sociology and political science departments.") + theme(plot.title = element_text(hjust = 0.5, face = "bold"), plot.subtitle = element_text(hjust=0.5), plot.caption = element_text(hjust = 1))
-
-```
-
-#### without isolates
-
-```{r gen without iso}
-#assign gender to scholar 
-V(test_w1)$gender <- df_ego$gender
-
-# assign h-index to scholar
-V(test_w1)$h_index <- df_ego$h_index
-V(test_w1)$indegree <- indegr_w1
-
-#remove isolates
-noisolates_w1 <- delete_vertices(test_w1, V(test_w1)[degree(test_w1) == 0])
-
-p_noisogender <- ggraph(noisolates_w1,
-  layout = "fr") +
-  geom_edge_link(color = "#BEBADA", width = 0.5) +
-  geom_node_point(aes(size = indegree, color = h_index, shape = as.factor(gender))) +   
-  scale_size(range = c(3, 10)) + 
-  scale_color_gradient(low = "red", high = "blue") + 
-  theme_void()
-
-p_noisogender + labs(title = "Network without isolates",
-        subtitle = "Plot of indegree, H-index and gender",
-        caption = "Gender: 0 = female, 1 = male.\n Data refer to: Scholars RU sociology and political science departments.") + theme(plot.title = element_text(hjust = 0.5, face = "bold"), plot.subtitle = element_text(hjust=0.5))
-
-```
-
-# Detour: Colors
-
-```{r mypalette, include = FALSE, eval = FALSE, hide = TRUE}
-# palette i like:
-palette("Set 3");  sinplot("Set 3")
-palette.swatch("Set 3")
-palette.colors(palette = "Set 3")
- "#8DD3C7" "#FFFFB3" "#BEBADA" "#FB8072" "#80B1D3" "#FDB462"
- "#B3DE69" "#FCCDE5" "#D9D9D9" "#BC80BD" "#CCEBC5" "#FFED6F"
-```
-
-```{r colors in R, include = TRUE, eval = FALSE, hide = TRUE}
-colors (distinct = TRUE) # prints all colors R knows
-palette.pals()
-#  [1] "R3"              "R4"              "ggplot2"        
-#  [4] "Okabe-Ito"       "Accent"          "Dark 2"         
-#  [7] "Paired"          "Pastel 1"        "Pastel 2"       
-# [10] "Set 1"           "Set 2"           "Set 3"          
-# [13] "Tableau 10"      "Classic Tableau" "Polychrome 36"  
-# [16] "Alphabet"
-
-palette.colors(palette = "-palette name here-")
-# [1] "#000000" "#E69F00" "#56B4E9" "#009E73" "#F0E442" "#0072B2"
-# [7] "#D55E00" "#CC79A7" "#999999"
-```
-
-```{r look at colors PLOT, include = TRUE, eval = FALSE, hide = TRUE}
-## Demonstrate the colors 1:8 in different palettes using a custom matplot()
-sinplot <- function(main=NULL, n = 8) {
-    x <- outer(
-	seq(-pi, pi, length.out = 50),
-	seq(  0, pi, length.out = n),
-	function(x, y) sin(x - y)
-    )
-    matplot(x, type = "l", lwd = 4, lty = 1, col = 1:n, ylab = "", main=main)
-}
-sinplot("default palette")
-
-palette("R3");        sinplot("R3")
-palette("Okabe-Ito"); sinplot("Okabe-Ito")
-palette("Tableau")  ; sinplot("Tableau", n = 10) # i like 
-palROB <- colorRampPalette(c("red", "darkorange2", "blue"), space = "Lab")
-palette(palROB(16)); sinplot("palROB(16)", n = 16) # the orange purple blue rainbow retro vibe yay 
-palette("default") # reset
-```
-
-```{r look at colors SWATCH, include = TRUE, eval = FALSE, hide = TRUE}
-palette.swatch <- function(palette = palette.pals(), n = 8, nrow = 8,
-                           border = "black", cex = 1, ...)
-{
-     cols <- sapply(palette, palette.colors, n = n, recycle = TRUE)
-     ncol <- ncol(cols)
-     nswatch <- min(ncol, nrow)
-     op <- par(mar = rep(0.1, 4),
-               mfrow = c(1, min(5, ceiling(ncol/nrow))),
-     	       cex = cex, ...)
-     on.exit(par(op))
-     while (length(palette)) {
- 	subset <- seq_len(min(nrow, ncol(cols)))
- 	plot.new()
- 	plot.window(c(0, n), c(0.25, nrow + 0.25))
- 	y <- rev(subset)
- 	text(0, y + 0.1, palette[subset], adj = c(0, 0))
- 	y <- rep(y, each = n)
- 	rect(rep(0:(n-1), n), y, rep(1:n, n), y - 0.5,
- 	     col = cols[, subset], border = border)
- 	palette <- palette[-subset]
- 	cols    <- cols [, -subset, drop = FALSE]
-     }
-}
-
-palette.swatch()
-
-palette.swatch(n = 26) # show full "Alphabet"; recycle most others
-
-```

### 2024-11-23 draft1desresults.Rmd
modelestimates-GOFs-desresults-darkgraph

---
title: "Draft Result Descriptives"
author: "Verooo"
date: "2024-11-23"
output: html_document
---

<html lang="en">

<head>

<meta charset="UTF-8">

<meta name="viewport" content="width=device-width, initial-scale=1.0">

<title>My Descriptives</title>

<link rel="stylesheet" href="styles.css"> <!-- Link to the CSS file I created for dark mode code chunks -->

</head>

</html>

```{r globalsettings, echo=FALSE, warning=FALSE, results='hide'}
library(knitr)

knitr::opts_chunk$set(echo = TRUE)
opts_chunk$set(tidy.opts=list(width.cutoff=100),tidy=TRUE, warning = FALSE, message = FALSE,comment = "#>", cache=TRUE, class.source=c("test"), class.output=c("test2"))
options(width = 100)
rgl::setupKnitr()

colorize <- function(x, color) {sprintf("<span style='color: %s;'>%s</span>", color, x) }

```

```{r klippy, echo=FALSE, include=TRUE}
klippy::klippy(position = c('top', 'right'))
#klippy::klippy(color = 'darkred')
#klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done')
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

# Getting started

```{r clean}
rm(list = ls())
```

## Packages

```{r package, hide=TRUE}
require(tidyverse)
require(RSiena)
require(RsienaTwoStep)

#install.packages("data.table")
require(data.table)  # mainly for faster data handling
# install.packages('xml2')
require(xml2)
# install.packages('rvest')
require(rvest)
require(igraph)
require(ggraph)
require(ggplot2)

#install.packages('visNetwork')
require(visNetwork)
#install.packages('threejs')
require(threejs)
#install.packages('networkD3')
require(networkD3)

require(RColorBrewer)

```

## Functions

Functions chunk

```{r functions 1, hide =TRUE}
fpackage.check <- function(packages) {
    lapply(packages, FUN = function(x) {
        if (!require(x, character.only = TRUE)) {
            install.packages(x, dependencies = TRUE)
            library(x, character.only = TRUE)
        }
    })
}

fsave <- function(x, file = NULL, location = "./data/processed/") {
    ifelse(!dir.exists("data"), dir.create("data"), FALSE)
    ifelse(!dir.exists("data/processed"), dir.create("data/processed"), FALSE)
    if (is.null(file))
        file = deparse(substitute(x))
    datename <- substr(gsub("[:-]", "", Sys.time()), 1, 8)
    totalname <- paste(location, file, "_", datename, ".rda", sep = "")
    save(x, file = totalname)  #need to fix if file is reloaded as input name, not as x. 
}

fload <- function(filename) {
    load(filename)
    get(ls()[ls() != "filename"])
}

fshowdf <- function(x, ...) {
    knitr::kable(x, digits = 2, "html", ...) %>%
        kableExtra::kable_styling(bootstrap_options = c("striped", "hover")) %>%
        kableExtra::scroll_box(width = "100%", height = "300px")
}

# this is the most important one. We created it in the previous script

f_pubnets <- function(df_scholars = df, list_publications = publications, discip = "sociology"+"political science", affiliation = "RU",
    waves = list(wave1 = c(2018, 2019, 2020), wave2 = c(2021, 2022, 2023))) {

    publications <- list_publications %>%
        bind_rows() %>%
        distinct(title, .keep_all = TRUE)

    df_scholars %>%
        filter(affil1 == affiliation | affil2 == affiliation) %>%
        filter(discipline == discip) -> df_sel

    networklist <- list()
    for (wave in 1:length(waves)) {
        networklist[[wave]] <- matrix(0, nrow = nrow(df_sel), ncol = nrow(df_sel))
    }

    publicationlist <- list()
    for (wave in 1:length(waves)) {
        publicationlist[[wave]] <- publications %>%
            filter(gs_id %in% df_sel$gs_id) %>%
            filter(year %in% waves[[wave]]) %>%
            select(author) %>%
            lapply(str_split, pattern = ",")
    }

    publicationlist2 <- list()
    for (wave in 1:length(waves)) {
        publicationlist2[[wave]] <- publicationlist[[wave]]$author %>%
            # lowercase
        lapply(tolower) %>%
            # Removing diacritics
        lapply(stri_trans_general, id = "latin-ascii") %>%
            # only last name
        lapply(word, start = -1, sep = " ") %>%
            # only last last name
        lapply(word, start = -1, sep = "-")
    }

    for (wave in 1:length(waves)) {
        # let us remove all publications with only one author
        remove <- which(sapply(publicationlist2[[wave]], FUN = function(x) length(x) == 1) == TRUE)
        publicationlist2[[wave]] <- publicationlist2[[wave]][-remove]
    }

    for (wave in 1:length(waves)) {
        pubs <- publicationlist2[[wave]]
        for (ego in 1:nrow(df_sel)) {
            # which ego?
            lastname_ego <- df_sel$lastname[ego]
            # for all publications
            for (pub in 1:length(pubs)) {
                # only continue if ego is author of pub
                if (lastname_ego %in% pubs[[pub]]) {
                  aut_pot <- which.max(pubs[[pub]] %in% lastname_ego)
                  # only continue if ego is first author of pub
                  if (aut_pot == 1) {
                    # check all alters/co-authors
                    for (alter in 1:nrow(df_sel)) {
                      # which alter
                      lastname_alter <- df_sel$lastname[alter]
                      if (lastname_alter %in% pubs[[pub]]) {
                        networklist[[wave]][ego, alter] <- networklist[[wave]][ego, alter] + 1
                      }
                    }
                  }
                }
            }
        }
    }
    return(list(df = df_sel, network = networklist))
}

```

More functions

```{r functions 2, hide=TRUE}
fcolnet <- function(data = scholars, university = "RU", discipline = "sociology"+"political science", waves = list(c(2015,
    2018), c(2019, 2023)), type = c("first")) {

    # step 1
    demographics <- do.call(rbind.data.frame, data$demographics)
    demographics <- demographics %>%
        mutate(Universiteit1.22 = replace(Universiteit1.22, is.na(Universiteit1.22), ""), Universiteit2.22 = replace(Universiteit2.22,
            is.na(Universiteit2.22), ""), Universiteit1.24 = replace(Universiteit1.24, is.na(Universiteit1.24),
            ""), Universiteit2.24 = replace(Universiteit2.24, is.na(Universiteit2.24), ""), discipline.22 = replace(discipline.22,
            is.na(discipline.22), ""), discipline.24 = replace(discipline.24, is.na(discipline.24), ""))

    sample <- which((demographics$Universiteit1.22 %in% university | demographics$Universiteit2.22 %in%
        university | demographics$Universiteit1.24 %in% university | demographics$Universiteit2.24 %in%
        university) & (demographics$discipline.22 %in% discipline | demographics$discipline.24 %in% discipline))

    demographics_soc <- demographics[sample, ]
    scholars_sel <- lapply(scholars, "[", sample)

    # step 2
    ids <- demographics_soc$au_id
    nwaves <- length(waves)
    nets <- array(0, dim = c(nwaves, length(ids), length(ids)), dimnames = list(wave = 1:nwaves, ids,
        ids))
    dimnames(nets)

    # step 3
    df_works <- tibble(works_id = unlist(lapply(scholars_sel$work, function(l) l$id)), works_author = unlist(lapply(scholars_sel$work,
        function(l) l$author), recursive = FALSE), works_year = unlist(lapply(scholars_sel$work, function(l) l$publication_year),
        recursive = FALSE))

    df_works <- df_works[!duplicated(df_works), ]

    # step 4
    if (type == "first") {
        for (j in 1:nwaves) {
            df_works_w <- df_works[df_works$works_year >= waves[[j]][1] & df_works$works_year <= waves[[j]][2],
                ]
            for (i in 1:nrow(df_works_w)) {
                ego <- df_works_w$works_author[i][[1]]$au_id[1]
                alters <- df_works_w$works_author[i][[1]]$au_id[-1]
                if (sum(ids %in% ego) > 0 & sum(ids %in% alters) > 0) {
                  nets[j, which(ids %in% ego), which(ids %in% alters)] <- 1
                }
            }
        }
    }

    if (type == "last") {
        for (j in 1:nwaves) {
            df_works_w <- df_works[df_works$works_year >= waves[[j]][1] & df_works$works_year <= waves[[j]][2],
                ]
            for (i in 1:nrow(df_works_w)) {
                ego <- rev(df_works_w$works_author[i][[1]]$au_id)[1]
                alters <- rev(df_works_w$works_author[i][[1]]$au_id)[-1]
                if (sum(ids %in% ego) > 0 & sum(ids %in% alters) > 0) {
                  nets[j, which(ids %in% ego), which(ids %in% alters)] <- 1
                }
            }
        }
    }

    if (type == "all") {
        for (j in 1:nwaves) {
            df_works_w <- df_works[df_works$works_year >= waves[[j]][1] & df_works$works_year <= waves[[j]][2],
                ]
            for (i in 1:nrow(df_works_w)) {
                egos <- df_works_w$works_author[i][[1]]$au_id
                if (sum(ids %in% egos) > 0) {
                  nets[j, which(ids %in% egos), which(ids %in% egos)] <- 1
                }
            }
        }
    }
    output <- list()
    output$data <- scholars_sel
    output$nets <- nets
    return(output)
}
```

## Load data

Scholar data

```{r scholar data}
scholars <- fload("./data/processed/scholars_20240924.rda") 
#make sure to lead fload first of course
```

```{r saving scholar output}
# save the output of your function

test  <- fcolnet(data = scholars, 
                university = "RU", 
                discipline = c("sociology", "political science"),
                waves = list(c(2015, 2018), c(2019, 2023)), 
                type = c("first"))
```

Ego data

```{r df_ego data}
df_ego <- fload("./data/processed/df_ego_20241108.rda")

```

```{r matrix data ego}

test_w1 <- igraph::graph_from_adjacency_matrix(
  test$nets[1,,], # first wave of data. 
  # (thus I select the array of networks and take the first matrix)
  mode = c("directed"),
  weighted = NULL,
  diag = FALSE,
  add.colnames = NULL,
  add.rownames = NULL)

```

## Network Description

The network data we are looking at pertains to 101 scholars and their publications. In the time frame of the wave at hand, namely form 2015 to 2018, we find 47 edges, with 6 reciprocated collaborations 36 ties that are asymmetric. Additionally, there were 5009 occasions in which a ties could have been made but was not. The edge density of 0.004 suggests that from all possible edges, this sample contains relatively few.

In terms of triad-configurations, pertaining to the different possibilities three scholars could collaborate, we find that the most common one is no collaboration at all (configuration '003'). Beyond that, the configuration '012' is also common, meaning that only one directed edge is present in the triad. In our sample it is also common for such edge to be reciprocated, as seen in the third-highes-t count of the triad-configuration '102', a graph with a mutual connection between two vertices. Overall, the seems to be high number of isolates in the sample network.

### Nr. of nodes/vertices

```{r nodes}
vcount(test_w1)
```

### Nr. of edges

```{r edges}
ecount(test_w1)
```

### Dyad census

```{r dyad cen}
igraph::dyad_census(test_w1)
```

### Triad-census

```{r triad cen}
igraph::triad_census(test_w1)
```

```{=html}
<!-- 
TRIAD CONFIGURATIONS (16 possible)

o   Three digits [x, x, x]
  First: nr. of reciprocal ties 
  Middle counts: nr of directed ties
  On right: if no ties
o   D, U, C 
  Down 
  Up 
  Cyclical

1. # 003 A,B,C, the empty graph.

2. # 012 A->B, C, the graph with a single directed edge.

3. # 102 A<->B, C, the graph with a mutual connection between two vertices.

4. # 021D A<-B->C, the out-star.

5. # 021U A->B<-C, the in-star.

6. # 021C A->B->C, directed line.

7. # 111D A<->B<-C.

8. # 111U A<->B->C.

9. #- 030T A->B<-C, A->C.

10.#X 030C A<-B<-C, A->C.

11.#- 201 A<->B<->C.

12.#X 120D A<-B->C, A<->C.

13.#- 120U A->B<-C, A<->C.

14.#- 120C A->B->C, A<->C.

15.#- 210 A->B<->C, A<->C.

16.#X 300 A<->B<->C, A<->C, the complete graph.

-->
```
### Edge-density

```{r edge dens}
# edge density
igraph::edge_density(test_w1)
```

### more in depth:

````{=html}
<!--

#### reciprocity

```{r recip}
reciprocity(test_w1, ignore.loops = TRUE, mode = c("default", "ratio"))
```

-->
````

#### Degree centrality

Degree centrality, often simply called 'degree', measures the number of connections a scholar, or ego, has with other scholars, known as alters. In the context of our dataset, we distinguish between two types of degrees: incoming connections (indegrees) and outgoing connections (outdegrees). Indegrees represent ties directed toward the ego, which in this case signify instances where the ego is **not** the primary author of a paper. Conversely, outdegrees represent ties originating from the ego, indicating collaborations where the ego assumes the role of the first author.

```{r degree}
# Calculate degree centrality
degree_testw1 <- degree(test_w1)
degree_testw1 <- as.data.frame(degree_testw1)

ggplot(degree_testw1, aes(x = as.numeric(degree_testw1))) +
  geom_histogram(binwidth = 0.9, fill = "#FFFFB3", color = "black") +  
  labs(
    title = "Distribution Degrees Wave 1",
    x = "Distribution of Degrees",
    y = "Count"
  ) +
  ylim(0, 15) +  # Set y-axis limits 
  theme_minimal(base_family = "Arial") +  # Minimal, clean base theme
  theme(
    plot.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark background
    panel.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark panel background
    panel.grid.major = element_line(color = "#444444"),  # Subtle grid lines
    panel.grid.minor = element_line(color = "#444444"),
    axis.text = element_text(color = "#f0f0f0"),  # White axis text
    axis.title = element_text(color = "#f0f0f0", face = "bold"),  # Bold white axis titles
    plot.title = element_text(color = "#f0f0f0", face = "bold", hjust = 0.5),  # White centered title
    legend.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark legend background
    legend.text = element_text(color = "#f0f0f0")  # White legend text
  ) +
  guides(fill = "none")  # Remove the legend

```

<!-- ylim was 65 at some point priot due to one higher bar, I wonder what changed since... -->

The indegree distribution is right-skewed. This suggests that only very few vertices have many infegrees, and that most vertices have a low number of indegrees.

#### Betweenness Centrality

(with isolates)

```{r betweenness}
# Calculate betweenness centrality
betweenness_w1 <- igraph::betweenness(test_w1, directed = TRUE)
betweenness_w1 <- as.data.frame(betweenness_w1)

ggplot(betweenness_w1, aes(as.numeric(betweenness_w1), colour = as.numeric(betweenness_w1))) +
  geom_histogram(binwidth = 1.2, fill = "#FFFFB3") +
  labs(
    title = "Distribution Betweenness Wave 1",
    x = "Distribution of Betweenness",
    y = "Count") +
   theme_minimal(base_family = "Arial") +  # Minimal, clean base theme
  theme(
    plot.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark background
    panel.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark panel background
    panel.grid.major = element_line(color = "#444444"),  # Subtle grid lines
    panel.grid.minor = element_line(color = "#444444"),
    axis.text = element_text(color = "#f0f0f0"),  # White axis text
    axis.title = element_text(color = "#f0f0f0", face = "bold"),  # Bold white axis titles
    plot.title = element_text(color = "#f0f0f0", face = "bold", hjust = 0.5),  # White centered title
    legend.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark legend background
    legend.text = element_text(color = "#f0f0f0")  # White legend text
  ) +
  guides(fill = guide_legend(title = "Betweenness (rounded)"))  # Customize legend

```

#### Clustering

```{r}
# Clustering the wave 
clustering_w1 <- igraph::transitivity(test_w1, type = "local")
clustering_w1 <- as.data.frame(clustering_w1)

# Generate the dark mode plot with a single color fill
ggplot(clustering_w1, aes(x = as.numeric(clustering_w1))) +
   geom_histogram(binwidth = 0.05, fill = "#FFFFB3", color = "black", position = "dodge") +  
  labs(
    title = "Distribution Clustering Wave 1",
    x = "Distribution of Clustering",
    y = "Count"
  ) +
  theme_minimal(base_family = "Arial") +  # Clean, minimal base theme
  theme(
    plot.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark background
    panel.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark panel background
    panel.grid.major = element_line(color = "#444444"),  # Subtle grid lines
    panel.grid.minor = element_line(color = "#444444"),
    axis.text = element_text(color = "#f0f0f0"),  # White axis text
    axis.title = element_text(color = "#f0f0f0", face = "bold"),  # Bold white axis titles
    plot.title = element_text(color = "#f0f0f0", face = "bold", hjust = 0.5),  # White centered title
    legend.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark legend background
    legend.text = element_text(color = "#f0f0f0")  # White legend text
  ) + guides(fill = "none")  # Remove the legend (since all bars are the same color)

```

# Network-level descriptives

## x. Average path length

```{r path length}
mean((ego_size(test_w1, order = 2, mode = "out") - 1)/vcount(test_w1))
```

## STILL DO! Segregation - Mortons I - also graphs below

**STILL DO!**

# Plotting:

## Plots WITH isolates 
###Gender 
#### whole network
```{r plot gender}

plot(test_w1,
     vertex.color = ifelse(df_ego$gender == 1, "#FFED6F", "#80B1D3"), # now, I can use actor attributes for plotting.
# here: if gender = 1 (aka man) then red dot, if not then blue 
  vertex.label = NA,
  vertex.size = 7.5,
  edge.width = 0.5,
  edge.arrow.size = 0.1,
  main = "Network with isolates [yellow = female, blue = male]",)

```

#### per department

```{r with iso gender per dep old code }

indegr_w1 <- degree(test_w1, mode = "in")

# assign gender to scholar
V(test_w1)$gender <- df_ego$gender

# assign discipline to scholar
V(test_w1)$discipline <- df_ego$discipline.24

V(test_w1)$indegree <- indegr_w1

p_gender <- ggraph(test_w1, layout = "fr") + geom_edge_link(end_cap = circle(4, 'mm'),color = "#D9D9D9", width = 0.7, arrow = arrow(length = unit(2, "mm"), type = "closed")) + geom_node_point(aes(size = indegree,
    color = as.factor(discipline), shape = as.factor(gender))) + scale_size(range = c(3, 10)) + theme_void() +  theme(
    plot.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark background
    panel.background = element_rect(fill = "#2d2d2d", color = NA),
    text = element_text(color = "#f0f0f0")  # White text
  )

p_gender + labs(title = "Departments with isolates", subtitle = "Plot of indegree and gender", caption = "Gender: 0 = female, 1 = male.\n Data refer to scholars from Radboud University.") +
    theme(plot.title = element_text(hjust = 0.5, face = "bold", color = "#f0f0f0"), plot.subtitle = element_text(hjust = 0.5, color = "#f0f0f0"), plot.caption = element_text(hjust = 1, color = "#f0f0f0"))
```

### H-Index 
#### whole network 
```{r  h ind with iso old code }
indegr_w1 <- degree(test_w1, mode = "in")

# assign h-index to scholar
V(test_w1)$h_index <- df_ego$h_index
V(test_w1)$indegree <- indegr_w1

# set size of plot
options(repr.plot.width = 15, repr.plot.height = 18)

# plot wave 1 with isolates
p_iso <- ggraph(test_w1, layout = "fr") + geom_edge_link(end_cap = circle(4, 'mm'),color = "#D9D9D9", width = 0.3, arrow = arrow(length = unit(1, "mm"), type = "closed")) + geom_node_point(aes(size = indegree,
    color = h_index)) + scale_size(range = c(3, 10)) +
  scale_color_gradient(low = "#F6222E", high = "#3283FE") +  # Retain original gradient
  theme_void() +
  theme(
    plot.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark background
    panel.background = element_rect(fill = "#2d2d2d", color = NA),
    text = element_text(color = "#f0f0f0")  # White text
    )

p_iso + labs(title = "Network with isolates", subtitle = "Plot of indegree and H-index", caption = "Data refer to: Scholars RU sociology and political science departments") +
    theme(plot.title = element_text(hjust = 0.5, face = "bold"), plot.subtitle = element_text(hjust = 0.5),
        plot.caption = element_text(hjust = 1))
```

### H-Index and Gender
#### whole network 
```{r dark g&h with iso}
indegr_w1 <- degree(test_w1, mode = "in")

#assign gender to scholar 
V(test_w1)$gender <- df_ego$gender
# V(test_w1)$gender <- ifelse(df_ego$gender >= 0.5,1,0)

# assign h-index to scholar
V(test_w1)$h_index <- df_ego$h_index
V(test_w1)$indegree <- indegr_w1

p_gender <- ggraph(test_w1,
  layout = "fr") +
  geom_edge_link(end_cap = circle(4, 'mm'),color = "#D9D9D9", width = 0.3, arrow = arrow(length = unit(1, "mm"), type = "closed")) +  # Darker edge color
  geom_node_point(aes(size = indegree, color = h_index, shape = as.factor(gender))) +   
  scale_size(range = c(3, 10)) + 
  scale_color_gradient(low = "#F6222E", high = "#3283FE") +  # Retain original gradient
  theme_void() +
  theme(
    plot.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark background
    panel.background = element_rect(fill = "#2d2d2d", color = NA),
    text = element_text(color = "#f0f0f0")  # White text
  )

p_gender + 
  labs(title = "Network with isolates",
    subtitle = "Plot of indegree, H-index and gender",
    caption = "Gender: 0 = female, 1 = male.\nData refer to: Scholars RU sociology and political science departments.") +
  theme(plot.title = element_text(hjust = 0.5, face = "bold", color = "#f0f0f0"), plot.subtitle = element_text(hjust = 0.5, color = "#f0f0f0"), plot.caption = element_text(hjust = 1, color = "#f0f0f0"))

```

---

## Plots WITHOUT isolates 
The isolates of the network have been removed to allow for a better readability of the graphs. Only vertices with edges remain part of the visualizations. In other words, only scholars with collaborations are seen in the following graphs.

```{r removing isolates}
indegr_w1 <- igraph::degree(test_w1, mode = "in")

isolates_w1 <- V(test_w1)[degree(test_w1, mode = "all") == 0]

noisolates_w1 <- delete_vertices(test_w1, isolates_w1)

gsize(noisolates_w1) # edges
gorder(noisolates_w1) # vertices 
```

### Gender 
#### DESCIP<> whole network

```{r plot wo isolates}
plot(noisolates_w1,
  vertex.color = ifelse(df_ego$gender == 1, "#80B1D3", "#FFED6F"), # now, I can use actor attributes for plotting.
  # here: if gender = 1 (aka man) then red dot, if not then blue 
  vertex.label = NA,
  vertex.size = 9,
  vertex.frame.color = "black",
  edge.curved = 0.1,
  edge.arrow.size = 0.5,
  edge.color = "#999999",
  edge.width = 0.5,
  main = "Network without isolates [yellow = female, blue = male]",
  asp=0)
```
#### RESULTS <> indegree & department

```{r without iso gender per dep old code}
# assign gender to scholar
V(test_w1)$gender <- df_ego$gender

# assign disciplines to scholars
V(test_w1)$discipline <- df_ego$discipline.24
V(test_w1)$indegree <- indegr_w1

# remove isolates
noisolates_w1 <- delete_vertices(test_w1, V(test_w1)[degree(test_w1) == 0])

p_noisgender <- ggraph(noisolates_w1, layout = "fr") + geom_edge_link(end_cap = circle(4, 'mm'),color = "#D9D9D9", width = 0.7, arrow = arrow(length = unit(2, "mm")), type = "closed") +
    geom_node_point(aes(size = indegree, color = as.factor(discipline), shape = as.factor(gender))) +
    scale_size(range = c(3, 10)) + theme_void() +   theme(
    plot.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark background
    panel.background = element_rect(fill = "#2d2d2d", color = NA),
    text = element_text(color = "#f0f0f0")  # White text
  )

p_noisgender + labs(title = "Departments without isolates", subtitle = "Plot of indegree and gender",
    caption = "Gender: 0 = female, 1 = male.\n Data refer to scholars from Radboud University.") + theme(plot.title = element_text(hjust = 0.5, face = "bold", color = "#f0f0f0"), plot.subtitle = element_text(hjust = 0.5, color = "#f0f0f0"), plot.caption = element_text(hjust = 1, color = "#f0f0f0"))
```

### H-index 
#### RESULTS<> Whole network (indegree)
```{r}
indegr_w1 <- degree(test_w1, mode = "in")

# assign h-index to scholar
V(test_w1)$h_index <- df_ego$h_index
V(test_w1)$indegree <- indegr_w1

# remove isolates
noisolates_w1 <- delete_vertices(test_w1, V(test_w1)[degree(test_w1) == 0])

# set size of plot
options(repr.plot.width = 15, repr.plot.height = 15)

# plot wave 1 without isolates
p_noiso <- ggraph(noisolates_w1, layout = "fr") + geom_edge_link(end_cap = circle(3, 'mm'),color = "#D9D9D9", width = 0.7, arrow = arrow(length = unit(2, "mm"), type = "closed")) + geom_node_point(aes(size = indegree,
    color = h_index)) + scale_size(range = c(3, 10)) + scale_color_gradient(low = "red", high = "blue") +
    theme_void() +   theme(
    plot.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark background
    panel.background = element_rect(fill = "#2d2d2d", color = NA),
    text = element_text(color = "#f0f0f0")  # White text
  )

p_noiso + labs(title = "Network without isolates", subtitle = "Plot of indegree and H-index", caption = "Data refer to: Scholars RU sociology and political science departments") +
    theme(plot.title = element_text(hjust = 0.5, face = "bold", color = "#f0f0f0"), plot.subtitle = element_text(hjust = 0.5, color = "#f0f0f0"), plot.caption = element_text(hjust = 1, color = "#f0f0f0"))
```

#### per department
```{r hind without iso old code}
indegr_w1 <- degree(test_w1, mode = "in")

# assign h-index to scholar
V(test_w1)$h_index <- df_ego$h_index
# assign discipline to scholar
V(test_w1)$discipline <- df_ego$discipline.24

V(test_w1)$indegree <- indegr_w1

# remove isolates
noisolates_w1 <- delete_vertices(test_w1, V(test_w1)[degree(test_w1) == 0])

# set size of plot
options(repr.plot.width = 15, repr.plot.height = 15)

# plot wave 1 without isolates
p_noiso <- ggraph(noisolates_w1, layout = "fr") + geom_edge_link(end_cap = circle(4, 'mm'),color = "#D9D9D9", width = 0.7, arrow = arrow(length = unit(2, "mm"), type = "closed")) + geom_node_point(aes(size = indegree,
    color = h_index, shape = as.factor(discipline))) + scale_size(range = c(3, 10)) + scale_color_gradient(low = "red",
    high = "blue") + theme_void() +   theme(
    plot.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark background
    panel.background = element_rect(fill = "#2d2d2d", color = NA),
    text = element_text(color = "#f0f0f0")  # White text
  )

p_noiso + labs(title = "Departments without isolates", subtitle = "Plot of indegree and H-index", caption = "Data refer to scholars from Radboud University.") +
    theme(plot.title = element_text(hjust = 0.5, face = "bold", color = "#f0f0f0"), plot.subtitle = element_text(hjust = 0.5, color = "#f0f0f0"), plot.caption = element_text(hjust = 1, color = "#f0f0f0"))
```

### RESULTS <> H-index AND Gender (indegree)

```{r dark g&h without iso}
#assign gender to scholar 
V(test_w1)$gender <- df_ego$gender

# assign h-index to scholar
V(test_w1)$h_index <- df_ego$h_index
V(test_w1)$indegree <- indegr_w1

#remove isolates
noisolates_w1 <- delete_vertices(test_w1, V(test_w1)[degree(test_w1) == 0])

p_noisogender <- ggraph(noisolates_w1,
  layout = "fr") +
  geom_edge_link(end_cap = circle(3, 'mm'),color = "#D9D9D9", width = 0.7, arrow = arrow(length = unit(1.75, "mm"), type = "closed")) +  # Darker edge color
  geom_node_point(aes(size = indegree, color = h_index, shape = as.factor(gender))) +   
  scale_size(range = c(3, 10)) + 
  scale_color_gradient(low = "#F6222E", high = "#3283FE") +  # Retain original gradient
  theme_void() +
  theme(
    plot.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark background
    panel.background = element_rect(fill = "#2d2d2d", color = NA),
    text = element_text(color = "#f0f0f0")  # White text
  )

p_noisogender + labs(title = "Network without isolates",
        subtitle = "Plot of indegree, H-index and gender",
        caption = "Gender: 0 = female, 1 = male.\n Data refer to: Scholars RU sociology and political science departments.") +   
  theme(plot.title = element_text(hjust = 0.5, face = "bold", color = "#f0f0f0"), plot.subtitle = element_text(hjust = 0.5, color = "#f0f0f0"), plot.caption = element_text(hjust = 1, color = "#f0f0f0"))

```

### 2024-11-23 draftGOF.Rmd
modelestimates-GOFs-desresults-darkgraph

---
title: "GOFdraft"
author: "Verooo"
date: "2024-11-23"
output: html_document
---

<html lang="en">
<head>
    <meta charset="UTF-8">
    <meta name="viewport" content="width=device-width, initial-scale=1.0">
    <title>My Descriptives</title>
    <link rel="stylesheet" href="styles.css">  <!-- Link to the CSS file I created for dark mode code chunks -->

</head>
</html>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, globalsettings, echo=FALSE, warning=FALSE, results='hide'}
library(knitr)

knitr::opts_chunk$set(echo = TRUE)
opts_chunk$set(tidy.opts=list(width.cutoff=100),tidy=TRUE, warning = FALSE, message = FALSE,comment = "#>", cache=TRUE, class.source=c("test"), class.output=c("test2"))
options(width = 100)
rgl::setupKnitr()

colorize <- function(x, color) {sprintf("<span style='color: %s;'>%s</span>", color, x) }

```

```{r klippy, echo=FALSE, include=TRUE}
klippy::klippy(position = c('top', 'right'))
#klippy::klippy(color = 'darkred')
#klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done')
```

# Goodness of fit **CHANGE**
Koen:

The goodness of fit of a model indicates whether an estimated model represents the observed data. This is important as `RSiena` uses simulation to estimate the changes in the network. The goodness of fit checks whether the simulation matches the changes in the observed network. 
Due to the nature of the research questions, which focus on the tie formation dependent on indegrees, I tested the goodness of fit for the indegree distribution for each model.

For model 1, 2, and 3, which all included a quadratic effect of indegree popularity, there is a good fit of the data with a p-value between **0,332 and 0,367**. This means that the fit only slightly increases when adding ego-level effects on top of the structural network effects. Additionally, this means that the estimates for these models can be interpreted. 
For model 4, which replaces the squared estimate of indegree popularity for a non-quadratic effect, there is a significant difference in the observed and expected indegree distribution (**p = 0,03**), indicating the the squared estimate is a better fit for the data. This is also in line with the theoretical explanation that the more indegree someone has the the stronger this popularity effect will be. The estimates in Model 4 can thus **not be interpreted reliably**.

# Setup
Clean workspace. 
```{r clean}
rm(list = ls())
```

## Packages

```{r package}
require(RSiena)

```

## Functions

Functions chunk

```{r functions 1, hide = TRUE}
fpackage.check <- function(packages) {
    lapply(packages, FUN = function(x) {
        if (!require(x, character.only = TRUE)) {
            install.packages(x, dependencies = TRUE)
            library(x, character.only = TRUE)
        }
    })
}

fsave <- function(x, file = NULL, location = "./data/processed/") {
    ifelse(!dir.exists("data"), dir.create("data"), FALSE)
    ifelse(!dir.exists("data/processed"), dir.create("data/processed"), FALSE)
    if (is.null(file))
        file = deparse(substitute(x))
    datename <- substr(gsub("[:-]", "", Sys.time()), 1, 8)
    totalname <- paste(location, file, "_", datename, ".rda", sep = "")
    save(x, file = totalname)  #need to fix if file is reloaded as input name, not as x. 
}

fload <- function(filename) {
    load(filename)
    get(ls()[ls() != "filename"])
}

fshowdf <- function(x, ...) {
    knitr::kable(x, digits = 2, "html", ...) %>%
        kableExtra::kable_styling(bootstrap_options = c("striped", "hover")) %>%
        kableExtra::scroll_box(width = "100%", height = "300px")
}

```

# Model 0
```{r}
Model0.1 <- fload("./data/processed/estimated_M0.1_20241123.rda")
Model0.1
```

```{r GOF M0}
GOF_M0.1 <- sienaGOF(Model0.1, IndegreeDistribution, verbose = FALSE, join = TRUE, varName = "nets")

plot(GOF_M0.1, main = 'GOF - "Null" Model 0.1 \n Indegree Distribution')

```

# Model 1
```{r}
Model1.1 <- fload("./data/processed/estimated_M1.1_20241123.rda")
```

```{r GOF M1}
GOF_M1.1 <- sienaGOF(Model1.1, IndegreeDistribution, verbose = FALSE, join = TRUE, varName = "nets")

plot(GOF_M1.1, main = "GOF - Model 1 \n Indegree Distribution")
```

# Model 2
```{r}
Model2.1 <- fload ("./data/processed/estimated_M2.1_20241123.rda")
Model2.1
```

```{r GOF M2}
GOF_M2.1 <- sienaGOF(Model2.1, IndegreeDistribution, verbose = FALSE, join = TRUE, varName = "nets")

plot(GOF_M2.1, main = "GOF - Model 2 \n Indegree Distribution")
```

# Model 3
```{r, hide=TRUE}
Model3 <- fload("./data/processed/estimated_M3_20241123.rda")
```

```{r GOF M3, hide=TRUE}
GOF_M3 <- sienaGOF(Model3, IndegreeDistribution, verbose = FALSE, join = TRUE, varName = "nets")

plot(GOF_M3, main = "GOF - Model 3 \n Indegree Distribution")
```
# Model 4
```{r, hide=TRUE}
Model4 <- fload("./data/processed/estimated_M4_20241123.rda")
```

```{r GOF M4, hide=TRUE}
GOF_M4 <- sienaGOF(Model4, IndegreeDistribution, verbose = FALSE, join = TRUE, varName = "nets")

plot(GOF_M4, main = "GOF - Model 4 \n Indegree Distribution")
```

### 2024-11-23 draftdata.Rmd
modelestimates-GOFs-desresults-darkgraph

@@
 \_igraph: Network Analysis and Visualization in R\_.
-<doi:10.5281/zenodo.7682609> \<[[https://doi.org/10.5281/zenodo.7682609\\\\](https://doi.org/10.5281/zenodo.7682609\\){.uri}]([https://doi.org/10.5281/zenodo.7682609\\](https://doi.org/10.5281/zenodo.7682609\){.uri}){.uri}\>, R package version 2.1.1.9005, \<[[https://CRAN.R-project.org/package=igraph\\\\](https://CRAN.R-project.org/package=igraph\\){.uri}]([https://CRAN.R-project.org/package=igraph\\](https://CRAN.R-project.org/package=igraph\){.uri}){.uri}\>.
+<doi:10.5281/zenodo.7682609> \<[[https://doi.org/10.5281/zenodo.7682609\\\\](https://doi.org/10.5281/zenodo.7682609){.uri}](%5Bhttps://doi.org/10.5281/zenodo.7682609%5D(https://doi.org/10.5281/zenodo.7682609)%7B.uri%7D){.uri}\>, R package version 2.1.1.9005, \<[[https://CRAN.R-project.org/package=igraph\\\\](https://CRAN.R-project.org/package=igraph){.uri}](%5Bhttps://CRAN.R-project.org/package=igraph%5D(https://CRAN.R-project.org/package=igraph)%7B.uri%7D){.uri}\>.
 

### 2024-11-23 draftdesresults.Rmd
modelestimates-GOFs-desresults-darkgraph

--- 2024-11-23 draft1desresults.Rmd
@@
 ---
-title: "Draft Result Descriptives"
+title: "Descriptive Results"
 author: "Verooo"
@@
 </html>
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = TRUE)
+```
 
@@
 #klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done')
-```
-
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
-
 ```
@@
 
-## Network Description
+# Network Description
 
@@
 
-### Nr. of nodes/vertices
+## Nr. of nodes/vertices
 
@@
 
-### Nr. of edges
+## Nr. of edges
 
@@
 
-### Dyad census
+## Dyad census
 
@@
 
-### Triad-census
+## Triad-census
 
@@
 ```
-### Edge-density
+## Edge-density
 
@@
 
-### more in depth:
-
-````{=html}
-<!--
-
-#### reciprocity
-
-```{r recip}
-reciprocity(test_w1, ignore.loops = TRUE, mode = c("default", "ratio"))
-```
-
--->
-````
-
-#### Degree centrality
+## Degree centrality
 
@@
 
-#### Betweenness Centrality
+## Betweenness Centrality
 
@@
 
-#### Clustering
+## Clustering
 
@@
 
-# Network-level descriptives
+## Segregation ?
 
-## x. Average path length
-
-```{r path length}
-mean((ego_size(test_w1, order = 2, mode = "out") - 1)/vcount(test_w1))
-```
-
-## STILL DO! Segregation - Mortons I - also graphs below
-
-**STILL DO!**
-
-# Plotting:
-
-## Plots WITH isolates 
-###Gender 
-#### whole network
-```{r plot gender}
-
-plot(test_w1,
-     vertex.color = ifelse(df_ego$gender == 1, "#FFED6F", "#80B1D3"), # now, I can use actor attributes for plotting.
-# here: if gender = 1 (aka man) then red dot, if not then blue 
-  vertex.label = NA,
-  vertex.size = 7.5,
-  edge.width = 0.5,
-  edge.arrow.size = 0.1,
-  main = "Network with isolates [yellow = female, blue = male]",)
-
-```
-
-#### per department
-
-```{r with iso gender per dep old code }
-
-indegr_w1 <- degree(test_w1, mode = "in")
-
-# assign gender to scholar
-V(test_w1)$gender <- df_ego$gender
-
-# assign discipline to scholar
-V(test_w1)$discipline <- df_ego$discipline.24
-
-V(test_w1)$indegree <- indegr_w1
-
-p_gender <- ggraph(test_w1, layout = "fr") + geom_edge_link(end_cap = circle(4, 'mm'),color = "#D9D9D9", width = 0.7, arrow = arrow(length = unit(2, "mm"), type = "closed")) + geom_node_point(aes(size = indegree,
-    color = as.factor(discipline), shape = as.factor(gender))) + scale_size(range = c(3, 10)) + theme_void() +  theme(
-    plot.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark background
-    panel.background = element_rect(fill = "#2d2d2d", color = NA),
-    text = element_text(color = "#f0f0f0")  # White text
-  )
-
-p_gender + labs(title = "Departments with isolates", subtitle = "Plot of indegree and gender", caption = "Gender: 0 = female, 1 = male.\n Data refer to scholars from Radboud University.") +
-    theme(plot.title = element_text(hjust = 0.5, face = "bold", color = "#f0f0f0"), plot.subtitle = element_text(hjust = 0.5, color = "#f0f0f0"), plot.caption = element_text(hjust = 1, color = "#f0f0f0"))
-```
-
-### H-Index 
-#### whole network 
-```{r  h ind with iso old code }
-indegr_w1 <- degree(test_w1, mode = "in")
-
-# assign h-index to scholar
-V(test_w1)$h_index <- df_ego$h_index
-V(test_w1)$indegree <- indegr_w1
-
-# set size of plot
-options(repr.plot.width = 15, repr.plot.height = 18)
-
-# plot wave 1 with isolates
-p_iso <- ggraph(test_w1, layout = "fr") + geom_edge_link(end_cap = circle(4, 'mm'),color = "#D9D9D9", width = 0.3, arrow = arrow(length = unit(1, "mm"), type = "closed")) + geom_node_point(aes(size = indegree,
-    color = h_index)) + scale_size(range = c(3, 10)) +
-  scale_color_gradient(low = "#F6222E", high = "#3283FE") +  # Retain original gradient
-  theme_void() +
-  theme(
-    plot.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark background
-    panel.background = element_rect(fill = "#2d2d2d", color = NA),
-    text = element_text(color = "#f0f0f0")  # White text
-    )
-
-p_iso + labs(title = "Network with isolates", subtitle = "Plot of indegree and H-index", caption = "Data refer to: Scholars RU sociology and political science departments") +
-    theme(plot.title = element_text(hjust = 0.5, face = "bold"), plot.subtitle = element_text(hjust = 0.5),
-        plot.caption = element_text(hjust = 1))
-```
-
-### H-Index and Gender
-#### whole network 
-```{r dark g&h with iso}
-indegr_w1 <- degree(test_w1, mode = "in")
-
-#assign gender to scholar 
-V(test_w1)$gender <- df_ego$gender
-# V(test_w1)$gender <- ifelse(df_ego$gender >= 0.5,1,0)
-
-# assign h-index to scholar
-V(test_w1)$h_index <- df_ego$h_index
-V(test_w1)$indegree <- indegr_w1
-
-p_gender <- ggraph(test_w1,
-  layout = "fr") +
-  geom_edge_link(end_cap = circle(4, 'mm'),color = "#D9D9D9", width = 0.3, arrow = arrow(length = unit(1, "mm"), type = "closed")) +  # Darker edge color
-  geom_node_point(aes(size = indegree, color = h_index, shape = as.factor(gender))) +   
-  scale_size(range = c(3, 10)) + 
-  scale_color_gradient(low = "#F6222E", high = "#3283FE") +  # Retain original gradient
-  theme_void() +
-  theme(
-    plot.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark background
-    panel.background = element_rect(fill = "#2d2d2d", color = NA),
-    text = element_text(color = "#f0f0f0")  # White text
-  )
-
-p_gender + 
-  labs(title = "Network with isolates",
-    subtitle = "Plot of indegree, H-index and gender",
-    caption = "Gender: 0 = female, 1 = male.\nData refer to: Scholars RU sociology and political science departments.") +
-  theme(plot.title = element_text(hjust = 0.5, face = "bold", color = "#f0f0f0"), plot.subtitle = element_text(hjust = 0.5, color = "#f0f0f0"), plot.caption = element_text(hjust = 1, color = "#f0f0f0"))
-
-```
-
----
-
-## Plots WITHOUT isolates 
-The isolates of the network have been removed to allow for a better readability of the graphs.
-Only vertices with edges remain part of the visualizations.
-In other words, only scholars with collaborations are seen in the following graphs.
-
-```{r removing isolates}
-indegr_w1 <- igraph::degree(test_w1, mode = "in")
-
-isolates_w1 <- V(test_w1)[degree(test_w1, mode = "all") == 0]
-
-noisolates_w1 <- delete_vertices(test_w1, isolates_w1)
-
-gsize(noisolates_w1) # edges
-gorder(noisolates_w1) # vertices 
-```
-
-### Gender 
-#### DESCIP<> whole network
-
-```{r plot wo isolates}
-plot(noisolates_w1,
-  vertex.color = ifelse(df_ego$gender == 1, "#80B1D3", "#FFED6F"), # now, I can use actor attributes for plotting.
-  # here: if gender = 1 (aka man) then red dot, if not then blue 
-  vertex.label = NA,
-  vertex.size = 9,
-  vertex.frame.color = "black",
-  edge.curved = 0.1,
-  edge.arrow.size = 0.5,
-  edge.color = "#999999",
-  edge.width = 0.5,
-  main = "Network without isolates [yellow = female, blue = male]",
-  asp=0)
-```
-#### RESULTS <> indegree & department
-
-```{r without iso gender per dep old code}
-# assign gender to scholar
-V(test_w1)$gender <- df_ego$gender
-
-# assign disciplines to scholars
-V(test_w1)$discipline <- df_ego$discipline.24
-V(test_w1)$indegree <- indegr_w1
-
-# remove isolates
-noisolates_w1 <- delete_vertices(test_w1, V(test_w1)[degree(test_w1) == 0])
-
-p_noisgender <- ggraph(noisolates_w1, layout = "fr") + geom_edge_link(end_cap = circle(4, 'mm'),color = "#D9D9D9", width = 0.7, arrow = arrow(length = unit(2, "mm")), type = "closed") +
-    geom_node_point(aes(size = indegree, color = as.factor(discipline), shape = as.factor(gender))) +
-    scale_size(range = c(3, 10)) + theme_void() +   theme(
-    plot.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark background
-    panel.background = element_rect(fill = "#2d2d2d", color = NA),
-    text = element_text(color = "#f0f0f0")  # White text
-  )
-
-p_noisgender + labs(title = "Departments without isolates", subtitle = "Plot of indegree and gender",
-    caption = "Gender: 0 = female, 1 = male.\n Data refer to scholars from Radboud University.") + theme(plot.title = element_text(hjust = 0.5, face = "bold", color = "#f0f0f0"), plot.subtitle = element_text(hjust = 0.5, color = "#f0f0f0"), plot.caption = element_text(hjust = 1, color = "#f0f0f0"))
-```
-
-### H-index 
-#### RESULTS<> Whole network (indegree)
-```{r}
-indegr_w1 <- degree(test_w1, mode = "in")
-
-# assign h-index to scholar
-V(test_w1)$h_index <- df_ego$h_index
-V(test_w1)$indegree <- indegr_w1
-
-# remove isolates
-noisolates_w1 <- delete_vertices(test_w1, V(test_w1)[degree(test_w1) == 0])
-
-# set size of plot
-options(repr.plot.width = 15, repr.plot.height = 15)
-
-# plot wave 1 without isolates
-p_noiso <- ggraph(noisolates_w1, layout = "fr") + geom_edge_link(end_cap = circle(3, 'mm'),color = "#D9D9D9", width = 0.7, arrow = arrow(length = unit(2, "mm"), type = "closed")) + geom_node_point(aes(size = indegree,
-    color = h_index)) + scale_size(range = c(3, 10)) + scale_color_gradient(low = "red", high = "blue") +
-    theme_void() +   theme(
-    plot.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark background
-    panel.background = element_rect(fill = "#2d2d2d", color = NA),
-    text = element_text(color = "#f0f0f0")  # White text
-  )
-
-p_noiso + labs(title = "Network without isolates", subtitle = "Plot of indegree and H-index", caption = "Data refer to: Scholars RU sociology and political science departments") +
-    theme(plot.title = element_text(hjust = 0.5, face = "bold", color = "#f0f0f0"), plot.subtitle = element_text(hjust = 0.5, color = "#f0f0f0"), plot.caption = element_text(hjust = 1, color = "#f0f0f0"))
-```
-
-#### per department
-```{r hind without iso old code}
-indegr_w1 <- degree(test_w1, mode = "in")
-
-# assign h-index to scholar
-V(test_w1)$h_index <- df_ego$h_index
-# assign discipline to scholar
-V(test_w1)$discipline <- df_ego$discipline.24
-
-V(test_w1)$indegree <- indegr_w1
-
-# remove isolates
-noisolates_w1 <- delete_vertices(test_w1, V(test_w1)[degree(test_w1) == 0])
-
-# set size of plot
-options(repr.plot.width = 15, repr.plot.height = 15)
-
-# plot wave 1 without isolates
-p_noiso <- ggraph(noisolates_w1, layout = "fr") + geom_edge_link(end_cap = circle(4, 'mm'),color = "#D9D9D9", width = 0.7, arrow = arrow(length = unit(2, "mm"), type = "closed")) + geom_node_point(aes(size = indegree,
-    color = h_index, shape = as.factor(discipline))) + scale_size(range = c(3, 10)) + scale_color_gradient(low = "red",
-    high = "blue") + theme_void() +   theme(
-    plot.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark background
-    panel.background = element_rect(fill = "#2d2d2d", color = NA),
-    text = element_text(color = "#f0f0f0")  # White text
-  )
-
-p_noiso + labs(title = "Departments without isolates", subtitle = "Plot of indegree and H-index", caption = "Data refer to scholars from Radboud University.") +
-    theme(plot.title = element_text(hjust = 0.5, face = "bold", color = "#f0f0f0"), plot.subtitle = element_text(hjust = 0.5, color = "#f0f0f0"), plot.caption = element_text(hjust = 1, color = "#f0f0f0"))
-```
-
-### RESULTS <> H-index AND Gender (indegree)
-
-```{r dark g&h without iso}
-#assign gender to scholar 
-V(test_w1)$gender <- df_ego$gender
-
-# assign h-index to scholar
-V(test_w1)$h_index <- df_ego$h_index
-V(test_w1)$indegree <- indegr_w1
-
-#remove isolates
-noisolates_w1 <- delete_vertices(test_w1, V(test_w1)[degree(test_w1) == 0])
-
-p_noisogender <- ggraph(noisolates_w1,
-  layout = "fr") +
-  geom_edge_link(end_cap = circle(3, 'mm'),color = "#D9D9D9", width = 0.7, arrow = arrow(length = unit(1.75, "mm"), type = "closed")) +  # Darker edge color
-  geom_node_point(aes(size = indegree, color = h_index, shape = as.factor(gender))) +   
-  scale_size(range = c(3, 10)) + 
-  scale_color_gradient(low = "#F6222E", high = "#3283FE") +  # Retain original gradient
-  theme_void() +
-  theme(
-    plot.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark background
-    panel.background = element_rect(fill = "#2d2d2d", color = NA),
-    text = element_text(color = "#f0f0f0")  # White text
-  )
-
-p_noisogender + labs(title = "Network without isolates",
-        subtitle = "Plot of indegree, H-index and gender",
-        caption = "Gender: 0 = female, 1 = male.\n Data refer to: Scholars RU sociology and political science departments.") +   
-  theme(plot.title = element_text(hjust = 0.5, face = "bold", color = "#f0f0f0"), plot.subtitle = element_text(hjust = 0.5, color = "#f0f0f0"), plot.caption = element_text(hjust = 1, color = "#f0f0f0"))
-
-```
+# Plots

### 2024-11-23 drafttheory.Rmd
modelestimates-GOFs-desresults-darkgraph

@@
 
--   ***H3**: Gender homophily is less influential in collaboration decisions when the potential collaborator has a high level of academic prestige (e.g., a strong publication record in high-prestige journals).*
+-   ***H3**: Gender homophily is less influential in collaboration decisions when the potential collaborator has a higher Hirsch-Index.*
 
-This hypothesis posits that prestige serves as a countervailing force to homophily.
+This hypothesis posits that prestige (higher h-index) serves as a countervailing force to homophily.
 Collaboration with high-prestige individuals is a strategic choice, driven by the potential for increased visibility and career advancement, which may diminish the salience of gender in collaboration decisions.

### 2024-11-23 estimate_M0.Rmd
modelestimates-GOFs-desresults-darkgraph

--- 2024-11-09 RSienatry.Rmd
@@
 ---
-title: "RSienatry"
+title: "Estimate_M0"
 author: "Verooo"
-date: "2024-11-08"
+date: "2024-11-22"
 output: html_document
 ---
+
+<html lang="en">
+<head>
+    <meta charset="UTF-8">
+    <meta name="viewport" content="width=device-width, initial-scale=1.0">
+    <title>My Descriptives</title>
+    <link rel="stylesheet" href="styles.css">  <!-- Link to the CSS file I created for dark mode code chunks -->
+
+</head>
+</html>
+
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = TRUE)
+```
+
 ```{r, globalsettings, echo=FALSE, warning=FALSE, results='hide'}
@@
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+NULL MODEL
+Testing if the models can be estimated in separate files without error.
+Easier for me than cleanign the workspace due to oversight of having separate tabs.
+Of course I still clean the workspace in between but yaknow.
+Visual distinction.
 
-```
-
-# Getting started
-
+# Setup
+Clean workspace
 ```{r clean}
@@
 ## Functions
+
+Functions chunk
 
@@
 
-## More functions
+More functions
 
@@
 
-## Load data
+GOF auxiliary Functions 
+<!--
+# see here: ?'sienaGOF-auxiliary'
 
-```{r data}
-scholars <- fload("./data/processed/scholars_20240924.rda") #make sure to lead fload first ofcourse
+# The geodesic distribution is not available from within RSiena, and therefore is copied from the
+# help page of sienaGOF-auxiliary:
+
+# GeodesicDistribution calculates the distribution of non-directed geodesic distances; see
+# ?sna::geodist The default for \code{levls} reflects the usual phenomenon that geodesic distances
+# larger than 5 do not differ appreciably with respect to interpretation.  Note that the levels of
+# the result are named; these names are used in the \code{plot} method.
+
+-->
+[unsure if needed. put these here when trying to figure out why sienaGOF function does not work.]
+```{r}
+
+GeodesicDistribution <- function(i, data, sims, period, groupName, varName, levls = c(1:5, Inf), cumulative = TRUE,
+    ...) {
+    x <- networkExtraction(i, data, sims, period, groupName, varName)
+    require(sna)
+    a <- sna::geodist(symmetrize(x))$gdist
+    if (cumulative) {
+        gdi <- sapply(levls, function(i) {
+            sum(a <= i)
+        })
+    } else {
+        gdi <- sapply(levls, function(i) {
+            sum(a == i)
+        })
+    }
+    names(gdi) <- as.character(levls)
+    gdi
+}
+
+# The following function is taken from the help page for sienaTest
+
+testall <- function(ans) {
+    for (i in which(ans$test)) {
+        sct <- score.Test(ans, i)
+        cat(ans$requestedEffects$effectName[i], "\n")
+        print(sct)
+    }
+    invisible(score.Test(ans))
+}
 ```
+
+# Get Data
+
+## Load Scholar Data
+
+```{r scholar data}
+scholars <- fload("./data/processed/scholars_20240924.rda") 
+#make sure to lead fload first of course
+```
+
+Save the output of the function.
 
@@
                 waves = list(c(2015, 2018), c(2019, 2023)), 
-                type = c("all")) # all, first, last # which ties in there
-
-# USE not all but first or last so the ties are directed from "perspective" of first author of the publications 
-# usually first most prestige
+                type = c("first"))
 
@@
 
-## Step 1: Define data
-```{r RSiena}
+## Load Ego Data
+
+```{r df_ego data, include= FALSE}
+df_ego <- fload("./data/processed/df_ego_20241108.rda")
+
+```
+
+# Make Network Data
+
+```{r RSiena network data}
 #step1 data
@@
 
-#put diagonals to zero 
-diag(wave1) <- 0
-diag(wave2) <- 0
-# we want a binary tie (not a weighted tie)
-wave1[wave1 > 1] <- 1
-wave2[wave2 > 1] <- 1
-```
-
-```{r RSiena define 1}
-# put the nets in an array
+# put nets in an array
 net_array <- array(data = c(wave1, wave2), dim = c(dim(wave1), 2))
-#dependent
-nets <- sienaDependent(net_array)
-```
-
-```{r RSiena define 2}
-
-df_ego <- fload("./data/processed/df_ego_20241108.rda") #make sure to lead fload first ofcourse
-
-#put gender in object 
-gender <- df_ego$gender
-#covariate
-gender_RS <- coCovar(gender) # gender as covariate in Rsiena
-
-#put h-index in object 
-h_index <- df_ego$h_index
-df_ego$h_index
-#covarite 2
-h_index_RS <- coCovar(h_index) # h_index as covariate in RSiena
-
-#define data 
-mydata <- sienaDataCreate(nets, gender_RS, h_index_RS)
 
@@
 
-## Step 2: Make effects structure 
-```{r RSiena myeff}
-#define effects structure 
-myeff <- getEffects(mydata)
+## Model 0 - Null Model
+
+**CHANGE** First, I estimate a null model with only reciprocity and
+degree. It has a convergence of NUMBER and a Goodness of Fit on the
+indegree distribution of 0 (**NUMBER BEOFRE**), indicating that the model
+fits the data very badly. This makes sense, given that the model does
+not include any network statistics. Both reciprocity and density are
+significant for an alpha of NUMBER. It is important to mention that
+significance in RSiena means something different than in conventional
+statistics. In normal statistics, such as OLS-regression, significance
+of estimates refers to the fact that they are not 0 (RELEVANT?). In
+RSiena, however, it refers to the fact that the estimates were precisely
+determined (Ripley et al. 2011). Going forward with this chapter,
+significance will refer to this definition of significance. The density
+parameter has a value of NUMBER, which means that people generally do
+not want to have a dense network. The reciprocity parameter has a value
+of NUMBER, which means that people like to send ties back to people who
+have sent a tie to them.
+
+5.1.1 Create SienaData
+
+### Step 1: Define Siena Data & Variables
+
+```{r RSiena define m0}
+# dependent variable 
+nets <- sienaDependent(net_array)
+
+# define data object 
+mydata_M0 <- sienaDataCreate(nets)
 
@@
 
-## Step 3: initial description (skipped)
-Nothing for now. :)
+Print short descriptive report
 
-## Step 4: Specify model 
-```{r RSiena spec mod}
+```{r}
+ifelse(!dir.exists("results"), dir.create("results"), FALSE)
 
-myeff <- includeEffects(myeff, isolateNet, inPop, outAct)
+#if there is not a folder called "results" in your repository: make one
 
-myeff <- includeEffects(myeff, egoX, altX, sameX, interaction1 = "gender_RS")
-#include effect of h index later too etc
-#look up which effects to iclude
-
-myAlgorithm <- sienaAlgorithmCreate(modelType = c(nets=6), projname = "proProject")
-# undirected: model 6 "additive model", #check manual for this
 ```
 
-## Step 5: Estimate model 
-```{r RSiena-model estimate, eval = FALSE}
-# estimate the model 
-model1 <- siena07(myAlgorithm, data = mydata, effects = myeff, returnDeps = TRUE)
-#latter needed for GOF
+```{r}
+print01Report(mydata_M0, modelname = "./results/results_M0") # create file with report in results folder 
+```
 
-model1
+### Step 2: Make effects object/structure
 
-# output:  convergence ration NA probably bc we chose all ties to be included (type = "all") earlier
-# we can go back and change that or change it here in the myAlgorithm function
-
-# Make it a directed network 
-# focus: writing, 
-# model interpretation
+```{r RSiena myeff M0}
+# define effects structure 
+myeff_M0 <- getEffects(mydata_M0)
 
 ```
+
+### Step 3: Add Effects
+
+```{r effects M0}
+# Null model: just myeff (just degree and reciprocity by default) # model0  #for this when you create Siena Data, do not add the gender variable
+
+myeff_M0 <- includeEffects(myeff_M0, isolateNet, inPop, outAct)
+
+```
+
+### Step 4: Specify model/algorithm
+
+```{r algo M0}
+
+myAlgorithm_M0 <- sienaAlgorithmCreate (projname = "results_M0")
+
+```
+
+### Step 5: Estimate model
+
+```{r estimate M0, eval=FALSE}
+
+# estimate the model 
+Model0 <- siena07(myAlgorithm_M0, data = mydata_M0, effects = myeff_M0, returnDeps = TRUE)
+
+Model0
+# maximum convergence >.25
+
+# run again:
+Model0.1 <- siena07(myAlgorithm_M0, data = mydata_M0, effects = myeff_M0, prevAns= Model0, returnDeps = TRUE)
+
+Model0.1
+
+# fsave(Model0, file ="estimated_M0")
+# fsave(Model0.1, file = "estimated_M0.1")
+
+```
+
+```{r load M0 output, echo=FALSE}
+Model0 <- fload("./data/processed/estimated_M0_20241123.rda")
+Model0
+
+Model0.1 <- fload("./data/processed/estimated_M0.1_20241123.rda")
+Model0.1
+
+```
+
+### Step 6: GOF - Goodness of Fit
+
+```{r GOF M0}
+GOF_M0.1 <- sienaGOF(Model0.1, IndegreeDistribution, verbose = FALSE, join = TRUE, varName = "nets")
+
+plot(GOF_M0.1, main = 'GOF - "Null" Model 0.1 \n Indegree Distribution')
+```

### 2024-11-23 estimate_M1.Rmd
modelestimates-GOFs-desresults-darkgraph

--- 2024-11-23 estimate_M0.Rmd
@@
 ---
-title: "Estimate_M0"
+title: "Estimate_M1"
 author: "Verooo"
@@
 
-NULL MODEL
-Testing if the models can be estimated in separate files without error.
-Easier for me than cleanign the workspace due to oversight of having separate tabs.
-Of course I still clean the workspace in between but yaknow.
-Visual distinction.
-
 # Setup
-Clean workspace
+Clean workspace. 
 ```{r clean}
@@
 
+MODEL 1
+Testing if the models can be estimated in separate files without error.
+Easier for me than cleanign the workspace due to oversight of having separate tabs.
+Of course I still clean the workspace in between but yaknow.
+Visual distinction.
+
 ## Load Ego Data
@@
 
-## Model 0 - Null Model
+## Model 1 - Structural Effects
 
-**CHANGE** First, I estimate a null model with only reciprocity and
-degree. It has a convergence of NUMBER and a Goodness of Fit on the
-indegree distribution of 0 (**NUMBER BEOFRE**), indicating that the model
-fits the data very badly. This makes sense, given that the model does
-not include any network statistics. Both reciprocity and density are
-significant for an alpha of NUMBER. It is important to mention that
-significance in RSiena means something different than in conventional
-statistics. In normal statistics, such as OLS-regression, significance
-of estimates refers to the fact that they are not 0 (RELEVANT?). In
-RSiena, however, it refers to the fact that the estimates were precisely
-determined (Ripley et al. 2011). Going forward with this chapter,
-significance will refer to this definition of significance. The density
-parameter has a value of NUMBER, which means that people generally do
-not want to have a dense network. The reciprocity parameter has a value
-of NUMBER, which means that people like to send ties back to people who
-have sent a tie to them.
+**CHANGE** This model includes the relevant network statistics: InPop,
+outAct, isolateNet.
 
-5.1.1 Create SienaData
+It has a convergence of NUMBER and a Goodness of Fit on the indegree
+distribution of NUMBER.
+
+Indegree Popularity (inPop) is defined as the extent to which people who
+have a lot of indegrees are more popular to connect with. This parameter
+is NUMBER, meaning that actors have a preference to connect with actors
+who have a lot of indegrees. The parameter is significant for an alpha
+of NUMBER.
+
+Outdegree Activity (outAct) has a value of NUMBER, but is not
+significant. IsolateNet is significant andhas a value of NUMBER and
+refers to the preference of remaining an isolate. As this value is
+positive (IS IT??!), it means that people prefer to be an isolate in the
+network.
 
@@
 
-```{r RSiena define m0}
+```{r RSiena define M1}
 # dependent variable 
@@
 # define data object 
-mydata_M0 <- sienaDataCreate(nets)
+mydata_M1 <- sienaDataCreate(nets)
 
@@
 ```{r}
-print01Report(mydata_M0, modelname = "./results/results_M0") # create file with report in results folder 
+print01Report(mydata_M1, modelname = "./results/results_M1") # create file with report in results folder 
 ```
@@
 
-```{r RSiena myeff M0}
+```{r RSiena myeff m1}
 # define effects structure 
-myeff_M0 <- getEffects(mydata_M0)
+myeff_M1 <- getEffects(mydata_M1)
 
@@
 
-```{r effects M0}
-# Null model: just myeff (just degree and reciprocity by default) # model0  #for this when you create Siena Data, do not add the gender variable
-
-myeff_M0 <- includeEffects(myeff_M0, isolateNet, inPop, outAct)
+```{r effects m1}
+myeff_M1 <- includeEffects(myeff_M1, isolateNet, inPop, outAct)
 
@@
 
-```{r algo M0}
+```{r algo m1}
 
-myAlgorithm_M0 <- sienaAlgorithmCreate (projname = "results_M0")
+myAlgorithm_M1 <- sienaAlgorithmCreate (projname = "results_M1")
 
@@
 
-```{r estimate M0, eval=FALSE}
+```{r estimate m1}
+# estimate the model 
+Model1 <- siena07(myAlgorithm_M1, data = mydata_M1, effects = myeff_M1, returnDeps = TRUE)
+#latter needed for GOF
 
-# estimate the model 
-Model0 <- siena07(myAlgorithm_M0, data = mydata_M0, effects = myeff_M0, returnDeps = TRUE)
+Model1
 
-Model0
-# maximum convergence >.25
-
-# run again:
-Model0.1 <- siena07(myAlgorithm_M0, data = mydata_M0, effects = myeff_M0, prevAns= Model0, returnDeps = TRUE)
-
-Model0.1
-
-# fsave(Model0, file ="estimated_M0")
-# fsave(Model0.1, file = "estimated_M0.1")
-
-```
-
-```{r load M0 output, echo=FALSE}
-Model0 <- fload("./data/processed/estimated_M0_20241123.rda")
-Model0
-
-Model0.1 <- fload("./data/processed/estimated_M0.1_20241123.rda")
-Model0.1
+Model1.1 <- siena07(myAlgorithm_M1, data = mydata_M1, effects = myeff_M1, prevAns =Model1, returnDeps = TRUE)
+#latter needed for GOF 
+Model1.1
 
@@
 
-```{r GOF M0}
-GOF_M0.1 <- sienaGOF(Model0.1, IndegreeDistribution, verbose = FALSE, join = TRUE, varName = "nets")
+```{r GOF M1}
+GOF_M1 <- sienaGOF(Model1.1, IndegreeDistribution, verbose = FALSE, join = TRUE, varName = "nets")
 
-plot(GOF_M0.1, main = 'GOF - "Null" Model 0.1 \n Indegree Distribution')
+plot(GOF_M1, main = "GOF - Model 1 \n Indegree Distribution")
 ```

### 2024-11-23 estimate_M2.Rmd
modelestimates-GOFs-desresults-darkgraph

--- 2024-11-23 estimate_M1.Rmd
@@
 ---
-title: "Estimate_M1"
+title: "Estimate_M2"
 author: "Verooo"
@@
 
+MODEL 2
+Testing if the models can be estimated in separate files without error.
+Easier for me than cleanign the workspace due to oversight of having separate tabs.
+Of course I still clean the workspace in between but yaknow.
+Visual distinction.
+
 # Setup
-Clean workspace. 
+clean workspace
 ```{r clean}
@@
 
-MODEL 1
-Testing if the models can be estimated in separate files without error.
-Easier for me than cleanign the workspace due to oversight of having separate tabs.
-Of course I still clean the workspace in between but yaknow.
-Visual distinction.
-
 ## Load Ego Data
@@
 
-## Model 1 - Structural Effects
+## Model 2 - Gender
 
-**CHANGE** This model includes the relevant network statistics: InPop,
-outAct, isolateNet.
-
-It has a convergence of NUMBER and a Goodness of Fit on the indegree
-distribution of NUMBER.
-
-Indegree Popularity (inPop) is defined as the extent to which people who
-have a lot of indegrees are more popular to connect with. This parameter
-is NUMBER, meaning that actors have a preference to connect with actors
-who have a lot of indegrees. The parameter is significant for an alpha
-of NUMBER.
-
-Outdegree Activity (outAct) has a value of NUMBER, but is not
-significant. IsolateNet is significant andhas a value of NUMBER and
-refers to the preference of remaining an isolate. As this value is
-positive (IS IT??!), it means that people prefer to be an isolate in the
-network.
+**CHANGE** Model 2 builds on Model 1 and includes the network statistics
+for gender: diffX, diffXTransTrip, egoX & altX. This model has a
+convergence of 0.23 and a Goodness of Fit on the indegree distribution
+of 0.184. For the structural network statistics we find similar results,
+in terms of estimate size and significance, as in Model 1. However, the
+outdegree activity parameter almost reaches significance (-1.7135484).
+With regard to the covariate network statistics, we find that the gender
+of ego (egoX), the gender of alter (altX) and the difference between ego
+and alter (diffX) is not significant and thus the estimate cannot be
+trusted. The transtrip for different gender (diffXTransTrip) is positive
+and significant, which implies that an ego prefers to close triads with
+alters who have a different gender score than theirs. This is an
+interesting finding, because it implies that their is a tendency towards
+diverse collaboration. However, when compared to the level of gender
+clustering and the fact that this clustering decreased, this finding
+does make sense.
 
@@
 
-```{r RSiena define M1}
+```{r RSiena define m2}
 # dependent variable 
@@
 
+# put gender in object 
+gender <- df_ego$gender
+
+# covariate 1
+gender_RS <- coCovar(gender) # gender as covariate in Rsiena
+
 # define data object 
-mydata_M1 <- sienaDataCreate(nets)
+mydata_M2 <- sienaDataCreate(nets, gender_RS)
 
@@
 ```{r}
-print01Report(mydata_M1, modelname = "./results/results_M1") # create file with report in results folder 
+print01Report(mydata_M2, modelname = "./results/results_M2") # create file with report in results folder 
 ```
@@
 
-```{r RSiena myeff m1}
+```{r RSiena myeff m2}
 # define effects structure 
-myeff_M1 <- getEffects(mydata_M1)
+myeff_M2 <- getEffects(mydata_M2)
 
@@
 
-```{r effects m1}
-myeff_M1 <- includeEffects(myeff_M1, isolateNet, inPop, outAct)
+```{r effects m2}
+myeff_M2 <- includeEffects(myeff_M2, isolateNet, inPop, outAct)
+
+myeff_M2 <- includeEffects(myeff_M2, egoX, altX, sameX, interaction1 = "gender_RS")
 
@@
 
-```{r algo m1}
+```{r algo m2}
 
-myAlgorithm_M1 <- sienaAlgorithmCreate (projname = "results_M1")
+myAlgorithm_M2 <- sienaAlgorithmCreate (projname = "results_M2")
 
@@
 
-```{r estimate m1}
+```{r estimate m2}
 # estimate the model 
-Model1 <- siena07(myAlgorithm_M1, data = mydata_M1, effects = myeff_M1, returnDeps = TRUE)
+Model2 <- siena07(myAlgorithm_M2, data = mydata_M2, effects = myeff_M2, returnDeps = TRUE)
 #latter needed for GOF
 
-Model1
-
-Model1.1 <- siena07(myAlgorithm_M1, data = mydata_M1, effects = myeff_M1, prevAns =Model1, returnDeps = TRUE)
-#latter needed for GOF 
-Model1.1
+Model2
 
@@
 
-```{r GOF M1}
-GOF_M1 <- sienaGOF(Model1.1, IndegreeDistribution, verbose = FALSE, join = TRUE, varName = "nets")
+```{r GOF M2}
+GOF_M2 <- sienaGOF(Model2, IndegreeDistribution, verbose = FALSE, join = TRUE, varName = "nets")
 
-plot(GOF_M1, main = "GOF - Model 1 \n Indegree Distribution")
+plot(GOF_M2, main = "GOF - Model 2 \n Indegree Distribution")
 ```

### 2024-11-23 estimate_M3.Rmd
modelestimates-GOFs-desresults-darkgraph

--- 2024-11-23 estimate_M1.Rmd
@@
 ---
-title: "Estimate_M1"
+title: "Estimate_M3"
 author: "Verooo"
@@
 ```
+
+MODEL 3 - Gender & H-index 
+Testing if the models can be estimated in separate files without error.
+Easier for me than cleanign the workspace due to oversight of having separate tabs.
+Of course I still clean the workspace in between but yaknow.
+Visual distinction.
 
@@
 
-## Model 1 - Structural Effects
+## Model 3 - H-Index
 
-**CHANGE** This model includes the relevant network statistics: InPop,
-outAct, isolateNet.
-
-It has a convergence of NUMBER and a Goodness of Fit on the indegree
-distribution of NUMBER.
-
-Indegree Popularity (inPop) is defined as the extent to which people who
-have a lot of indegrees are more popular to connect with. This parameter
-is NUMBER, meaning that actors have a preference to connect with actors
-who have a lot of indegrees. The parameter is significant for an alpha
-of NUMBER.
-
-Outdegree Activity (outAct) has a value of NUMBER, but is not
-significant. IsolateNet is significant andhas a value of NUMBER and
-refers to the preference of remaining an isolate. As this value is
-positive (IS IT??!), it means that people prefer to be an isolate in the
-network.
+**CHANGE!!!** Model 3 includes the covariate network statistics for
+Prestige: egoX, altX and inPopX. This model has a convergence ratio of
+0.23 and a a Goodness of Fit on the indegree distribution of 0.64. In
+this model, the parameters for density and reciprocity are still
+significant, with values of -1.98 (se = 0.71) and 2.59 (se = 0.38)
+respectively, meaning that actors prefer sparse networks, but do prefer
+to send ties to alters who have sent ties to them. IsolateNet is still
+significant with a value of 3.23 (se = 1.06), implying that actors
+prefer to be isolates. In this model, indegree popularity squared (b =
+0.17, se = 0.21) is no longer significant, implying that this might be
+explained by other network statistics in the model. The covariate
+statistics for gender show similar findings as Model 2 & Model 2.5,
+namely that actors prefer to close triads with alters that have a
+different score for gender (b = 1.51, se = 0.44). the ego effect and
+alter effect for gender are non-significant, as was the case in Model 2
+& Model 2.5. Lastly, Model 3 shows some significant results with regards
+to the covariate network statistics for prestige. The prestige effect
+for alters is positive, implying that people prefer to send ties to
+people who have a higher amount of prestige (b = 0.042, se = 0.0089).
+Additionally, the prestige effect for egos is negative, which indicates
+that people who have higher prestige send less ties (b = -0.030, se =
+0.015). This is in line with theories of preferential attachment and
+upward mobility, because as egos with higher prestige will are more
+likely to receive request for collaboration rather then sending request
+for collaboration. Interestingly enough, the indegree popularity
+statistic for prestige is not significant (b = -0.012, se = 0.023),
+implying that actors who are more prestigious do not receive more
+indegrees.
 
@@
 
-```{r RSiena define M1}
+```{r RSiena define m3}
 # dependent variable 
@@
 
+# put gender in object 
+gender <- df_ego$gender
+
+# covariate 1
+gender_RS <- coCovar(gender) # gender as covariate in Rsiena
+
+# put h-index in object 
+h_index <- df_ego$h_index
+df_ego$h_index
+
+# covariate 2
+h_index_RS <- coCovar(h_index) # h_index as covariate in RSiena
+
 # define data object 
-mydata_M1 <- sienaDataCreate(nets)
+mydata_M3 <- sienaDataCreate(nets, gender_RS, h_index_RS)
 
@@
 ifelse(!dir.exists("results"), dir.create("results"), FALSE)
-
-#if there is not a folder called "results" in your repository: make one
+# if there is not a folder called "results" in your repository: make one
 
@@
 ```{r}
-print01Report(mydata_M1, modelname = "./results/results_M1") # create file with report in results folder 
+print01Report(mydata_M3, modelname = "./results/results_M3") # create file with report in results folder 
 ```
@@
 
-```{r RSiena myeff m1}
+```{r RSiena myeff M3}
+
 # define effects structure 
-myeff_M1 <- getEffects(mydata_M1)
+myeff_M3 <- getEffects(mydata_M3)
 
@@
 
-```{r effects m1}
-myeff_M1 <- includeEffects(myeff_M1, isolateNet, inPop, outAct)
+```{r effects M3}
+myeff_M3 <- includeEffects(myeff_M3, isolateNet, inPop, outAct) # model1
+
+myeff_M3 <- includeEffects(myeff_M3, egoX, altX, sameX, interaction1 = "gender_RS") # model2
+
+myeff_M3 <- includeEffects(myeff_M3, egoX, altX, inPopX, interaction1 = "h_index_RS") # model3
 
 ```
+<!-- # isolatenet: if individual is alone they "like to/tend to stay alone"
+# inPop: ppl like to collab with people who are popular
 
+# change statistics to fit whatever I want to know about h-index 
+# not sameX 
+# look up inPopX: preferential attachment (cf. Koen lel), higher h-index more popular 
+  # cf. Fridas modeling process (Jochem told her that )
+-->
 ### Step 4: Specify model/algorithm
 
-```{r algo m1}
+```{r algo M3}
 
-myAlgorithm_M1 <- sienaAlgorithmCreate (projname = "results_M1")
+myAlgorithm_M3 <- sienaAlgorithmCreate (projname = "results_M3")
 
@@
 
-```{r estimate m1}
+```{r estimate M3}
 # estimate the model 
-Model1 <- siena07(myAlgorithm_M1, data = mydata_M1, effects = myeff_M1, returnDeps = TRUE)
+Model3 <- siena07(myAlgorithm_M3, data = mydata_M3, effects = myeff_M3, returnDeps = TRUE)
 #latter needed for GOF
 
-Model1
-
-Model1.1 <- siena07(myAlgorithm_M1, data = mydata_M1, effects = myeff_M1, prevAns =Model1, returnDeps = TRUE)
-#latter needed for GOF 
-Model1.1
+Model3
 
@@
 
-```{r GOF M1}
-GOF_M1 <- sienaGOF(Model1.1, IndegreeDistribution, verbose = FALSE, join = TRUE, varName = "nets")
+```{r GOF M3}
+GOF_M3 <- sienaGOF(Model3, IndegreeDistribution, verbose = FALSE, join = TRUE, varName = "nets")
 
-plot(GOF_M1, main = "GOF - Model 1 \n Indegree Distribution")
+plot(GOF_M3, main = "GOF - Model 3 \n Indegree Distribution")
 ```

### 2024-11-23 finalGOF.Rmd
modelestimates-GOFs-desresults-darkgraph

---
title: "GOF"
author: "Verooo"
date: "2024-11-23"
output: html_document
---

### 2024-11-23 finaldata.Rmd
modelestimates-GOFs-desresults-darkgraph

---
title: "Data & Methods"
author: "Verooo"
date: "2024-11-23"
output: html_document
---

### 2024-11-23 finaldataprep.Rmd
modelestimates-GOFs-desresults-darkgraph

---
title: "Data preparation"
author: "Verooo"
date: "2024-11-23"
output: html_document
---

### 2024-11-23 finaldescriptives.Rmd
modelestimates-GOFs-desresults-darkgraph

---
title: "Data description"
author: "Verooo"
date: "2024-11-23"
output: html_document
---

### 2024-11-23 finaldesresults.Rmd
modelestimates-GOFs-desresults-darkgraph

---
title: "Results - Descriptives"
author: "Verooo"
date: "2024-11-23"
output: html_document
---

### 2024-11-23 finaldiscussion.Rmd
modelestimates-GOFs-desresults-darkgraph

---
title: "Discussion"
author: "Verooo"
date: "2024-11-23"
output: html_document
---

### 2024-11-23 finalestimate.Rmd
modelestimates-GOFs-desresults-darkgraph

---
title: "Model Estimation"
author: "Verooo"
date: "2024-11-23"
output: html_document
---

### 2024-11-23 finalintro.Rmd
modelestimates-GOFs-desresults-darkgraph

---
title: "Introduction"
author: "Verooo"
date: "2024-11-23"
output: html_document
---

### 2024-11-23 finaltheory.Rmd
modelestimates-GOFs-desresults-darkgraph

---
title: "Theory"
author: "Verooo"
date: "2024-11-23"
output: html_document
---

### 2024-11-23 modelestimate.Rmd
modelestimates-GOFs-desresults-darkgraph

---
title: "Model estimation"
author: "Verooo"
date: "2024-11-20"
output: html_document
editor_options: 
  markdown: 
    wrap: 72
---

<html lang="en">

<head>

<meta charset="UTF-8">

<meta name="viewport" content="width=device-width, initial-scale=1.0">

<title>My Descriptives</title>

<link rel="stylesheet" href="styles.css">
<!-- Link to the CSS file I created for dark mode code chunks -->

</head>

</html>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, globalsettings, echo=FALSE, warning=FALSE, results='hide'}
library(knitr)

knitr::opts_chunk$set(echo = TRUE)
opts_chunk$set(tidy.opts=list(width.cutoff=100),tidy=TRUE, warning = FALSE, message = FALSE,comment = "#>", cache=TRUE, class.source=c("test"), class.output=c("test2"))
options(width = 100)
rgl::setupKnitr()

colorize <- function(x, color) {sprintf("<span style='color: %s;'>%s</span>", color, x) }

```

```{r klippy, echo=FALSE, include=TRUE}
klippy::klippy(position = c('top', 'right'))
#klippy::klippy(color = 'darkred')
#klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done')
```

# Setup

Clean workspace. As always.

```{r clean}
rm(list = ls())
```

## Packages

```{r package, include=TRUE, hide=TRUE, eval=TRUE}
require(tidyverse)
require(RSiena)
require(RsienaTwoStep)

#install.packages("data.table")
require(data.table)  # mainly for faster data handling
# install.packages('xml2')
require(xml2)
# install.packages('rvest')
require(rvest)
require(igraph)
require(ggraph)

#install.packages('visNetwork')
require(visNetwork)
#install.packages('threejs')
require(threejs)
#install.packages('networkD3')
require(networkD3)

```

## Functions

Functions chunk:

```{r functions 1, hide=TRUE}
fpackage.check <- function(packages) {
    lapply(packages, FUN = function(x) {
        if (!require(x, character.only = TRUE)) {
            install.packages(x, dependencies = TRUE)
            library(x, character.only = TRUE)
        }
    })
}

fsave <- function(x, file = NULL, location = "./data/processed/") {
    ifelse(!dir.exists("data"), dir.create("data"), FALSE)
    ifelse(!dir.exists("data/processed"), dir.create("data/processed"), FALSE)
    if (is.null(file))
        file = deparse(substitute(x))
    datename <- substr(gsub("[:-]", "", Sys.time()), 1, 8)
    totalname <- paste(location, file, "_", datename, ".rda", sep = "")
    save(x, file = totalname)  #need to fix if file is reloaded as input name, not as x. 
}

fload <- function(filename) {
    load(filename)
    get(ls()[ls() != "filename"])
}

fshowdf <- function(x, ...) {
    knitr::kable(x, digits = 2, "html", ...) %>%
        kableExtra::kable_styling(bootstrap_options = c("striped", "hover")) %>%
        kableExtra::scroll_box(width = "100%", height = "300px")
}

# this is the most important one. We created it in the previous script

f_pubnets <- function(df_scholars = df, list_publications = publications, discip = "sociology"+"political science", affiliation = "RU",
    waves = list(wave1 = c(2018, 2019, 2020), wave2 = c(2021, 2022, 2023))) {

    publications <- list_publications %>%
        bind_rows() %>%
        distinct(title, .keep_all = TRUE)

    df_scholars %>%
        filter(affil1 == affiliation | affil2 == affiliation) %>%
        filter(discipline == discip) -> df_sel

    networklist <- list()
    for (wave in 1:length(waves)) {
        networklist[[wave]] <- matrix(0, nrow = nrow(df_sel), ncol = nrow(df_sel))
    }

    publicationlist <- list()
    for (wave in 1:length(waves)) {
        publicationlist[[wave]] <- publications %>%
            filter(gs_id %in% df_sel$gs_id) %>%
            filter(year %in% waves[[wave]]) %>%
            select(author) %>%
            lapply(str_split, pattern = ",")
    }

    publicationlist2 <- list()
    for (wave in 1:length(waves)) {
        publicationlist2[[wave]] <- publicationlist[[wave]]$author %>%
            # lowercase
        lapply(tolower) %>%
            # Removing diacritics
        lapply(stri_trans_general, id = "latin-ascii") %>%
            # only last name
        lapply(word, start = -1, sep = " ") %>%
            # only last last name
        lapply(word, start = -1, sep = "-")
    }

    for (wave in 1:length(waves)) {
        # let us remove all publications with only one author
        remove <- which(sapply(publicationlist2[[wave]], FUN = function(x) length(x) == 1) == TRUE)
        publicationlist2[[wave]] <- publicationlist2[[wave]][-remove]
    }

    for (wave in 1:length(waves)) {
        pubs <- publicationlist2[[wave]]
        for (ego in 1:nrow(df_sel)) {
            # which ego?
            lastname_ego <- df_sel$lastname[ego]
            # for all publications
            for (pub in 1:length(pubs)) {
                # only continue if ego is author of pub
                if (lastname_ego %in% pubs[[pub]]) {
                  aut_pot <- which.max(pubs[[pub]] %in% lastname_ego)
                  # only continue if ego is first author of pub
                  if (aut_pot == 1) {
                    # check all alters/co-authors
                    for (alter in 1:nrow(df_sel)) {
                      # which alter
                      lastname_alter <- df_sel$lastname[alter]
                      if (lastname_alter %in% pubs[[pub]]) {
                        networklist[[wave]][ego, alter] <- networklist[[wave]][ego, alter] + 1
                      }
                    }
                  }
                }
            }
        }
    }
    return(list(df = df_sel, network = networklist))
}

```

More functions:

```{r functions 2, hide= TRUE}
fcolnet <- function(data = scholars, university = "RU", discipline = "sociology"+"political science", waves = list(c(2015,
    2018), c(2019, 2023)), type = c("first")) {

    # step 1
    demographics <- do.call(rbind.data.frame, data$demographics)
    demographics <- demographics %>%
        mutate(Universiteit1.22 = replace(Universiteit1.22, is.na(Universiteit1.22), ""), Universiteit2.22 = replace(Universiteit2.22,
            is.na(Universiteit2.22), ""), Universiteit1.24 = replace(Universiteit1.24, is.na(Universiteit1.24),
            ""), Universiteit2.24 = replace(Universiteit2.24, is.na(Universiteit2.24), ""), discipline.22 = replace(discipline.22,
            is.na(discipline.22), ""), discipline.24 = replace(discipline.24, is.na(discipline.24), ""))

    sample <- which((demographics$Universiteit1.22 %in% university | demographics$Universiteit2.22 %in%
        university | demographics$Universiteit1.24 %in% university | demographics$Universiteit2.24 %in%
        university) & (demographics$discipline.22 %in% discipline | demographics$discipline.24 %in% discipline))

    demographics_soc <- demographics[sample, ]
    scholars_sel <- lapply(scholars, "[", sample)

    # step 2
    ids <- demographics_soc$au_id
    nwaves <- length(waves)
    nets <- array(0, dim = c(nwaves, length(ids), length(ids)), dimnames = list(wave = 1:nwaves, ids,
        ids))
    dimnames(nets)

    # step 3
    df_works <- tibble(works_id = unlist(lapply(scholars_sel$work, function(l) l$id)), works_author = unlist(lapply(scholars_sel$work,
        function(l) l$author), recursive = FALSE), works_year = unlist(lapply(scholars_sel$work, function(l) l$publication_year),
        recursive = FALSE))

    df_works <- df_works[!duplicated(df_works), ]

    # step 4
    if (type == "first") {
        for (j in 1:nwaves) {
            df_works_w <- df_works[df_works$works_year >= waves[[j]][1] & df_works$works_year <= waves[[j]][2],
                ]
            for (i in 1:nrow(df_works_w)) {
                ego <- df_works_w$works_author[i][[1]]$au_id[1]
                alters <- df_works_w$works_author[i][[1]]$au_id[-1]
                if (sum(ids %in% ego) > 0 & sum(ids %in% alters) > 0) {
                  nets[j, which(ids %in% ego), which(ids %in% alters)] <- 1
                }
            }
        }
    }

    if (type == "last") {
        for (j in 1:nwaves) {
            df_works_w <- df_works[df_works$works_year >= waves[[j]][1] & df_works$works_year <= waves[[j]][2],
                ]
            for (i in 1:nrow(df_works_w)) {
                ego <- rev(df_works_w$works_author[i][[1]]$au_id)[1]
                alters <- rev(df_works_w$works_author[i][[1]]$au_id)[-1]
                if (sum(ids %in% ego) > 0 & sum(ids %in% alters) > 0) {
                  nets[j, which(ids %in% ego), which(ids %in% alters)] <- 1
                }
            }
        }
    }

    if (type == "all") {
        for (j in 1:nwaves) {
            df_works_w <- df_works[df_works$works_year >= waves[[j]][1] & df_works$works_year <= waves[[j]][2],
                ]
            for (i in 1:nrow(df_works_w)) {
                egos <- df_works_w$works_author[i][[1]]$au_id
                if (sum(ids %in% egos) > 0) {
                  nets[j, which(ids %in% egos), which(ids %in% egos)] <- 1
                }
            }
        }
    }
    output <- list()
    output$data <- scholars_sel
    output$nets <- nets
    return(output)
}
```

# Get Data

Load Scholar Data

```{r scholar data}
scholars <- fload("./data/processed/scholars_20240924.rda") 
```

Save the output of the function.

```{r saving output}
# save the output of your function
test  <- fcolnet(data = scholars, 
                university = "RU", 
                discipline = c("sociology", "political science"),
                waves = list(c(2015, 2018), c(2019, 2023)), 
                type = c("first"))
```

Load Ego Data

```{r df_ego data, include= FALSE}
df_ego <- fload("./data/processed/df_ego_20241108.rda")

```

# Make Network Data

```{r RSiena network data}
#step1 data
wave1 <- test$nets[1,,]
wave2 <- test$nets[2,,]

# put nets in an array
net_array <- array(data = c(wave1, wave2), dim = c(dim(wave1), 2))

```

------------------------------------------------------------------------

# Analysis

```{=html}
<!--
## TEST MODEL

### test 1: Define Siena Data & Variables
-->
```
```{r RSiena define, hide =TRUE, echo=FALSE, eval=FALSE}
# dependent variable 
nets <- sienaDependent(net_array)

# put gender in object 
gender <- df_ego$gender

# covariate 1
gender_RS <- coCovar(gender) # gender as covariate in Rsiena

# put h-index in object 
h_index <- df_ego$h_index
df_ego$h_index

# covariate 2
h_index_RS <- coCovar(h_index) # h_index as covariate in RSiena

# define data object 
mydata <- sienaDataCreate(nets, gender_RS, h_index_RS)

```

<!-- Print short descriptive report-->

```{r, hide =TRUE, echo=FALSE, eval=FALSE}
ifelse(!dir.exists("results"), dir.create("results"), FALSE)

#if there is not a folder called "results" in your repository: make one

```

```{r, hide =TRUE, echo=FALSE, eval=FALSE}
print01Report(mydata, modelname = "./results/try") # create file with report in results folder 
```

<!-- ### test 2: Make effects object/structure -->

```{r RSiena myeff, hide =TRUE, echo=FALSE, eval=FALSE}

# define effects structure 
myeff <- getEffects(mydata)

```

```{=html}
<!--

e.g. outdegree (density), called density, three things: evaluation,
endowment, and creation you can only include two of the three (tie
creation, breaking and maintaining)

The assumption is: mechanisms to make and break a a tie are the same so
WE ONLY USE THE EVALUATION part

All these effects are described in the manual of RSiena Chapter 12!

-->
```
```{=html}
<!--  
### Step X: Initial description
-->
```
```{=html}
<!--
Has a lot of information in there Also: how tie CHANGED Also: Jaccard
index (measure of stability) Also rate parameter and outdegree

<https://www.stats.ox.ac.uk/~snijders/siena/RSiena_Manual.pdf>

In the package RsienaTwoStep there are functions for the following
network statistics ***s*** :

degree: `ts_degree()`

reciprocity: `ts_recip()`

outdegree activity: `ts_outAct()`

indegree activity: `ts_inAct()`

outdegree popularity: `ts_outPop()`

indegree popularity: `ts_inPop()`

transitivity: `ts_transTrip()`

mediated transitivity: `ts_transMedTrip()`

transitive reciprocated triplets: `ts_transRecTrip()`

number of three-cycles: `ts_cycle3()`
-->
```
<!-- ### test 3: Add Effects -->

```{r effects, hide =TRUE, echo=FALSE, eval=FALSE}

# Null model: just myeff (just degree and reciprocity by default) # model0  #for this when you create Siena Data, do not add the gender variable

myeff <- includeEffects(myeff, isolateNet, inPop, outAct) 
# isolatenet: if individual is alone they "like to/tend to stay alone"
# inPop: ppl like to collab with people who are popular
  # over time: inpop: ppl with lots of indegrees will havelot of indegrees

#n-degree related popularity effect (inPop) (earlier called popularity or popularity of alter effect), defined by the sum of the in-degrees of the others to whom i is tied,

# later (in population) outAct: ppl with lots of outdegrees will have lot
# of indegrees later

myeff <- includeEffects(myeff, egoX, altX, sameX, interaction1 = "gender_RS") # model1
# include effect of h index later too etc
# look up which effects to include

myeff <- includeEffects(myeff, egoX, altX, inPopX, interaction1 = "h_index_RS") # model 2 (as long as myeff is eithin the brackets too, the other things get added to the myeff object)

# change statistics to fit whatever I want to know about h-index 
# not sameX 
# look up inPopX: preferential attachment (cf. Koen lel), higher h-index more popular 
  # cf. Fridas modeling process (Jochem told her that )

#diffXTransTrip
#different covariate × transitive triplets (diffXTransTrip), defined by the number of transitive triplets i → h → j ← i that have different covariate values for i and j, diff. cov. values = diff gender -RSiena manual

# "The transtrip for different gender (diffXTransTrip) is positive and significant, which implies that an ego prefers to close triads with alters who have a different gender score than theirs. This is an interesting finding, because it implies that their is a tendency towards diverse collaboration. However, when compared to the level of gender clustering and the fact that this clustering decreased, this finding does make sense." - Niels

```

```{=html}
<!--

hint FOR MY OWN PROJECT: interaction effect of these statistics and the
effect of gender

THE "X" in altX and eogX refer to the "interaction 1" variable, so it's eg. ego x gender_RS and alter x gender_RS!

altX - egos send more ties who have more on gender (aka. gender =1) 
(iiiish look at egoX explanantion, this is basically the same but in "reverse", aka about receiving rather than sending)

-   covariate-alter or covariate-related popularity (altX), defined by
    the sum of the covariate over all actors to whom ***i*** has a tie,
-   same as egoX but RECEIVING ties

egoX - [definition?]

-   covariate-ego or covariate-related activity (egoX), defined by i’s
    out-degree weighted by his covariate value,
-   since male = 1 egoX only "looks at" men's ties 
-   if egoX significant then men's ties sign. diff. based on whether its to a man or woman (look at direction of effect to know which gender)

"interaction1" HAS NOTHING TO DO WITH AN INTERACTION EFFECT

-   If there are several dependent variables (networks and/or behavioral
    variables), the name of the dependent variable (name) also is
    required to specify the effect, and will be given in the column
    interaction1 (etc.) of the effects object.

-   It should be mentioned that the keywords interaction1, interaction2,
    and interaction3 in functions such as includeEffects do not point to
    interactions between effects. These keywords are used only to
    exactly specify an effect. They point to the covariate or other
    dependent variable used in the effect; this name was chosen for the
    keyword because this other variable may be said to be interacting
    with the dependent variable (network or behavior).

-->
```
<!-- ### test 4: Specify model/algorithm -->

```{r algo, hide =TRUE, echo=FALSE, eval=FALSE}
# Algorithm from when Jochem and I sat together but it's not fitting anymore bc model type is for undirected ties 
# myAlgorithm <- sienaAlgorithmCreate(modelType = c(nets=6), projname = "proProject")
# undirected: model 6 "additive model", #check manual for this NOW IT'S UNDIRECTED!!!

# Niels advice: take his algorithm instead. haha ok, no questions asked my guy, you got it. 
myAlgorithm_test <- sienaAlgorithmCreate (projname = "results_test")

```

<!-- ### test 5: Estimate model -->

```{r estimate, hide =TRUE, echo=FALSE, eval=FALSE}
# estimate the model 
model_test <- siena07(myAlgorithm_test, data = mydata, effects = myeff, returnDeps = TRUE)
#latter needed for GOF lateron

model_test

```

```{=html}
<!-- 
output:  convergence ration NA probably bc we chose all ties to be included (type = "all") earlier
we can go back and change that or change it here in the myAlgorithm function

convergence ratio should be <.25   !!!
- if above, run model again
- if stays above .25, remove some of the netw. stats
- if close to threshold (e.g. 0.2584) add prevAns = model1  to the siena07 command and rerun then
      model1 <- siena07(myAlgorithm, data = mydata, effects = myeff, prevAns= model1, returnDeps = TRUE)

-->
```
<!-- ### test 6: GOF - Goodness of Fit -->

```{r GOF test, hide =TRUE, echo=FALSE, eval=FALSE}
GOF <- sienaGOF(model_test, IndegreeDistribution, verbose = FALSE, join = TRUE, varName = "nets")

plot(GOF, main = "Test Indegree Distr")

# "Error using packet 1 "bw" is not positive"

#--------- Try to fix error:  -------  
##--------- Inspect GOF object  ------- 
# str(GOF)
  # summary(GOF$Joint$SimulatedTestStat)

##--------- Check for invalid /infinte values ------- 
    # anyNA(GOF$Joint$SimulatedTestStat)  # Should return FALSE
    # any(!is.finite(GOF$Joint$SimulatedTestStat))  # Should return FALSE
    # summary(GOF$Joint$SimulatedTestStat)  # Inspect the range of values

    # Get rid of invalid or infinite values
        # GOF$Joint$SimulatedTestStat <- na.omit(GOF$Joint$SimulatedTestStat)
        # GOF$Joint$SimulatedTestStat <-   GOF$Joint$SimulatedTestStat[is.finite(GOF$Joint$SimulatedTestStat)]

  # var(GOF$Joint$SimulatedTestStat)  # Should return a positive value

##--------- Density simulation  ------- 
    # simulated <- GOF$Joint$SimulatedTestStat
    # # Try density estimation with default bandwidth
    #   density_est <- tryCatch(density(simulated), error = function(e) e)
    #   if (inherits(density_est, "error")) {
    #   print("Density estimation failed.")
    #     } else {
    #             print("Density estimation succeeded.")
    #             plot(density_est, main = "Simulated Test Statistics")
    #     }
    #   
##--------- Force bandwidth -------     
      # Force the Bandwidth in plot.sienaGOF
      # plot(GOF, main = "Indegree Distribution Goodness of Fit", bw = 0.5)
      # #nope does not work

##--------- Custom function -------  
      # custom_plot_sienaGOF <- function(gof, bw = 0.5, ...) {
      # simulated <- gof$Joint$SimulatedTestStat
      # observed <- gof$Joint$ObservedTestStat
      # 
      # # Perform density estimation with forced bandwidth
      # density_est <- density(simulated, bw = bw)
      # 
      # # Plot the density
      # plot(density_est, main = "Custom Indegree Distr.- GOF", ...)
      # abline(v = observed, col = "red", lty = 2, lwd = 2) 
      # }
      # 
      #  #run custom function      
      # custom_plot_sienaGOF(GOF, bw = 0.5)
      # # works but not the same at all 
      # 
##--------- Ggplot2 ------- 
# Fuck this shit. I using ggplot 
    # library(ggplot2)
    # 
    # # Prepare data
    # data <- data.frame(
    #   value = GOF$Joint$SimulatedTestStat,
    #   type = "Simulated"
    # )
    # data <- rbind(data, data.frame(value = GOF$Joint$ObservedTestStat, type = "Observed"))
    # 
    # # Plot density
    # ggplot(data, aes(x = value, fill = type)) +
    #   geom_density(alpha = 0.5, adjust = 1, bw = 0.5) +
    #   geom_vline(xintercept = GOF$Joint$ObservedTestStat, color = "red", linetype = "dashed") +
    #   ggtitle("Indegree Distribution Goodness of Fit") +
    #   theme_minimal()

# works but it's the same thing as with the custom function... It not a violin-plot and just does not hit the spot. 
# The only violins I have are the ones playing the sad self-pity music in my brain right now.

##--------- reinstall RSiena -------

# I.... 
    # ....
      # .... 
        # .... sure.

# --------- I hate myself and back we go to GOF -----
# other siena GOF functions (outdegree does not work either, GeodesicDistribution weirdly enough works.)

#gofo0 <- sienaGOF(model_test, OutdegreeDistribution, verbose = FALSE, join = TRUE, levls = c(0:10, 15, 20), varName = "nets")
#plot(gofo0, main ="Test Outdegree Distr")

#gof0.gd <- sienaGOF(model_test, GeodesicDistribution, cumulative = FALSE, verbose = FALSE, join = TRUE, varName = "nets")
#plot(gof0.gd, main ="Test Geodesic")

```

```{=html}
<!--

Make it a directed network:  ties from "all" to "first"
focus: writing,
model interpretation

### Questions

-   Is the use of RSiena different for people who look at 1 vs 2 waves.
    I need to look at one, made 2 anyways bc RSiena needs waves to do
    it's thing but:\
    Doesn't it look at ministeps over time? How can I interpret the
    output in a way that pertains to only one wave when the process
    seems to consider it within the construct of 'future change'?

    -   How does my model interpretation potentially differ from peeps
        who looked at two waves (or more)?

-   not looking at TWoStep! diff. modelling process. 
RSiena works with ministeps indeed not just Twosteps (that works with two steps lol)

- diff. betweeen wave 1 and wave 2 model -> convergence 
- default recip. and degree: estimates the putput based on a certain reciproc. and degree "assumption"

-->
```
## \<\> Model 0 - Null Model

First, I estimate a null model with only reciprocity and degree. The
maximum convergence of the model is **NUMBER** The GOF on the Indegree
Distribution is **NUMBER** To have all GOF plots compiled in one place,
see here: *Link GOF page* This indicates that the model is a bad fit for
the data, which was to be expected since we ran a null model without any
network effects.

**CHANGE** Both reciprocity and density are significant for an alpha of
**NUMBER**.

**meaning of significance in RSiena** "It is important to mention that
significance in RSiena means something different than in conventional
statistics. In normal statistics, such as OLS-regression, significance
of estimates refers to the fact that they are not 0 (**RELEVANT?**). In
RSiena, however, it refers to the fact that the estimates were precisely
determined (Ripley et al. 2011). Going forward with this chapter,
significance will refer to this definition of significance." - Niels
Vullings

This model has a density parameter of **NUMBER**, suggesting that
"people generally do not want to have a dense network".

The reciprocity parameter of **NUMBER** indicates that "people like to
send ties back to people who have sent a tie to them."

### ---Step 1: Define Siena Data & Variables

```{r RSiena define m0}
# dependent variable 
nets <- sienaDependent(net_array)

# define data object 
mydata_M0 <- sienaDataCreate(nets)

```

Print short descriptive report

```{r}
ifelse(!dir.exists("results"), dir.create("results"), FALSE)

```

```{r}
print01Report(mydata_M0, modelname = "./results/results_M0") # create file with report in results folder 
```

### ---Step 2: Make effects object/structure

```{r RSiena myeff M0}
# define effects structure 
myeff_M0 <- getEffects(mydata_M0)

```

### ---Step 3: Add Effects

```{r effects M0}

myeff_M0 <- includeEffects(myeff_M0, isolateNet, inPop, outAct)

```

<!-- # Null model: just myeff (just degree and reciprocity by default) # model0  #for this when you create Siena Data, do not add the gender variable -->

### ---Step 4: Specify model/algorithm

```{r algo M0}

myAlgorithm_M0 <- sienaAlgorithmCreate (projname = "results_M0")

```

### ---Step 5: Estimate model

```{r estimate M0, eval=FALSE}
# estimate the model 
Model0 <- siena07(myAlgorithm_M0, data = mydata_M0, effects = myeff_M0, returnDeps = TRUE)
Model0
# maximum convergence >.25
# run again:
Model0.1 <- siena07(myAlgorithm_M0, data = mydata_M0, effects = myeff_M0, prevAns= Model0, returnDeps = TRUE)
Model0.1

#fsave(Model0, file ="estimated_M0")
#fsave(Model0.1, file = "estimated_M0.1")

```

```{r load M0 output, echo=FALSE}
Model0 <- fload("./data/processed/estimated_M0_20241123.rda")
Model0

Model0.1 <- fload("./data/processed/estimated_M0.1_20241123.rda")
Model0.1

```

```{r GOF M0}
GOF_M0.1 <- sienaGOF(Model0.1, IndegreeDistribution, verbose = FALSE, join = TRUE, varName = "nets")

plot(GOF_M0.1, main = 'GOF - "Null" Model 0 \n Indegree Distribution')
```

------------------------------------------------------------------------

## \<\> Model 1 - Structural Effects

This model additionally entails InPop, outAct, isolateNet as network
statistics.

**CHANGE** "It has a convergence of **NUMBER** and a Goodness of Fit on
the indegree distribution of **NUMBER**."

"Indegree Popularity (inPop) is defined as the extent to which people
who have a lot of indegrees are more popular to connect with. This
parameter is NUMBER, meaning that actors have a preference to connect
with actors who have a lot of indegrees. The parameter is significant
for an alpha of **NUMBER**."

"Outdegree Activity (outAct) has a value of **NUMBER**, but is not
significant. IsolateNet is significant andhas a value of NUMBER and
refers to the preference of remaining an isolate. As this value is
positive (\*IS IT??!\*\*), it means that people prefer to be an isolate
in the network."

### ---Step 1: Define Siena Data & Variables

```{r RSiena define M1}
# dependent variable 
nets <- sienaDependent(net_array)

# define data object 
mydata_M1 <- sienaDataCreate(nets)

```

Print short descriptive report

```{r}
ifelse(!dir.exists("results"), dir.create("results"), FALSE)

```

```{r}
print01Report(mydata_M1, modelname = "./results/results_M1") # create file with report in results folder 
```

### ---Step 2: Make effects object/structure

```{r RSiena myeff m1}
# define effects structure 
myeff_M1 <- getEffects(mydata_M1)

```

### ---Step 3: Add Effects

```{r effects m1}

myeff_M1 <- includeEffects(myeff_M1, isolateNet, inPop, outAct)

```

### ---Step 4: Specify model/algorithm

```{r algo m1}

myAlgorithm_M1 <- sienaAlgorithmCreate (projname = "results_M1")

```

### ---Step 5: Estimate model

```{r estimate m1, eval = FALSE}
# estimate the model 
Model1 <- siena07(myAlgorithm_M1, data = mydata_M1, effects = myeff_M1, returnDeps = TRUE)
Model1
# maximum convergence >.25
# run again:
Model1.1 <- siena07(myAlgorithm_M1, data = mydata_M1, effects = myeff_M1, prevAns= Model1, returnDeps = TRUE)
Model1.1

#fsave(Model1, file ="estimated_M1")
#fsave(Model1.1, file = "estimated_M1.1")

```

```{r load M1 output, echo=FALSE}

Model1 <- fload("./data/processed/estimated_M1_20241123.rda")
Model1

Model1.1 <- fload("./data/processed/estimated_M1.1_20241123.rda")
Model1.1
```

### ---Step 6: GOF - Goodness of Fit

```{r GOF M1}
GOF_M1.1 <- sienaGOF(Model1.1, IndegreeDistribution, verbose = FALSE, join = TRUE, varName = "nets")

plot(GOF_M1.1, main = "GOF - Model 1 \n Indegree Distribution")
```

------------------------------------------------------------------------

## \<\> Model 2 - Gender

This model is partly similar to Model 1 but additionally holds the
network statistics sameX, diffXTransTrip, egoX & altX of the covariate
gender.

**CHANGE** "This model has a convergence of **0.23** and a Goodness of
Fit on the indegree distribution of **0.184**. For the structural
network statistics we find similar results, in terms of estimate size
and significance, as in Model 1. However, the outdegree activity
parameter almost reaches significance (**-1.7135484**).

With regard to the covariate network statistics, we find that the gender
of ego (egoX), the gender of alter (altX) **are not significant and thus
the estimate cannot be trusted**."

### ---Step 1: Define Siena Data & Variables

```{r RSiena define m2}
# dependent variable 
nets <- sienaDependent(net_array)

# put gender in object 
gender <- df_ego$gender

# covariate 1
gender_RS <- coCovar(gender) # gender as covariate in Rsiena

# define data object 
mydata_M2 <- sienaDataCreate(nets, gender_RS)

```

Print short descriptive report

```{r}
ifelse(!dir.exists("results"), dir.create("results"), FALSE)

```

```{r}
print01Report(mydata_M2, modelname = "./results/results_M2") # create file with report in results folder 
```

### ---Step 2: Make effects object/structure

```{r RSiena myeff m2}
# define effects structure 
myeff_M2 <- getEffects(mydata_M2)
```

### ---Step 3: Add Effects

```{r effects m2}
myeff_M2 <- includeEffects(myeff_M2, isolateNet, inPop, outAct)

myeff_M2 <- includeEffects(myeff_M2, egoX, altX, diffXTransTrip, sameX, interaction1 = "gender_RS") 
```

```{=html}
<!--
# isolatenet: if individual is alone they "like to/tend to stay alone"
# inPop: ppl like to collaborate with people who are popular

# sameX
# same covariate, which can also be called covariate-related identity (sameX), defined by the number of ties of i to all other actors j who have exactly the same value on the covariate, s net i95(x) = P jxij I{vi = vj},
# where the indicator function I{vi = vj} is 1 if the condition {vi = vj} is satisfied, and 0 if it is not;

#diffXTransTrip
different covariate × transitive triplets (diffXTransTrip), defined by the number
of transitive triplets i → h → j ← i that have different covariate values for i and j,
diff. cov. values = diff gender

-->
```
### ---Step 4: Specify model/algorithm

```{r algo m2}

myAlgorithm_M2 <- sienaAlgorithmCreate (projname = "results_M2")

```

### ---Step 5: Estimate model

```{r estimate m2, eval =FALSE}
# estimate the model 
Model2 <- siena07(myAlgorithm_M2, data = mydata_M2, effects = myeff_M2, returnDeps = TRUE)
Model2
# maximum convergence >.25
# run again:
Model2.1 <- siena07(myAlgorithm_M2, data = mydata_M2, effects = myeff_M2, prevAns= Model2, returnDeps = TRUE)
Model2.1

#fsave(Model2, file ="estimated_M2")
#fsave(Model2.1, file = "estimated_M2.1")

```

```{r load M2 output, echo=FALSE}

Model2 <- fload("./data/processed/estimated_M2_20241123.rda")
Model2

Model2.1 <- fload ("./data/processed/estimated_M2.1_20241123.rda")
Model2.1
```

### ---Step 6: GOF - Goodness of Fit

```{r GOF M2}
GOF_M2.1 <- sienaGOF(Model2.1, IndegreeDistribution, verbose = FALSE, join = TRUE, varName = "nets")

plot(GOF_M2.1, main = "GOF - Model 2 \n Indegree Distribution")
```

------------------------------------------------------------------------

## \<\> Model 3 - Department

This model is partly similar to Model 2 but additionally holds the
network statistics egoX and altX for the main effect of department, to
test if an alter's department affects an ego's tendency to initiate
collaborations and to see if department affects an individual’s
attractiveness as a collaborator.

**CHANGE** "This model has a convergence of **0.23** and a Goodness of
Fit on the indegree distribution of **0.184**. For the structural
network statistics we find similar results, in terms of estimate size
and significance, as in Model 1. However, the outdegree activity
parameter almost reaches significance (**-1.7135484**).

With regard to the covariate network statistics, we find that the gender
of ego (egoX), the gender of alter (altX) **are not significant and thus
the estimate cannot be trusted**."

### ---Step 1: Define Siena Data & Variables

```{r RSiena define m3}
# dependent variable 
nets <- sienaDependent(net_array)

# put gender in object 
gender <- df_ego$gender

# covariate 1
gender_RS <- coCovar(gender) # gender as covariate in Rsiena

#put department in object 
department <- factor(df_ego$discipline.24, levels = c("sociology", "political science"))
#make numeric
department_numeric <- as.numeric(department) - 1 # sociology = 0, political science = 1
# covariate 2
departm_RS <- coCovar(department_numeric)

# define data object 
mydata_M3 <- sienaDataCreate(nets, gender_RS, departm_RS)

```

Print short descriptive report

```{r}
ifelse(!dir.exists("results"), dir.create("results"), FALSE)

```

```{r}
print01Report(mydata_M3, modelname = "./results/results_M3") # create file with report in results folder 
```

### ---Step 2: Make effects object/structure

```{r RSiena myeff m3}
# define effects structure 
myeff_M3 <- getEffects(mydata_M3)
```

### ---Step 3: Add Effects

```{r effects m3}
myeff_M3 <- includeEffects(myeff_M3, isolateNet, inPop, outAct) # model 1

myeff_M3 <- includeEffects(myeff_M3, egoX, altX, diffXTransTrip, sameX, interaction1 = "gender_RS") #model 2

myeff_M3 <- includeEffects(myeff_M3, egoX, altX, sameX, interaction1 = "departm_RS") #model 3

```

```{=html}
<!--
# isolatenet: if individual is alone they "like to/tend to stay alone"
# inPop: ppl like to collaborate with people who are popular

# sameX
# same covariate, which can also be called covariate-related identity (sameX), defined by the number of ties of i to all other actors j who have exactly the same value on the covariate, s net i95(x) = P jxij I{vi = vj},
# where the indicator function I{vi = vj} is 1 if the condition {vi = vj} is satisfied, and 0 if it is not;

#diffXTransTrip
different covariate × transitive triplets (diffXTransTrip), defined by the number
of transitive triplets i → h → j ← i that have different covariate values for i and j,
diff. cov. values = diff gender

-->
```
### ---Step 4: Specify model/algorithm

```{r algo m3}

myAlgorithm_M3 <- sienaAlgorithmCreate (projname = "results_M3")

```

### ---Step 5: Estimate model

```{r estimate m3, eval =FALSE}
# estimate the model 
Model3 <- siena07(myAlgorithm_M3, data = mydata_M3, effects = myeff_M3, returnDeps = TRUE)
Model3

# if maximum convergence >.25: run again
#Model3.1 <- siena07(myAlgorithm_M3, data = mydata_M3, effects = myeff_M3, prevAns= Model3, returnDeps = TRUE)
#Model3.1

#fsave(Model3, file ="estimated_M3")
#fsave(Model3.1, file = "estimated_M3.1")

```

```{r load M3 output, echo=FALSE}

Model3 <- fload("./data/processed/estimated_M3_20241123.rda")
Model3

#Model3.1 <- fload ("./data/processed/estimated_M3.1_20241123.rda")
#Model3.1
```

### ---Step 6: GOF - Goodness of Fit

```{r GOF M3}
GOF_M3 <- sienaGOF(Model3, IndegreeDistribution, verbose = FALSE, join = TRUE, varName = "nets")

plot(GOF_M3, main = "GOF - Model 3 \n Indegree Distribution")
```

------------------------------------------------------------------------

## \<\> Model 4 - H-Index

This model further builds on the prior model and also includes the
network statistics of the covariat H-index, namely **egoX, altX and
inPopX**.

**CHANGE!!!** "This model has a convergence ratio of **0.23** and a a
Goodness of Fit on the indegree distribution of **0.64**. In this model,
the parameters for density and reciprocity are still significant, with
values of **-1.98** (se = **0.71**) and **2.59** (se = **0.38**)
respectively, meaning that actors prefer sparse networks, but do prefer
to send ties to alters who have sent ties to them.

IsolateNet is still significant with a value of **3.23** (se =
**1.06**), implying that actors prefer to be isolates.

In this model, **indegree popularity squared** (b = **0.17**, se =
**0.21**) is no longer significant, implying that this might be
explained by other network statistics in the model.

The covariate statistics for gender show similar findings as Model 2,
namely that actors prefer to close triads with alters that have a
different score for gender (b = **1.51**, se = **0.44**).

The ego effect and alter effect for gender are **non-significant**, as
was the case in Model 2.

Lastly, Model 3 shows some significant results with regards to the
covariate network statistics for prestige. The prestige effect for
alters is positive, implying that people prefer to send ties to people
who have a higher amount of prestige (b = **0.042**, se = **0.0089**).

Additionally, the prestige effect for egos is negative, which indicates
that people who have higher prestige send less ties (b = **-0.030**, se
= **0.015**). **This is in line with theories of preferential attachment
and upward mobility, because as egos with higher prestige will are more
likely to receive request for collaboration rather then sending request
for collaboration.**

Interestingly enough, the indegree popularity statistic for prestige is
not significant (b = **-0.012**, se = **0.023**), implying that actors
who are more prestigious do not receive more indegrees."

### ---Step 1: Define Siena Data & Variables

```{r RSiena define m4}
# dependent variable 
nets <- sienaDependent(net_array)

# put gender in object 
gender <- df_ego$gender
# covariate 1
gender_RS <- coCovar(gender) # gender as covariate in Rsiena

#put department in object 
department <- factor(df_ego$discipline.24, levels = c("sociology", "political science"))
#make numeric
department_numeric <- as.numeric(department) - 1 # sociology = 0, political science = 1
# covariate 2
departm_RS <- coCovar(department_numeric)

# put h-index in object 
h_index <- df_ego$h_index
df_ego$h_index
# covariate 3
h_index_RS <- coCovar(h_index) # h_index as covariate in RSiena

# define data object 
mydata_M4 <- sienaDataCreate(nets, gender_RS, departm_RS, h_index_RS)

```

Print short descriptive report

```{r}
ifelse(!dir.exists("results"), dir.create("results"), FALSE)

```

```{r}
print01Report(mydata_M4, modelname = "./results/results_M4") # create file with report in results folder 
```

### ---Step 2: Make effects object/structure

```{r RSiena myeff M4}

# define effects structure 
myeff_M4 <- getEffects(mydata_M4)

```

### ---Step 3: Add Effects

```{r effects M4}

myeff_M3 <- includeEffects(myeff_M3, isolateNet, inPop, outAct) # model 1

myeff_M3 <- includeEffects(myeff_M3, egoX, altX, diffXTransTrip, sameX, interaction1 = "gender_RS") #model 2

myeff_M3 <- includeEffects(myeff_M3, egoX, altX, sameX, interaction1 = "departm_RS") #model 3

myeff_M4 <- includeEffects(myeff_M4, egoX, altX, inPopX, interaction1 = "h_index_RS") # model 4

```

```{=html}
<!--
# isolatenet: if individual is alone they "like to/tend to stay alone"
# inPop: ppl like to collab with people who are popular

# sameX
# same covariate, which can also be called covariate-related identity (sameX), defined by the number of ties of i to all other actors j who have exactly the same value on the covariate, s net i95(x) = P jxij I{vi = vj},
# where the indicator function I{vi = vj} is 1 if the condition {vi = vj} is satisfied, and 0 if it is not;

# look up inPopX: preferential attachment (cf. Koen lel), higher h-index more popular 
  # cf. Fridas modeling process (Jochem told her that )

-->
```
### ---Step 4: Specify model/algorithm

```{r algo M4}

myAlgorithm_M4 <- sienaAlgorithmCreate (projname = "results_M4")

```

### ---Step 5: Estimate model

```{r estimate M4, eval =FALSE}
# estimate the model 
Model4 <- siena07(myAlgorithm_M4, data = mydata_M4, effects = myeff_M4, returnDeps = TRUE)
Model4

fsave(Model4, file ="estimated_M4")

```

```{r load M4 output, echo=FALSE}

Model4 <- fload("./data/processed/estimated_M4_20241123.rda")
Model4

```

### ---Step 6: GOF - Goodness of Fit

```{r GOF M4}
GOF_M4 <- sienaGOF(Model4, IndegreeDistribution, verbose = FALSE, join = TRUE, varName = "nets")

plot(GOF_M4, main = "GOF - Model 4 \n Indegree Distribution")
```

### 2024-11-23 revisitwithJochem.Rmd
modelestimates-GOFs-desresults-darkgraph

@@
 # undirected: model 6 "additive model", #check manual for this
+# NOW ITS DIRECTED SO USE DIFFERENT MODELTYPE FOR ALGORITHM 
 ```

### 2024-11-23 week5-2.Rmd
modelestimates-GOFs-desresults-darkgraph

@@
 # 7.13 STEP 4: Specify model 
-Sometimes similartostep 2 (but here you include specifically the effects you want to look at)
+Sometimes similartostep  (but here you include specifically the effects you want to look at)2
 ```{r}
@@
 over time:
-inpope ppl with lots of indegrees will havelot of indegrees later (in population)
- outAct ppl with lots of outdegrees will have lot of indegrees later
+inpop: ppl with lots of indegrees will havelot of indegrees later (in population)
+ outAct: ppl with lots of outdegrees will have lot of indegrees later
 
@@
 
-# Sidenote: H- index via openAlex
+## Sidenote: H- index via openAlex
 
@@
 # STUDY CHAPTER 12 of RSiena Manual! 
-# PrACTICE WITH RSIENA
-
-# DONT GO OVERBOARD!!! 
-# REMAIN FOCUSED!!!
+## PrACTICE WITH RSIENA 
+# DONT GO OVERBOARD!!! & REMAIN FOCUSED!!!

### 2024-11-23 weekbacktrack.Rmd
modelestimates-GOFs-desresults-darkgraph

@@
 |                                                                                                   |                                                              |                                                                 |                                                                                            |                                                                               |                                                                            |                                                                                      |
-| ![](images/socialnetworking_meh.jpg){width="800"}Check in with Jochem                             | ![](images/used_arson%20frog.jpg){width="952"}*[university]* | ![](images/used_arson%20frog.jpg)*[university]*                 | ![](images/socialnetworking_meh.jpg)*[Depression]*                                         | ![](images/socialnetworking_meh.jpg)*[Depression]*                            | ![](images/socialnetworking.jpg){width="800"}Write data, methods           | ![](images/socialnetworking_meh.jpg)*[university]*write introduction, and theory [W] |
+| ![](images/socialnetworking_meh.jpg){width="800"}Check in with Jochem                             | ![](images/used_arson%20frog.jpg){width="952"}*[university]* | ![](images/used_arson%20frog.jpg)*[university]*                 | ![](images/socialnetworking_meh.jpg)*[Depression]*                                         | ![](images/socialnetworking_meh.jpg)*[Depression]*                            | ![](images/socialnetworking.jpg){width="800"}Write data, methods outline   | ![](images/socialnetworking_meh.jpg)*[university]*write introduction, and theory [W] |
 |                                                                                                   |                                                              |                                                                 |                                                                                            |                                                                               |                                                                            |                                                                                      |
-| Continue description & plotting [S3]                                                              |                                                              |                                                                 | Continue description & plotting [S3]                                                       | Data & methods part [W]                                                       |                                                                            |                                                                                      |
+| Continue description & plotting [S3]                                                              |                                                              |                                                                 | Continue description & plotting [S3]                                                       | write Data part [W]                                                           | Make darkmode bc my eyes will fall out                                     |                                                                                      |
 +---------------------------------------------------------------------------------------------------+--------------------------------------------------------------+-----------------------------------------------------------------+--------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------+----------------------------------------------------------------------------+--------------------------------------------------------------------------------------+

### 2024-11-23 modelestimate.Rmd
nullmodelcorrection

@@
 
-First, I estimate a null model with only reciprocity and degree. The
-maximum convergence of the model is **NUMBER** The GOF on the Indegree
-Distribution is **NUMBER** To have all GOF plots compiled in one place,
-see here: *Link GOF page* This indicates that the model is a bad fit for
-the data, which was to be expected since we ran a null model without any
-network effects.
-
-**CHANGE** Both reciprocity and density are significant for an alpha of
+First, I estimate a null model with only reciprocity and degree.
+
+The maximum convergence ratio of the model is 0.084. The GOF on the
+Indegree Distribution is zero**.** This indicates that the model is a
+very bad fit for the data. This is not suprising since we ran a null
+model without any network effects.ffects.
+
+For all GOF plots compiled in one place, see here:
+<https://treesdude.github.io/labjournal/finalGOF.html>
+
+CHANGE Both reciprocity and density are significant for an alpha of
 **NUMBER**.
+
+Estimates and standard errors
+
+Rate parameters:
+
+0\. Rate parameter 2.117 ( 0.3561)
+
+Other parameters:
+
+1\. eval: outdegree (density) -2.6388 ( 0.1460) convergence t ratio:
+0.0182
+
+2\. eval: reciprocity 1.8035 ( 0.4343) convergence t ratio: -0.0668
 
@@
 
-```{r effects M0}
-
-myeff_M0 <- includeEffects(myeff_M0, isolateNet, inPop, outAct)
-
-```
-
-<!-- # Null model: just myeff (just degree and reciprocity by default) # model0  #for this when you create Siena Data, do not add the gender variable -->
+Null model: none.
 
@@
 Model0
-# maximum convergence >.25
-# run again:
-Model0.1 <- siena07(myAlgorithm_M0, data = mydata_M0, effects = myeff_M0, prevAns= Model0, returnDeps = TRUE)
-Model0.1
-
-#fsave(Model0, file ="estimated_M0")
-#fsave(Model0.1, file = "estimated_M0.1")
+
+fsave(Model0, file ="estimated_M0")
 
@@
 
-Model0.1 <- fload("./data/processed/estimated_M0.1_20241123.rda")
-Model0.1
-
 ```
@@
 ```{r GOF M0}
-GOF_M0.1 <- sienaGOF(Model0.1, IndegreeDistribution, verbose = FALSE, join = TRUE, varName = "nets")
-
-plot(GOF_M0.1, main = 'GOF - "Null" Model 0 \n Indegree Distribution')
+GOF_M0 <- sienaGOF(Model0, IndegreeDistribution, verbose = FALSE, join = TRUE, varName = "nets")
+
+plot(GOF_M0, main = 'GOF - "Null" Model 0 \n Indegree Distribution')
 ```
@@
 
-**CHANGE** "It has a convergence of **NUMBER** and a Goodness of Fit on
-the indegree distribution of **NUMBER**."
+"The model has a maximum convergence ratio of **0.17** and a Goodness of
+Fit on the indegree distribution of **.002.**"
 
@@
 in the network."
+
+Estimates and standard errors
+
+Rate parameters:
+
+0\. Rate parameter 3.3566 ( 0.5773)
+
+Other parameters:
+
+1\. eval: outdegree (density) -2.0862 ( 0.7050)
+
+2\. eval: reciprocity 1.0894 ( 0.4144)
+
+3\. eval: indegree - popularity 0.2549 ( 0.0439)
+
+4\. eval: outdegree - activity -0.0936 ( 0.1301)
+
+5\. eval: network-isolate 4.9645 ( 1.1146)
+
+convergence t ratio:
+
+```         
+1
+0.0232
+```
+
+```         
+2
+0.0467
+```
+
+```         
+3
+-0.0195
+```
+
+```         
+4
+-0.0423
+```
+
+```         
+5
+-0.061
+```
+
+```         
+ -0.0617
+```
 
@@
 
-**CHANGE** "This model has a convergence of **0.23** and a Goodness of
-Fit on the indegree distribution of **0.184**. For the structural
-network statistics we find similar results, in terms of estimate size
-and significance, as in Model 1. However, the outdegree activity
-parameter almost reaches significance (**-1.7135484**).
+```         
+Estimates, standard errors and convergence t-ratios                                                
+                                            Estimate   Standard   Convergence
+                                                        Error      t-ratio     
+Rate parameters:    
+0       Rate parameter                       2.9204  ( 0.4617   )
+
+Other parameters:    
+1. eval outdegree (density)                 -1.8628  ( 1.1060   )    0.0703      
+2. eval reciprocity                          1.3341  ( 0.4543   )   -0.0152      
+3. eval indegree - popularity                0.2209  ( 0.0470   )   -0.0083      
+4. eval outdegree - activity                -0.3017  ( 0.2287   )    0.0806      
+5. eval network-isolate                      4.7507  ( 1.5194   )   -0.0379      
+6. eval gender_RS alter                      0.3254  ( 0.2701   )    0.0411      
+7. eval gender_RS ego                       -1.0642  ( 0.6055   )   -0.0400      
+8. eval same gender_RS                       0.6637  ( 0.2685   )    0.0308      
+9. eval transitive triplets diff. gender_RS  2.1787  ( 0.6027   )    0.0416   
+```
+
+The maximum convergence ratio for model 2 is **0.132** and the Goodness
+of Fit on the indegree distribution is **0.096**.
+
+**CHANGE!!**
+
+"For the structural network statistics we find similar results, in terms
+of estimate size and significance, as in Model 1. However, the outdegree
+activity parameter almost reaches significance (**-1.7135484**).
 
@@
 the estimate cannot be trusted**."
+
+egoX and altX: model whether male or female scholars are more likely to
+initiate or receive ties.
+
+**sameX (Gender)**: Tests whether scholars prefer same-gender
+collaborators (direct measure of gender homophily).\
+model the general tendency for scholars to collaborate with same-gender
+peers.
+
+**Confirmation**:
+
+-   Significant and positive coefficient for `sameX` in the RSiena
+    output would confirm that gender homophily exists.
+
+-   A non-significant or negative coefficient would disconfirm this
+    hypothesis.
+
+**Confirmation**:
+
+-   Significant and positive coefficient for `sameX` in the RSiena
+    output would confirm that gender homophily exists.
+
+-   A non-significant or negative coefficient would disconfirm this
+    hypothesis.
+
+Hypothesis about structural effects
+
+-   **Network Statistics**:
+
+    -   **sameX (Gender)**: Tests for gender homophily directly.
+
+    -   Structural statistics like **reciprocity**, **inPop**,
+        **outAct**, and **isolateNet** are control variables to account
+        for network-level dynamics.
+
+-   **Confirmation**:
+
+    -   A significant `sameX` coefficient, even after including
+        structural controls, would confirm that gender homophily exists
+        at the dyadic level.
+
+    -   If `sameX` becomes non-significant after controls, it suggests
+        structural factors, not individual preferences, explain gender
+        clustering.
 
@@
 network statistics egoX and altX for the main effect of department, to
-test if an alter's department affects an ego's tendency to initiate
-collaborations and to see if department affects an individual’s
-attractiveness as a collaborator.
-
-**CHANGE** "This model has a convergence of **0.23** and a Goodness of
-Fit on the indegree distribution of **0.184**. For the structural
-network statistics we find similar results, in terms of estimate size
-and significance, as in Model 1. However, the outdegree activity
-parameter almost reaches significance (**-1.7135484**).
+control for differences in collaboration patterns between the two
+departments.
+
+Model 3 has a maximum convergence ratio of **0.182** and a Goodness of
+Fit on the indegree distribution of **0.108**.
+
+**CHANGE** !!!!
+
+For the structural network statistics we find similar results, in terms
+of estimate size and significance, as in Model 1. However, the outdegree
+activity parameter almost reaches significance (**-1.7135484**).
 
@@
 the estimate cannot be trusted**."
+
+Estimates and standard errors
+
+Rate parameters:
+
+0\. Rate parameter 3.1013 ( 0.5186)
+
+Other parameters:
+
+1\. eval: outdegree (density) -4.3233 ( 1.0871)
+
+2\. eval: reciprocity 1.0725 ( 0.4174)
+
+3\. eval: indegree - popularity 0.2122 ( 0.0517)
+
+4\. eval: outdegree - activity -0.3364 ( 0.2182)
+
+5\. eval: network-isolate 4.2006 ( 1.3007)
+
+6\. eval: gender_RS alter 0.3356 ( 0.2659)
+
+7\. eval: gender_RS ego -1.0066 ( 0.5121)
+
+8\. eval: same gender_RS 0.6632 ( 0.2623)
+
+9\. eval: transitive triplets diff. gender_RS 1.5479 ( 0.5403)
+
+10\. eval: departm_RS alter 0.4141 ( 0.7546)
+
+11\. eval: departm_RS ego -1.1573 ( 0.9148)
+
+12\. eval: same departm_RS 2.7240 ( 0.7277)
+
+-   **Network Statistics**:
+
+    -   **sameX (Gender)**: Compute and compare the size and
+        significance of the coefficient for each department. This
+        requires separate models for each department or interaction
+        terms that allow the effect to vary by department.
+
+-   **Confirmation**:
+
+    -   A significantly stronger positive coefficient for `sameX` in
+        Political Science compared to Sociology would confirm the
+        hypothesis.
+
+    -   Similar coefficients or reversed patterns would disconfirm the
+        hypothesis.
 
@@
 
-# if maximum convergence >.25: run again
-#Model3.1 <- siena07(myAlgorithm_M3, data = mydata_M3, effects = myeff_M3, prevAns= Model3, returnDeps = TRUE)
-#Model3.1
+#if maximum convergence >.25: run again
+Model3.1 <- siena07(myAlgorithm_M3, data = mydata_M3, effects = myeff_M3, prevAns= Model3, returnDeps = TRUE)
+Model3.1
 
@@
 
-#Model3.1 <- fload ("./data/processed/estimated_M3.1_20241123.rda")
-#Model3.1
+Model3.1 <- fload ("./data/processed/estimated_M3.1_20241123.rda")
+Model3.1
 ```
@@
 ```{r GOF M3}
-GOF_M3 <- sienaGOF(Model3, IndegreeDistribution, verbose = FALSE, join = TRUE, varName = "nets")
-
-plot(GOF_M3, main = "GOF - Model 3 \n Indegree Distribution")
+GOF_M3.1 <- sienaGOF(Model3.1 , IndegreeDistribution, verbose = FALSE, join = TRUE, varName = "nets")
+
+plot(GOF_M3.1, main = "GOF - Model 3 \n Indegree Distribution")
 ```
@@
 
-**CHANGE!!!** "This model has a convergence ratio of **0.23** and a a
-Goodness of Fit on the indegree distribution of **0.64**. In this model,
-the parameters for density and reciprocity are still significant, with
-values of **-1.98** (se = **0.71**) and **2.59** (se = **0.38**)
-respectively, meaning that actors prefer sparse networks, but do prefer
-to send ties to alters who have sent ties to them.
+"The last model has a maximum convergence ratio of **0.23** and a a
+Goodness of Fit on the indegree distribution of **0.197**.
+
+**CHANGE!!!**
+
+"In this model, the parameters for density and reciprocity are still
+significant, with values of **-1.98** (se = **0.71**) and **2.59** (se =
+**0.38**) respectively, meaning that actors prefer sparse networks, but
+do prefer to send ties to alters who have sent ties to them.
 
@@
 
+About Hypothesis 4
+
+modeling how the department of the actor (Sociology or Political
+Science) influences their collaboration choices in terms of gender.
+
+**Interaction1 = "departm_RS"**: This allows you to test how department
+(Sociology vs Political Science) influences the probability of forming
+collaborations, potentially differing by gender. This means that gender
+homophily (whether a person collaborates more often with same-gender
+peers) might be different in the two departments.
+
+allows you to explore how **department** influences the likelihood of
+**same-gender** collaborations (`sameX`), which is central to your
+research question. If the **department variable** is acting as an
+important covariate influencing collaboration patterns, this line
+captures that effect.
+
+testing how being in a particular department influences the likelihood
+of collaborating with someone of the same gender. In other words, it
+checks if the department modifies the strength of gender homophily
+(`sameX`).
+
+**Network Statistics**:
+
+-   **egoX (h-index)**: Examines how the h-index of the focal scholar
+    affects their collaboration behavior.
+
+-   **altX (h-index)**: Examines how the h-index of potential
+    collaborators affects their attractiveness as partners.
+
+    Add `egoX` and `altX` effects for `HIndex_RS` to test if prestigious
+    scholars are more likely to initiate or receive ties.
+
+-   **inPopX (h-index)**: Assesses whether prestige increases the
+    likelihood of being sought out as a collaborator.
+
+**Confirmation**:
+
+-   A significant negative interaction term between `sameX` and h-index
+    statistics would confirm that prestige reduces the strength of
+    gender homophily.
+
+-   If h-index variables do not significantly influence `sameX`, this
+    would disconfirm H3.
+
 ### ---Step 1: Define Siena Data & Variables
@@
 
-myeff_M3 <- includeEffects(myeff_M3, isolateNet, inPop, outAct) # model 1
-
-myeff_M3 <- includeEffects(myeff_M3, egoX, altX, diffXTransTrip, sameX, interaction1 = "gender_RS") #model 2
-
-myeff_M3 <- includeEffects(myeff_M3, egoX, altX, sameX, interaction1 = "departm_RS") #model 3
+myeff_M4 <- includeEffects(myeff_M4, isolateNet, inPop, outAct) # model 1
+
+myeff_M4 <- includeEffects(myeff_M4, egoX, altX, diffXTransTrip, sameX, interaction1 = "gender_RS") #model 2
+
+myeff_M4 <- includeEffects(myeff_M4, egoX, altX, sameX, interaction1 = "departm_RS") #model 3
 
@@
 
-fsave(Model4, file ="estimated_M4")
+#fsave(Model4, file ="estimated_M4")
 

### 2024-11-24 draftGOF.Rmd
draft discussion

@@
 output: html_document
+bibliography: references.bib
+csl: apa.csl
 ---
@@
 <html lang="en">
+
 <head>
+
 <meta charset="UTF-8">
+
 <meta name="viewport" content="width=device-width, initial-scale=1.0">
-    <title>My Descriptives</title>
+
+<title>GOF</title>
+
 <link rel="stylesheet" href="styles.css"> <!-- Link to the CSS file I created for dark mode code chunks -->
@@
 </head>
+
 </html>
@@
 
-# Goodness of fit **CHANGE**
-Koen:
+# Setup
 
-The goodness of fit of a model indicates whether an estimated model represents the observed data.
-This is important as `RSiena` uses simulation to estimate the changes in the network.
-The goodness of fit checks whether the simulation matches the changes in the observed network.
-Due to the nature of the research questions, which focus on the tie formation dependent on indegrees, I tested the goodness of fit for the indegree distribution for each model.
+Clean workspace.
 
-For model 1, 2, and 3, which all included a quadratic effect of indegree popularity, there is a good fit of the data with a p-value between **0,332 and 0,367**.
-This means that the fit only slightly increases when adding ego-level effects on top of the structural network effects.
-Additionally, this means that the estimates for these models can be interpreted.
-For model 4, which replaces the squared estimate of indegree popularity for a non-quadratic effect, there is a significant difference in the observed and expected indegree distribution (**p = 0,03**), indicating the the squared estimate is a better fit for the data.
-This is also in line with the theoretical explanation that the more indegree someone has the the stronger this popularity effect will be.
-The estimates in Model 4 can thus **not be interpreted reliably**.
-
-# Setup
-Clean workspace. 
-```{r clean}
+```{r clean, hide =TRUE}
 rm(list = ls())
@@
 
-```{r package}
+```{r package, hide =TRUE}
 require(RSiena)
@@
 
+# Goodness of Fit
+
+The goodness of fit (GOF) for a model assesses how well the estimated model fits the observed data.
+This evaluation is crucial because `RSiena` relies on simulations to estimate changes within the network (@RSiena_manual).
+GOF measures indicate whether the simulated network matches the changes in the observed network.
+The use of the specific GOF measure of a model's Indegree Distribution seems most appropriate since the study's focus lies on changes in directed ties between schoalrs.
+A GOF with a p-value below .05 indicates a poor fit and calls for adjustment of the model, while a p-value above .05 usually indicates an acceptable or good fit.
+\
+The GOF measures of Indegree Distribution for the null model (*p* = .008) and model 1 *(p* = .002) both display p-values below .05.
+This indicates that they do not fit the data well.
+This makes sense, since the null model and model 1 do not contain any network effects yet.
+This also implies that we should not interpret the estimates of these models.
+The GOF of model 2 (*p* = .096) indicates an acceptable fit, while model 3 (*p* = .12) seems to be even better fitting.
+Overall, the final model, model 4 (*p* = .197), including all the covariates investigated in this study, has the best fit.
+
+```{=html}
+<!--  M0: 0.008  M1: 0.002  M2: 0.096  M3: 0.12  M4: 0.197  -->
+```
 # Model 0
+
 ```{r}
@@
 # Model 1
+
 ```{r}
 Model1.1 <- fload("./data/processed/estimated_M1.1_20241123.rda")
+
 ```
@@
 # Model 2
+
 ```{r}
@@
 # Model 3
+
 ```{r, hide=TRUE}
@@
 ```
+
 # Model 4
+
 ```{r, hide=TRUE}

### 2024-11-24 draftdiscussion.Rmd
draft discussion

---
title: "draft discussion"
author: "Verooo"
date: "2024-11-01"
output: html_document
bibliography: references.bib
csl: apa.csl
---

```{=html}
<style>
body {
text-align: left;
line-height: 1.5;
}

h1, .h1, h2, .h2, h3, .h3 {
  margin-top: 24px;
  line-height: 1;
}

</style>
```
```{r, globalsettings, echo=FALSE, warning=FALSE, results='hide'}
library(knitr)

knitr::opts_chunk$set(echo = TRUE)
opts_chunk$set(tidy.opts=list(width.cutoff=100),tidy=TRUE, warning = FALSE, message = FALSE,comment = "#>", cache=TRUE, class.source=c("test"), class.output=c("test2"))
options(width = 100)
rgl::setupKnitr()

colorize <- function(x, color) {sprintf("<span style='color: %s;'>%s</span>", color, x) }

```

```{r klippy, echo=FALSE, include=TRUE}
klippy::klippy(position = c('top', 'right'))
#klippy::klippy(color = 'darkred')
#klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done')
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

# Discussion Draft

## Short Summary

This study investigates how co-authorship networks among scholars are influenced by gender, departmental affiliation, and academic prestige. By examining networks within the Political Science and Sociology departments at Radboud University, the study aims to understand how these factors jointly shape collaboration networks. Scholars often prefer collaborators of the same gender, a phenomenon rooted in societal norms and perceived status differences. This results in gender clustering within academic networks, with men and women showing distinct preferences for same-gender collaborations (*Hypothesis 1).* Disciplines differ in their gender dynamics. Sociology, characterized by a more balanced gender representation, may facilitate more cross-gender collaborations compared to the male-dominated field of Political Science. Hence, gender homophily might be less influential in collaboration preferences of scholars in the sociology department than those in political science *(Hypothesis 2).\
*Furthermore, structural features of collaboration networks, such as reciprocity, indegree popularity, and outdegree activity, shape how collaboration ties form. These structural network effects may reinforce gender homophily in collaboration preferences in the creation of ties betwen scholars *(Hypothesis 3)*. Prestige, as measured by the Hirsch-Index, may mitigate gender homophily by increasing the appeal of high-status collaborators regardless of their gender. This hypothesis examines whether strategic collaborations dilute gendered preferences in scholarly networks. Specifically it investigates whether gender homophily is less promnounced in scholars' preference to collaborate when potential collaborators have a higher H-index *(Hypothesis 4).*

#### **Gender Homophily (H1)**

The results consistently support **Hypothesis 1**, showing significant evidence of gender homophily across all models. The parameter for same-gender collaboration (sameX) remains positive and significant, indicating that scholars are more likely to collaborate with same-gender peers than with different-gender peers. This aligns with previous research suggesting that gendered barriers in academia, whether structural or cultural, can lead to the formation of gendered clusters/silos in collaborative networks (**\*\*SOURCE\*\***).

Interestingly, the significance of gender homophily persists even after controlling for other covariates, such as department affiliation and h-index, demonstrating that it is a robust phenomenon in these networks. While this result is not unexpected, it emphasizes the enduring influence of gender dynamics on scholarly collaborations.

#### **Departmental Differences in Gender Homophily (H2)**

**Hypothesi 2** proposed that scholars in the sociology department exhibit weaker gender homophily than those in the political science department. While this hypothesis was not explicitly tested using an interaction term, comparisons across models suggest no substantial department-level differences in gender homophily. The same-gender collaboration parameter (sameX for gender) is nearly identical in models 2 and 3, indicating that the inclusion of department as a covariate does not significantly alter the pattern of same-gender collaborations.

However, the department-related parameter for ego’s tendency to initiate collaborations (egoX for department) becomes significant in model 4, revealing a lower likelihood for political scientists to initiate collaborations compared to sociologists. This could imply department-level differences in collaboration norms or opportunities, which might indirectly influence gender homophily. ***Future research should include interaction terms between department and gender to further investigate these nuances.***

Hypothesis 2 was not supported. While scholars show a significant preference for collaborating within their own department, with sociologists more likely to initiate collaborations than political scientists, *no* substantial differences in gender homophily were observed in relation to scholars' departments.

#### **Structural Network Effects and Gender Homophily (H3)**

In terms of structural network effects, reciprocity emerges as a consistently significant factor, indicating that collaborations are more likely to be mutual. This aligns with existing theories of dyadic reciprocity in networks, suggesting that once a collaboration tie is initiated, it is likely to be reciprocated (**\*\*SOURCE\*\***). Interestingly, the outdegree parameter (baseline likelihood of initiating a tie) fluctuates in significance across models but remains consistently negative when significant, indicating that scholars generally show a low tendency to initiate collaborations.

In line with Hypothesis 3, Gender homophily (sameX) remains significant even when controlling for these structural effects, reinforcing its importance. This finding implies that scholars' same-gender preferences in creating ties are not merely a byproduct of network structure but reflect deeper social or cultural dynamics.

#### **Prestige and Gender Homophily (H4)**

The results provide little to no support for **Hypothesis 4**, which proposed that gender homophily is less influential when potential collaborators have higher academic prestige (as measured by the h-index). The inclusion of h-index as a covariate in model 4 reveals that scholars with higher h-index scores are more likely to attract collaborations (significant positive alter effect, altX) but less likely to initiate them (significant negative ego effect, egoX). This is consistent with theories of preferential attachment and upward mobility, where prestigious scholars act as hubs, receiving collaboration requests rather than initiating them (\*\***SOURCE**\*\*).

However, since the the same-gender parameter (sameX) remained significant and largely unchanged, the influence of genderhomophily on scholars' decisions to collaborate is not substantially impacted by scholars' h-index. This finding suggests that while prestige plays a role in shaping collaboration networks, it does mitigate the tendency of scholars to prefer same-gender collaborations over different-gendered ones. Thus, while prestigious scholars are more sought after, their collaboration patterns remain influenced by gender.

------------------------------------------------------------------------

------------------------------------------------------------------------

***STILL DOOOOO! INSERT SOURCES IN TEXT ABOVE***

***PROOF READING NEXT PARTS:***

------------------------------------------------------------------------

------------------------------------------------------------------------

#### **Broader Implications**

The findings of this study highlight the interplay between structural, departmental, and individual factors in shaping co-authorship networks. Gender homophily appears to be a robust and enduring feature of these networks, resisting the influence of prestige and departmental context. This raises important questions about the structural barriers faced by scholars, particularly women, in accessing diverse collaboration opportunities.

From a policy perspective, these results underscore the need for initiatives aimed at reducing gendered collaboration silos. For example, mentorship programs or institutional incentives that encourage cross-gender and cross-department collaborations could help mitigate these patterns. Additionally, the finding that prestigious scholars are less likely to initiate collaborations suggests that early-career researchers, particularly those from underrepresented groups, may face challenges in accessing these high-prestige hubs. Institutions should consider strategies to facilitate connections between early-career and high-prestige scholars to promote equity in collaboration opportunities.

#### **Limitations and Future Research**

This study has several limitations that warrant consideration. First, the lack of interaction terms between gender and department or h-index limits the ability to make strong conclusions about how these factors jointly influence collaboration patterns. Future studies should include such interactions to better understand these dynamics. Second, while the h-index serves as a useful proxy for academic prestige, other measures of prestige or influence, such as grant funding or editorial roles, might yield additional insights. Finally, the generalizability of these findings is limited to the specific departments and network structures examined here.

Future research should explore longitudinal changes in collaboration patterns to assess whether gender homophily weakens over time, particularly as scholars gain prestige. Additionally, examining the role of institutional interventions, such as funding programs or diversity initiatives, could provide valuable insights into strategies for fostering more equitable collaboration networks.

### **Conclusion**

This study contributes to our understanding of the dynamics of co-authorship networks by highlighting the persistent influence of gender homophily, even in the presence of academic prestige and structural network effects. While prestigious scholars are more likely to attract collaborations, gendered patterns of collaboration endure, underscoring the need for targeted interventions to address these disparities. By disentangling the effects of gender, department, and prestige, this research provides a foundation for future studies and practical efforts aimed at fostering more inclusive and diverse academic collaboration networks.

### Key Insights

\- Gender homophily is a consistent and significant driver of collaboration, resistant to the moderating effects of department or academic prestige.

\- Department affiliation influences collaboration behavior, with a preference for same-department collaborators but minimal effect on gendered collaboration patterns.

\- Prestige affects who is sought as a collaborator but does not weaken the gendered preferences within these networks.

------------------------------------------------------------------------

# Discussion Outline

Hypothesis 1 was strongly supported as scholars were more likely to collaborate with same-gender peers. Gender homophily (sameX) remains consistently significant across all models,with consistent evidence that scholars prefer same-gender collaborators. This effect persists even after controlling for departmental affiliation and prestige.

#### 1. **Overview of Findings**

-   Briefly summarize the main results in relation to the research questions.

    -   Confirmed presence of **gender homophily** (H1).

    -   No significant differences in homophily between departments sociology and political science departments (H2).

    -   Structural network effects, such as reciprocity and indegree popularity, amplified collaboration patterns without mitigating gender homophily (H3).

    -   High academic prestige (measured by h-index) reduced gender homophily, but its impact was nuanced (H4).

-   *//H1 (Gender Homophily): Supported across all models, with consistent evidence that scholars prefer same-gender collaborators. This effect persists even after controlling for departmental affiliation and prestige.*

-   *H2 (Departmental Differences in Gender Homophily): Not supported; no significant variation in gender homophily is found between Sociology and Political Science departments.*

-   *H3 (Structural Effects and Gender Homophily): Structural effects like reciprocity and indegree popularity consistently influence collaboration patterns, but these effects do not diminish gender homophily.*

-   *H4 (Gender Homophily and Prestige): Partially supported; while prestige influences collaboration preferences, gender homophily remains significant, indicating that prestige does not weaken gender-based patterns in co-authorship. These results provide a nuanced understanding of how gender, departmental affiliation, and academic prestige shape collaboration networks, highlighting persistent gender homophily alongside structural and prestige-related effects.//*

#### 2. **Interpretation of Results**

##### **Gender Homophily in Academic Networks (H1 & RQ1a)**

-   Discuss the observed levels of gender homophily, confirming that scholars predominantly collaborate with same-gender peers.

-   Link findings to existing literature, reinforcing prior work (e.g., Kwiek & Roszka, 2021).

-   Highlight implications for gender equity, particularly the potential barriers for cross-gender collaborations.

##### **Disciplinary Differences in Gender Homophily (H2 & RQ1b)**

-   Analyze why Sociology showed weaker gender homophily than Political Science.

    -   Discuss potential cultural and structural differences in the disciplines, including gender composition and norms.

    -   Relate to societal perceptions of Sociology as more inclusive and Political Science as more male-dominated.

-   Compare findings to prior literature on discipline-specific collaboration patterns and stereotypes.

##### **Structural Network Effects and Reinforcement of Gender Homophily (H3 & RQ2)**

-   Reflect on how structural effects (reciprocity, indegree popularity) shaped collaboration patterns without diminishing homophily.

    -   Structural mechanisms as amplifiers of existing preferences and inequalities.

    -   Discuss potential explanations, such as the persistence of gendered trust or comfort in professional relationships.

-   Consider implications for network-based interventions aimed at reducing gender disparities.

##### **Prestige and Gender Homophily (H4 & RQ3)**

-   Discuss the complex relationship between prestige and gender homophily.

    -   Highlight how high h-index scholars were less constrained by homophilic tendencies, with collaboration patterns becoming more gender-neutral.

    -   Consider why prestige might disrupt homophily: increased visibility, strategic collaborations, or less reliance on informal networks.

    -   Discuss nuances, such as whether the prestige effect benefits men and women equally.

-   Connect findings to upward mobility and preferential attachment theories, emphasizing prestige as a potential pathway to mitigate gender clustering.

#### Theoretical implications

##### H Index

Results: Both an alter's and an ego's H-Index seem to be relevant in collaboration preferences. The significant and positive estimateof AltX (b = 0.0829, SE = 0.0364) suggest that scholars with higher h-index are more preferred as collaborators. The egoX estimate is significant and negative (b = -0.1591, SE = 0.0744) suggesting that scholars with higher h-index are less likely to initiate collaborations. The estimate for the Indegree Popularity weighted by h-index is insignificant, suggesting that high-prestige individuals (as measured by their h-index) do not significantly receive more indegrees

Discussion part about egoX h.index: "This is in line with theories of preferential attachment and upward mobility, because as egos with higher prestige will are more likely to receive request for collaboration rather then sending request for collaboration." - Niels/

#### 3. **Theoretical Implications**

-   **Gender Homophily and Network Dynamics:**

    -   Extend understanding of how homophily operates across different contexts and disciplines.

    -   Reinforce the need for theoretical frameworks that integrate individual preferences, structural factors, and institutional dynamics.

-   **Role of Prestige:**

    -   Position prestige as a critical factor that can challenge entrenched gender biases in collaboration.

    -   Discuss potential for upward mobility to disrupt traditional network inequalities.

#### 4. **Practical Implications**

-   Suggest interventions to address gender disparities in academic networks.

    -   Encourage cross-gender mentoring and collaboration initiatives.

    -   Highlight the importance of creating equitable opportunities for women to attain academic prestige.

-   Advocate for institutional policies that recognize and reward diverse collaboration patterns.

#### 5. **Limitations**

-   Acknowledge constraints of the study:

    -   Focus on two departments at a single university; limited generalizability.

    -   Reliance on h-index as a measure of prestige, which may not capture all dimensions of academic influence.

    -   Potential underreporting or misclassification of gender in the dataset.

-   Discuss the impact of these limitations on the interpretation of findings.

#### 6. **Future Research Directions**

-   Propose avenues for further investigation:

    -   Explore gender homophily across additional disciplines and institutions.

    -   Examine other dimensions of prestige (e.g., leadership roles, grant funding).

    -   Investigate how collaboration networks evolve over time, particularly for early-career scholars.

    -   Study the role of intersectionality, including race, ethnicity, and other identities, in shaping academic networks.

#### **Conclusion**

-   Reiterate the study’s contributions to understanding gender homophily, disciplinary differences, and the role of prestige in academic collaboration.

-   Emphasize the importance of addressing gender dynamics in networks to foster inclusivity and equity in academia.

# References

### 2024-11-24 draftintro.Rmd
draft discussion

@@
 Academic networks often mirror broader societal inequalities, with persistent disparities in opportunities and recognition.
-One such disparity is gender inequality, which continues to shape interactions, opportunities, and outcomes within academia.
+One such disparity id gender inequality, which continues to shape interactions, opportunities, and outcomes within academia.
 
@@
 This phenomenon can influence who gains access to collaboration opportunities, thereby shaping academic trajectories and reinforcing existing inequalities.
-Understanding these dynamics is essential to uncovering how collaboration networks may perpetuate or mitigate gender-based disparities in academia.
+Understanding these dynamics is essential to uncovering how collaboration networks may perpetuate or lessen gender-based disparities in academia.
 
@@
 The structure of these networks affects not only who collaborates but also how academic recognition and resources are distributed (@Cheong2009).
-For example, male-dominated networks may facilitate better access to high-impact collaborations and grant opportunities for men, further perpetuating the gender gap in academic success.
+For example, male-dominated networks may provide better access to high-impact collaborations and grant opportunities for men, further perpetuating the gender gap in academic successes.
 
@@
 
-Another crucial factor influencing collaboration is academic prestige, often measured by publication in high-impact journals.
+Another crucial factor influencing collaboration id academic prestige.
 Scholars with higher prestige, indicated by metrics such as the h-index or publication in top-tier journals, are generally more sought after as collaborators.
@@
 Bellotti et al.
-(@Bellotti2022) found that prestigious male scholars often form networks that exclude women, while McDowell, Singell, and Stater (@Mcdowell2007) observed that female scholars, despite demonstrating similar academic competence, face greater challenges in accessing high-prestige collaborative networks.
+(@Bellotti2022) found that prestigious male scholars often form networks that exclude women, while McDowell and colleagues (@Mcdowell2007) also observed that female scholars, despite demonstrating similar academic competence, face greater challenges in accessing high-prestige collaborative networks.
 
 In this context, it is crucial to explore whether the tendency for gender-based collaboration shifts when prestige factors come into play.
-Specifically, does publishing in prestigious journals mitigate or exacerbate gender homophily in academic networks?
+Specifically, do scholars' h-indeces exacerbate gender homophily in academic networks?
 
@@
 By applying a social network perspective, it offers insights into how gender-based preferences influence co-authorship patterns and how these dynamics vary between disciplines.
-Moreover, by exploring the role of journal prestige, this research highlights how structural factors may intersect with social biases to shape academic opportunities, providing a nuanced understanding of the mechanisms underlying gender disparities in academia.
+Moreover, by exploring the role of journal prestige, this research highlights how structural factors may intersect with social biases to shapw academic opportunities, providing a nuanced understanding of the mechanisms underlying gender disparities in academia.
 

### 2024-11-24 drafttheory.Rmd
draft discussion

@@
 ```
+
 ```{r, globalsettings, echo=FALSE, warning=FALSE, results='hide'}
@@
 
-# Theory Draft
+# Theory Draft 2
+
+## **1.0.1 Theory and Hypotheses**
+
+Understanding collaboration patterns in academia requires examining how individual preferences, structural factors, and institutional norms interact to shape scholarly networks.
+Two key mechanisms guide this inquiry: **homophily**, the tendency to form ties with similar others (@McPherson2001), and **preferential attachment**, where individuals gravitate toward high-prestige collaborators (@Merton1968).
+Additionally, the concept of **upward mobility** highlights how strategic collaborations with prestigious scholars can counterbalance preferences based on similarity, such as gender homophily.
+
+The study tests four hypotheses across the Political Science and Sociology departments at Radboud University to explore how these mechanisms interact to influence collaboration patterns.
+
+### **H1: Gender Homophily in Collaboration Networks**
+
+Homophily explains the widespread tendency of individuals to associate with similar others, a phenomenon deeply embedded in academic networks (@McPherson2001).
+In this context, **gender homophily** manifests as a preference for same-gender collaborations, resulting in gendered clustering within scholarly networks.
+Research highlights that men frequently collaborate with other men, and women with other women, perpetuating disparities in visibility, resource access, and academic advancement (@Horta2022; @Kwiek2021).
+
+This hypothesis builds on evidence of gendered collaboration patterns in academia and investigates whether these patterns persist across diverse academic contexts.
+
+***H1:** Across the collaboration networks of both departments, scholars are more likely to collaborate with same-gender peers than with different-gender peers, indicating the presence of gender homophily.*
+
+### **H2: Variation in Gender Homophily Between Departments**
+
+The extent of gender homophily may vary by discipline due to differences in gender representation and cultural norms.
+Sociology, often seen as more gender-balanced or even female-dominated, may facilitate cross-gender collaborations more than Political Science, which remains a male-dominated field associated with traditional masculine traits such as assertiveness and rationality (@Kwiek2021).
+These cultural perceptions influence collaboration preferences, potentially reducing gender homophily in disciplines where gender parity is normalized.
+
+This hypothesis tests whether departmental norms and gender dynamics shape the degree of homophily observed in collaboration networks.
+
+***H2:** Scholars in the Sociology Department exhibit weaker gender homophily in their collaborations than those in the Political Science Department.*
+
+### **H3: Structural Network Effects and Gender Homophily**
+
+Collaboration networks are also shaped by structural effects such as **reciprocity** (mutual collaboration), **indegree popularity** (preference for well-connected individuals), and **outdegree activity** (individuals actively seeking collaborators).
+These mechanisms reinforce broader social dynamics in scholarly networks, often amplifying existing tendencies such as gender homophily (@Snijders2010).
+For example, well-connected scholars may still attract same-gender collaborators due to persistent societal norms or unconscious biases, even as their popularity grows.
+
+This hypothesis examines whether structural effects enhance collaboration patterns while leaving underlying gender preferences intact.
+
+***H3:** Structural network effects, such as reciprocity and indegree popularity, amplify collaboration tendencies but do not diminish the effect of gender homophily.*
+
+### **H4: The Influence of Prestige on Gender Homophily**
+
+While homophily shapes collaboration patterns, prestige can alter these dynamics by creating opportunities for **upward mobility**.
+Prestige, often measured by the Hirsch-Index, serves as a powerful signal of influence and impact in academia (@Bornmann2020).Scholars seeking career advancement may prioritize collaborations with prestigious colleagues, even if it means collaborating across gender lines(@Broido2019).
+However, as women and other underrepresented groups gain visibility and prestige, their collaboration opportunities expand, potentially mitigating homophily effects (@Knobloch2013).
+Hence, the last hypothesis explores whether the pursuit of prestige mitigates the influence of gender homophily in academic collaboration networks.
+
+***H4:** Gender homophily is less influential in collaboration decisions when the potential collaborator has a higher Hirsch-Index.*
+
+------------------------------------------------------------------------
+
+# Theory Draft 1
 
@@
 
-Understanding collaboration patterns in academia is crucial for unpacking the mechanisms behind the formation of scholarly networks.
+Understanding collaboration patterns in academia id crucial for unpacking the mechanisms behind the formation of scholarly networks.
 One key principle that shapes these networks is **homophily**, the tendency of individuals to associate with others who are similar to them (@McPherson2001).
@@
 Research consistently shows that men tend to collaborate more frequently with other men, and women with other women ( @Horta2022; @Kwiek2021).
-However, the degree and dynamics of this homophily can vary across disciplines and contexts, making it a fertile ground for investigation.
+However, the degree and dynamics of this homophily can vary across disciplines and contexts, making it an interesting field for investigation.
 
@@
 The theoretical framework draws on both **homophily theory** and the concept of **preferential attachment** in academic networks.
-The homophily principle explains the tendency for scholars to form ties with others who share their gender, while preferential attachment highlights the allure of prestigious collaborators ( @Merton1968; @Broido2019).
-Together, these mechanisms shape the structure and evolution of collaboration networks.
+The homophily principle explains the tendency for scholars to form ties with others who share their gender, while preferential attachment highlights the appeal of prestigious collaborators ( @Merton1968; @Broido2019).
+Together, these mechanisms shape thr structure and evolution of collaboration networks.
 
@@
 
+Snijders, T.
+A., Van De Bunt, G.
+G., & Steglich, C.
+E.
+(2009).
+Introduction to stochastic actor-based models for network dynamics.
+*Social Networks*, *32*(1), 44–60.
+<https://doi.org/10.1016/j.socnet.2009.02.004>
+
+@Snijders2010
+
 ------------------------------------------------------------------------

### 2024-11-24 finalGOF.Rmd
draft discussion

@@
 output: html_document
+bibliography: references.bib
+csl: apa.csl
 ---
+```{=html}
+<style>
+body {
+text-align: left;
+line-height: 1.5;
+}
+
+h1, .h1, h2, .h2, h3, .h3 {
+  margin-top: 24px;
+  line-height: 1;
+}
+
+</style>
+```
+
+```{r, globalsettings, echo=FALSE, warning=FALSE, results='hide'}
+library(knitr)
+
+knitr::opts_chunk$set(echo = TRUE)
+opts_chunk$set(tidy.opts=list(width.cutoff=100),tidy=TRUE, warning = FALSE, message = FALSE,comment = "#>", cache=TRUE, class.source=c("test"), class.output=c("test2"))
+options(width = 100)
+rgl::setupKnitr()
+
+colorize <- function(x, color) {sprintf("<span style='color: %s;'>%s</span>", color, x) }
+
+```
+
+```{r klippy, echo=FALSE, include=TRUE}
+klippy::klippy(position = c('top', 'right'))
+#klippy::klippy(color = 'darkred')
+#klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done')
+```
+
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = TRUE)
+
+```

### 2024-11-24 finaltheory.Rmd
draft discussion

@@
 output: html_document
+bibliography: references.bib
+csl: apa.csl
 ---
+
+```{=html}
+<style>
+body {
+text-align: left;
+line-height: 1.5;
+}
+
+h1, .h1, h2, .h2, h3, .h3 {
+  margin-top: 24px;
+  line-height: 1;
+}
+
+</style>
+```
+```{r, globalsettings, echo=FALSE, warning=FALSE, results='hide'}
+library(knitr)
+
+knitr::opts_chunk$set(echo = TRUE)
+opts_chunk$set(tidy.opts=list(width.cutoff=100),tidy=TRUE, warning = FALSE, message = FALSE,comment = "#>", cache=TRUE, class.source=c("test"), class.output=c("test2"))
+options(width = 100)
+rgl::setupKnitr()
+
+colorize <- function(x, color) {sprintf("<span style='color: %s;'>%s</span>", color, x) }
+
+```
+
+```{r klippy, echo=FALSE, include=TRUE}
+klippy::klippy(position = c('top', 'right'))
+#klippy::klippy(color = 'darkred')
+#klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done')
+```
+
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = TRUE)
+
+```
+
+# Theory & Hypotheses
+
+Understanding collaboration patterns in academia requires examining how individual preferences, structural factors, and institutional norms interact to shape scholarly networks.
+Two key mechanisms guide this inquiry: **homophily**, the tendency to form ties with similar others (@McPherson2001), and **preferential attachment**, where individuals gravitate toward high-prestige collaborators (@Merton1968).
+Additionally, the concept of **upward mobility** highlights how strategic collaborations with prestigious scholars can counterbalance preferences based on similarity, such as gender homophily.
+The study tests four hypotheses across the Political Science and Sociology departments at Radboud University to explore how these mechanisms may interact to influence scholars' collaboration patterns.
+
+## **H1: Gender Homophily in Collaboration Networks**
+
+Homophily explains the widespread tendency of individuals to associate with similar others, a phenomenon deeply embedded in academic networks (@McPherson2001).
+In this context, **gender homophily** manifests as a preference for same-gender collaborations, resulting in gendered clustering within scholars' networks.
+Research highlights that men frequently collaborate with other men, and women with other women, perpetuating disparities in visibility, resource access, and academic advancement (@Horta2022; @Kwiek2021).
+Thus, the first hypothesis builds on evidence of gendered collaboration patterns in academia and investigates whether these patterns persist across diverse academic contexts.
+
+-   ***H1:** Across the collaboration networks of both, the sociology and the political sciene department, scholars are more likely to collaborate with same-gender peers than with different-gender peers, indicating the presence of gender homophily.*
+
+## **H2: Variation in Gender Homophily Between Departments**
+
+The extent of gender homophily may vary by discipline duee to differences in gender representation and cultural norms.
+Sociology, often seen as more gender-balanced or even female-dominated, may facilitate cross-gender collaborations more than Political Science, which remains a male-dominated field associated with traditional masculine traits such as assertiveness and rationality (@Kwiek2021).
+These cultural perceptions influence collaboration preferences, potentially reducing gender homophily in disciplines where gender parity id normalized.
+The second hypothesis tests whether departmental norms and gender dynamics affect scholars' tendency for gender homophily in their collaborations.
+
+-   ***H2:** Scholars in the sociology department exhibit weaker preferences for same-gender collaborators than those in the political science department.*
+
+## **H3: Structural Network Effects and Gender Homophily**
+
+Collaboration networks are also shaped by structural effects such as **reciprocity** (mutual collaboration), **indegree popularity** (preference for well-connected scholars), and **outdegree activity** (scholars actively seeking collaborators).
+These mechanisms reinforce broader social dynamics in scholarly networks, often amplifying existing tendencies such as gender homophily (@Snijders2010).
+For example, well-connected scholars may still attract same-gender collaborators due to persistent societal norms or unconscious biases, even as their popularity grows.
+Hence, the next hypothesis examines whether structural effects enhance collaboration patterns in scholars tie creations.
+
+-   ***H3:** Gender homophily in collaboration between scholars persists after controlling for network structure (e.g., reciprocity, degree distribution).*
+
+## **H4: The Influence of Prestige on Gender Homophily**
+
+While homophily shapes collaboration patterns, prestige can alter these dynamics by creating opportunities for **upward mobility**.
+Prestige, often measured by the Hirsch-Index (h-index), serves as a powerful signal of influence and impact in academia (@Bornmann2020).Scholars seeking career advancement may prioritize collaborations with prestigious colleagues, even if it means collaborating across gender lines(@Broido2019).
+However, as women and other nderrepresented groups gain visibility and prestige, their collaboration opportunities expand, potentially mitigating homophily effects (@Knobloch2013).
+Hence, the last hypothesis explores whether high prestige mitigates the influence of gender homophily in academic collaboration networks.
+
+-   ***H4:** Gender homophily is less influential in collaboration decisions when the potential collaborator has a higher Hirsch-Index.*
+
+------------------------------------------------------------------------
+
+# References

### 2024-11-24 modelestimate.Rmd
actualnullmodelfix
draft discussion

@@
 output: html_document
+bibliography: references.bib
+csl: apa.csl
 editor_options: 
@@
 ```
+
+Note to self. Keep in mind: \
+**meaning of significance in RSiena** "It is important to mention that
+significance in RSiena means something different than in conventional
+statistics. In normal statistics, such as OLS-regression, significance
+of estimates refers to the fact that they are not 0 (**RELEVANT?**). In
+RSiena, however, it refers to the fact that the estimates were precisely
+determined (Ripley et al. 2011). Going forward with this chapter,
+significance will refer to this definition of significance." - Niels
+Vullings
 
@@
 
-#n-degree related popularity effect (inPop) (earlier called popularity or popularity of alter effect), defined by the sum of the in-degrees of the others to whom i is tied,
+#in-degree related popularity effect (inPop) (earlier called popularity or popularity of alter effect), defined by the sum of the in-degrees of the others to whom i is tied,
 
@@
 -   if egoX significant then men's ties sign. diff. based on whether its to a man or woman (look at direction of effect to know which gender)
+
+sameX (Gender): Tests whether scholars prefer same-gender collaborators (direct measure of gender homophily).
+model the general tendency for scholars to collaborate with same-gender peers.
+
+  Confirmation:
+
+    Significant and positive coefficient for sameX in the RSiena output would confirm that gender homophily exists.
+
+    A non-significant or negative coefficient would disconfirm this hypothesis.
 
@@
 
-First, I estimate a null model with only reciprocity and degree.
-
-The maximum convergence ratio of the model is 0.084. The GOF on the
-Indegree Distribution is zero**.** This indicates that the model is a
-very bad fit for the data. This is not suprising since we ran a null
-model without any network effects.ffects.
-
-For all GOF plots compiled in one place, see here:
-<https://treesdude.github.io/labjournal/finalGOF.html>
-
-CHANGE Both reciprocity and density are significant for an alpha of
-**NUMBER**.
-
-Estimates and standard errors
-
-Rate parameters:
-
-0\. Rate parameter 2.117 ( 0.3561)
-
-Other parameters:
-
-1\. eval: outdegree (density) -2.6388 ( 0.1460) convergence t ratio:
-0.0182
-
-2\. eval: reciprocity 1.8035 ( 0.4343) convergence t ratio: -0.0668
-
-**meaning of significance in RSiena** "It is important to mention that
-significance in RSiena means something different than in conventional
-statistics. In normal statistics, such as OLS-regression, significance
-of estimates refers to the fact that they are not 0 (**RELEVANT?**). In
-RSiena, however, it refers to the fact that the estimates were precisely
-determined (Ripley et al. 2011). Going forward with this chapter,
-significance will refer to this definition of significance." - Niels
-Vullings
-
-This model has a density parameter of **NUMBER**, suggesting that
-"people generally do not want to have a dense network".
-
-The reciprocity parameter of **NUMBER** indicates that "people like to
-send ties back to people who have sent a tie to them."
+First, I estimated a null model with only reciprocity and degree. The
+maximum convergence ratio of the model is 0.084. The GOF on the Indegree
+Distribution is zero**.** This indicates that the model is a very bad
+fit for the data and estimates of this model do not give us reliable
+information. \
+*For all GOF plots compiled in one place, see here:
+<https://treesdude.github.io/labjournal/finalGOF.html>.\
+*For the sake of practise, here they are anyways:\
+The outdegree (density) effect assesses the tendency of nodes to
+establish outgoing connections, serving as a baseline for the likelihood
+that any given node will initiate an outgoing tie. In the context of
+this study, these outgoing ties represent the initiation of
+co-publications. The outdegree estimate is significant and negative (b =
+-2.6388, SE = 0.1460), suggesting that a scholar's tendency to initiate
+collaboration is low and dense networks are less sought after. The
+reciprocity parameter id significant and positive (b = 1.8035, SE =
+0.4343), which implies that directed ties are likely to be reciprocated.
+Specific to our case, it describes that scholars tend to initiate
+collaborations with those alters who sent a tie to them too.
 
@@
 fsave(Model0, file ="estimated_M0")
-
 ```
@@
 Model0
-
 ```
@@
 
-This model additionally entails InPop, outAct, isolateNet as network
-statistics.
-
-"The model has a maximum convergence ratio of **0.17** and a Goodness of
-Fit on the indegree distribution of **.002.**"
-
-"Indegree Popularity (inPop) is defined as the extent to which people
-who have a lot of indegrees are more popular to connect with. This
-parameter is NUMBER, meaning that actors have a preference to connect
-with actors who have a lot of indegrees. The parameter is significant
-for an alpha of **NUMBER**."
-
-"Outdegree Activity (outAct) has a value of **NUMBER**, but is not
-significant. IsolateNet is significant andhas a value of NUMBER and
-refers to the preference of remaining an isolate. As this value is
-positive (\*IS IT??!\*\*), it means that people prefer to be an isolate
-in the network."
-
-Estimates and standard errors
-
-Rate parameters:
-
-0\. Rate parameter 3.3566 ( 0.5773)
-
-Other parameters:
-
-1\. eval: outdegree (density) -2.0862 ( 0.7050)
-
-2\. eval: reciprocity 1.0894 ( 0.4144)
-
-3\. eval: indegree - popularity 0.2549 ( 0.0439)
-
-4\. eval: outdegree - activity -0.0936 ( 0.1301)
-
-5\. eval: network-isolate 4.9645 ( 1.1146)
-
-convergence t ratio:
-
-```         
-1
-0.0232
-```
-
-```         
-2
-0.0467
-```
-
-```         
-3
--0.0195
-```
-
-```         
-4
--0.0423
-```
-
-```         
-5
--0.061
-```
-
-```         
- -0.0617
-```
+This model additionally entails InPop, outAct, isolateNet to control for
+effects of network statistics. The maximum convergence ratio of this
+model is **0.17** and a Goodness of Fit on the indegree distribution is
+**0.002.** Estimates of this model do not fit the data well and thus do
+not give us reliable information.
+
+For the sake of practise, here they are anyways:\
+As in our null model, the parameters for outdegree (b = -2.0862, SE =
+0.7050) and reciprocity (b = 1.0894, SE = 0.4144) remain significant and
+unchanged on their 'direction'.
+
+The added parameter for indegree popularity tells us something about the
+popularity of people who have a lot of outgoing ties. In our model the
+estimate for this parameter is significantly positive (b =0.2549, SE
+=0.0439), suggesting that scholars specifically like to initiate
+collaborations with those who have a lot of indegrees.
+
+Further, the parameter for outdegree activity conveys information about
+scholars' preferences to collaborate with others who have a lot of
+outdegrees. In our case, the estimate is insignificant and cannot be
+reliably interpreted.
+
+Lastly, the network isolate parameter can be used to infer about
+scholars' tendency to neither send nor receive ties. The estimate for
+this parameter is significantly positive (b = 4.9645, SE = 1.1146) in
+our model, indicating that the scholars of our sample tend to remain
+isolates.
 
@@
 network statistics sameX, diffXTransTrip, egoX & altX of the covariate
-gender.
+gender. EgoX and AltX ought to indicate whether male or female scholars
+are more likely to initiate or receive ties, while sameX models the
+general tendency for scholars to collaborate with same-gender peers.
+
+The statistic for transitive triplets based on a different covariate
+value (here: different gender) was originally included to control for
+relationships of triadic nature (diffXTransTrip), but will be
+disregarded in the interpretation of the results since a more
+appropriate control statistic would have been that of transitive
+triplets (TransTrip), but I simply lack the time to adjust the models.
 
@@
 Other parameters:    
-1. eval outdegree (density)                 -1.8628  ( 1.1060   )    0.0703      
-2. eval reciprocity                          1.3341  ( 0.4543   )   -0.0152      
-3. eval indegree - popularity                0.2209  ( 0.0470   )   -0.0083      
-4. eval outdegree - activity                -0.3017  ( 0.2287   )    0.0806      
-5. eval network-isolate                      4.7507  ( 1.5194   )   -0.0379      
-6. eval gender_RS alter                      0.3254  ( 0.2701   )    0.0411      
-7. eval gender_RS ego                       -1.0642  ( 0.6055   )   -0.0400      
-8. eval same gender_RS                       0.6637  ( 0.2685   )    0.0308      
-9. eval transitive triplets diff. gender_RS  2.1787  ( 0.6027   )    0.0416   
+1. eval outdegree (density)                 -1.8628  ( 1.1060   )    0.0703 --> insign. (-1.684268)    
+2. eval reciprocity                          1.3341  ( 0.4543   )   -0.0152 --> sign.    (2.936606)***     
+3. eval indegree - popularity                0.2209  ( 0.0470   )   -0.0083 --> sign.    (4.7)     ***
+4. eval outdegree - activity                -0.3017  ( 0.2287   )    0.0806 --> insign. (-1.319195)    
+5. eval network-isolate                      4.7507  ( 1.5194   )   -0.0379 --> sign.    (3.126695)***
+
+6. eval gender_RS alter                      0.3254  ( 0.2701   )    0.0411 --> insign.  (1.204739)      
+7. eval gender_RS ego                       -1.0642  ( 0.6055   )   -0.0400 --> insign. (-1.757556)     
+8. eval same gender_RS                       0.6637  ( 0.2685   )    0.0308 --> sign.    (2.471881)***     
+9. eval transitive triplets diff. gender_RS  2.1787  ( 0.6027   )    0.0416 --> sign.    (3.6149)  ***
 ```
@@
 
-**CHANGE!!**
-
-"For the structural network statistics we find similar results, in terms
-of estimate size and significance, as in Model 1. However, the outdegree
-activity parameter almost reaches significance (**-1.7135484**).
-
-With regard to the covariate network statistics, we find that the gender
-of ego (egoX), the gender of alter (altX) **are not significant and thus
-the estimate cannot be trusted**."
-
-egoX and altX: model whether male or female scholars are more likely to
-initiate or receive ties.
-
-**sameX (Gender)**: Tests whether scholars prefer same-gender
-collaborators (direct measure of gender homophily).\
-model the general tendency for scholars to collaborate with same-gender
-peers.
-
-**Confirmation**:
-
--   Significant and positive coefficient for `sameX` in the RSiena
-    output would confirm that gender homophily exists.
-
--   A non-significant or negative coefficient would disconfirm this
-    hypothesis.
-
-**Confirmation**:
-
--   Significant and positive coefficient for `sameX` in the RSiena
-    output would confirm that gender homophily exists.
-
--   A non-significant or negative coefficient would disconfirm this
-    hypothesis.
+Looking at our 'base-line' network statistics, it bears noting that the
+estimate for Outdegree is not significant anymore. This statistic's
+prior significance can seemingly be explained by a parameter relating to
+the covariate gender that I added to this model. However, the estimate
+of the outdegree parameter is still nearing the significance 'threshold'
+(b = -1.8628, SE = 1.1060, b/SE = -1.684268).
+
+Comparing this model to the prior ones, we see that the reciprocity
+estimate is still significantly positive (b = 1.3341, SE = 0.4543).
+
+The parameters of the structural network statistics also show similar
+patterns in estimates and significance as they did in model 1.
+
+Concerning the added covariate "gender", we find that the parameter
+estimates for both covariate-related activity (egoX) , pertaining to the
+gender of the ego, and covariate-related popularity (altX), relating to
+the gender of the alter, do **not** show any significance and hence do
+not allow for reliable inferences.
+
+The 'same-covariate' measure (sameX) for gender is significantly
+positive (b = 0.6637, SE =0.2685). It reveals that scholars, indeed,
+prefer same-gender collaborators. This supports H1, which posits gender
+homophily in collaboration patterns.
+
+Model 2 provides strong evidence for gender homophily (H1), with
+scholars more likely to collaborate with same-gender peers, but no
+significant differences in collaboration tendencies based on the gender
+of ego or alter.
 
@@
         clustering.
+
+--\> unsure if this hpold true for me, since I added gender only after
+running a model that controls for structural effects so I cannot really
+infer that but it'S too late to change that now.
 
@@
 network statistics egoX and altX for the main effect of department, to
-control for differences in collaboration patterns between the two
-departments.
+investigate differences in same-gender collaboration patterns based on
+the two departments.
+
+Originally, I planned to also include an interaction term of departm_RS
+and gender_RS to obtain clearer insights into variations in patterns of
+gender homophily in relation to scholars' departments. However, I have
+refrained from adding another model to this project. I decided against
+this partly due to time constraints but I also reason that I can use the
+comparison of model 2 and 3 to examine changes in the estimate of
+'sameX' (gender), to *tentatively* infer whether the department of
+scholars modifies the collaboration patterns at hand.
 
@@
 
-**CHANGE** !!!!
-
-For the structural network statistics we find similar results, in terms
-of estimate size and significance, as in Model 1. However, the outdegree
-activity parameter almost reaches significance (**-1.7135484**).
-
-With regard to the covariate network statistics, we find that the gender
-of ego (egoX), the gender of alter (altX) **are not significant and thus
-the estimate cannot be trusted**."
-
-Estimates and standard errors
-
-Rate parameters:
-
-0\. Rate parameter 3.1013 ( 0.5186)
-
-Other parameters:
-
-1\. eval: outdegree (density) -4.3233 ( 1.0871)
-
-2\. eval: reciprocity 1.0725 ( 0.4174)
-
-3\. eval: indegree - popularity 0.2122 ( 0.0517)
-
-4\. eval: outdegree - activity -0.3364 ( 0.2182)
-
-5\. eval: network-isolate 4.2006 ( 1.3007)
-
-6\. eval: gender_RS alter 0.3356 ( 0.2659)
-
-7\. eval: gender_RS ego -1.0066 ( 0.5121)
-
-8\. eval: same gender_RS 0.6632 ( 0.2623)
-
-9\. eval: transitive triplets diff. gender_RS 1.5479 ( 0.5403)
-
-10\. eval: departm_RS alter 0.4141 ( 0.7546)
-
-11\. eval: departm_RS ego -1.1573 ( 0.9148)
-
-12\. eval: same departm_RS 2.7240 ( 0.7277)
+Interestingly, the estimate for outdegree (density) that had lost its
+significance in model 2, is now back to being significant and negative
+(b = -4.3233, SE = 1.0871).
+
+In terms of estimate size and significance of the structural network
+statistics we, once again, find similar patterns as in models 1 and 2.
+However, the outdegree parameter has now reached significance (b =
+-4.3233, SE = 1.0871).
+
+With regard to the network statistics of the covariate 'gender', we find
+that the estimates relating to the gender of an ego (egoX) and the
+gender of an alter (altX) remain non-significant. The parameter
+estimates for sameX remains significantly positive (b = 0.6632, SE =
+0.2623) and are almost identical to those of model 2 (b = 0.6632, SE =
+0.2623). This suggests that adding the covariate 'department' did not
+bring about any noteworthy changes in patterns of scholars seeking out
+same-gendered scholars to collaborate.
+
+When it comes to the parameters pertaining to the added covariate
+'department', we find that any differences in collaboration based on the
+department of an ego (egoX) or of an alter (altX) are not warranted, as
+the estimates of these parameters are insignificant. However, we find a
+significantly positive estimate for the parameter of 'covariate-related
+identity' (sameX), which indicates that scholars are more likely to
+collaborate with people from their own department, indicating
+**department-based homophily**. (b = 2.7240, SE = 0.7277).
+
+Model 3 highlights persistent gender homophily (H1) across departments
+but does not provide evidence for differences in gender homophily
+between Sociology and Political Science, contrary to H2.
+
+------------------------------------------------------
+
+Estimates and SEs model 3:
+
+1\. eval: outdegree (density) -4.3233 ( 1.0871) \*\*\*
+
+2\. eval: reciprocity 1.0725 ( 0.4174) \*\*\*
+
+3\. eval: indegree - popularity 0.2122 ( 0.0517) \*\*\*
+
+4\. eval: outdegree - activity -0.3364 ( 0.2182) insign. (-1.541705)
+
+5\. eval: network-isolate 4.2006 ( 1.3007) \*\*\*
+
+6\. eval: gender_RS alter 0.3356 ( 0.2659) insign (1.262129)
+
+7\. eval: gender_RS ego -1.0066 ( 0.5121) insign (-1.965632) almost
+significant
+
+8\. eval: same gender_RS 0.6632 ( 0.2623) sign. (2.52840) \*\*\* \
+(sameX: comparison model 2 and 3:\
+estimate got hardly any smaller (0.6637--\>0.6632), SE got hardly any
+smaller (0.2685--\>0.2623), significance value got bigger
+(2.47881--\>2.52840))
+
+9\. eval: tr. tripl. diff. gend. 1.5479 ( 0.5403) sign. (2.86489)
+\*\*\*\
+(diffxTrTrip comparison model 2 and 3:\
+estimate got smaller and NEGATIVE (2.1787 –\>-1.5479), SE got smaller
+(0.6027 –\> 0.5403), significance value got smaller (3.6149--\>2.86489))
+
+10\. eval: departm_RS alter 0.4141 ( 0.7546) insign. (0.549)
+
+11\. eval: departm_RS ego -1.1573 ( 0.9148) insign (-1.27)
+
+12\. eval: same departm_RS 2.7240 ( 0.7277) \*\*\*
 
@@
         hypothesis.
+
+altX - egos send more ties who have more on gender (aka. gender =1)
+(iiiish look at egoX explanantion, this is basically the same but in
+"reverse", aka about receiving rather than sending)
+
+-   covariate-alter or covariate-related popularity (altX), defined by
+    the sum of the covariate over all actors to whom ***i*** has a tie,
+-   same as egoX but RECEIVING ties
+
+egoX - [definition?]
+
+-   covariate-ego or covariate-related activity (egoX), defined by i’s
+    out-degree weighted by his covariate value,
+-   since male = 1 egoX only "looks at" men's ties
+-   if egoX significant then men's ties sign. diff. based on whether its
+    to a man or woman (look at direction of effect to know which gender)
 
@@
 
-This model further builds on the prior model and also includes the
-network statistics of the covariat H-index, namely **egoX, altX and
-inPopX**.
-
-"The last model has a maximum convergence ratio of **0.23** and a a
-Goodness of Fit on the indegree distribution of **0.197**.
-
-**CHANGE!!!**
-
-"In this model, the parameters for density and reciprocity are still
-significant, with values of **-1.98** (se = **0.71**) and **2.59** (se =
-**0.38**) respectively, meaning that actors prefer sparse networks, but
-do prefer to send ties to alters who have sent ties to them.
-
-IsolateNet is still significant with a value of **3.23** (se =
-**1.06**), implying that actors prefer to be isolates.
-
-In this model, **indegree popularity squared** (b = **0.17**, se =
-**0.21**) is no longer significant, implying that this might be
-explained by other network statistics in the model.
-
-The covariate statistics for gender show similar findings as Model 2,
-namely that actors prefer to close triads with alters that have a
-different score for gender (b = **1.51**, se = **0.44**).
-
-The ego effect and alter effect for gender are **non-significant**, as
-was the case in Model 2.
-
-Lastly, Model 3 shows some significant results with regards to the
-covariate network statistics for prestige. The prestige effect for
-alters is positive, implying that people prefer to send ties to people
-who have a higher amount of prestige (b = **0.042**, se = **0.0089**).
-
-Additionally, the prestige effect for egos is negative, which indicates
-that people who have higher prestige send less ties (b = **-0.030**, se
-= **0.015**). **This is in line with theories of preferential attachment
-and upward mobility, because as egos with higher prestige will are more
-likely to receive request for collaboration rather then sending request
-for collaboration.**
-
-Interestingly enough, the indegree popularity statistic for prestige is
-not significant (b = **-0.012**, se = **0.023**), implying that actors
-who are more prestigious do not receive more indegrees."
-
-About Hypothesis 4
-
-modeling how the department of the actor (Sociology or Political
-Science) influences their collaboration choices in terms of gender.
-
-**Interaction1 = "departm_RS"**: This allows you to test how department
-(Sociology vs Political Science) influences the probability of forming
-collaborations, potentially differing by gender. This means that gender
-homophily (whether a person collaborates more often with same-gender
-peers) might be different in the two departments.
-
-allows you to explore how **department** influences the likelihood of
-**same-gender** collaborations (`sameX`), which is central to your
-research question. If the **department variable** is acting as an
-important covariate influencing collaboration patterns, this line
-captures that effect.
-
-testing how being in a particular department influences the likelihood
-of collaborating with someone of the same gender. In other words, it
-checks if the department modifies the strength of gender homophily
-(`sameX`).
-
-**Network Statistics**:
-
--   **egoX (h-index)**: Examines how the h-index of the focal scholar
-    affects their collaboration behavior.
-
--   **altX (h-index)**: Examines how the h-index of potential
-    collaborators affects their attractiveness as partners.
-
-    Add `egoX` and `altX` effects for `HIndex_RS` to test if prestigious
-    scholars are more likely to initiate or receive ties.
-
--   **inPopX (h-index)**: Assesses whether prestige increases the
-    likelihood of being sought out as a collaborator.
-
-**Confirmation**:
-
--   A significant negative interaction term between `sameX` and h-index
-    statistics would confirm that prestige reduces the strength of
-    gender homophily.
-
--   If h-index variables do not significantly influence `sameX`, this
-    would disconfirm H3.
+This model further builds on the prior model and also includes network
+statistics of the covariate H-Index, namely egoX, altX and inPopX. By
+adding these effects we can model how the h-index of a scholar
+influences their preferences regarding same-gendered collaborations.
+Similarly, to model 3, this model could have profited from a 'follow-up'
+model that includes and interaction term between h-index and gender to
+better infer about their influences. The same reasoning for my decision
+to stick with one model prior also applies to this case. EgoX for this
+covariate examines how the h-index of a scholar affects their
+collaboration behavior, while AltX examines how the h-index of potential
+collaborators affects their attractiveness as partners. With the help of
+these effects we can test prestigious scholars are more likely to
+initiate or receive ties. By looking at in-degree popularity weighted by
+sender’s H-index (inPopXi) we can assesse whether a high h-index
+increases the likelihood of being sought out as a collaborator.\
+
+```         
+Estimates, standard errors and convergence t-ratios
+                                               Estimate   Standard   Convergence
+                                                          Error      t-ratio
+Rate parameters:  
+  0      Rate parameter                       2.6891  ( 0.3675   )
+
+Other parameters:     
+   1. eval outdegree (density)                 -2.7693  ( 1.9205   )    0.0698 --> insign. (-1.441968)       
+   2. eval reciprocity                          2.1770  ( 0.5960   )    0.0919 --> sign.    (3.652685)***      
+   3. eval indegree - popularity               -0.0653  ( 0.1654   )   -0.0104 --> insign. (-0.3948005)      
+   4. eval outdegree - activity                -0.6851  ( 0.4029   )    0.0527 --> insign. (-1.700422)      
+   5. eval network-isolate                      5.4634  ( 2.2770   )    0.0028 --> sign.    (2.399385)***      
+   6. eval gender_RS alter                     -0.0903  ( 0.3372   )    0.0129 --> insign. (-0.2677936)       
+   7. eval gender_RS ego                        0.2993  ( 0.4934   )   -0.0503 --> insign. (0.6066072)      
+   8. eval same gender_RS                       0.6820  ( 0.2804   )    0.0201 --> sign.   (2.43224)  ***       
+   9. eval transitive triplets diff. gender_RS  2.4871  ( 0.6670   )    0.0505 --> sign.   (3.728786) ***    
+  10. eval departm_RS alter                     0.3929  ( 0.6128   )   -0.0061 --> insign. (0.6411554)    
+  11. eval departm_RS ego                      -1.4652  ( 0.6963   )   -0.0115 --> SIGN.   (-2.104265)***
+  12. eval same departm_RS                      2.6327  ( 0.6080   )    0.0173 --> sign    (4.330099) ***    
+  13. eval h_index_RS alter                     0.0829  ( 0.0364   )   -0.0031 --> SIGN    (2.277473) ***
+  14. eval h_index_RS ego                      -0.1591  ( 0.0744   )    0.0161 --> SIGN.  (-2.138441) ***   
+  15. eval ind. pop.^(1/1) weighted h_index_RS -0.0287  ( 0.0570   )   -0.0129 --> insign.(-0.5035088)
+```
+
+Model 4 has a maximum convergence ratio of **0.23,** and a a Goodness of
+Fit on the indegree distribution of **0.197**.
+
+Structural network statistics:
+
+The estimate for outdegree is negative but not significant. This
+suggests that, after accounting for other variables, the baseline
+likelihood of forming ties remains low and is not a major driver of
+collaboration patterns. Reciprocity has a significant positive estimate
+(b = 2.1770, SE = 0.5960). This reflects a strong tendency for mutual
+collaborations, meaning if one scholar collaborates with another, the
+latter is likely to collaborate back (dyadic reciprocity). The paramters
+Indegree Popularity and Outdegree Activity are both insignificant,
+suggesting that neither the tendency to receive many collaborations
+(indegree popularity) nor the tendency to initiate them (outdegree
+activity) is significantly relevant to the network structure. The
+network isolate estimate is, once again, significantly positive ( b =
+5.4634, SE = 2.2770), indicating that as isolates tend to remain
+isolated.
+
+Gender:
+
+Similar to AltX and EgoX in prior models, both an alter's gender (b =
+-0.0903, SE = 0.3372) and an ego's gender (b = 0.2993, SE = 0.4934)
+still have insignificant effects. The parameter SameX shows a
+significant positive estimate (b = 0.6820, SE = 0.2804) which barely
+differs from the two prior models. This suggests that adding the
+covariate 'H-Index' did not prompt any major changes in scholars'
+preferences for same-gendered collaborators.
+
+Department:
+
+While an alter's departmen**t** (AltX) remained insignificant to the
+collaboration patterns, the estimates for an ego's department changed
+incomparison to the prior model. In this model, egoX seems to be of
+significant relevance (b = -1.4652, SE = 0.6963), with its negative
+estimate indicating that, once effects of h-index are controlled for,
+scholars from the political science (coded as 1) department have a lower
+tendency to initiate collaborations than scholars from the sociology
+department (coded as 0). \
+Similar to the prior model, the sameX parameter for department shows a
+significant positive estimate (b = 2.6327, SE = 0.6080) scholars are
+still more likely to collaborate with others from the same department.
+
+H-Index:
+
+Both an alter's and an ego's H-Index seem to be relevant in
+collaboration preferences. The significant and positive estimateof AltX
+(b = 0.0829, SE = 0.0364) suggest that scholars with higher h-index are
+more preferred as collaborators. The egoX estimate is significant and
+negative (b = -0.1591, SE = 0.0744) suggesting that scholars with higher
+h-index are less likely to initiate collaborations.
+
+*Discussion part about egoX h.index: **"This is in line with theories of
+preferential attachment and upward mobility, because as egos with higher
+prestige will are more likely to receive request for collaboration
+rather then sending request for collaboration." - Niels***
+
+The estimate for the Indegree Popularity weighted by h-index is
+insignificant, suggesting that high-prestige individuals (as measured by
+their h-index) do not significantly receive more indegrees
+
+The results partially support **H4**, as the h-index is shown to
+influence collaboration patterns, with prestigious scholars being more
+likely to attract collaborations as alters but less likely to initiate
+them as egos. However, gender homophily remains significant even after
+controlling for the h-index, suggesting that prestige does not
+substantially weaken the influence of gender homophily in co-authorship
+networks.
+
+Transitive Triplets (Diff Gender): A positive significant effect
+(b=2.4871, SE = 0.6670). This suggests that transitive structures (where
+two people connected to a common third party collaborate) are more
+likely even across gender differences. Could be a potential
+counterbalance to homophily.
+
+R-Manual: in-degree popularity weighted by sender’s V (inPopX)
+defined by the sum of values of V for actors h for which there are ties
+i → j ← h
+
+note that to use this effect for p = 2 the variable V must be
+nonnegative, which
+implies that it must be non-centered;
+further note that if V is a behavioral variable, it will be used in the
+centered version,
+so that p must be 1; if weighting by a non-centered behavioral variable
+is desired, a
+new effect is necessary;
 

### 2024-11-25 descriptivestry.Rmd
draft discussion
restructuring data with ego descriptives

@@
 ---
-title: "Descriptive adventures"
+title: "draft Descriptive Data"
 author: "Verooo"
@@
 output: html_document
+bibliography: references.bib
+csl: apa.csl
 ---
+
+```{=html}
+<style>
+body {
+text-align: left;
+line-height: 1.5;
+}
+
+h1, .h1, h2, .h2, h3, .h3 {
+  margin-top: 24px;
+  line-height: 1;
+}
+
+</style>
+```
 
@@
 </html>
+<!-- now part of data & Analysis part: ego level description of data -->
 
@@
 knitr::opts_chunk$set(echo = TRUE)
-
 ```
@@
 
-```{r clean}
+```{r clean, results='hide'}
 rm(list = ls())
@@
 
-```{r package, hide=TRUE}
+```{r package, hide=TRUE, results='hide'}
 require(tidyverse)
@@
 
-```{r functions 1, hide =TRUE}
+```{r functions 1, hide =TRUE, results='hide'}
 fpackage.check <- function(packages) {
@@
 
-```{r functions 2, hide=TRUE}
+```{r functions 2, hide=TRUE, results='hide'}
 fcolnet <- function(data = scholars, university = "RU", discipline = "sociology"+"political science", waves = list(c(2015,
@@
 
-# Descriptives - Demographics 
-The following graphs represent the segregation of the network based on gender and on H-index for the wave of interest (2015-2018).
+### Gender - Ego level
 
-## Ego level
-
-### Gender
-
-descriptives (mean etc.) in whole sample
+Descriptives (mean, distibution, etc.) in whole sample
 
@@
 
-### h index
+### H index - Ego level
 
-descriptives (mean etc.)
+Descriptives (mean, distribution, etc.)
 
@@
 
-Overall(2015-2018)
+H-Index Whole sample
 

### 2024-11-25 draft1desresults.Rmd
draft discussion
restructuring data with ego descriptives

@@
 ---
-title: "Draft Result Descriptives"
+title: "Draft Descriptives try "
 author: "Verooo"
@@
 </html>
+
+```{=html}
+<style>
+body {
+text-align: left;
+line-height: 1.5;
+}
+
+h1, .h1, h2, .h2, h3, .h3 {
+  margin-top: 24px;
+  line-height: 1;
+}
+
+</style>
+```
 

### 2024-11-25 draftGOF.Rmd
restructuring data with ego descriptives

@@
 
-<html lang="en">
+```{=html}
+<style>
+body {
+text-align: left;
+line-height: 1.5;
+}
 
-<head>
+h1, .h1, h2, .h2, h3, .h3 {
+  margin-top: 24px;
+  line-height: 1;
+}
 
-<meta charset="UTF-8">
-
-<meta name="viewport" content="width=device-width, initial-scale=1.0">
-
-<title>GOF</title>
-
-<link rel="stylesheet" href="styles.css"> <!-- Link to the CSS file I created for dark mode code chunks -->
-
-</head>
-
-</html>
+</style>
+```
 
@@
 The use of the specific GOF measure of a model's Indegree Distribution seems most appropriate since the study's focus lies on changes in directed ties between schoalrs.
-A GOF with a p-value below .05 indicates a poor fit and calls for adjustment of the model, while a p-value above .05 usually indicates an acceptable or good fit.
-\
+A GOF with a p-value below .05 indicates a poor fit and calls for adjustment of the model, while a p-value above .05 usually indicates an acceptable or good fit.\
 The GOF measures of Indegree Distribution for the null model (*p* = .008) and model 1 *(p* = .002) both display p-values below .05.
@@
 
-```{=html}
 <!--  M0: 0.008  M1: 0.002  M2: 0.096  M3: 0.12  M4: 0.197  -->
-```
+
 # Model 0

### 2024-11-25 draftdata.Rmd
restructuring data with ego descriptives

@@
 
+## Getting started
+
+```{r clean, results='hide', hide =TRUE}
+rm(list = ls())
+```
+
+### Packages
+
+```{r package, hide=TRUE, results='hide'}
+require(tidyverse)
+require(RSiena)
+require(RsienaTwoStep)
+
+#install.packages("data.table")
+require(data.table)  # mainly for faster data handling
+# install.packages('xml2')
+require(xml2)
+# install.packages('rvest')
+require(rvest)
+require(igraph)
+require(ggraph)
+require(ggplot2)
+
+#install.packages('visNetwork')
+require(visNetwork)
+#install.packages('threejs')
+require(threejs)
+#install.packages('networkD3')
+require(networkD3)
+
+require(RColorBrewer)
+
+```
+
+### Functions
+
+```{r functions 1, hide =TRUE, results='hide'}
+fpackage.check <- function(packages) {
+    lapply(packages, FUN = function(x) {
+        if (!require(x, character.only = TRUE)) {
+            install.packages(x, dependencies = TRUE)
+            library(x, character.only = TRUE)
+        }
+    })
+}
+
+fsave <- function(x, file = NULL, location = "./data/processed/") {
+    ifelse(!dir.exists("data"), dir.create("data"), FALSE)
+    ifelse(!dir.exists("data/processed"), dir.create("data/processed"), FALSE)
+    if (is.null(file))
+        file = deparse(substitute(x))
+    datename <- substr(gsub("[:-]", "", Sys.time()), 1, 8)
+    totalname <- paste(location, file, "_", datename, ".rda", sep = "")
+    save(x, file = totalname)  #need to fix if file is reloaded as input name, not as x. 
+}
+
+fload <- function(filename) {
+    load(filename)
+    get(ls()[ls() != "filename"])
+}
+
+fshowdf <- function(x, ...) {
+    knitr::kable(x, digits = 2, "html", ...) %>%
+        kableExtra::kable_styling(bootstrap_options = c("striped", "hover")) %>%
+        kableExtra::scroll_box(width = "100%", height = "300px")
+}
+
+# this is the most important one. We created it in the previous script
+
+f_pubnets <- function(df_scholars = df, list_publications = publications, discip = "sociology"+"political science", affiliation = "RU",
+    waves = list(wave1 = c(2018, 2019, 2020), wave2 = c(2021, 2022, 2023))) {
+
+    publications <- list_publications %>%
+        bind_rows() %>%
+        distinct(title, .keep_all = TRUE)
+
+    df_scholars %>%
+        filter(affil1 == affiliation | affil2 == affiliation) %>%
+        filter(discipline == discip) -> df_sel
+
+    networklist <- list()
+    for (wave in 1:length(waves)) {
+        networklist[[wave]] <- matrix(0, nrow = nrow(df_sel), ncol = nrow(df_sel))
+    }
+
+    publicationlist <- list()
+    for (wave in 1:length(waves)) {
+        publicationlist[[wave]] <- publications %>%
+            filter(gs_id %in% df_sel$gs_id) %>%
+            filter(year %in% waves[[wave]]) %>%
+            select(author) %>%
+            lapply(str_split, pattern = ",")
+    }
+
+    publicationlist2 <- list()
+    for (wave in 1:length(waves)) {
+        publicationlist2[[wave]] <- publicationlist[[wave]]$author %>%
+            # lowercase
+        lapply(tolower) %>%
+            # Removing diacritics
+        lapply(stri_trans_general, id = "latin-ascii") %>%
+            # only last name
+        lapply(word, start = -1, sep = " ") %>%
+            # only last last name
+        lapply(word, start = -1, sep = "-")
+    }
+
+    for (wave in 1:length(waves)) {
+        # let us remove all publications with only one author
+        remove <- which(sapply(publicationlist2[[wave]], FUN = function(x) length(x) == 1) == TRUE)
+        publicationlist2[[wave]] <- publicationlist2[[wave]][-remove]
+    }
+
+    for (wave in 1:length(waves)) {
+        pubs <- publicationlist2[[wave]]
+        for (ego in 1:nrow(df_sel)) {
+            # which ego?
+            lastname_ego <- df_sel$lastname[ego]
+            # for all publications
+            for (pub in 1:length(pubs)) {
+                # only continue if ego is author of pub
+                if (lastname_ego %in% pubs[[pub]]) {
+                  aut_pot <- which.max(pubs[[pub]] %in% lastname_ego)
+                  # only continue if ego is first author of pub
+                  if (aut_pot == 1) {
+                    # check all alters/co-authors
+                    for (alter in 1:nrow(df_sel)) {
+                      # which alter
+                      lastname_alter <- df_sel$lastname[alter]
+                      if (lastname_alter %in% pubs[[pub]]) {
+                        networklist[[wave]][ego, alter] <- networklist[[wave]][ego, alter] + 1
+                      }
+                    }
+                  }
+                }
+            }
+        }
+    }
+    return(list(df = df_sel, network = networklist))
+}
+
+```
+
+```{r functions 2, hide=TRUE, results='hide'}
+fcolnet <- function(data = scholars, university = "RU", discipline = "sociology"+"political science", waves = list(c(2015,
+    2018), c(2019, 2023)), type = c("first")) {
+
+    # step 1
+    demographics <- do.call(rbind.data.frame, data$demographics)
+    demographics <- demographics %>%
+        mutate(Universiteit1.22 = replace(Universiteit1.22, is.na(Universiteit1.22), ""), Universiteit2.22 = replace(Universiteit2.22,
+            is.na(Universiteit2.22), ""), Universiteit1.24 = replace(Universiteit1.24, is.na(Universiteit1.24),
+            ""), Universiteit2.24 = replace(Universiteit2.24, is.na(Universiteit2.24), ""), discipline.22 = replace(discipline.22,
+            is.na(discipline.22), ""), discipline.24 = replace(discipline.24, is.na(discipline.24), ""))
+
+    sample <- which((demographics$Universiteit1.22 %in% university | demographics$Universiteit2.22 %in%
+        university | demographics$Universiteit1.24 %in% university | demographics$Universiteit2.24 %in%
+        university) & (demographics$discipline.22 %in% discipline | demographics$discipline.24 %in% discipline))
+
+    demographics_soc <- demographics[sample, ]
+    scholars_sel <- lapply(scholars, "[", sample)
+
+    # step 2
+    ids <- demographics_soc$au_id
+    nwaves <- length(waves)
+    nets <- array(0, dim = c(nwaves, length(ids), length(ids)), dimnames = list(wave = 1:nwaves, ids,
+        ids))
+    dimnames(nets)
+
+    # step 3
+    df_works <- tibble(works_id = unlist(lapply(scholars_sel$work, function(l) l$id)), works_author = unlist(lapply(scholars_sel$work,
+        function(l) l$author), recursive = FALSE), works_year = unlist(lapply(scholars_sel$work, function(l) l$publication_year),
+        recursive = FALSE))
+
+    df_works <- df_works[!duplicated(df_works), ]
+
+    # step 4
+    if (type == "first") {
+        for (j in 1:nwaves) {
+            df_works_w <- df_works[df_works$works_year >= waves[[j]][1] & df_works$works_year <= waves[[j]][2],
+                ]
+            for (i in 1:nrow(df_works_w)) {
+                ego <- df_works_w$works_author[i][[1]]$au_id[1]
+                alters <- df_works_w$works_author[i][[1]]$au_id[-1]
+                if (sum(ids %in% ego) > 0 & sum(ids %in% alters) > 0) {
+                  nets[j, which(ids %in% ego), which(ids %in% alters)] <- 1
+                }
+            }
+        }
+    }
+
+    if (type == "last") {
+        for (j in 1:nwaves) {
+            df_works_w <- df_works[df_works$works_year >= waves[[j]][1] & df_works$works_year <= waves[[j]][2],
+                ]
+            for (i in 1:nrow(df_works_w)) {
+                ego <- rev(df_works_w$works_author[i][[1]]$au_id)[1]
+                alters <- rev(df_works_w$works_author[i][[1]]$au_id)[-1]
+                if (sum(ids %in% ego) > 0 & sum(ids %in% alters) > 0) {
+                  nets[j, which(ids %in% ego), which(ids %in% alters)] <- 1
+                }
+            }
+        }
+    }
+
+    if (type == "all") {
+        for (j in 1:nwaves) {
+            df_works_w <- df_works[df_works$works_year >= waves[[j]][1] & df_works$works_year <= waves[[j]][2],
+                ]
+            for (i in 1:nrow(df_works_w)) {
+                egos <- df_works_w$works_author[i][[1]]$au_id
+                if (sum(ids %in% egos) > 0) {
+                  nets[j, which(ids %in% egos), which(ids %in% egos)] <- 1
+                }
+            }
+        }
+    }
+    output <- list()
+    output$data <- scholars_sel
+    output$nets <- nets
+    return(output)
+}
+```
+
 # Data
@@
 The coordinator of this course, Jochem Tolsma, has provided a dataset with said information to be used in this project (**source sunbelt?** ).
-OpenAlex was used to scrape all published works, including important work-related information such as work id, concepts, citations, abstracts, and subjects, up until 2024 (@Priem2022).
-From this data, I created a final dataset (n=101) that included all authors from the Sociology and Political Science departments at Radboud University within the time frame of **[INSERT TIME FRAME]**.
-
--   [**timeframe of focus**]{.underline}
+'OpenAlex' was used to scrape all published works, including important work-related information such as work id, concepts, citations, abstracts, and subjects, up until 2024 (@Priem2022).
+From this data, I created a final dataset (n=101) that included all authors from the Sociology and Political Science departments at Radboud University within the time frame of 2015 to 2018.
+I also included a second wave of data, pertainning to 2019-2024, which is purely included for the sake of running the simulations needed to analyse the data, while the focus remained on the first wave (2015-2018) only.
+Based on this data collaboration networks were constructed to capture whether two scholars in the sample had collaborated on a publication during a given wave.
 
@@
 The dependent variable in this dataset, indicated by the ties between scholars, refers to academic collaborations between them and are often called co-authorships.
-The data was scraped from OpenAlex API using the rvest and xml2 packages in R ( @Priem2022, @xml2**,** @rvest).
+The data was scraped from OpenAlex API using the rvest and xml2 packages in R ( @Priem2022, @xml2, @rvest).
 The dependent variable, represented by an *adjacency matrix*, shows whether two actors or writers collaborated on one of their publications in the specified wave.\
@@
 
--   ***In this study, ties are described as directional*** **[ARE THEY??]** which implies that they are delivered by one actor and received by another.
+**I**n the collboartion networks analysed in this study, ties are described as directional, which implies that they are delivered by one actor and received by another.
 This means each actor has both outdegrees and indegrees.
-Outdegrees refer to 'sent' connections that refer to being the first author of a manuscript.
+Outdegrees refer to 'sent' connections that refer to being the first author of a publication.
 Indegrees, or 'received' connections, imply collaboration on an article without being the 'initial' author.
-The generated adjacency matrix can take the form of a network, indicating the collaboration patterns of the academics at Radboud University between **YEAR AND YEAR**.
+The generated adjacency matrix is thus holds a network, indicating the collaboration patterns of the academics at Radboud University between 2015-2018.
 
@@
 If the website indicated that a name was used my more males than females, the scholar with that name was considered be male, and vice versa (female/male: 0/1).
+In cases the website did not suggest a majority for, the name was manually assigned a gender by the person who coded the data, based on limited online research (aka I did a quick Google search) on the name in question.
 
-For the sake of simplicity, gender in this study was inferred from scholars’ names and treated as binary, conflating gender identity with biological sex.
+For the sake of simplicity, scholars' gender in this study was inferred from scholars’ names and treated as binary, which conflates the concepts of gender identity with biological sex.
 I acknowledge that names do not reliably indicate a person's gender identity and that gender encompasses more than the categories of men and women.
 Additionally, I recognize that while *men* and *women* typically refer to gender identities, *male* and *female* are often used to denote biological sex.
-These distinctions were not upheld in this study, which conflates the terms and disregards individuals' self-identified genders.
-This approach was taken solely due to the constraints of a university assignment and does not reflect my standard research practices, which would respect and account for the complexity of gender and self-identification outside the academic coursework context.
+These distinctions were not upheld throughout the documentation of this study, which conflates the terms and disregards individuals' self-identified genders.
+This approach was taken solely due to the constraints of this being a university assignment and does not reflect my standard research practices, which would try to respect and account for the complexity of gender and self-identification outside this coursework context.
 
@@
 
-# Methods
+## Ethical concerns
 
-To evaluate the homophiliy in collaboration networks by gender and h-index, the analysis of the data will be as follows.
-The first step involves examining descriptives of the data to answer question of how homophily manifests in terms of degree and prestige within these networks.
-These descriptive findings will then serve as a foundation for the second phase of the analysis, which focuses on answering the explanatory research question of this study.
-This phase investigates the impact of homophily on collaboration and explores the interaction between gender and h-index.
-Descriptive analyses will utilize functions of the igraph and ggraph packages and t-tests, while the explanatory questions will be examined using Stochastic Actor-Based Models implemented via the RSiena package (@igraph, @ggraph, @RSiena_package, @RSiena_manual).
-
-## Descriptives
-
-**[Revisit and only talk about those that make sense to examine here]**
-
-First, ego-level descriptives such as the counts and distributions of gender and h-indices in both departments were generated to establish a clearer picture of the data at hand.
-
-I also examined descriptives of the ego network and of the whole network of scholars included in the data.
-Among others, these included the number of nodes, edges, reciprocity, degreee centrality, clustering, density, and path-length.
-With the help of these decriptives it was possible for me to......
-**[INSERT INSIGHT FROM DESCRIPTIVES HERE]**
-
-\
-**[UNSURE IF THIS IS NEEDED IF GENDER IS FIRST COVARIATE AND H INDEX ONLY CONTRL VARIABLE]**\
-Then, the networks were visualized using graphs to identify the presence of hubs and examine whether these hubs are concentrated among individuals with the highest h-index.
-Various centrality measures were also calculated and analyzed to determine their correlation with the scholars' h-index, providing further insight into whether network hubs tend to form around those with the highest h-index.
-
-## RSiena
-
-SIENA, which stands for *Simulation Investigation for Empirical Network Analysis*, is a software tool designed to perform statistical estimation of models for longitudinal social network data.
-SIENA version 4.0, also known as RSiena, is a package for the R statistical software and was developed by Ruth Ripley and Krists Boitmanis, in collaboration with Tom Snijders (@RSiena_package, @RSiena_manual).
-The use of RSiena for this project is highly based on the book "[Social Network Analysis for Social Scientists](https://jochemtolsma.github.io/SNA-4-Social-Scientists/)**"** by Jochem Tolsma and Bas Hofstra (@SNASS).
-
-# Ethical concerns
-
-## Webscraping
+### Webscraping
 
@@
 Despite these precautions, the fundamental issue of using non-consensual data persists.
-I do not adhere to the view that making data publicly available equates to granting unrestricted permission for its use in research.
+I do not agree with the view that making data publicly available equates to granting unrestricted permission for its use in research.
 While the data in this study was already accessible online, the research generates new insights, such as patterns of tie formation between scholars, which were not previously explicit.
@@
 
-## Operationalization of gender
+### Operationalization of gender
 
@@
 This approach disregards the complexity of gender identity and risks misrepresentation.
-A more detailed explanation of how gender data was defined and its limitations is provided in the data definition section.
+
+# Analysis
+
+To evaluate the homophiliy in collaboration networks by gender and h-index, the analysis of the data will be as follows.
+The first step involves examining descriptive analyses and visualisaitons of the data which will then serve as a foundation for the second phase of the analysis, which focuses on answering the explanatory research question of this study.
+This latter phase investigates the impact of same-gender preference in scholars' collaboration networks and explores the interaction between the gender and h-index of scholars.
+Descriptive analyses will utilize functions of the igraph and ggraph packages, while the explanatory questions will be examined using Stochastic Actor-Based Models implemented via the RSiena package (@igraph, @ggraph, @RSiena_package, @RSiena_manual).
+
+## RSiena
+
+SIENA, which stands for *Simulation Investigation for Empirical Network Analysis*, is a software tool designed to perform statistical estimation of models for longitudinal social network data.
+SIENA version 4.0, also known as RSiena, is a package for the R statistical software and was developed by Ruth Ripley and Krists Boitmanis, in collaboration with Tom Snijders (@RSiena_package, @RSiena_manual).
+The use of RSiena for this project is highly based on the practical information provided in "[Social Network Analysis for Social Scientists](https://jochemtolsma.github.io/SNA-4-Social-Scientists/)**"** (@SNASS).
+
+To ensure the model accurately represents the collaboration network, I developed it iteratively, beginning with a null model (Model 0) and gradually building up to a more comprehensive model (Model 4).
+Each successive model incorporates additional effects, allowing for targeted testing of specific hypotheses.
+The **null model** serves as the foundation and includes only basic structural effects: reciprocity and outdegree (density), as is standard in RSiena.
+This model provides a baseline for comparison but does not address any hypotheses directly.
+The **first model** incorporates additional structural network effects, such as isolates, indegree popularity, and outdegree activity, to examine how these features influence collaboration dynamics.
+This model offers insights into *Hypothesis 3*, as it highlights the structural factors shaping network patterns.
+Building on model 1, this model introduces covariate effects for gender, including ego, alter, and same-gender preferences (sameX), as well as a structural effect for gender-differentiated transitivity (diffXTransTrip).
+By analyzing gender-based network patterns, this model tests *Hypothesis 1*, which focuses on gender homophily.\
+Expanding on model 2, **model 3** incorporates departmental effects, such as ego and alter preferences for department membership, as well as same-department collaboration tendencies (sameX).
+This addition allows for a more nuanced analysis of departmental differences in gender homophily, addressing *Hypothesis 2*.
+The final model (**model 4**) integrates prestige effects through covariate interactions for the h-index, including ego, alter, and indegree popularity weighted by the h-index.
+These additions test *Hypothesis 4*, examining whether prestige moderates gender homophily in collaboration patterns.
+The fit of each model and its relevance interpreting the estimates will be reported in the Analysis chapter and further detailed in the [GOFpart](https://treesdude.github.io/labjournal/finalGOF.html) of this final report webpage.
+
+## Descriptives
+
+**[Revisit and only talk about those that make sense to examine here]**
+
+First, ego-level descriptives such as the counts and distributions of gender and h-indices in both departments were generated to establish a clearer picture of the data at hand.
+
+I also examined descriptives of the ego network and of the whole collaboration network of scholars.
+Among others, these included the number of nodes, edges, reciprocity, degreee centrality, clustering, density, and path-length.
+**[INSERT RELEVANT DESCRIPTIVES HERE]**\
+\
+Then, the networks were visualized using graphs to identify the presence of clustering and examine whether they are concentrated among individuals with the highest h-index or around specifically gendered scholars.
+
+**[UNSURE IF THIS IS NEEDED IF GENDER IS FIRST COVARIATE AND H INDEX ONLY CONTRL VARIABLE]**
+
+Various centrality measures were also calculated and analyzed to determine their correlation with the scholars' h-index, providing further insight into whether network hubs tend to form around those with the highest h-index.
+
+------------------------------------------------------------------------
+
+# Ego-Level Descriptives
+
+**Load data**
+
+Scholar data
+
+```{r scholar data}
+scholars <- fload("./data/processed/scholars_20240924.rda") 
+#make sure to lead fload first of course
+```
+
+```{r saving scholar output}
+# save the output of your function
+test  <- fcolnet(data = scholars, 
+                university = "RU", 
+                discipline = c("sociology", "political science"),
+                waves = list(c(2015, 2018), c(2019, 2023)), 
+                type = c("first"))
+```
+
+Ego data
+
+```{r df_ego data}
+df_ego <- fload("./data/processed/df_ego_20241108.rda")
+```
+
+```{r matrix data ego}
+
+test_w1 <- igraph::graph_from_adjacency_matrix(
+  test$nets[1,,], # first wave of data. 
+  # (thus I select the array of networks and take the first matrix)
+  mode = c("directed"),
+  weighted = NULL,
+  diag = FALSE,
+  add.colnames = NULL,
+  add.rownames = NULL)
+
+```
+
+## Gender - Ego level
+
+Descriptives (mean, distibution, etc.) in whole sample
+
+```{r sum gender, hide = TRUE, echo=FALSE }
+summary(df_ego$gender)
+```
+
+gender counts across whole sample (0 = female, 1 = male)
+
+```{r counts gender-all, hide = TRUE, echo=FALSE }
+table(df_ego$gender)
+```
+
+Histogram: overall gender distribution in sample
+
+```{r histogram gender, hide = TRUE, echo=FALSE }
+# Convert gender to a factor to avoid errors
+df_ego$gender <- as.factor(df_ego$gender)
+# Create the histogram with a dark theme and two colors for bars
+ggplot(df_ego, aes(x = gender, fill = gender)) +
+  geom_bar(color = "darkgrey", width = 0.6) +  # Add borders for bars
+  scale_fill_manual(
+    values = c("0" = "#FFFFB3", "1" = "#80B1D3"),  # Custom colors: yellow for females, blue for males
+    labels = c("Female", "Male")  # Optional: customize legend labels
+  ) +
+  labs(
+    title = "Gender Distribution",
+    x = "Gender\n (0 = female, 1 = male)",
+    y = "Count",
+    fill = "Gender"  # Legend title
+  ) +
+  theme_minimal(base_family = "Arial") +  # Clean, minimal base theme
+  theme(
+    plot.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark background
+    panel.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark panel background
+    panel.grid.major = element_line(color = "#444444"),  # Subtle grid lines
+    panel.grid.minor = element_line(color = "#444444"),
+    axis.text = element_text(color = "#f0f0f0"),  # White axis text
+    axis.title = element_text(color = "#f0f0f0", face = "bold"),  # Bold white axis titles
+    plot.title = element_text(color = "#f0f0f0", face = "bold", hjust = 0.5),  # White centered title
+    legend.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark legend background
+    legend.text = element_text(color = "#f0f0f0"),  # White legend text
+    legend.title = element_text(color = "#f0f0f0")  # White legend title
+    )
+
+```
+
+Genders per department (0 = female, 1 = male)
+
+```{r gender per dep., hide = TRUE, echo=FALSE }
+
+# Wave 1: Gender count per department 
+table(df_ego$discipline.24, df_ego$gender)
+```
+
+## H index - Ego level
+
+Descriptives (mean, distribution, etc.)
+
+```{r summary h index, hide = TRUE, echo=FALSE }
+summary(df_ego$h_index)
+```
+
+H-Index Whole sample
+
+```{r hist h index, hide = TRUE, echo=FALSE }
+# Histogram of prestige scores for Wave 1
+
+# Create a data frame for ggplot2 
+df_h_index <- data.frame(h_index = df_ego$h_index)
+
+# Generate the histogram with ggplot2
+ggplot(df_h_index, aes(x = h_index)) +
+  geom_histogram(
+    bins = 30,
+    fill = "#FFFFB3",  # Bar color
+    color = "black"    # Border color for bars
+  ) +
+  labs(
+    title = "Distribution of H-Index from 2015 to 2018",
+    x = "H Index",
+    y = "Frequency"
+  ) +
+  theme_minimal(base_family = "Arial") +  # Clean, minimal base theme
+  theme(
+    plot.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark background
+    panel.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark panel background
+    panel.grid.major = element_line(color = "#444444"),  # Subtle grid lines
+    panel.grid.minor = element_line(color = "#444444"),
+    axis.text = element_text(color = "#f0f0f0"),  # White axis text
+    axis.title = element_text(color = "#f0f0f0", face = "bold"),  # Bold white axis titles
+    plot.title = element_text(color = "#f0f0f0", face = "bold", hjust = 0.5)  # White centered title
+  )
+
+```
+
+H index per department
+
+```{r table per dep h index, hide = TRUE, echo=FALSE }
+# Wave 1: Prestige distribution by dep. and total
+df_ego %>%
+    group_by(discipline.24) %>%
+    summarise(mean_h_index = mean(h_index, na.rm = TRUE), min_h_index = min(h_index,
+        na.rm = TRUE), max_h_index = max(h_index, na.rm = TRUE), sd_h_index = sd(h_index,
+        na.rm = TRUE)) %>%
+    bind_rows(df_ego %>%
+        summarise(discipline.24 = "total", mean_h_index = mean(h_index, na.rm = TRUE), min_h_index = min(h_index,
+            na.rm = TRUE), max_h_index = max(h_index, na.rm = TRUE), sd_h_index = sd(h_index,
+            na.rm = TRUE)))
+```
+
+------------------------------------------------------------------------
 

### 2024-11-25 draftdesresults.Rmd
draft discussion
restructuring data with ego descriptives

@@
 
-```{r clean}
+```{r clean, hide =TRUE}
 rm(list = ls())
@@
 
-```{r functions 1, hide =TRUE}
+```{r functions 1, hide =TRUE, results = 'hide' }
 fpackage.check <- function(packages) {
@@
 
-```{r functions 2, hide=TRUE}
+```{r functions 2, hide=TRUE, results ='hide'}
 fcolnet <- function(data = scholars, university = "RU", discipline = "sociology"+"political science", waves = list(c(2015,

### 2024-11-25 draftdiscussion.Rmd
restructuring data with ego descriptives

@@
 This study investigates how co-authorship networks among scholars are influenced by gender, departmental affiliation, and academic prestige.
-By examining networks within the Political Science and Sociology departments at Radboud University, the study aims to understand how these factors jointly shape collaboration networks.
-Scholars often prefer collaborators of the same gender, a phenomenon rooted in societal norms and perceived status differences.
+By examining networks within the Political Science and Sociology departments at Radboud University, this study utilizes 'RSiena', simulating changes in social networks, to understand how these factors jointly shape scholars' collaboration patterns (@RSiena_manual, @RSiena_package.
+Scholars often prefer collaborators of the same gender, a phenomenon rooted in societal norms and perceived status differences ( @Horta2022 ).
 This results in gender clustering within academic networks, with men and women showing distinct preferences for same-gender collaborations (*Hypothesis 1).* Disciplines differ in their gender dynamics.
-Sociology, characterized by a more balanced gender representation, may facilitate more cross-gender collaborations compared to the male-dominated field of Political Science.
+Sociology, characterized by a more balanced gender representation, may facilitate more cross-gender collaborations compared to field of Political Science (@Kwiek2021).
 Hence, gender homophily might be less influential in collaboration preferences of scholars in the sociology department than those in political science *(Hypothesis 2).\
-*Furthermore, structural features of collaboration networks, such as reciprocity, indegree popularity, and outdegree activity, shape how collaboration ties form.
+*Furthermore, structural features of collaboration networks, such as reciprocity, indegree popularity, and outdegree activity, shape how collaboration ties form (@Snijders2010).
 These structural network effects may reinforce gender homophily in collaboration preferences in the creation of ties betwen scholars *(Hypothesis 3)*.
-Prestige, as measured by the Hirsch-Index, may mitigate gender homophily by increasing the appeal of high-status collaborators regardless of their gender.
+Prestige, as measured by the Hirsch-Index, may mitigate gender homophily by increasing the appeal of high-status collaborators regardless of their gender (@Bellotti2022).
 This hypothesis examines whether strategic collaborations dilute gendered preferences in scholarly networks.
@@
 The parameter for same-gender collaboration (sameX) remains positive and significant, indicating that scholars are more likely to collaborate with same-gender peers than with different-gender peers.
-This aligns with previous research suggesting that gendered barriers in academia, whether structural or cultural, can lead to the formation of gendered clusters/silos in collaborative networks (**\*\*SOURCE\*\***).
+This aligns with previous research suggesting that gendered barriers in academia, whether structural or cultural, can lead to gender clustering in collaborative networks (@Horta2022; @Kwiek2021; @McPherson2001).
 
-Interestingly, the significance of gender homophily persists even after controlling for other covariates, such as department affiliation and h-index, demonstrating that it is a robust phenomenon in these networks.
+Interestingly, the significance of gender clustering persists even after controlling for other covariates, such as department affiliation and h-index, demonstrating that it is a robust phenomenon in these networks.
 While this result is not unexpected, it emphasizes the enduring influence of gender dynamics on scholarly collaborations.
@@
 **Hypothesi 2** proposed that scholars in the sociology department exhibit weaker gender homophily than those in the political science department.
-While this hypothesis was not explicitly tested using an interaction term, comparisons across models suggest no substantial department-level differences in gender homophily.
+While this hypothesis was not explicitly tested using an interaction term, comparisons across models suggest no substantial department-level differences in gender clustering.
 The same-gender collaboration parameter (sameX for gender) is nearly identical in models 2 and 3, indicating that the inclusion of department as a covariate does not significantly alter the pattern of same-gender collaborations.
@@
 In terms of structural network effects, reciprocity emerges as a consistently significant factor, indicating that collaborations are more likely to be mutual.
-This aligns with existing theories of dyadic reciprocity in networks, suggesting that once a collaboration tie is initiated, it is likely to be reciprocated (**\*\*SOURCE\*\***).
+This aligns with existing theories of dyadic reciprocity in networks, suggesting that once a collaboration tie is initiated, it is likely to be reciprocated (@Snijders2010).
 Interestingly, the outdegree parameter (baseline likelihood of initiating a tie) fluctuates in significance across models but remains consistently negative when significant, indicating that scholars generally show a low tendency to initiate collaborations.
@@
 
-The results provide little to no support for **Hypothesis 4**, which proposed that gender homophily is less influential when potential collaborators have higher academic prestige (as measured by the h-index).
+The results provide little to no support for Hypothesis 4, which proposed that gender homophily is less influential when potential collaborators have higher academic prestige (as measured by the h-index).
 The inclusion of h-index as a covariate in model 4 reveals that scholars with higher h-index scores are more likely to attract collaborations (significant positive alter effect, altX) but less likely to initiate them (significant negative ego effect, egoX).
-This is consistent with theories of preferential attachment and upward mobility, where prestigious scholars act as hubs, receiving collaboration requests rather than initiating them (\*\***SOURCE**\*\*).
+This is consistent with theories of preferential attachment and upward mobility, where prestigious scholars act as hubs, receiving collaboration requests rather than initiating them (@Broido2019; @Knobloch2013).
 
@@
 This finding suggests that while prestige plays a role in shaping collaboration networks, it does mitigate the tendency of scholars to prefer same-gender collaborations over different-gendered ones.
-Thus, while prestigious scholars are more sought after, their collaboration patterns remain influenced by gender.
+Thus, while prestigious scholars are more sought after, collaboration preferences in scholars' networks remain influenced by gender-preferences.
 
@@
 
-------------------------------------------------------------------------
-
-***STILL DOOOOO! INSERT SOURCES IN TEXT ABOVE***
-
 ***PROOF READING NEXT PARTS:***
-
-------------------------------------------------------------------------
 
@@
 
-From a policy perspective, these results underscore the need for initiatives aimed at reducing gendered collaboration silos.
-For example, mentorship programs or institutional incentives that encourage cross-gender and cross-department collaborations could help mitigate these patterns.
-Additionally, the finding that prestigious scholars are less likely to initiate collaborations suggests that early-career researchers, particularly those from underrepresented groups, may face challenges in accessing these high-prestige hubs.
+From a policy perspective, these results underscore the need for initiatives aimed at reducing gendered collaboration clustering.
+For example, mentorship programs or institutional incentives that encourage cross-gender and cross-department collaborations could help lessen these pattern.
+Additionally, the finding that prestigious scholars are less likely to initiate collaborations suggests that researchers early int heir career, particularly those from underrepresented groups, may face challenges in accessing these high-prestige hubs.
 Institutions should consider strategies to facilitate connections between early-career and high-prestige scholars to promote equity in collaboration opportunities.
@@
 Future studies should include such interactions to better understand these dynamics.
-Second, while the h-index serves as a useful proxy for academic prestige, other measures of prestige or influence, such as grant funding or editorial roles, might yield additional insights.
-Finally, the generalizability of these findings is limited to the specific departments and network structures examined here.
+Second, while the h-index serves as a useful proxy for academic prestige, this study did not control for author characteristics such as age, which may account for some of the effects found.
+Besides, other measures of prestige or influence, such as grant funding or editorial roles, might yield additional insights.
+Finally, the examined sample is arguably small, and the generalizability of these findings is further limited to the specific departments and network structures examined here.
 

### 2024-11-25 finalGOF.Rmd
restructuring data with ego descriptives

@@
 ---
+
 ```{=html}
@@
 ```
+
+# Setup
+
+Clean workspace.
+
+```{r clean, hide =TRUE}
+rm(list = ls())
+```
+
+## Packages
+
+```{r package, hide =TRUE}
+require(RSiena)
+
+```
+
+## Functions
+
+Functions chunk
+
+```{r functions 1, hide = TRUE}
+fpackage.check <- function(packages) {
+    lapply(packages, FUN = function(x) {
+        if (!require(x, character.only = TRUE)) {
+            install.packages(x, dependencies = TRUE)
+            library(x, character.only = TRUE)
+        }
+    })
+}
+
+fsave <- function(x, file = NULL, location = "./data/processed/") {
+    ifelse(!dir.exists("data"), dir.create("data"), FALSE)
+    ifelse(!dir.exists("data/processed"), dir.create("data/processed"), FALSE)
+    if (is.null(file))
+        file = deparse(substitute(x))
+    datename <- substr(gsub("[:-]", "", Sys.time()), 1, 8)
+    totalname <- paste(location, file, "_", datename, ".rda", sep = "")
+    save(x, file = totalname)  #need to fix if file is reloaded as input name, not as x. 
+}
+
+fload <- function(filename) {
+    load(filename)
+    get(ls()[ls() != "filename"])
+}
+
+fshowdf <- function(x, ...) {
+    knitr::kable(x, digits = 2, "html", ...) %>%
+        kableExtra::kable_styling(bootstrap_options = c("striped", "hover")) %>%
+        kableExtra::scroll_box(width = "100%", height = "300px")
+}
+
+```
+
+# Goodness of Fit
+
+The goodness of fit (GOF) for a model assesses how well the estimated model fits the observed data.
+This evaluation is crucial because `RSiena` relies on simulations to estimate changes within the network (@RSiena_manual).
+GOF measures indicate whether the simulated network matches the changes in the observed network.
+The use of the specific GOF measure of a model's Indegree Distribution seems most appropriate since the study's focus lies on changes in directed ties between schoalrs.
+A GOF with a p-value below .05 indicates a poor fit and calls for adjustment of the model, while a p-value above .05 usually indicates an acceptable or good fit.\
+The GOF measures of Indegree Distribution for the null model (*p* = .008) and model 1 *(p* = .002) both display p-values below .05.
+This indicates that they do not fit the data well.
+This makes sense, since the null model and model 1 do not contain any network effects yet.
+This also implies that we should not interpret the estimates of these models.
+The GOF of model 2 (*p* = .096) indicates an acceptable fit, while model 3 (*p* = .12) seems to be even better fitting.
+Overall, the final model, model 4 (*p* = .197), including all the covariates investigated in this study, has the best fit.
+
+<!--  M0: 0.008  M1: 0.002  M2: 0.096  M3: 0.12  M4: 0.197  -->
+
+# Model 0
+
+```{r, hide = TRUE}
+Model0.1 <- fload("./data/processed/estimated_M0.1_20241123.rda")
+Model0.1
+```
+
+```{r GOF M0, hide = TRUE}
+GOF_M0.1 <- sienaGOF(Model0.1, IndegreeDistribution, verbose = FALSE, join = TRUE, varName = "nets")
+
+plot(GOF_M0.1, main = 'GOF - "Null" Model 0.1 \n Indegree Distribution')
+
+```
+
+# Model 1
+
+```{r, hide = TRUE}
+Model1.1 <- fload("./data/processed/estimated_M1.1_20241123.rda")
+
+```
+
+```{r GOF M1, hide = TRUE}
+GOF_M1.1 <- sienaGOF(Model1.1, IndegreeDistribution, verbose = FALSE, join = TRUE, varName = "nets")
+
+plot(GOF_M1.1, main = "GOF - Model 1 \n Indegree Distribution")
+```
+
+# Model 2
+
+```{r, hide = TRUE}
+Model2.1 <- fload ("./data/processed/estimated_M2.1_20241123.rda")
+Model2.1
+```
+
+```{r GOF M2, hide = TRUE}
+GOF_M2.1 <- sienaGOF(Model2.1, IndegreeDistribution, verbose = FALSE, join = TRUE, varName = "nets")
+
+plot(GOF_M2.1, main = "GOF - Model 2 \n Indegree Distribution")
+```
+
+# Model 3
+
+```{r, hide=TRUE}
+Model3 <- fload("./data/processed/estimated_M3_20241123.rda")
+```
+
+```{r GOF M3, hide=TRUE}
+GOF_M3 <- sienaGOF(Model3, IndegreeDistribution, verbose = FALSE, join = TRUE, varName = "nets")
+
+plot(GOF_M3, main = "GOF - Model 3 \n Indegree Distribution")
+```
+
+# Model 4
+
+```{r, hide=TRUE}
+Model4 <- fload("./data/processed/estimated_M4_20241123.rda")
+```
+
+```{r GOF M4, hide=TRUE}
+GOF_M4 <- sienaGOF(Model4, IndegreeDistribution, verbose = FALSE, join = TRUE, varName = "nets")
+
+plot(GOF_M4, main = "GOF - Model 4 \n Indegree Distribution")
+```

### 2024-11-25 finaldata.Rmd
restructuring data with ego descriptives

@@
 ---
-title: "Data & Methods"
+title: "Data & Analysis"
 author: "Verooo"
@@
 ```
+
+# Data
+
+----
+
+# References

### 2024-11-25 finaldiscussion.Rmd
restructuring data with ego descriptives

@@
 ```
+
+# Discussion
+
+This study investigates how co-authorship networks among scholars are influenced by gender, departmental affiliation, and academic prestige.
+By examining networks within the Political Science and Sociology departments at Radboud University, this study utilizes 'RSiena', simulating changes in social networks, to understand how these factors jointly shape scholars' collaboration patterns (@RSiena_manual, @RSiena_package.
+Scholars often prefer collaborators of the same gender, a phenomenon rooted in societal norms and perceived status differences ( @Horta2022 ).
+This is expected to result in gender clustering within academic networks, with men and women showing distinct preferences for same-gender collaborations (*Hypothesis 1).* Disciplines differ in their gender dynamics.
+Sociology, characterized by a more balanced gender representation, may facilitate cross-gender collaborations more so than the field of Political Science (@Kwiek2021).
+Hence, gender homophily was expected to be less influential in collaboration preferences of scholars in the sociology department than those in political science *(Hypothesis 2).\
+*Furthermore, structural features of collaboration networks, such as reciprocity, indegree popularity, and outdegree activity, shape how collaboration ties form (@Snijders2010).
+These structural network effects may reinforce gender homophily in collaboration preferences in the creation of ties betwen scholars *(Hypothesis 3)*.
+Prestige, as measured by the Hirsch-Index, may mitigate gender homophily by increasing the appeal of high-status collaborators regardless of their gender (@Bellotti2022).
+This hypothesis examined whether strategic collaborations dilute gendered preferences in scholarly networks.
+Specifically it investigated whether gender homophily is less promnounced in scholars' preference to collaborate when potential collaborators have a higher H-index *(Hypothesis 4).*
+
+## Situating Findings
+
+### **Gender Homophily (H1)**
+
+The results consistently support Hypothesis 1, showing significant evidence of gender homophily across all models.
+The parameter for same-gender collaboration (sameX) remains positive and significant, indicating that scholars are more likely to collaborate with same-gender peers than with different-gender peers.
+This aligns with previous research suggesting that gendered barriers in academia, whether structural or cultural, can lead to gender clustering in collaborative networks (@Horta2022; @Kwiek2021; @McPherson2001).
+
+Interestingly, the significance of gender clustering persists even after controlling for other covariates, such as department affiliation and h-index, demonstrating that it is a robust phenomenon in these networks.
+While this result is not unexpected, it emphasizes the enduring influence of gender dynamics on scholarly collaborations.
+
+### **Departmental Differences in Gender Homophily (H2)**
+
+Hypothesi 2 proposed that scholars in the sociology department exhibit weaker gender homophily than those in the political science department.
+While this hypothesis was not explicitly tested using an interaction term, comparisons across models suggest no substantial department-level differences in gender clustering.
+The same-gender collaboration parameter (sameX for gender) is nearly identical in models 2 and 3, indicating that the inclusion of department as a covariate does not significantly alter the pattern of same-gender collaborations.
+
+However, the department-related parameter for ego’s tendency to initiate collaborations (egoX for department) becomes significant in model 4, revealing a lower likelihood for political scientists to initiate collaborations compared to sociologists.
+This could imply department-level differences in collaboration norms or opportunities, which might indirectly influence gender homophily.
+An interaction term between department and gender would have been useful to further investigate these nuances.
+
+After all, hypothesis 2 was not supported.
+While scholars show a significant preference for collaborating within their own department, with sociologists more likely to initiate collaborations than political scientists, *no* substantial differences in gender homophily were observed in relation to scholars' departments.
+
+### **Structural Network Effects and Gender Homophily (H3)**
+
+In terms of structural network effects, reciprocity emerges as a consistently significant factor, indicating that collaborations are more likely to be mutual.
+This aligns with existing theories of dyadic reciprocity in networks, suggesting that once a collaboration tie is initiated, it is likely to be reciprocated (@Snijders2010).
+Interestingly, the outdegree parameter (baseline likelihood of initiating a tie) fluctuates in significance across models but remains consistently negative when significant, indicating that scholars generally show a low tendency to initiate collaborations.
+
+In line with Hypothesis 3, Gender homophily (sameX) remains significant even when controlling for these structural effects, reinforcing its importance.
+This finding implies that scholars' same-gender preferences in creating ties are not merely a byproduct of network structure but reflect deeper social or cultural dynamics.
+
+### Prestige and Gender Homopgily (H4)
+
+The results provide little to no support for Hypothesis 4, which proposed that gender homophily is less influential when potential collaborators have higher academic prestige (as measured by the h-index).
+The inclusion of h-index as a covariate in model 4 reveals that scholars with higher h-index scores are more likely to attract collaborations (significant positive alter effect, altX) but less likely to initiate them (significant negative ego effect, egoX).
+This is consistent with theories of preferential attachment and upward mobility, where prestigious scholars act as hubs, receiving collaboration requests rather than initiating them (@Broido2019; @Knobloch2013).
+
+However, since the the same-gender parameter (sameX) remained significant and largely unchanged, the influence of genderhomophily on scholars' decisions to collaborate is not substantially impacted by scholars' h-index.
+This finding suggests that while prestige plays a role in shaping collaboration networks, it does mitigate the tendency of scholars to prefer same-gender collaborations over different-gendered ones.
+Thus, while prestigious scholars are more sought after, collaboration preferences in scholars' networks remain influenced by gender-preferences.
+
+## **Broader Implications**
+
+The findings of this study highlight the interplay between structural, departmental, and individual factors in shaping co-authorship networks.
+Gender homophily appears to be a robust and enduring feature of these networks, resisting the influence of prestige and departmental context.
+This raises important questions about the structural barriers faced by scholars, particularly women, in accessing diverse collaboration opportunities.
+
+From a policy perspective, these results underscore the need for initiatives aimed at reducing gendered collaboration clustering.
+For example, mentorship programs or institutional incentives that encourage cross-gender and cross-department collaborations could help lessen these pattern.
+Additionally, the finding that prestigious scholars are less likely to initiate collaborations suggests that researchers early int heir career, particularly those from underrepresented groups, may face challenges in accessing these high-prestige hubs.
+Institutions should consider strategies to facilitate connections between early-career and high-prestige scholars to promote equity in collaboration opportunities.
+
+## **Limitations and Future Research**
+
+This study has several limitations that warrant consideration.
+First, the lack of interaction terms between gender and department or h-index limits the ability to make strong conclusions about how these factors jointly influence collaboration patterns.
+Future studies should include such interactions to better understand these dynamics.
+Second, while the h-index serves as a useful proxy for academic prestige, this study did not control for author characteristics such as age, which may account for some of the effects found.
+Besides, other measures of prestige or influence, such as grant funding or editorial roles, might yield additional insights.
+Finally, the examined sample is arguably small, and the generalizability of these findings is further limited to the specific departments and network structures examined here.
+
+Future research should explore longitudinal changes in collaboration patterns to assess whether gender homophily weakens over time, particularly as scholars gain prestige.
+Additionally, examining the role of institutional interventions, such as funding programs or diversity initiatives, could provide valuable insights into strategies for fostering more equitable collaboration networks.
+
+## **Conclusion**
+
+This study contributes to our understanding of the dynamics of co-authorship networks by highlighting the persistent influence of gender homophily in scholars' collaboration preferences, even in the presence of academic prestige and structural network effects.
+While prestigious scholars are more likely to attract collaborations, gendered patterns of collaboration endure.
+This underrscores the need for targeted interventions to address these disparities.
+By disentangling the effects of gender, department, and prestige, this research provides a foundation for future studies and practical efforts aimed at fostering more inclusive and diverse academic collaboration networks.
+
+------------------------------------------------------------------------
+
+# References

### 2024-11-25 finaltheory.Rmd
restructuring data with ego descriptives

@@
 Additionally, the concept of **upward mobility** highlights how strategic collaborations with prestigious scholars can counterbalance preferences based on similarity, such as gender homophily.
-The study tests four hypotheses across the Political Science and Sociology departments at Radboud University to explore how these mechanisms may interact to influence scholars' collaboration patterns.
+The study tests four hypotheses across the political science and sociology departments at Radboud University to explore how these mechanisms may interact to influence scholars' collaboration patterns.
 
@@
 The extent of gender homophily may vary by discipline duee to differences in gender representation and cultural norms.
-Sociology, often seen as more gender-balanced or even female-dominated, may facilitate cross-gender collaborations more than Political Science, which remains a male-dominated field associated with traditional masculine traits such as assertiveness and rationality (@Kwiek2021).
-These cultural perceptions influence collaboration preferences, potentially reducing gender homophily in disciplines where gender parity id normalized.
+Sociology, often seen as more gender-balanced or even female-dominated, may facilitate cross-gender collaborations more than political science, which remains a male-dominated field associated with traditional masculine traits such as assertiveness and rationality (@Kwiek2021).
+These cultural perceptions influence collaboration preferences, potentially reducing gender homophily in disciplines where gender parity id normalized (@Knobloch2013).
 The second hypothesis tests whether departmental norms and gender dynamics affect scholars' tendency for gender homophily in their collaborations.

### 2024-11-25 modelestimate.Rmd
restructuring data with ego descriptives

@@
 
-<title>My Descriptives</title>
+<title>My Models</title>
 
@@
 
-Note to self. Keep in mind: \
+Note to self. Keep in mind:\
 **meaning of significance in RSiena** "It is important to mention that
@@
 fit for the data and estimates of this model do not give us reliable
-information. \
+information.\
 *For all GOF plots compiled in one place, see here:
@@
 
-------------------------------------------------------
+------------------------------------------------------------------------
 
@@
 
-8\. eval: same gender_RS 0.6632 ( 0.2623) sign. (2.52840) \*\*\* \
+8\. eval: same gender_RS 0.6632 ( 0.2623) sign. (2.52840) \*\*\*\
 (sameX: comparison model 2 and 3:\
@@
 tendency to initiate collaborations than scholars from the sociology
-department (coded as 0). \
+department (coded as 0).\
 Similar to the prior model, the sameX parameter for department shows a
@@
 
-R-Manual: in-degree popularity weighted by sender’s V (inPopX)
-defined by the sum of values of V for actors h for which there are ties
-i → j ← h
+R-Manual: in-degree popularity weighted by sender’s V (inPopX) defined
+by the sum of values of V for actors h for which there are ties i → j ←
+h
 
 note that to use this effect for p = 2 the variable V must be
-nonnegative, which
-implies that it must be non-centered;
-further note that if V is a behavioral variable, it will be used in the
-centered version,
-so that p must be 1; if weighting by a non-centered behavioral variable
-is desired, a
-new effect is necessary;
+nonnegative, which implies that it must be non-centered; further note
+that if V is a behavioral variable, it will be used in the centered
+version, so that p must be 1; if weighting by a non-centered behavioral
+variable is desired, a new effect is necessary;
 

### 2024-11-25 draftdata.Rmd
ypagenorespond

@@
 
-```{r clean, results='hide', hide =TRUE}
+```{r clean, echo=FALSE}
 rm(list = ls())
@@
 
-```{r package, hide=TRUE, results='hide'}
+```{r package, echo=FALSE}
 require(tidyverse)
@@
 
-```{r functions 1, hide =TRUE, results='hide'}
+```{r functions 1, echo=FALSE}
 fpackage.check <- function(packages) {
@@
 
-```{r functions 2, hide=TRUE, results='hide'}
+```{r functions 2, echo=FALSE}
 fcolnet <- function(data = scholars, university = "RU", discipline = "sociology"+"political science", waves = list(c(2015,
@@
 # Ego-Level Descriptives
+Below you can find some descriptive information about the ego-level data after data preparation. For more information, consult the 'data preparation' part of this final report.
 
@@
 
-```{r sum gender, hide = TRUE, echo=FALSE }
+```{r sum gender, echo=FALSE }
 summary(df_ego$gender)
@@
 
-```{r counts gender-all, hide = TRUE, echo=FALSE }
+```{r counts gender-all, echo=FALSE }
 table(df_ego$gender)
@@
 
-```{r histogram gender, hide = TRUE, echo=FALSE }
+```{r histogram gender, echo=FALSE }
 # Convert gender to a factor to avoid errors
@@
 
-```{r gender per dep., hide = TRUE, echo=FALSE }
+```{r gender per dep., echo=FALSE }
 
@@
 
-```{r summary h index, hide = TRUE, echo=FALSE }
+```{r summary h index, echo=FALSE }
 summary(df_ego$h_index)
@@
 
-```{r hist h index, hide = TRUE, echo=FALSE }
+```{r hist h index, echo=FALSE }
 # Histogram of prestige scores for Wave 1
@@
 
-```{r table per dep h index, hide = TRUE, echo=FALSE }
+```{r table per dep h index, echo=FALSE }
 # Wave 1: Prestige distribution by dep. and total

### 2024-11-25 draftdata.Rmd
finaldatatest

@@
 
-I also examined descriptives of the ego network and of the whole collaboration network of scholars.
-Among others, these included the number of nodes, edges, reciprocity, degreee centrality, clustering, density, and path-length.
-**[INSERT RELEVANT DESCRIPTIVES HERE]**\
-\
-Then, the networks were visualized using graphs to identify the presence of clustering and examine whether they are concentrated among individuals with the highest h-index or around specifically gendered scholars.
+Then, to identify the presence of clustering and examine whether they are concentrated among individuals with the highest h-index or around specifically gendered scholars, the networks were visualized.
+Further, centrality measures were examined to investigate their correlation to the ego-level variables gender and H-index.
 
-**[UNSURE IF THIS IS NEEDED IF GENDER IS FIRST COVARIATE AND H INDEX ONLY CONTRL VARIABLE]**
-
-Various centrality measures were also calculated and analyzed to determine their correlation with the scholars' h-index, providing further insight into whether network hubs tend to form around those with the highest h-index.
+.  Among others, these included the number of nodes, edges, reciprocity, degreee centrality, clustering, density, and path-length. **[INSERT RELEVANT DESCRIPTIVES HERE]**\visualized using graphs
 

### 2024-11-25 finaldata.Rmd
finaldatatest

@@
 
+## Getting started
+
+```{r clean, echo=FALSE}
+rm(list = ls())
+```
+
+### Packages
+
+```{r package, echo=FALSE}
+require(tidyverse)
+require(RSiena)
+require(RsienaTwoStep)
+
+#install.packages("data.table")
+require(data.table)  # mainly for faster data handling
+# install.packages('xml2')
+require(xml2)
+# install.packages('rvest')
+require(rvest)
+require(igraph)
+require(ggraph)
+require(ggplot2)
+
+#install.packages('visNetwork')
+require(visNetwork)
+#install.packages('threejs')
+require(threejs)
+#install.packages('networkD3')
+require(networkD3)
+
+require(RColorBrewer)
+
+```
+
+### Functions
+
+```{r functions 1, echo=FALSE}
+fpackage.check <- function(packages) {
+    lapply(packages, FUN = function(x) {
+        if (!require(x, character.only = TRUE)) {
+            install.packages(x, dependencies = TRUE)
+            library(x, character.only = TRUE)
+        }
+    })
+}
+
+fsave <- function(x, file = NULL, location = "./data/processed/") {
+    ifelse(!dir.exists("data"), dir.create("data"), FALSE)
+    ifelse(!dir.exists("data/processed"), dir.create("data/processed"), FALSE)
+    if (is.null(file))
+        file = deparse(substitute(x))
+    datename <- substr(gsub("[:-]", "", Sys.time()), 1, 8)
+    totalname <- paste(location, file, "_", datename, ".rda", sep = "")
+    save(x, file = totalname)  #need to fix if file is reloaded as input name, not as x. 
+}
+
+fload <- function(filename) {
+    load(filename)
+    get(ls()[ls() != "filename"])
+}
+
+fshowdf <- function(x, ...) {
+    knitr::kable(x, digits = 2, "html", ...) %>%
+        kableExtra::kable_styling(bootstrap_options = c("striped", "hover")) %>%
+        kableExtra::scroll_box(width = "100%", height = "300px")
+}
+
+# this is the most important one. We created it in the previous script
+
+f_pubnets <- function(df_scholars = df, list_publications = publications, discip = "sociology"+"political science", affiliation = "RU",
+    waves = list(wave1 = c(2018, 2019, 2020), wave2 = c(2021, 2022, 2023))) {
+
+    publications <- list_publications %>%
+        bind_rows() %>%
+        distinct(title, .keep_all = TRUE)
+
+    df_scholars %>%
+        filter(affil1 == affiliation | affil2 == affiliation) %>%
+        filter(discipline == discip) -> df_sel
+
+    networklist <- list()
+    for (wave in 1:length(waves)) {
+        networklist[[wave]] <- matrix(0, nrow = nrow(df_sel), ncol = nrow(df_sel))
+    }
+
+    publicationlist <- list()
+    for (wave in 1:length(waves)) {
+        publicationlist[[wave]] <- publications %>%
+            filter(gs_id %in% df_sel$gs_id) %>%
+            filter(year %in% waves[[wave]]) %>%
+            select(author) %>%
+            lapply(str_split, pattern = ",")
+    }
+
+    publicationlist2 <- list()
+    for (wave in 1:length(waves)) {
+        publicationlist2[[wave]] <- publicationlist[[wave]]$author %>%
+            # lowercase
+        lapply(tolower) %>%
+            # Removing diacritics
+        lapply(stri_trans_general, id = "latin-ascii") %>%
+            # only last name
+        lapply(word, start = -1, sep = " ") %>%
+            # only last last name
+        lapply(word, start = -1, sep = "-")
+    }
+
+    for (wave in 1:length(waves)) {
+        # let us remove all publications with only one author
+        remove <- which(sapply(publicationlist2[[wave]], FUN = function(x) length(x) == 1) == TRUE)
+        publicationlist2[[wave]] <- publicationlist2[[wave]][-remove]
+    }
+
+    for (wave in 1:length(waves)) {
+        pubs <- publicationlist2[[wave]]
+        for (ego in 1:nrow(df_sel)) {
+            # which ego?
+            lastname_ego <- df_sel$lastname[ego]
+            # for all publications
+            for (pub in 1:length(pubs)) {
+                # only continue if ego is author of pub
+                if (lastname_ego %in% pubs[[pub]]) {
+                  aut_pot <- which.max(pubs[[pub]] %in% lastname_ego)
+                  # only continue if ego is first author of pub
+                  if (aut_pot == 1) {
+                    # check all alters/co-authors
+                    for (alter in 1:nrow(df_sel)) {
+                      # which alter
+                      lastname_alter <- df_sel$lastname[alter]
+                      if (lastname_alter %in% pubs[[pub]]) {
+                        networklist[[wave]][ego, alter] <- networklist[[wave]][ego, alter] + 1
+                      }
+                    }
+                  }
+                }
+            }
+        }
+    }
+    return(list(df = df_sel, network = networklist))
+}
+
+```
+
+```{r functions 2, echo=FALSE}
+fcolnet <- function(data = scholars, university = "RU", discipline = "sociology"+"political science", waves = list(c(2015,
+    2018), c(2019, 2023)), type = c("first")) {
+
+    # step 1
+    demographics <- do.call(rbind.data.frame, data$demographics)
+    demographics <- demographics %>%
+        mutate(Universiteit1.22 = replace(Universiteit1.22, is.na(Universiteit1.22), ""), Universiteit2.22 = replace(Universiteit2.22,
+            is.na(Universiteit2.22), ""), Universiteit1.24 = replace(Universiteit1.24, is.na(Universiteit1.24),
+            ""), Universiteit2.24 = replace(Universiteit2.24, is.na(Universiteit2.24), ""), discipline.22 = replace(discipline.22,
+            is.na(discipline.22), ""), discipline.24 = replace(discipline.24, is.na(discipline.24), ""))
+
+    sample <- which((demographics$Universiteit1.22 %in% university | demographics$Universiteit2.22 %in%
+        university | demographics$Universiteit1.24 %in% university | demographics$Universiteit2.24 %in%
+        university) & (demographics$discipline.22 %in% discipline | demographics$discipline.24 %in% discipline))
+
+    demographics_soc <- demographics[sample, ]
+    scholars_sel <- lapply(scholars, "[", sample)
+
+    # step 2
+    ids <- demographics_soc$au_id
+    nwaves <- length(waves)
+    nets <- array(0, dim = c(nwaves, length(ids), length(ids)), dimnames = list(wave = 1:nwaves, ids,
+        ids))
+    dimnames(nets)
+
+    # step 3
+    df_works <- tibble(works_id = unlist(lapply(scholars_sel$work, function(l) l$id)), works_author = unlist(lapply(scholars_sel$work,
+        function(l) l$author), recursive = FALSE), works_year = unlist(lapply(scholars_sel$work, function(l) l$publication_year),
+        recursive = FALSE))
+
+    df_works <- df_works[!duplicated(df_works), ]
+
+    # step 4
+    if (type == "first") {
+        for (j in 1:nwaves) {
+            df_works_w <- df_works[df_works$works_year >= waves[[j]][1] & df_works$works_year <= waves[[j]][2],
+                ]
+            for (i in 1:nrow(df_works_w)) {
+                ego <- df_works_w$works_author[i][[1]]$au_id[1]
+                alters <- df_works_w$works_author[i][[1]]$au_id[-1]
+                if (sum(ids %in% ego) > 0 & sum(ids %in% alters) > 0) {
+                  nets[j, which(ids %in% ego), which(ids %in% alters)] <- 1
+                }
+            }
+        }
+    }
+
+    if (type == "last") {
+        for (j in 1:nwaves) {
+            df_works_w <- df_works[df_works$works_year >= waves[[j]][1] & df_works$works_year <= waves[[j]][2],
+                ]
+            for (i in 1:nrow(df_works_w)) {
+                ego <- rev(df_works_w$works_author[i][[1]]$au_id)[1]
+                alters <- rev(df_works_w$works_author[i][[1]]$au_id)[-1]
+                if (sum(ids %in% ego) > 0 & sum(ids %in% alters) > 0) {
+                  nets[j, which(ids %in% ego), which(ids %in% alters)] <- 1
+                }
+            }
+        }
+    }
+
+    if (type == "all") {
+        for (j in 1:nwaves) {
+            df_works_w <- df_works[df_works$works_year >= waves[[j]][1] & df_works$works_year <= waves[[j]][2],
+                ]
+            for (i in 1:nrow(df_works_w)) {
+                egos <- df_works_w$works_author[i][[1]]$au_id
+                if (sum(ids %in% egos) > 0) {
+                  nets[j, which(ids %in% egos), which(ids %in% egos)] <- 1
+                }
+            }
+        }
+    }
+    output <- list()
+    output$data <- scholars_sel
+    output$nets <- nets
+    return(output)
+}
+```
+
+## Sample data
+
+The data for this study was obtained by collecting information from all Sociology and Political Science scholars at all Dutch institutions.
+During the initial phase of data collection, all important information regarding the author's position, university affiliation, names, IDs, departments, and more was gathered.
+The coordinator of this course, Jochem Tolsma, has provided a dataset with said information to be used in this project (**source sunbelt?** ).
+'OpenAlex' was used to scrape all published works, including important work-related information such as work id, concepts, citations, abstracts, and subjects, up until 2024 (@Priem2022).
+From this data, I created a final dataset (n=101) that included all authors from the Sociology and Political Science departments at Radboud University within the time frame of 2015 to 2018.
+I also included a second wave of data, pertainning to 2019-2024, which is purely included for the sake of running the simulations needed to analyse the data, while the focus remained on the first wave (2015-2018) only.
+Based on this data collaboration networks were constructed to capture whether two scholars in the sample had collaborated on a publication during a given wave.
+
+## Dependent variable
+
+The dependent variable in this dataset, indicated by the ties between scholars, refers to academic collaborations between them and are often called co-authorships.
+The data was scraped from OpenAlex API using the rvest and xml2 packages in R ( @Priem2022, @xml2, @rvest).
+The dependent variable, represented by an *adjacency matrix*, shows whether two actors or writers collaborated on one of their publications in the specified wave.\
+Each dyad (author combination) is assessed based on whether they collaborated (1) or not (0) throughout the data period.
+
+**I**n the collboartion networks analysed in this study, ties are described as directional, which implies that they are delivered by one actor and received by another.
+This means each actor has both outdegrees and indegrees.
+Outdegrees refer to 'sent' connections that refer to being the first author of a publication.
+Indegrees, or 'received' connections, imply collaboration on an article without being the 'initial' author.
+The generated adjacency matrix is thus holds a network, indicating the collaboration patterns of the academics at Radboud University between 2015-2018.
+
+## Independent variables
+
+### Gender
+
+The first covariate of my study is the gender of the scholars in the sample.
+This information was not available through OpenAlex, and was instead manually generated by consulting the website of the Dutch 'Voornamenbank' of the Meertens Institute (@MeertensInstituut).
+If the website indicated that a name was used my more males than females, the scholar with that name was considered be male, and vice versa (female/male: 0/1).
+In cases the website did not suggest a majority for, the name was manually assigned a gender by the person who coded the data, based on limited online research (aka I did a quick Google search) on the name in question.
+
+For the sake of simplicity, scholars' gender in this study was inferred from scholars’ names and treated as binary, which conflates the concepts of gender identity with biological sex.
+I acknowledge that names do not reliably indicate a person's gender identity and that gender encompasses more than the categories of men and women.
+Additionally, I recognize that while *men* and *women* typically refer to gender identities, *male* and *female* are often used to denote biological sex.
+These distinctions were not upheld throughout the documentation of this study, which conflates the terms and disregards individuals' self-identified genders.
+This approach was taken solely due to the constraints of this being a university assignment and does not reflect my standard research practices, which would try to respect and account for the complexity of gender and self-identification outside this coursework context.
+
+### Prestige
+
+The scholars' h-indices will serve as a control variable in this research design (@Bornmann2020, @Bornmann2021).
+The h-index calculates the number of publications that have been cited at least as frequently as the author's total number of publications.
+This number can then be used as measure for the author's 'prestige' (@Hirsch2005).
+The number of citations and publications needed for this calculation were webscraped through OpenAlex API (@Priem2022**).** The code for this process was provided by Lucan Bovens.
+
+## Ethical concerns
+
+### Webscraping
+
+This study relies on data obtained through web scraping publicly available sources, which raises several ethical concerns.
+One key issue is that the scholars included in the dataset did not provide informed consent for the use of their data in this research.
+To address this, several measures were implemented.
+First, efforts were made to anonymize the data presented in this study to the greatest extent possible.
+Second, only information directly relevant to the research objectives was collected, minimizing potential intrusions on privacy.
+Third, the scraped data did not include sensitive or harmful content, thereby reducing the risk of any negative consequences arising from its use.
+
+Despite these precautions, the fundamental issue of using non-consensual data persists.
+I do not agree with the view that making data publicly available equates to granting unrestricted permission for its use in research.
+While the data in this study was already accessible online, the research generates new insights, such as patterns of tie formation between scholars, which were not previously explicit.
+Although names and other identifying details have been omitted to avoid recognizing individuals within network graphs or other outputs, informed consent for the use of personal data was not obtained.
+As such, this method of data collection remains ethically contentious at best.
+
+### Operationalization of gender
+
+An additional ethical concern relates to the treatment of gender in this study.
+The method used to infer gender, based on names and a binary framework, may raise issues regarding inclusivity and respect for individuals’ self-identified gender.
+This approach disregards the complexity of gender identity and risks misrepresentation.
+
+# Analysis
+
+To evaluate the homophiliy in collaboration networks by gender and h-index, the analysis of the data will be as follows.
+The first step involves examining descriptive analyses and visualisaitons of the data which will then serve as a foundation for the second phase of the analysis, which focuses on answering the explanatory research question of this study.
+This latter phase investigates the impact of same-gender preference in scholars' collaboration networks and explores the interaction between the gender and h-index of scholars.
+Descriptive analyses will utilize functions of the igraph and ggraph packages, while the explanatory questions will be examined using Stochastic Actor-Based Models implemented via the RSiena package (@igraph, @ggraph, @RSiena_package, @RSiena_manual).
+
+## RSiena
+
+SIENA, which stands for *Simulation Investigation for Empirical Network Analysis*, is a software tool designed to perform statistical estimation of models for longitudinal social network data.
+SIENA version 4.0, also known as RSiena, is a package for the R statistical software and was developed by Ruth Ripley and Krists Boitmanis, in collaboration with Tom Snijders (@RSiena_package, @RSiena_manual).
+The use of RSiena for this project is highly based on the practical information provided in "[Social Network Analysis for Social Scientists](https://jochemtolsma.github.io/SNA-4-Social-Scientists/)**"** (@SNASS).
+
+To ensure the model accurately represents the collaboration network, I developed it iteratively, beginning with a null model (Model 0) and gradually building up to a more comprehensive model (Model 4).
+Each successive model incorporates additional effects, allowing for targeted testing of specific hypotheses.
+The **null model** serves as the foundation and includes only basic structural effects: reciprocity and outdegree (density), as is standard in RSiena.
+This model provides a baseline for comparison but does not address any hypotheses directly.
+The **first model** incorporates additional structural network effects, such as isolates, indegree popularity, and outdegree activity, to examine how these features influence collaboration dynamics.
+This model offers insights into *Hypothesis 3*, as it highlights the structural factors shaping network patterns.
+Building on model 1, this model introduces covariate effects for gender, including ego, alter, and same-gender preferences (sameX), as well as a structural effect for gender-differentiated transitivity (diffXTransTrip).
+By analyzing gender-based network patterns, this model tests *Hypothesis 1*, which focuses on gender homophily.\
+Expanding on model 2, **model 3** incorporates departmental effects, such as ego and alter preferences for department membership, as well as same-department collaboration tendencies (sameX).
+This addition allows for a more nuanced analysis of departmental differences in gender homophily, addressing *Hypothesis 2*.
+The final model (**model 4**) integrates prestige effects through covariate interactions for the h-index, including ego, alter, and indegree popularity weighted by the h-index.
+These additions test *Hypothesis 4*, examining whether prestige moderates gender homophily in collaboration patterns.
+The fit of each model and its relevance interpreting the estimates will be reported in the Analysis chapter and further detailed in the [GOFpart](https://treesdude.github.io/labjournal/finalGOF.html) of this final report webpage.
+
+## Descriptives
+
+**[Revisit and only talk about those that make sense to examine here]**
+
+First, ego-level descriptives such as the counts and distributions of gender and h-indices in both departments were generated to establish a clearer picture of the data at hand.
+
+Then, to identify the presence of clustering and examine whether they are concentrated among individuals with the highest h-index or around specifically gendered scholars, the networks were visualized.
+Further, centrality measures were examined to investigate their correlation to the ego-level variables gender and H-index.
+
+.  Among others, these included the number of nodes, edges, reciprocity, degreee centrality, clustering, density, and path-length. **[INSERT RELEVANT DESCRIPTIVES HERE]**\visualized using graphs
+
+------------------------------------------------------------------------
+
+# <> Ego-Level Descriptives
+Below you can find some descriptive information about the ego-level data after data preparation. For more information, consult the 'data preparation' part of this final report.
+
+**Load data**
+
+Scholar data
+
+```{r scholar data}
+scholars <- fload("./data/processed/scholars_20240924.rda") 
+#make sure to lead fload first of course
+```
+
+```{r saving scholar output}
+# save the output of your function
+test  <- fcolnet(data = scholars, 
+                university = "RU", 
+                discipline = c("sociology", "political science"),
+                waves = list(c(2015, 2018), c(2019, 2023)), 
+                type = c("first"))
+```
+
+Ego data
+
+```{r df_ego data}
+df_ego <- fload("./data/processed/df_ego_20241108.rda")
+```
+
+```{r matrix data ego}
+
+test_w1 <- igraph::graph_from_adjacency_matrix(
+  test$nets[1,,], # first wave of data. 
+  # (thus I select the array of networks and take the first matrix)
+  mode = c("directed"),
+  weighted = NULL,
+  diag = FALSE,
+  add.colnames = NULL,
+  add.rownames = NULL)
+
+```
+
+## Gender - Ego level
+
+Descriptives (mean, distibution, etc.) in whole sample
+
+```{r sum gender, echo=FALSE }
+summary(df_ego$gender)
+```
+
+gender counts across whole sample (0 = female, 1 = male)
+
+```{r counts gender-all, echo=FALSE }
+table(df_ego$gender)
+```
+
+Histogram: overall gender distribution in sample
+
+```{r histogram gender, echo=FALSE }
+# Convert gender to a factor to avoid errors
+df_ego$gender <- as.factor(df_ego$gender)
+# Create the histogram with a dark theme and two colors for bars
+ggplot(df_ego, aes(x = gender, fill = gender)) +
+  geom_bar(color = "darkgrey", width = 0.6) +  # Add borders for bars
+  scale_fill_manual(
+    values = c("0" = "#FFFFB3", "1" = "#80B1D3"),  # Custom colors: yellow for females, blue for males
+    labels = c("Female", "Male")  # Optional: customize legend labels
+  ) +
+  labs(
+    title = "Gender Distribution",
+    x = "Gender\n (0 = female, 1 = male)",
+    y = "Count",
+    fill = "Gender"  # Legend title
+  ) +
+  theme_minimal(base_family = "Arial") +  # Clean, minimal base theme
+  theme(
+    plot.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark background
+    panel.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark panel background
+    panel.grid.major = element_line(color = "#444444"),  # Subtle grid lines
+    panel.grid.minor = element_line(color = "#444444"),
+    axis.text = element_text(color = "#f0f0f0"),  # White axis text
+    axis.title = element_text(color = "#f0f0f0", face = "bold"),  # Bold white axis titles
+    plot.title = element_text(color = "#f0f0f0", face = "bold", hjust = 0.5),  # White centered title
+    legend.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark legend background
+    legend.text = element_text(color = "#f0f0f0"),  # White legend text
+    legend.title = element_text(color = "#f0f0f0")  # White legend title
+    )
+
+```
+
+Genders per department (0 = female, 1 = male)
+
+```{r gender per dep., echo=FALSE }
+
+# Wave 1: Gender count per department 
+table(df_ego$discipline.24, df_ego$gender)
+```
+
+## H index - Ego level
+
+Descriptives (mean, distribution, etc.)
+
+```{r summary h index, echo=FALSE }
+summary(df_ego$h_index)
+```
+
+H-Index Whole sample
+
+```{r hist h index, echo=FALSE }
+# Histogram of prestige scores for Wave 1
+
+# Create a data frame for ggplot2 
+df_h_index <- data.frame(h_index = df_ego$h_index)
+
+# Generate the histogram with ggplot2
+ggplot(df_h_index, aes(x = h_index)) +
+  geom_histogram(
+    bins = 30,
+    fill = "#FFFFB3",  # Bar color
+    color = "black"    # Border color for bars
+  ) +
+  labs(
+    title = "Distribution of H-Index from 2015 to 2018",
+    x = "H Index",
+    y = "Frequency"
+  ) +
+  theme_minimal(base_family = "Arial") +  # Clean, minimal base theme
+  theme(
+    plot.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark background
+    panel.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark panel background
+    panel.grid.major = element_line(color = "#444444"),  # Subtle grid lines
+    panel.grid.minor = element_line(color = "#444444"),
+    axis.text = element_text(color = "#f0f0f0"),  # White axis text
+    axis.title = element_text(color = "#f0f0f0", face = "bold"),  # Bold white axis titles
+    plot.title = element_text(color = "#f0f0f0", face = "bold", hjust = 0.5)  # White centered title
+  )
+
+```
+
+H index per department
+
+```{r table per dep h index, echo=FALSE }
+# Wave 1: Prestige distribution by dep. and total
+df_ego %>%
+    group_by(discipline.24) %>%
+    summarise(mean_h_index = mean(h_index, na.rm = TRUE), min_h_index = min(h_index,
+        na.rm = TRUE), max_h_index = max(h_index, na.rm = TRUE), sd_h_index = sd(h_index,
+        na.rm = TRUE)) %>%
+    bind_rows(df_ego %>%
+        summarise(discipline.24 = "total", mean_h_index = mean(h_index, na.rm = TRUE), min_h_index = min(h_index,
+            na.rm = TRUE), max_h_index = max(h_index, na.rm = TRUE), sd_h_index = sd(h_index,
+            na.rm = TRUE)))
+```
+
 ----

### 2024-11-25 draftdata.Rmd
tryfixpagenorespond

@@
 ---
+
+<html lang="en">
+
+<head>
+
+<meta charset="UTF-8">
+
+<meta name="viewport" content="width=device-width, initial-scale=1.0">
+
+<title>My Descriptives</title>
+
+<link rel="stylesheet" href="styles.css"> <!-- Link to the CSS file I created for dark mode code chunks -->
+
+</head>
+
+</html>
 
@@
 These additions test *Hypothesis 4*, examining whether prestige moderates gender homophily in collaboration patterns.
-The fit of each model and its relevance interpreting the estimates will be reported in the Analysis chapter and further detailed in the [GOFpart](https://treesdude.github.io/labjournal/finalGOF.html) of this final report webpage.
+The fit of each model and its relevance interpreting the estimates will be reported in the Analysis chapter and further detailed in the GOF part of this final report webpage.
 

### 2024-11-25 draftdata.Rmd
whynooooworkstill

@@
 
-<title>My Descriptives</title>
+<title>My Data</title>
 
@@
 </html>
-
-```{=html}
-<style>
-body {
-text-align: left;
-line-height: 1.5;
-}
-
-h1, .h1, h2, .h2, h3, .h3 {
-  margin-top: 24px;
-  line-height: 1;
-}
-
-</style>
-```
 
@@
 The data was scraped from OpenAlex API using the rvest and xml2 packages in R ( @Priem2022, @xml2, @rvest).
-The dependent variable, represented by an *adjacency matrix*, shows whether two actors or writers collaborated on one of their publications in the specified wave.\
+The dependent variable, represented by an *adjacency matrix*, shows whether two actors or writers collaborated on one of their publications in the specified wave.
 Each dyad (author combination) is assessed based on whether they collaborated (1) or not (0) throughout the data period.
 
-**I**n the collboartion networks analysed in this study, ties are described as directional, which implies that they are delivered by one actor and received by another.
+In the collboartion networks analysed in this study, ties are described as directional, which implies that they are delivered by one actor and received by another.
 This means each actor has both outdegrees and indegrees.
@@
 This number can then be used as measure for the author's 'prestige' (@Hirsch2005).
-The number of citations and publications needed for this calculation were webscraped through OpenAlex API (@Priem2022**).** The code for this process was provided by Lucan Bovens.
+The number of citations and publications needed for this calculation were webscraped through OpenAlex API (@Priem2022).
+The code for this process was provided by Lucan Bovens.
 
@@
 
-```{r sum gender, echo=FALSE }
+```{r sum gender, echo=FALSE}
 summary(df_ego$gender)
@@
 
-```{r counts gender-all, echo=FALSE }
+```{r counts gender-all, echo=FALSE}
 table(df_ego$gender)
@@
 
-```{r histogram gender, echo=FALSE }
+```{r histogram gender, echo=FALSE}
 # Convert gender to a factor to avoid errors
@@
 
-```{r gender per dep., echo=FALSE }
+```{r gender per dep., echo=FALSE}
 
@@
 
-```{r summary h index, echo=FALSE }
+```{r summary h index, echo=FALSE}
 summary(df_ego$h_index)
@@
 
-```{r hist h index, echo=FALSE }
+```{r hist h index, echo=FALSE}
 # Histogram of prestige scores for Wave 1
@@
 
-```{r table per dep h index, echo=FALSE }
+```{r table dep h index, echo=FALSE}
 # Wave 1: Prestige distribution by dep. and total

### 2024-11-25 draftdata.Rmd
descriptivescontd

@@
 Histogram: overall gender distribution in sample
-
 ```{r histogram gender, echo=FALSE}
@@
 Genders per department (0 = female, 1 = male)
-
 ```{r gender per dep., echo=FALSE}
-
 # Wave 1: Gender count per department 
@@
 
-## H index - Ego level
+## H-Index - Ego level
 

### 2024-11-25 draftdesresults.Rmd
ypagenorespond
descriptivescontd

@@
 </html>
+
 ```{r setup, include=FALSE}
@@
 
-```{r clean, hide =TRUE}
+```{r clean, echo=FALSE}
 rm(list = ls())
@@
 
-```{r package, hide=TRUE, results='hide'}
+```{r package, hide=TRUE, echo=FALSE}
 require(tidyverse)
@@
 
-```{r functions 1, hide =TRUE, results = 'hide' }
+```{r functions 1, echo=FALSE}
 fpackage.check <- function(packages) {
@@
 More functions
-
-```{r functions 2, hide=TRUE, results ='hide'}
+```{r functions 2, echo=FALSE}
 fcolnet <- function(data = scholars, university = "RU", discipline = "sociology"+"political science", waves = list(c(2015,
@@
 
-```{r scholar data}
+```{r scholar data,echo=FALSE}
 scholars <- fload("./data/processed/scholars_20240924.rda") 
@@
 
-```{r saving scholar output}
+```{r saving scholar output,echo=FALSE}
 # save the output of your function
@@
 
-```{r df_ego data}
+```{r df_ego data,echo=FALSE}
 df_ego <- fload("./data/processed/df_ego_20241108.rda")
@@
 
-```{r matrix data ego}
+# Descriptive Analysis
+
+[For Ego-level descriptives on gender and h-index, please consult the latter part of the Data & Analysis part of this final report]
+
+## Network Description
+
+The network data we are looking at pertains to 101 scholars and their publications.
+In the time frame of the wave at hand, namely form 2015 to 2018, we find 47 edges, with 6 reciprocated collaborations 36 ties that are asymmetric.
+Additionally, there were 5009 occasions in which a ties could have been made but was not.
+The edge density of 0.004 suggests that from all possible edges, this sample contains relatively few.
+
+In terms of triad-configurations, pertaining to the different possibilities three scholars could collaborate, we find that the most common one is no collaboration at all (configuration '003').
+Beyond that, the configuration '012' is also common, meaning that only one directed edge is present in the triad.
+In our sample it is also common for such edge to be reciprocated, as seen in the third-highes-t count of the triad-configuration '102', a graph with a mutual connection between two vertices.
+Overall, the seems to be high number of isolates in the sample network.
+
+## Making graph object
+
+```{r matrix data ego, echo=FALSE}
 
@@
 
-# Network Description
-
-The network data we are looking at pertains to 101 scholars and their publications.
-In the time frame of the wave at hand, namely form 2015 to 2018, we find 47 edges, with 6 reciprocated collaborations 36 ties that are asymmetric.
-Additionally, there were 5009 occasions in which a ties could have been made but was not.
-The edge density of 0.004 suggests that from all possible edges, this sample contains relatively few.
-
-In terms of triad-configurations, pertaining to the different possibilities three scholars could collaborate, we find that the most common one is no collaboration at all (configuration '003').
-Beyond that, the configuration '012' is also common, meaning that only one directed edge is present in the triad.
-In our sample it is also common for such edge to be reciprocated, as seen in the third-highes-t count of the triad-configuration '102', a graph with a mutual connection between two vertices.
-Overall, the seems to be high number of isolates in the sample network.
-
 ## Nr. of nodes/vertices
 
-```{r nodes}
+```{r nodes, echo=FALSE}
 vcount(test_w1)
@@
 
-```{r edges}
+```{r edges, echo=FALSE}
 ecount(test_w1)
@@
 
-```{r dyad cen}
+```{r dyad cen, echo=FALSE}
 igraph::dyad_census(test_w1)
@@
 
-```{r triad cen}
+```{r triad cen, echo=FALSE}
 igraph::triad_census(test_w1)
@@
 
-```{r edge dens}
+```{r edge dens, echo=FALSE}
 # edge density
@@
 Degree centrality, often simply called 'degree', measures the number of connections a scholar, or ego, has with other scholars, known as alters.
-In the context of our dataset, we distinguish between two types of degrees: incoming connections (indegrees) and outgoing connections (outdegrees).
+Here, we distinguish between two types of degrees: incoming connections (indegrees) and outgoing connections (outdegrees).
 Indegrees represent ties directed toward the ego, which in this case signify instances where the ego is **not** the primary author of a paper.
@@
 
-```{r degree}
+```{r degree, echo=FALSE}
 # Calculate degree centrality
@@
 
-```{r betweenness}
+```{r betweenness, echo=FALSE}
 # Calculate betweenness centrality
@@
 
-```{r}
+```{r, echo=FALSE}
 # Clustering the wave 
@@
 ```
-
-## Segregation ?
-
-# Plots
+## Network Plots

### 2024-11-25 draftdesresults.Rmd
finaldesresultsandgof

@@
 More functions
+
 ```{r functions 2, echo=FALSE}
@@
 
-[For Ego-level descriptives on gender and h-index, please consult the latter part of the Data & Analysis part of this final report]
+The network statistics, and descriptives, just as visualizations of the collaboration network can be found on this page.
+For Ego-level descriptives on gender and h-index, please consult the latter part of the Data & Analysis part of this final report.
+
+------------------------------------------------------------------------
 
@@
 
-## Making graph object
+Degree centrality, often simply called 'degree', measures the number of connections a scholar, or ego, has with other scholars, known as alters.
+Here, we distinguish between two types of degrees: incoming connections (indegrees) and outgoing connections (outdegrees).
+Indegrees represent ties directed toward the ego, which in this case signify instances where the ego is **not** the primary author of a paper.
+Conversely, outdegrees represent ties originating from the ego, indicating collaborations where the ego assumes the role of the first author.
+From the histograms below we can already observe patterns of clustering in terms of scholars' publications, as only very few vertices have many infegrees, while most vertices have a low number of indegrees.
+Hence, there seems to be a skew in collaboration ties.
 
-```{r matrix data ego, echo=FALSE}
+**Making graph object**
 
+```{r matrix data ego}
 test_w1 <- igraph::graph_from_adjacency_matrix(
@@
   add.rownames = NULL)
-
 ```
 
-## Nr. of nodes/vertices
+### Nr. of nodes/vertices
 
@@
 
-## Nr. of edges
+### Nr. of edges
 
@@
 
-## Dyad census
+### Dyad census
 
@@
 
-## Triad-census
+### Triad-census
 
@@
 ```
-## Edge-density
+### Edge-density
 
@@
 
-## Degree centrality
+### Degree centrality
 
-Degree centrality, often simply called 'degree', measures the number of connections a scholar, or ego, has with other scholars, known as alters.
-Here, we distinguish between two types of degrees: incoming connections (indegrees) and outgoing connections (outdegrees).
-Indegrees represent ties directed toward the ego, which in this case signify instances where the ego is **not** the primary author of a paper.
-Conversely, outdegrees represent ties originating from the ego, indicating collaborations where the ego assumes the role of the first author.
+(with isolates)
 
@@
 
-The indegree distribution is right-skewed. This suggests that only very few vertices have many infegrees, and that most vertices have a low number of indegrees.
-
-## Betweenness Centrality
+### Betweenness Centrality
 
@@
 
-## Clustering
+### Clustering
+
+(with isolates)
 
@@
 ```
-## Network Plots
+
+------------------------------------------------------------------------
+
+## Network Visualization (WITHOUT isolates)
+
+The isolates of the network have been removed to allow for a better readability of the graphs.
+Only vertices with edges remain part of the visualizations.
+In other words, only scholars with collaborations are seen in the following graphs.
+It should be noted that this may make the graphs look different and potentially makes the networks seems more well connected than they actually are.
+Nonetheless, some things stand out upon first glance.
+Consult the texts below for a more detailed description.
+
+**Removing isolates** Remaining edges and vertices:
+
+```{r removing isolates, echo=FALSE}
+indegr_w1 <- igraph::degree(test_w1, mode = "in")
+
+isolates_w1 <- V(test_w1)[degree(test_w1, mode = "all") == 0]
+
+noisolates_w1 <- delete_vertices(test_w1, isolates_w1)
+
+gsize(noisolates_w1) # edges
+gorder(noisolates_w1) # vertices 
+```
+
+### Gender
+
+```{r plot wo isolates, echo=FALSE}
+plot(noisolates_w1,
+  vertex.color = ifelse(df_ego$gender == 1, "#80B1D3", "#FFED6F"), # now, I can use actor attributes for plotting.
+  # here: if gender = 1 (aka man) then blue dot, if not then yellow
+  vertex.label = NA,
+  vertex.size = 9,
+  vertex.frame.color = "black",
+  edge.curved = 0.1,
+  edge.arrow.size = 0.5,
+  edge.color = "#999999",
+  edge.width = 0.5,
+  main = "Network without isolates [yellow = female, blue = male]",
+  asp=0)
+```
+
+In this network visualization yellow nodes represent women, while blue nodes represent men.
+We find some clusters of blue nodes, which suggests that clustering based on scholars' gender might be present in their collaboration preferences.
+However, these patterns do not stand out as drastically as they could upon first glance.
+
+### Gender & Department (indegree)
+
+```{r without iso gender per dep old code, echo=FALSE}
+# assign gender to scholar
+V(test_w1)$gender <- df_ego$gender
+
+# assign disciplines to scholars
+V(test_w1)$discipline <- df_ego$discipline.24
+V(test_w1)$indegree <- indegr_w1
+
+# remove isolates
+noisolates_w1 <- delete_vertices(test_w1, V(test_w1)[degree(test_w1) == 0])
+
+p_noisgender <- ggraph(noisolates_w1, layout = "fr") + geom_edge_link(end_cap = circle(4, 'mm'),color = "#D9D9D9", width = 0.7, arrow = arrow(length = unit(2, "mm")), type = "closed") +
+    geom_node_point(aes(size = indegree, color = as.factor(discipline), shape = as.factor(gender))) +
+    scale_size(range = c(3, 10)) + theme_void() +   theme(
+    plot.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark background
+    panel.background = element_rect(fill = "#2d2d2d", color = NA),
+    text = element_text(color = "#f0f0f0")  # White text
+  )
+
+p_noisgender + labs(title = "Departments without isolates", subtitle = "Plot of indegree and gender",
+    caption = "Gender: 0 = female, 1 = male.\n Data refer to scholars from Radboud University.") + theme(plot.title = element_text(hjust = 0.5, face = "bold", color = "#f0f0f0"), plot.subtitle = element_text(hjust = 0.5, color = "#f0f0f0"), plot.caption = element_text(hjust = 1, color = "#f0f0f0"))
+```
+
+In the graph above, the size of a node represents their indegree, the color represents their belonging to a department (red = political science, blue = sociology), and the shape represents the gender (circle = woman, triangle = man).
+Focusing on department, represented by the colors, we can see a clear difference between the indegrees of the two departments.
+However, there seems to be very few scholars of the political science department in the non-isolate network to begin with.
+This may explain some of the later findings.
+
+### Gender & H-index (indegree)
+
+```{r dark g&h without iso, echo=FALSE}
+#assign gender to scholar 
+V(test_w1)$gender <- df_ego$gender
+
+# assign h-index to scholar
+V(test_w1)$h_index <- df_ego$h_index
+V(test_w1)$indegree <- indegr_w1
+
+#remove isolates
+noisolates_w1 <- delete_vertices(test_w1, V(test_w1)[degree(test_w1) == 0])
+
+p_noisogender <- ggraph(noisolates_w1,
+  layout = "fr") +
+  geom_edge_link(end_cap = circle(3, 'mm'),color = "#D9D9D9", width = 0.7, arrow = arrow(length = unit(1.75, "mm"), type = "closed")) +  # Darker edge color
+  geom_node_point(aes(size = indegree, color = h_index, shape = as.factor(gender))) +   
+  scale_size(range = c(3, 10)) + 
+  scale_color_gradient(low = "#F6222E", high = "#3283FE") +  # Retain original gradient
+  theme_void() +
+  theme(
+    plot.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark background
+    panel.background = element_rect(fill = "#2d2d2d", color = NA),
+    text = element_text(color = "#f0f0f0")  # White text
+  )
+
+p_noisogender + labs(title = "Network without isolates",
+        subtitle = "Plot of indegree, H-index and gender",
+        caption = "Gender: 0 = female, 1 = male.\n Data refer to: Scholars RU sociology and political science departments.") +   
+  theme(plot.title = element_text(hjust = 0.5, face = "bold", color = "#f0f0f0"), plot.subtitle = element_text(hjust = 0.5, color = "#f0f0f0"), plot.caption = element_text(hjust = 1, color = "#f0f0f0"))
+
+```
+
+In this graph, the colour gradient from blue to red indicates the prestige of a scholar, with blue marking the highest h-index and red marking the lowest.
+The size represents the indegrees that node has, which refers to the number of collaboration that other scholars initiated with this scholar within the time span of 2015-2018.
+The shape represents scholars' gender with triangles representing men and circles representing women.
+With regard to H-index, we observe that the nodes with colors that are more blue are simultaneously also the biggest ones, indicating that scholars with high H-Indeces also have more indegrees and that clustering may be present based on scholars' prestige.
+In terms of gender difference, we see that those aformentioned nodes are also mostly triangular in shape, which signals that the men in this non-isolate sample seem to have an overall higher h-index and high number of indegress.
+This implies that clustering in collaborations is present and seems to relate to both scholars' prestige and gender.

### 2024-11-25 finalGOF.Rmd
finaldesresultsandgof

@@
 
-```{r, hide = TRUE}
+```{r, hide = TRUE, echo=FALSE}
 Model0.1 <- fload("./data/processed/estimated_M0.1_20241123.rda")
@@
 
-```{r GOF M0, hide = TRUE}
+```{r GOF M0, hide = TRUE,echo=FALSE}
 GOF_M0.1 <- sienaGOF(Model0.1, IndegreeDistribution, verbose = FALSE, join = TRUE, varName = "nets")
@@
 
-```{r, hide = TRUE}
+```{r, hide = TRUE, echo=FALSE}
 Model1.1 <- fload("./data/processed/estimated_M1.1_20241123.rda")
@@
 
-```{r GOF M1, hide = TRUE}
+```{r GOF M1, hide = TRUE, echo=FALSE}
 GOF_M1.1 <- sienaGOF(Model1.1, IndegreeDistribution, verbose = FALSE, join = TRUE, varName = "nets")
@@
 
-```{r, hide = TRUE}
+```{r, hide = TRUE, echo=FALSE}
 Model2.1 <- fload ("./data/processed/estimated_M2.1_20241123.rda")
@@
 
-```{r GOF M2, hide = TRUE}
+```{r GOF M2, hide = TRUE, echo=FALSE}
 GOF_M2.1 <- sienaGOF(Model2.1, IndegreeDistribution, verbose = FALSE, join = TRUE, varName = "nets")
@@
 
-```{r, hide=TRUE}
+```{r, hide=TRUE, echo=FALSE}
 Model3 <- fload("./data/processed/estimated_M3_20241123.rda")
@@
 
-```{r GOF M3, hide=TRUE}
+```{r GOF M3, hide=TRUE, echo=FALSE}
 GOF_M3 <- sienaGOF(Model3, IndegreeDistribution, verbose = FALSE, join = TRUE, varName = "nets")
@@
 
-```{r, hide=TRUE}
+```{r, hide=TRUE, echo=FALSE}
 Model4 <- fload("./data/processed/estimated_M4_20241123.rda")
@@
 
-```{r GOF M4, hide=TRUE}
+```{r GOF M4, hide=TRUE, echo=FALSE}
 GOF_M4 <- sienaGOF(Model4, IndegreeDistribution, verbose = FALSE, join = TRUE, varName = "nets")

### 2024-11-25 finaldata.Rmd
whynooooworkstill
finaldesresultsandgof

--- 2024-11-24 finaldata.Rmd
@@
 ---
-title: "Data & Methods"
+title: "Data & Analysis"
 author: "Verooo"
-date: "2024-11-23"
+date: "2024-11-25"
 output: html_document
@@
 csl: apa.csl
+editor_options: 
+  markdown: 
+    wrap: 72
 ---
-```{=html}
-<style>
-body {
-text-align: left;
-line-height: 1.5;
-}
 
-h1, .h1, h2, .h2, h3, .h3 {
-  margin-top: 24px;
-  line-height: 1;
-}
+<html lang="en">
 
-</style>
+<head>
+
+<meta charset="UTF-8">
+
+<meta name="viewport" content="width=device-width, initial-scale=1.0">
+
+<title>My Models</title>
+
+<link rel="stylesheet" href="styles.css">
+<!-- Link to the CSS file I created for dark mode code chunks -->
+
+</head>
+
+</html>
+
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = TRUE)
 ```
@@
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
-
-```
+This work?

### 2024-11-25 finaldesresults.Rmd
finaldesresultsandgof

@@
 ---
-```{=html}
-<style>
-body {
-text-align: left;
-line-height: 1.5;
-}
 
-h1, .h1, h2, .h2, h3, .h3 {
-  margin-top: 24px;
-  line-height: 1;
-}
+<html lang="en">
 
-</style>
-```
+<head>
+
+<meta charset="UTF-8">
+
+<meta name="viewport" content="width=device-width, initial-scale=1.0">
+
+<title>My Descriptive Results</title>
+
+<link rel="stylesheet" href="styles.css"> <!-- Link to the CSS file I created for dark mode code chunks -->
+
+</head>
+
+</html>
 
@@
 ```
+
+# Getting started
+
+```{r clean, echo=FALSE}
+rm(list = ls())
+```
+
+## Packages
+
+```{r package, hide=TRUE, echo=FALSE}
+require(tidyverse)
+require(RSiena)
+require(RsienaTwoStep)
+
+#install.packages("data.table")
+require(data.table)  # mainly for faster data handling
+# install.packages('xml2')
+require(xml2)
+# install.packages('rvest')
+require(rvest)
+require(igraph)
+require(ggraph)
+require(ggplot2)
+
+#install.packages('visNetwork')
+require(visNetwork)
+#install.packages('threejs')
+require(threejs)
+#install.packages('networkD3')
+require(networkD3)
+
+require(RColorBrewer)
+
+```
+
+## Functions
+
+Functions chunk
+
+```{r functions 1, echo=FALSE}
+fpackage.check <- function(packages) {
+    lapply(packages, FUN = function(x) {
+        if (!require(x, character.only = TRUE)) {
+            install.packages(x, dependencies = TRUE)
+            library(x, character.only = TRUE)
+        }
+    })
+}
+
+fsave <- function(x, file = NULL, location = "./data/processed/") {
+    ifelse(!dir.exists("data"), dir.create("data"), FALSE)
+    ifelse(!dir.exists("data/processed"), dir.create("data/processed"), FALSE)
+    if (is.null(file))
+        file = deparse(substitute(x))
+    datename <- substr(gsub("[:-]", "", Sys.time()), 1, 8)
+    totalname <- paste(location, file, "_", datename, ".rda", sep = "")
+    save(x, file = totalname)  #need to fix if file is reloaded as input name, not as x. 
+}
+
+fload <- function(filename) {
+    load(filename)
+    get(ls()[ls() != "filename"])
+}
+
+fshowdf <- function(x, ...) {
+    knitr::kable(x, digits = 2, "html", ...) %>%
+        kableExtra::kable_styling(bootstrap_options = c("striped", "hover")) %>%
+        kableExtra::scroll_box(width = "100%", height = "300px")
+}
+
+# this is the most important one. We created it in the previous script
+
+f_pubnets <- function(df_scholars = df, list_publications = publications, discip = "sociology"+"political science", affiliation = "RU",
+    waves = list(wave1 = c(2018, 2019, 2020), wave2 = c(2021, 2022, 2023))) {
+
+    publications <- list_publications %>%
+        bind_rows() %>%
+        distinct(title, .keep_all = TRUE)
+
+    df_scholars %>%
+        filter(affil1 == affiliation | affil2 == affiliation) %>%
+        filter(discipline == discip) -> df_sel
+
+    networklist <- list()
+    for (wave in 1:length(waves)) {
+        networklist[[wave]] <- matrix(0, nrow = nrow(df_sel), ncol = nrow(df_sel))
+    }
+
+    publicationlist <- list()
+    for (wave in 1:length(waves)) {
+        publicationlist[[wave]] <- publications %>%
+            filter(gs_id %in% df_sel$gs_id) %>%
+            filter(year %in% waves[[wave]]) %>%
+            select(author) %>%
+            lapply(str_split, pattern = ",")
+    }
+
+    publicationlist2 <- list()
+    for (wave in 1:length(waves)) {
+        publicationlist2[[wave]] <- publicationlist[[wave]]$author %>%
+            # lowercase
+        lapply(tolower) %>%
+            # Removing diacritics
+        lapply(stri_trans_general, id = "latin-ascii") %>%
+            # only last name
+        lapply(word, start = -1, sep = " ") %>%
+            # only last last name
+        lapply(word, start = -1, sep = "-")
+    }
+
+    for (wave in 1:length(waves)) {
+        # let us remove all publications with only one author
+        remove <- which(sapply(publicationlist2[[wave]], FUN = function(x) length(x) == 1) == TRUE)
+        publicationlist2[[wave]] <- publicationlist2[[wave]][-remove]
+    }
+
+    for (wave in 1:length(waves)) {
+        pubs <- publicationlist2[[wave]]
+        for (ego in 1:nrow(df_sel)) {
+            # which ego?
+            lastname_ego <- df_sel$lastname[ego]
+            # for all publications
+            for (pub in 1:length(pubs)) {
+                # only continue if ego is author of pub
+                if (lastname_ego %in% pubs[[pub]]) {
+                  aut_pot <- which.max(pubs[[pub]] %in% lastname_ego)
+                  # only continue if ego is first author of pub
+                  if (aut_pot == 1) {
+                    # check all alters/co-authors
+                    for (alter in 1:nrow(df_sel)) {
+                      # which alter
+                      lastname_alter <- df_sel$lastname[alter]
+                      if (lastname_alter %in% pubs[[pub]]) {
+                        networklist[[wave]][ego, alter] <- networklist[[wave]][ego, alter] + 1
+                      }
+                    }
+                  }
+                }
+            }
+        }
+    }
+    return(list(df = df_sel, network = networklist))
+}
+
+```
+
+More functions
+
+```{r functions 2, echo=FALSE}
+fcolnet <- function(data = scholars, university = "RU", discipline = "sociology"+"political science", waves = list(c(2015,
+    2018), c(2019, 2023)), type = c("first")) {
+
+    # step 1
+    demographics <- do.call(rbind.data.frame, data$demographics)
+    demographics <- demographics %>%
+        mutate(Universiteit1.22 = replace(Universiteit1.22, is.na(Universiteit1.22), ""), Universiteit2.22 = replace(Universiteit2.22,
+            is.na(Universiteit2.22), ""), Universiteit1.24 = replace(Universiteit1.24, is.na(Universiteit1.24),
+            ""), Universiteit2.24 = replace(Universiteit2.24, is.na(Universiteit2.24), ""), discipline.22 = replace(discipline.22,
+            is.na(discipline.22), ""), discipline.24 = replace(discipline.24, is.na(discipline.24), ""))
+
+    sample <- which((demographics$Universiteit1.22 %in% university | demographics$Universiteit2.22 %in%
+        university | demographics$Universiteit1.24 %in% university | demographics$Universiteit2.24 %in%
+        university) & (demographics$discipline.22 %in% discipline | demographics$discipline.24 %in% discipline))
+
+    demographics_soc <- demographics[sample, ]
+    scholars_sel <- lapply(scholars, "[", sample)
+
+    # step 2
+    ids <- demographics_soc$au_id
+    nwaves <- length(waves)
+    nets <- array(0, dim = c(nwaves, length(ids), length(ids)), dimnames = list(wave = 1:nwaves, ids,
+        ids))
+    dimnames(nets)
+
+    # step 3
+    df_works <- tibble(works_id = unlist(lapply(scholars_sel$work, function(l) l$id)), works_author = unlist(lapply(scholars_sel$work,
+        function(l) l$author), recursive = FALSE), works_year = unlist(lapply(scholars_sel$work, function(l) l$publication_year),
+        recursive = FALSE))
+
+    df_works <- df_works[!duplicated(df_works), ]
+
+    # step 4
+    if (type == "first") {
+        for (j in 1:nwaves) {
+            df_works_w <- df_works[df_works$works_year >= waves[[j]][1] & df_works$works_year <= waves[[j]][2],
+                ]
+            for (i in 1:nrow(df_works_w)) {
+                ego <- df_works_w$works_author[i][[1]]$au_id[1]
+                alters <- df_works_w$works_author[i][[1]]$au_id[-1]
+                if (sum(ids %in% ego) > 0 & sum(ids %in% alters) > 0) {
+                  nets[j, which(ids %in% ego), which(ids %in% alters)] <- 1
+                }
+            }
+        }
+    }
+
+    if (type == "last") {
+        for (j in 1:nwaves) {
+            df_works_w <- df_works[df_works$works_year >= waves[[j]][1] & df_works$works_year <= waves[[j]][2],
+                ]
+            for (i in 1:nrow(df_works_w)) {
+                ego <- rev(df_works_w$works_author[i][[1]]$au_id)[1]
+                alters <- rev(df_works_w$works_author[i][[1]]$au_id)[-1]
+                if (sum(ids %in% ego) > 0 & sum(ids %in% alters) > 0) {
+                  nets[j, which(ids %in% ego), which(ids %in% alters)] <- 1
+                }
+            }
+        }
+    }
+
+    if (type == "all") {
+        for (j in 1:nwaves) {
+            df_works_w <- df_works[df_works$works_year >= waves[[j]][1] & df_works$works_year <= waves[[j]][2],
+                ]
+            for (i in 1:nrow(df_works_w)) {
+                egos <- df_works_w$works_author[i][[1]]$au_id
+                if (sum(ids %in% egos) > 0) {
+                  nets[j, which(ids %in% egos), which(ids %in% egos)] <- 1
+                }
+            }
+        }
+    }
+    output <- list()
+    output$data <- scholars_sel
+    output$nets <- nets
+    return(output)
+}
+```
+
+## Load data
+
+Scholar data
+
+```{r scholar data,echo=FALSE}
+scholars <- fload("./data/processed/scholars_20240924.rda") 
+#make sure to lead fload first of course
+```
+
+```{r saving scholar output,echo=FALSE}
+# save the output of your function
+
+test  <- fcolnet(data = scholars, 
+                university = "RU", 
+                discipline = c("sociology", "political science"),
+                waves = list(c(2015, 2018), c(2019, 2023)), 
+                type = c("first"))
+```
+
+Ego data
+
+```{r df_ego data,echo=FALSE}
+df_ego <- fload("./data/processed/df_ego_20241108.rda")
+
+```
+
+---
+---
+---
+
+# Descriptive Analysis
+
+The network statistics, and descriptives, just as visualizations of the collaboration network can be found on this page.
+For Ego-level descriptives on gender and h-index, please consult the latter part of the Data & Analysis part of this final report.
+
+------------------------------------------------------------------------
+
+## Network Description
+
+The network data we are looking at pertains to 101 scholars and their publications.
+In the time frame of the wave at hand, namely form 2015 to 2018, we find 47 edges, with 6 reciprocated collaborations 36 ties that are asymmetric.
+Additionally, there were 5009 occasions in which a ties could have been made but was not.
+The edge density of 0.004 suggests that from all possible edges, this sample contains relatively few.
+
+In terms of triad-configurations, pertaining to the different possibilities three scholars could collaborate, we find that the most common one is no collaboration at all (configuration '003').
+Beyond that, the configuration '012' is also common, meaning that only one directed edge is present in the triad.
+In our sample it is also common for such edge to be reciprocated, as seen in the third-highes-t count of the triad-configuration '102', a graph with a mutual connection between two vertices.
+Overall, the seems to be high number of isolates in the sample network.
+
+Degree centrality, often simply called 'degree', measures the number of connections a scholar, or ego, has with other scholars, known as alters.
+Here, we distinguish between two types of degrees: incoming connections (indegrees) and outgoing connections (outdegrees).
+Indegrees represent ties directed toward the ego, which in this case signify instances where the ego is **not** the primary author of a paper.
+Conversely, outdegrees represent ties originating from the ego, indicating collaborations where the ego assumes the role of the first author.
+From the histograms below we can already observe patterns of clustering in terms of scholars' publications, as only very few vertices have many infegrees, while most vertices have a low number of indegrees.
+Hence, there seems to be a skew in collaboration ties.
+
+**Making graph object**
+
+```{r matrix data ego}
+test_w1 <- igraph::graph_from_adjacency_matrix(
+  test$nets[1,,], # first wave of data. 
+  # (thus I select the array of networks and take the first matrix)
+  mode = c("directed"),
+  weighted = NULL,
+  diag = FALSE,
+  add.colnames = NULL,
+  add.rownames = NULL)
+```
+
+### Nr. of nodes/vertices
+
+```{r nodes, echo=FALSE}
+vcount(test_w1)
+```
+
+### Nr. of edges
+
+```{r edges, echo=FALSE}
+ecount(test_w1)
+```
+
+### Dyad census
+
+```{r dyad cen, echo=FALSE}
+igraph::dyad_census(test_w1)
+```
+
+### Triad-census
+
+```{r triad cen, echo=FALSE}
+igraph::triad_census(test_w1)
+```
+
+### Edge-density
+
+```{r edge dens, echo=FALSE}
+# edge density
+igraph::edge_density(test_w1)
+```
+
+### Degree centrality
+
+(with isolates)
+
+```{r degree, echo=FALSE}
+# Calculate degree centrality
+degree_testw1 <- degree(test_w1)
+degree_testw1 <- as.data.frame(degree_testw1)
+
+ggplot(degree_testw1, aes(x = as.numeric(degree_testw1))) +
+  geom_histogram(binwidth = 0.9, fill = "#FFFFB3", color = "black") +  
+  labs(
+    title = "Distribution Degrees Wave 1",
+    x = "Distribution of Degrees",
+    y = "Count"
+  ) +
+  ylim(0, 15) +  # Set y-axis limits 
+  theme_minimal(base_family = "Arial") +  # Minimal, clean base theme
+  theme(
+    plot.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark background
+    panel.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark panel background
+    panel.grid.major = element_line(color = "#444444"),  # Subtle grid lines
+    panel.grid.minor = element_line(color = "#444444"),
+    axis.text = element_text(color = "#f0f0f0"),  # White axis text
+    axis.title = element_text(color = "#f0f0f0", face = "bold"),  # Bold white axis titles
+    plot.title = element_text(color = "#f0f0f0", face = "bold", hjust = 0.5),  # White centered title
+    legend.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark legend background
+    legend.text = element_text(color = "#f0f0f0")  # White legend text
+  ) +
+  guides(fill = "none")  # Remove the legend
+
+```
+
+<!-- ylim was 65 at some point priot due to one higher bar, I wonder what changed since... -->
+
+### Betweenness Centrality
+
+(with isolates)
+
+```{r betweenness, echo=FALSE}
+# Calculate betweenness centrality
+betweenness_w1 <- igraph::betweenness(test_w1, directed = TRUE)
+betweenness_w1 <- as.data.frame(betweenness_w1)
+
+ggplot(betweenness_w1, aes(as.numeric(betweenness_w1), colour = as.numeric(betweenness_w1))) +
+  geom_histogram(binwidth = 1.2, fill = "#FFFFB3") +
+  labs(
+    title = "Distribution Betweenness Wave 1",
+    x = "Distribution of Betweenness",
+    y = "Count") +
+   theme_minimal(base_family = "Arial") +  # Minimal, clean base theme
+  theme(
+    plot.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark background
+    panel.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark panel background
+    panel.grid.major = element_line(color = "#444444"),  # Subtle grid lines
+    panel.grid.minor = element_line(color = "#444444"),
+    axis.text = element_text(color = "#f0f0f0"),  # White axis text
+    axis.title = element_text(color = "#f0f0f0", face = "bold"),  # Bold white axis titles
+    plot.title = element_text(color = "#f0f0f0", face = "bold", hjust = 0.5),  # White centered title
+    legend.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark legend background
+    legend.text = element_text(color = "#f0f0f0")  # White legend text
+  ) +
+  guides(fill = guide_legend(title = "Betweenness (rounded)"))  # Customize legend
+
+```
+
+### Clustering
+
+(with isolates)
+
+```{r, echo=FALSE}
+# Clustering the wave 
+clustering_w1 <- igraph::transitivity(test_w1, type = "local")
+clustering_w1 <- as.data.frame(clustering_w1)
+
+# Generate the dark mode plot with a single color fill
+ggplot(clustering_w1, aes(x = as.numeric(clustering_w1))) +
+   geom_histogram(binwidth = 0.05, fill = "#FFFFB3", color = "black", position = "dodge") +  
+  labs(
+    title = "Distribution Clustering Wave 1",
+    x = "Distribution of Clustering",
+    y = "Count"
+  ) +
+  theme_minimal(base_family = "Arial") +  # Clean, minimal base theme
+  theme(
+    plot.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark background
+    panel.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark panel background
+    panel.grid.major = element_line(color = "#444444"),  # Subtle grid lines
+    panel.grid.minor = element_line(color = "#444444"),
+    axis.text = element_text(color = "#f0f0f0"),  # White axis text
+    axis.title = element_text(color = "#f0f0f0", face = "bold"),  # Bold white axis titles
+    plot.title = element_text(color = "#f0f0f0", face = "bold", hjust = 0.5),  # White centered title
+    legend.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark legend background
+    legend.text = element_text(color = "#f0f0f0")  # White legend text
+  ) + guides(fill = "none")  # Remove the legend (since all bars are the same color)
+
+```
+
+------------------------------------------------------------------------
+
+## Network Visualization (WITHOUT isolates)
+
+The isolates of the network have been removed to allow for a better readability of the graphs.
+Only vertices with edges remain part of the visualizations.
+In other words, only scholars with collaborations are seen in the following graphs.
+It should be noted that this may make the graphs look different and potentially makes the networks seems more well connected than they actually are.
+Nonetheless, some things stand out upon first glance.
+Consult the texts below for a more detailed description.
+
+**Removing isolates**
+
+```{r removing isolates, echo=TRUE}
+indegr_w1 <- igraph::degree(test_w1, mode = "in")
+
+isolates_w1 <- V(test_w1)[degree(test_w1, mode = "all") == 0]
+
+noisolates_w1 <- delete_vertices(test_w1, isolates_w1)
+
+```
+
+Remaining edges and vertices:
+
+```{r, echo=FALSE}
+gsize(noisolates_w1) # edges
+gorder(noisolates_w1) # vertices
+```
+
+### Gender
+
+```{r plot wo isolates, echo=FALSE}
+plot(noisolates_w1,
+  vertex.color = ifelse(df_ego$gender == 1, "#80B1D3", "#FFED6F"), # now, I can use actor attributes for plotting.
+  # here: if gender = 1 (aka man) then blue dot, if not then yellow
+  vertex.label = NA,
+  vertex.size = 9,
+  vertex.frame.color = "black",
+  edge.curved = 0.1,
+  edge.arrow.size = 0.5,
+  edge.color = "#999999",
+  edge.width = 0.5,
+  main = "Network without isolates [yellow = female, blue = male]",
+  asp=0)
+```
+
+In this network visualization yellow nodes represent women, while blue nodes represent men.
+We find some clusters of blue nodes, which suggests that clustering based on scholars' gender might be present in their collaboration preferences.
+However, these patterns do not stand out as drastically as they could upon first glance.
+
+### Gender & Department (indegree)
+
+```{r without iso gender per dep old code, echo=FALSE}
+# assign gender to scholar
+V(test_w1)$gender <- df_ego$gender
+
+# assign disciplines to scholars
+V(test_w1)$discipline <- df_ego$discipline.24
+V(test_w1)$indegree <- indegr_w1
+
+# remove isolates
+noisolates_w1 <- delete_vertices(test_w1, V(test_w1)[degree(test_w1) == 0])
+
+p_noisgender <- ggraph(noisolates_w1, layout = "fr") + geom_edge_link(end_cap = circle(4, 'mm'),color = "#D9D9D9", width = 0.7, arrow = arrow(length = unit(2, "mm")), type = "closed") +
+    geom_node_point(aes(size = indegree, color = as.factor(discipline), shape = as.factor(gender))) +
+    scale_size(range = c(3, 10)) + theme_void() +   theme(
+    plot.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark background
+    panel.background = element_rect(fill = "#2d2d2d", color = NA),
+    text = element_text(color = "#f0f0f0")  # White text
+  )
+
+p_noisgender + labs(title = "Departments without isolates", subtitle = "Plot of indegree and gender",
+    caption = "Gender: 0 = female, 1 = male.\n Data refer to scholars from Radboud University.") + theme(plot.title = element_text(hjust = 0.5, face = "bold", color = "#f0f0f0"), plot.subtitle = element_text(hjust = 0.5, color = "#f0f0f0"), plot.caption = element_text(hjust = 1, color = "#f0f0f0"))
+```
+
+In the graph above, the size of a node represents their indegree, the color represents their belonging to a department (red = political science, blue = sociology), and the shape represents the gender (circle = woman, triangle = man).
+Focusing on department, represented by the colors, we can see a clear difference between the indegrees of the two departments.
+However, there seems to be very few scholars of the political science department in the non-isolate network to begin with.
+This may explain some of the later findings.
+
+### Gender & H-index (indegree)
+
+```{r dark g&h without iso, echo=FALSE}
+#assign gender to scholar 
+V(test_w1)$gender <- df_ego$gender
+
+# assign h-index to scholar
+V(test_w1)$h_index <- df_ego$h_index
+V(test_w1)$indegree <- indegr_w1
+
+#remove isolates
+noisolates_w1 <- delete_vertices(test_w1, V(test_w1)[degree(test_w1) == 0])
+
+p_noisogender <- ggraph(noisolates_w1,
+  layout = "fr") +
+  geom_edge_link(end_cap = circle(3, 'mm'),color = "#D9D9D9", width = 0.7, arrow = arrow(length = unit(1.75, "mm"), type = "closed")) +  # Darker edge color
+  geom_node_point(aes(size = indegree, color = h_index, shape = as.factor(gender))) +   
+  scale_size(range = c(3, 10)) + 
+  scale_color_gradient(low = "#F6222E", high = "#3283FE") +  # Retain original gradient
+  theme_void() +
+  theme(
+    plot.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark background
+    panel.background = element_rect(fill = "#2d2d2d", color = NA),
+    text = element_text(color = "#f0f0f0")  # White text
+  )
+
+p_noisogender + labs(title = "Network without isolates",
+        subtitle = "Plot of indegree, H-index and gender",
+        caption = "Gender: 0 = female, 1 = male.\n Data refer to: Scholars RU sociology and political science departments.") +   
+  theme(plot.title = element_text(hjust = 0.5, face = "bold", color = "#f0f0f0"), plot.subtitle = element_text(hjust = 0.5, color = "#f0f0f0"), plot.caption = element_text(hjust = 1, color = "#f0f0f0"))
+
+```
+
+In this graph, the colour gradient from blue to red indicates the prestige of a scholar, with blue marking the highest h-index and red marking the lowest.
+The size represents the indegrees that node has, which refers to the number of collaboration that other scholars initiated with this scholar within the time span of 2015-2018.
+The shape represents scholars' gender with triangles representing men and circles representing women.
+With regard to H-index, we observe that the nodes with colors that are more blue are simultaneously also the biggest ones, indicating that scholars with high H-Indeces also have more indegrees and that clustering may be present based on scholars' prestige.
+In terms of gender difference, we see that those aformentioned nodes are also mostly triangular in shape, which signals that the men in this non-isolate sample seem to have an overall higher h-index and high number of indegress.
+This implies that clustering in collaborations is present and seems to relate to both scholars' prestige and gender.

### 2024-11-25 finalestimate.Rmd
finaldesresultsandgof

@@
 csl: apa.csl
+editor_options: 
+  markdown: 
+    wrap: 72
 ---
-```{=html}
-<style>
-body {
-text-align: left;
-line-height: 1.5;
-}
 
-h1, .h1, h2, .h2, h3, .h3 {
-  margin-top: 24px;
-  line-height: 1;
-}
+<html lang="en">
 
-</style>
-```
+<head>
+
+<meta charset="UTF-8">
+
+<meta name="viewport" content="width=device-width, initial-scale=1.0">
+
+<title>My Models</title>
+
+<link rel="stylesheet" href="styles.css">
+<!-- Link to the CSS file I created for dark mode code chunks -->
+
+</head>
+
+</html>
 
@@
 ```
+
+# Setup
+
+Clean workspace. As always.
+
+```{r clean, echo=FALSE}
+rm(list = ls())
+```
+
+## Packages
+
+```{r package, include=TRUE, echo=FALSE, eval=TRUE}
+require(tidyverse)
+require(RSiena)
+require(RsienaTwoStep)
+
+#install.packages("data.table")
+require(data.table)  # mainly for faster data handling
+# install.packages('xml2')
+require(xml2)
+# install.packages('rvest')
+require(rvest)
+require(igraph)
+require(ggraph)
+
+#install.packages('visNetwork')
+require(visNetwork)
+#install.packages('threejs')
+require(threejs)
+#install.packages('networkD3')
+require(networkD3)
+
+```
+
+## Functions
+
+```{r functions 1, echo=FALSE}
+fpackage.check <- function(packages) {
+    lapply(packages, FUN = function(x) {
+        if (!require(x, character.only = TRUE)) {
+            install.packages(x, dependencies = TRUE)
+            library(x, character.only = TRUE)
+        }
+    })
+}
+
+fsave <- function(x, file = NULL, location = "./data/processed/") {
+    ifelse(!dir.exists("data"), dir.create("data"), FALSE)
+    ifelse(!dir.exists("data/processed"), dir.create("data/processed"), FALSE)
+    if (is.null(file))
+        file = deparse(substitute(x))
+    datename <- substr(gsub("[:-]", "", Sys.time()), 1, 8)
+    totalname <- paste(location, file, "_", datename, ".rda", sep = "")
+    save(x, file = totalname)  #need to fix if file is reloaded as input name, not as x. 
+}
+
+fload <- function(filename) {
+    load(filename)
+    get(ls()[ls() != "filename"])
+}
+
+fshowdf <- function(x, ...) {
+    knitr::kable(x, digits = 2, "html", ...) %>%
+        kableExtra::kable_styling(bootstrap_options = c("striped", "hover")) %>%
+        kableExtra::scroll_box(width = "100%", height = "300px")
+}
+
+# this is the most important one. We created it in the previous script
+
+f_pubnets <- function(df_scholars = df, list_publications = publications, discip = "sociology"+"political science", affiliation = "RU",
+    waves = list(wave1 = c(2018, 2019, 2020), wave2 = c(2021, 2022, 2023))) {
+
+    publications <- list_publications %>%
+        bind_rows() %>%
+        distinct(title, .keep_all = TRUE)
+
+    df_scholars %>%
+        filter(affil1 == affiliation | affil2 == affiliation) %>%
+        filter(discipline == discip) -> df_sel
+
+    networklist <- list()
+    for (wave in 1:length(waves)) {
+        networklist[[wave]] <- matrix(0, nrow = nrow(df_sel), ncol = nrow(df_sel))
+    }
+
+    publicationlist <- list()
+    for (wave in 1:length(waves)) {
+        publicationlist[[wave]] <- publications %>%
+            filter(gs_id %in% df_sel$gs_id) %>%
+            filter(year %in% waves[[wave]]) %>%
+            select(author) %>%
+            lapply(str_split, pattern = ",")
+    }
+
+    publicationlist2 <- list()
+    for (wave in 1:length(waves)) {
+        publicationlist2[[wave]] <- publicationlist[[wave]]$author %>%
+            # lowercase
+        lapply(tolower) %>%
+            # Removing diacritics
+        lapply(stri_trans_general, id = "latin-ascii") %>%
+            # only last name
+        lapply(word, start = -1, sep = " ") %>%
+            # only last last name
+        lapply(word, start = -1, sep = "-")
+    }
+
+    for (wave in 1:length(waves)) {
+        # let us remove all publications with only one author
+        remove <- which(sapply(publicationlist2[[wave]], FUN = function(x) length(x) == 1) == TRUE)
+        publicationlist2[[wave]] <- publicationlist2[[wave]][-remove]
+    }
+
+    for (wave in 1:length(waves)) {
+        pubs <- publicationlist2[[wave]]
+        for (ego in 1:nrow(df_sel)) {
+            # which ego?
+            lastname_ego <- df_sel$lastname[ego]
+            # for all publications
+            for (pub in 1:length(pubs)) {
+                # only continue if ego is author of pub
+                if (lastname_ego %in% pubs[[pub]]) {
+                  aut_pot <- which.max(pubs[[pub]] %in% lastname_ego)
+                  # only continue if ego is first author of pub
+                  if (aut_pot == 1) {
+                    # check all alters/co-authors
+                    for (alter in 1:nrow(df_sel)) {
+                      # which alter
+                      lastname_alter <- df_sel$lastname[alter]
+                      if (lastname_alter %in% pubs[[pub]]) {
+                        networklist[[wave]][ego, alter] <- networklist[[wave]][ego, alter] + 1
+                      }
+                    }
+                  }
+                }
+            }
+        }
+    }
+    return(list(df = df_sel, network = networklist))
+}
+
+```
+
+```{r functions 2, echo=FALSE}
+fcolnet <- function(data = scholars, university = "RU", discipline = "sociology"+"political science", waves = list(c(2015,
+    2018), c(2019, 2023)), type = c("first")) {
+
+    # step 1
+    demographics <- do.call(rbind.data.frame, data$demographics)
+    demographics <- demographics %>%
+        mutate(Universiteit1.22 = replace(Universiteit1.22, is.na(Universiteit1.22), ""), Universiteit2.22 = replace(Universiteit2.22,
+            is.na(Universiteit2.22), ""), Universiteit1.24 = replace(Universiteit1.24, is.na(Universiteit1.24),
+            ""), Universiteit2.24 = replace(Universiteit2.24, is.na(Universiteit2.24), ""), discipline.22 = replace(discipline.22,
+            is.na(discipline.22), ""), discipline.24 = replace(discipline.24, is.na(discipline.24), ""))
+
+    sample <- which((demographics$Universiteit1.22 %in% university | demographics$Universiteit2.22 %in%
+        university | demographics$Universiteit1.24 %in% university | demographics$Universiteit2.24 %in%
+        university) & (demographics$discipline.22 %in% discipline | demographics$discipline.24 %in% discipline))
+
+    demographics_soc <- demographics[sample, ]
+    scholars_sel <- lapply(scholars, "[", sample)
+
+    # step 2
+    ids <- demographics_soc$au_id
+    nwaves <- length(waves)
+    nets <- array(0, dim = c(nwaves, length(ids), length(ids)), dimnames = list(wave = 1:nwaves, ids,
+        ids))
+    dimnames(nets)
+
+    # step 3
+    df_works <- tibble(works_id = unlist(lapply(scholars_sel$work, function(l) l$id)), works_author = unlist(lapply(scholars_sel$work,
+        function(l) l$author), recursive = FALSE), works_year = unlist(lapply(scholars_sel$work, function(l) l$publication_year),
+        recursive = FALSE))
+
+    df_works <- df_works[!duplicated(df_works), ]
+
+    # step 4
+    if (type == "first") {
+        for (j in 1:nwaves) {
+            df_works_w <- df_works[df_works$works_year >= waves[[j]][1] & df_works$works_year <= waves[[j]][2],
+                ]
+            for (i in 1:nrow(df_works_w)) {
+                ego <- df_works_w$works_author[i][[1]]$au_id[1]
+                alters <- df_works_w$works_author[i][[1]]$au_id[-1]
+                if (sum(ids %in% ego) > 0 & sum(ids %in% alters) > 0) {
+                  nets[j, which(ids %in% ego), which(ids %in% alters)] <- 1
+                }
+            }
+        }
+    }
+
+    if (type == "last") {
+        for (j in 1:nwaves) {
+            df_works_w <- df_works[df_works$works_year >= waves[[j]][1] & df_works$works_year <= waves[[j]][2],
+                ]
+            for (i in 1:nrow(df_works_w)) {
+                ego <- rev(df_works_w$works_author[i][[1]]$au_id)[1]
+                alters <- rev(df_works_w$works_author[i][[1]]$au_id)[-1]
+                if (sum(ids %in% ego) > 0 & sum(ids %in% alters) > 0) {
+                  nets[j, which(ids %in% ego), which(ids %in% alters)] <- 1
+                }
+            }
+        }
+    }
+
+    if (type == "all") {
+        for (j in 1:nwaves) {
+            df_works_w <- df_works[df_works$works_year >= waves[[j]][1] & df_works$works_year <= waves[[j]][2],
+                ]
+            for (i in 1:nrow(df_works_w)) {
+                egos <- df_works_w$works_author[i][[1]]$au_id
+                if (sum(ids %in% egos) > 0) {
+                  nets[j, which(ids %in% egos), which(ids %in% egos)] <- 1
+                }
+            }
+        }
+    }
+    output <- list()
+    output$data <- scholars_sel
+    output$nets <- nets
+    return(output)
+}
+```
+
+## Get Data
+
+Load Scholar Data
+
+```{r scholar data}
+scholars <- fload("./data/processed/scholars_20240924.rda") 
+```
+
+Save the output of the function.
+
+```{r saving output}
+# save the output of your function
+test  <- fcolnet(data = scholars, 
+                university = "RU", 
+                discipline = c("sociology", "political science"),
+                waves = list(c(2015, 2018), c(2019, 2023)), 
+                type = c("first"))
+```
+
+Load Ego Data
+
+```{r df_ego data, include= FALSE}
+df_ego <- fload("./data/processed/df_ego_20241108.rda")
+
+```
+
+# Make Network Data
+
+```{r RSiena network data}
+#step1 data
+wave1 <- test$nets[1,,]
+wave2 <- test$nets[2,,]
+
+# put nets in an array
+net_array <- array(data = c(wave1, wave2), dim = c(dim(wave1), 2))
+
+```
+
+------------------------------------------------------------------------
+
+# Analysis - Model Estimation
+
+## \<\> Model 0 - Null Model
+
+First, I estimated a null model with only reciprocity and degree. The
+maximum convergence ratio of the model is 0.084. The GOF on the Indegree
+Distribution is zero**.** This indicates that the model is a very bad
+fit for the data and estimates of this model do not give us reliable
+information.\
+\
+*For all GOF plots compiled in one place, see here:
+<https://treesdude.github.io/labjournal/finalGOF.html>.*
+
+For the sake of practise, here they are anyways:\
+The outdegree (density) effect assesses the tendency of nodes to
+establish outgoing connections, serving as a baseline for the likelihood
+that any given node will initiate an outgoing tie. In the context of
+this study, these outgoing ties represent the initiation of
+co-publications. The outdegree estimate is significant and negative (b =
+-2.6388, SE = 0.1460), suggesting that a scholar's tendency to initiate
+collaboration is low and dense networks are less sought after. The
+reciprocity parameter id significant and positive (b = 1.8035, SE =
+0.4343), which implies that directed ties are likely to be reciprocated.
+Specific to our case, it describes that scholars tend to initiate
+collaborations with those alters who sent a tie to them too.
+
+### ---Step 1: Define Siena Data & Variables
+
+```{r RSiena define m0}
+# dependent variable 
+nets <- sienaDependent(net_array)
+
+# define data object 
+mydata_M0 <- sienaDataCreate(nets)
+
+```
+
+Print short descriptive report
+
+```{r}
+ifelse(!dir.exists("results"), dir.create("results"), FALSE)
+
+```
+
+```{r}
+print01Report(mydata_M0, modelname = "./results/results_M0") # create file with report in results folder 
+```
+
+### ---Step 2: Make effects object/structure
+
+```{r RSiena myeff M0}
+# define effects structure 
+myeff_M0 <- getEffects(mydata_M0)
+
+```
+
+### ---Step 3: Add Effects
+
+Null model: none.
+
+### ---Step 4: Specify model/algorithm
+
+```{r algo M0}
+
+myAlgorithm_M0 <- sienaAlgorithmCreate (projname = "results_M0")
+
+```
+
+### ---Step 5: Estimate model
+
+```{r estimate M0, eval=FALSE}
+# estimate the model 
+Model0 <- siena07(myAlgorithm_M0, data = mydata_M0, effects = myeff_M0, returnDeps = TRUE)
+Model0
+
+fsave(Model0, file ="estimated_M0")
+```
+
+```{r load M0 output, echo=FALSE}
+Model0 <- fload("./data/processed/estimated_M0_20241123.rda")
+Model0
+```
+
+```{r GOF M0}
+GOF_M0 <- sienaGOF(Model0, IndegreeDistribution, verbose = FALSE, join = TRUE, varName = "nets")
+
+plot(GOF_M0, main = 'GOF - "Null" Model 0 \n Indegree Distribution')
+```
+
+------------------------------------------------------------------------
+
+## \<\> Model 1 - Structural Effects
+
+This model additionally entails InPop, outAct, isolateNet to control for
+effects of network statistics. The maximum convergence ratio of this
+model is **0.17** and a Goodness of Fit on the indegree distribution is
+**0.002.** Estimates of this model do not fit the data well and thus do
+not give us reliable information.
+
+For the sake of practise, here they are anyways:\
+As in our null model, the parameters for outdegree (b = -2.0862, SE =
+0.7050) and reciprocity (b = 1.0894, SE = 0.4144) remain significant and
+unchanged on their 'direction'. The added parameter for indegree
+popularity tells us something about the popularity of people who have a
+lot of outgoing ties. In our model the estimate for this parameter is
+significantly positive (b =0.2549, SE =0.0439), suggesting that scholars
+specifically like to initiate collaborations with those who have a lot
+of indegrees.
+
+Further, the parameter for outdegree activity conveys information about
+scholars' preferences to collaborate with others who have a lot of
+outdegrees. In our case, the estimate is insignificant and cannot be
+reliably interpreted. Lastly, the network isolate parameter can be used
+to infer about scholars' tendency to neither send nor receive ties. The
+estimate for this parameter is significantly positive (b = 4.9645, SE =
+1.1146) in our model, indicating that the scholars of our sample tend to
+remain isolates.
+
+### ---Step 1: Define Siena Data & Variables
+
+```{r RSiena define M1}
+# dependent variable 
+nets <- sienaDependent(net_array)
+
+# define data object 
+mydata_M1 <- sienaDataCreate(nets)
+
+```
+
+```{r, echo=FALSE}
+# make folder 
+ifelse(!dir.exists("results"), dir.create("results"), FALSE)
+
+```
+
+```{r,echo=FALSE}
+#Print short descriptive report
+print01Report(mydata_M1, modelname = "./results/results_M1") 
+```
+
+### ---Step 2: Make effects object/structure
+
+```{r RSiena myeff m1}
+# define effects structure 
+myeff_M1 <- getEffects(mydata_M1)
+
+```
+
+### ---Step 3: Add Effects
+
+```{r effects m1}
+
+myeff_M1 <- includeEffects(myeff_M1, isolateNet, inPop, outAct)
+
+```
+
+### ---Step 4: Specify model/algorithm
+
+```{r algo m1}
+
+myAlgorithm_M1 <- sienaAlgorithmCreate (projname = "results_M1")
+
+```
+
+### ---Step 5: Estimate model
+
+```{r estimate m1, eval = FALSE}
+# estimate the model 
+Model1 <- siena07(myAlgorithm_M1, data = mydata_M1, effects = myeff_M1, returnDeps = TRUE)
+Model1
+# maximum convergence >.25
+# run again:
+Model1.1 <- siena07(myAlgorithm_M1, data = mydata_M1, effects = myeff_M1, prevAns= Model1, returnDeps = TRUE)
+Model1.1
+
+#fsave(Model1, file ="estimated_M1")
+#fsave(Model1.1, file = "estimated_M1.1")
+
+```
+
+```{r load M1 output, echo=FALSE}
+
+Model1 <- fload("./data/processed/estimated_M1_20241123.rda")
+Model1
+
+Model1.1 <- fload("./data/processed/estimated_M1.1_20241123.rda")
+Model1.1
+```
+
+### ---Step 6: GOF - Goodness of Fit
+
+```{r GOF M1}
+GOF_M1.1 <- sienaGOF(Model1.1, IndegreeDistribution, verbose = FALSE, join = TRUE, varName = "nets")
+
+plot(GOF_M1.1, main = "GOF - Model 1 \n Indegree Distribution")
+```
+
+------------------------------------------------------------------------
+
+## \<\> Model 2 - Gender
+
+This model is partly similar to Model 1 but additionally holds the
+network statistics sameX, diffXTransTrip, egoX & altX of the covariate
+gender. EgoX and AltX ought to indicate whether male or female scholars
+are more likely to initiate or receive ties, while sameX models the
+general tendency for scholars to collaborate with same-gender peers. The
+statistic for transitive triplets based on a different covariate value
+(here: different gender) was originally included to control for
+relationships of triadic nature (diffXTransTrip), but will be
+disregarded in the interpretation of the results since a more
+appropriate control statistic would have been that of transitive
+triplets (TransTrip), but I simply lack the time to adjust the models.
+
+The maximum convergence ratio for model 2 is **0.132** and the Goodness
+of Fit on the indegree distribution is **0.096**. Looking at our
+'base-line' network statistics, it is noteworthy that the estimate for
+Outdegree is not significant anymore. This statistic's prior
+significance can seemingly be explained by a parameter relating to the
+covariate gender that I added to this model. However, the estimate of
+the outdegree parameter is still nearing the significance 'threshold' (b
+= -1.8628, SE = 1.1060, b/SE = -1.684268).
+
+Comparing this model to the prior ones, we see that the reciprocity
+estimate is still significantly positive (b = 1.3341, SE = 0.4543). The
+parameters of the structural network statistics also show similar
+patterns in estimates and significance as they did in model 1.
+Concerning the added covariate "gender", we find that the parameter
+estimates for both covariate-related activity (egoX) , pertaining to the
+gender of the ego, and covariate-related popularity (altX), relating to
+the gender of the alter, do **not** show any significance and hence do
+not allow for reliable inferences. The 'same-covariate' measure (sameX)
+for gender is significantly positive (b = 0.6637, SE =0.2685). It
+reveals that scholars, indeed, prefer same-gender collaborators. This
+supports H1, which posits gender homophily in collaboration patterns.
+
+Model 2 provides strong evidence for gender homophily (H1), with
+scholars more likely to collaborate with same-gender peers, but no
+significant differences in collaboration tendencies based on the gender
+of ego or alter.
+
+### ---Step 1: Define Siena Data & Variables
+
+```{r RSiena define m2}
+# dependent variable 
+nets <- sienaDependent(net_array)
+
+# put gender in object 
+gender <- df_ego$gender
+
+# covariate 1
+gender_RS <- coCovar(gender) # gender as covariate in Rsiena
+
+# define data object 
+mydata_M2 <- sienaDataCreate(nets, gender_RS)
+
+```
+
+Print short descriptive report
+
+```{r, echo=FALSE}
+ifelse(!dir.exists("results"), dir.create("results"), FALSE)
+
+```
+
+```{r, echo=FALSE}
+print01Report(mydata_M2, modelname = "./results/results_M2") # create file with report in results folder 
+```
+
+### ---Step 2: Make effects object/structure
+
+```{r RSiena myeff m2}
+# define effects structure 
+myeff_M2 <- getEffects(mydata_M2)
+```
+
+### ---Step 3: Add Effects
+
+```{r effects m2}
+myeff_M2 <- includeEffects(myeff_M2, isolateNet, inPop, outAct)
+
+myeff_M2 <- includeEffects(myeff_M2, egoX, altX, diffXTransTrip, sameX, interaction1 = "gender_RS") 
+```
+
+### ---Step 4: Specify model/algorithm
+
+```{r algo m2}
+
+myAlgorithm_M2 <- sienaAlgorithmCreate (projname = "results_M2")
+
+```
+
+### ---Step 5: Estimate model
+
+```{r estimate m2, eval =FALSE}
+# estimate the model 
+Model2 <- siena07(myAlgorithm_M2, data = mydata_M2, effects = myeff_M2, returnDeps = TRUE)
+Model2
+# maximum convergence >.25
+# run again:
+Model2.1 <- siena07(myAlgorithm_M2, data = mydata_M2, effects = myeff_M2, prevAns= Model2, returnDeps = TRUE)
+Model2.1
+
+#fsave(Model2, file ="estimated_M2")
+#fsave(Model2.1, file = "estimated_M2.1")
+
+```
+
+```{r load M2 output, echo=FALSE}
+
+Model2 <- fload("./data/processed/estimated_M2_20241123.rda")
+Model2
+
+Model2.1 <- fload ("./data/processed/estimated_M2.1_20241123.rda")
+Model2.1
+```
+
+### ---Step 6: GOF - Goodness of Fit
+
+```{r GOF M2}
+GOF_M2.1 <- sienaGOF(Model2.1, IndegreeDistribution, verbose = FALSE, join = TRUE, varName = "nets")
+
+plot(GOF_M2.1, main = "GOF - Model 2 \n Indegree Distribution")
+```
+
+------------------------------------------------------------------------
+
+## \<\> Model 3 - Department
+
+This model is partly similar to Model 2 but additionally holds the
+network statistics egoX and altX for the main effect of department, to
+investigate differences in same-gender collaboration patterns based on
+the two departments.
+
+Originally, I planned to also include an interaction term of departm_RS
+and gender_RS to obtain clearer insights into variations in patterns of
+gender homophily in relation to scholars' departments. However, I have
+refrained from adding another model to this project. I decided against
+this partly due to time constraints but I also reason that I can use the
+comparison of model 2 and 3 to examine changes in the estimate of
+'sameX' (gender), to *tentatively* infer whether the department of
+scholars modifies the collaboration patterns at hand.
+
+Model 3 has a maximum convergence ratio of **0.182** and a Goodness of
+Fit on the indegree distribution of **0.108**.
+
+Interestingly, the estimate for outdegree (density) that had lost its
+significance in model 2, is now back to being significant and negative
+(b = -4.3233, SE = 1.0871).
+
+In terms of estimate size and significance of the structural network
+statistics we, once again, find similar patterns as in models 1 and 2.
+However, the outdegree parameter has now reached significance (b =
+-4.3233, SE = 1.0871).
+
+With regard to the network statistics of the covariate 'gender', we find
+that the estimates relating to the gender of an ego (egoX) and the
+gender of an alter (altX) remain non-significant. The parameter
+estimates for sameX remains significantly positive (b = 0.6632, SE =
+0.2623) and are almost identical to those of model 2 (b = 0.6632, SE =
+0.2623). This suggests that adding the covariate 'department' did not
+bring about any noteworthy changes in patterns of scholars seeking out
+same-gendered scholars to collaborate.
+
+When it comes to the parameters pertaining to the added covariate
+'department', we find that any differences in collaboration based on the
+department of an ego (egoX) or of an alter (altX) are not warranted, as
+the estimates of these parameters are insignificant. However, we find a
+significantly positive estimate for the parameter of 'covariate-related
+identity' (sameX), which indicates that scholars are more likely to
+collaborate with people from their own department, indicating
+**department-based homophily**. (b = 2.7240, SE = 0.7277).
+
+Model 3 highlights persistent gender homophily (H1) across departments
+but does not provide evidence for differences in gender homophily
+between Sociology and Political Science, contrary to H2.
+
+### ---Step 1: Define Siena Data & Variables
+
+```{r RSiena define m3}
+# dependent variable 
+nets <- sienaDependent(net_array)
+
+# put gender in object 
+gender <- df_ego$gender
+
+# covariate 1
+gender_RS <- coCovar(gender) # gender as covariate in Rsiena
+
+#put department in object 
+department <- factor(df_ego$discipline.24, levels = c("sociology", "political science"))
+#make numeric
+department_numeric <- as.numeric(department) - 1 # sociology = 0, political science = 1
+# covariate 2
+departm_RS <- coCovar(department_numeric)
+
+# define data object 
+mydata_M3 <- sienaDataCreate(nets, gender_RS, departm_RS)
+
+```
+
+```{r, echo=FALSE}
+#create folder
+ifelse(!dir.exists("results"), dir.create("results"), FALSE)
+
+```
+
+```{r, echo=FALSE}
+#Print short descriptive report
+print01Report(mydata_M3, modelname = "./results/results_M3") #
+```
+
+### ---Step 2: Make effects object/structure
+
+```{r RSiena myeff m3}
+# define effects structure 
+myeff_M3 <- getEffects(mydata_M3)
+```
+
+### ---Step 3: Add Effects
+
+```{r effects m3}
+myeff_M3 <- includeEffects(myeff_M3, isolateNet, inPop, outAct) # model 1
+
+myeff_M3 <- includeEffects(myeff_M3, egoX, altX, diffXTransTrip, sameX, interaction1 = "gender_RS") #model 2
+
+myeff_M3 <- includeEffects(myeff_M3, egoX, altX, sameX, interaction1 = "departm_RS") #model 3
+
+```
+
+### ---Step 4: Specify model/algorithm
+
+```{r algo m3}
+
+myAlgorithm_M3 <- sienaAlgorithmCreate (projname = "results_M3")
+
+```
+
+### ---Step 5: Estimate model
+
+```{r estimate m3, eval =FALSE}
+# estimate the model 
+Model3 <- siena07(myAlgorithm_M3, data = mydata_M3, effects = myeff_M3, returnDeps = TRUE)
+Model3
+
+#if maximum convergence >.25: run again
+Model3.1 <- siena07(myAlgorithm_M3, data = mydata_M3, effects = myeff_M3, prevAns= Model3, returnDeps = TRUE)
+Model3.1
+
+#fsave(Model3, file ="estimated_M3")
+#fsave(Model3.1, file = "estimated_M3.1")
+
+```
+
+```{r load M3 output, echo=FALSE}
+
+Model3 <- fload("./data/processed/estimated_M3_20241123.rda")
+Model3
+
+Model3.1 <- fload ("./data/processed/estimated_M3.1_20241123.rda")
+Model3.1
+```
+
+### ---Step 6: GOF - Goodness of Fit
+
+```{r GOF M3}
+GOF_M3.1 <- sienaGOF(Model3.1 , IndegreeDistribution, verbose = FALSE, join = TRUE, varName = "nets")
+
+plot(GOF_M3.1, main = "GOF - Model 3 \n Indegree Distribution")
+```
+
+------------------------------------------------------------------------
+
+## \<\> Model 4 - H-Index
+
+This model further builds on the prior model and also includes network
+statistics of the covariate H-Index, namely egoX, altX and inPopX. By
+adding these effects we can model how the h-index of a scholar
+influences their preferences regarding same-gendered collaborations.
+Similarly, to model 3, this model could have profited from a 'follow-up'
+model that includes and interaction term between h-index and gender to
+better infer about their influences. The same reasoning for my decision
+to stick with one model prior also applies to this case. EgoX for this
+covariate examines how the h-index of a scholar affects their
+collaboration behavior, while AltX examines how the h-index of potential
+collaborators affects their attractiveness as partners. With the help of
+these effects we can test prestigious scholars are more likely to
+initiate or receive ties. By looking at in-degree popularity weighted by
+sender’s H-index (inPopX) we can assess whether a high h-index increases
+the likelihood of being sought out as a collaborator.
+
+Model 4 has a maximum convergence ratio of **0.23,** and a a Goodness of
+Fit on the indegree distribution of **0.197**.
+
+**Structural network statistics.** The estimate for outdegree is
+negative but not significant. This suggests that, after accounting for
+other variables, the baseline likelihood of forming ties remains low and
+is not a major driver of collaboration patterns. Reciprocity has a
+significant positive estimate (b = 2.1770, SE = 0.5960). This reflects a
+strong tendency for mutual collaborations, meaning if one scholar
+collaborates with another, the latter is likely to collaborate back
+(dyadic reciprocity). The paramters Indegree Popularity and Outdegree
+Activity are both insignificant, suggesting that neither the tendency to
+receive many collaborations (indegree popularity) nor the tendency to
+initiate them (outdegree activity) is significantly relevant to the
+network structure. The network isolate estimate is, once again,
+significantly positive ( b = 5.4634, SE = 2.2770), indicating that as
+isolates tend to remain isolated.
+
+**Gender.** Similar to AltX and EgoX in prior models, both an alter's
+gender (b = -0.0903, SE = 0.3372) and an ego's gender (b = 0.2993, SE =
+0.4934) still have insignificant effects. The parameter SameX shows a
+significant positive estimate (b = 0.6820, SE = 0.2804) which barely
+differs from the two prior models. This suggests that adding the
+covariate 'H-Index' did not prompt any major changes in scholars'
+preferences for same-gendered collaborators.
+
+**Department.** While an alter's departmen**t** (AltX) remained
+insignificant to the collaboration patterns, the estimates for an ego's
+department changed incomparison to the prior model. In this model, egoX
+seems to be of significant relevance (b = -1.4652, SE = 0.6963), with
+its negative estimate indicating that, once effects of h-index are
+controlled for, scholars from the political science (coded as 1)
+department have a lower tendency to initiate collaborations than
+scholars from the sociology department (coded as 0).\
+Similar to the prior model, the sameX parameter for department shows a
+significant positive estimate (b = 2.6327, SE = 0.6080) scholars are
+still more likely to collaborate with others from the same department.
+
+**H-Index**. Both an alter's and an ego's H-Index seem to be relevant in
+collaboration preferences. The significant and positive estimateof AltX
+(b = 0.0829, SE = 0.0364) suggest that scholars with higher h-index are
+more preferred as collaborators. The egoX estimate is significant and
+negative (b = -0.1591, SE = 0.0744) suggesting that scholars with higher
+h-index are less likely to initiate collaborations.
+
+The results partially support **H4**, as the h-index is shown to
+influence collaboration patterns, with prestigious scholars being more
+likely to attract collaborations as alters but less likely to initiate
+them as egos. However, gender homophily remains significant even after
+controlling for the h-index, suggesting that prestige does not
+substantially weaken the influence of gender homophily in co-authorship
+networks.
+
+### ---Step 1: Define Siena Data & Variables
+
+```{r RSiena define m4}
+# dependent variable 
+nets <- sienaDependent(net_array)
+
+# put gender in object 
+gender <- df_ego$gender
+# covariate 1
+gender_RS <- coCovar(gender) # gender as covariate in Rsiena
+
+#put department in object 
+department <- factor(df_ego$discipline.24, levels = c("sociology", "political science"))
+#make numeric
+department_numeric <- as.numeric(department) - 1 # sociology = 0, political science = 1
+# covariate 2
+departm_RS <- coCovar(department_numeric)
+
+# put h-index in object 
+h_index <- df_ego$h_index
+df_ego$h_index
+# covariate 3
+h_index_RS <- coCovar(h_index) # h_index as covariate in RSiena
+
+# define data object 
+mydata_M4 <- sienaDataCreate(nets, gender_RS, departm_RS, h_index_RS)
+
+```
+
+```{r, echo=FALSE}
+#create folder
+ifelse(!dir.exists("results"), dir.create("results"), FALSE)
+
+```
+
+```{r, echo=FALSE}
+#Print short descriptive report
+print01Report(mydata_M4, modelname = "./results/results_M4") 
+```
+
+### ---Step 2: Make effects object/structure
+
+```{r RSiena myeff M4}
+
+# define effects structure 
+myeff_M4 <- getEffects(mydata_M4)
+
+```
+
+### ---Step 3: Add Effects
+
+```{r effects M4}
+
+myeff_M4 <- includeEffects(myeff_M4, isolateNet, inPop, outAct) # model 1
+
+myeff_M4 <- includeEffects(myeff_M4, egoX, altX, diffXTransTrip, sameX, interaction1 = "gender_RS") #model 2
+
+myeff_M4 <- includeEffects(myeff_M4, egoX, altX, sameX, interaction1 = "departm_RS") #model 3
+
+myeff_M4 <- includeEffects(myeff_M4, egoX, altX, inPopX, interaction1 = "h_index_RS") # model 4
+
+```
+
+### ---Step 4: Specify model/algorithm
+
+```{r algo M4}
+
+myAlgorithm_M4 <- sienaAlgorithmCreate (projname = "results_M4")
+
+```
+
+### ---Step 5: Estimate model
+
+```{r estimate M4, eval =FALSE}
+# estimate the model 
+Model4 <- siena07(myAlgorithm_M4, data = mydata_M4, effects = myeff_M4, returnDeps = TRUE)
+Model4
+
+#fsave(Model4, file ="estimated_M4")
+
+```
+
+```{r load M4 output, echo=FALSE}
+
+Model4 <- fload("./data/processed/estimated_M4_20241123.rda")
+Model4
+
+```
+
+### ---Step 6: GOF - Goodness of Fit
+
+```{r GOF M4}
+GOF_M4 <- sienaGOF(Model4, IndegreeDistribution, verbose = FALSE, join = TRUE, varName = "nets")
+
+plot(GOF_M4, main = "GOF - Model 4 \n Indegree Distribution")
+```

### 2024-11-25 draftdata.Rmd
finaldatatrytofixplsplsplsplsplswork

@@
 
-## Getting started
+# Getting started
 
@@
 
-### Packages
+## Packages
 
@@
 
-### Functions
+## Functions
 
@@
 
+------------------------------------------------------------------------
+
+------------------------------------------------------------------------
+
 # Data
@@
 
+------------------------------------------------------------------------
+
+------------------------------------------------------------------------
+
 # Analysis
@@
 
-**[Revisit and only talk about those that make sense to examine here]**
+First, ego-level descriptives such as the counts and distributions of gender and h-indices in both departments were generated to establish a clearer picture of the data at hand.
+Consult them below on this page.
+Then, several statistics describing the network were generated, including measures such as the number of nodes, edges, reciprocity, degreee centrality, clustering to investigate the structure of the network further.
+Lastly, to better identify the presence of clustering in the collaboration network and examine whether such patterns occur in connection with scholars' gender or h-index, the networks were visualized.
+The description of the latter two approaches is found under "Descriptive Analysis" in this final report.
 
-First, ego-level descriptives such as the counts and distributions of gender and h-indices in both departments were generated to establish a clearer picture of the data at hand.
-
-Then, to identify the presence of clustering and examine whether they are concentrated among individuals with the highest h-index or around specifically gendered scholars, the networks were visualized.
-Further, centrality measures were examined to investigate their correlation to the ego-level variables gender and H-index.
-
-.  Among others, these included the number of nodes, edges, reciprocity, degreee centrality, clustering, density, and path-length. **[INSERT RELEVANT DESCRIPTIVES HERE]**\visualized using graphs
+------------------------------------------------------------------------
 

### 2024-11-25 finaldata.Rmd
finaldatatrytofixplsplsplsplsplswork

--- 2024-11-25 finaldata.Rmd
@@
 author: "Verooo"
-date: "2024-11-23"
+date: "2024-11-25"
 output: html_document
@@
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+<!-- This work? -->
 
-```
-
-# Data
-
-## Getting started
+# Getting started
 
@@
 
+------------------------------------------------------------------------
+
+------------------------------------------------------------------------
+
+# Data
+
 ## Sample data
@@
 This approach disregards the complexity of gender identity and risks misrepresentation.
+
+------------------------------------------------------------------------
+
+------------------------------------------------------------------------
 
@@
 
-**[Revisit and only talk about those that make sense to examine here]**
-
 First, ego-level descriptives such as the counts and distributions of gender and h-indices in both departments were generated to establish a clearer picture of the data at hand.
-
-Then, to identify the presence of clustering and examine whether they are concentrated among individuals with the highest h-index or around specifically gendered scholars, the networks were visualized.
-Further, centrality measures were examined to investigate their correlation to the ego-level variables gender and H-index.
-
-.  Among others, these included the number of nodes, edges, reciprocity, degreee centrality, clustering, density, and path-length. **[INSERT RELEVANT DESCRIPTIVES HERE]**\visualized using graphs
+Consult them below on this page.
+Then, several statistics describing the network were generated, including measures such as the number of nodes, edges, reciprocity, degreee centrality, clustering to investigate the structure of the network further.
+Lastly, to better identify the presence of clustering in the collaboration network and examine whether such patterns occur in connection with scholars' gender or h-index, the networks were visualized.
+The description of the latter two approaches is found under "Descriptive Analysis" in this final report.
 
@@
 
-# <> Ego-Level Descriptives
+------------------------------------------------------------------------
+
+# Ego-Level Descriptives
 Below you can find some descriptive information about the ego-level data after data preparation. For more information, consult the 'data preparation' part of this final report.
@@
 Histogram: overall gender distribution in sample
-
-```{r histogram gender, echo=FALSE }
+```{r histogram gender, echo=FALSE}
 # Convert gender to a factor to avoid errors
@@
 Genders per department (0 = female, 1 = male)
-
-```{r gender per dep., echo=FALSE }
-
+```{r gender per dep., echo=FALSE}
 # Wave 1: Gender count per department 
@@
 
-----
+------------------------------------------------------------------------
+
+------------------------------------------------------------------------
 

### 2024-11-25 datapreptrynew.Rmd
prettyplotsindescriptives
firstfinalpushmaybe

@@
 ```{r data}
-scholars <- fload("./data/processed/scholars_20240924.rda") #make sure to lead fload first ofcourse
+scholars <- fload("./data/processed/scholars_20240924.rda") 
 ```
@@
 
-# USE not all but first or last so the ties are directed from "perspective" of first author of the publications 
-# usually first most prestige
-
 ```
 
- note to self:look at publications website (sunbelt workshop)
+# Saving data
 
-# Gender
-
-## saving data for each department 
 This part, despite being lengthy and principally unnecessary, needed to stay in my code for the sake of transparency.
-AFterall, this code is what accumulated in the gender-data of each department in my data set.
+AFterall, this code and the following code on this page is what accumulated in the gender-data of each department in my data set.
 
 ```{r}
-#inspecting scholars_20240924.rda object
-#df_ego <- do.call(rbind.data.frame, scholars$demographics)
-#unique(df_ego$discipline.22)
 
@@
 
-#### soc department save
+## Sociology Department
 
@@
 
-#### polsci department save
+## Political Science Department
 
@@
 
-### gender - sociology department
+# Gender
+### Sociology Department SCholars
 
@@
 
-### gender - polsci
+### Politicla Science Scholars
 
@@
 
-### save gender data sets
+Save gender data
 
@@
 
-### Combine data (gender)
+Combine data
 
@@
 ```
+
+Throughout my code I will use two data sets called "scholars_..." and called "ego_df_...".
+I am aware that it would be more convenient to use a single dataset as a fondation for many analyses.
+However, as I went down a few rabbit holes in trying to prepare my data, a lot of my code relied on either two fo these data frames.
+I had passed a 'point of no return' in terms of the data frames and files I generated as re-doing this part yielded in messing up most of the code for other parts of this project.
+Hence, the two data sets.

### 2024-11-25 finaldata.Rmd
firstfinalpushmaybe

@@
 author: "Verooo"
-date: "2024-11-25"
+date: "2024-11-23"
 output: html_document
@@
 ```
-
-<!-- This work? -->
 
@@
 During the initial phase of data collection, all important information regarding the author's position, university affiliation, names, IDs, departments, and more was gathered.
-The coordinator of this course, Jochem Tolsma, has provided a dataset with said information to be used in this project (**source sunbelt?** ).
+The coordinator of this course, Jochem Tolsma, has provided a dataset with said information to be used in this project.
 'OpenAlex' was used to scrape all published works, including important work-related information such as work id, concepts, citations, abstracts, and subjects, up until 2024 (@Priem2022).
@@
 SIENA version 4.0, also known as RSiena, is a package for the R statistical software and was developed by Ruth Ripley and Krists Boitmanis, in collaboration with Tom Snijders (@RSiena_package, @RSiena_manual).
-The use of RSiena for this project is highly based on the practical information provided in "[Social Network Analysis for Social Scientists](https://jochemtolsma.github.io/SNA-4-Social-Scientists/)**"** (@SNASS).
+The use of RSiena for this project is highly based on the practical information provided in "[Social Network Analysis for Social Scientists](https://jochemtolsma.github.io/SNA-4-Social-Scientists/)" (@SNASS).
 

### 2024-11-25 finaldataprep.Rmd
firstfinalpushmaybe

@@
 ---
-```{=html}
-<style>
-body {
-text-align: left;
-line-height: 1.5;
-}
 
-h1, .h1, h2, .h2, h3, .h3 {
-  margin-top: 24px;
-  line-height: 1;
-}
+<html lang="en">
 
-</style>
-```
+<head>
+
+<meta charset="UTF-8">
+
+<meta name="viewport" content="width=device-width, initial-scale=1.0">
+
+<title>My Models</title>
+
+<link rel="stylesheet" href="styles.css"> <!-- Link to the CSS file I created for dark mode code chunks -->
+
+</head>
+
+</html>
 
@@
 ```
+
+# Getting started
+
+```{r clean}
+rm(list = ls())
+```
+
+## Packages
+
+```{r package}
+require(tidyverse)
+require(RSiena)
+require(RsienaTwoStep)
+
+#install.packages("data.table")
+require(data.table)  # mainly for faster data handling
+# install.packages('xml2')
+require(xml2)
+# install.packages('rvest')
+require(rvest)
+require(igraph)
+
+require(ggraph)
+#install.packages('visNetwork')
+require(visNetwork)
+#install.packages('threejs')
+require(threejs)
+#install.packages('networkD3')
+require(networkD3)
+
+```
+
+## Functions
+
+```{r functions 1}
+fpackage.check <- function(packages) {
+    lapply(packages, FUN = function(x) {
+        if (!require(x, character.only = TRUE)) {
+            install.packages(x, dependencies = TRUE)
+            library(x, character.only = TRUE)
+        }
+    })
+}
+
+fsave <- function(x, file = NULL, location = "./data/processed/") {
+    ifelse(!dir.exists("data"), dir.create("data"), FALSE)
+    ifelse(!dir.exists("data/processed"), dir.create("data/processed"), FALSE)
+    if (is.null(file))
+        file = deparse(substitute(x))
+    datename <- substr(gsub("[:-]", "", Sys.time()), 1, 8)
+    totalname <- paste(location, file, "_", datename, ".rda", sep = "")
+    save(x, file = totalname)  #need to fix if file is reloaded as input name, not as x. 
+}
+
+fload <- function(filename) {
+    load(filename)
+    get(ls()[ls() != "filename"])
+}
+
+fshowdf <- function(x, ...) {
+    knitr::kable(x, digits = 2, "html", ...) %>%
+        kableExtra::kable_styling(bootstrap_options = c("striped", "hover")) %>%
+        kableExtra::scroll_box(width = "100%", height = "300px")
+}
+
+# this is the most important one. We created it in the previous script
+
+f_pubnets <- function(df_scholars = df, list_publications = publications, discip = "sociology"+"political science", affiliation = "RU",
+    waves = list(wave1 = c(2018, 2019, 2020), wave2 = c(2021, 2022, 2023))) {
+
+    publications <- list_publications %>%
+        bind_rows() %>%
+        distinct(title, .keep_all = TRUE)
+
+    df_scholars %>%
+        filter(affil1 == affiliation | affil2 == affiliation) %>%
+        filter(discipline == discip) -> df_sel
+
+    networklist <- list()
+    for (wave in 1:length(waves)) {
+        networklist[[wave]] <- matrix(0, nrow = nrow(df_sel), ncol = nrow(df_sel))
+    }
+
+    publicationlist <- list()
+    for (wave in 1:length(waves)) {
+        publicationlist[[wave]] <- publications %>%
+            filter(gs_id %in% df_sel$gs_id) %>%
+            filter(year %in% waves[[wave]]) %>%
+            select(author) %>%
+            lapply(str_split, pattern = ",")
+    }
+
+    publicationlist2 <- list()
+    for (wave in 1:length(waves)) {
+        publicationlist2[[wave]] <- publicationlist[[wave]]$author %>%
+            # lowercase
+        lapply(tolower) %>%
+            # Removing diacritics
+        lapply(stri_trans_general, id = "latin-ascii") %>%
+            # only last name
+        lapply(word, start = -1, sep = " ") %>%
+            # only last last name
+        lapply(word, start = -1, sep = "-")
+    }
+
+    for (wave in 1:length(waves)) {
+        # let us remove all publications with only one author
+        remove <- which(sapply(publicationlist2[[wave]], FUN = function(x) length(x) == 1) == TRUE)
+        publicationlist2[[wave]] <- publicationlist2[[wave]][-remove]
+    }
+
+    for (wave in 1:length(waves)) {
+        pubs <- publicationlist2[[wave]]
+        for (ego in 1:nrow(df_sel)) {
+            # which ego?
+            lastname_ego <- df_sel$lastname[ego]
+            # for all publications
+            for (pub in 1:length(pubs)) {
+                # only continue if ego is author of pub
+                if (lastname_ego %in% pubs[[pub]]) {
+                  aut_pot <- which.max(pubs[[pub]] %in% lastname_ego)
+                  # only continue if ego is first author of pub
+                  if (aut_pot == 1) {
+                    # check all alters/co-authors
+                    for (alter in 1:nrow(df_sel)) {
+                      # which alter
+                      lastname_alter <- df_sel$lastname[alter]
+                      if (lastname_alter %in% pubs[[pub]]) {
+                        networklist[[wave]][ego, alter] <- networklist[[wave]][ego, alter] + 1
+                      }
+                    }
+                  }
+                }
+            }
+        }
+    }
+    return(list(df = df_sel, network = networklist))
+}
+
+```
+
+## More functions
+
+```{r functions 2}
+fcolnet <- function(data = scholars, university = "RU", discipline = "sociology"+"political science", waves = list(c(2015,
+    2018), c(2019, 2023)), type = c("first")) {
+
+    # step 1
+    demographics <- do.call(rbind.data.frame, data$demographics)
+    demographics <- demographics %>%
+        mutate(Universiteit1.22 = replace(Universiteit1.22, is.na(Universiteit1.22), ""), Universiteit2.22 = replace(Universiteit2.22,
+            is.na(Universiteit2.22), ""), Universiteit1.24 = replace(Universiteit1.24, is.na(Universiteit1.24),
+            ""), Universiteit2.24 = replace(Universiteit2.24, is.na(Universiteit2.24), ""), discipline.22 = replace(discipline.22,
+            is.na(discipline.22), ""), discipline.24 = replace(discipline.24, is.na(discipline.24), ""))
+
+    sample <- which((demographics$Universiteit1.22 %in% university | demographics$Universiteit2.22 %in%
+        university | demographics$Universiteit1.24 %in% university | demographics$Universiteit2.24 %in%
+        university) & (demographics$discipline.22 %in% discipline | demographics$discipline.24 %in% discipline))
+
+    demographics_soc <- demographics[sample, ]
+    scholars_sel <- lapply(scholars, "[", sample)
+
+    # step 2
+    ids <- demographics_soc$au_id
+    nwaves <- length(waves)
+    nets <- array(0, dim = c(nwaves, length(ids), length(ids)), dimnames = list(wave = 1:nwaves, ids,
+        ids))
+    dimnames(nets)
+
+    # step 3
+    df_works <- tibble(works_id = unlist(lapply(scholars_sel$work, function(l) l$id)), works_author = unlist(lapply(scholars_sel$work,
+        function(l) l$author), recursive = FALSE), works_year = unlist(lapply(scholars_sel$work, function(l) l$publication_year),
+        recursive = FALSE))
+
+    df_works <- df_works[!duplicated(df_works), ]
+
+    # step 4
+    if (type == "first") {
+        for (j in 1:nwaves) {
+            df_works_w <- df_works[df_works$works_year >= waves[[j]][1] & df_works$works_year <= waves[[j]][2],
+                ]
+            for (i in 1:nrow(df_works_w)) {
+                ego <- df_works_w$works_author[i][[1]]$au_id[1]
+                alters <- df_works_w$works_author[i][[1]]$au_id[-1]
+                if (sum(ids %in% ego) > 0 & sum(ids %in% alters) > 0) {
+                  nets[j, which(ids %in% ego), which(ids %in% alters)] <- 1
+                }
+            }
+        }
+    }
+
+    if (type == "last") {
+        for (j in 1:nwaves) {
+            df_works_w <- df_works[df_works$works_year >= waves[[j]][1] & df_works$works_year <= waves[[j]][2],
+                ]
+            for (i in 1:nrow(df_works_w)) {
+                ego <- rev(df_works_w$works_author[i][[1]]$au_id)[1]
+                alters <- rev(df_works_w$works_author[i][[1]]$au_id)[-1]
+                if (sum(ids %in% ego) > 0 & sum(ids %in% alters) > 0) {
+                  nets[j, which(ids %in% ego), which(ids %in% alters)] <- 1
+                }
+            }
+        }
+    }
+
+    if (type == "all") {
+        for (j in 1:nwaves) {
+            df_works_w <- df_works[df_works$works_year >= waves[[j]][1] & df_works$works_year <= waves[[j]][2],
+                ]
+            for (i in 1:nrow(df_works_w)) {
+                egos <- df_works_w$works_author[i][[1]]$au_id
+                if (sum(ids %in% egos) > 0) {
+                  nets[j, which(ids %in% egos), which(ids %in% egos)] <- 1
+                }
+            }
+        }
+    }
+    output <- list()
+    output$data <- scholars_sel
+    output$nets <- nets
+    return(output)
+}
+```
+
+## Load data
+
+```{r data}
+scholars <- fload("./data/processed/scholars_20240924.rda") 
+```
+
+```{r saving output}
+# save the output of your function
+
+test  <- fcolnet(data = scholars, 
+                university = "RU", 
+                discipline = c("sociology", "political science"),
+                waves = list(c(2015, 2018), c(2019, 2023)), 
+                type = c("all")) # all, first, last # which ties in there
+
+```
+
+# Saving data
+
+This part, despite being lengthy and principally unnecessary, needed to stay in my code for the sake of transparency.
+AFterall, this code and the following code on this page is what accumulated in the gender-data of each department in my data set.
+
+```{r}
+
+# save the output of your function
+testsoc  <- fcolnet(data = scholars, 
+                university = "RU", 
+                discipline = "sociology", 
+                waves = list(c(2015, 2018), c(2019, 2023)),
+
+                            type = c("first"))
+
+testpolsci <- fcolnet(data = scholars, 
+                university = "RU", 
+                discipline = "political science", 
+                waves = list(c(2015, 2018), c(2019, 2023)), 
+                type = c("first"))
+```
+
+## Sociology Department
+
+```{r}
+soc_nets <- testsoc$nets
+
+df_ego_demo <- testsoc$data$demographics
+df_ego_oa <- testsoc$data$scholars_oa
+df_ego_works <- testsoc$data$works
+
+# DEMO
+  str(df_ego_demo, 1)
+
+  df_ego_demo <- do.call(rbind.data.frame, df_ego_demo)
+  df_ego_demo[[1]]
+
+# OA
+  #str(df_ego_oa, 1)
+  df_ego_oa[[1]]
+  df_ego_oa <- do.call(rbind.data.frame, df_ego_oa)
+
+  # --> EGO DATAFRAME with demo and oa (sociology)
+
+  df_soc_ego <- left_join(df_ego_demo, df_ego_oa, by = join_by(au_id == id))
+
+  rownames(soc_nets[1,,]) == df_soc_ego$au_id # checking if the author id's are the same as in df_ego in nets dataframe 
+  # --> yes, the correct ones!!!
+
+  df_ego_works[[1]]$author 
+#authors of all the works that first scholar (here: Ana Macanovic) is part of
+
+```
+
+## Political Science Department
+
+```{r}
+# dependent
+# pol_net <- sienaDependent(net_pol_array)
+
+# dependent 
+pol_nets <- testpolsci$nets
+
+df_pol_ego_demo <- testpolsci$data$demographics
+df_pol_ego_oa <- testpolsci$data$scholars_oa
+df_pol_ego_works <- testpolsci$data$works
+
+# DEMO
+  #str(df_pol_ego_demo, 1)
+
+  df_pol_ego_demo <- do.call(rbind.data.frame, df_pol_ego_demo)
+  df_pol_ego_demo[[1]]
+
+# OA
+  #str(df_pol_ego_oa, 1)
+  df_pol_ego_oa[[1]]
+  df_pol_ego_oa <- do.call(rbind.data.frame, df_pol_ego_oa)
+
+# --> EGO DATAFRAME with demo and oa (political science)
+  df_pol_ego <- left_join(df_pol_ego_demo, df_pol_ego_oa, by = join_by(au_id == id))
+
+  rownames(pol_nets[1,,]) == df_pol_ego$au_id # checking if the author id's are the same as in df_ego in nets dataframe 
+  # --> yes, the correct ones!!!
+```
+
+# Gender
+### Sociology Department SCholars
+
+```{r gender s}
+df_soc_ego$Naam # list of all names in sociology department
+
+df_soc_ego$gender <- c(0,1,0,1,0,0,1,1,0,0,
+                       0,1,1,0,1,0,1,1,1,1,
+                       0,1,1,0,1,1,0,1,0,1,
+                       0,1,0,0,0,0,0,0,1,0,
+                       0,1,1,1,0,1,0,1,0,0) 
+# manually filled in gender 0 = woman, 1 = man, based on majority given in NL voornamen bank
+
+# check if it went smoothly 
+# view(df_soc_ego[c('Naam', 'gender', 'au_id')])
+
+# fsave(df_soc_ego)
+
+```
+
+### Politicla Science Scholars
+
+```{r gender p}
+df_pol_ego$Naam # list of all names
+
+df_pol_ego$gender <- c(1,0,1,0,0,0,1,0,1,0,
+                       1,1,0,0,1,1,1,0,0,1,
+                       0,1,1,0,0,1,1,1,0,0,
+                       0,0,0,1,1,0,0,1,1,0,
+                       0,0,0,1,0,1,1,1,0,0,0) 
+    # manually filled in gender 0 = woman, 1 = man, based on majority given in NL voornamen bank, Guangyu was not in name bank but based on the employee-picture of RU, this person presents feminine, thus I assumed 0.
+
+# check if it went smoothly 
+# view(df_pol_ego[c('Naam', 'gender', 'au_id')])
+
+#covariate 
+# gender <- coCovar(df_ego$gender)
+
+# fsave(df_pol_ego)
+```
+
+Save gender data
+
+```{r gender data}
+soc_gender <- fload("./data/processed/df_soc_ego_20241105.rda")
+pol_gender <- fload("./data/processed/df_pol_ego_20241105.rda")
+```
+
+Combine data
+
+```{r combine gender set}
+df <- test$data # make dataset with all data 
+df_ego <- do.call(rbind.data.frame, df$demographics) # data set with demographic information
+
+soc_gender <- soc_gender[,c("Naam", "gender")] # selecting only the content we need
+pol_gender <- pol_gender[,c("Naam", "gender")] # selecting only the content we need
+
+gender <- rbind(soc_gender, pol_gender) # combining the gender data sets
+
+df_ego <- df_ego %>% 
+            left_join(gender) #dcombining data set of gender with the one with demographic information 
+```
+
+# H-index
+
+Credits to Lucan Bovens for the code.
+
+```{r h-index}
+# Add h-index and i10-index columns to df_ego
+df_ego <- df_ego %>%
+  mutate(h_index = NA_real_, i10_index = NA_real_)
+
+# Get H-index and i10-index 
+get_openalex_metrics <- function(openalex_id) {
+  url <- paste0("https://api.openalex.org/authors/", openalex_id)
+  author_data <- tryCatch({
+    jsonlite::fromJSON(url)
+  }, error = function(e) {
+    message(paste("Error fetching data for OpenAlex ID:", openalex_id))
+    return(NULL)
+  })
+
+  if (!is.null(author_data)) {
+    h_index <- author_data$summary_stats$h_index
+    i10_index <- author_data$summary_stats$i10_index
+    works_count <- author_data$works_count
+    cited_by_count <- author_data$cited_by_count
+    return(list(h_index = h_index, i10_index = i10_index, works_count = works_count, cited_by_count = cited_by_count))
+  } else {
+    return(list(h_index = NA, i10_index = NA, works_count = NA, cited_by_count = NA))
+  }
+}
+
+# Loop for each scholar 
+for (i in 1:nrow(df_ego)) {
+  openalex_id <- df_ego$au_id[i]  # assuming au_id is the OpenAlex ID in df_ego
+  metrics <- get_openalex_metrics(openalex_id)
+  df_ego$h_index[i] <- metrics$h_index
+  df_ego$i10_index[i] <- metrics$i10_index
+  df_ego$works_count[i] <- metrics$works_count
+  df_ego$cited_by_count[i] <- metrics$cited_by_count
+}
+
+# View updated df_ego with h-index and i10-index
+view(df_ego[c('au_id','Naam','gender','h_index','i10_index')])
+
+# fsave(df_ego)
+
+```
+
+Throughout my code I will use two data sets called "scholars_..." and called "ego_df_...".
+I am aware that it would be more convenient to use a single dataset as a fondation for many analyses.
+However, as I went down a few rabbit holes in trying to prepare my data, a lot of my code relied on either two fo these data frames.
+I had passed a 'point of no return' in terms of the data frames and files I generated as re-doing this part yielded in messing up most of the code for other parts of this project.
+Hence, the two data sets.

### 2024-11-25 finaldiscussion.Rmd
firstfinalpushmaybe

@@
 The parameter for same-gender collaboration (sameX) remains positive and significant, indicating that scholars are more likely to collaborate with same-gender peers than with different-gender peers.
-This aligns with previous research suggesting that gendered barriers in academia, whether structural or cultural, can lead to gender clustering in collaborative networks (@Horta2022; @Kwiek2021; @McPherson2001).
-
+This aligns with previous research suggesting that gendered barriers in academia, whether structural or cultural, can lead to gender clustering in collaborative networks (@Horta2022; @Kwiek2021; @McPherson2001).\
 Interestingly, the significance of gender clustering persists even after controlling for other covariates, such as department affiliation and h-index, demonstrating that it is a robust phenomenon in these networks.
@@
 While this hypothesis was not explicitly tested using an interaction term, comparisons across models suggest no substantial department-level differences in gender clustering.
-The same-gender collaboration parameter (sameX for gender) is nearly identical in models 2 and 3, indicating that the inclusion of department as a covariate does not significantly alter the pattern of same-gender collaborations.
-
+The same-gender collaboration parameter (sameX for gender) is nearly identical in models 2 and 3, indicating that the inclusion of department as a covariate does not significantly alter the pattern of same-gender collaborations.\
 However, the department-related parameter for ego’s tendency to initiate collaborations (egoX for department) becomes significant in model 4, revealing a lower likelihood for political scientists to initiate collaborations compared to sociologists.
@@
 An interaction term between department and gender would have been useful to further investigate these nuances.
-
 After all, hypothesis 2 was not supported.
@@
 Interestingly, the outdegree parameter (baseline likelihood of initiating a tie) fluctuates in significance across models but remains consistently negative when significant, indicating that scholars generally show a low tendency to initiate collaborations.
-
 In line with Hypothesis 3, Gender homophily (sameX) remains significant even when controlling for these structural effects, reinforcing its importance.
@@
 The inclusion of h-index as a covariate in model 4 reveals that scholars with higher h-index scores are more likely to attract collaborations (significant positive alter effect, altX) but less likely to initiate them (significant negative ego effect, egoX).
-This is consistent with theories of preferential attachment and upward mobility, where prestigious scholars act as hubs, receiving collaboration requests rather than initiating them (@Broido2019; @Knobloch2013).
-
+This is consistent with theories of preferential attachment and upward mobility, where prestigious scholars act as hubs, receiving collaboration requests rather than initiating them (@Broido2019; @Knobloch2013).\
 However, since the the same-gender parameter (sameX) remained significant and largely unchanged, the influence of genderhomophily on scholars' decisions to collaborate is not substantially impacted by scholars' h-index.
@@
 Gender homophily appears to be a robust and enduring feature of these networks, resisting the influence of prestige and departmental context.
-This raises important questions about the structural barriers faced by scholars, particularly women, in accessing diverse collaboration opportunities.
-
+This raises important questions about the structural barriers faced by scholars, particularly women, in accessing diverse collaboration opportunities.\
 From a policy perspective, these results underscore the need for initiatives aimed at reducing gendered collaboration clustering.
@@
 Finally, the examined sample is arguably small, and the generalizability of these findings is further limited to the specific departments and network structures examined here.
-
+\
 Future research should explore longitudinal changes in collaboration patterns to assess whether gender homophily weakens over time, particularly as scholars gain prestige.

### 2024-11-25 finalestimate.Rmd
firstfinalpushmaybe

@@
 
+------------------------------------------------------------------------
+
 # Analysis - Model Estimation
@@
 supports H1, which posits gender homophily in collaboration patterns.
-
 Model 2 provides strong evidence for gender homophily (H1), with
@@
 investigate differences in same-gender collaboration patterns based on
-the two departments.
-
-Originally, I planned to also include an interaction term of departm_RS
-and gender_RS to obtain clearer insights into variations in patterns of
-gender homophily in relation to scholars' departments. However, I have
-refrained from adding another model to this project. I decided against
-this partly due to time constraints but I also reason that I can use the
-comparison of model 2 and 3 to examine changes in the estimate of
-'sameX' (gender), to *tentatively* infer whether the department of
-scholars modifies the collaboration patterns at hand.
+the two departments. Originally, I planned to also include an
+interaction term of departm_RS and gender_RS to obtain clearer insights
+into variations in patterns of gender homophily in relation to scholars'
+departments. However, I have refrained from adding another model to this
+project. I decided against this partly due to time constraints but I
+also reason that I can use the comparison of model 2 and 3 to examine
+changes in the estimate of 'sameX' (gender), to *tentatively* infer
+whether the department of scholars modifies the collaboration patterns
+at hand.
 
 Model 3 has a maximum convergence ratio of **0.182** and a Goodness of
-Fit on the indegree distribution of **0.108**.
-
-Interestingly, the estimate for outdegree (density) that had lost its
-significance in model 2, is now back to being significant and negative
-(b = -4.3233, SE = 1.0871).
-
-In terms of estimate size and significance of the structural network
-statistics we, once again, find similar patterns as in models 1 and 2.
-However, the outdegree parameter has now reached significance (b =
--4.3233, SE = 1.0871).
+Fit on the indegree distribution of **0.108**. Interestingly, the
+estimate for outdegree (density) that had lost its significance in model
+2, is now back to being significant and negative (b = -4.3233, SE =
+1.0871). In terms of estimate size and significance of the structural
+network statistics we, once again, find similar patterns as in models 1
+and 2. However, the outdegree parameter has now reached significance (b
+= -4.3233, SE = 1.0871).
 
@@
 collaborate with people from their own department, indicating
-**department-based homophily**. (b = 2.7240, SE = 0.7277).
-
-Model 3 highlights persistent gender homophily (H1) across departments
-but does not provide evidence for differences in gender homophily
-between Sociology and Political Science, contrary to H2.
+**department-based homophily**. (b = 2.7240, SE = 0.7277). Model 3
+highlights persistent gender homophily (H1) across departments but does
+not provide evidence for differences in gender homophily between
+Sociology and Political Science, contrary to H2.
 
@@
 Model 4 has a maximum convergence ratio of **0.23,** and a a Goodness of
-Fit on the indegree distribution of **0.197**.
-
+Fit on the indegree distribution of **0.197**. \
 **Structural network statistics.** The estimate for outdegree is
@@
 significantly positive ( b = 5.4634, SE = 2.2770), indicating that as
-isolates tend to remain isolated.
-
+isolates tend to remain isolated.\
 **Gender.** Similar to AltX and EgoX in prior models, both an alter's
@@
 covariate 'H-Index' did not prompt any major changes in scholars'
-preferences for same-gendered collaborators.
-
+preferences for same-gendered collaborators.\
 **Department.** While an alter's departmen**t** (AltX) remained
@@
 significant positive estimate (b = 2.6327, SE = 0.6080) scholars are
-still more likely to collaborate with others from the same department.
-
+still more likely to collaborate with others from the same department.\
 **H-Index**. Both an alter's and an ego's H-Index seem to be relevant in
@@
 negative (b = -0.1591, SE = 0.0744) suggesting that scholars with higher
-h-index are less likely to initiate collaborations.
-
+h-index are less likely to initiate collaborations.\
 The results partially support **H4**, as the h-index is shown to

### 2024-11-25 finalintro.Rmd
firstfinalpushmaybe

@@
 knitr::opts_chunk$set(echo = TRUE)
+```
 
-```
+------------------------------------------------------------------------
+
+# Introduction
+
+## Contextualization
+
+Collaboration has become a cornerstone of modern academic practice, with scholars increasingly working together to leverage diverse expertise, share resources, and enhance their research output.
+Co-authorship, in particular, is a key indicator of collaboration, often reflecting the dynamics of professional relationships and the distribution of academic opportunities.
+As Cheong (@Cheong2009) highlights, collaboration enables researchers to combine intellectual and institutional resources, contributing significantly to their scholarly success.
+However, collaboration is not free from social patterns and biases.
+Academic networks often mirror broader societal inequalities, with persistent disparities in opportunities and recognition.
+One such disparity id gender inequality, which continues to shape interactions, opportunities, and outcomes within academia.
+
+## Research Problem and Goal
+
+In this study, I examine the role of gender homophily in shaping co-authorship networks in the Sociology and Political Science Departments at Radboud University.
+Gender homophily refers to the tendency of individuals to collaborate with others of the same gender.
+This phenomenon can influence who gains access to collaboration opportunities, thereby shaping academic trajectories and reinforcing existing inequalities.
+Understanding these dynamics is essential to uncovering how collaboration networks may perpetuate or lessen gender-based disparities in academia.
+
+## Prior findings
+
+### Gender and Collaboration
+
+Previous research has consistently shown that gender plays a significant role in academic collaboration.
+Horta and colleagues (@Horta2022) reveal that male researchers are more likely to collaborate with other men, while female researchers exhibit a weaker but still present tendency towards homophily.
+Kwiek and Roszka (@Kwiek2021) found that such patterns contributes to the persistence of gender imbalances in co-authorship, where all-male teams remain more common than all-female teams.
+These trends are particularly concerning in fields such as Sociology and Political Science, where collaboration is vital for career advancement (@Cheong2009).
+The structure of these networks affects not only who collaborates but also how academic recognition and resources are distributed (@Cheong2009).
+For example, male-dominated networks may provide better access to high-impact collaborations and grant opportunities for men, further perpetuating the gender gap in academic successes.
+
+### Prestige and Collaboration
+
+Another crucial factor influencing collaboration id academic prestige.
+Scholars with higher prestige, indicated by metrics such as the h-index or publication in top-tier journals, are generally more sought after as collaborators.
+Existing research suggests that prestige might interact with gender homophily in significant ways.
+Bellotti et al.
+(@Bellotti2022) found that prestigious male scholars often form networks that exclude women, while McDowell and colleagues (@Mcdowell2007) also observed that female scholars, despite demonstrating similar academic competence, face greater challenges in accessing high-prestige collaborative networks.
+In this context, it is crucial to explore whether the tendency for gender-based collaboration shifts when prestige factors come into play.
+Specifically, do scholars' h-indeces exacerbate gender homophily in academic networks?
+
+## Research Focus and Questions
+
+This study aims to analyze gender homophily within the co-authorship networks of the Sociology and Political Science Departments at Radboud University, focusing on the role of prestige.
+The research is guided by the following questions:
+
+-   ***RQ1a:** To what extent does gender homophily occur across all co-publications of the staff in the Sociology and Political Science Departments at Radboud University?*
+
+-   ***RQ1b:** To what extent do the two departments differ in their levels of gender homophily?*
+
+These questions focus on descriptive patterns, providing a macro-level view of gender clustering in academic networks.
+
+-   ***RQ2:** To what extent can gender homophily in collaboration networks be explained by preferences at the dyadic level, controlling for structural network and individual-level covariates?*
+
+This question shifts the focus to the micro-level, examining whether individual choices and structural factors drive homophily in co-authorship.
+
+-   **RQ3:** How does the prestige of scholars, measured by scholars' h-index, influence gender homophily in co-authorship networks?
+
+This question explores whether prestige interacts with gender homophily, shedding light on how academic recognition impacts collaborative behaviors.
+Specifically, it investigates whether male and female scholars with similar prestige levels experience different patterns of collaboration and whether prestige reduces or amplifies gender clustering.
+
+## Relevance and Contribution
+
+This study contributes to the growing body of literature on gender inequalities in academia by focusing on the intersection of gender and academic prestige in shaping collaboration networks.
+By applying a social network perspective, it offers insights into how gender-based preferences influence co-authorship patterns and how these dynamics vary between disciplines.
+Moreover, by exploring the role of journal prestige, this research highlights how structural factors may intersect with social biases to shapw academic opportunities, providing a nuanced understanding of the mechanisms underlying gender disparities in academia.
+
+------------------------------------------------------------------------
+
+# References

### 2024-11-25 finaldata.Rmd
finalpushh

@@
 title: "Data & Analysis"
-author: "Verooo"
+author: "Vero Palm"
 date: "2024-11-23"

### 2024-11-25 finalestimate.Rmd
finalpushh

@@
 title: "Model Estimation"
-author: "Verooo"
+author: "Vero Palm"
 date: "2024-11-23"

### 2024-11-25 index.Rmd
finalpushh

@@
 title: "Lab journal"
-author: "by: Verooo"
+author: "by: Vero Palm"
 bibliography: references.bib
@@
 # First page of something totally awesome yes.
+Last compiled on `r format(Sys.time(), '%B, %Y')`
+*Description: Very cool lab journal. Yes, yes.*
+
+## Cool keybinds
 
@@
 [STR + SHIFT + C can make a comment of multiple lines you highlighted]{.smallcaps}
-
-Last compiled on `r format(Sys.time(), '%B, %Y')`
-
-*Description: Very cool lab journal. Yes, yes.*
 
@@
 ```
+
 ## Open Science
 
-Everyone can fork this repository. Use this example to journal your lab work and assignments.
+Everyone can fork this repository. I have used this example to journal my lab work and assignments.
 
-We, Jochem Tolsma and Bas Hofstra, use this repository for our Social Network Analysis For Social Scientists course [@SNASS].
+Jochem Tolsma and Bas Hofstra use this repository for their Social Network Analysis For Social Scientists course [@SNASS].
 <!--- this is a reference, stored in references.bib.
@@
 
-treeeeees
 :::
@@
 ![](images/krill-issue.jpg)
+
+Very krillaxing, isn't it?
+
 :::
 :::
+
+**Reference:**
